### 2018-06-22 paper/main.tex
project started

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Masters/Doctoral Thesis
% LaTeX Template
% Version 2.5 (27/8/17)
%
% This template was downloaded from:
% http://www.LaTeXTemplates.com
%
% Version 2.x major modifications by:
% Vel (vel@latextemplates.com)
%
% This template is based on a template by:
% Steve Gunn (http://users.ecs.soton.ac.uk/srg/softwaretools/document/templates/)
% Sunil Patel (http://www.sunilpatel.co.uk/thesis-template/)
%
% Template license:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters

\usepackage{mathpazo} % Use the Palatino font by default

\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

\addbibresource{example.bib} % The filename of the bibliography

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

%----------------------------------------------------------------------------------------
%	MARGIN SETTINGS
%----------------------------------------------------------------------------------------

\geometry{
	paper=a4paper, % Change to letterpaper for US letter
	inner=2.5cm, % Inner margin
	outer=3.8cm, % Outer margin
	bindingoffset=.5cm, % Binding offset
	top=1.5cm, % Top margin
	bottom=1.5cm, % Bottom margin
	%showframe, % Uncomment to show how the type block is set on the page
}

%----------------------------------------------------------------------------------------
%	THESIS INFORMATION
%----------------------------------------------------------------------------------------

\thesistitle{The timing of Carbonhydrate intake in the NDNS 2008-2014 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{MSc in Medical Statistics} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Chaochen \textsc{Wang}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

\subject{Medical Statistics} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{https://www.lshtm.ac.uk/}{London School of Hygiene and Tropical Medicine}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{}{Page count: XX page from Introduction to Conclusions}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{Candidate number: 110765} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{http://faculty.university.com}{Faculty Name}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

\AtBeginDocument{
\hypersetup{pdftitle=\ttitle} % Set the PDF's title to your title
\hypersetup{pdfauthor=\authorname} % Set the PDF's author to your name
\hypersetup{pdfkeywords=\keywordnames} % Set the PDF's keywords to your keywords
}

\begin{document}

\frontmatter % Use roman page numbering style (i, ii, iii, iv...) for the pre-content pages

\pagestyle{plain} % Default to the plain heading style until the thesis style is called for the body content

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage}

\includegraphics[width=45mm]{logos.jpg} % University/department logo - uncomment to place it
\begin{center}

\vspace*{.06\textheight}
{\scshape\Huge \bfseries \univname\par}\vspace{1.5cm} % University name
\textsc{\Large MSc Project Report \\ 2017-2018}\\[0.5cm] % Thesis type

\HRule \\[0.4cm] % Horizontal line
{\Large \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
\HRule \\[1.5cm] % Horizontal line

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\href{wangcc.me}{\authorname} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
\href{https://www.lshtm.ac.uk/aboutus/people/palla.luigi}{\supname} % Supervisor name - remove the \href bracket to remove the link
\end{flushright}
\end{minipage}\\[3cm]

\vfill

\large \textit{Submitted in part fulfillment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
%\textit{in the}\\[0.4cm]
\groupname\\\deptname\\[2cm] % Research group name and department name

\vfill

{\large \today}\\[4cm] % Date

\vfill
\end{center}
\end{titlepage}

%----------------------------------------------------------------------------------------
%	DECLARATION PAGE
%----------------------------------------------------------------------------------------

\begin{declaration}
\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:

\begin{itemize}
\item This work was done wholly or mainly while in candidature for a research degree at this University.
\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
\end{itemize}

\noindent Signed:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature

\noindent Date:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}

\cleardoublepage

%----------------------------------------------------------------------------------------
%	QUOTATION PAGE
%----------------------------------------------------------------------------------------

\vspace*{0.2\textheight}

\noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak

\hfill Dave Barry

%----------------------------------------------------------------------------------------
%	ABSTRACT PAGE
%----------------------------------------------------------------------------------------

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
\end{abstract}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
\end{acknowledgements}

%----------------------------------------------------------------------------------------
%	LIST OF CONTENTS/FIGURES/TABLES PAGES
%----------------------------------------------------------------------------------------

\tableofcontents % Prints the main table of contents

\listoffigures % Prints the list of figures

\listoftables % Prints the list of tables

%----------------------------------------------------------------------------------------
%	ABBREVIATIONS
%----------------------------------------------------------------------------------------

\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)

\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere\\
\textbf{WSF} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or\\

\end{abbreviations}

%----------------------------------------------------------------------------------------
%	PHYSICAL CONSTANTS/OTHER DEFINITIONS
%----------------------------------------------------------------------------------------

\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table

% The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it

Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
%Constant Name & $Symbol$ & $Constant Value$ with units\\
%testovaci komentar
\end{constants}

%----------------------------------------------------------------------------------------
%	SYMBOLS
%----------------------------------------------------------------------------------------

\begin{symbols}{lll} % Include a list of Symbols (a three column table)

$a$ & distance & \si{\meter} \\
$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
%Symbol & Name & Unit \\

\addlinespace % Gap to separate the Roman symbols from the Greek

$\omega$ & angular frequency & \si{\radian} \\

\end{symbols}

%----------------------------------------------------------------------------------------
%	DEDICATION
%----------------------------------------------------------------------------------------

\dedicatory{For/Dedicated to/To my\ldots}

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - CHAPTERS
%----------------------------------------------------------------------------------------

\mainmatter % Begin numeric (1,2,3...) page numbering

\pagestyle{thesis} % Return the page headers back to the "thesis" style

% Include the chapters of the thesis as separate files from the Chapters folder
% Uncomment the lines as you write the chapters

\include{Chapters/Chapter1}
%\include{Chapters/Chapter2}
%\include{Chapters/Chapter3}
%\include{Chapters/Chapter4}
%\include{Chapters/Chapter5}

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - APPENDICES
%----------------------------------------------------------------------------------------

\appendix % Cue to tell LaTeX that the following "chapters" are Appendices

% Include the appendices of the thesis as separate files from the Appendices folder
% Uncomment the lines as you write the Appendices

\include{Appendices/AppendixA}
%\include{Appendices/AppendixB}
%\include{Appendices/AppendixC}

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\printbibliography[heading=bibintoc]

%----------------------------------------------------------------------------------------

\end{document}

### 2018-06-22 initialise.R

@@ -1,0 +1,1 @@
+setwd("C:/Users/abela/Documents/UKDA-6533-stata11_se/stata11_se/")

### 2018-06-25 paper/main.tex
references added, R code some, paper template confirmed

@@
 
-\addbibresource{example.bib} % The filename of the bibliography
+\addbibresource{summer.bib} % The filename of the bibliography
 
@@
 \vspace*{.06\textheight}
-{\scshape\Huge \bfseries \univname\par}\vspace{1.5cm} % University name
+{\scshape\huge \bfseries \univname\par}\vspace{1.5cm} % University name
 \textsc{\Large MSc Project Report \\ 2017-2018}\\[0.5cm] % Thesis type
@@
 \HRule \\[0.4cm] % Horizontal line
-{\Large \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
+{\Huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
 \HRule \\[1.5cm] % Horizontal line
 
-\begin{minipage}[t]{0.4\textwidth}
-\begin{flushleft} \large
-\emph{Author:}\\
-\href{wangcc.me}{\authorname} % Author name - remove the \href bracket to remove the link
-\end{flushleft}
-\end{minipage}
-\begin{minipage}[t]{0.4\textwidth}
-\begin{flushright} \large
+%\begin{minipage}[t]{0.4\textwidth}
+%\begin{flushleft} \large
+%\emph{Author:}\\
+%\href{wangcc.me}{\authorname} % Author name - remove the \href bracket to remove the link
+%\end{flushleft}
+%\end{minipage}
+%\begin{minipage}[t]{0.4\textwidth}
+%\begin{flushright} \large
 \emph{Supervisor:} \\
 \href{https://www.lshtm.ac.uk/aboutus/people/palla.luigi}{\supname} % Supervisor name - remove the \href bracket to remove the link
-\end{flushright}
-\end{minipage}\\[3cm]
+%\end{flushright}
+%\end{minipage}\\[3cm]
 

### 2018-06-25 phrases.Rmd
references added, R code some, paper template confirmed

---
title: "Some usefull words/expressions/sentences"
output: html_document
---

# Words

- discernable [di'sə:nəbl, -'zə:-]

```
===== 辞典翻译: discernable ======
adj. 可辨别的；可认识的
============ 网络释义 ============
-------- discernable ---------
可辨别的
方向
分辨
-- discernable recognizable --
可辨别的
--- discernable visible ----
可辨别的
```

-   abstinence ['æbstinəns]

```
====== 辞典翻译: abstinence ======
  n. 节制；节欲；戒酒；禁食
============ 网络释义 ============
--------- abstinence ---------
  节制
  禁欲
  禁戒
----- alcohol abstinence -----
  酒戒断
----- Abstinence theory ------
  节欲论
  弃权
  忍欲说
```

-  exhaustive [iɡ'zɔ:stiv]

```
====== 辞典翻译: exhaustive ======
  adj. 详尽的；彻底的；消耗的
============ 网络释义 ============
--------- Exhaustive ---------
  无遗
  详尽的
  全部
----- Exhaustive search ------
  穷举搜索
  穷举搜索完全搜索
  全程搜索
----- exhaustive voting ------
  淘汰投票
  消耗性投票
```

-   temperament ['tempərəmənt]

```
===== 辞典翻译: temperament ======
  n. 气质，性情，性格；急躁
============ 网络释义 ============
-------- temperament ---------
  气质
  气质 (心理学)
  性格
------ Well Temperament ------
  Well temperament
  Well Temperament
  平均律
---- Musical temperament -----
  律学
  一份音乐的气质
  音乐性
```

# Expressions

# Sentences

#### terry2017discontinuous - Discontinuous Patterns of Cigarette Smoking From Ages 18 to 50 in the United States: A Repeated-Measures Latent Class Analysis

- RMLCA models were fitted in SAS 9.4 using PROC LCA. Parameters were estimated by maximum likelihood using the EM algorithm.

- To ascertain if the same latent class structure was observed for males and females, multiple-group RMLCA models by sex were fitted in PROC LCA using the GROUPS statement (both with and without imposing measurement invariance across males and females).

- Model selection (ie, the number of latent classes specified) was determined by model fit, parsimony, and stability.

- Simulations have shown that the Bayesian information criterion (BIC) and sample size-adjusted BIC (a-BIC) perform particularly well at selecting the “correct” latent class model.

- Improvement in both BIC and consistent Akaike information criterion (CAIC) values continued only through the 12-class model; thus, the 12-class model was selected as optimal.

#### lanza2007proc - PROC LCA: A SAS procedure for latent class analysis

- In traditional LCA, two sets of parameters are estimated: class membership probabilities and item-response probabilities conditional on class membership.

- Latent class models usually involve categorical indicators (although a version of LCA involving continuous indicators called latent profile analysis [Gibson, 1959] is being used increasingly).

- When categorical data are used, the latent class model has the advantage of making no assumptions about the distributions of the indicators other than that of local independence; that is, the assumption that within a latent class the indicators are independent.

### 2018-06-25 Rcode/Raoulcodes.R

@@ -1,0 +1,142 @@
+setwd("D:/Dropbox/LSHTM/study/project/6533STATA11/UKDA-6533-stata11_se/stata11_se/")
+install.packages("poLCA")
+# install.packages("ggplot")
+# install.packages("ggplot2")
+library(plyr)
+library(ggplot2)
+source("../../../Rcode/Raoulmycode.R")
+
+
+options(stringsAsFactors=FALSE)
+library(haven)
+data <- read_dta("ndns_rp_yr1-4a_foodleveldietarydata_uk.dta")
+data56 <- read_dta("ndns_rp_yr5-6a_foodleveldietarydata.dta")
+# data <- read.csv("ndns_rp_yr1-4a_foodleveldietarydata_uk.csv", header=TRUE, sep=",")
+# data56 <- read.csv("h:/icarus/data/ndns_rp_yr5-6a_foodleveldietarydata_viastata.csv", header=TRUE, sep=",")
+
+names(data)[names(data)=="seriali"] <- "id"
+names(data56)[names(data56)=="seriali"] <- "id"
+ df14d<-data[,c(113,1,2,3,5,6,7,8,9,21,24,55,57,58,59,60,61,62,63,64)]
+ 
+ names(data)[c(113,1,2,3,5,6,7,8,9,21,24,55,57,58,59,60,61,62,63,64)]
+ # [1] "id"                 "SurveyYear"             
+ # [3] "Age"                     "Sex"                    
+ # [5] "DayofWeek"               "DayNo"                  
+ # [7] "DiaryDaysCompleted"      "MealTimeDescription"    
+ # [9] "MealTime"                "EnergykJ"               
+ # [11] "Carbohydrateg"           "Totalsugarsg"           
+ # [13] "Starchg"                 "Glucoseg"               
+ # [15] "Fructoseg"               "Sucroseg"               
+ # [17] "Maltoseg"                "Lactoseg"               
+ # [19] "Nonmilkextrinsicsugarsg" "Intrinsicandmilksugarsg"
+df56d<-data56[,c(113,1,2,3,5,6,7,8,9,21,24,55,57,58,59,60,61,62,63,64)]
+dfs1<-rbind(df14d,df56d)
+
+
+dfs2<-dfs1[dfs1$Age>=19,]
[…]

### 2018-06-25 Rcode/Raoulmycode.R

@@ -1,0 +1,790 @@
+
+myplot<-function(mylist,mysubtitle) {
+  myclasspr<-round(mylist[[2]],3)
+  myplottext<-paste0(mylist[[3]]," Observations\n")
+  myplottext<-paste0(myplottext,"class pr ",myclasspr[1]," ",myclasspr[2]," ",myclasspr[3],"\n")
+  title<-"Probability of an Eating Occasion \n"
+  myheading<-paste(title,mysubtitle)
+  pr <-mylist[[2]]
+  df2<-mylist[[1]]
+  nobs<-mylist[[1]]
+  ggplot(df2,aes(x=df2$hour)) +
+    geom_line(aes(y = df2$pr1, colour = "Class 1")) +
+    geom_point(aes(y = df2$pr1, colour = "Class 1"),size=0.4) +
+    geom_line(aes(y = df2$pr2, colour = "Class 2")) +
+    geom_point(aes(y = df2$pr2, colour = "Class 2"),size=0.4) +
+    geom_line(aes(y = df2$pr3, colour = "Class 3")) +
+    geom_point(aes(y = df2$pr3, colour = "Class 3"),size=0.4) +
+    scale_colour_manual(name="line key", 
+                        breaks = c("Class 1", "Class 2", "Class 3"),
+                        values = c("red", "green", "blue") ) +
+    ggtitle(myheading) +
+    xlab('hour') +
+    ylab('Probability')+
+    annotate("text", label = myplottext, x=7,y = .03, size = 3, colour = "black",hjust = 0) +
+    scale_x_continuous(breaks = seq(0,22 ,2))
+}
+
+
+mypoLCAfemale <- function(df1, reps) {
+  f <- cbind(h0,h1,h2,h3,h4,h5,h6,h7,h8,h9,h10,h11,h12,h13,h14,h15,h16,h17,h18,h19,h20,h21,h22,h23)~1
+  lc3 <- poLCA(f,df1,nclass=3,graphs = FALSE,nrep=reps)
+  probs.start<-poLCA.reorder(lc3$probs.start,order(lc3$P,decreasing = T))
+  new.probs.start <- poLCA.reorder(probs.start,c(2,1,3))
[…]

### 2018-06-25 Rcode/trying to understand the looping code.R

@@ -1,0 +1,47 @@
+dftmp<-dfs4[dfs4$id==vecid[1],]
+dftmp<-dftmp[,c(1,6,7)]
+dfmin<-data.frame(min=0:1439)
+dfmin$id<-vecid[1]
+dfmin$f1<-FALSE
+
+for (i in 0:1439){
+  if(nrow(dftmp[dftmp$MealMinN0==i,])>=1){
+    dfsub<-subset(dftmp,(MealMinN0>=i & MealMinN0 <(i+(gap-1)))) 
+    if (nrow(dfsub)>0){
+      dfsub2<-ddply(dfsub,~id,summarise,Sum=sum(dfsub$EnergyKJ))
+      if (dfsub2$Sum>energy_threshold){
+        dfmin$f1[[i+1]]<-TRUE
+      }
+    }
+  }
+}
+
+# 
+# dfsub<-subset(dftmp,(MealMinN0>=900 & MealMinN0 <(900+(gap-1)))) 
+# dfsub2<-aggregate(dfsub$EnergyKJAve,by=list(id=dfsub$id),
+#                   FUN=sum, na.rm=TRUE)
+# library(plyr)
+# ddply(dfsub,~id,summarise,Sum=sum(dfsub$EnergyKJ))
+
+
+dfmin$f2<-FALSE
+for (i in 1:1440){
+  if (dfmin$f1[[i]]==TRUE){
+    dfmin$f2[[i]]<-TRUE
+    if (i!=1) {
+      tmp<-min((i-1),gap)
+      for (j in 1:tmp){
+        if(dfmin$f1[[i-j]]==TRUE){
+          dfmin$f2[[i]]<-FALSE
+        }
+      }
+    }
+  }
+}
+
+dfmin$hour<-trunc(dfmin$min/60)
+# dfmin$f1<-NULL
+# dfmin$min<-NULL
+dfmin<-unique(dfmin[dfmin$f2==TRUE,])
+# dfmin$f2<-NULL
+dfidmin<-rbind(dfidmin,dfmin)

### 2018-06-26 Memo_of_meeting.Rmd
memo added

---
title: "Memo of meeting"
output: word_document
---

**Date and time:** 2018-06-25 14:00 - 15:00

**Attendees:** Professor Luigi Palla, Dr. Suzana Almoosawi, Chaochen Wang

**Notekeeper:** Chaochen Wang

**Main Topic:** how to define an eating occasion specifically for carbohydrate intake or what approaches can we use to analysis the eating time pattern of carbohydrate.

- From Professor Luigi: 
    - We may use gram consumed per hour; 
    - Percentage of energy from carbohydrate per eating occasion (we already know that the cut-off value for energy eating occasion is defined as $\geqslant$ 210 kJ); 
    - Or is there any definition of eating time window block? (For total energy intake we used 15 minutes).

- From Dr. Suzana: 
    - According to the guideline (which?), it is suggested that the distribution of carbohydrate intake should be equal for breakfast (25%), lunch (25%), dinner (25%), and snacks (25%). Therefore, the recommendation is 270 g/day (for both men and women?) which lead to 67.5 gram per meal.
    - Or if we consider the composition of energy sources, it is also recommended that 25% of the total energy should come from carbohydrates.
    - We may also use the ratio of carbohydrates and (for example) fibre: 1 g fibre/ 10 g carbohydrates.
    - In the NDNS survey, they already defined 7 meal blocks: 
        - breakfast (6 am to 9 am); 
        - mid-morning snack (9 am to 12 noon); 
        - lunch (12 noon to 2 pm); 
        - afternoon snack (2 pm to 5 pm); 
        - dinner (5 pm to 8 pm); 
        - late-night snack (8 pm to 10 pm); 
        - midnight snack (10 pm to 6 am).
    - Use the already defined 7 meal blocks will be easier in terms of comparing with existing publications from NDNS data.

- From Professor Luigi: 
    - Can we use 1 hour window for each participant? So each person will have 24 time sequence of eating (carbohydrates) per day. 
    - **We may calculate the energy consumption per hour for each participant. And also calculate the percentage of energy that come from carbohydrate each hour. Would that be sensible?**
    - What cut-off would be appropriate to say that within that specific hour, the consumption of carbohydrates would be good or bad?

- From Dr. Suzana: 
    - Probably, this could be an option. Usually, a food product/meal can be categorised as with low carbohydrates or sugar condensed if the contribution of energy from carbohydrates in that food/meal is lower than 25% or higher than 70%: 
        - if 25% energy from carbohydrates $\Rightarrow$ low-carbohydrates; 
        - if 70% energy from carbohydrates $\Rightarrow$ high-carbohydrates; 
        - if 26% ~ 69% energy from carbohydrates $\Rightarrow$ medium-carbohydrates.
    - But if we need to dichotomise, I need to confirm again whether there is any evidence/suggestion about that.
    - Still, this could the first step of our analysis. The second step we may think about is the quality (ratio) between different subtypes of carbohydrates within the hour.

### 2018-06-26 phrases.Rmd
memo added

@@
 
+- trivial ['triviəl]
+
+```
+======= 辞典翻译: trivial ========
+  adj. 不重要的，琐碎的；琐细的
+============ 网络释义 ============
+---------- trivial -----------
+  琐碎的
+  微不足道的
+  小巫见大巫
+------ Trivial Pursuit -------
+  棋盘问答
+  打破砂锅问到底
+  追根究底
+-------- trivial name --------
+  惯用名
+  俗名
+  种名
+```
+
+- prudent ['pru:dənt]
+
+```
+======= 辞典翻译: prudent ========
+  adj. 谨慎的；精明的；节俭的
+  n. (Prudent)人名；(法)普吕当
+============ 网络释义 ============
+---------- prudent -----------
+  谨慎的
+  明智的
+  审慎的
+--------- prudent s ----------
+  善于经营的
+  谨慎
+  精明的
+----- PRESIDENT PRUDENT ------
+  普鲁登特总统城
+```
+
 # Expressions
@@
 - When categorical data are used, the latent class model has the advantage of making no assumptions about the distributions of the indicators other than that of local independence; that is, the assumption that within a latent class the indicators are independent.
+
+- In PROC LCA, parameters are estimated by maximum likelihood using an EM (expectation-maximization) type procedure.
+Missing data on the latent class indicators are handled in this procedure, with data assumed to be missing at
+random (MAR).
+
+- A test of the null hypothesis that data are missing completely at random appears in the output.
+
+- a helpful preliminary step in any LCA is exploring overall relations among pairs of items by conducting cross-tab analyses.
+
+- A good starting point for identifying an optimal baseline model is to fit a sequence of models with two classes, three classes, and so on.
+
+- A variety of tools can be used together for model selection, including the likelihood-ratio G 2 statis-
+tic, Akaike’s Information Criterion (AIC; Akaike, 1974) and Bayesian Information Criterion (BIC; Schwarz, 1978).
+
+- For example, each class should be distinguishable from the others on the basis of the item-response probabilities, no class should be trivial in size (i.e., with a near-zero probability of membership), and it should be possible to assign a meaningful label to each class.
+
+- The AIC and BIC are penalized log-likelihood model information criteria that can be used to compare competing models (e.g., models with different numbers of latent classes) fit to the same data.
+A smaller AIC and BIC for a particular model suggests that the trade-off between fit and parsimony is preferable.
+
+- Often when a grouping variable is included it is important to test for measurement invariance across groups.
+To do this, a model with free estimation of the $\rho$ parameters can be compared to the same model that includes restrictions equating the $\rho$ parameters across groups.
+A significant p value suggests that the null hypothesis of measurement invariance should be rejected.
+
+- Based on a data set, a particular model specification, and starting values for the parameters, the algo-
+rithm iterates between the Expectation (E) step and the Maximization (M) step until either the convergence criterion is achieved or the maximum number of iterations is reached.
+
+- The best way to detect identification problems or local optima (i.e., solutions other than the optimal one) is to fit the same model using multiple sets of starting values.
+This can be done by calling the procedure repeatedly with different seeds specified.
+
+- Even well-identified models can land on a different solution occasionally; if the solution with the smallest log-likelihood is arrived at using the majority of the seeds, one can have confidence that it is the optimal solution.

### 2018-06-26 Rcode/Raoulcodes.R

@@ -1,13 +1,17 @@
-setwd("D:/Dropbox/LSHTM/study/project/6533STATA11/UKDA-6533-stata11_se/stata11_se/")
-install.packages("poLCA")
+# setwd("D:/Dropbox/LSHTM/study/project/6533STATA11/UKDA-6533-stata11_se/stata11_se/") # on Win 10
+setwd("~/Dropbox/LSHTM/study/project/6533STATA11/UKDA-6533-stata11_se/stata11_se") # on Ubuntu
+
+# setwd("~/Documents/LSHTMproject") # back to project
+
+# install.packages("poLCA")
 # install.packages("ggplot")
 # install.packages("ggplot2")
-library(plyr)
-library(ggplot2)
-source("../../../Rcode/Raoulmycode.R")
-
-
-options(stringsAsFactors=FALSE)
+# library(plyr)
+# library(ggplot2)
+# source("../../../Rcode/Raoulmycode.R")
+# 
+# 
+# options(stringsAsFactors=FALSE)
 library(haven)
 data <- read_dta("ndns_rp_yr1-4a_foodleveldietarydata_uk.dta")
 data56 <- read_dta("ndns_rp_yr5-6a_foodleveldietarydata.dta")
@@ -34,7 +38,7 @@ dfs1<-rbind(df14d,df56d)
 
 
 dfs2<-dfs1[dfs1$Age>=19,]
-rm(data, data56)
+ rm(data, data56)
 dfs2$MealTime_chr <- as.character(dfs2$MealTime)
 dfs2$MealTime_hm <- unlist(strsplit(dfs2$MealTime_chr," "))[c(FALSE, TRUE)]
 

### 2018-06-27 phrases.Rmd
foundamentalpart read 30%

@@
 
+- daunting ['dɔ:ntiŋ]
+
+```
+======= 辞典翻译: daunting =======
+adj. 使人畏缩的；使人气馁的；令人怯步的
+============ 网络释义 ============
+---------- Daunting ----------
+令人生畏
+使人畏缩的
+使人气馁的
+------ However Daunting ------
+但艰巨
+--------- B daunting ---------
+使胆怯
+```
+
+- discern [di'sə:n, -'zə:n]
+
+```
+======= 辞典翻译: discern ========
+  vt. 识别；领悟，认识
+  vi. 看清楚，辨别
+============ 网络释义 ============
+---------- discern -----------
+  看出
+  辨别
+  识别
+-------- Discern Lies --------
+  辨知谎言
+  辨识谎言
+  洞悉谎言
+------- discern safely -------
+  安全识别
+```
+
 # Expressions
@@
 - Even well-identified models can land on a different solution occasionally; if the solution with the smallest log-likelihood is arrived at using the majority of the seeds, one can have confidence that it is the optimal solution.
+
+#### collins2010latent - Latent Class and Latent Transition Analysis: With Applications in the Social, Behavioral, and Health Sciences
+
+- It is particularly noteworthy that the causal flow is *from* the latent variable *to* the indicator variable, not the other way around.
+That is, observed indicator variables do not cause the latent variables.
+
+- The purpose of LCA is to help the investigator to discern any meaningful, scientifically interesting classes against the noisy background of error.
+
+- In LCA, it is the responsibility of the investigator to assign names to the latent classes.
+
+- The starting point for conducting a latent class analysis on empirical data is a contingency table formed by cross-tabulating all the observed variables to be involved in the analysis.

### 2018-06-29 phrases.Rmd
data manipulation

@@
 - The starting point for conducting a latent class analysis on empirical data is a contingency table formed by cross-tabulating all the observed variables to be involved in the analysis.
+
+- The local independence assumption refers only to conditioning on the latent variable.
+It does not imply that in a data set that is to be analyzed, the observed variables are independent.
+In fact, it is the relations among the observed variables that are explained by the latent classes.
+
+- An observed data set is a mixture of all the latent classes. Independence is assumed to hold only within each latent class, which is why it is called "local".
+
+- LCA makes the assumption of local independence, which states that conditional on latent class, observed variables are independent.
+
+- **A high degree of latent class separation implies a high degree of homogeneity.**
+
+- **However, a high degree of homegeneity does not necessarily imply a high degree of latent class separation.**
+
+- Thus, it is possible to have high homogeneity but poor latent class separation.
+
+- Some of the latent classes may be characterized by more than one response pattern, but there is no response pattern that appears to be closely associated with more than one latent class.
+Thus the latent classes are conceptually distinct and can readily be labeled.
+
+- Model selection may be challenging.
+Furtunately, a variety of tools are available to assist, including tests of absolute model fit, assessment of relative fit of competing models, and cross-validation.
+In addition to the tools discussed, there are two additional consideration that are critically important when evaluating a model: **parsimony and model interpretability**.
+
+- We see statistical models as lenses through which investigators examine their data in order to gain useful insights.
+
+- The likelihood-ratio statistics $G^2$  $$G^2 = 2\sum_{w=1}^W f_w\log(\frac{f_w}{\widehat{f_w}})$$
+
+- Where $f_w$ represents the observed frequency of cell $w$, and $\widehat{f_w}$ represent the expected frequency of cell $w$ according to the model that has been fit.
+
+- The larger the value of $G^2$, the more evidence there is against the null hypothesis. (The larger it is, the worse model fitting it is.)
+
+- The degrees of freedom of $G^2$: $$df = W - P - 1$$
+
+- Where $P$ is the number of estimated parameters.

### 2018-06-29 Rcode/LatentClassAnalysisSim.R

@@ -1,0 +1,26 @@
+alpha = rep(0.25, 4)
+## equal
+p1 = 0.85
+p2 = 0.1
+p3 = 0.2
+P = matrix(c(
+  p1,p2,p2,p2,
+  p1,p3,p3,p3,
+  p2,p1,p2,p2,
+  p3,p1,p3,p3,
+  p2,p2,p1,p2,
+  p3,p3,p1,p3,
+  p2,p2,p2,p1,
+  p3,p3,p3,p1), nrow=8, ncol=4, byrow = TRUE)
+
+
+library(poLCA)
+
+source("Rcode/simLCA.R")
+set.seed(37421)
+X = simLCA(alpha, P, sampleSize=50, nsim=1)[[1]]
+head(X)
+
+
+f = cbind(Y1, Y2, Y3, Y4, Y5, Y6, Y7, Y8) ~ 1
+poLCA(f, X, nclass = 3, verbose=FALSE)

### 2018-06-29 Rcode/analysis8yrsA.R

@@ -1,0 +1,95 @@
+
+# NDNS analysis, data management ------------------------------------------
+
+
+# Change the data path accordingly ----------------------------------------
+
+setwd("/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/") # on Ubuntu
+
+library(tidyverse)
+library(epiDisplay)
+
+# Read the data into memory -----------------------------------------------
+
+library(haven)
+
+
+data <- read_dta("ndns_rp_yr1-4a_foodleveldietarydata_uk.dta")
+
+data56 <- read_dta("ndns_rp_yr5-6a_foodleveldietarydata.dta")
+
+data78 <- read_dta("ndns_rp_yr7-8a_foodleveldietarydata.dta")
+
+names(data)
+
+names(data56)
+
+names(data78)
+
+names(data)[names(data)=="seriali"] <- "id"
+names(data56)[names(data56)=="seriali"] <- "id"
+names(data78)[names(data78)=="seriali"] <- "id"
+
+
+
+# Extract the data we needed ----------------------------------------------
+
+
+df14d <- data[,c(113,1,2,3,5,6,7,8,9,21,24,55,57,58,59,60,61,62,63,64)]
+
+var <- names(df14d)
+
+df56d <- data56 %>% 
+  select(var)
+
+df78d <- data78 %>% 
+  select(var)
+
+dfs1 <- rbind(df14d, df56d, df78d)
+
+
+dfs2 <- dfs1[dfs1$Age>=19,]
+rm(data, data56, data78)
+
+dfs2
+
+
+# Calculate the time (minute and hour) when they eat ----------------------
+
+dfs2$MealTime_chr <- as.character(dfs2$MealTime)
+dfs2$MealTime_hm <- unlist(strsplit(dfs2$MealTime_chr," "))[c(FALSE, TRUE)]
+
+
+dfs2$MealHourN <- as.numeric(unlist(strsplit(dfs2$MealTime_hm,":"))[c(TRUE, FALSE, FALSE)])
+dfs2$MealMinN <- as.numeric(unlist(strsplit(dfs2$MealTime_hm,":"))[c(FALSE, TRUE, FALSE)])
+dfs2$MealMinN0 <- (60*dfs2$MealHourN)+dfs2$MealMinN
+
+
+dfs3 <- dfs2[order(dfs2$id,dfs2$DayNo,dfs2$MealMinN0),]
+
+
+length(unique(dfs3$id)) ## number of participants = 6155
+
+
+
[…]

### 2018-06-29 Rcode/simLCA.R

@@ -1,0 +1,11 @@
+simLCA <- function(alpha, ProbMat, sampleSize, nsim) {
+  ## Reformat the probability Matrix to a form required by poLCA.simdata
+  probs = vector("list", nrow(ProbMat))
+  for (i in 1:nrow(ProbMat)) {
+    probs[[i]] = cbind(ProbMat[i,], 1 - ProbMat[i,])
+  }
+
+X = poLCA.simdata(N = sampleSize*nsim, probs = probs, P = alpha)$dat
+split(X, rep(1:nsim, each=sampleSize))
+
+}

### 2018-06-29 Rcode/analysis8yrsA.R
LCA day1 tried

@@ -6,8 +6,11 @@
 
 setwd("/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/") # on Ubuntu
 
-library(tidyverse)
+
 library(epiDisplay)
+library(plyr)
+library(tidyverse)
+
 
 # Read the data into memory -----------------------------------------------
 
@@ -93,3 +96,197 @@ with(NDNS, tab1(SurveyYear, graph = FALSE, decimal = 2))
   # Total          6155  100.00       100.00
 
 save.image("NDNS.Rdata")
+
+
+
+# start analysis from loading the extracted data --------------------------
+setwd("~/Documents/LSHTMproject/Rcode")
+load("NDNS.Rdata")
+
+
+
+# how many men and women --------------------------------------------------
+
+with(NDNS, tab1(Sex, graph = FALSE, decimal = 2))
+
+# Sex : 
+      #   Frequency Percent Cum. percent
+# 1            2537   41.22        41.22 Men
+# 2            3618   58.78       100.00 Women
+  # Total      6155  100.00       100.00
+
+
+# create a variable combine id and day No ---------------------------------
+
+
+dfs3 <- dfs3 %>% 
+  mutate(id_dy = paste(id, DayNo, sep = "D"))
+
+
+
+# For each subject, the total energy/carbohydrate intake for each eating time can be calculated --------
+
+old<-Sys.time()
+Energy <- ddply(dfs3, .(id_dy, id, SurveyYear, DayNo, Age, Sex, DiaryDaysCompleted, MealHourN),  
+                summarise, Tot_Energ = sum(EnergykJ), Tot_Carb = sum(Carbohydrateg), Tot_Sugar = sum(Totalsugarsg), Tot_Starch = sum(Starchg))
+new<-Sys.time()-old
+print(new)
+    
+# Time difference of 3.876385 mins
+
+rm(df14d, df56d, df78d, dfs2)
+
+head(Energy)
+
+
+vecid<-unique(Energy$id)
+
+
+# Calculate the energy from total carbohydrates ---------------------------
+
+Energy <- Energy %>% 
[…]

### 2018-06-30 9thJuly/9thJuly.Rmd
initial results using day1 data

---
title: "Preliminary results"
output: html_document
---

## Data description

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
setwd("~/Documents/LSHTMproject/Rcode")

load("LCA.Rdata")

library(epiDisplay)
library(plyr)
library(tidyverse)

# Number of subjects per survey year
with(NDNS, tab1(SurveyYear, graph = FALSE, decimal = 2))

# Number of subjects per servey year by gender where Men == 1, Women == 2

with(NDNS, tabpct(SurveyYear, Sex,  graph = FALSE, decimal = 2))

# summary of their age

NDNS %>% 
  group_by(SurveyYear, Sex) %>% 
  summarise(N = n(), MeanAge = mean(Age), SDAge = sd(Age), minAge = min(Age), maxAge = max(Age))

# Dietary data by day

vecid1<-unique(dta_day1$id) # n = 6153
vecid2<-unique(dta_day2$id) # n = 6153
vecid3<-unique(dta_day3$id) # n = 6151
vecid4<-unique(dta_day4$id) # n = 6026

setdiff(vecid, vecid1) # two subjects did not have day 1 data

setdiff(vecid, vecid2) # two subjects did not have day 2 data

setdiff(vecid, vecid3) # four subjects did not have day 3 data

setdiff(vecid, vecid4) # 129 subjects did not have day 4 data
```

### day 1 data (3 classes)

```{r}

# LCA in day1 -------------------------------------------------------------

# noquote(paste(rep("H", 24), 0:23, sep = ""))
#H0  H1  H2  H3  H4  H5  H6  H7  H8  H9  H10 H11 H12 H13 H14 H15 H16 H17 H18 H19 H20 H21 H22 H23
library(poLCA)
f <- cbind(H0, H1, H2, H3, H4, H5, H6, H7, H8, H9, H10,H11,H12,H13,H14,H15,H16,H17,H18,H19,H20,H21,H22,H23) ~ 1
lc3 <- poLCA(f, dta_d1_wide, nclass = 3, graphs = TRUE, maxiter = 10000)

# lc3$llik #log-likelihood of model
# 
# lc3$P #Estimated class population shares 
# 
# lc3$predclass
```

### day 1 data (Fig.)

```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE}

library(ggthemr)
a <- (data.frame(lc3$probs))
a$Class <- c("Class1", "Class2", "Class3")

a_long <- a %>% 
  gather(Hour, Prob, -Class) %>% 
  separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")

a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))

a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb"))

a_long <- a_long %>% 
  filter(Carbo != "Not_eating")

ggthemr("fresh", layout = "scientific")

ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 45.71%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  41.71%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 3:  12.58%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))
```

### Model comparison and selection

```{r echo=FALSE}
library(kableExtra)
dt <- read.csv("../Tablecsv/Modelfit.csv", header = T)
names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")

kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Model Comparison.") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(5, bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; G^2, the likelihood ratio statistic; AIC, Akaike information criterion; BIC, Bayesian information criterion.")
```

### Five classes visualisation

```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE}

library(ggthemr)

lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)

a <- (data.frame(lc5$probs))
a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")

a_long <- a %>% 
  gather(Hour, Prob, -Class) %>% 
  separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")

a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))

a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb"))

a_long <- a_long %>% 
  filter(Carbo != "Not_eating")

ggthemr("fresh", layout = "scientific")

ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 33.38%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  25.89%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 3:  22.46%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 4:  7.65%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 5:  12.27%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))
```

### 2018-06-30 Rcode/analysis8yrsA.R

@@ -246,30 +246,30 @@ names(dta_d4_wide)
 
 for (i in 1:ncol(dta_d1_wide)) 
   if(is.factor(dta_d1_wide[,i])) 
-    levels(dta_d1_wide[,i]) <- c(levels(dta_d1_wide[,i]), "Not eating")
+    levels(dta_d1_wide[,i]) <- c(levels(dta_d1_wide[,i]), "Not_eating")
 
-dta_d1_wide[is.na(dta_d1_wide)] <- "Not eating"
+dta_d1_wide[is.na(dta_d1_wide)] <- "Not_eating"
 
 
 for (i in 1:ncol(dta_d2_wide)) 
   if(is.factor(dta_d2_wide[,i])) 
-    levels(dta_d2_wide[,i]) <- c(levels(dta_d2_wide[,i]), "Not eating")
+    levels(dta_d2_wide[,i]) <- c(levels(dta_d2_wide[,i]), "Not_eating")
 
-dta_d2_wide[is.na(dta_d2_wide)] <- "Not eating"
+dta_d2_wide[is.na(dta_d2_wide)] <- "Not_eating"
 
 
 for (i in 1:ncol(dta_d3_wide)) 
   if(is.factor(dta_d3_wide[,i])) 
-    levels(dta_d3_wide[,i]) <- c(levels(dta_d3_wide[,i]), "Not eating")
+    levels(dta_d3_wide[,i]) <- c(levels(dta_d3_wide[,i]), "Not_eating")
 
-dta_d3_wide[is.na(dta_d3_wide)] <- "Not eating"
+dta_d3_wide[is.na(dta_d3_wide)] <- "Not_eating"
 
 
 for (i in 1:ncol(dta_d4_wide)) 
   if(is.factor(dta_d4_wide[,i])) 
-    levels(dta_d4_wide[,i]) <- c(levels(dta_d4_wide[,i]), "Not eating")
+    levels(dta_d4_wide[,i]) <- c(levels(dta_d4_wide[,i]), "Not_eating")
 
-dta_d4_wide[is.na(dta_d4_wide)] <- "Not eating"
+dta_d4_wide[is.na(dta_d4_wide)] <- "Not_eating"
 
 
 # LCA in day1 -------------------------------------------------------------
@@ -280,13 +280,85 @@ library(poLCA)
[…]

### 2018-07-01 9thJuly/9thJuly.Rmd
day2 added

@@
 library(tidyverse)
-
+library(poLCA)
 # Number of subjects per survey year
@@
 #H0  H1  H2  H3  H4  H5  H6  H7  H8  H9  H10 H11 H12 H13 H14 H15 H16 H17 H18 H19 H20 H21 H22 H23
-library(poLCA)
+
 f <- cbind(H0, H1, H2, H3, H4, H5, H6, H7, H8, H9, H10,H11,H12,H13,H14,H15,H16,H17,H18,H19,H20,H21,H22,H23) ~ 1
@@
 library(kableExtra)
-dt <- read.csv("../Tablecsv/Modelfit.csv", header = T)
+dt <- read.csv("../Tablecsv/Modelfitd01.csv", header = T)
 names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
@@
 kable(dt, digits = 3, row.names = FALSE, align = "c",
-              format = "html", caption = "Model Comparison.") %>%
+              format = "html", caption = "Model Comparison. (Day 1, n = 6153)") %>%
  kable_styling(font_size = 16, 
@@
   row_spec(5, bold = T, color = "white", background = "#D7261E") %>% 
-  footnote(general = "Abbreviation: N, number; G^2, the likelihood ratio statistic; AIC, Akaike information criterion; BIC, Bayesian information criterion.")
+  footnote(general = "Abbreviation: N, number; G^2, the likelihood ratio statistic; df, degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion.")
 ```
@@
 ```
+
+### day 2 data (Fig.)
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE}
+
+library(ggthemr)
+lc3 <- poLCA(f, dta_d2_wide, nclass = 3, graphs = FALSE, maxiter = 10000)
+
+a <- (data.frame(lc3$probs))
+a$Class <- c("Class1", "Class2", "Class3")
+
+a_long <- a %>% 
+  gather(Hour, Prob, -Class) %>% 
+  separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")
+
+a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
+
+a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb"))
+
+a_long <- a_long %>% 
+  filter(Carbo != "Not_eating")
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 35.92%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  12.50%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 3:  51.58%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+```
+
+### Model comparison and selection
+
+```{r echo=FALSE}
+library(kableExtra)
+dt <- read.csv("../Tablecsv/Modelfitd02.csv", header = T)
+names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
+
+kable(dt, digits = 3, row.names = FALSE, align = "c",
+              format = "html", caption = "Model Comparison. (Day 2, n = 6153)") %>%
+ kable_styling(font_size = 16, 
+        bootstrap_options = c("striped", "hover", "condensed"),
+        position = "center", full_width = FALSE) %>% 
+  row_spec(5, bold = T, color = "white", background = "#D7261E") %>% 
+  footnote(general = "Abbreviation: N, number; G^2, the likelihood ratio statistic; df, degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion.")
+```
+
+### Four classes visualisation
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE}
+
+library(ggthemr)
+
+# lc4 <- poLCA(f, dta_d2_wide, nclass = 4, graphs = FALSE, maxiter = 10000)
+lc5 <- poLCA(f, dta_d2_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
+
+a <- (data.frame(lc5$probs))
+a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+
+a_long <- a %>% 
+  gather(Hour, Prob, -Class) %>% 
+  separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")
+
+a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
+
+a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb"))
+
+a_long <- a_long %>% 
+  filter(Carbo != "Not_eating")
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 11.80%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  8.50%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 3:  25.0%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 4:  44.40%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 5:  %", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+```

### 2018-07-01 Rcode/analysis8yrsA.R

@@ -361,4 +361,94 @@ lc2 <- poLCA(f, dta_d1_wide, nclass = 2, graphs = T, maxiter = 10000)
 lc1 <- poLCA(f, dta_d1_wide, nclass = 1, graphs = T, maxiter = 10000)
 
 
+
+# LCA in day2 -------------------------------------------------------------
+
+lc1 <- poLCA(f, dta_d2_wide, nclass = 1, graphs = T, maxiter = 10000)
+
+lc2 <- poLCA(f, dta_d2_wide, nclass = 2, graphs = T, maxiter = 10000)
+
+
+
+
+
+lc3 <- poLCA(f, dta_d2_wide, nclass = 3, graphs = TRUE, maxiter = 10000)
+
+lc3$llik
+
+# lc3[[4]][[1]][1,2]
+# 
+lc3$P #Estimated class population shares 
+
+lc3$predclass
+
+a <- (data.frame(lc3$probs))
+a$Class <- c("Class1", "Class2", "Class3")
+
+a_long <- a %>% 
+  gather(Hour, Prob, -Class) %>% 
+  separate(Hour, into = c("HourN", "Carbo"), sep = "\\.") 
+
+a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13",
+                                                "H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
+
+a_long <- a_long %>% 
+  filter(Carbo != "Not_eating")
+
+
+ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point() + 
+  geom_line()
+
+ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point() + 
+  geom_line()
+
+ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point() + 
+  geom_line()
+
+lc4 <- poLCA(f, dta_d2_wide, nclass = 4, graphs = TRUE, maxiter = 10000)
+
+
+lc4_prob <- (data.frame(lc4$probs))
+lc4_prob$Class <- c("Class1", "Class2", "Class3", "Class4")
[…]

### 2018-07-04 phrases.Rmd
toc added

@@
 title: "Some usefull words/expressions/sentences"
-output: html_document
+output: 
+  html_document:
+    toc: true
+    toc_float: true
 ---
@@
 
-#### terry2017discontinuous - Discontinuous Patterns of Cigarette Smoking From Ages 18 to 50 in the United States: A Repeated-Measures Latent Class Analysis
+## terry2017discontinuous
+
+(Discontinuous Patterns of Cigarette Smoking From Ages 18 to 50 in the United States: A Repeated-Measures Latent Class Analysis)
 
@@
 
-#### lanza2007proc - PROC LCA: A SAS procedure for latent class analysis
+## lanza2007proc
+
+(PROC LCA: A SAS procedure for latent class analysis)
 
@@
 
-#### collins2010latent - Latent Class and Latent Transition Analysis: With Applications in the Social, Behavioral, and Health Sciences
+## collins2010latent
+
+(Latent Class and Latent Transition Analysis: With Applications in the Social, Behavioral, and Health Sciences)
 
@@
 - Where $P$ is the number of estimated parameters.
+
+- Sometimes fitting a series of latent class models with different numbers of latent classes to data at a single time point can be helpful as a preliminary step in model selection in LTA.
+Doing this at each time point can be informative about the latent structrue within times, and how that structure changes accross timie points.
+
+- It is important to note that the best-fitting latent class model at any given time may not correspond to the best-fitting latent transition model fit to all occasions of measurements.
+The best-fitting model based on the data from all occasions of measurement may include a different number of latent stuatuses than the number of latent classes identified at one particular time.
+
+- However, based on the latent status prevalences at each time alone, it is impossible to tell hou and to what extent individuals were moving between latent statuses.
+
+- **In 7.11 we used a different empirical example to test the hypothesis that the item-response probabilities in a LTA are equal across times.
+This type of restriction on the item-response probabilities is commonly used in LTA.
+It helps with model identification and, importantly, ensures that the meaning of the latent statuses remains constant over time.**

### 2018-07-04 Rcode/analysis8yrsA.R

@@ -278,7 +278,7 @@ dta_d4_wide[is.na(dta_d4_wide)] <- "Not_eating"
 #H0  H1  H2  H3  H4  H5  H6  H7  H8  H9  H10 H11 H12 H13 H14 H15 H16 H17 H18 H19 H20 H21 H22 H23
 library(poLCA)
 f <- cbind(H0, H1, H2, H3, H4, H5, H6, H7, H8, H9, H10,H11,H12,H13,H14,H15,H16,H17,H18,H19,H20,H21,H22,H23) ~ 1
-lc3 <- poLCA(f, dta_d1_wide, nclass = 3, graphs = TRUE, maxiter = 10000)
+lc3 <- poLCA(f, dta_d1_wide, nclass = 3, graphs = TRUE, maxiter = 10000, nrep = 25)
 
 lc3$llik
 

### 2018-07-05 9thJuly/9thJuly.Rmd
toc added
LCA analysis by day

--- 2018-06-30 9thJuly/9thJuly.Rmd
@@
 title: "Preliminary results"
-output: html_document
+output: 
+  html_document:
+    toc: true
+    toc_depth: 3
+    toc_float: true
 ---
 
-## Data description
+# Data description
 
-```{r message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 setwd("~/Documents/LSHTMproject/Rcode")
@@
 library(tidyverse)
+library(poLCA)
+```
 
-# Number of subjects per survey year
+## Number of subjects per survey year
+
+```{r message=FALSE, warning=FALSE, paged.print=FALSE}
+
 with(NDNS, tab1(SurveyYear, graph = FALSE, decimal = 2))
 
-# Number of subjects per servey year by gender where Men == 1, Women == 2
+```
 
+## Number of subjects per servey year by gender where Men == 1, Women == 2
+
+```{r message=FALSE, warning=FALSE, paged.print=FALSE}
 with(NDNS, tabpct(SurveyYear, Sex,  graph = FALSE, decimal = 2))
+```
 
-# summary of their age
-
+## Summary of their age 
+```{r message=FALSE, warning=FALSE, paged.print=FALSE}
 NDNS %>% 
@@
   summarise(N = n(), MeanAge = mean(Age), SDAge = sd(Age), minAge = min(Age), maxAge = max(Age))
+```
 
-# Dietary data by day
+## Distribution of the dietary data (by Day of Week)
+
+### Day1
+
+```{r}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/NDNSday1_4.Rdata")
+with(dta_d1_wide, tab1(DayofWeek, graph = FALSE, decimal = 2))
+```
+
+### Day2
+
+```{r}
+with(dta_d2_wide, tab1(DayofWeek, graph = FALSE, decimal = 2))
+```
+
+### Day3
+
+```{r}
+with(dta_d3_wide, tab1(DayofWeek, graph = FALSE, decimal = 2))
+```
+
+### Day4
+
+```{r}
+with(dta_d4_wide, tab1(DayofWeek, graph = FALSE, decimal = 2))
+```
+
+## Distribution of the dietary data (by DayNo)
+
+### Monday
+
+```{r}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/NDNSMon_Sun.Rdata")
+with(dta_Mon_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+### Tuesday
+
+```{r}
+with(dta_Tue_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+### Wednesday
+
+```{r}
+with(dta_Wed_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+### Thursday
+
+```{r}
+with(dta_Thurs_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+### Friday
+
+```{r}
+with(dta_Fri_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+### Saturday
+
+```{r}
+with(dta_Sat_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+### Sunday
+
+```{r}
+with(dta_Sun_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+**The problem of analysing data by day of the week would be that every subject only contributed 3-4 days' data. Therefore, we cannot see one subject's dietary change during a Mon-Sun week.**
+
+## Dietary data by day
+
+```{r message=FALSE, warning=FALSE, paged.print=FALSE}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/NDNSday1_4.Rdata")
+
+vecid <- unique(dfs3$id)
 
@@
 
-### day 1 data (3 classes)
+# LCA analyses by day
 
-```{r}
+## Day 1
 
-# LCA in day1 -------------------------------------------------------------
-
-# noquote(paste(rep("H", 24), 0:23, sep = ""))
-#H0  H1  H2  H3  H4  H5  H6  H7  H8  H9  H10 H11 H12 H13 H14 H15 H16 H17 H18 H19 H20 H21 H22 H23
-library(poLCA)
-f <- cbind(H0, H1, H2, H3, H4, H5, H6, H7, H8, H9, H10,H11,H12,H13,H14,H15,H16,H17,H18,H19,H20,H21,H22,H23) ~ 1
-lc3 <- poLCA(f, dta_d1_wide, nclass = 3, graphs = TRUE, maxiter = 10000)
-
-# lc3$llik #log-likelihood of model
-# 
-# lc3$P #Estimated class population shares 
-# 
-# lc3$predclass
+```{r eval=FALSE}
+set.seed(01012)
+max_II <- 100000
+lc1<-poLCA(f, data=dta_d1_wide, nclass=1, na.rm = FALSE, nrep=20, maxiter=max_II) #Loglinear independence model.
+lc2<-poLCA(f, data=dta_d1_wide, nclass=2, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc3<-poLCA(f, data=dta_d1_wide, nclass=3, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc4<-poLCA(f, data=dta_d1_wide, nclass=4, na.rm = FALSE, nrep=20, maxiter=max_II) 
+lc5<-poLCA(f, data=dta_d1_wide, nclass=5, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc6<-poLCA(f, data=dta_d1_wide, nclass=6, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc7<-poLCA(f, data=dta_d1_wide, nclass=7, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc8<-poLCA(f, data=dta_d1_wide, nclass=8, na.rm = FALSE, nrep=20, maxiter=max_II)
 ```
 
-### day 1 data (Fig.)
+### Model comparison and selection
+
+```{r echo=FALSE}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/day1LCA1_6.Rdata")
+
+library(kableExtra)
+# dt <- read.csv("../Tablecsv/Modelfitd01.csv", header = T)
+# names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
+lca_results[1,9] <- "---"
+kable(lca_results, digits = 3, row.names = FALSE, align = "c",
+              format = "html", caption = "Model Comparison. (Day 1, n = 6153)") %>%
+ kable_styling(font_size = 16, 
+        bootstrap_options = c("striped", "hover", "condensed"),
+        position = "center", full_width = FALSE) %>% 
+  row_spec(c(4,6), bold = T, color = "white", background = "#D7261E") %>% 
+  footnote(general = "Abbreviation: N, number; resid.df, residual degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
+```
+
+### Day 1 data (Fig. 4 classes)
 
@@
 library(ggthemr)
-a <- (data.frame(lc3$probs))
-a$Class <- c("Class1", "Class2", "Class3")
+
+# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
+
+# a <- (data.frame(lc5$probs))
+a <- (data.frame(lc4$probs))
+# a <- (data.frame(lc6$probs))
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+a$Class <- c("Class1", "Class2", "Class3", "Class4")
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")
 
@@
         ) + 
-  labs(title = "Class 1: 45.71%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 1: 38.80%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
         ) + 
-  labs(title = "Class 2:  41.71%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 2:  28.25%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
         ) + 
-  labs(title = "Class 3:  12.58%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 3:  10.81%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
   ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 4:  23.14%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+# 
+# ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 5:  18.52%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+# 
+# ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 6:  10.02%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
 ```
 
-### Model comparison and selection
-
-```{r echo=FALSE}
-library(kableExtra)
-dt <- read.csv("../Tablecsv/Modelfit.csv", header = T)
-names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
-
-kable(dt, digits = 3, row.names = FALSE, align = "c",
-              format = "html", caption = "Model Comparison.") %>%
- kable_styling(font_size = 16, 
-        bootstrap_options = c("striped", "hover", "condensed"),
-        position = "center", full_width = FALSE) %>% 
-  row_spec(5, bold = T, color = "white", background = "#D7261E") %>% 
-  footnote(general = "Abbreviation: N, number; G^2, the likelihood ratio statistic; AIC, Akaike information criterion; BIC, Bayesian information criterion.")
-```
-
-### Five classes visualisation
+### Day 1 data (Fig. 6 classes)
 
@@
 
-lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
+# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
 
-a <- (data.frame(lc5$probs))
-a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+# a <- (data.frame(lc5$probs))
+# a <- (data.frame(lc4$probs))
+a <- (data.frame(lc6$probs))
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+# a$Class <- c("Class1", "Class2", "Class3", "Class4")
+
+a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")
 
@@
         ) + 
-  labs(title = "Class 1: 33.38%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 1: 26.79%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
         ) + 
-  labs(title = "Class 2:  25.89%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 2:  11.72%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
         ) + 
-  labs(title = "Class 3:  22.46%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 3:  7.37%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
         ) + 
-  labs(title = "Class 4:  7.65%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 4:  25.58%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
         ) +
-  labs(title = "Class 5:  12.27%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 5:  18.52%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 6:  10.02%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") +
@@
 ```
+
+## Day 2
+
+```{r eval=FALSE}
+set.seed(01012)
+max_II <- 100000
+lc1<-poLCA(f, data=dta_d1_wide, nclass=1, na.rm = FALSE, nrep=20, maxiter=max_II) #Loglinear independence model.
+lc2<-poLCA(f, data=dta_d1_wide, nclass=2, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc3<-poLCA(f, data=dta_d1_wide, nclass=3, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc4<-poLCA(f, data=dta_d1_wide, nclass=4, na.rm = FALSE, nrep=20, maxiter=max_II) 
+lc5<-poLCA(f, data=dta_d1_wide, nclass=5, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc6<-poLCA(f, data=dta_d1_wide, nclass=6, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc7<-poLCA(f, data=dta_d1_wide, nclass=7, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc8<-poLCA(f, data=dta_d1_wide, nclass=8, na.rm = FALSE, nrep=20, maxiter=max_II)
+
+# running time:  31.60514 mins
+```
+
+### Model comparison and selection
+
+```{r echo=FALSE}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/day2LCA1_6.Rdata")
+
+library(kableExtra)
+# dt <- read.csv("../Tablecsv/Modelfitd01.csv", header = T)
+# names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
+lca_results[1,9] <- "---"
+kable(lca_results, digits = 3, row.names = FALSE, align = "c",
+              format = "html", caption = "Model Comparison. (Day 2, n = 6153)") %>%
+ kable_styling(font_size = 16, 
+        bootstrap_options = c("striped", "hover", "condensed"),
+        position = "center", full_width = FALSE) %>% 
+  row_spec(c(4,6), bold = T, color = "white", background = "#D7261E") %>% 
+  footnote(general = "Abbreviation: N, number; resid.df, residual degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
+```
+
+### Day 2 data (Fig. 4 classes)
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE}
+
+library(ggthemr)
+
+# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
+
+# a <- (data.frame(lc5$probs))
+a <- (data.frame(lc4$probs))
+# a <- (data.frame(lc6$probs))
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+a$Class <- c("Class1", "Class2", "Class3", "Class4")
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")
+
+a_long <- a %>% 
+  gather(Hour, Prob, -Class) %>% 
+  separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")
+
+a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
+
+a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb"))
+
+a_long <- a_long %>% 
+  filter(Carbo != "Not_eating")
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 9.77%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  24.68%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 3:  38.28%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 4:  27.27%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+# 
+# ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 5:  18.52%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+# 
+# ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 6:  10.02%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+```
+
+### Day 2 data (Fig. 6 classes)
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE}
+
+library(ggthemr)
+
+# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
+
+# a <- (data.frame(lc5$probs))
+# a <- (data.frame(lc4$probs))
+a <- (data.frame(lc6$probs))
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+# a$Class <- c("Class1", "Class2", "Class3", "Class4")
+
+a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")
+
+a_long <- a %>% 
+  gather(Hour, Prob, -Class) %>% 
+  separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")
+
+a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
+
+a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb"))
+
+a_long <- a_long %>% 
+  filter(Carbo != "Not_eating")
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 23.54%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  17.43%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 3:  7.50%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 4:  23.53%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 5:  18.29%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 6:  9.70%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+```
+
+## Day 3
+
+```{r eval=FALSE}
+set.seed(01012)
+max_II <- 100000
+lc1 <- poLCA(f, data=dta_d3_wide, nclass=1, na.rm = FALSE, nrep=20, maxiter=max_II) #Loglinear independence model.
+lc2 <- poLCA(f, data=dta_d3_wide, nclass=2, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc3 <- poLCA(f, data=dta_d3_wide, nclass=3, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc4 <- poLCA(f, data=dta_d3_wide, nclass=4, na.rm = FALSE, nrep=20, maxiter=max_II) 
+lc5 <- poLCA(f, data=dta_d3_wide, nclass=5, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc6 <- poLCA(f, data=dta_d3_wide, nclass=6, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc7 <- poLCA(f, data=dta_d3_wide, nclass=7, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc8 <- poLCA(f, data=dta_d3_wide, nclass=8, na.rm = FALSE, nrep=20, maxiter=max_II)
+
+# running time:  31.65244 mins
+```
+
+### Model comparison and selection
+
+```{r echo=FALSE}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/day3LCA1_6.Rdata")
+
+library(kableExtra)
+# dt <- read.csv("../Tablecsv/Modelfitd01.csv", header = T)
+# names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
+lca_results[1,9] <- "---"
+kable(lca_results, digits = 3, row.names = FALSE, align = "c",
+              format = "html", caption = "Model Comparison. (Day 3, n = 6151)") %>%
+ kable_styling(font_size = 16, 
+        bootstrap_options = c("striped", "hover", "condensed"),
+        position = "center", full_width = FALSE) %>% 
+  row_spec(c(4,6), bold = T, color = "white", background = "#D7261E") %>% 
+  footnote(general = "Abbreviation: N, number; resid.df, residual degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
+```
+
+### Day 3 data (Fig. 4 classes)
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE}
+
+library(ggthemr)
+
+# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
+
+# a <- (data.frame(lc5$probs))
+a <- (data.frame(lc4$probs))
+# a <- (data.frame(lc6$probs))
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+a$Class <- c("Class1", "Class2", "Class3", "Class4")
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")
+
+a_long <- a %>% 
+  gather(Hour, Prob, -Class) %>% 
+  separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")
+
+a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
+
+a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb"))
+
+a_long <- a_long %>% 
+  filter(Carbo != "Not_eating")
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 8.79%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  39.49%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 3:  25.02%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 4:  26.69%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+# 
+# ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 5:  18.52%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+# 
+# ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 6:  10.02%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+```
+
+### Day 3 data (Fig. 6 classes)
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE}
+
+library(ggthemr)
+
+# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
+
+# a <- (data.frame(lc5$probs))
+# a <- (data.frame(lc4$probs))
+a <- (data.frame(lc6$probs))
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+# a$Class <- c("Class1", "Class2", "Class3", "Class4")
+
+a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")
+
+a_long <- a %>% 
+  gather(Hour, Prob, -Class) %>% 
+  separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")
+
+a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
+
+a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb"))
+
+a_long <- a_long %>% 
+  filter(Carbo != "Not_eating")
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 19.41%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  6.65%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 3:  15.12%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 4:  15.43%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 5:  20.84%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 6:  22.56%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+```
+
+## Day 4
+
+```{r eval=FALSE}
+set.seed(01012)
+max_II <- 100000
+lc1<-poLCA(f, data=dta_d4_wide, nclass=1, na.rm = FALSE, nrep=20, maxiter=max_II) #Loglinear independence model.
+lc2<-poLCA(f, data=dta_d4_wide, nclass=2, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc3<-poLCA(f, data=dta_d4_wide, nclass=3, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc4<-poLCA(f, data=dta_d4_wide, nclass=4, na.rm = FALSE, nrep=20, maxiter=max_II) 
+lc5<-poLCA(f, data=dta_d4_wide, nclass=5, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc6<-poLCA(f, data=dta_d4_wide, nclass=6, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc7<-poLCA(f, data=dta_d4_wide, nclass=7, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc8<-poLCA(f, data=dta_d4_wide, nclass=8, na.rm = FALSE, nrep=20, maxiter=max_II)
+
+# running time:  27.12666 mins
+```
+
+### Model comparison and selection
+
+```{r echo=FALSE}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")
+
+library(kableExtra)
+# dt <- read.csv("../Tablecsv/Modelfitd01.csv", header = T)
+# names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
+lca_results[1,9] <- "---"
+kable(lca_results, digits = 3, row.names = FALSE, align = "c",
+              format = "html", caption = "Model Comparison. (Day 4, n = 6026)") %>%
+ kable_styling(font_size = 16, 
+        bootstrap_options = c("striped", "hover", "condensed"),
+        position = "center", full_width = FALSE) %>% 
+  row_spec(c(4,6), bold = T, color = "white", background = "#D7261E") %>% 
+  footnote(general = "Abbreviation: N, number; resid.df, residual degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
+```
+
+### Day 4 data (Fig. 4 classes)
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE}
+
+library(ggthemr)
+
+# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
+
+# a <- (data.frame(lc5$probs))
+a <- (data.frame(lc4$probs))
+# a <- (data.frame(lc6$probs))
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+a$Class <- c("Class1", "Class2", "Class3", "Class4")
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")
+
+a_long <- a %>% 
+  gather(Hour, Prob, -Class) %>% 
+  separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")
+
+a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
+
+a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb"))
+
+a_long <- a_long %>% 
+  filter(Carbo != "Not_eating")
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 10.11%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  29.94%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 3:  24.40%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 4:  35.55%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+# 
+# ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 5:  18.52%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+# 
+# ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 6:  10.02%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+```
+
+### Day 4 data (Fig. 6 classes)
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE}
+
+library(ggthemr)
+
+# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
+
+# a <- (data.frame(lc5$probs))
+# a <- (data.frame(lc4$probs))
+a <- (data.frame(lc6$probs))
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+# a$Class <- c("Class1", "Class2", "Class3", "Class4")
+
+a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")
+
+a_long <- a %>% 
+  gather(Hour, Prob, -Class) %>% 
+  separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")
+
+a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
+
+a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb"))
+
+a_long <- a_long %>% 
+  filter(Carbo != "Not_eating")
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 7.51%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  27.19%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 3:  25.77%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 4:  16.17%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 5:  7.87%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 6:  15.49%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+```

### 2018-07-05 phrases.Rmd
LCA analysis by day

@@
 It helps with model identification and, importantly, ensures that the meaning of the latent statuses remains constant over time.**
+
+- Note that because each row of the transition probability matrix is conditioned on Time 1 latent status, this analysis of change in delinquency over time implicitly controls for time 1 delinquency.
+
+- Data can be used from individuals who provide responses to only some questions at a particular time and from those

### 2018-07-05 Rcode/Diagram.R

@@ -1,0 +1,90 @@
+#---------------------------------
+# PLOT
+#---------------------------------
+library("DiagrammeR")
+library("V8")
+# This code stems from D.L. Dahly 
+
+# build dataframe with predicted class for each observation
+x1<-rep(1, nrow(lc1$predclass))        
+x2<-lc2$predclass
+x3<-lc3$predclass
+x4<-lc4$predclass
+x5<-lc5$predclass
+results <- cbind(x1, x2, x3, x4, x5)
+results <-as.data.frame(results)
+results
+
+# avoid double naming of classes (because each LCA named their classes 1,2,...,k)
+N<-ncol(results) 
+n<-0
+for(i in 2:N) {
+  results[,i]<- (results[,i])+((i-1)+n)
+  n<-((i-1)+n)
+}
+
+# Make a data frame for the edges and counts
+# cross-tabulations and their frequencies
+g1<-plyr::count(results,c("x1","x2"))
+g2<-plyr::count(results,c("x2","x3"))
+colnames(g2)<-c("x1","x2","freq")
+g3<-plyr::count(results, c("x3","x4"))
+colnames(g3)<-c("x1", "x2","freq")
+g4<-plyr::count(results,c("x4","x5"))
+colnames(g4)<-c("x1","x2","freq")
+edges<-rbind(g1,g2,g3,g4)
+
+# Make a data frame for the class sizes
+h1<-plyr::count(results,c("x1"))
+h2<-plyr::count(results,c("x2"))
+colnames(h2)<-c("x1","freq")
+h3<- plyr::count(results,c("x3"))
+colnames(h3)<-c("x1","freq")
+h4<-plyr::count(results,c("x4"))
+colnames(h4)<-c("x1","freq")
+h5<-plyr::count(results,c("x5"))
+colnames(h5)<-c("x1", "freq")
+nodes<-rbind(h1,h2,h3,h4,h5)
+
+
+
+
+#dataframe for nodes - columns: node, label, type, attributes (like color and stuff)
+colnames(nodes)<-c("node","label")
+
+#scale nodes
+# nodes <- scale_nodes(nodes_df = nodes,
+#                      to_scale = nodes$label,
+#                      node_attr = "penwidth",
+#                      range = c(2, 5))
+
+#dataframe for edges - columns: edge from, edge to, label, relationship, attributes 
+colnames(edges)<-c("from", "to", "label")
+edges$relationship<-c("given_to")
+
+# #scale edges
+# edges <- scale_edges(edges_df = edges,
[…]

### 2018-07-05 Rcode/analysis8yrsA.R

@@ -127,14 +127,16 @@ dfs3 <- dfs3 %>%
 # For each subject, the total energy/carbohydrate intake for each eating time can be calculated --------
 
 old<-Sys.time()
-Energy <- ddply(dfs3, .(id_dy, id, SurveyYear, DayNo, Age, Sex, DiaryDaysCompleted, MealHourN),  
+Energy <- ddply(dfs3, .(id_dy, id, SurveyYear, DayNo, Age, Sex, DiaryDaysCompleted, MealHourN, DayofWeek),  
                 summarise, Tot_Energ = sum(EnergykJ), Tot_Carb = sum(Carbohydrateg), Tot_Sugar = sum(Totalsugarsg), Tot_Starch = sum(Starchg))
 new<-Sys.time()-old
 print(new)
     
 # Time difference of 3.876385 mins
+# Time difference of 3.882332 mins #"2018-07-04 11:52:13 BST"
+# Time difference of 3.765663 mins  "2018-07-04 14:47:13 BST"
 
-rm(df14d, df56d, df78d, dfs2)
+# rm(df14d, df56d, df78d, dfs2)
 
 head(Energy)
 
@@ -147,7 +149,8 @@ vecid<-unique(Energy$id)
 Energy <- Energy %>% 
   mutate(KJcarbo = Tot_Carb*16) %>% 
   mutate(CarKJpercentage = KJcarbo/Tot_Energ) %>% 
-  mutate(Carbo = cut(CarKJpercentage, breaks = c(0, 0.25999999999999, 0.7, 1.01), right = FALSE))
+  mutate(Carbo = cut(CarKJpercentage, breaks = c(0, 0.25999999999999, 0.7, 1.01), right = FALSE)) %>% 
+  mutate(Carbo2 = cut(CarKJpercentage, breaks = c(0, 0.25999999999999, 2), right = FALSE))
 
 Energy0 <- Energy[!(Energy$Tot_Energ == 0), ] # some food consumption does not contain any carbohydrates
 
@@ -157,27 +160,38 @@ Energy0$Carbo[is.na(Energy0$Carbo)] <- "[0.7,1.01)"
 
 Energy0$Carbo <- factor(Energy0$Carbo, labels = c("Low_carb", "Med_carb", "High_carb"))
 
[…]

### 2018-07-06 9thJuly/9thJuly.Rmd
new cut-off used

--- 2018-06-30 9thJuly/9thJuly.Rmd
@@
   summarise(N = n(), MeanAge = mean(Age), SDAge = sd(Age), minAge = min(Age), maxAge = max(Age))
+```
 
-# Dietary data by day
+## Distribution of the dietary data (by Day of Week)
+
+### Day1
+
+```{r}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/NDNSday1_4.Rdata")
+with(dta_d1_wide, tab1(DayofWeek, graph = FALSE, decimal = 2))
+```
+
+### Day2
+
+```{r}
+with(dta_d2_wide, tab1(DayofWeek, graph = FALSE, decimal = 2))
+```
+
+### Day3
+
+```{r}
+with(dta_d3_wide, tab1(DayofWeek, graph = FALSE, decimal = 2))
+```
+
+### Day4
+
+```{r}
+with(dta_d4_wide, tab1(DayofWeek, graph = FALSE, decimal = 2))
+```
+
+## Distribution of the dietary data (by DayNo)
+
+### Monday
+
+```{r}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/NDNSMon_Sun.Rdata")
+with(dta_Mon_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+### Tuesday
+
+```{r}
+with(dta_Tue_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+### Wednesday
+
+```{r}
+with(dta_Wed_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+### Thursday
+
+```{r}
+with(dta_Thurs_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+### Friday
+
+```{r}
+with(dta_Fri_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+### Saturday
+
+```{r}
+with(dta_Sat_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+### Sunday
+
+```{r}
+with(dta_Sun_wide, tab1(DayNo, graph = FALSE, decimal = 2))
+```
+
+**The problem of analysing data by day of the week would be that every subject only contributed 2-4 days' data. Therefore, we cannot see one subject's dietary change during a Mon-Sun week.**
+
+## Dietary data by day
+
+```{r message=FALSE, warning=FALSE, paged.print=FALSE}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/NDNSday1_4.Rdata")
+
+vecid <- unique(dfs3$id)
 
@@
 
-### day 1 data (3 classes)
+# Definition of carbohydrates intake groups:
 
-```{r}
+In this analysis, subjects have 2-4 days' dietary data: their food during the participation were self-recorded.
+We were able to calculate their energy intake each hour, then we also calculated the percentage of energy coming from carbohydrates that contributed to each hour when there is food consumption recorded.
+**Four categories were identified:**
 
-# LCA in day1 -------------------------------------------------------------
+1. Not eating; 
+2. Eating low carbohydrate food (energy contribution less than or equal to 25%); 
+3. Eating medium carbohyrate food (energy contribution between 26% and 75%); 
+4. Eating high carbohydrate food (energy contribution higher or equal to 75%).
 
-# noquote(paste(rep("H", 24), 0:23, sep = ""))
-#H0  H1  H2  H3  H4  H5  H6  H7  H8  H9  H10 H11 H12 H13 H14 H15 H16 H17 H18 H19 H20 H21 H22 H23
-library(poLCA)
-f <- cbind(H0, H1, H2, H3, H4, H5, H6, H7, H8, H9, H10,H11,H12,H13,H14,H15,H16,H17,H18,H19,H20,H21,H22,H23) ~ 1
-lc3 <- poLCA(f, dta_d1_wide, nclass = 3, graphs = TRUE, maxiter = 10000)
+# LCA analyses by day
 
-# lc3$llik #log-likelihood of model
-# 
-# lc3$P #Estimated class population shares 
-# 
-# lc3$predclass
+## Day 1
+
+```{r eval=FALSE}
+set.seed(01012)
+max_II <- 100000
+lc1<-poLCA(f, data=dta_d1_wide, nclass=1, na.rm = FALSE, nrep=20, maxiter=max_II) #Loglinear independence model.
+lc2<-poLCA(f, data=dta_d1_wide, nclass=2, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc3<-poLCA(f, data=dta_d1_wide, nclass=3, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc4<-poLCA(f, data=dta_d1_wide, nclass=4, na.rm = FALSE, nrep=20, maxiter=max_II) 
+lc5<-poLCA(f, data=dta_d1_wide, nclass=5, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc6<-poLCA(f, data=dta_d1_wide, nclass=6, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc7<-poLCA(f, data=dta_d1_wide, nclass=7, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc8<-poLCA(f, data=dta_d1_wide, nclass=8, na.rm = FALSE, nrep=20, maxiter=max_II)
 ```
 
-### day 1 data (Fig.)
+### Model comparison and selection
+
+```{r echo=FALSE}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/day1LCA1_6.Rdata")
+
+library(kableExtra)
+# dt <- read.csv("../Tablecsv/Modelfitd01.csv", header = T)
+# names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
+lca_results[1,9] <- "---"
+kable(lca_results, digits = 3, row.names = FALSE, align = "c",
+              format = "html", caption = "Model Comparison. (Day 1, n = 6153)") %>%
+ kable_styling(font_size = 16, 
+        bootstrap_options = c("striped", "hover", "condensed"),
+        position = "center", full_width = FALSE) %>% 
+  row_spec(7, bold = T, color = "white", background = "#D7261E") %>%
+  footnote(general = "Abbreviation: N, number; resid.df, residual degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
+```
+
+### Day 1 data (Fig. 7 classes)
 
@@
 library(ggthemr)
-a <- (data.frame(lc3$probs))
-a$Class <- c("Class1", "Class2", "Class3")
+
+# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
+
+# a <- (data.frame(lc5$probs))
+# a <- (data.frame(lc4$probs))
+# a <- (data.frame(lc6$probs))
+ a <- (data.frame(lc7$probs))
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+# a$Class <- c("Class1", "Class2", "Class3", "Class4")
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")
+
+a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6", "Class7")
 
@@
         ) + 
-  labs(title = "Class 1: 45.71%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 1: 18.67%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
         ) + 
-  labs(title = "Class 2:  41.71%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 2:  11.81%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
         ) + 
-  labs(title = "Class 3:  12.58%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 3:  10.66%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 4:  6.78%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 5:  17.45%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 6:  25.50%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class7", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 7:  9.15%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") +
@@
 
+<!-- ### Day 1 data (Fig. 6 classes)  -->
+
+<!-- ```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE} -->
+
+<!-- library(ggthemr) -->
+
+<!-- # lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000) -->
+
+<!-- # a <- (data.frame(lc5$probs)) -->
+<!-- # a <- (data.frame(lc4$probs)) -->
+<!-- a <- (data.frame(lc6$probs)) -->
+
+<!-- # a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5") -->
+<!-- # a$Class <- c("Class1", "Class2", "Class3", "Class4") -->
+
+<!-- a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6") -->
+
+<!-- a_long <- a %>%  -->
+<!--   gather(Hour, Prob, -Class) %>%  -->
+<!--   separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")  -->
+
+<!-- a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")) -->
+
+<!-- a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb")) -->
+
+<!-- a_long <- a_long %>%  -->
+<!--   filter(Carbo != "Not_eating") -->
+
+<!-- ggthemr("fresh", layout = "scientific") -->
+
+<!-- ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--   geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 1: 26.79%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--  geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 2:  11.72%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--  geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 3:  7.37%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--  geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 4:  25.58%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + -->
+<!--  geom_point(size = 3) + -->
+<!--   geom_line(size = 1.5) + -->
+<!--   theme(axis.title = element_text(size = 18), -->
+<!--         axis.text = element_text(size = 18), -->
+<!--         axis.line = element_line(colour = "black"), -->
+<!--         panel.border = element_blank(), -->
+<!--         panel.background = element_blank(), -->
+<!--         legend.text = element_text(size = 15), -->
+<!--         legend.title = element_text(size = 15) -->
+<!--         # legend.position = "bottom", -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) + -->
+<!--   labs(title = "Class 5:  18.52%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") + -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) + -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + -->
+<!--  geom_point(size = 3) + -->
+<!--   geom_line(size = 1.5) + -->
+<!--   theme(axis.title = element_text(size = 18), -->
+<!--         axis.text = element_text(size = 18), -->
+<!--         axis.line = element_line(colour = "black"), -->
+<!--         panel.border = element_blank(), -->
+<!--         panel.background = element_blank(), -->
+<!--         legend.text = element_text(size = 15), -->
+<!--         legend.title = element_text(size = 15) -->
+<!--         # legend.position = "bottom", -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) + -->
+<!--   labs(title = "Class 6:  10.02%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") + -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) + -->
+<!--   ylim(c(0,1)) -->
+<!-- ``` -->
+
+## Day 2
+
+```{r eval=FALSE}
+set.seed(01012)
+max_II <- 100000
+lc1<-poLCA(f, data=dta_d1_wide, nclass=1, na.rm = FALSE, nrep=20, maxiter=max_II) #Loglinear independence model.
+lc2<-poLCA(f, data=dta_d1_wide, nclass=2, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc3<-poLCA(f, data=dta_d1_wide, nclass=3, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc4<-poLCA(f, data=dta_d1_wide, nclass=4, na.rm = FALSE, nrep=20, maxiter=max_II) 
+lc5<-poLCA(f, data=dta_d1_wide, nclass=5, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc6<-poLCA(f, data=dta_d1_wide, nclass=6, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc7<-poLCA(f, data=dta_d1_wide, nclass=7, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc8<-poLCA(f, data=dta_d1_wide, nclass=8, na.rm = FALSE, nrep=20, maxiter=max_II)
+
+# running time:  31.60514 mins
+```
+
 ### Model comparison and selection
@@
 ```{r echo=FALSE}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/day2LCA1_6.Rdata")
+
 library(kableExtra)
-dt <- read.csv("../Tablecsv/Modelfit.csv", header = T)
-names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
-
-kable(dt, digits = 3, row.names = FALSE, align = "c",
-              format = "html", caption = "Model Comparison.") %>%
+# dt <- read.csv("../Tablecsv/Modelfitd01.csv", header = T)
+# names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
+lca_results[1,9] <- "---"
+kable(lca_results, digits = 3, row.names = FALSE, align = "c",
+              format = "html", caption = "Model Comparison. (Day 2, n = 6153)") %>%
  kable_styling(font_size = 16, 
@@
         position = "center", full_width = FALSE) %>% 
-  row_spec(5, bold = T, color = "white", background = "#D7261E") %>% 
-  footnote(general = "Abbreviation: N, number; G^2, the likelihood ratio statistic; AIC, Akaike information criterion; BIC, Bayesian information criterion.")
+  row_spec(7, bold = T, color = "white", background = "#D7261E") %>% 
+  footnote(general = "Abbreviation: N, number; resid.df, residual degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
 ```
 
-### Five classes visualisation
+### Day 2 data (Fig. 7 classes)
 
@@
 
-lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
+# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
 
-a <- (data.frame(lc5$probs))
-a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+# a <- (data.frame(lc5$probs))
+# a <- (data.frame(lc4$probs))
+# a <- (data.frame(lc6$probs))
+a <- (data.frame(lc7$probs))
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+# a$Class <- c("Class1", "Class2", "Class3", "Class4")
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")
+a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6", "Class7")
 
@@
         ) + 
-  labs(title = "Class 1: 33.38%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 1: 18.67%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
         ) + 
-  labs(title = "Class 2:  25.89%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 2:  11.81%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
         ) + 
-  labs(title = "Class 3:  22.46%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 3:  10.66%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
         ) + 
-  labs(title = "Class 4:  7.65%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 4:  6.78%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
         ) +
-  labs(title = "Class 5:  12.27%", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 5:  17.45%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 6:  25.50%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class7", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 7:  9.15%", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") +
@@
 ```
+
+<!-- ### Day 2 data (Fig. 6 classes)  -->
+
+<!-- ```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE} -->
+
+<!-- library(ggthemr) -->
+
+<!-- # lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000) -->
+
+<!-- # a <- (data.frame(lc5$probs)) -->
+<!-- # a <- (data.frame(lc4$probs)) -->
+<!-- a <- (data.frame(lc6$probs)) -->
+
+<!-- # a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5") -->
+<!-- # a$Class <- c("Class1", "Class2", "Class3", "Class4") -->
+
+<!-- a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6") -->
+
+<!-- a_long <- a %>%  -->
+<!--   gather(Hour, Prob, -Class) %>%  -->
+<!--   separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")  -->
+
+<!-- a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")) -->
+
+<!-- a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb")) -->
+
+<!-- a_long <- a_long %>%  -->
+<!--   filter(Carbo != "Not_eating") -->
+
+<!-- ggthemr("fresh", layout = "scientific") -->
+
+<!-- ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--   geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 1: 23.54%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--  geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 2:  17.43%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--  geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 3:  7.50%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--  geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 4:  23.53%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + -->
+<!--  geom_point(size = 3) + -->
+<!--   geom_line(size = 1.5) + -->
+<!--   theme(axis.title = element_text(size = 18), -->
+<!--         axis.text = element_text(size = 18), -->
+<!--         axis.line = element_line(colour = "black"), -->
+<!--         panel.border = element_blank(), -->
+<!--         panel.background = element_blank(), -->
+<!--         legend.text = element_text(size = 15), -->
+<!--         legend.title = element_text(size = 15) -->
+<!--         # legend.position = "bottom", -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) + -->
+<!--   labs(title = "Class 5:  18.29%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") + -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) + -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + -->
+<!--  geom_point(size = 3) + -->
+<!--   geom_line(size = 1.5) + -->
+<!--   theme(axis.title = element_text(size = 18), -->
+<!--         axis.text = element_text(size = 18), -->
+<!--         axis.line = element_line(colour = "black"), -->
+<!--         panel.border = element_blank(), -->
+<!--         panel.background = element_blank(), -->
+<!--         legend.text = element_text(size = 15), -->
+<!--         legend.title = element_text(size = 15) -->
+<!--         # legend.position = "bottom", -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) + -->
+<!--   labs(title = "Class 6:  9.70%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") + -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) + -->
+<!--   ylim(c(0,1)) -->
+<!-- ``` -->
+
+## Day 3
+
+```{r eval=FALSE}
+set.seed(01012)
+max_II <- 100000
+lc1 <- poLCA(f, data=dta_d3_wide, nclass=1, na.rm = FALSE, nrep=20, maxiter=max_II) #Loglinear independence model.
+lc2 <- poLCA(f, data=dta_d3_wide, nclass=2, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc3 <- poLCA(f, data=dta_d3_wide, nclass=3, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc4 <- poLCA(f, data=dta_d3_wide, nclass=4, na.rm = FALSE, nrep=20, maxiter=max_II) 
+lc5 <- poLCA(f, data=dta_d3_wide, nclass=5, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc6 <- poLCA(f, data=dta_d3_wide, nclass=6, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc7 <- poLCA(f, data=dta_d3_wide, nclass=7, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc8 <- poLCA(f, data=dta_d3_wide, nclass=8, na.rm = FALSE, nrep=20, maxiter=max_II)
+
+# running time:  31.65244 mins
+```
+
+### Model comparison and selection
+
+```{r echo=FALSE}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/day3LCA1_6.Rdata")
+
+library(kableExtra)
+# dt <- read.csv("../Tablecsv/Modelfitd01.csv", header = T)
+# names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
+lca_results[1,9] <- "---"
+kable(lca_results, digits = 3, row.names = FALSE, align = "c",
+              format = "html", caption = "Model Comparison. (Day 3, n = 6151)") %>%
+ kable_styling(font_size = 16, 
+        bootstrap_options = c("striped", "hover", "condensed"),
+        position = "center", full_width = FALSE) %>% 
+  row_spec(7, bold = T, color = "white", background = "#D7261E") %>% 
+  footnote(general = "Abbreviation: N, number; resid.df, residual degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
+```
+
+### Day 3 data (Fig. 7 classes)
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE}
+
+library(ggthemr)
+
+# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
+
+# a <- (data.frame(lc5$probs))
+# a <- (data.frame(lc4$probs))
+# a <- (data.frame(lc6$probs))
+a <- (data.frame(lc7$probs))
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+# a$Class <- c("Class1", "Class2", "Class3", "Class4")
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")
+
+a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6", "Class7")
+
+a_long <- a %>% 
+  gather(Hour, Prob, -Class) %>% 
+  separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")
+
+a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
+
+a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb"))
+
+a_long <- a_long %>% 
+  filter(Carbo != "Not_eating")
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 6.13%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  13.32%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 3:  17.95%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 4:  8.16%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 5:  20.48%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 6:  20.58%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class7", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 7:  13.38%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+```
+
+<!-- ### Day 3 data (Fig. 6 classes)  -->
+
+<!-- ```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE} -->
+
+<!-- library(ggthemr) -->
+
+<!-- # lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000) -->
+
+<!-- # a <- (data.frame(lc5$probs)) -->
+<!-- # a <- (data.frame(lc4$probs)) -->
+<!-- a <- (data.frame(lc6$probs)) -->
+
+<!-- # a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5") -->
+<!-- # a$Class <- c("Class1", "Class2", "Class3", "Class4") -->
+
+<!-- a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6") -->
+
+<!-- a_long <- a %>%  -->
+<!--   gather(Hour, Prob, -Class) %>%  -->
+<!--   separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")  -->
+
+<!-- a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")) -->
+
+<!-- a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb")) -->
+
+<!-- a_long <- a_long %>%  -->
+<!--   filter(Carbo != "Not_eating") -->
+
+<!-- ggthemr("fresh", layout = "scientific") -->
+
+<!-- ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--   geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 1: 19.41%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--  geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 2:  6.65%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--  geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 3:  15.12%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--  geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 4:  15.43%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + -->
+<!--  geom_point(size = 3) + -->
+<!--   geom_line(size = 1.5) + -->
+<!--   theme(axis.title = element_text(size = 18), -->
+<!--         axis.text = element_text(size = 18), -->
+<!--         axis.line = element_line(colour = "black"), -->
+<!--         panel.border = element_blank(), -->
+<!--         panel.background = element_blank(), -->
+<!--         legend.text = element_text(size = 15), -->
+<!--         legend.title = element_text(size = 15) -->
+<!--         # legend.position = "bottom", -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) + -->
+<!--   labs(title = "Class 5:  20.84%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") + -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) + -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + -->
+<!--  geom_point(size = 3) + -->
+<!--   geom_line(size = 1.5) + -->
+<!--   theme(axis.title = element_text(size = 18), -->
+<!--         axis.text = element_text(size = 18), -->
+<!--         axis.line = element_line(colour = "black"), -->
+<!--         panel.border = element_blank(), -->
+<!--         panel.background = element_blank(), -->
+<!--         legend.text = element_text(size = 15), -->
+<!--         legend.title = element_text(size = 15) -->
+<!--         # legend.position = "bottom", -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) + -->
+<!--   labs(title = "Class 6:  22.56%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") + -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) + -->
+<!--   ylim(c(0,1)) -->
+<!-- ``` -->
+
+## Day 4
+
+```{r eval=FALSE}
+set.seed(01012)
+max_II <- 100000
+lc1<-poLCA(f, data=dta_d4_wide, nclass=1, na.rm = FALSE, nrep=20, maxiter=max_II) #Loglinear independence model.
+lc2<-poLCA(f, data=dta_d4_wide, nclass=2, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc3<-poLCA(f, data=dta_d4_wide, nclass=3, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc4<-poLCA(f, data=dta_d4_wide, nclass=4, na.rm = FALSE, nrep=20, maxiter=max_II) 
+lc5<-poLCA(f, data=dta_d4_wide, nclass=5, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc6<-poLCA(f, data=dta_d4_wide, nclass=6, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc7<-poLCA(f, data=dta_d4_wide, nclass=7, na.rm = FALSE, nrep=20, maxiter=max_II)
+lc8<-poLCA(f, data=dta_d4_wide, nclass=8, na.rm = FALSE, nrep=20, maxiter=max_II)
+
+# running time:  27.12666 mins
+```
+
+### Model comparison and selection
+
+```{r echo=FALSE}
+rm(list=ls(all=TRUE))
+load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")
+
+library(kableExtra)
+# dt <- read.csv("../Tablecsv/Modelfitd01.csv", header = T)
+# names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
+lca_results[1,9] <- "---"
+kable(lca_results, digits = 3, row.names = FALSE, align = "c",
+              format = "html", caption = "Model Comparison. (Day 4, n = 6026)") %>%
+ kable_styling(font_size = 16, 
+        bootstrap_options = c("striped", "hover", "condensed"),
+        position = "center", full_width = FALSE) %>% 
+  row_spec(8, bold = T, color = "white", background = "#D7261E") %>% 
+  footnote(general = "Abbreviation: N, number; resid.df, residual degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
+```
+
+### Day 4 data (Fig. 8 classes)
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE}
+
+library(ggthemr)
+
+# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)
+
+# a <- (data.frame(lc5$probs))
+# a <- (data.frame(lc4$probs))
+# a <- (data.frame(lc6$probs))
+a <- (data.frame(lc8$probs))
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
+# a$Class <- c("Class1", "Class2", "Class3", "Class4")
+
+# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")
+
+a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6", "Class7", "Class8")
+
+a_long <- a %>% 
+  gather(Hour, Prob, -Class) %>% 
+  separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")
+
+a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
+
+a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb"))
+
+a_long <- a_long %>% 
+  filter(Carbo != "Not_eating")
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 6.67%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  10.61%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 3:  14.93%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 4:  20.54%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 5:  5.76%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 6:  16.97%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class7", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 7:  12.17%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(a_long[a_long$Class == "Class8", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 8:  12.36%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+```
+
+<!-- ### Day 4 data (Fig. 6 classes)  -->
+
+<!-- ```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE} -->
+
+<!-- library(ggthemr) -->
+
+<!-- # lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000) -->
+
+<!-- # a <- (data.frame(lc5$probs)) -->
+<!-- # a <- (data.frame(lc4$probs)) -->
+<!-- a <- (data.frame(lc6$probs)) -->
+
+<!-- # a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5") -->
+<!-- # a$Class <- c("Class1", "Class2", "Class3", "Class4") -->
+
+<!-- a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6") -->
+
+<!-- a_long <- a %>%  -->
+<!--   gather(Hour, Prob, -Class) %>%  -->
+<!--   separate(Hour, into = c("HourN", "Carbo"), sep = "\\.")  -->
+
+<!-- a_long$HourN <- factor(a_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")) -->
+
+<!-- a_long$Carbo <- factor(a_long$Carbo, levels = c("Low_carb", "Med_carb", "High_carb")) -->
+
+<!-- a_long <- a_long %>%  -->
+<!--   filter(Carbo != "Not_eating") -->
+
+<!-- ggthemr("fresh", layout = "scientific") -->
+
+<!-- ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--   geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 1: 7.51%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--  geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 2:  27.19%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--  geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 3:  25.77%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +  -->
+<!--  geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) +  -->
+<!--   labs(title = "Class 4:  16.17%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) +  -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + -->
+<!--  geom_point(size = 3) + -->
+<!--   geom_line(size = 1.5) + -->
+<!--   theme(axis.title = element_text(size = 18), -->
+<!--         axis.text = element_text(size = 18), -->
+<!--         axis.line = element_line(colour = "black"), -->
+<!--         panel.border = element_blank(), -->
+<!--         panel.background = element_blank(), -->
+<!--         legend.text = element_text(size = 15), -->
+<!--         legend.title = element_text(size = 15) -->
+<!--         # legend.position = "bottom", -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) + -->
+<!--   labs(title = "Class 5:  7.87%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") + -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) + -->
+<!--   ylim(c(0,1)) -->
+
+<!-- ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + -->
+<!--  geom_point(size = 3) + -->
+<!--   geom_line(size = 1.5) + -->
+<!--   theme(axis.title = element_text(size = 18), -->
+<!--         axis.text = element_text(size = 18), -->
+<!--         axis.line = element_line(colour = "black"), -->
+<!--         panel.border = element_blank(), -->
+<!--         panel.background = element_blank(), -->
+<!--         legend.text = element_text(size = 15), -->
+<!--         legend.title = element_text(size = 15) -->
+<!--         # legend.position = "bottom", -->
+<!--         # legend.direction = "horizontal" -->
+<!--         ) + -->
+<!--   labs(title = "Class 6:  15.49%", x = "Hour of the day", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") + -->
+<!--   scale_color_discrete(labels = c("Low", "Medium", "High")) + -->
+<!--   ylim(c(0,1)) -->
+<!-- ``` -->

### 2018-07-06 Rcode/analysis8yrsA.R

@@ -149,12 +149,12 @@ vecid<-unique(Energy$id)
 Energy <- Energy %>% 
   mutate(KJcarbo = Tot_Carb*16) %>% 
   mutate(CarKJpercentage = KJcarbo/Tot_Energ) %>% 
-  mutate(Carbo = cut(CarKJpercentage, breaks = c(0, 0.25999999999999, 0.7, 1.01), right = FALSE)) %>% 
-  mutate(Carbo2 = cut(CarKJpercentage, breaks = c(0, 0.25999999999999, 2), right = FALSE))
+  mutate(Carbo = cut(CarKJpercentage, breaks = c(0, 0.26, 0.75, 2), right = FALSE)) %>% 
+  mutate(Carbo2 = cut(CarKJpercentage, breaks = c(0, 0.26, 2), right = FALSE))
 
 Energy0 <- Energy[!(Energy$Tot_Energ == 0), ] # some food consumption does not contain any carbohydrates
 
-Energy0$Carbo[is.na(Energy0$Carbo)] <- "[0.7,1.01)"
+# Energy0$Carbo[is.na(Energy0$Carbo)] <- "[0.7,1.01)"
 #
 
 
@@ -568,6 +568,7 @@ f <- cbind(H0, H1, H2, H3, H4, H5, H6, H7, H8, H9, H10,H11,H12,H13,H14,H15,H16,H
 
 set.seed(20180705)
 max_II <- 100000
+old <- Sys.time()
 lc1 <- poLCA(f, data=dta_d1_wide, nclass=1, na.rm = FALSE, nrep=20, maxiter=max_II) #Loglinear independence model.
 lc2 <- poLCA(f, data=dta_d1_wide, nclass=2, na.rm = FALSE, nrep=20, maxiter=max_II)
 lc3 <- poLCA(f, data=dta_d1_wide, nclass=3, na.rm = FALSE, nrep=20, maxiter=max_II)
@@ -576,6 +577,8 @@ lc5 <- poLCA(f, data=dta_d1_wide, nclass=5, na.rm = FALSE, nrep=20, maxiter=max_
 lc6 <- poLCA(f, data=dta_d1_wide, nclass=6, na.rm = FALSE, nrep=20, maxiter=max_II)
 lc7 <- poLCA(f, data=dta_d1_wide, nclass=7, na.rm = FALSE, nrep=20, maxiter=max_II)
 lc8 <- poLCA(f, data=dta_d1_wide, nclass=8, na.rm = FALSE, nrep=20, maxiter=max_II)
[…]

### 2018-07-08 9thJuly/9thJuly.Rmd
mixed results added

@@
     toc_float: true
+    number_sections: true
+    nature:
+      highlightLines: true
 ---
@@
 2. Eating low carbohydrate food (energy contribution less than or equal to 25%); 
-3. Eating medium carbohyrate food (energy contribution between 26% and 75%); 
+3. Eating medium carbohydrate food (energy contribution between 26% and 75%); 
 4. Eating high carbohydrate food (energy contribution higher or equal to 75%).
@@
 
-```{r echo=FALSE}
+```{r echo=FALSE, cache=TRUE}
 rm(list=ls(all=TRUE))
@@
 
-```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE}
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
 
@@
 <!-- ``` -->
+
+# How to deal with within-individual variation?
+
+1.
+LTA (latent transit analysis): this method can help calculate the probabilities of transition from one class to another on condition of the previous (occasion's) class.
+I don't think we can apply this method since every subject in the NDNS data set has a different four days of Week:
+    - For example subject A provided dietary data for Monday (day1), Tuesday (day2), Wednesday (day3), and Thursday (day4); 
+    - However, subject B provided dietary data on Thursday (day1), Friday (day2), Saturday (day3), and Sunday (day4); 
+    - Using day 1 (or any day from the four days) data alone would be not appropriate since different people started from different day, their day 1 might be weekday or weekends. 
+    - So using LTA analysis would be a good choice when all of the subjects were measured on the same day of the week. Here, in our case, it may not be a good option.
+
+2.
+LCA with random effect: this approach is actually using all of the data that we have, taking the personal variation into account.
+By saying random effect here, we mean in the data set, some observations are not independent from each other (every 2-4 observations are from an exact same person), in other words, **they are nested within the person**.
+Then we should tell software that it is the persons rather than the observations are independent from each other.
+This is more reasonable than enforcing a subject to stay in the same class for all four days, because it is certainly possible that one person can belong to a class for a few days, and jump to another class on the other day(s) within the survey.
+
+Therefore, we chose the 2nd method in the analyses.
+This can be done by [installing the LCA macro in the SAS program (https://methodology.psu.edu/downloads/proclcalta)](https://methodology.psu.edu/downloads/proclcalta), and using the `PROC LCA` command.
+
+# Mixed effect LCA (or shall we call it multilevel LCA?) results
+
+## Input and Output example when fitting a three class LCA model
+
+### SAS code in running the three classes mixed effect LCA analysis on the NDNS data
+
+```{r  eval=FALSE}
+PROC LCA DATA=store.NDNS OUTPOST=STORE.NDNS_PP3 OUTEST=STORE.NDNS_EST3
+            OUTPARAM=STORE.NDNS_PARAM3; /* input data and output (results, estimation, posterior probabilities) dataset names */
+NCLASS 3; /* number of classes fitting*/                                  
+ID ID_DAY ID SEX DAYOFWEEK AGE; /* variable names want to keep in the output datasets */
+ITEMS H0 H1 H2 H3 H4 H5 H6 H7 H8 H9 H10 H11 H12 H13 H14 H15 H16 H17 H18 H19 H20 H21 H22 H23;
+CATEGORIES 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4;
+CLUSTERS ID; /* this is the key, to specify ID as the cluster variable */ 
+MAXITER 100000;
+SEED 100000;
+RUN;
+```
+
+### SAS output of running the mixed effect LCA analysis
+
+The following output shows that there are 24483 observations in the NDNS data set, the number of cluster is 6155 (which matches the sample size what we described in the description section).
+Smallest/largest cluster size is 2/4 indicating the number of observations within individual varies between 2 to 4.
+
+```{r eval=FALSE}
+Data Summary, Model Information, and Fit Statistics (EM Algorithm)
+
+Number of subjects in dataset:       24483 
+Number of subjects in analysis:      24483
+Number of clusters in analysis:       6155 
+Smallest cluster size:                   2 
+Largest cluster size:                    4
+
+Number of measurement items:            24
+Response categories per item:            4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4 4
+Number of groups in the data:            1
+Number of latent classes:                3
+
+The analysis includes clusters.
+Cluster variable name:  id
+Rho starting values were randomly generated (seed = 100000).
+
+No parameter restrictions were specified (freely estimated).
+
+The model converged in 298 iterations.
+
+Maximum number of iterations: 100000
+Convergence method: maximum absolute deviation (MAD)
+Convergence criterion:  0.000001000
+
+=============================================
+Fit statistics:
+=============================================
+
+Log-likelihood:   -380275.38
+G-squared:         275662.53
+AIC:               276098.53
+BIC:               277865.58
+CAIC:              278083.58
+Adjusted BIC:      277172.79
+Entropy:                0.85
+(Based on the pseudo-likelihood.)
+```
+
+### Example of the posterior probabilities estimated by the model
+
+Where:
+
+- **POSTLC1**: posterior probability of belonging to latent class 1 given the subject's carbohydrate eating pattern on that day. 
+- **POSTLC2**: posterior probability of belonging to latent class 2 given the subject's carbohydrate eating pattern on that day. 
+- **POSTLC3**: posterior probability of belonging to latent class 3 given the subject's carbohydrate eating pattern on that day.
+- **BEST**: The latent class group assigned by the model (highest probability among POSTLC1, POSTLC2, and, POSTLC3).
+
+```{r echo=FALSE}
+rm(list=ls(all=TRUE))
+dt <- read.csv("../Tablecsv/ndns_pp3.csv", header = T)
+# names(dt) <- c("N of classes", "log-likelihood", "G^2",  "AIC", "BIC", "cAIC", "aBIC", "Entropy")
+# dt[1,8] <- "---"
+
+library(DT)
+dt <- dt %>% 
+  select(id, Sex, DayofWeek, Age, POSTLC1, POSTLC2, POSTLC3, BEST) %>% 
+  filter(id < 40000000)
+datatable(dt, options = list(
+  searching = TRUE,
+  pageLength = 15,
+  lengthMenu = c(5, 10, 15, 20)
+)) %>% 
+  formatRound("POSTLC1", 3) %>% 
+  formatRound("POSTLC2", 3) %>% 
+  formatRound("POSTLC3", 3) 
+```
+
+## Model comparison and selection
+
+```{r echo=FALSE}
+rm(list=ls(all=TRUE))
+# load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")
+
+library(kableExtra)
+dt <- read.csv("../Tablecsv/ModelsMixed.csv", header = T)
+names(dt) <- c("N of classes", "log-likelihood", "G^2",  "AIC", "BIC", "cAIC", "aBIC", "Entropy")
+dt[1,8] <- "---"
+kable(dt, digits = 3, row.names = FALSE, align = "c",
+              format = "html", caption = "Model Comparison. (All data, n = 6155)") %>%
+ kable_styling(font_size = 16, 
+        bootstrap_options = c("striped", "hover", "condensed"),
+        position = "center", full_width = FALSE) %>% 
+  row_spec(6, bold = T, color = "white", background = "#D7261E") %>% 
+  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
+```
+
+From comparing output of different mixed effect LCA models in the above table, **we think a 6 class model may be considered as an appropriate model among them.**
+
+## Visualisation of the 6-class model
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+
+library(ggthemr)
+rm(list=ls(all=TRUE))
+
+ggthemr("fresh", layout = "scientific")
+
+dt <- read.csv("../Tablecsv/ndns_param6.csv", header = T)
+
+dt_long <- dt[-1,-c(1,2)] %>% 
+  gather(Hour, Prob, -VARIABLE, -RESPCAT) %>% 
+  separate(Hour, into = c("EST" ,"Class"), sep = "T")
+
+dt_long <- dt_long %>% 
+  filter(RESPCAT != 1) %>% 
+  mutate(RESPCAT = as.factor(RESPCAT)) %>% 
+  mutate(Carbo = revalue(RESPCAT, c("2" = "Low_carb", "3" = "Med_carb", "4" = "High_carb"))) %>% 
+  mutate(HourN = as.character(VARIABLE)) %>% 
+  mutate(HourN = factor(HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")))
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(dt_long[dt_long$Class == "LC1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 12.78%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  24.73%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 3:  21.24%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 4:  23.08%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 5:  4.07%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 6:  14.10%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+# 
+# ggplot(a_long[a_long$Class == "Class7", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 7:  12.17%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+# 
+# ggplot(a_long[a_long$Class == "Class8", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 8:  12.36%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+```
+
+## Visualisation of the classes by Carbohydrate eating types
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(dt_long[dt_long$Carbo == "Low_carb", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
+  geom_point(size = 2) + 
+  geom_line(size = 1.2) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Low carbohydarte food consumption by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
+  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Carbo == "Med_carb", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
+  geom_point(size = 2) + 
+  geom_line(size = 1.2) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Medium carbohydarte food consumption by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
+  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Carbo == "High_carb", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
+  geom_point(size = 2) + 
+  geom_line(size = 1.2) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "High carbohydarte food consumption by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
+  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6")) + 
+  ylim(c(0,1))
+```
+
+From this results, we might consider combining high-carbohydrate with the medium-carbohydrate category since in the third figure ("High carbohydrate consumption by latent classes") above, there is hardly any difference can be recognised.
+So, we tried the same analysis in the same data set combining medium and high carbohydrate consumptions together:
+
+# Mixed effect LCA with carbohydrates intake groups redefined:
+
+1. Not eating; 
+2. Eating low carbohydrate food (energy contribution less than or equal to 25%); 
+3. Eating medium-or-high carbohydrate food (energy contribution higher than 26%); 
+4. ~~Eating high carbohydrate food (energy contribution higher or equal to 75%).~~
+
+## Model comparison and selection
+
+```{r echo=FALSE}
+rm(list=ls(all=TRUE))
+# load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")
+
+library(kableExtra)
+dt <- read.csv("../Tablecsv/ModelsMixedLOWORMEDIUM.csv", header = T)
+names(dt) <- c("N of classes", "log-likelihood", "G^2",  "AIC", "BIC", "cAIC", "aBIC", "Entropy")
+dt[1,8] <- "---"
+kable(dt, digits = 3, row.names = FALSE, align = "c",
+              format = "html", caption = "Model Comparison. (All data, n = 6155)") %>%
+ kable_styling(font_size = 16, 
+        bootstrap_options = c("striped", "hover", "condensed"),
+        position = "center", full_width = FALSE) %>% 
+  row_spec(c(3,4,6), bold = T, color = "white", background = "#D7261E") %>% 
+  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
+```
+
+## Visualisation of the 3-class model
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+
+library(ggthemr)
+rm(list=ls(all=TRUE))
+
+ggthemr("fresh", layout = "scientific")
+
+dt <- read.csv("../Tablecsv/ndns_param3_2cat.csv", header = T)
+
+dt_long <- dt[-1,-c(1,2)] %>% 
+  gather(Hour, Prob, -VARIABLE, -RESPCAT) %>% 
+  separate(Hour, into = c("EST" ,"Class"), sep = "T")
+
+dt_long <- dt_long %>% 
+  filter(RESPCAT != 1) %>% 
+  mutate(RESPCAT = as.factor(RESPCAT)) %>% 
+  mutate(Carbo = revalue(RESPCAT, c("2" = "Low_carb", "3" = "Med_carb", "4" = "High_carb"))) %>% 
+  mutate(HourN = as.character(VARIABLE)) %>% 
+  mutate(HourN = factor(HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")))
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(dt_long[dt_long$Class == "LC1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 70.85%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  24.72%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 3:  4.43%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+# 
+# ggplot(dt_long[dt_long$Class == "LC4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+#  geom_point(size = 3) + 
+#   geom_line(size = 1.5) + 
+#   theme(axis.title = element_text(size = 18), 
+#         axis.text = element_text(size = 18), 
+#         axis.line = element_line(colour = "black"), 
+#         panel.border = element_blank(), 
+#         panel.background = element_blank(), 
+#         legend.text = element_text(size = 15), 
+#         legend.title = element_text(size = 15) 
+#         # legend.position = "bottom", 
+#         # legend.direction = "horizontal"
+#         ) + 
+#   labs(title = "Class 4:  23.08%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") + 
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+#   ylim(c(0,1))
+# 
+# 
+# ggplot(dt_long[dt_long$Class == "LC5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 5:  4.07%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+# 
+# ggplot(dt_long[dt_long$Class == "LC6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 6:  14.10%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+```
+
+## Visualisation of the 4-class model
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+
+library(ggthemr)
+rm(list=ls(all=TRUE))
+
+ggthemr("fresh", layout = "scientific")
+
+dt <- read.csv("../Tablecsv/ndns_param4_2cat.csv", header = T)
+
+dt_long <- dt[-1,-c(1,2)] %>% 
+  gather(Hour, Prob, -VARIABLE, -RESPCAT) %>% 
+  separate(Hour, into = c("EST" ,"Class"), sep = "T")
+
+dt_long <- dt_long %>% 
+  filter(RESPCAT != 1) %>% 
+  mutate(RESPCAT = as.factor(RESPCAT)) %>% 
+  mutate(Carbo = revalue(RESPCAT, c("2" = "Low_carb", "3" = "Med_carb", "4" = "High_carb"))) %>% 
+  mutate(HourN = as.character(VARIABLE)) %>% 
+  mutate(HourN = factor(HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")))
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(dt_long[dt_long$Class == "LC1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 43.24%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  24.67%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 3:  4.59%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 4:  27.49%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+# 
+# ggplot(dt_long[dt_long$Class == "LC5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 5:  4.07%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+# 
+# ggplot(dt_long[dt_long$Class == "LC6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 6:  14.10%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+```
+
+## Visualisation of the 5-class model
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+
+library(ggthemr)
+rm(list=ls(all=TRUE))
+
+ggthemr("fresh", layout = "scientific")
+
+dt <- read.csv("../Tablecsv/ndns_param5_2cat.csv", header = T)
+
+dt_long <- dt[-1,-c(1,2)] %>% 
+  gather(Hour, Prob, -VARIABLE, -RESPCAT) %>% 
+  separate(Hour, into = c("EST" ,"Class"), sep = "T")
+
+dt_long <- dt_long %>% 
+  filter(RESPCAT != 1) %>% 
+  mutate(RESPCAT = as.factor(RESPCAT)) %>% 
+  mutate(Carbo = revalue(RESPCAT, c("2" = "Low_carb", "3" = "Med_carb", "4" = "High_carb"))) %>% 
+  mutate(HourN = as.character(VARIABLE)) %>% 
+  mutate(HourN = factor(HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")))
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(dt_long[dt_long$Class == "LC1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 29.13%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  24.67%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 3:  4.10%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 4:  22.53%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 5:  19.58%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+# 
+# ggplot(dt_long[dt_long$Class == "LC6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 6:  14.10%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+```
+
+## Visualisation of the 6-class model
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+
+library(ggthemr)
+rm(list=ls(all=TRUE))
+
+ggthemr("fresh", layout = "scientific")
+
+dt <- read.csv("../Tablecsv/ndns_param6_2cat.csv", header = T)
+
+dt_long <- dt[-1,-c(1,2)] %>% 
+  gather(Hour, Prob, -VARIABLE, -RESPCAT) %>% 
+  separate(Hour, into = c("EST" ,"Class"), sep = "T")
+
+dt_long <- dt_long %>% 
+  filter(RESPCAT != 1) %>% 
+  mutate(RESPCAT = as.factor(RESPCAT)) %>% 
+  mutate(Carbo = revalue(RESPCAT, c("2" = "Low_carb", "3" = "Med_carb", "4" = "High_carb"))) %>% 
+  mutate(HourN = as.character(VARIABLE)) %>% 
+  mutate(HourN = factor(HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")))
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(dt_long[dt_long$Class == "LC1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 22.29%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  24.61%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 3:  3.94%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 4:  22.31%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 5:  15.98%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 6:  10.86%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Low", "Medium", "High")) +
+  ylim(c(0,1))
+```

### 2018-07-08 paper/main.tex
update of the main acknowledgement

@@
 
-\thesistitle{The timing of Carbonhydrate intake in the NDNS 2008-2014 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+\thesistitle{The timing of carbohydrate intake in UK adults, using the National Dietary and Nutrition Survey (NDNS) 2008-2014 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
 \supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
@@
 \begin{itemize}
-\item This work was done wholly or mainly while in candidature for a research degree at this University.
-\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
+\item This work was done wholly or mainly while in candidature for a MSc degree on Medical Statistics at this University.
+\item No part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution.
 \item Where I have consulted the published work of others, this is always clearly attributed.
@@
 
+%----------------------------------------------------------------------------------------
+%	ACKNOWLEDGEMENTS
+%----------------------------------------------------------------------------------------
+
+\begin{acknowledgements}
+\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
+
+I would like to thank my tutor and supervisor \supname, for his guidance, patience, and help while working on this project and also to Dr.
+Suzana Almoosawi for her invaluable nutritional academic insight, and suggestions.
+\\
+
+Thanks to Raoul Mansukhani, for sharing his previous work and thoughts on the analyses, methodology in helpful discussions.	 \\
+
+I would like to thank the team of the National Dietary and Nutrition Survey (NDNS) who have made their data available to the public for academic study. \\
+
+I would like to thank all of the teachers, lecturers, staffs, and fellow course mates in the Department of Medical Statistics for providing their wonderful teaching techniques, sharing their excellent ideas that made this year such fruitful and enjoyable.\\
+
+I also want to express my gratitude to my family for their unconditional support, understanding, and encouragement throughout this year. \\
+
+\end{acknowledgements}
+
 \cleardoublepage
@@
 
-\noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak
+\noindent\enquote{\itshape All models are wrong, but some are useful.}\bigbreak
 
-\hfill Dave Barry
+\hfill George E. P. Box
 
@@
 \addchaptertocentry{\abstractname} % Add the abstract to the table of contents
-The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
+The National Dietary and Nutrition Survey (NDNS) database of detailed four-day food diaries was used to \dots
 \end{abstract}
-
-%----------------------------------------------------------------------------------------
-%	ACKNOWLEDGEMENTS
-%----------------------------------------------------------------------------------------
-
-\begin{acknowledgements}
-\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
-The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
-\end{acknowledgements}
 

### 2018-07-09 phrases.Rmd
mixed results added
2 categories done

@@
 
-# Expressions
+  heuristics [hjuə'ristiks]
+
+```
+====== 辞典翻译: heuristics ======
+  n. 启发法；启发式教学法
+============ 网络释义 ============
+--------- heuristics ---------
+  试探法
+  启发
+  启发式
+ representativeness heuristics
+  代表性启发式
+  代表性启发法
+---- Advanced Heuristics -----
+  高级启发式
+  先进的启发式辨认引擎
+```
+
+-  posit ['pɔzit]
+
+```
+======== 辞典翻译: posit =========
+  n. 假设；设想
+  vt. 安置；假定
+============ 网络释义 ============
+----------- posit ------------
+  断定
+  位置
+  假定
+------- Posit Science --------
+  研究对波赛特科学
+-------- posit clause --------
+  断定子句
+```
+
+- circumvent
+
+```
+====== 辞典翻译: circumvent ======
+  v. 包围；智取；绕行，规避
+============ 网络释义 ============
+--------- circumvent ---------
+  避免
+  欺诈
+  用计谋战胜
+------ Circumvent glass ------
+  防御玻璃墙
+----- around circumvent ------
+  绕圈子
+```
+
+-  manifest ['mænifest]
+
+```
+======= 辞典翻译: manifest =======
+  n. 载货单，货单；旅客名单
+  vt. 证明，表明；显示
+  adj. 显然的，明显的；明白的
+  vi. 显示，出现
+============ 网络释义 ============
+---------- MANIFEST ----------
+  舱单
+  清单
+  显示
+------ Manifest Destiny ------
+  昭昭天命
+  昭昭天命
+  天定命运
+------- cargo manifest -------
+  载货清单
+  货物舱单
+  货物清单
+```
 
@@
 - Data can be used from individuals who provide responses to only some questions at a particular time and from those
+
+## bray2015eliminating
+
+(Eliminating bias in classify-analyze approaches for latent class analysis)
+
+- The latent class model, which posits a mutually exclusive and exhaustive underlying set of latent classes (i.e. subgroups) inferred from multiple categorical observed variables.
+
+- LCA has been proven to be a useful tool for identifying qualitatively different population subgroups in a variety of disciplines.
+
+- Classify-analyze (Clogg, 1995) is a common technique used to circumvent the challenge of not having an LCA model-based solution.
+This technique first classifying individuals into latent classes, and then performing a subsequent analysis treating latent class membership as known (i.e., as manifest categorical variable) in a larger model of interest.
+
+- Fundamentally, LCA is a probability-based approach that does not require assignment of individuals to latent classes; this is one of its greatest strengths....

### 2018-07-09 paper/Appendices/Appendix0_10.Rmd
structure and R codes added

---
title: "Appendix0_10"
output: 
  pdf_document:
    keep_tex: true
    highlight: kate
---

```{r eval=FALSE}
# NDNS analysis, data management ------------------------------------------

# Change the data path accordingly ----------------------------------------
setwd("/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/") # on Ubuntu
library(epiDisplay)
library(plyr)
library(tidyverse)

# Read the data into memory -----------------------------------------------
library(haven)
data <- read_dta("ndns_rp_yr1-4a_foodleveldietarydata_uk.dta")
data56 <- read_dta("ndns_rp_yr5-6a_foodleveldietarydata.dta")
data78 <- read_dta("ndns_rp_yr7-8a_foodleveldietarydata.dta")
names(data)
names(data56)
names(data78)
names(data)[names(data) == "seriali"] <- "id"
names(data56)[names(data56) == "seriali"] <- "id"
names(data78)[names(data78) == "seriali"] <- "id"

# Extract the data we needed ----------------------------------------------
df14d <- data[, c(113, 1, 2, 3, 5, 6, 7, 8, 9, 21, 24, 55, 57, 58, 
    59, 60, 61, 62, 63, 64)]
var <- names(df14d)
df56d <- data56 %>% select(var)
df78d <- data78 %>% select(var)
dfs1 <- rbind(df14d, df56d, df78d)
dfs2 <- dfs1[dfs1$Age >= 19, ]
rm(data, data56, data78)
dfs2

# Calculate the time (minute and hour) when they eat ----------------------

dfs2$MealTime_chr <- as.character(dfs2$MealTime)
dfs2$MealTime_hm <- unlist(strsplit(dfs2$MealTime_chr, " "))[c(FALSE, 
    TRUE)]
dfs2$MealHourN <- as.numeric(unlist(strsplit(dfs2$MealTime_hm, ":"))[c(TRUE, 
    FALSE, FALSE)])
dfs2$MealMinN <- as.numeric(unlist(strsplit(dfs2$MealTime_hm, ":"))[c(FALSE, 
    TRUE, FALSE)])
dfs2$MealMinN0 <- (60 * dfs2$MealHourN) + dfs2$MealMinN
dfs3 <- dfs2[order(dfs2$id, dfs2$DayNo, dfs2$MealMinN0), ]
length(unique(dfs3$id))  ## number of participants = 6155

# Create a subset data with only the first observation of each
# participant --------
NDNS <- dfs3[!duplicated(dfs3$id), ]
with(NDNS, tab1(SurveyYear, graph = FALSE, decimal = 2))

# #SurveyYear :
            # Frequency Percent Cum. percent
# NDNS Year 1       801   13.01        13.01
# NDNS Year 2       812   13.19        26.21
# NDNS Year 3       782   12.71        38.91
# NDNS Year 4      1055   17.14        56.05
# NDNS Year 5       625   10.15        66.21
# NDNS Year 6       663   10.77        76.98
# NDNS Year 7       703   11.42        88.40
# NDNS Year 8       714   11.60       100.00
  # Total          6155  100.00       100.00

# create a variable combine id and day No ---------------------------------
dfs3 <- dfs3 %>%
mutate(id_dy = paste(id, DayNo, sep = "D"))

# For each subject, the total energy/carbohydrate intake for each eating 
# time can be calculated --------
old <- Sys.time()
Energy <- ddply(dfs3, .(id_dy, id, SurveyYear, DayNo, Age, Sex, 
                        DiaryDaysCompleted, MealHourN, DayofWeek), 
                summarise, 
                Tot_Energ = sum(EnergykJ), 
                Tot_Carb = sum(Carbohydrateg), 
                Tot_Sugar = sum(Totalsugarsg), 
                Tot_Starch = sum(Starchg))
new <- Sys.time() - old
print(new)
# Time difference of 3.876385 mins

rm(df14d, df56d, df78d, dfs2)

# Calculate the energy from total carbohydrates ---------------------------
Energy <- Energy %>% 
  mutate(KJcarbo = Tot_Carb * 16) %>% 
  mutate(CarKJpercentage = KJcarbo/Tot_Energ) %>% 
  mutate(Carbo = cut(CarKJpercentage, breaks = c(0, 0.26, 0.75, 2), 
        right = FALSE)) %>% mutate(Carbo2 = cut(CarKJpercentage, breaks = c(0, 
    0.26, 2), right = FALSE))
Energy0 <- Energy[!(Energy$Tot_Energ == 0), ]  
          # some food consumption does not contain any carbohydrates
Energy0$Carbo <- factor(Energy0$Carbo, labels = c("Low_carb", "Med_carb", 
    "High_carb"))
Energy0$Carbo2 <- factor(Energy0$Carbo2, labels = c("Low_carb", "Med_or_high_carb"))

# Generate data sets for each day ----------------------------------------------------------
dta_day1 <- Energy0 %>% 
  filter(DayNo == 1) %>% 
  select(c("id", "Age", 
    "Sex", "DayofWeek", "MealHourN", "Carbo", "Carbo2")) %>% 
  mutate(DayofWeek = factor(DayofWeek, 
    levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", 
        "Saturday", "Sunday")))

dta_day2 <- Energy0 %>% 
  filter(DayNo == 2) %>% 
  select(c("id", "Age", 
    "Sex", "DayofWeek", "MealHourN", "Carbo", "Carbo2")) %>% 
  mutate(DayofWeek = factor(DayofWeek, 
    levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", 
        "Saturday", "Sunday")))

dta_day3 <- Energy0 %>% 
  filter(DayNo == 3) %>% 
  select(c("id", "Age", 
    "Sex", "DayofWeek", "MealHourN", "Carbo", "Carbo2")) %>% 
  mutate(DayofWeek = factor(DayofWeek, 
    levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", 
        "Saturday", "Sunday")))

dta_day4 <- Energy0 %>% 
  filter(DayNo == 4) %>% 
  select(c("id", "Age", 
    "Sex", "DayofWeek", "MealHourN", "Carbo", "Carbo2")) %>% 
  mutate(DayofWeek = factor(DayofWeek, 
    levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", 
        "Saturday", "Sunday")))
vecid1 <- unique(dta_day1$id) # n = 6153
vecid2 <- unique(dta_day2$id) # n = 6153
vecid3 <- unique(dta_day3$id) # n = 6151
vecid4 <- unique(dta_day4$id) # n = 6026

Noday1 <- setdiff(vecid, vecid1)  # two subjects did not have day 1 data
Noday2 <- setdiff(vecid, vecid2)  # two subjects did not have day 2 data
Noday3 <- setdiff(vecid, vecid3)  # four subjects did not have day 3 data
Noday4 <- setdiff(vecid, vecid4)  # 129 subjects did not have day 4 data

# Transform the data shape from long to wide ---------------------------------
dta_d1_wide <- dta_day1[, -7] %>% 
  spread(key = MealHourN, value = Carbo)
names(dta_d1_wide)[5:28] <- paste(rep("H", 24), 0:23, sep = "")

dta_d2_wide <- dta_day2[, -7] %>% 
  spread(key = MealHourN, value = Carbo)
names(dta_d2_wide)[5:28] <- paste(rep("H", 24), 0:23, sep = "")

dta_d3_wide <- dta_day3[, -7] %>% 
  spread(key = MealHourN, value = Carbo)
names(dta_d3_wide)[5:28] <- paste(rep("H", 24), 0:23, sep = "")

dta_d4_wide <- dta_day4[, -7] %>% 
  spread(key = MealHourN, value = Carbo)
names(dta_d4_wide)[5:28] <- paste(rep("H", 24), 0:23, sep = "")

# recode NA to not eating -------------------------------------------------
for (i in 5:ncol(dta_d1_wide)) 
  if (is.factor(dta_d1_wide[, i])) levels(dta_d1_wide[, 
    i]) <- c(levels(dta_d1_wide[, i]), "Not_eating")

dta_d1_wide[is.na(dta_d1_wide)] <- "Not_eating"

for (i in 5:ncol(dta_d2_wide)) 
  if (is.factor(dta_d2_wide[, i])) levels(dta_d2_wide[, 
    i]) <- c(levels(dta_d2_wide[, i]), "Not_eating")

dta_d2_wide[is.na(dta_d2_wide)] <- "Not_eating"

for (i in 5:ncol(dta_d3_wide)) 
  if (is.factor(dta_d3_wide[, i])) levels(dta_d3_wide[, 
    i]) <- c(levels(dta_d3_wide[, i]), "Not_eating")

dta_d3_wide[is.na(dta_d3_wide)] <- "Not_eating"

for (i in 5:ncol(dta_d4_wide)) 
  if (is.factor(dta_d4_wide[, i])) levels(dta_d4_wide[, 
    i]) <- c(levels(dta_d4_wide[, i]), "Not_eating")

dta_d4_wide[is.na(dta_d4_wide)] <- "Not_eating"
```

### 2018-07-09 paper/Appendices/Appendix0_10.tex
structure and R codes added

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Appendix0\_10},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{255,255,255}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.67,0.33,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.57,0.30,0.62}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.24,0.68,0.91}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{1.00,0.33,0.00}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{1.00,0.33,0.00}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.54,0.53,0.53}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.38,0.47,0.50}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.79,0.38,0.79}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.00,0.58,1.00}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.43,0.16}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.39,0.29,0.61}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.39,0.29,0.61}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.58,1.00}{\textbf{#1}}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.00,0.43,0.16}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{\textbf{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{\underline{#1}}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{#1}}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{Appendix0\_10}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

\begin{document}
\maketitle

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# NDNS analysis, data management ------------------------------------------}

\CommentTok{# Change the data path accordingly ----------------------------------------}
\KeywordTok{setwd}\NormalTok{(}\StringTok{"/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }\CommentTok{# on Ubuntu}
\KeywordTok{library}\NormalTok{(epiDisplay)}
\KeywordTok{library}\NormalTok{(plyr)}
\KeywordTok{library}\NormalTok{(tidyverse)}

\CommentTok{# Read the data into memory -----------------------------------------------}
\KeywordTok{library}\NormalTok{(haven)}
\NormalTok{data <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr1-4a_foodleveldietarydata_uk.dta"}\NormalTok{)}
\NormalTok{data56 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr5-6a_foodleveldietarydata.dta"}\NormalTok{)}
\NormalTok{data78 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr7-8a_foodleveldietarydata.dta"}\NormalTok{)}
\KeywordTok{names}\NormalTok{(data)}
\KeywordTok{names}\NormalTok{(data56)}
\KeywordTok{names}\NormalTok{(data78)}
\KeywordTok{names}\NormalTok{(data)[}\KeywordTok{names}\NormalTok{(data) }\OperatorTok{==}\StringTok{ "seriali"}\NormalTok{] <-}\StringTok{ "id"}
\KeywordTok{names}\NormalTok{(data56)[}\KeywordTok{names}\NormalTok{(data56) }\OperatorTok{==}\StringTok{ "seriali"}\NormalTok{] <-}\StringTok{ "id"}
\KeywordTok{names}\NormalTok{(data78)[}\KeywordTok{names}\NormalTok{(data78) }\OperatorTok{==}\StringTok{ "seriali"}\NormalTok{] <-}\StringTok{ "id"}

\CommentTok{# Extract the data we needed ----------------------------------------------}
\NormalTok{df14d <-}\StringTok{ }\NormalTok{data[, }\KeywordTok{c}\NormalTok{(}\DecValTok{113}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{, }\DecValTok{3}\NormalTok{, }\DecValTok{5}\NormalTok{, }\DecValTok{6}\NormalTok{, }\DecValTok{7}\NormalTok{, }\DecValTok{8}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{21}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{55}\NormalTok{, }\DecValTok{57}\NormalTok{, }\DecValTok{58}\NormalTok{, }
    \DecValTok{59}\NormalTok{, }\DecValTok{60}\NormalTok{, }\DecValTok{61}\NormalTok{, }\DecValTok{62}\NormalTok{, }\DecValTok{63}\NormalTok{, }\DecValTok{64}\NormalTok{)]}
\NormalTok{var <-}\StringTok{ }\KeywordTok{names}\NormalTok{(df14d)}
\NormalTok{df56d <-}\StringTok{ }\NormalTok{data56 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(var)}
\NormalTok{df78d <-}\StringTok{ }\NormalTok{data78 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(var)}
\NormalTok{dfs1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(df14d, df56d, df78d)}
\NormalTok{dfs2 <-}\StringTok{ }\NormalTok{dfs1[dfs1}\OperatorTok{$}\NormalTok{Age }\OperatorTok{>=}\StringTok{ }\DecValTok{19}\NormalTok{, ]}
\KeywordTok{rm}\NormalTok{(data, data56, data78)}
\NormalTok{dfs2}

\CommentTok{# Calculate the time (minute and hour) when they eat ----------------------}

\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_chr <-}\StringTok{ }\KeywordTok{as.character}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime)}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_hm <-}\StringTok{ }\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_chr, }\StringTok{" "}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }
    \OtherTok{TRUE}\NormalTok{)]}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm, }\StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{TRUE}\NormalTok{, }
    \OtherTok{FALSE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm, }\StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }
    \OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN0 <-}\StringTok{ }\NormalTok{(}\DecValTok{60} \OperatorTok{*}\StringTok{ }\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN) }\OperatorTok{+}\StringTok{ }\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN}
\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs2[}\KeywordTok{order}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{id, dfs2}\OperatorTok{$}\NormalTok{DayNo, dfs2}\OperatorTok{$}\NormalTok{MealMinN0), ]}
\KeywordTok{length}\NormalTok{(}\KeywordTok{unique}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id))  ## number of participants = 6155}

\CommentTok{# Create a subset data with only the first observation of each}
\CommentTok{# participant --------}
\NormalTok{NDNS <-}\StringTok{ }\NormalTok{dfs3[}\OperatorTok{!}\KeywordTok{duplicated}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id), ]}
\KeywordTok{with}\NormalTok{(NDNS, }\KeywordTok{tab1}\NormalTok{(SurveyYear, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{decimal =} \DecValTok{2}\NormalTok{))}

\CommentTok{# #SurveyYear :}
            \CommentTok{# Frequency Percent Cum. percent}
\CommentTok{# NDNS Year 1       801   13.01        13.01}
\CommentTok{# NDNS Year 2       812   13.19        26.21}
\CommentTok{# NDNS Year 3       782   12.71        38.91}
\CommentTok{# NDNS Year 4      1055   17.14        56.05}
\CommentTok{# NDNS Year 5       625   10.15        66.21}
\CommentTok{# NDNS Year 6       663   10.77        76.98}
\CommentTok{# NDNS Year 7       703   11.42        88.40}
\CommentTok{# NDNS Year 8       714   11.60       100.00}
  \CommentTok{# Total          6155  100.00       100.00}

\CommentTok{# create a variable combine id and day No ---------------------------------}
\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs3 }\OperatorTok{%>%}
\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{id_dy =} \KeywordTok{paste}\NormalTok{(id, DayNo, }\DataTypeTok{sep =} \StringTok{"D"}\NormalTok{))}

\CommentTok{# For each subject, the total energy/carbohydrate intake for each eating }
\CommentTok{# time can be calculated --------}
\NormalTok{old <-}\StringTok{ }\KeywordTok{Sys.time}\NormalTok{()}
\NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(dfs3, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
\NormalTok{                        DiaryDaysCompleted, MealHourN, DayofWeek), }
\NormalTok{                summarise, }
                \DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(EnergykJ), }
                \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Carbohydrateg), }
                \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Totalsugarsg), }
                \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Starchg))}
\NormalTok{new <-}\StringTok{ }\KeywordTok{Sys.time}\NormalTok{() }\OperatorTok{-}\StringTok{ }\NormalTok{old}
\KeywordTok{print}\NormalTok{(new)}
\CommentTok{# Time difference of 3.876385 mins}

\KeywordTok{rm}\NormalTok{(df14d, df56d, df78d, dfs2)}

\CommentTok{# Calculate the energy from total carbohydrates ---------------------------}
\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{KJcarbo =}\NormalTok{ Tot_Carb }\OperatorTok{*}\StringTok{ }\DecValTok{16}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CarKJpercentage =}\NormalTok{ KJcarbo}\OperatorTok{/}\NormalTok{Tot_Energ) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.26}\NormalTok{, }\FloatTok{0.75}\NormalTok{, }\DecValTok{2}\NormalTok{), }
        \DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo2 =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }
    \FloatTok{0.26}\NormalTok{, }\DecValTok{2}\NormalTok{), }\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
\NormalTok{Energy0 <-}\StringTok{ }\NormalTok{Energy[}\OperatorTok{!}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{Tot_Energ }\OperatorTok{==}\StringTok{ }\DecValTok{0}\NormalTok{), ]  }
          \CommentTok{# some food consumption does not contain any carbohydrates}
\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Low_carb"}\NormalTok{, }\StringTok{"Med_carb"}\NormalTok{, }
    \StringTok{"High_carb"}\NormalTok{))}
\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo2 <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo2, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Low_carb"}\NormalTok{, }\StringTok{"Med_or_high_carb"}\NormalTok{))}

\CommentTok{# Generate data sets for each day ----------------------------------------------------------}
\NormalTok{dta_day1 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day2 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{2}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day3 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day4 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
\NormalTok{vecid1 <-}\StringTok{ }\KeywordTok{unique}\NormalTok{(dta_day1}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
\NormalTok{vecid2 <-}\StringTok{ }\KeywordTok{unique}\NormalTok{(dta_day2}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
\NormalTok{vecid3 <-}\StringTok{ }\KeywordTok{unique}\NormalTok{(dta_day3}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6151}
\NormalTok{vecid4 <-}\StringTok{ }\KeywordTok{unique}\NormalTok{(dta_day4}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6026}

\NormalTok{Noday1 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid1)  }\CommentTok{# two subjects did not have day 1 data}
\NormalTok{Noday2 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid2)  }\CommentTok{# two subjects did not have day 2 data}
\NormalTok{Noday3 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid3)  }\CommentTok{# four subjects did not have day 3 data}
\NormalTok{Noday4 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid4)  }\CommentTok{# 129 subjects did not have day 4 data}

\CommentTok{# Transform the data shape from long to wide ---------------------------------}
\NormalTok{dta_d1_wide <-}\StringTok{ }\NormalTok{dta_day1[, }\OperatorTok{-}\DecValTok{7}\NormalTok{] }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ MealHourN, }\DataTypeTok{value =}\NormalTok{ Carbo)}
\KeywordTok{names}\NormalTok{(dta_d1_wide)[}\DecValTok{5}\OperatorTok{:}\DecValTok{28}\NormalTok{] <-}\StringTok{ }\KeywordTok{paste}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"H"}\NormalTok{, }\DecValTok{24}\NormalTok{), }\DecValTok{0}\OperatorTok{:}\DecValTok{23}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{)}

\NormalTok{dta_d2_wide <-}\StringTok{ }\NormalTok{dta_day2[, }\OperatorTok{-}\DecValTok{7}\NormalTok{] }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ MealHourN, }\DataTypeTok{value =}\NormalTok{ Carbo)}
\KeywordTok{names}\NormalTok{(dta_d2_wide)[}\DecValTok{5}\OperatorTok{:}\DecValTok{28}\NormalTok{] <-}\StringTok{ }\KeywordTok{paste}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"H"}\NormalTok{, }\DecValTok{24}\NormalTok{), }\DecValTok{0}\OperatorTok{:}\DecValTok{23}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{)}

\NormalTok{dta_d3_wide <-}\StringTok{ }\NormalTok{dta_day3[, }\OperatorTok{-}\DecValTok{7}\NormalTok{] }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ MealHourN, }\DataTypeTok{value =}\NormalTok{ Carbo)}
\KeywordTok{names}\NormalTok{(dta_d3_wide)[}\DecValTok{5}\OperatorTok{:}\DecValTok{28}\NormalTok{] <-}\StringTok{ }\KeywordTok{paste}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"H"}\NormalTok{, }\DecValTok{24}\NormalTok{), }\DecValTok{0}\OperatorTok{:}\DecValTok{23}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{)}

\NormalTok{dta_d4_wide <-}\StringTok{ }\NormalTok{dta_day4[, }\OperatorTok{-}\DecValTok{7}\NormalTok{] }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ MealHourN, }\DataTypeTok{value =}\NormalTok{ Carbo)}
\KeywordTok{names}\NormalTok{(dta_d4_wide)[}\DecValTok{5}\OperatorTok{:}\DecValTok{28}\NormalTok{] <-}\StringTok{ }\KeywordTok{paste}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"H"}\NormalTok{, }\DecValTok{24}\NormalTok{), }\DecValTok{0}\OperatorTok{:}\DecValTok{23}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{)}

\CommentTok{# recode NA to not eating -------------------------------------------------}
\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{5}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d1_wide)) }
  \ControlFlowTok{if}\NormalTok{ (}\KeywordTok{is.factor}\NormalTok{(dta_d1_wide[, i])) }\KeywordTok{levels}\NormalTok{(dta_d1_wide[, }
\NormalTok{    i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(dta_d1_wide[, i]), }\StringTok{"Not_eating"}\NormalTok{)}

\NormalTok{dta_d1_wide[}\KeywordTok{is.na}\NormalTok{(dta_d1_wide)] <-}\StringTok{ "Not_eating"}

\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{5}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d2_wide)) }
  \ControlFlowTok{if}\NormalTok{ (}\KeywordTok{is.factor}\NormalTok{(dta_d2_wide[, i])) }\KeywordTok{levels}\NormalTok{(dta_d2_wide[, }
\NormalTok{    i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(dta_d2_wide[, i]), }\StringTok{"Not_eating"}\NormalTok{)}

\NormalTok{dta_d2_wide[}\KeywordTok{is.na}\NormalTok{(dta_d2_wide)] <-}\StringTok{ "Not_eating"}

\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{5}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d3_wide)) }
  \ControlFlowTok{if}\NormalTok{ (}\KeywordTok{is.factor}\NormalTok{(dta_d3_wide[, i])) }\KeywordTok{levels}\NormalTok{(dta_d3_wide[, }
\NormalTok{    i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(dta_d3_wide[, i]), }\StringTok{"Not_eating"}\NormalTok{)}

\NormalTok{dta_d3_wide[}\KeywordTok{is.na}\NormalTok{(dta_d3_wide)] <-}\StringTok{ "Not_eating"}

\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{5}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d4_wide)) }
  \ControlFlowTok{if}\NormalTok{ (}\KeywordTok{is.factor}\NormalTok{(dta_d4_wide[, i])) }\KeywordTok{levels}\NormalTok{(dta_d4_wide[, }
\NormalTok{    i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(dta_d4_wide[, i]), }\StringTok{"Not_eating"}\NormalTok{)}

\NormalTok{dta_d4_wide[}\KeywordTok{is.na}\NormalTok{(dta_d4_wide)] <-}\StringTok{ "Not_eating"}
\end{Highlighting}
\end{Shaded}

\end{document}

### 2018-07-09 paper/Appendices/AppendixA.tex
structure and R codes added

--- 2018-07-09 paper/Appendices/Appendix0_10.tex
@@
-\documentclass[]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\usepackage[margin=1in]{geometry}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
-            pdftitle={Appendix0\_10},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{255,255,255}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.67,0.33,0.00}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.57,0.30,0.62}{#1}}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.24,0.68,0.91}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{1.00,0.33,0.00}{#1}}
-\newcommand{\ImportTok}[1]{\textcolor[rgb]{1.00,0.33,0.00}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.54,0.53,0.53}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.38,0.47,0.50}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.79,0.38,0.79}{#1}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.00,0.58,1.00}{#1}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.43,0.16}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.39,0.29,0.61}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{\textbf{#1}}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{#1}}
-\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.39,0.29,0.61}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.58,1.00}{\textbf{#1}}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.00,0.43,0.16}{#1}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
-\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{\textbf{#1}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{\underline{#1}}}
-\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{#1}}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
+% Appendix A
 
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
+\chapter{R code for importing and manipulating the data} % Main appendix title
 
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\newcommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
-
-  \title{Appendix0\_10}
-    \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-    \author{}
-    \preauthor{}\postauthor{}
-    \date{}
-    \predate{}\postdate{}
-
-\begin{document}
-\maketitle
+\label{AppendixA} % For referencing this appendix elsewhere, use \ref{AppendixA}
 
@@
 \CommentTok{# Change the data path accordingly ----------------------------------------}
-\KeywordTok{setwd}\NormalTok{(}\StringTok{"/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }\CommentTok{# on Ubuntu}
+\KeywordTok{setwd}\NormalTok{(}\StringTok{"/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }\CommentTok{# in Ubuntu}
 \KeywordTok{library}\NormalTok{(epiDisplay)}
@@
 
-\end{document}
+%\section{How do I change the colors of links?}
+%
+%The color of links can be changed to your liking using:
+%
+%{\small\verb!\hypersetup{urlcolor=red}!}, or
+%
+%{\small\verb!\hypersetup{citecolor=green}!}, or
+%
+%{\small\verb!\hypersetup{allcolor=blue}!}.
+%
+%\noindent If you want to completely hide the links, you can use:
+%
+%{\small\verb!\hypersetup{allcolors=.}!}, or even better:
+%
+%{\small\verb!\hypersetup{hidelinks}!}.
+%
+%\noindent If you want to have obvious links in the PDF but not %the printed text, use:
+%
+%{\small\verb!\hypersetup{colorlinks=false}!}.

### 2018-07-09 paper/Chapters/Chapter2.tex
structure and R codes added

% Chapter Template

\chapter{Methods} % Main chapter title

\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Main Section 1}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam ultricies lacinia euismod. Nam tempus risus in dolor rhoncus in interdum enim tincidunt. Donec vel nunc neque. In condimentum ullamcorper quam non consequat. Fusce sagittis tempor feugiat. Fusce magna erat, molestie eu convallis ut, tempus sed arcu. Quisque molestie, ante a tincidunt ullamcorper, sapien enim dignissim lacus, in semper nibh erat lobortis purus. Integer dapibus ligula ac risus convallis pellentesque.

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Subsection 1}

Nunc posuere quam at lectus tristique eu ultrices augue venenatis. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam erat volutpat. Vivamus sodales tortor eget quam adipiscing in vulputate ante ullamcorper. Sed eros ante, lacinia et sollicitudin et, aliquam sit amet augue. In hac habitasse platea dictumst.

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\subsection{Subsection 2}
Morbi rutrum odio eget arcu adipiscing sodales. Aenean et purus a est pulvinar pellentesque. Cras in elit neque, quis varius elit. Phasellus fringilla, nibh eu tempus venenatis, dolor elit posuere quam, quis adipiscing urna leo nec orci. Sed nec nulla auctor odio aliquet consequat. Ut nec nulla in ante ullamcorper aliquam at sed dolor. Phasellus fermentum magna in augue gravida cursus. Cras sed pretium lorem. Pellentesque eget ornare odio. Proin accumsan, massa viverra cursus pharetra, ipsum nisi lobortis velit, a malesuada dolor lorem eu neque.

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Main Section 2}

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.

### 2018-07-09 paper/main.tex
update of the main acknowledgement
structure and R codes added

@@
 \documentclass[
-11pt, % The default document font size, options: 10pt, 11pt, 12pt
+12pt, % The default document font size, options: 10pt, 11pt, 12pt
 %oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
@@
 	paper=a4paper, % Change to letterpaper for US letter
-	inner=2.5cm, % Inner margin
-	outer=3.8cm, % Outer margin
+	inner=2.0cm, % Inner margin
+	outer=2.8cm, % Outer margin
 	bindingoffset=.5cm, % Binding offset
@@
 }
+
+%----------------------------------------------------------------------------------------
+% For pringting the R/SAS/STATA codes
+%----------------------------------------------------------------------------------------
+
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={Appendix0\_10},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{255,255,255}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.67,0.33,0.00}{#1}}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.57,0.30,0.62}{#1}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.24,0.68,0.91}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{1.00,0.33,0.00}{#1}}
+\newcommand{\ImportTok}[1]{\textcolor[rgb]{1.00,0.33,0.00}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.54,0.53,0.53}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.38,0.47,0.50}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.79,0.38,0.79}{#1}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.00,0.58,1.00}{#1}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.43,0.16}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.39,0.29,0.61}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{\textbf{#1}}}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{#1}}
+\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.39,0.29,0.61}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.58,1.00}{\textbf{#1}}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.00,0.43,0.16}{#1}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
+\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{\textbf{#1}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{\underline{#1}}}
+\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{#1}}
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
@@
 
-\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere\\
-\textbf{WSF} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or\\
-
+\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
+\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
+\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
+\textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
+\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
+\textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
+\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
+\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
+\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
+\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
+\textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
+\textbf{NDNS} & the \textbf{N}ational \textbf{D}ietary and \textbf{N}utrition \textbf{S}urvey \\
+\textbf{OR} & \textbf{O}dds \textbf{R}atio \\
 \end{abbreviations}
@@
 
-\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table
+%\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table
 
@@
 
-Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
+%Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
 %Constant Name & $Symbol$ & $Constant Value$ with units\\
 %testovaci komentar
-\end{constants}
+%\end{constants}
 
@@
 
-\begin{symbols}{lll} % Include a list of Symbols (a three column table)
-
-$a$ & distance & \si{\meter} \\
-$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
-%Symbol & Name & Unit \\
-
-\addlinespace % Gap to separate the Roman symbols from the Greek
-
-$\omega$ & angular frequency & \si{\radian} \\
-
-\end{symbols}
+%\begin{symbols}{lll} % Include a list of Symbols (a three %column table)
+%
+%$a$ & distance & \si{\meter} \\
+%$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
+%%Symbol & Name & Unit \\
+%
+%\addlinespace % Gap to separate the Roman symbols from the Greek
+%
+%$\omega$ & angular frequency & \si{\radian} \\
+%
+%\end{symbols}
 
@@
 
-\dedicatory{For/Dedicated to/To my\ldots}
+%\dedicatory{For/Dedicated to/To my\ldots}
 
@@
 \include{Chapters/Chapter1}
-%\include{Chapters/Chapter2}
+\include{Chapters/Chapter2}
 %\include{Chapters/Chapter3}

### 2018-07-09 phrases.Rmd
structure and R codes added

@@
 
+-  undue [,ʌn'dju:]
+
+```
+======== 辞典翻译: undue =========
+  adj. 过度的，过分的；不适当的；未到期的
+============ 网络释义 ============
+----------- undue ------------
+  不适当的
+  过度的
+  过分
+--------- undue wear ---------
+  过度的磨损
+  不正常磨损
+  过度磨损
+------- undue pressure -------
+  不必要的压力
+  不适当的压力
+```
+
 # Sentences
@@
 - Fundamentally, LCA is a probability-based approach that does not require assignment of individuals to latent classes; this is one of its greatest strengths....
+
+- The classification of individuals to latent classes is a form of imputation; because an individual's true class membership cannot be known, the latent class variable is 100% missing.
+
+- Once the parameters of a latent class model have been estimated, posterior probabilities of membership in each latent class can be obtained for each individual using Bayes' theorem.
+
+- Two classify-analyze approaches for LCA are commonly used in practice.
+Both approaches reply on posterior probablities to classify individuals.
+We refer to the first approach as the *maximum-probability assignment* rule.
+...
+The second approach is *multiple pseudo-class draws*.
+This approach is similar to maximum-proability  assignment but accounts for uncertainty in class assignment.
+Using this method, individuals are randomly classified into latent class multiple times based on their distributions of posterior probabilities.
+Often, 20 pseudo-class draws are used; that is, individuals are classfied 20 times.
+The subsequent analysis is performed once for each draw (i.e., 20 times) and results are combined across draws using rules derived for multiple imputation for missing data.
+
+- We showed that maximum-probability assignment is less biased than multiple pseudo-class draws regardless of whether inclusive or non-inclusive LCA is used.
+
+- A series of steps when using classify-analyze approaches for LCA: 
+    1. determine the optimal number of latent classes by fitting and comparing models without covariates included in the model (i.e., use non-inclusive LCA for model selection); 
+    2. re-fit the latent class model with the other variables of interest included as covariates to produce posterior probabilities; 
+    3. use either maximum-probability assignment or multiple pseudo-class draw, as the analyst prefers, to classify individuals; 
+    4. treat class membership as known to perform the desired analysis.
+
+- Simply by including other variables of interest as covariates, inclusive LCA can be conducted with any of these packages.
+
+- Inclusive LCA is analogous to multiple imputation, a model-based procedure that requires assumptions about the missing data mechanism, specifically that data are missing at random (MAR).
+
+- Multiple imputation also typically requires the additional assumption that data are from a multivariate normal distribution.
+
+- Similarly, the inclusive strategy for imputing latent class membership, a variable that is 100% missing, relies on certain assumptions. In the scenarios examined here, we have assumed: 
+    1. independence of the indicators conditional latent class; 
+    2. a linear relation (on the logit scale) between the latent class variable and any other variables of interest (here, distal outcome); 
+    3. independence of the indicators and any other variables of interest conditional on latent class
+
+## Beath2017 - randomLCA: An R Package for Latent Class with Random Effects Analysis
+
+- An advantage of using latent class analysis over other classification methods is that the classification is model based, allowing use of model selection techniques to determine which classfication scheme is most appropriate.
+
+- The assumption of latent class models is conditional or local independence, where the outcomes are independent conditional on the latent class.
+This assumes that subjects within a class are homogeneous.

### 2018-07-09 Rcode/analysis8yrsA.R

@@ -1245,3 +1245,12 @@ save(lc1, lc2, lc3, lc4, lc5, lc6, lc7, lc8, lca_results, file = "day4LCA1_6.Rda
 
 
 # save.image("LCA.Rdata")
+
+
+
+
+# Try randomLCA -----------------------------------------------------------
+# 
+# library(randomLCA)
+# 
+# randomLCA(dta_d1_wide[, 5:28], nclass = 1)

### 2018-07-10 paper/Appendices/AppendixC.tex
introduction example of diary added

% Appendix Template

\chapter{Example of a food diary for one day} % Main appendix title

\label{AppendixC} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}
%\begin{verbatim}

\begin{figure}[H]
%\vspace*{13cm}
\centering
\includegraphics{Figures/Diary1.png}
\decoRule
\caption[One day food diary example 6 am to 2 pm]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, from 6 am to 2 pm.}
\label{fig:diary1}
\end{figure}
%\end{verbatim}

\begin{figure}[H]
%\vspace*{13cm}
\centering
\includegraphics{Figures/Diary2.png}
\decoRule
\caption[One day food diary example 2 pm to 6 am]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, from 2 pm to 6 am.}
\label{fig:diary2}
\end{figure}
%\end{verbatim}

\begin{figure}[H]
%\vspace*{13cm}
\centering
\includegraphics{Figures/Diary3.png}
\decoRule
\caption[Food diary example of home made food recipes]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, home made food recipes.}
\label{fig:diary3}
\end{figure}

### 2018-07-10 paper/Chapters/Chapter3.tex
introduction example of diary added

--- 2018-07-09 paper/Chapters/Chapter2.tex
@@
 
-\chapter{Methods} % Main chapter title
+\chapter{Results} % Main chapter title
 
-\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+\label{Chapter 3} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam ultricies lacinia euismod.
-Nam tempus risus in dolor rhoncus in interdum enim tincidunt.
-Donec vel nunc neque.
-In condimentum ullamcorper quam non consequat.
-Fusce sagittis tempor feugiat.
-Fusce magna erat, molestie eu convallis ut, tempus sed arcu.
-Quisque molestie, ante a tincidunt ullamcorper, sapien enim dignissim lacus, in semper nibh erat lobortis purus.
-Integer dapibus ligula ac risus convallis pellentesque.
-
 %-----------------------------------
@@
 \subsection{Subsection 1}
-
-Nunc posuere quam at lectus tristique eu ultrices augue venenatis.
-Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam erat volutpat.
-Vivamus sodales tortor eget quam adipiscing in vulputate ante ullamcorper.
-Sed eros ante, lacinia et sollicitudin et, aliquam sit amet augue.
-In hac habitasse platea dictumst.
 
@@
 \subsection{Subsection 2}
-Morbi rutrum odio eget arcu adipiscing sodales.
-Aenean et purus a est pulvinar pellentesque.
-Cras in elit neque, quis varius elit.
-Phasellus fringilla, nibh eu tempus venenatis, dolor elit posuere quam, quis adipiscing urna leo nec orci.
-Sed nec nulla auctor odio aliquet consequat.
-Ut nec nulla in ante ullamcorper aliquam at sed dolor.
-Phasellus fermentum magna in augue gravida cursus.
-Cras sed pretium lorem.
-Pellentesque eget ornare odio.
-Proin accumsan, massa viverra cursus pharetra, ipsum nisi lobortis velit, a malesuada dolor lorem eu neque.
 
@@
 \section{Main Section 2}
-
-Sed ullamcorper quam eu nisl interdum at interdum enim egestas.
-Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor.
-Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula.
-Donec eget quam sapien, in viverra eros.
-Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum.
-Vestibulum in orci quis felis tempor lacinia.
-Vivamus ornare ultrices facilisis.
-Ut hendrerit volutpat vulputate.
-Morbi condimentum venenatis augue, id porta ipsum vulputate in.
-Curabitur luctus tempus justo.
-Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl.
-Aliquam dictum sagittis velit sed iaculis.
-Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis.
-Nam elit libero, tincidunt ut aliquam at, molestie in quam.
-Aenean rhoncus vehicula hendrerit.

### 2018-07-11 9thJuly/9thJuly.Rmd
updated results

@@
 
-# Mixed effect LCA with carbohydrates intake groups redefined:
+# Mixed effect LCA with carbohydrates intake groups redefined: (cutoff=25%)
 
@@
 ```
+
+# Mixed effect LCA with carbohydrates intake groups redefined: (cutoff = 25%, 50%, 75%)
+
+1. Not eating; 
+2. Eating low carbohydrate food (energy contribution less than or equal to 25%); 
+3. Eating low-to-medium carbohydrate food (energy contribution between 25% and 50%); 
+3. Eating medium-to-high carbohydrate food (energy contribution between 50% and 75%); 
+4. Eating high carbohydrate food (energy contribution higher or equal to 75%).
+
+## Model comparison and selection
+
+```{r echo=FALSE}
+rm(list=ls(all=TRUE))
+# load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")
+
+library(kableExtra)
+dt <- read.csv("../Tablecsv/ModelsMixed255075.csv", header = T)
+names(dt) <- c("N of classes", "log-likelihood", "G^2",  "AIC", "BIC", "cAIC", "aBIC", "Entropy")
+dt[1,8] <- "---"
+kable(dt, digits = 3, row.names = FALSE, align = "c",
+              format = "html", caption = "Model Comparison. (All data, n = 6155)") %>%
+ kable_styling(font_size = 16, 
+        bootstrap_options = c("striped", "hover", "condensed"),
+        position = "center", full_width = FALSE) %>% 
+  row_spec(c(3,7), bold = T, color = "white", background = "#D7261E") %>% 
+  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
+```
+
+## Visualisation of the 3-class model
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+
+library(ggthemr)
+rm(list=ls(all=TRUE))
+
+dt <- read.csv("../Tablecsv/ndns_param3255075.csv", header = T)
+
+dt_long <- dt[-1,-c(1,2)] %>% 
+  gather(Hour, Prob, -VARIABLE, -RESPCAT) %>% 
+  separate(Hour, into = c("EST" ,"Class"), sep = "T")
+
+dt_long <- dt_long %>% 
+  filter(RESPCAT != 1) %>% 
+  mutate(RESPCAT = as.factor(RESPCAT)) %>% 
+  mutate(Carbo = revalue(RESPCAT, c("2" = "< 25%", "3" = "25% - 50%", "4" = "50% - 75%", "5" = "> 75%"))) %>% 
+  mutate(HourN = as.character(VARIABLE)) %>% 
+  mutate(HourN = factor(HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")))
+
+# ggthemr("pale", layout = "scientific")
+
+ggthemr("fresh", layout = "scientific")
+
+ggplot(dt_long[dt_long$Class == "LC1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 22.57%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  27.85%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 3:  49.6%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
+  ylim(c(0,1))
+
+# 
+# ggplot(dt_long[dt_long$Class == "LC4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+#  geom_point(size = 3) + 
+#   geom_line(size = 1.5) + 
+#   theme(axis.title = element_text(size = 18), 
+#         axis.text = element_text(size = 18), 
+#         axis.line = element_line(colour = "black"), 
+#         panel.border = element_blank(), 
+#         panel.background = element_blank(), 
+#         legend.text = element_text(size = 15), 
+#         legend.title = element_text(size = 15) 
+#         # legend.position = "bottom", 
+#         # legend.direction = "horizontal"
+#         ) + 
+#   labs(title = "Class 4:  23.08%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") + 
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) + 
+#   ylim(c(0,1))
+# 
+# 
+# ggplot(dt_long[dt_long$Class == "LC5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 5:  4.07%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+# 
+# ggplot(dt_long[dt_long$Class == "LC6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+#  geom_point(size = 3) +
+#   geom_line(size = 1.5) +
+#   theme(axis.title = element_text(size = 18),
+#         axis.text = element_text(size = 18),
+#         axis.line = element_line(colour = "black"),
+#         panel.border = element_blank(),
+#         panel.background = element_blank(),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_text(size = 15)
+#         # legend.position = "bottom",
+#         # legend.direction = "horizontal"
+#         ) +
+#   labs(title = "Class 6:  14.10%", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") +
+#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
+#   ylim(c(0,1))
+```
+
+## Visualisation of the classes by Carbohydrate eating types (3 classes)
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+
+ggthemr("pale", layout = "scientific")
+
+ggplot(dt_long[dt_long$Carbo == "< 25%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
+  geom_point(size = 2) + 
+  geom_line(size = 1.2) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Low carbohydarte food consumption (< 25%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
+  scale_color_discrete(labels = c("1", "2", "3")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Carbo == "25% - 50%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
+  geom_point(size = 2) + 
+  geom_line(size = 1.2) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Low-to-Medium carbohydarte food consumption (25% - 50%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
+  scale_color_discrete(labels = c("1", "2", "3")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Carbo == "50% - 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
+  geom_point(size = 2) + 
+  geom_line(size = 1.2) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Medium-to-High carbohydarte food consumption (50% - 75%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
+  scale_color_discrete(labels = c("1", "2", "3")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Carbo == "> 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
+  geom_point(size = 2) + 
+  geom_line(size = 1.2) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "High carbohydarte food consumption (> 75%) probability by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
+  scale_color_discrete(labels = c("1", "2", "3")) + 
+  ylim(c(0,1))
+```
+
+## Visualisation of the 7-class model
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+
+library(ggthemr)
+rm(list=ls(all=TRUE))
+
+# ggthemr("fresh", layout = "scientific")
+
+dt <- read.csv("../Tablecsv/ndns_param7255075.csv", header = T)
+
+dt_long <- dt[-1,-c(1,2)] %>% 
+  gather(Hour, Prob, -VARIABLE, -RESPCAT) %>% 
+  separate(Hour, into = c("EST" ,"Class"), sep = "T")
+
+dt_long <- dt_long %>% 
+  filter(RESPCAT != 1) %>% 
+  mutate(RESPCAT = as.factor(RESPCAT)) %>% 
+  mutate(Carbo = revalue(RESPCAT, c("2" = "< 25%", "3" = "25% - 50%", "4" = "50% - 75%", "5" = "> 75%"))) %>% 
+  mutate(HourN = as.character(VARIABLE)) %>% 
+  mutate(HourN = factor(HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")))
+
+ggthemr("pale", layout = "scientific")
+
+ggplot(dt_long[dt_long$Class == "LC1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 1: 10.64%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+ geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Class 2:  15.01%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 3:  11.56%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 4:  11.31%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 5:  9.3%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 6:  9.41%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Class == "LC7", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+ geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+        ) +
+  labs(title = "Class 7:  32.7%", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
+  ylim(c(0,1))
+```
+
+## Visualisation of the classes by Carbohydrate eating types (7 classes)
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+
+ggthemr("pale", layout = "scientific")
+
+ggplot(dt_long[dt_long$Carbo == "< 25%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
+  geom_point(size = 2) + 
+  geom_line(size = 1.2) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Low carbohydarte food consumption (< 25%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
+  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6", "7")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Carbo == "25% - 50%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
+  geom_point(size = 2) + 
+  geom_line(size = 1.2) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Low-to-Medium carbohydarte food consumption (25% - 50%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
+  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6", "7")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Carbo == "50% - 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
+  geom_point(size = 2) + 
+  geom_line(size = 1.2) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "Medium-to-High carbohydarte food consumption (50% - 75%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
+  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6", "7")) + 
+  ylim(c(0,1))
+
+ggplot(dt_long[dt_long$Carbo == "> 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
+  geom_point(size = 2) + 
+  geom_line(size = 1.2) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+        ) + 
+  labs(title = "High carbohydarte food consumption (> 75%) probability by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
+  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6", "7")) + 
+  ylim(c(0,1))
+```
+
+# Mixed effect LCA with carbohydrates intake groups redefined: (cutoff = 50%)
+
+1. Not eating; 
+2. ~~Eating low carbohydrate food (energy contribution less than or equal to 25%);~~
+3. Eating low-to-medium carbohydrate food (energy contribution between < 50%); 
+3. Eating medium-to-high carbohydrate food (energy contribution between > = 50%); 
+4. ~~Eating high carbohydrate food (energy contribution higher or equal to 75%).~~
+
+## Model comparison and selection
+
+```{r echo=FALSE}
+rm(list=ls(all=TRUE))
+# load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")
+
+library(kableExtra)
+dt <- read.csv("../Tablecsv/ModelsMixed50.csv", header = T)
+names(dt) <- c("N of classes", "log-likelihood", "G^2",  "AIC", "BIC", "cAIC", "aBIC", "Entropy")
+dt[1,8] <- "---"
+kable(dt, digits = 3, row.names = FALSE, align = "c",
+              format = "html", caption = "Model Comparison. (All data, n = 6155)") %>%
+ kable_styling(font_size = 16, 
+        bootstrap_options = c("striped", "hover", "condensed"),
+        position = "center", full_width = FALSE) %>% 
+  row_spec(c(5,7), bold = T, color = "white", background = "#D7261E") %>% 
+  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
+```

### 2018-07-11 Memo_of_meeting.Rmd
foundamentalpart read 30%
updated results

@@
     - What cut-off would be appropriate to say that within that specific hour, the consumption of carbohydrates would be good or bad?
+    - **Just to add that if there is a concern that too few people would have consumed CH for example at night then we can collapse the hours at night into one class as we did with Raoul, say from 11pm till 5am or from 12 till 6am.**
 
@@
     - Still, this could the first step of our analysis. The second step we may think about is the quality (ratio) between different subtypes of carbohydrates within the hour.
+
+----------
+
+**Date and time:** 2018-07-10 14:00 - 15:00
+
+**Attendees:** Professor Luigi Palla, Dr. Suzana Almoosawi, Chaochen Wang
+
+**Notekeeper:** Chaochen Wang
+
+**Main Topic:** Discuss about the preliminary results and what should we do next?
+
+- From what we have seen from the preliminary results, maybe we should change the cut-off values to 25%, 50%, and 75% (i.e.
+four categories), in order to divide the previous 26% to 75% category (medium carbohydrate food/meal).
+
+- After the above step, maybe we can further consider combining the lower two categories (< 25% and 26% to 50%) and the higher two categories (50% to 75% and > 75%).
+
+- One possiblity of next analysis objective could be:  carb-fibre ratio and various variation of this ratio.
+Usually I (Dr.
+Suzana) would calculate how much fibre is provided for every 10g of carbohydrate for each food product.
+For example, a product providing 30g of carb and 15g of fibre would have a carb-fibre ratio of 10:5.
+It may be the case that the same rules applies to eating occasions/meals.
+In the past I (Dr.
+Suzana) usually used to calculate the ratio and then use the actual proportion within the analysis, so a fibre-carb ratio of 2-10 would expressed as 0.2, and 1-10 would be 0.1.
+I wonder if given that the carb value remain always constant at 10g whether we could simply use the value for the fibre 2, 1...etc
+
+- How to use our results from mixed LCA analysis to express the variability or regularity of carbohydrate eating within a person?
+
+(The following idea is from Chaochen Wang, not fully discussed yet.)
+
+- After we can decide the number of classes in the study sample, maybe we can create a variable according to their change of classes during the survey. 
+    - For example, if we decided to use 3 classes or maybe 4 classes. We can use the personal class change as a way to express the regularity. 
+        - In this case, if for four days survey, the subject stayed in the same class, he/she can be considered as a regular eater. 
+        - For the others, if they change class for more than 1 day, he/she can be considered as a irregular eater.
+        - So in the sample we will separate the subjects into regular eaters or not (2 groups)
+    - Another way, probably we can try to define them with less strict rules:
+        - For more than half (2 in 2, 2 in 3, or >=2 in 4) survey days, if the subject managed to stay in the same class, then he/she can be defined as a regular eater.
+        - Otherwise, he/she is defined as irregular eaters. 
+    - The two approaches proposed here, one is more strict than the other is because there may be only small numbers of people actually stayed in the same class for all four survey days.
+Because with the number of latent classes increases, the probability of jumping from one class to the other will increase, in other words, the probability of staying in the same class for four days will become lower and lower.
+
+- Survey weighting variables.    
+    - There are different weighting variables in the data set.

### 2018-07-11 results/results.Rmd
updated results

---
title: "Updated results"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
---

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(epiDisplay)
library(plyr)
library(tidyverse)
library(poLCA)
```

[Link (http://rpubs.com/winterwang/ndnsd1)](http://rpubs.com/winterwang/ndnsd1) to the preliminary results.

# Mixed effect LCA with carbohydrates intake groups redefined: (cutoff = 25%, 50%, 75%)

1. Not eating; 
2. Eating low carbohydrate food (energy contribution less than 25%); 
3. Eating low-to-medium carbohydrate food (energy contribution between 25% and 50%); 
3. Eating medium-to-high carbohydrate food (energy contribution between 50% and 75%); 
4. Eating high carbohydrate food (energy contribution higher or equal to 75%).

## Model comparison and selection

```{r echo=FALSE}
rm(list=ls(all=TRUE))
# load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")

library(kableExtra)
dt <- read.csv("../Tablecsv/ModelsMixed255075.csv", header = T)
names(dt) <- c("N of classes", "log-likelihood", "G^2",  "AIC", "BIC", "cAIC", "aBIC", "Entropy")
dt[1,8] <- "---"
kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Model Comparison. (All data, n = 6155)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(c(3,7), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
```

## Visualisation of the 3-class model

```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}

library(ggthemr)
rm(list=ls(all=TRUE))

dt <- read.csv("../Tablecsv/ndns_param3255075.csv", header = T)

dt_long <- dt[-1,-c(1,2)] %>% 
  gather(Hour, Prob, -VARIABLE, -RESPCAT) %>% 
  separate(Hour, into = c("EST" ,"Class"), sep = "T")

dt_long <- dt_long %>% 
  filter(RESPCAT != 1) %>% 
  mutate(RESPCAT = as.factor(RESPCAT)) %>% 
  mutate(Carbo = revalue(RESPCAT, c("2" = "< 25%", "3" = "25% - 50%", "4" = "50% - 75%", "5" = "> 75%"))) %>% 
  mutate(HourN = as.character(VARIABLE)) %>% 
  mutate(HourN = factor(HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")))

# ggthemr("pale", layout = "scientific")

ggthemr("fresh", layout = "scientific")

ggplot(dt_long[dt_long$Class == "LC1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 22.57%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") + 
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  27.85%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") + 
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 3:  49.6%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") +
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

# 
# ggplot(dt_long[dt_long$Class == "LC4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
#  geom_point(size = 3) + 
#   geom_line(size = 1.5) + 
#   theme(axis.title = element_text(size = 18), 
#         axis.text = element_text(size = 18), 
#         axis.line = element_line(colour = "black"), 
#         panel.border = element_blank(), 
#         panel.background = element_blank(), 
#         legend.text = element_text(size = 15), 
#         legend.title = element_text(size = 15) 
#         # legend.position = "bottom", 
#         # legend.direction = "horizontal"
#         ) + 
#   labs(title = "Class 4:  23.08%", x = "Hour of the day", y = "Probability",
#        color = "Carbohydrates\nContribution") + 
#   scale_color_discrete(labels = c("Low", "Medium", "High")) + 
#   ylim(c(0,1))
# 
# 
# ggplot(dt_long[dt_long$Class == "LC5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
#  geom_point(size = 3) +
#   geom_line(size = 1.5) +
#   theme(axis.title = element_text(size = 18),
#         axis.text = element_text(size = 18),
#         axis.line = element_line(colour = "black"),
#         panel.border = element_blank(),
#         panel.background = element_blank(),
#         legend.text = element_text(size = 15),
#         legend.title = element_text(size = 15)
#         # legend.position = "bottom",
#         # legend.direction = "horizontal"
#         ) +
#   labs(title = "Class 5:  4.07%", x = "Hour of the day", y = "Probability",
#        color = "Carbohydrates\nContribution") +
#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
#   ylim(c(0,1))
# 
# ggplot(dt_long[dt_long$Class == "LC6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
#  geom_point(size = 3) +
#   geom_line(size = 1.5) +
#   theme(axis.title = element_text(size = 18),
#         axis.text = element_text(size = 18),
#         axis.line = element_line(colour = "black"),
#         panel.border = element_blank(),
#         panel.background = element_blank(),
#         legend.text = element_text(size = 15),
#         legend.title = element_text(size = 15)
#         # legend.position = "bottom",
#         # legend.direction = "horizontal"
#         ) +
#   labs(title = "Class 6:  14.10%", x = "Hour of the day", y = "Probability",
#        color = "Carbohydrates\nContribution") +
#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
#   ylim(c(0,1))
```

## Visualisation of the classes by Carbohydrate eating types (3 classes)

```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}

ggthemr("pale", layout = "scientific")

ggplot(dt_long[dt_long$Carbo == "< 25%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Low carbohydarte food consumption (< 25%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Carbo == "25% - 50%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Low-to-Medium carbohydarte food consumption (25% - 50%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Carbo == "50% - 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Medium-to-High carbohydarte food consumption (50% - 75%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Carbo == "> 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "High carbohydarte food consumption (> 75%) probability by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3")) + 
  ylim(c(0,1))
```

## Visualisation of the 7-class model

```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}

library(ggthemr)
rm(list=ls(all=TRUE))

# ggthemr("fresh", layout = "scientific")

dt <- read.csv("../Tablecsv/ndns_param7255075.csv", header = T)

dt_long <- dt[-1,-c(1,2)] %>% 
  gather(Hour, Prob, -VARIABLE, -RESPCAT) %>% 
  separate(Hour, into = c("EST" ,"Class"), sep = "T")

dt_long <- dt_long %>% 
  filter(RESPCAT != 1) %>% 
  mutate(RESPCAT = as.factor(RESPCAT)) %>% 
  mutate(Carbo = revalue(RESPCAT, c("2" = "< 25%", "3" = "25% - 50%", "4" = "50% - 75%", "5" = "> 75%"))) %>% 
  mutate(HourN = as.character(VARIABLE)) %>% 
  mutate(HourN = factor(HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")))

ggthemr("pale", layout = "scientific")

ggplot(dt_long[dt_long$Class == "LC1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 10.64%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") + 
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  15.01%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") + 
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 3:  11.56%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") +
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 4:  11.31%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") +
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 5:  9.3%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") +
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 6:  9.41%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") +
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC7", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 7:  32.7%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") +
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))
```

## Visualisation of the classes by Carbohydrate eating types (7 classes)

```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}

ggthemr("pale", layout = "scientific")

ggplot(dt_long[dt_long$Carbo == "< 25%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Low carbohydarte food consumption (< 25%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6", "7")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Carbo == "25% - 50%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Low-to-Medium carbohydarte food consumption (25% - 50%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6", "7")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Carbo == "50% - 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Medium-to-High carbohydarte food consumption (50% - 75%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6", "7")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Carbo == "> 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "High carbohydarte food consumption (> 75%) probability by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6", "7")) + 
  ylim(c(0,1))
```

# Mixed effect LCA with carbohydrates intake groups redefined: (cutoff = 50%)

1. Not eating; 
2. ~~Eating low carbohydrate food (energy contribution less than or equal to 25%);~~
3. Eating low-to-medium carbohydrate food (energy contribution between < 50%); 
3. Eating medium-to-high carbohydrate food (energy contribution between > = 50%); 
4. ~~Eating high carbohydrate food (energy contribution higher or equal to 75%).~~

## Model comparison and selection

```{r echo=FALSE}
rm(list=ls(all=TRUE))
# load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")

library(kableExtra)
dt <- read.csv("../Tablecsv/ModelsMixed50.csv", header = T)
names(dt) <- c("N of classes", "log-likelihood", "G^2",  "AIC", "BIC", "cAIC", "aBIC", "Entropy")
dt[1,8] <- "---"
kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Model Comparison. (All data, n = 6155)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(c(5,7), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
```

## Visualisation of the 5-class model

```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}

library(ggthemr)
rm(list=ls(all=TRUE))

dt <- read.csv("../Tablecsv/ndns_param5_50.csv", header = T)

dt_long <- dt[-1,-c(1,2)] %>% 
  gather(Hour, Prob, -VARIABLE, -RESPCAT) %>% 
  separate(Hour, into = c("EST" ,"Class"), sep = "T")

dt_long <- dt_long %>% 
  filter(RESPCAT != 1) %>% 
  mutate(RESPCAT = as.factor(RESPCAT)) %>% 
  mutate(Carbo = revalue(RESPCAT, c("2" = "< 50%", "3" = ">= 50%"))) %>% 
  mutate(HourN = as.character(VARIABLE)) %>% 
  mutate(HourN = factor(HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")))

# ggthemr("pale", layout = "scientific")

ggthemr("fresh", layout = "scientific")

ggplot(dt_long[dt_long$Class == "LC1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 32.3%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") + 
  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  20.70%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") + 
  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 3:  2.73%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") +
  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 4:  25.38%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") +
  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 5:  18.87%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrates\nContribution") +
  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
  ylim(c(0,1))
# 
# ggplot(dt_long[dt_long$Class == "LC6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
#  geom_point(size = 3) +
#   geom_line(size = 1.5) +
#   theme(axis.title = element_text(size = 18),
#         axis.text = element_text(size = 18),
#         axis.line = element_line(colour = "black"),
#         panel.border = element_blank(),
#         panel.background = element_blank(),
#         legend.text = element_text(size = 15),
#         legend.title = element_text(size = 15)
#         # legend.position = "bottom",
#         # legend.direction = "horizontal"
#         ) +
#   labs(title = "Class 6:  14.10%", x = "Hour of the day", y = "Probability",
#        color = "Carbohydrates\nContribution") +
#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
#   ylim(c(0,1))
```

## Visualisation of the classes by Carbohydrate eating types (5 classes)

```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}

ggthemr("pale", layout = "scientific")

ggplot(dt_long[dt_long$Carbo == "< 50%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Low carbohydarte food consumption (< 50%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3", "4", "5")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Carbo == ">= 50%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Medium to high carbohydarte food consumption (> 50%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3", "4", "5")) + 
  ylim(c(0,1))

# 
# ggplot(dt_long[dt_long$Carbo == "50% - 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
#   geom_point(size = 2) + 
#   geom_line(size = 1.2) + 
#   theme(axis.title = element_text(size = 18), 
#         axis.text = element_text(size = 18), 
#         axis.line = element_line(colour = "black"), 
#         panel.border = element_blank(), 
#         panel.background = element_blank(), 
#         legend.text = element_text(size = 15), 
#         legend.title = element_text(size = 15) 
#         # legend.position = "bottom", 
#         # legend.direction = "horizontal"
#         ) + 
#   labs(title = "Medium-to-High carbohydarte food consumption (50% - 75%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
#   scale_color_discrete(labels = c("1", "2", "3", "4", "5")) + 
#   ylim(c(0,1))

# ggplot(dt_long[dt_long$Carbo == "> 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
#   geom_point(size = 2) + 
#   geom_line(size = 1.2) + 
#   theme(axis.title = element_text(size = 18), 
#         axis.text = element_text(size = 18), 
#         axis.line = element_line(colour = "black"), 
#         panel.border = element_blank(), 
#         panel.background = element_blank(), 
#         legend.text = element_text(size = 15), 
#         legend.title = element_text(size = 15) 
#         # legend.position = "bottom", 
#         # legend.direction = "horizontal"
#         ) + 
#   labs(title = "High carbohydarte food consumption (> 75%) probability by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
#   scale_color_discrete(labels = c("1", "2", "3", "4", "5")) + 
#   ylim(c(0,1))
```

# Some comments on changing the cut-off values

In the above analyses, cut-off values were 25%, 50%, 75% or simply 50% only. However, both analyese produced worse models compared with cut-offs (25%, 75% or simply 25%) in the [preliminary results](http://rpubs.com/winterwang/ndnsd1). Entropy dropped largely, BIC, AIC etc. also increased.

### 2018-07-12 Memo_of_meeting.Rmd
memo updated, introduction added some words

@@
 
-- One possiblity of next analysis objective could be:  carb-fibre ratio and various variation of this ratio.
+- One possibility of next analysis objective could be:  carb-fibre ratio and various variation of this ratio.
 Usually I (Dr.
@@
 I wonder if given that the carb value remain always constant at 10g whether we could simply use the value for the fibre 2, 1...etc
+
+- Comment SA: Reviewing the work of Morimoto and Ghodsian, Morimoto calculated a fibre-to-carb ratio by dividing fibre in grams by carbohydrates in grams multiplied by 100%.
+Taken the example above, this will be 15/30*100 = 50.
+Ghodsian calculated the carb:fibre ratio by diving carbohyrdrates in grams by fibre in grams.
+Although these methods are currently used in the literature, **standardizing everything by 10g of carbohydrates makes the findings easier to interpret in terms of public health.** For example, a person can see that a food product with a minimum of 1g of fibre per 10g of crabohydrates is a good quality carbohydrate product, whereas if the fibre value falls below 1 then it means it is of poorer carbohydrate quality.
+
+(Morimoto, N., Kasuga, C., Tanaka, A., Kamachi, K., Ai, M., Urayama, K., & Tanaka, A.
+(2018).
+Association between dietary fibre:carbohydrate intake ratio and insulin resistance in Japanese adults without type 2 diabetes. British Journal of Nutrition,119(6), 620-628.
+doi:10.1017/S0007114517003725)
+
+(Ghodsian B1, Madden AM1.Evaluating the ≤10:1 wholegrain criterion in identifying nutrient quality and health implications of UK breads and breakfast cereals.
+Public Health Nutr. 2018 Apr;21(6):1186-1193.
+doi: 10.1017/S1368980017003718.
+Epub 2017 Dec 26.)
 
@@
         - For more than half (2 in 2, 2 in 3, or >=2 in 4) survey days, if the subject managed to stay in the same class, then he/she can be defined as a regular eater.
-        - Otherwise, he/she is defined as irregular eaters. 
+        - Otherwise, he/she is defined as an irregular eater. 
     - The two approaches proposed here, one is more strict than the other is because there may be only small numbers of people actually stayed in the same class for all four survey days.
 Because with the number of latent classes increases, the probability of jumping from one class to the other will increase, in other words, the probability of staying in the same class for four days will become lower and lower.
+- Comment SA: I like both approaches as it simply gives a dichotomized variable.
+It is true that a certain degree of change in clusters is expected between weekdays and weekends.
+Hence, it is difficult to assume that if a person shifts clusters between weekdays and weekends that they are irregular eaters.
+Moreover, defining how much change is a bad change is tricky, hence why I would have perhaps in the future used some form of a coefficient of variation to define variability or irregularity of eating, potentially based on the variable ‘Best’.
 
@@
     - There are different weighting variables in the data set.
+        - Wti_CY1234 for dietary data
+        - Wtb_CY1234 if using blood data to calculate presence or absence of diabetes status
+        - wti_Y56
+        - wtb_Y56

### 2018-07-12 paper/main.tex
introduction example of diary added
tested on R 3.5.1 in ubuntu 18.04
memo updated, introduction added some words

@@
 \addbibresource{summer.bib} % The filename of the bibliography
-
+\DeclareRobustCommand{\firstsecond}[2]{#1}
 \usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
-
 %----------------------------------------------------------------------------------------
@@
 \university{\href{https://www.lshtm.ac.uk/}{London School of Hygiene and Tropical Medicine}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
-\department{\href{}{Page count: XX page from Introduction to Conclusions}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
+\department{\href{}{Page count: XX from Introduction to Conclusions}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
 \group{Candidate number: 110765} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
@@
 }{}
-\usepackage[margin=1in]{geometry}
+%\usepackage[margin=1in]{geometry}
+\usepackage{geometry}
 \usepackage{hyperref}
@@
 
+\usepackage{float}
+
 \begin{document}
@@
 
-{\large \today}\\[4cm] % Date
+{\large September 2018}\\[4cm] % Date
 
@@
 \textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
+\textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
 \textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
 \textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
+\textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
 \textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
@@
 \textbf{OR} & \textbf{O}dds \textbf{R}atio \\
+\textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
 \end{abbreviations}
@@
 \include{Chapters/Chapter2}
-%\include{Chapters/Chapter3}
-%\include{Chapters/Chapter4}
+\include{Chapters/Chapter3}
+\include{Chapters/Chapter4}
 %\include{Chapters/Chapter5}
+
+%----------------------------------------------------------------------------------------
+%	BIBLIOGRAPHY
+%----------------------------------------------------------------------------------------
+
+\printbibliography[heading=bibintoc]
 
@@
 \include{Appendices/AppendixA}
-%\include{Appendices/AppendixB}
-%\include{Appendices/AppendixC}
-
-%----------------------------------------------------------------------------------------
-%	BIBLIOGRAPHY
-%----------------------------------------------------------------------------------------
-
-\printbibliography[heading=bibintoc]
+\include{Appendices/AppendixB}
+\include{Appendices/AppendixC}
 

### 2018-07-12 results/results.Rmd
memo updated, introduction added some words

@@
 In the above analyses, cut-off values were 25%, 50%, 75% or simply 50% only.
-However, both analyese produced worse models compared with cut-offs (25%, 75% or simply 25%) in the [preliminary results](http://rpubs.com/winterwang/ndnsd1).
+However, both analyses produced worse models compared with cut-offs (25%, 75% or simply 25%) in the [preliminary results](http://rpubs.com/winterwang/ndnsd1).
 Entropy dropped largely, BIC, AIC etc.

### 2018-07-13 paper/Chapters/Chapter2.tex
method updated 10%

@@
 
-\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+\label{Chapter 2} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
 
@@
 
-\section{Main Section 1}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam ultricies lacinia euismod.
-Nam tempus risus in dolor rhoncus in interdum enim tincidunt.
-Donec vel nunc neque.
-In condimentum ullamcorper quam non consequat.
-Fusce sagittis tempor feugiat.
-Fusce magna erat, molestie eu convallis ut, tempus sed arcu.
-Quisque molestie, ante a tincidunt ullamcorper, sapien enim dignissim lacus, in semper nibh erat lobortis purus.
-Integer dapibus ligula ac risus convallis pellentesque.
+\section{Strategy}
 
@@
 %-----------------------------------
-\subsection{Subsection 1}
-
-Nunc posuere quam at lectus tristique eu ultrices augue venenatis.
-Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam erat volutpat.
-Vivamus sodales tortor eget quam adipiscing in vulputate ante ullamcorper.
-Sed eros ante, lacinia et sollicitudin et, aliquam sit amet augue.
-In hac habitasse platea dictumst.
+\subsection{Latent class analysis (LCA)}
 
@@
 
-\subsection{Subsection 2}
-Morbi rutrum odio eget arcu adipiscing sodales.
-Aenean et purus a est pulvinar pellentesque.
-Cras in elit neque, quis varius elit.
-Phasellus fringilla, nibh eu tempus venenatis, dolor elit posuere quam, quis adipiscing urna leo nec orci.
-Sed nec nulla auctor odio aliquet consequat.
-Ut nec nulla in ante ullamcorper aliquam at sed dolor.
-Phasellus fermentum magna in augue gravida cursus.
-Cras sed pretium lorem.
-Pellentesque eget ornare odio.
-Proin accumsan, massa viverra cursus pharetra, ipsum nisi lobortis velit, a malesuada dolor lorem eu neque.
+\subsection{Multilevel latent class analysis (MLCA)}
+
+Multilevel latent class analysis accounts for the nested structure of the data by allowing latent class intercepts to vary across level 2 units and thereby examining if and how level 2 units influence the level 1 latent classes.
+These random intercepts allow the probability of
+membership in a particular level 1 (observations) latent class to vary across level 2 units (e.g., here in the current context are the individuals).
+Essentially this allows the probability that an observation will belong to a
+particular level 1 latent class to vary across Level 2 units (individuals).
+
+\subsubsection{Parametric approach}
+
+A traditional, parametric approach can be applied using a logistic regression model.
+In an unconditional logistic regression model, the probability of the outcome (i.e.
+being in latent class $k$) is constant within the 4-day survey for each individual (level 2).
+Therefore, say when we are fitting a model with $k (k = 1, \cdots, K)$ latent classes in level 1, then in each individual (level 2), there is a probability of being in latent class $k$.
+A random effect model consider the individual (level 2) to be drawn from a population of adults in the UK, and the probability of the outcome (i.e.
+being in latent class $k$) across individuals is considered to be a random variable \parencite{stawski2013multilevel}.
+The 2-level random intercept effect regression model can be expressed as:
+
+\begin{equation}
+\begin{aligned}
+\text{logit}[P(C_{ij} = t)] & = \beta_{0j} & \textbf{(level 1)}  \\
+\beta_{0j} & = \gamma_0 + \gamma_1 w_j + u_{0j} & \textbf{(level 2)} \\ 
+\Rightarrow P(C_{ij} = t) & = \frac{\exp{(\gamma_0 + \gamma_1 w_j + u_{0j})}}{1 + \exp{(\gamma_0 + \gamma_1 w_j + u_{0j})}} \\
+\end{aligned}
+\end{equation}
+
+Where we define:
+
+\begin{itemize}
+	\item $P(C_{ij} = t)$ as the probability that the observation is belonging to latent class $t$;
+	\item $u_{0j}$ as the random intercept for $j$th individual; 
+	\item the random intercept are assumed be normally distributed (i.e.
+$u_{0j} \sim N(0, \sigma_{u_0}^2)$), the magnitude of the $u_{0j}$ variance ($\sigma_{u_0}^2$) indicates the influence of the individuals (level 2);
+	\item $w_j$ is the predictor for individual (level 2), such as age, and/or sex.
+\end{itemize}
+
+\begin{equation}
+%\begin{aligned}
+P(U_{ij1} = s_1, U_{ij2} = s_2, \cdots, U_{ijk} = s_{k}) = \sum_{t=1}^{T}P(C_{ij}=t)\prod_{k=1}^{K}P(U_{ijk} = s_k | C_{ij} = t)
+%\end{aligned}
+\label{MLCA}
+\end{equation}
+
+Where,
+
+\begin{itemize}
+	\item $ U_{ijk} $ represents the response of eating \textcolor{red}{high/low} carbohydrates on $i$th day of the survey ($i \in (1,2,3,4)$) in subject $j$ (level 2) at the $k$th hour of the day ($k \in (1, 2, 3, \cdots, 24)$);
+	\item $C_{ij}$ denotes the latent class membership for subject $j$ on $i$th day of the survey;
+	\item A specific latent class is referred to as $t$, and the total number of latent classes by $T$;
+	\item $P(U_{ijk} = s_k|C_{ij} = t)$ is the probability of a specific response pattern, conditional on membership in latent class $t$.
+\end{itemize}
+
+The $P(C_{ij} = t)$ in equation \ref{MLCA} can be defined by following steps:
+
+\subsubsection{Non-Parametric approach}
 
@@
 
-\section{Main Section 2}
+\section{Survey Data}
 
-Sed ullamcorper quam eu nisl interdum at interdum enim egestas.
-Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor.
-Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula.
-Donec eget quam sapien, in viverra eros.
-Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum.
-Vestibulum in orci quis felis tempor lacinia.
-Vivamus ornare ultrices facilisis.
-Ut hendrerit volutpat vulputate.
-Morbi condimentum venenatis augue, id porta ipsum vulputate in.
-Curabitur luctus tempus justo.
-Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl.
-Aliquam dictum sagittis velit sed iaculis.
-Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis.
-Nam elit libero, tincidunt ut aliquam at, molestie in quam.
-Aenean rhoncus vehicula hendrerit.
+%-----------------------------------
+%	SUBSECTION 1
+%-----------------------------------
+\subsection{Survey Selection Method}
+
+%-----------------------------------
+%	SUBSECTION 2
+%-----------------------------------
+\subsection{Response rates}

### 2018-07-13 paper/Chapters/Chapter2.tex
parametric approach added

@@
 
-\subsection{Multilevel latent class analysis (MLCA)}
+\subsection{Multilevel latent class analysis (MLCA)}\vspace{-0.3cm}
 
@@
 Essentially this allows the probability that an observation will belong to a
-particular level 1 latent class to vary across Level 2 units (individuals).
+particular level 1 latent class to vary across Level 2 units (individuals). \vspace{-0.5cm}
 
-\subsubsection{Parametric approach}
+\subsubsection{Parametric approach}\vspace{-0.3cm}
 
-A traditional, parametric approach can be applied using a logistic regression model.
+Proposed by Vermunt \parencite{Vermunt, vermunt2008latent} and Asparouhov and Muth\'en \parencite{muthen2009multilevel},  a traditional, parametric approach can be applied using a logistic regression model.
 In an unconditional logistic regression model, the probability of the outcome (i.e.
@@
 A random effect model consider the individual (level 2) to be drawn from a population of adults in the UK, and the probability of the outcome (i.e.
-being in latent class $k$) across individuals is considered to be a random variable \parencite{stawski2013multilevel}.
-The 2-level random intercept effect regression model can be expressed as:
+being in latent class $k$) across individuals is considered to be a random variable \parencite{snijders2011multilevel}.
+The 2-level random intercept effect regression model can be expressed as:\vspace{-0.4cm}
 
@@
 \end{aligned}
+\label{randomLCA}
 \end{equation}
+\vspace{-0.3cm}
 
@@
 
+Same as in the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrates within each hour, over 24 hours and during 4 consecutive days of survey period).
+Considering that the latent class indicators are indicator variables ($U_{ijk}$), the MLCA model can be written as follows:\vspace{-0.8cm}
+
 \begin{equation}
@@
 \end{equation}
+\vspace{-0.8cm}
 
@@
 	\item $C_{ij}$ denotes the latent class membership for subject $j$ on $i$th day of the survey;
-	\item A specific latent class is referred to as $t$, and the total number of latent classes by $T$;
+	\item A specific latent class is referred to as $t$, and the total number of level 1 latent classes is denoted by $T$;
 	\item $P(U_{ijk} = s_k|C_{ij} = t)$ is the probability of a specific response pattern, conditional on membership in latent class $t$.
@@
 
-The $P(C_{ij} = t)$ in equation \ref{MLCA} can be defined by following steps:
+The $P(C_{ij} = t)$ in equation \ref{MLCA} is what we have already defined in equation \ref{randomLCA}.
 
-\subsubsection{Non-Parametric approach}
+\vspace{-0.5cm}
+\subsubsection{Non-Parametric approach}\vspace{-0.3cm}
+
+Another approach is a non-parametric MLCA. The $T-1$
 

### 2018-07-14 paper/Chapters/Chapter2.tex
methodology updated

@@
 
-%----------------------------------------------------------------------------------------
+%-----------------------------------
 %	SECTION 1
-%----------------------------------------------------------------------------------------
+%-----------------------------------
+\section{Latent class analysis (LCA)}\vspace{-0.3cm}
 
-\section{Strategy}
+Latent class analysis is a statistical technique that identifies categorical latent (unobserved) class variables on the basis of observed categorical variables \parencite{collins2010latent}.
+It belongs to the family of latent variable models, and is directly analogous to the factor analysis model.
+The major difference is that the latent variable in LCA is categorical, not continuous as in factor analysis.
+The basic assumptions in LCA are independent observations, and local independence, as shown in the fundamental expression of a typical LCA model: \vspace{-0.8cm}
 
-%-----------------------------------
-%	SUBSECTION 1
-%-----------------------------------
-\subsection{Latent class analysis (LCA)}
+\begin{equation}
+P(U_{i1} = s_1, U_{i2} = s_2, \cdots, U_{ik} = s_K) = \sum_{t=t}^{T}P(C_i = t)\prod_{k = 1}^{K}P(U_{ik} = s_k | C_i = t)
+\label{LCA}
+\end{equation}\vspace{-0.7cm}
+
+Where,
+
+\begin{itemize}
+	\item $P(U_{i1} = s_1, U_{i2} = s_2, \cdots, U_{ik} = s_k)$ is the probability of observing a particular vector of responses;
+	\item $P(C_i = t)$ is the probability that a randomly selected $i$th observation will be in class $t$;
+	\item $P(U_{ik} = s_k | C_i = t)$ is the probability of a particular observed response pattern $U_{ik} = s_k$ conditional on membership in latent class $t$.
+\end{itemize}
+
+Equation \ref{LCA} indicates that responses for an observation to the measuring variables are independent of one another given its membership in latent class $t$.
+However, in the NDNS RP data set, the assumption of independent observations is violated.
+Each individual completed their dietary diary for four consecutive days, their diary recordings were later converted into 4 sequences of categorical responses reflecting the type of carbohydrate consumption at each hour of the day.
+The 4 observed sequences (observations) are nested in the participants and therefore are not independent.
+This nested data structure requires multilevel techniques.
+\vspace{-0.3cm}
 
@@
 
-\subsection{Multilevel latent class analysis (MLCA)}\vspace{-0.3cm}
+\section{Multilevel latent class analysis (MLCA)}\vspace{-0.3cm}
 
@@
 
-\subsubsection{Parametric approach}\vspace{-0.3cm}
+\subsection{Parametric approach}\vspace{-0.3cm}
 
@@
 \begin{itemize}
-	\item $P(C_{ij} = t)$ as the probability that the observation is belonging to latent class $t$;
+	\item $P(C_{ij} = t)$ as the probability that the randomly selected $i$th observation of $j$th individual is belonging to latent class $t$;
 	\item $u_{0j}$ as the random intercept for $j$th individual; 
@@
 %\begin{aligned}
-P(U_{ij1} = s_1, U_{ij2} = s_2, \cdots, U_{ijk} = s_{k}) = \sum_{t=1}^{T}P(C_{ij}=t)\prod_{k=1}^{K}P(U_{ijk} = s_k | C_{ij} = t)
+P(U_{ij1} = s_1, U_{ij2} = s_2, \cdots, U_{ijk} = s_{K}) = \sum_{t=1}^{T}P(C_{ij}=t)\prod_{k=1}^{K}P(U_{ijk} = s_k | C_{ij} = t)
 %\end{aligned}
@@
 \vspace{-0.5cm}
-\subsubsection{Non-Parametric approach}\vspace{-0.3cm}
+\subsection{Non-Parametric approach}\vspace{-0.3cm}
 
-Another approach is a non-parametric MLCA. The $T-1$
+Another approach is using a non-parametric MLCA, in which separate latent class models are specified for level 1 and level 2.
+Similar with the parametric MLCA approach, there are $T-1$ random intercepts, where $T$ is the number of level 1 latent classes.
+However, rather than assuming the random intercepts following a normal distribution, the non-parametric MLCA assumes a multinomial (discrete) distribution of the level 2 latent classes.
+This approach is less computationally demanding compared with the parametric approach.
+These level 2 latent
+classes reflect differences in the probability of belonging to a specific level 1 latent class, so that clusters (i.e., individuals) that contain observations with similar probabilities for the level 1 latent classes will be grouped together.
+The non-parametric MLCA model can be defined as follows: \vspace{-0.7cm}
+
+\begin{equation}
+P(C_{ij} = t | CB_j = m)  = \frac{\exp(\gamma_{tm})}{\sum_{r=1}^{T}\exp(\gamma_{tm})}
+\end{equation}
+
+Where,
+
+\begin{itemize}
+	\item $CB_j$ is level 2 latent class membership for $j$th individual;
+	\item $\gamma_{tm}$ is level 1 and level 2 indicators.
+\end{itemize}
+
+According to Finch and French's simulation study \parencite{finch2014multilevel}, non-parametric approach generally resulted in more accurate recovery of the underlying latent structure of the data at both levels and provided better latent class model.
+Specifically, we are interested in exploring meaningful individual (level 2) latent classes rather than their daily consumption classification.
+Therefore, non-parametric MLCA was employed 1) to identify latent classes of observations (level 1) based on the subjects' responses to the 4-day food and drink diary and 2) to form distinct latent classes of individuals (level 2) based on the distribution of observation-level latent classes within individuals.
 

### 2018-07-15 paper/Chapters/Chapter2.tex
MLCA updated results shared with super

@@
 %	SECTION 1
+%-----------------------------------
+\section{Dietary diary collected in the NDNS RP}\vspace{-0.3cm}
+
+Participants were asked to keep a record of everything eaten or drunk over four consecutive days.
+Interviewers undertook three visits with each participant.
+At the first visit, the interviewer explained the method followed a protocol, taking participants through the sections in the diary including how to describe details of food and drink and portion size and an example day.
+The second was a brief visit to check for compliance, answer questions or deal with problems and review the diary to identify and edit possible omissions and missing detail.
+The third visit was to collect the diary and again review and edit possible omissions.
+
+In the diary, participants were asked to record portion sizes in household measures (e.g.
+one tablespoon of beans, one Kit Kat finger-size), or for packaged foods to note the weight indicated on the packet.
+For homemade dishes, participants were asked to record on a separate page in the diary the individual ingredients and quantities for the whole dish along with a brief description of the cooking method and how much of dish they had consumed.
+In addition to details of what and how much was eaten, participants recorded for each eating occasion; when was it, where they were, who they were eating with.
+An example, used as guidance for participants, of a food diary for one day is shown in \textbf{Appendix \ref{AppendixC}}.
+
+%-----------------------------------
+%	SECTION 2
 %-----------------------------------

### 2018-07-15 results/Multlevel LCA.Rmd
MLCA updated results shared with super

---
title: "Multilevel LCA"
author: "Chaochen Wang"
date: "15 July 2018"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
---

# What was not correct before?

When I am trying to write down the statistical details of multilevel LCA in `PROC LCA`, I found an important information that actually make me feel all the analyses about mixed effect LCA [we have been conducting previously](http://rpubs.com/winterwang/MixedLCA) were somehow misleading.

In the [`PROC LCA` user's guideline (https://methodology.psu.edu/sites/default/files/software/proclcalta/proc_lca_lta_1-3-2-1_users_guide.pdf)](https://methodology.psu.edu/sites/default/files/software/proclcalta/proc_lca_lta_1-3-2-1_users_guide.pdf), if you go to Page 10, last sentence of the top paragraph. It says **"Clustering is ignored for estimation purposes, but is taken into account in calculating standard errors by using a 'robust' or 'sandwich' style covariance estimate."** Which contradicts with what was described in page 21 about the function of `CLUSTER` option: **"This statement tells `PROC LCA` that the subjects are not independent random draws, but are nested within clusters such as schools or classrooms..."**

Therefore, I ran two SAS `PROC LCA` programmes (one with the `CLUSTER ID` option, one without) and compared the outputs from the two programmes. If the data structure was considered properly, the two programmes should have given me two different estimates. However, it turned out that **they produced identical parameter estimates**. This meant that the clustered data structure was ignored in `SAS`, even if we used the `CLUSTER ID` statement, the observations were considered as independent in the previous calculations. I was really disappointed, and sincerely sorry about that. But they were not in vain, because when digging into the methodology, conducting LCA by ingoring the data structure should be the first step when someone perform a Multilevel LCA.

# What should I have done?

According to a multilevel LCA (MLCA) example paper: [Multilevel latent class analysis: An application of adolescent smoking typologies with individual and contextual predictors](https://www.tandfonline.com/doi/abs/10.1080/10705511003659342):

**"MLCA accounts for the nested structure of the data by allowing latent class intercepts to vary across Level 2 units and thereby examining if and how Level 2 units influence the Level 1 latent classes. These random intercepts allow the probability of membership in a particular Level 1 latent class to vary across Level 2 units (e.g., communities)."**

In their article, they wanted to identify the smoking pattern for individuals while the individuals were nested within the communities. So they applied MLCA to identify smoking pattern for their study sample, and then within the MLCA framework, communities were also classified by the patterns of smokers within the community:

![](Selection_013.png)

This gave me an idea of "how to deal with the non-consistent eaters problem" that we were concerning about. Because we don't need to. A proper MLCA does it for us.

In MLCA, separate latent class models are specified for level 1 (in NDNS data, the observations) and level 2 (in NDNS data, the individuals). So our data from NDNS actually provided valuable data about how adults in the UK eat throughout the day for 4 days. We can use the data to capture the carbohydrates (or whatever else we are interested) eating time patterns from these observations, and then based on the carb eating patterns calculated by the model, people that eated similar across four days should be regrouped. So there should be two-steps of regrouping.

# An example that examined 3 level 1 classes and 2 level 2 classes in the NDNS data

I have done a MLCA that specified 3 latent classes in level 1 (observations) and two latent classes in level 2 (individuals) using Mplus 7.4, and the summary of analysis as well as the results are shown below:

1. In this analysis, carbohydrates intake was defined as: 
    - not eating; 
    - eating and carbohydrates contributed less than 50% of energy;
    - eating and carbohydrates contributed higher or equal to 50% of energy.

2. Level 1 latent classes are called **within classes (CW)**, level 2 latent classes are called **between classes (CB)**;

3. Univariate proportions and counts for the responses about carborhydrates consumption: (Note that H0-H23 indicate the hour of the day)

```
UNIVARIATE PROPORTIONS AND COUNTS FOR CATEGORICAL VARIABLES

    H0            proportion        counts
         Not eating    0.974        23838.000
       < 50% energy    0.015          364.000
      >= 50% energy    0.011          281.000
    H1
         Not eating    0.988        24190.000
       < 50% energy    0.006          150.000
      >= 50% energy    0.006          143.000
    H2
         Not eating    0.992        24295.000
       < 50% energy    0.004           89.000
      >= 50% energy    0.004           99.000
    H3
         Not eating    0.993        24315.000
       < 50% energy    0.003           77.000
      >= 50% energy    0.004           91.000
    H4
         Not eating    0.992        24284.000
       < 50% energy    0.003           73.000
      >= 50% energy    0.005          126.000
    H5
         Not eating    0.986        24143.000
       < 50% energy    0.005          125.000
      >= 50% energy    0.009          215.000
    H6
         Not eating    0.869        21265.000
       < 50% energy    0.051         1253.000
      >= 50% energy    0.080         1965.000
    H7
         Not eating    0.678        16599.000
       < 50% energy    0.095         2315.000
      >= 50% energy    0.227         5569.000
    H8
         Not eating    0.623        15248.000
       < 50% energy    0.118         2881.000
      >= 50% energy    0.260         6354.000
    H9
         Not eating    0.660        16149.000
       < 50% energy    0.117         2872.000
      >= 50% energy    0.223         5462.000
    H10
         Not eating    0.630        15428.000
       < 50% energy    0.154         3769.000
      >= 50% energy    0.216         5286.000
    H11
         Not eating    0.723        17706.000
       < 50% energy    0.121         2952.000
      >= 50% energy    0.156         3825.000
    H12
         Not eating    0.600        14683.000
       < 50% energy    0.222         5431.000
      >= 50% energy    0.178         4369.000
    H13
         Not eating    0.501        12262.000
       < 50% energy    0.277         6778.000
      >= 50% energy    0.222         5443.000
    H14
         Not eating    0.738        18061.000
       < 50% energy    0.129         3163.000
      >= 50% energy    0.133         3259.000
    H15
         Not eating    0.676        16548.000
       < 50% energy    0.144         3527.000
      >= 50% energy    0.180         4408.000
    H16
         Not eating    0.696        17045.000
       < 50% energy    0.146         3581.000
      >= 50% energy    0.158         3857.000
    H17
         Not eating    0.685        16779.000
       < 50% energy    0.189         4638.000
      >= 50% energy    0.125         3066.000
    H18
         Not eating    0.577        14134.000
       < 50% energy    0.276         6750.000
      >= 50% energy    0.147         3599.000
    H19
         Not eating    0.621        15207.000
       < 50% energy    0.242         5913.000
      >= 50% energy    0.137         3363.000
    H20
         Not eating    0.619        15144.000
       < 50% energy    0.227         5546.000
      >= 50% energy    0.155         3793.000
    H21
         Not eating    0.641        15690.000
       < 50% energy    0.199         4871.000
      >= 50% energy    0.160         3922.000
    H22
         Not eating    0.752        18403.000
       < 50% energy    0.132         3242.000
      >= 50% energy    0.116         2838.000
    H23
         Not eating    0.921        22548.000
       < 50% energy    0.043         1062.000
      >= 50% energy    0.036          873.000
```

4. Model defines 3 latent classes in level 1, and 2 latent classes in level 2, the distribution and proportion from the model are:

```
FINAL CLASS COUNTS AND PROPORTIONS FOR THE LATENT CLASS PATTERNS
BASED ON THEIR MOST LIKELY LATENT CLASS PATTERN

Class Counts and Proportions

  Latent Class
    Pattern
                    count       proportion
    1  1             4658          0.19025
    1  2             4190          0.17114
    1  3             6037          0.24658
    2  1              473          0.01932
    2  2             4761          0.19446
    2  3             4364          0.17825

FINAL CLASS COUNTS AND PROPORTIONS FOR EACH LATENT CLASS VARIABLE
BASED ON THEIR MOST LIKELY LATENT CLASS PATTERN

  Latent Class
    Variable    Class
                               count       proportion
    CB             1           14885          0.60797
                   2            9598          0.39203
    CW             1            5131          0.20957
                   2            8951          0.36560
                   3           10401          0.42483
```

## Visualisation of level 1 latent classes (CW)

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(RColorBrewer)
library(plyr)
library(tidyverse)
library(dplyr)
library(epiDisplay)
library(scales)
library(readr)
CW3CB2_50 <- read_table2("50NDNS_CW3CB2.txt",
                         col_names = FALSE)

names(CW3CB2_50) <- c("H0",
                      "H1",
                      "H2",
                      "H3",
                      "H4",
                      "H5",
                      "H6",
                      "H7",
                      "H8",
                      "H9",
                      "H10",
                      "H11",
                      "H12",
                      "H13",
                      "H14",
                      "H15",
                      "H16",
                      "H17",
                      "H18",
                      "H19",
                      "H20",
                      "H21",
                      "H22",
                      "H23",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      "CPROB5",
                      "CPROB6",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")

pp <- CW3CB2_50 %>% 
  group_by(CW) %>% 
  summarise(H0_1 = sum(H0 == 1)/length(H0), 
            H0_2 = sum(H0 == 2)/length(H0),
            H1_1 = sum(H1 == 1)/length(H1), 
            H1_2 = sum(H1 == 2)/length(H1),
            H2_1 = sum(H2 == 1)/length(H2), 
            H2_2 = sum(H2 == 2)/length(H2),
            H3_1 = sum(H3 == 1)/length(H3), 
            H3_2 = sum(H3 == 2)/length(H3),
            H4_1 = sum(H4 == 1)/length(H4), 
            H4_2 = sum(H4 == 2)/length(H4),
            H5_1 = sum(H5 == 1)/length(H5), 
            H5_2 = sum(H5 == 2)/length(H5),
            H6_1 = sum(H6 == 1)/length(H6), 
            H6_2 = sum(H6 == 2)/length(H6),
            H7_1 = sum(H7 == 1)/length(H7), 
            H7_2 = sum(H7 == 2)/length(H7),
            H8_1 = sum(H8 == 1)/length(H8), 
            H8_2 = sum(H8 == 2)/length(H8),
            H9_1 = sum(H9 == 1)/length(H9), 
            H9_2 = sum(H9 == 2)/length(H9),
            H10_1 = sum(H10 == 1)/length(H10), 
            H10_2 = sum(H10 == 2)/length(H10),
            H11_1 = sum(H11 == 1)/length(H11), 
            H11_2 = sum(H11 == 2)/length(H11),
            H12_1 = sum(H12 == 1)/length(H12), 
            H12_2 = sum(H12 == 2)/length(H12),
            H13_1 = sum(H13 == 1)/length(H13), 
            H13_2 = sum(H13 == 2)/length(H13),
            H14_1 = sum(H14 == 1)/length(H14), 
            H14_2 = sum(H14 == 2)/length(H14),
            H15_1 = sum(H15 == 1)/length(H15), 
            H15_2 = sum(H15 == 2)/length(H15),
            H16_1 = sum(H16 == 1)/length(H16), 
            H16_2 = sum(H16 == 2)/length(H16),
            H17_1 = sum(H17 == 1)/length(H17), 
            H17_2 = sum(H17 == 2)/length(H17),
            H18_1 = sum(H18 == 1)/length(H18), 
            H18_2 = sum(H18 == 2)/length(H18),
            H19_1 = sum(H19 == 1)/length(H19), 
            H19_2 = sum(H19 == 2)/length(H19),
            H20_1 = sum(H20 == 1)/length(H20), 
            H20_2 = sum(H20 == 2)/length(H20),
            H21_1 = sum(H21 == 1)/length(H21), 
            H21_2 = sum(H21 == 2)/length(H21),
            H22_1 = sum(H22 == 1)/length(H22), 
            H22_2 = sum(H22 == 2)/length(H22),
            H23_1 = sum(H23 == 1)/length(H23), 
            H23_2 = sum(H23 == 2)/length(H23))

pp_long <- pp %>% 
  gather(Hour, Prob, -CW) %>% 
  separate(Hour, into = c("HourN", "Carbo"), sep = "_")

pp_long$HourN <- factor(pp_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
```

```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
library(ggthemr)
ggthemr("fresh", layout = "scientific")
library(ggplot2)

ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
  labs(title = "Class 1 Big breakfast: 21.0%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
  labs(title = "Class 2 low-carb dinner: 36.6%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 3, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
  labs(title = "Class 3 late lunch late dinner low carb: 42.5%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
  ylim(c(0,1))
```

## Visualisation of level 2 latent classes (CB)

```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}

ndnsNNN <- read_csv("ndnsNNN.dat")
dt <- ndnsNNN[, c(2,5)]
names(dt) <- c("ID_DAY", "DayofWeek")

CW3CB2_50 <- CW3CB2_50 %>% 
  left_join(dt, by = "ID_DAY")

chart.data <- CW3CB2_50 %>% 
  group_by(CB, CW) %>% 
  tally %>% 
  group_by(CB) %>% 
  mutate(pct = n/sum(n))

chart.data <- ddply(chart.data, .(CB),
                     transform, pos = cumsum(pct) - (0.5 * pct))

chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"), 
                        labels = c("Late lunch late dinner low carb", "Low-carb dinner", "Big breakfast"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"), 
                        labels = c("Individual class 1\n(60.8%)",  "Individual class 2\n(39.2%)"))

library(ggthemr)
ggthemr("dust", layout = "scientific")
ggplot() + 
  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
           stat="identity") + 
  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
            size=4, colour="white", family="Atlas Grotesk Medium") + 
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank(), 
        axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        plot.title=element_text(family="Atlas Grotesk Medium"),
        text=element_text(family="Atlas Grotesk Light")) + 
  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
  scale_y_continuous(labels=percent)
```

So, if what we have defined in the level 1 classes are correct then in the individual level, there are two types of people, class 1 and class 2. Individuals in class 1 have about evenly distributed probabilities of carbohydrate eating pattern, while individuals in class 2 have very low possiblity (4.9%) of eating a big breakfast.

## Latent Classes patterns estimated by the model

Where:

- **CB**: Between individual (level 2) latent classes;
- **CW**: Observational latent classes (level 1);
- **LCpattern**: Latent Class Pattern defined as:

```  
  Latent Class         CB        CW
   Pattern No.      Class     Class

         1             1         1
         2             1         2
         3             1         3
         4             2         1
         5             2         2
         6             2         3
```

```{r echo=FALSE, cache=TRUE}
CW3CB2_50 <- CW3CB2_50[order(CW3CB2_50$ID,CW3CB2_50$ID_DAY,CW3CB2_50$CB),]
library(DT)

dt <- CW3CB2_50 %>% 
  dplyr::select(ID, DayofWeek, AGE, SEX, CB, CW, MLCJOINT) %>% 
  filter(ID < 21209611)

names(dt)[7] <- c("LCpattern")

datatable(dt, options = list(
  searching = TRUE,
  pageLength = 8,
  lengthMenu = c(5, 10, 15, 20)))
#  %>% 
#   formatRound("CPROB1", 1) %>% 
#   formatRound("CPROB2", 1) %>% 
#   formatRound("CPROB3", 1) %>% 
#   formatRound("CPROB4", 1) %>% 
#   formatRound("CPROB5", 1) %>% 
#   formatRound("CPROB6", 1)

```

### 2018-07-15 results/results.Rmd
MLCA updated results shared with super

@@
 
-# Mixed effect LCA with carbohydrates intake groups redefined: (cutoff = 25%, 50%, 75%)
+# ~~Mixed effect~~ LCA with carbohydrates intake groups redefined: (cutoff = 25%, 50%, 75%)
 
@@
 
-# Mixed effect LCA with carbohydrates intake groups redefined: (cutoff = 50%)
+# ~~Mixed effect~~ LCA with carbohydrates intake groups redefined: (cutoff = 50%)
 

### 2018-07-16 paper/Chapters/Chapter2.tex
strategy added

@@
 An example, used as guidance for participants, of a food diary for one day is shown in \textbf{Appendix \ref{AppendixC}}.
+
+\subsection{Definition of carbohydrate intake during the survey}
 
@@
 
+\section{Strategy}
+
+To identify the best-fitting model, we used the following sequential modelling strategy \parencite{henry2010multilevel}:
+
+\begin{itemize}
+	\item Firstly, we ignored the multilevel structure of the data and estimated a series of traditional LC models to determine the number of classes at the observational-level;
+	\item Next, a series of MLCA models were fitted to account for the multi-level structrure of the data.
+In these models, the number of observational-level classes was based on the best fitting LCA model from the first step, and the LCA model at the individual-level was estimated to identify the number of individual-level latent classes;
+	\item Thirdly, when number of individual-level latent classes is defined based on the previous stage, observational-level classes was modified (one class lower and one class higher than in the second step), to see the effect of changing level 1 classes and confirm the best fitting model.
+\end{itemize}
+
 %----------------------------------------------------------------------------------------

### 2018-07-16 paper/Chapters/Chapter2.tex
definition of carb intake added

@@
 In addition to details of what and how much was eaten, participants recorded for each eating occasion; when was it, where they were, who they were eating with.
-An example, used as guidance for participants, of a food diary for one day is shown in \textbf{Appendix \ref{AppendixC}}.
+An example, used as guidance for participants, of a food diary for one day is shown in \textbf{Appendix \ref{AppendixC}}.\vspace{-0.3cm}
 
-\subsection{Definition of carbohydrate intake during the survey}
+\subsection{Definition of carbohydrate intake}\vspace{-0.3cm}
+
+Detailed dairy checking was performed to code and convert the food consumption into energy and nutrients intake.
+Intakes of nutrients were calculated from the food consumption records using a specially adapted Nutrient Databank \parencite{smithers1993maff}, which was originally developed by the Ministry of Agriculture, Fisheries and Food (MAFF) for the Dietary and Nutritional Survey of British Adults.
+Further details of data
+coding and editing are outlined in Appendix A of the NDNS official reports \parencite{NDNSofficial}. Specifically, the main variables that we adopted in the current analysis were defined as:
+
+\begin{itemize}
+	\item Total Energy intake = (protein(gram) $\times$ 17) + (fat(gram) $\times$ 37) + (carbohydrate(gram) $\times$ 16) + (alcohol(gram) $\times$ 29)  kJ;
+	\item Carbohydrate intake = total sugars (gram) + starch (gram); 
+	\item Total sugars = sum of all individual sugars (gram).
+\end{itemize}
+
+To produce a sequence of discrete responses about the carbohydrate intake we are interested, we calculated the energy consumption per hour for each participant.
+The percentage of energy that contributed by carbohydrate within each hour were calculated for every every participant, each single day.
+Since we planed to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical.
+We then dichotomised the responses according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e.
+if within an hour if there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was higher or equal to 50\% of total energy.
+Consequently, for each day of the recording, there were 24 data points generated by the dairy.
 
@@
 
-Same as in the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrates within each hour, over 24 hours and during 4 consecutive days of survey period).
+Same as in the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each hour, over 24 hours and during 4 consecutive days of survey period).
 Considering that the latent class indicators are indicator variables ($U_{ijk}$), the MLCA model can be written as follows:\vspace{-0.8cm}
@@
 \begin{itemize}
-	\item $ U_{ijk} $ represents the response of eating \textcolor{red}{high/low} carbohydrates on $i$th day of the survey ($i \in (1,2,3,4)$) in subject $j$ (level 2) at the $k$th hour of the day ($k \in (1, 2, 3, \cdots, 24)$);
+	\item $ U_{ijk} $ represents the response of eating \textcolor{red}{high/low} carbohydrate on $i$th day of the survey ($i \in (1,2,3,4)$) in subject $j$ (level 2) at the $k$th hour of the day ($k \in (1, 2, 3, \cdots, 24)$);
 	\item $C_{ij}$ denotes the latent class membership for subject $j$ on $i$th day of the survey;
@@
 Specifically, we are interested in exploring meaningful individual (level 2) latent classes rather than their daily consumption classification.
-Therefore, non-parametric MLCA was employed 1) to identify latent classes of observations (level 1) based on the subjects' responses to the 4-day food and drink diary and 2) to form distinct latent classes of individuals (level 2) based on the distribution of observation-level latent classes within individuals.
+Therefore, non-parametric MLCA was employed 1) to identify latent classes of observations (level 1) based on the subjects' responses to the 4-day food and drink diary and 2) to form distinct latent classes of individuals (level 2) based on the distribution of observation-level latent classes within individuals.\vspace{-0.3cm}
 
-\section{Strategy}
+\section{Strategy}\vspace{-0.3cm}
 

### 2018-07-18 paper/Chapters/Chapter2.tex
some methods updated

@@
 The percentage of energy that contributed by carbohydrate within each hour were calculated for every every participant, each single day.
-Since we planed to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical.
-We then dichotomised the responses according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e.
+Since we planed to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical, we then dichotomised the responses according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e.
 if within an hour if there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was higher or equal to 50\% of total energy.
-Consequently, for each day of the recording, there were 24 data points generated by the dairy.
+Consequently, for each day of the recording, there were 24 data points generated by the dairy, each data point included one of the following responses:
+
+\begin{itemize}
+	\item Not eating; 
+	\item Eating, and carbohydrate contributed less than 50\% of the total energy intake;
+	\item Eating, and carbohydrate contributed higher or equal to 50\% of the total energy intake.
+\end{itemize}
 
@@
 
+The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} and the Bootstrap Likelihood ratio test (BS-LRT) \parencite{peel2000robust} which compare $q$ vs.
+$q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability.
+In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.
+
 %----------------------------------------------------------------------------------------

### 2018-07-18 phrases.Rmd
some methods updated

@@
 This assumes that subjects within a class are homogeneous.
+
+## hashimoto2018intake - Intake of Carbohydrate to Fiber Ratio Is a Useful Marker for Metabolic Syndrome in Patients with Type 2 Diabetes: A Cross-Sectional Study
+
+- Recent studies revealed that low carbohydrate diet (LCD) is useful for weight reduction [4, 5]. However,
+whether LCD is useful for human health, including all causes and cardiovascular disease mortality, or not is still
+controversial [6–8].
+
+## alessa2018carbohydrate - Carbohydrate quality and quantity and risk of coronary heart disease among US women and men
+
+- Compared with total carbohydrates, saturated fat intake was not significantly associated with CHD or cardiovascu-
+lar disease outcomes (10).

### 2018-07-19 CW3CB3_4.Rmd
multilevel LCA results updated

---
title: "NDNS multilevel LCA CW2CB2 or CW2CB3"
author: "Chaochen Wang"
date: "19 July 2018"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
---

# Steps of conducting a multilevel LCA

- Firstly, we ignored the multilevel structure of the data and estimated a series of traditional LC models to determine the number of classes at the observational-level;
- Next, a series of MLCA models were fitted to account for the multi-level structrure of the data. In these models, the number of observational-level classes was based on the best fitting LCA model from the first step, and the LCA model at the individual-level was estimated to identify the number of individual-level latent classes;
- Thirdly, when number of individual-level latent classes is defined based on the previous stage, observational-level classes was modified (one class lower and one class higher than in the second step), to see the effect of changing level 1 classes and confirm the best fitting model.

## How to decide the number of classes in level 1 and/or level 2 data

The number of classes in either level 1 were determined by

1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation;

2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} and the Bootstrap Likelihood ratio test (BS-LRT) \parencite{peel2000robust} which compare $q$ vs. $q-1$ class models, where $q$ is the number of latent classes;

3) pattern interpretability.

4) In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.

# Level 1 classes selection

- In this analysis, within each hour of the day carbohydrates intake was defined as: 
    - not eating; 
    - eating and carbohydrates contributed less than 50% of energy;
    - eating and carbohydrates contributed higher or equal to 50% of energy.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(RColorBrewer)
library(plyr)
library(tidyverse)
library(dplyr)
library(epiDisplay)
library(scales)
library(readr)
rm(list=ls(all=TRUE))
# load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")

library(kableExtra)
dt <- read.csv("../LSHTMproject/Tablecsv/ndns_level1only.csv", header = T)
names(dt) <- c("N of classes", "N of free parameters","log-likelihood",  "AIC", "BIC", "aBIC", "Entropy", "Lo-Mendel-Rubin LRT")
dt[1,8] <- "---"
dt[2,8] <- "< 0.0001"
dt[3,8] <- "< 0.0001"
kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Level 1 class selection. (All data, n = 6155, 24483 data points)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(c(2,3), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.")
```

From what is shown in the table that, although AIC, BIC, aBIC or entropy are improving with increasing n of classes, however, the Lo-Mendell-Rubun likelihood ratio test suggested that **n of classes higher than 4 did not fit the data necessarily better**. The null hypothesis of the LRT is that the fit of a n-class model is equal to that of the (n-1)-class model. So that p-value less than 0.05 indicates that the more complex model (the one with more latent classes) provides better fit to the data. We show the results from 3 classes (CW = 3) below.

## Fit information for each model (combination of level 1 and level 2 classes)

```{r echo=FALSE}
rm(list=ls(all=TRUE))
# load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")

library(kableExtra)
dt <- read.csv("../LSHTMproject/Tablecsv/Mixed_50.csv", header = T)
names(dt) <- c("Model", "1 class","2 classes",  "3 classes", "4 classes", "5 classes", "6 classes")
dt[is.na(dt)] <- ""
# library(formattable)
dt %>% 
  # mutate(
  #   `2 classes` = cell_spec(`2 classes`, color = ifelse())) %>% 
  kable(escape = F, 
        digits = 3, row.names = FALSE, align = "l",
        format = "html", caption = "Models Specification") %>% 
  add_header_above(c(" ", "Number of level 1 classes" = 6)) %>% 
  group_rows("Fixed effects model", 1, 5) %>%
  group_rows("Random effects model", 6, 20) %>%
  add_indent(c(2:5,7:10,12:15,17:20)) %>% 
  kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  #row_spec(c(2,3), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.")
```

## Visualisation of level 1 latent classes (CW = 2)

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

CW2CB2 <- read_table2("results/50NDNS_CW2CB2.txt",
                         col_names = FALSE)

names(CW2CB2) <- c("H0",
                      "H1",
                      "H2",
                      "H3",
                      "H4",
                      "H5",
                      "H6",
                      "H7",
                      "H8",
                      "H9",
                      "H10",
                      "H11",
                      "H12",
                      "H13",
                      "H14",
                      "H15",
                      "H16",
                      "H17",
                      "H18",
                      "H19",
                      "H20",
                      "H21",
                      "H22",
                      "H23",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      # "CPROB5",
                      # "CPROB6",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")

pp <- CW2CB2 %>% 
  group_by(CW) %>% 
  summarise(H0_1 = sum(H0 == 1)/length(H0), 
            H0_2 = sum(H0 == 2)/length(H0),
            H1_1 = sum(H1 == 1)/length(H1), 
            H1_2 = sum(H1 == 2)/length(H1),
            H2_1 = sum(H2 == 1)/length(H2), 
            H2_2 = sum(H2 == 2)/length(H2),
            H3_1 = sum(H3 == 1)/length(H3), 
            H3_2 = sum(H3 == 2)/length(H3),
            H4_1 = sum(H4 == 1)/length(H4), 
            H4_2 = sum(H4 == 2)/length(H4),
            H5_1 = sum(H5 == 1)/length(H5), 
            H5_2 = sum(H5 == 2)/length(H5),
            H6_1 = sum(H6 == 1)/length(H6), 
            H6_2 = sum(H6 == 2)/length(H6),
            H7_1 = sum(H7 == 1)/length(H7), 
            H7_2 = sum(H7 == 2)/length(H7),
            H8_1 = sum(H8 == 1)/length(H8), 
            H8_2 = sum(H8 == 2)/length(H8),
            H9_1 = sum(H9 == 1)/length(H9), 
            H9_2 = sum(H9 == 2)/length(H9),
            H10_1 = sum(H10 == 1)/length(H10), 
            H10_2 = sum(H10 == 2)/length(H10),
            H11_1 = sum(H11 == 1)/length(H11), 
            H11_2 = sum(H11 == 2)/length(H11),
            H12_1 = sum(H12 == 1)/length(H12), 
            H12_2 = sum(H12 == 2)/length(H12),
            H13_1 = sum(H13 == 1)/length(H13), 
            H13_2 = sum(H13 == 2)/length(H13),
            H14_1 = sum(H14 == 1)/length(H14), 
            H14_2 = sum(H14 == 2)/length(H14),
            H15_1 = sum(H15 == 1)/length(H15), 
            H15_2 = sum(H15 == 2)/length(H15),
            H16_1 = sum(H16 == 1)/length(H16), 
            H16_2 = sum(H16 == 2)/length(H16),
            H17_1 = sum(H17 == 1)/length(H17), 
            H17_2 = sum(H17 == 2)/length(H17),
            H18_1 = sum(H18 == 1)/length(H18), 
            H18_2 = sum(H18 == 2)/length(H18),
            H19_1 = sum(H19 == 1)/length(H19), 
            H19_2 = sum(H19 == 2)/length(H19),
            H20_1 = sum(H20 == 1)/length(H20), 
            H20_2 = sum(H20 == 2)/length(H20),
            H21_1 = sum(H21 == 1)/length(H21), 
            H21_2 = sum(H21 == 2)/length(H21),
            H22_1 = sum(H22 == 1)/length(H22), 
            H22_2 = sum(H22 == 2)/length(H22),
            H23_1 = sum(H23 == 1)/length(H23), 
            H23_2 = sum(H23 == 2)/length(H23))

pp_long <- pp %>% 
  gather(Hour, Prob, -CW) %>% 
  separate(Hour, into = c("HourN", "Carbo"), sep = "_")

pp_long$HourN <- factor(pp_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
```

```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
library(ggthemr)
ggthemr("fresh", layout = "scientific")
library(ggplot2)

ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
  labs(title = "Class 1 Lunch at 1 pm low carb at night", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
  labs(title = "Class 2 Lunch at noon, high carb breakfast", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
  ylim(c(0,1))

# 
# 
# ggplot(pp_long[pp_long$Class == 3, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
#   geom_point(size = 3) + 
#   geom_line(size = 1.5) + 
#   theme(axis.title = element_text(size = 18), 
#         axis.text = element_text(size = 18), 
#         axis.line = element_line(colour = "black"), 
#         panel.border = element_blank(), 
#         panel.background = element_blank(), 
#         legend.text = element_text(size = 15), 
#         legend.title = element_text(size = 15) 
#         # legend.position = "bottom", 
#         # legend.direction = "horizontal"
#   ) + 
#   labs(title = "Class 3 normal lunch at noon", x = "Hour of the day", y = "Probability",
#        color = "Carbohydrate\nintake") + 
#   scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
#   ylim(c(0,1))
# 
# 
# 
# ggplot(pp_long[pp_long$Class == 4, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
#   geom_point(size = 3) + 
#   geom_line(size = 1.5) + 
#   theme(axis.title = element_text(size = 18), 
#         axis.text = element_text(size = 18), 
#         axis.line = element_line(colour = "black"), 
#         panel.border = element_blank(), 
#         panel.background = element_blank(), 
#         legend.text = element_text(size = 15), 
#         legend.title = element_text(size = 15) 
#         # legend.position = "bottom", 
#         # legend.direction = "horizontal"
#   ) + 
#   labs(title = "Class 4 Low carb all day", x = "Hour of the day", y = "Probability",
#        color = "Carbohydrate\nintake") + 
#   scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
#   ylim(c(0,1))
```

## Visualisation of level 2 latent classes (CB = 2)

```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}

ndnsNNN <- read_csv("results/ndnsNNN.dat")
dt <- ndnsNNN[, c(2,5)]
names(dt) <- c("ID_DAY", "DayofWeek")

CW2CB2 <- CW2CB2 %>% 
  left_join(dt, by = "ID_DAY")

chart.data <- CW2CB2 %>% 
  group_by(CB, CW) %>% 
  tally %>% 
  group_by(CB) %>% 
  mutate(pct = n/sum(n))

chart.data <- ddply(chart.data, .(CB),
                     transform, pos = cumsum(pct) - (0.5 * pct))

chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"), 
                        labels = c("Lunch at 1 pm low carb at night", "Lunch at noon, high carb breakfast"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"), 
                        labels = c("Individual class 1\n(66.63%)",  "Individual class 2\n(33.37%)"))

library(ggthemr)
ggthemr("dust", layout = "scientific")
ggplot() + 
  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
           stat="identity") + 
  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
            size=4, colour="white", family="Atlas Grotesk Medium") + 
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank(), 
        axis.title = element_text(size = 18), 
        axis.text = element_text(size = 15), 
        axis.line = element_line(colour = "black"), 
        plot.title=element_text(family="Atlas Grotesk Medium"),
        text=element_text(family="Atlas Grotesk Light")) + 
  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
  scale_y_continuous(labels=percent)
```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

CW2CB3 <- read_table2("results/50NDNS_CW2CB3.txt",
                         col_names = FALSE)

names(CW2CB3) <- c("H0",
                      "H1",
                      "H2",
                      "H3",
                      "H4",
                      "H5",
                      "H6",
                      "H7",
                      "H8",
                      "H9",
                      "H10",
                      "H11",
                      "H12",
                      "H13",
                      "H14",
                      "H15",
                      "H16",
                      "H17",
                      "H18",
                      "H19",
                      "H20",
                      "H21",
                      "H22",
                      "H23",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      "CPROB5",
                      "CPROB6",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")

pp <- CW2CB3 %>% 
  group_by(CW) %>% 
  summarise(H0_1 = sum(H0 == 1)/length(H0), 
            H0_2 = sum(H0 == 2)/length(H0),
            H1_1 = sum(H1 == 1)/length(H1), 
            H1_2 = sum(H1 == 2)/length(H1),
            H2_1 = sum(H2 == 1)/length(H2), 
            H2_2 = sum(H2 == 2)/length(H2),
            H3_1 = sum(H3 == 1)/length(H3), 
            H3_2 = sum(H3 == 2)/length(H3),
            H4_1 = sum(H4 == 1)/length(H4), 
            H4_2 = sum(H4 == 2)/length(H4),
            H5_1 = sum(H5 == 1)/length(H5), 
            H5_2 = sum(H5 == 2)/length(H5),
            H6_1 = sum(H6 == 1)/length(H6), 
            H6_2 = sum(H6 == 2)/length(H6),
            H7_1 = sum(H7 == 1)/length(H7), 
            H7_2 = sum(H7 == 2)/length(H7),
            H8_1 = sum(H8 == 1)/length(H8), 
            H8_2 = sum(H8 == 2)/length(H8),
            H9_1 = sum(H9 == 1)/length(H9), 
            H9_2 = sum(H9 == 2)/length(H9),
            H10_1 = sum(H10 == 1)/length(H10), 
            H10_2 = sum(H10 == 2)/length(H10),
            H11_1 = sum(H11 == 1)/length(H11), 
            H11_2 = sum(H11 == 2)/length(H11),
            H12_1 = sum(H12 == 1)/length(H12), 
            H12_2 = sum(H12 == 2)/length(H12),
            H13_1 = sum(H13 == 1)/length(H13), 
            H13_2 = sum(H13 == 2)/length(H13),
            H14_1 = sum(H14 == 1)/length(H14), 
            H14_2 = sum(H14 == 2)/length(H14),
            H15_1 = sum(H15 == 1)/length(H15), 
            H15_2 = sum(H15 == 2)/length(H15),
            H16_1 = sum(H16 == 1)/length(H16), 
            H16_2 = sum(H16 == 2)/length(H16),
            H17_1 = sum(H17 == 1)/length(H17), 
            H17_2 = sum(H17 == 2)/length(H17),
            H18_1 = sum(H18 == 1)/length(H18), 
            H18_2 = sum(H18 == 2)/length(H18),
            H19_1 = sum(H19 == 1)/length(H19), 
            H19_2 = sum(H19 == 2)/length(H19),
            H20_1 = sum(H20 == 1)/length(H20), 
            H20_2 = sum(H20 == 2)/length(H20),
            H21_1 = sum(H21 == 1)/length(H21), 
            H21_2 = sum(H21 == 2)/length(H21),
            H22_1 = sum(H22 == 1)/length(H22), 
            H22_2 = sum(H22 == 2)/length(H22),
            H23_1 = sum(H23 == 1)/length(H23), 
            H23_2 = sum(H23 == 2)/length(H23))

pp_long <- pp %>% 
  gather(Hour, Prob, -CW) %>% 
  separate(Hour, into = c("HourN", "Carbo"), sep = "_")

pp_long$HourN <- factor(pp_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
```

## Visualisation of level 2 latent classes (CB = 3)

```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}

ndnsNNN <- read_csv("results/ndnsNNN.dat")
dt <- ndnsNNN[, c(2,5)]
names(dt) <- c("ID_DAY", "DayofWeek")

# 
# CW3CB3_50 <- read_table2("results/50NDNS_CW3CB3.txt",
#                          col_names = FALSE)
# 
# names(CW3CB3_50) <- c("H0",
#                       "H1",
#                       "H2",
#                       "H3",
#                       "H4",
#                       "H5",
#                       "H6",
#                       "H7",
#                       "H8",
#                       "H9",
#                       "H10",
#                       "H11",
#                       "H12",
#                       "H13",
#                       "H14",
#                       "H15",
#                       "H16",
#                       "H17",
#                       "H18",
#                       "H19",
#                       "H20",
#                       "H21",
#                       "H22",
#                       "H23",
#                       "ID_DAY",
#                       "AGE",
#                       "SEX",
#                       "CPROB1",
#                       "CPROB2",
#                       "CPROB3",
#                       "CPROB4",
#                       "CPROB5",
#                       "CPROB6",
#                       "CPROB7",
#                       "CPROB8",
#                       "CPROB9",
#                       "CB",
#                       "CW",
#                       "MLCJOINT",
#                       "ID")

CW2CB3 <- CW2CB3 %>% 
  left_join(dt, by = "ID_DAY")

chart.data <- CW2CB3 %>% 
  group_by(CB, CW) %>% 
  tally %>% 
  group_by(CB) %>% 
  mutate(pct = n/sum(n))

chart.data$CW[chart.data$CW == 1] <- 0 
chart.data$CW[chart.data$CW == 3] <- 1 
chart.data$CW[chart.data$CW == 0] <- 3

chart.data <- chart.data[order(chart.data$CB, chart.data$CW),]
chart.data <- ddply(chart.data, .(CB), 
                    transform, pos = cumsum(pct) - (0.5 * pct))

chart.data$CW <- factor(chart.data$CW, levels = c("3", "2"), 
                        labels = c("Lunch at 1 pm low carb at night", "Lunch at noon, high carb breakfast"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"), 
                        labels = c("Individual class 1\n(39.0%)",  "Individual class 2\n(28.05%)", 
                                   "Individual class 3\n(32.95%)"))

library(ggthemr)
ggthemr("dust", layout = "scientific")
ggplot() + 
  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
           stat="identity") + 
  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
            size=4, colour="white", family="Atlas Grotesk Medium") + 
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank(), 
        axis.title = element_text(size = 18), 
        axis.text = element_text(size = 15), 
        axis.line = element_line(colour = "black"), 
        plot.title=element_text(family="Atlas Grotesk Medium"),
        text=element_text(family="Atlas Grotesk Light")) + 
  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
  scale_y_continuous(labels=percent)
```

<!-- ## Visualisation of level 2 latent classes (CB = 4) -->

<!-- ```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE} -->

<!-- CW3CB4_50 <- read_table2("results/50NDNS_CW3CB4.txt", -->
<!--                          col_names = FALSE) -->

<!-- names(CW3CB4_50) <- c("H0", -->
<!--                       "H1", -->
<!--                       "H2", -->
<!--                       "H3", -->
<!--                       "H4", -->
<!--                       "H5", -->
<!--                       "H6", -->
<!--                       "H7", -->
<!--                       "H8", -->
<!--                       "H9", -->
<!--                       "H10", -->
<!--                       "H11", -->
<!--                       "H12", -->
<!--                       "H13", -->
<!--                       "H14", -->
<!--                       "H15", -->
<!--                       "H16", -->
<!--                       "H17", -->
<!--                       "H18", -->
<!--                       "H19", -->
<!--                       "H20", -->
<!--                       "H21", -->
<!--                       "H22", -->
<!--                       "H23", -->
<!--                       "ID_DAY", -->
<!--                       "AGE", -->
<!--                       "SEX", -->
<!--                       "CPROB1", -->
<!--                       "CPROB2", -->
<!--                       "CPROB3", -->
<!--                       "CPROB4", -->
<!--                       "CPROB5", -->
<!--                       "CPROB6", -->
<!--                       "CPROB7", -->
<!--                       "CPROB8", -->
<!--                       "CPROB9", -->
<!--                       "CPROB10", -->
<!--                       "CPROB11", -->
<!--                       "CPROB12", -->
<!--                       "CB", -->
<!--                       "CW", -->
<!--                       "MLCJOINT", -->
<!--                       "ID") -->

<!-- CW3CB4_50$ID_DAY <- CW3CB3_50$ID_DAY -->

<!-- CW3CB4_50 <- CW3CB4_50 %>%  -->
<!--   left_join(dt, by = "ID_DAY") -->

<!-- chart.data <- CW3CB4_50 %>%  -->
<!--   group_by(CB, CW) %>%  -->
<!--   tally %>%  -->
<!--   group_by(CB) %>%  -->
<!--   mutate(pct = n/sum(n)) -->

<!-- chart.data$CW[chart.data$CW == 1] <- 0 -->
<!-- chart.data$CW[chart.data$CW == 3] <- 1 -->
<!-- chart.data$CW[chart.data$CW == 0] <- 3 -->

<!-- chart.data <- chart.data[order(chart.data$CB, chart.data$CW),] -->

<!-- chart.data <- ddply(chart.data, .(CB), -->
<!--                      transform, pos = cumsum(pct) - (0.5 * pct)) -->

<!-- chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"), -->
<!--                         labels = c("late lunch at 1 pm", "low-carb all day till night", "Lunch at noon")) -->

<!-- chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3", "4"),  -->
<!--                         labels = c("Individual\n class 1\n(20.65%)",  "Individual\n class 2\n(25.68%)",  -->
<!--                                    "Individual\n class 3\n(23.87%)", "Individual\n class 3\n(29.80%)")) -->

<!-- library(ggthemr) -->
<!-- ggthemr("dust", layout = "scientific") -->
<!-- ggplot() +  -->
<!--   geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6, -->
<!--            stat="identity") +  -->
<!--   geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")), -->
<!--             size=4, colour="white", family="Atlas Grotesk Medium") +  -->
<!--   theme(legend.position="bottom", legend.direction="horizontal", -->
<!--         legend.title = element_blank(),  -->
<!--         axis.title = element_text(size = 18),  -->
<!--         axis.text = element_text(size = 13),  -->
<!--         axis.line = element_line(colour = "black"),  -->
<!--         plot.title=element_text(family="Atlas Grotesk Medium"), -->
<!--         text=element_text(family="Atlas Grotesk Light")) +  -->
<!--   labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") + -->
<!--   scale_y_continuous(labels=percent) -->
<!-- ``` -->

### 2018-07-19 paper/main.tex
method updated 10%
multilevel LCA results updated

@@
 	paper=a4paper, % Change to letterpaper for US letter
-	inner=2.0cm, % Inner margin
+	inner=2.54cm, % Inner margin
 	outer=2.8cm, % Outer margin
@@
 \usepackage{float}
+\usepackage{amsmath}
+\usepackage{color}
 
@@
 %----------------------------------------------------------------------------------------
+\onehalfspacing
 
@@
 \textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
+\textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
 \textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
@@
 %
-%\addlinespace % Gap to separate the Roman symbols from the Greek
+%\addspace % Gap to separate the Roman symbols from the Greek
 %
@@
 %----------------------------------------------------------------------------------------
-
+\cleardoublepage\makeatletter\@openrightfalse\makeatother
 \appendix % Cue to tell LaTeX that the following "chapters" are Appendices

### 2018-07-23 CW3CB3_4.Rmd
adding LCGA

@@
       highlightLines: true
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-The number of classes in either level 1 were determined by
+The number of classes in level 1 were determined by
 
@@
 
-2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} and the Bootstrap Likelihood ratio test (BS-LRT) \parencite{peel2000robust} which compare $q$ vs.
-$q-1$ class models, where $q$ is the number of latent classes;
+2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compares $q$ vs. $q-1$ class models, where $q$ is the number of latent classes;
 
@@
 
-4) In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.
+4) In the step of performing multilevel LCA, where LMR-LRT was not available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.
 
@@
 names(dt) <- c("N of classes", "N of free parameters","log-likelihood",  "AIC", "BIC", "aBIC", "Entropy", "Lo-Mendel-Rubin LRT")
-dt[1,8] <- "---"
+dt[1,8] <- "--"
 dt[2,8] <- "< 0.0001"
@@
 So that p-value less than 0.05 indicates that the more complex model (the one with more latent classes) provides better fit to the data.
-We show the results from 3 classes (CW = 3) below.
+We show the results from 2 classes (CW = 2) below.
 
@@
 
-## Visualisation of level 1 latent classes (CW = 2)
+# (CW = 2) Level 1 latent classes
+
+## Visualisation of level 1 latent classes
 
@@
   group_by(CW) %>% 
-  summarise(H0_1 = sum(H0 == 1)/length(H0), 
+  summarise(H0_0 = sum(H0 == 0)/length(H0), 
+            H0_1 = sum(H0 == 1)/length(H0), 
             H0_2 = sum(H0 == 2)/length(H0),
+            H1_0 = sum(H1 == 0)/length(H1),
             H1_1 = sum(H1 == 1)/length(H1), 
             H1_2 = sum(H1 == 2)/length(H1),
+            H2_0 = sum(H2 == 0)/length(H2),
             H2_1 = sum(H2 == 1)/length(H2), 
             H2_2 = sum(H2 == 2)/length(H2),
+            H3_0 = sum(H3 == 0)/length(H3),
             H3_1 = sum(H3 == 1)/length(H3), 
             H3_2 = sum(H3 == 2)/length(H3),
+            H4_0 = sum(H4 == 0)/length(H4),
             H4_1 = sum(H4 == 1)/length(H4), 
             H4_2 = sum(H4 == 2)/length(H4),
+            H5_0 = sum(H5 == 0)/length(H5),
             H5_1 = sum(H5 == 1)/length(H5), 
             H5_2 = sum(H5 == 2)/length(H5),
+            H6_0 = sum(H6 == 0)/length(H6),
             H6_1 = sum(H6 == 1)/length(H6), 
             H6_2 = sum(H6 == 2)/length(H6),
+            H7_0 = sum(H7 == 0)/length(H7),
             H7_1 = sum(H7 == 1)/length(H7), 
             H7_2 = sum(H7 == 2)/length(H7),
+            H8_0 = sum(H8 == 0)/length(H8),
             H8_1 = sum(H8 == 1)/length(H8), 
             H8_2 = sum(H8 == 2)/length(H8),
+            H9_0 = sum(H9 == 0)/length(H9),
             H9_1 = sum(H9 == 1)/length(H9), 
             H9_2 = sum(H9 == 2)/length(H9),
+            H10_0 = sum(H10 == 0)/length(H10),
             H10_1 = sum(H10 == 1)/length(H10), 
             H10_2 = sum(H10 == 2)/length(H10),
+            H11_0 = sum(H11 == 0)/length(H11),
             H11_1 = sum(H11 == 1)/length(H11), 
             H11_2 = sum(H11 == 2)/length(H11),
+            H12_0 = sum(H12 == 0)/length(H12),
             H12_1 = sum(H12 == 1)/length(H12), 
             H12_2 = sum(H12 == 2)/length(H12),
+            H13_0 = sum(H13 == 0)/length(H13),
             H13_1 = sum(H13 == 1)/length(H13), 
             H13_2 = sum(H13 == 2)/length(H13),
+            H14_0 = sum(H14 == 0)/length(H14),
             H14_1 = sum(H14 == 1)/length(H14), 
             H14_2 = sum(H14 == 2)/length(H14),
+            H15_0 = sum(H15 == 0)/length(H15),
             H15_1 = sum(H15 == 1)/length(H15), 
             H15_2 = sum(H15 == 2)/length(H15),
+            H16_0 = sum(H16 == 0)/length(H16),
             H16_1 = sum(H16 == 1)/length(H16), 
             H16_2 = sum(H16 == 2)/length(H16),
+            H17_0 = sum(H17 == 0)/length(H17),
             H17_1 = sum(H17 == 1)/length(H17), 
             H17_2 = sum(H17 == 2)/length(H17),
+            H18_0 = sum(H18 == 0)/length(H18),
             H18_1 = sum(H18 == 1)/length(H18), 
             H18_2 = sum(H18 == 2)/length(H18),
+            H19_0 = sum(H19 == 0)/length(H19),
             H19_1 = sum(H19 == 1)/length(H19), 
             H19_2 = sum(H19 == 2)/length(H19),
+            H20_0 = sum(H20 == 0)/length(H20),
             H20_1 = sum(H20 == 1)/length(H20), 
             H20_2 = sum(H20 == 2)/length(H20),
+            H21_0 = sum(H21 == 0)/length(H21),
             H21_1 = sum(H21 == 1)/length(H21), 
             H21_2 = sum(H21 == 2)/length(H21),
+            H22_0 = sum(H22 == 0)/length(H22),
             H22_1 = sum(H22 == 1)/length(H22), 
             H22_2 = sum(H22 == 2)/length(H22),
+            H23_0 = sum(H23 == 0)/length(H23),
             H23_1 = sum(H23 == 1)/length(H23), 
@@
   ) + 
-  labs(title = "Class 1 Lunch at 1 pm low carb at night", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 1 Lunch at 1 pm high carb breakfast", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
-  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
+  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
   ylim(c(0,1))
@@
   ) + 
-  labs(title = "Class 2 Lunch at noon, high carb breakfast", x = "Hour of the day", y = "Probability",
+  labs(title = "Class 2 Lunch at noon, eat until late", x = "Hour of the day", y = "Probability",
        color = "Carbohydrate\nintake") + 
-  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
+  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
   ylim(c(0,1))
@@
 chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"), 
-                        labels = c("Lunch at 1 pm low carb at night", "Lunch at noon, high carb breakfast"))
+                        labels = c("Lunch at 1 pm high carb breakfast", "Lunch at noon, eat until late"))
 chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"), 
@@
 chart.data$CW <- factor(chart.data$CW, levels = c("3", "2"), 
-                        labels = c("Lunch at 1 pm low carb at night", "Lunch at noon, high carb breakfast"))
+                        labels = c("Lunch at 1 pm high carb breakfast", "Lunch at noon, eat until late"))
 chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"), 
@@
                                    "Individual class 3\n(32.95%)"))
+
+library(ggthemr)
+ggthemr("dust", layout = "scientific")
+ggplot() + 
+  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
+           stat="identity") + 
+  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
+            size=4, colour="white", family="Atlas Grotesk Medium") + 
+  theme(legend.position="bottom", legend.direction="horizontal",
+        legend.title = element_blank(), 
+        axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 15), 
+        axis.line = element_line(colour = "black"), 
+        plot.title=element_text(family="Atlas Grotesk Medium"),
+        text=element_text(family="Atlas Grotesk Light")) + 
+  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
+  scale_y_continuous(labels=percent)
+```
+
+# (CW = 3) Level 1 latent classes
+
+## Visualisation of level 1 latent classes
+
+```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+CW3CB2 <- read_table2("results/50NDNS_CW3CB2.txt",
+                         col_names = FALSE)
+
+names(CW3CB2) <- c("H0",
+                      "H1",
+                      "H2",
+                      "H3",
+                      "H4",
+                      "H5",
+                      "H6",
+                      "H7",
+                      "H8",
+                      "H9",
+                      "H10",
+                      "H11",
+                      "H12",
+                      "H13",
+                      "H14",
+                      "H15",
+                      "H16",
+                      "H17",
+                      "H18",
+                      "H19",
+                      "H20",
+                      "H21",
+                      "H22",
+                      "H23",
+                      "ID_DAY",
+                      "AGE",
+                      "SEX",
+                      "CPROB1",
+                      "CPROB2",
+                      "CPROB3",
+                      "CPROB4",
+                      "CPROB5",
+                      "CPROB6",
+                      "CB",
+                      "CW",
+                      "MLCJOINT",
+                      "ID")
+
+pp <- CW3CB2 %>% 
+  group_by(CW) %>% 
+  summarise(H0_0 = sum(H0 == 0)/length(H0), 
+            H0_1 = sum(H0 == 1)/length(H0), 
+            H0_2 = sum(H0 == 2)/length(H0),
+            H1_0 = sum(H1 == 0)/length(H1),
+            H1_1 = sum(H1 == 1)/length(H1), 
+            H1_2 = sum(H1 == 2)/length(H1),
+            H2_0 = sum(H2 == 0)/length(H2),
+            H2_1 = sum(H2 == 1)/length(H2), 
+            H2_2 = sum(H2 == 2)/length(H2),
+            H3_0 = sum(H3 == 0)/length(H3),
+            H3_1 = sum(H3 == 1)/length(H3), 
+            H3_2 = sum(H3 == 2)/length(H3),
+            H4_0 = sum(H4 == 0)/length(H4),
+            H4_1 = sum(H4 == 1)/length(H4), 
+            H4_2 = sum(H4 == 2)/length(H4),
+            H5_0 = sum(H5 == 0)/length(H5),
+            H5_1 = sum(H5 == 1)/length(H5), 
+            H5_2 = sum(H5 == 2)/length(H5),
+            H6_0 = sum(H6 == 0)/length(H6),
+            H6_1 = sum(H6 == 1)/length(H6), 
+            H6_2 = sum(H6 == 2)/length(H6),
+            H7_0 = sum(H7 == 0)/length(H7),
+            H7_1 = sum(H7 == 1)/length(H7), 
+            H7_2 = sum(H7 == 2)/length(H7),
+            H8_0 = sum(H8 == 0)/length(H8),
+            H8_1 = sum(H8 == 1)/length(H8), 
+            H8_2 = sum(H8 == 2)/length(H8),
+            H9_0 = sum(H9 == 0)/length(H9),
+            H9_1 = sum(H9 == 1)/length(H9), 
+            H9_2 = sum(H9 == 2)/length(H9),
+            H10_0 = sum(H10 == 0)/length(H10),
+            H10_1 = sum(H10 == 1)/length(H10), 
+            H10_2 = sum(H10 == 2)/length(H10),
+            H11_0 = sum(H11 == 0)/length(H11),
+            H11_1 = sum(H11 == 1)/length(H11), 
+            H11_2 = sum(H11 == 2)/length(H11),
+            H12_0 = sum(H12 == 0)/length(H12),
+            H12_1 = sum(H12 == 1)/length(H12), 
+            H12_2 = sum(H12 == 2)/length(H12),
+            H13_0 = sum(H13 == 0)/length(H13),
+            H13_1 = sum(H13 == 1)/length(H13), 
+            H13_2 = sum(H13 == 2)/length(H13),
+            H14_0 = sum(H14 == 0)/length(H14),
+            H14_1 = sum(H14 == 1)/length(H14), 
+            H14_2 = sum(H14 == 2)/length(H14),
+            H15_0 = sum(H15 == 0)/length(H15),
+            H15_1 = sum(H15 == 1)/length(H15), 
+            H15_2 = sum(H15 == 2)/length(H15),
+            H16_0 = sum(H16 == 0)/length(H16),
+            H16_1 = sum(H16 == 1)/length(H16), 
+            H16_2 = sum(H16 == 2)/length(H16),
+            H17_0 = sum(H17 == 0)/length(H17),
+            H17_1 = sum(H17 == 1)/length(H17), 
+            H17_2 = sum(H17 == 2)/length(H17),
+            H18_0 = sum(H18 == 0)/length(H18),
+            H18_1 = sum(H18 == 1)/length(H18), 
+            H18_2 = sum(H18 == 2)/length(H18),
+            H19_0 = sum(H19 == 0)/length(H19),
+            H19_1 = sum(H19 == 1)/length(H19), 
+            H19_2 = sum(H19 == 2)/length(H19),
+            H20_0 = sum(H20 == 0)/length(H20),
+            H20_1 = sum(H20 == 1)/length(H20), 
+            H20_2 = sum(H20 == 2)/length(H20),
+            H21_0 = sum(H21 == 0)/length(H21),
+            H21_1 = sum(H21 == 1)/length(H21), 
+            H21_2 = sum(H21 == 2)/length(H21),
+            H22_0 = sum(H22 == 0)/length(H22),
+            H22_1 = sum(H22 == 1)/length(H22), 
+            H22_2 = sum(H22 == 2)/length(H22),
+            H23_0 = sum(H23 == 0)/length(H23),
+            H23_1 = sum(H23 == 1)/length(H23), 
+            H23_2 = sum(H23 == 2)/length(H23))
+
+pp_long <- pp %>% 
+  gather(Hour, Prob, -CW) %>% 
+  separate(Hour, into = c("HourN", "Carbo"), sep = "_")
+
+pp_long$HourN <- factor(pp_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
+```
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+library(ggthemr)
+ggthemr("fresh", layout = "scientific")
+library(ggplot2)
+
+ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+  ) + 
+  labs(title = "Class 1 Lunch at noon, high carb breakfast", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
+  ylim(c(0,1))
+
+ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+  ) + 
+  labs(title = "Class 2 Low carb at 6pm", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
+  ylim(c(0,1))
+
+# 
+# 
+ggplot(pp_long[pp_long$CW == 3, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+  geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+  ) +
+  labs(title = "Class 3 Lunch at 1 pm, low carb at night", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
+  ylim(c(0,1))
+
+# 
+# 
+# ggplot(pp_long[pp_long$Class == 4, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+#   geom_point(size = 3) + 
+#   geom_line(size = 1.5) + 
+#   theme(axis.title = element_text(size = 18), 
+#         axis.text = element_text(size = 18), 
+#         axis.line = element_line(colour = "black"), 
+#         panel.border = element_blank(), 
+#         panel.background = element_blank(), 
+#         legend.text = element_text(size = 15), 
+#         legend.title = element_text(size = 15) 
+#         # legend.position = "bottom", 
+#         # legend.direction = "horizontal"
+#   ) + 
+#   labs(title = "Class 4 Low carb all day", x = "Hour of the day", y = "Probability",
+#        color = "Carbohydrate\nintake") + 
+#   scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
+#   ylim(c(0,1))
+```
+
+## Visualisation of level 2 latent classes (CB = 2)
+
+```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}
+
+ndnsNNN <- read_csv("results/ndnsNNN.dat")
+dt <- ndnsNNN[, c(2,5)]
+names(dt) <- c("ID_DAY", "DayofWeek")
+
+CW3CB2 <- CW3CB2 %>% 
+  left_join(dt, by = "ID_DAY")
+
+chart.data <- CW3CB2 %>% 
+  group_by(CB, CW) %>% 
+  tally %>% 
+  group_by(CB) %>% 
+  mutate(pct = n/sum(n))
+
+chart.data <- ddply(chart.data, .(CB),
+                     transform, pos = cumsum(pct) - (0.5 * pct))
+
+chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"), 
+                        labels = c("Lunch at 1 pm,\nlow carb at night", "Low carb at 6pm", "Lunch at noon,\nhigh carb breakfast"))
+chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"), 
+                        labels = c("Individual class 1\n(60.06%)",  "Individual class 2\n(39.94%)"))
+
+library(ggthemr)
+ggthemr("dust", layout = "scientific")
+ggplot() + 
+  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
+           stat="identity") + 
+  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
+            size=4, colour="white", family="Atlas Grotesk Medium") + 
+  theme(legend.position="bottom", legend.direction="horizontal",
+        legend.title = element_blank(), 
+        axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 15), 
+        axis.line = element_line(colour = "black"), 
+        plot.title=element_text(family="Atlas Grotesk Medium"),
+        text=element_text(family="Atlas Grotesk Light")) + 
+  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
+  scale_y_continuous(labels=percent)
+```
+
+## Visualisation of level 2 latent classes (CB = 3)
+
+```{r message=FALSE, warning=FALSE, echo=FALSE, paged.print=FALSE}
+
+CW3CB3 <- read_table2("results/50NDNS_CW3CB3.txt",
+                         col_names = FALSE)
+
+names(CW3CB3) <- c("H0",
+                      "H1",
+                      "H2",
+                      "H3",
+                      "H4",
+                      "H5",
+                      "H6",
+                      "H7",
+                      "H8",
+                      "H9",
+                      "H10",
+                      "H11",
+                      "H12",
+                      "H13",
+                      "H14",
+                      "H15",
+                      "H16",
+                      "H17",
+                      "H18",
+                      "H19",
+                      "H20",
+                      "H21",
+                      "H22",
+                      "H23",
+                      "ID_DAY",
+                      "AGE",
+                      "SEX",
+                      "CPROB1",
+                      "CPROB2",
+                      "CPROB3",
+                      "CPROB4",
+                      "CPROB5",
+                      "CPROB6",
+                      "CPROB7",
+                      "CPROB8",
+                      "CPROB9",
+                      "CB",
+                      "CW",
+                      "MLCJOINT",
+                      "ID")
+
+ndnsNNN <- read_csv("results/ndnsNNN.dat")
+dt <- ndnsNNN[, c(2,5)]
+names(dt) <- c("ID_DAY", "DayofWeek")
+
+CW3CB3 <- CW3CB3 %>% 
+  left_join(dt, by = "ID_DAY")
+
+chart.data <- CW3CB3 %>% 
+  group_by(CB, CW) %>% 
+  tally %>% 
+  group_by(CB) %>% 
+  mutate(pct = n/sum(n))
+
+chart.data <- ddply(chart.data, .(CB),
+                     transform, pos = cumsum(pct) - (0.5 * pct))
+
+chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"), 
+                        labels = c("Lunch at 1 pm,\nlow carb at night", "Low carb at 6pm", "Lunch at noon,\nhigh carb breakfast"))
+chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"), 
+                        labels = c("Individual class 1\n(41.76%)",  "Individual class 2\n(27.25%)", "Individual class 3\n(30.10%)"))
+
+library(ggthemr)
+ggthemr("dust", layout = "scientific")
+ggplot() + 
+  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
+           stat="identity") + 
+  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
+            size=4, colour="white", family="Atlas Grotesk Medium") + 
+  theme(legend.position="bottom", legend.direction="horizontal",
+        legend.title = element_blank(), 
+        axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 15), 
+        axis.line = element_line(colour = "black"), 
+        plot.title=element_text(family="Atlas Grotesk Medium"),
+        text=element_text(family="Atlas Grotesk Light")) + 
+  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
+  scale_y_continuous(labels=percent)
+```
+
+# (CW = 4) Level 1 latent classes
+
+## Visualisation of level 1 latent classes
+
+```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+CW4CB2 <- read_table2("results/50NDNS_CW4CB2.txt",
+                         col_names = FALSE)
+
+names(CW4CB2) <- c("H0",
+                      "H1",
+                      "H2",
+                      "H3",
+                      "H4",
+                      "H5",
+                      "H6",
+                      "H7",
+                      "H8",
+                      "H9",
+                      "H10",
+                      "H11",
+                      "H12",
+                      "H13",
+                      "H14",
+                      "H15",
+                      "H16",
+                      "H17",
+                      "H18",
+                      "H19",
+                      "H20",
+                      "H21",
+                      "H22",
+                      "H23",
+                      "ID_DAY",
+                      "AGE",
+                      "SEX",
+                      "CPROB1",
+                      "CPROB2",
+                      "CPROB3",
+                      "CPROB4",
+                      "CPROB5",
+                      "CPROB6",
+                      "CPROB7",
+                      "CPROB8",
+                      "CB",
+                      "CW",
+                      "MLCJOINT",
+                      "ID")
+
+pp <- CW4CB2 %>% 
+  group_by(CW) %>% 
+  summarise(H0_0 = sum(H0 == 0)/length(H0), 
+            H0_1 = sum(H0 == 1)/length(H0), 
+            H0_2 = sum(H0 == 2)/length(H0),
+            H1_0 = sum(H1 == 0)/length(H1),
+            H1_1 = sum(H1 == 1)/length(H1), 
+            H1_2 = sum(H1 == 2)/length(H1),
+            H2_0 = sum(H2 == 0)/length(H2),
+            H2_1 = sum(H2 == 1)/length(H2), 
+            H2_2 = sum(H2 == 2)/length(H2),
+            H3_0 = sum(H3 == 0)/length(H3),
+            H3_1 = sum(H3 == 1)/length(H3), 
+            H3_2 = sum(H3 == 2)/length(H3),
+            H4_0 = sum(H4 == 0)/length(H4),
+            H4_1 = sum(H4 == 1)/length(H4), 
+            H4_2 = sum(H4 == 2)/length(H4),
+            H5_0 = sum(H5 == 0)/length(H5),
+            H5_1 = sum(H5 == 1)/length(H5), 
+            H5_2 = sum(H5 == 2)/length(H5),
+            H6_0 = sum(H6 == 0)/length(H6),
+            H6_1 = sum(H6 == 1)/length(H6), 
+            H6_2 = sum(H6 == 2)/length(H6),
+            H7_0 = sum(H7 == 0)/length(H7),
+            H7_1 = sum(H7 == 1)/length(H7), 
+            H7_2 = sum(H7 == 2)/length(H7),
+            H8_0 = sum(H8 == 0)/length(H8),
+            H8_1 = sum(H8 == 1)/length(H8), 
+            H8_2 = sum(H8 == 2)/length(H8),
+            H9_0 = sum(H9 == 0)/length(H9),
+            H9_1 = sum(H9 == 1)/length(H9), 
+            H9_2 = sum(H9 == 2)/length(H9),
+            H10_0 = sum(H10 == 0)/length(H10),
+            H10_1 = sum(H10 == 1)/length(H10), 
+            H10_2 = sum(H10 == 2)/length(H10),
+            H11_0 = sum(H11 == 0)/length(H11),
+            H11_1 = sum(H11 == 1)/length(H11), 
+            H11_2 = sum(H11 == 2)/length(H11),
+            H12_0 = sum(H12 == 0)/length(H12),
+            H12_1 = sum(H12 == 1)/length(H12), 
+            H12_2 = sum(H12 == 2)/length(H12),
+            H13_0 = sum(H13 == 0)/length(H13),
+            H13_1 = sum(H13 == 1)/length(H13), 
+            H13_2 = sum(H13 == 2)/length(H13),
+            H14_0 = sum(H14 == 0)/length(H14),
+            H14_1 = sum(H14 == 1)/length(H14), 
+            H14_2 = sum(H14 == 2)/length(H14),
+            H15_0 = sum(H15 == 0)/length(H15),
+            H15_1 = sum(H15 == 1)/length(H15), 
+            H15_2 = sum(H15 == 2)/length(H15),
+            H16_0 = sum(H16 == 0)/length(H16),
+            H16_1 = sum(H16 == 1)/length(H16), 
+            H16_2 = sum(H16 == 2)/length(H16),
+            H17_0 = sum(H17 == 0)/length(H17),
+            H17_1 = sum(H17 == 1)/length(H17), 
+            H17_2 = sum(H17 == 2)/length(H17),
+            H18_0 = sum(H18 == 0)/length(H18),
+            H18_1 = sum(H18 == 1)/length(H18), 
+            H18_2 = sum(H18 == 2)/length(H18),
+            H19_0 = sum(H19 == 0)/length(H19),
+            H19_1 = sum(H19 == 1)/length(H19), 
+            H19_2 = sum(H19 == 2)/length(H19),
+            H20_0 = sum(H20 == 0)/length(H20),
+            H20_1 = sum(H20 == 1)/length(H20), 
+            H20_2 = sum(H20 == 2)/length(H20),
+            H21_0 = sum(H21 == 0)/length(H21),
+            H21_1 = sum(H21 == 1)/length(H21), 
+            H21_2 = sum(H21 == 2)/length(H21),
+            H22_0 = sum(H22 == 0)/length(H22),
+            H22_1 = sum(H22 == 1)/length(H22), 
+            H22_2 = sum(H22 == 2)/length(H22),
+            H23_0 = sum(H23 == 0)/length(H23),
+            H23_1 = sum(H23 == 1)/length(H23), 
+            H23_2 = sum(H23 == 2)/length(H23))
+
+pp_long <- pp %>% 
+  gather(Hour, Prob, -CW) %>% 
+  separate(Hour, into = c("HourN", "Carbo"), sep = "_")
+
+pp_long$HourN <- factor(pp_long$HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23"))
+```
+
+```{r echo=FALSE, fig.height=5, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+library(ggthemr)
+ggthemr("fresh", layout = "scientific")
+library(ggplot2)
+
+ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+  ) + 
+  labs(title = "Class 1 Lunch at noon, low carb 5pm,\nhigh carb breakfast", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
+  ylim(c(0,1))
+
+ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
+  geom_point(size = 3) + 
+  geom_line(size = 1.5) + 
+  theme(axis.title = element_text(size = 18), 
+        axis.text = element_text(size = 18), 
+        axis.line = element_line(colour = "black"), 
+        panel.border = element_blank(), 
+        panel.background = element_blank(), 
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15) 
+        # legend.position = "bottom", 
+        # legend.direction = "horizontal"
+  ) + 
+  labs(title = "Class 2 Lunch at noon, low carb 6pm,\nhigh carb breakfast", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") + 
+  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
+  ylim(c(0,1))
+
+# 
+# 
+ggplot(pp_long[pp_long$CW == 3, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+  geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+  ) +
+  labs(title = "Class 3 Low carb late lunch (2pm) and \nLow carb dinner (7pm)", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
+  ylim(c(0,1))
+
+ggplot(pp_long[pp_long$CW == 4, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
+  geom_point(size = 3) +
+  geom_line(size = 1.5) +
+  theme(axis.title = element_text(size = 18),
+        axis.text = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_blank(),
+        panel.background = element_blank(),
+        legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15)
+        # legend.position = "bottom",
+        # legend.direction = "horizontal"
+  ) +
+  labs(title = "Class 4 Low carb lunch (1pm) and \nLow carb dinner (7pm)", x = "Hour of the day", y = "Probability",
+       color = "Carbohydrate\nintake") +
+  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
+  ylim(c(0,1))
+```
+
+## Visualisation of level 2 latent classes (CB = 2)
+
+```{r echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, cache=TRUE}
+
+ndnsNNN <- read_csv("results/ndnsNNN.dat")
+dt <- ndnsNNN[, c(2,5)]
+names(dt) <- c("ID_DAY", "DayofWeek")
+
+CW4CB2 <- CW4CB2 %>% 
+  left_join(dt, by = "ID_DAY")
+
+chart.data <- CW4CB2 %>% 
+  group_by(CB, CW) %>% 
+  tally %>% 
+  group_by(CB) %>% 
+  mutate(pct = n/sum(n))
+
+chart.data <- ddply(chart.data, .(CB),
+                     transform, pos = cumsum(pct) - (0.5 * pct))
+
+chart.data$CW <- factor(chart.data$CW, levels = c("4", "3", "2", "1"), 
+                        labels = c("Low carb lunch (1pm) and \nLow carb dinner (7pm)", 
+                                   "Low carb late\n lunch (2pm) and \nLow carb dinner (7pm)", 
+                                   "Lunch at noon,\n low carb 6pm,\nhigh carb breakfast", 
+                                   "Lunch at noon,\n low carb 5pm,\nhigh carb breakfast"))
+chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"), 
+                        labels = c("Individual class 1\n(59.81%)",  "Individual class 2\n(40.19%)"))
 
@@
 
-<!-- CW3CB4_50 <- read_table2("results/50NDNS_CW3CB4.txt", -->
+<!-- CW2CB4_50 <- read_table2("results/50NDNS_CW2CB4.txt", -->
 <!--                          col_names = FALSE) -->
 
-<!-- names(CW3CB4_50) <- c("H0", -->
+<!-- names(CW2CB4_50) <- c("H0", -->
 <!--                       "H1", -->
@@
 <!--                       "CPROB8", -->
-<!--                       "CPROB9", -->
-<!--                       "CPROB10", -->
-<!--                       "CPROB11", -->
-<!--                       "CPROB12", -->
+<!--                       # "CPROB9", -->
+<!--                       # "CPROB10", -->
+<!--                       # "CPROB11", -->
+<!--                       # "CPROB12", -->
 <!--                       "CB", -->
@@
 
-<!-- CW3CB4_50$ID_DAY <- CW3CB3_50$ID_DAY -->
+<!-- #CW3CB4_50$ID_DAY <- CW3CB3_50$ID_DAY -->
 
-<!-- CW3CB4_50 <- CW3CB4_50 %>%  -->
+<!-- CW2CB4_50 <- CW2CB4_50 %>% -->
 <!--   left_join(dt, by = "ID_DAY") -->
 
-<!-- chart.data <- CW3CB4_50 %>%  -->
+<!-- chart.data <- CW2CB4_50 %>% -->
 <!--   group_by(CB, CW) %>% -->

### 2018-07-23 Rcode/LGCA.R

@@ -1,0 +1,563 @@
+library(readr)
+CARB_50_LGCA_3CLASS <- read_table2("results/LCGA/CARB_50_LGCA_3CLASS.DAT", 
+                                   col_names = FALSE)
+
+head(CARB_50_LGCA_3CLASS)
+
+
+names(CARB_50_LGCA_3CLASS) <- c(
+  "H0_X",  "H1_X",
+  "H2_X",  "H3_X",
+  "H4_X",  "H5_X",
+  "H6_X",  "H7_X",
+  "H8_X",  "H9_X",
+  "H10_X",  "H11_X",
+  "H12_X",  "H13_X",
+  "H14_X",  "H15_X",
+  "H16_X",  "H17_X",
+  "H18_X",  "H19_X",
+  "H20_X",  "H21_X",
+  "H22_X",  "H23_X",
+  "H0_Y",  "H1_Y",
+  "H2_Y",  "H3_Y",
+  "H4_Y",  "H5_Y",
+  "H6_Y",  "H7_Y",
+  "H8_Y",  "H9_Y",
+  "H10_Y",  "H11_Y",
+  "H12_Y",  "H13_Y",
+  "H14_Y",  "H15_Y",
+  "H16_Y",  "H17_Y",
+  "H18_Y",  "H19_Y",
+  "H20_Y",  "H21_Y",
+  "H22_Y",  "H23_Y",
+  "H0_X_X",  "H1_X_X",
+  "H2_X_X",  "H3_X_X",
+  "H4_X_X",  "H5_X_X",
+  "H6_X_X",  "H7_X_X",
+  "H8_X_X",  "H9_X_X",
+  "H10_X_X",  "H11_X_X",
+  "H12_X_X",  "H13_X_X",
+  "H14_X_X",  "H15_X_X",
+  "H16_X_X",  "H17_X_X",
+  "H18_X_X",  "H19_X_X",
+  "H20_X_X",  "H21_X_X",
+  "H22_X_X",  "H23_X_X",
+  "H0_Y_Y",  "H1_Y_Y",
+  "H2_Y_Y",  "H3_Y_Y",
+  "H4_Y_Y",  "H5_Y_Y",
+  "H6_Y_Y",  "H7_Y_Y",
+  "H8_Y_Y",  "H9_Y_Y",
+  "H10_Y_Y",  "H11_Y_Y",
[…]

### 2018-07-23 Rcode/analysis8yrsA.R

@@ -43,10 +43,10 @@ df14d <- data[,c(113,1,2,3,5,6,7,8,9,21,24,55,57,58,59,60,61,62,63,64)]
 var <- names(df14d)
 
 df56d <- data56 %>% 
-  select(var)
+  dplyr::select(var)
 
 df78d <- data78 %>% 
-  select(var)
+  dplyr::select(var)
 
 dfs1 <- rbind(df14d, df56d, df78d)
 
@@ -149,23 +149,27 @@ vecid<-unique(Energy$id)
 Energy <- Energy %>% 
   mutate(KJcarbo = Tot_Carb*16) %>% 
   mutate(CarKJpercentage = KJcarbo/Tot_Energ) %>% 
-  mutate(Carbo = cut(CarKJpercentage, breaks = c(0, 0.26, 0.75, 2), right = FALSE)) %>% 
-  mutate(Carbo2 = cut(CarKJpercentage, breaks = c(0, 0.26, 2), right = FALSE))
+  # mutate(Carbo = cut(CarKJpercentage, breaks = c(0, 0.5, 2), right = FALSE))
+   mutate(Carbo = cut(CarKJpercentage, breaks = c(0, 0.25, 0.50, 0.75, 2), right = FALSE)) #%>% 
+  # mutate(Carbo2 = cut(CarKJpercentage, breaks = c(0, 0.26, 2), right = FALSE))
 
 Energy0 <- Energy[!(Energy$Tot_Energ == 0), ] # some food consumption does not contain any carbohydrates
 
 # Energy0$Carbo[is.na(Energy0$Carbo)] <- "[0.7,1.01)"
 #
 
+Energy0$Carbo <- factor(Energy0$Carbo, labels = c("1", "2", "3", "4"))
 
-Energy0$Carbo <- factor(Energy0$Carbo, labels = c("Low_carb", "Med_carb", "High_carb"))
+# Energy0$Carbo <- factor(Energy0$Carbo, labels = c("< 50%", ">= 50%"))
 
-Energy0$Carbo2 <- factor(Energy0$Carbo2, labels = c("Low_carb", "Med_or_high_carb"))
+# Energy0$Carbo <- factor(Energy0$Carbo, labels = c("Low_carb", "Med_carb", "High_carb"))
+# 
+# Energy0$Carbo2 <- factor(Energy0$Carbo2, labels = c("Low_carb", "Med_or_high_carb"))
 
 
[…]

### 2018-07-24 paper/Chapters/Chapter2.tex
aims and objectives

@@
 %-----------------------------------
-\section{Latent class analysis (LCA)}\vspace{-0.3cm}
+\section{Latent Class Analysis (LCA)}\vspace{-0.3cm}
 
@@
 
-\section{Multilevel latent class analysis (MLCA)}\vspace{-0.3cm}
+\section{Multilevel Latent Class Analysis (MLCA)}\vspace{-0.3cm}
 
@@
 
-\section{Strategy}\vspace{-0.3cm}
+\section{Strategy of conducting MLCA in the current analysis}\vspace{-0.3cm}
 
@@
 
-The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} and the Bootstrap Likelihood ratio test (BS-LRT) \parencite{peel2000robust} which compare $q$ vs.
+The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compare $q$ vs.
 $q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability.
 In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.
+
+\section{Latent Class Growth Analysis (LCGA)}
 
@@
 
+The NDNS RP participants were drawn from the UK Postcode Address File, a list of all the addresses in the UK. The addresses were clustered into Primary Sampling Units (PSUs)
+
 %-----------------------------------

### 2018-07-24 Rcode/analysis8yrsA.R

@@ -1326,3 +1326,9 @@ CARB_255075 <- CARB_255075 %>%
 head(CARB_255075)
 
 write_delim(CARB_255075, "CARB_255075.dat", na = ".", delim = " ")
+
+
+
+# posterior analysis classification with BMI etc. -------------------------
+
+

### 2018-07-24 paper/Chapters/Chapter2.tex
strata and weighting

@@
 \begin{itemize}
-	\item Total Energy intake = (protein(gram) $\times$ 17) + (fat(gram) $\times$ 37) + (carbohydrate(gram) $\times$ 16) + (alcohol(gram) $\times$ 29)  kJ;
-	\item Carbohydrate intake = total sugars (gram) + starch (gram); 
-	\item Total sugars = sum of all individual sugars (gram).
+	\item Total Energy intake = (protein(gramme) $\times$ 17) + (fat(gramme) $\times$ 37) + (carbohydrate(gramme) $\times$ 16) + (alcohol(gramme) $\times$ 29)  kJ;
+	\item Carbohydrate intake = total sugars (gramme) + starch (gramme); 
+%	\item Total sugars = sum of all individual sugars (gramme).
 \end{itemize}
@@
 \begin{itemize}
-	\item Not eating; 
+	\item Not eating any food; 
 	\item Eating, and carbohydrate contributed less than 50\% of the total energy intake;
@@
 \end{itemize}
+\vspace{-0.5cm}
+
+%----------------------------------------------------------------------------------------
+%	SECTION 2
+%----------------------------------------------------------------------------------------
+
+\section{Survey Data}\vspace{-0.3cm}
+
+%-----------------------------------
+%	SUBSECTION 1
+%-----------------------------------
+\subsection{Survey Selection Method}\vspace{-0.3cm}
+
+The NDNS RP participants were drawn from the UK Postcode Address File, a list of all the addresses in the UK.
+The addresses were clustered into Primary Sampling Units (PSUs), small geographical areas, based on postcode sectors, randomly selected from across the UK.
+A list of 27 or 28 addresses was then randomly selected from each PSU.
+
+Overall, for years 1 to 8 combined, a sample of 39,300 address was selected from 1,438 PSUs. The sampling selection process was:
+
+\begin{itemize}
+	\item Randomly select PSUs from the Postcode Address File; 
+	\item Randomly select 27 or 28 addresses in that postcode area; 
+	\item Randomly select one household at that address; 
+	\item Selected addresses were randomly allocated to one of two groups to determine whether an adult (aged 19 years or older) and a child (aged 1.5 to 18 years), or a child only, were selected for interview.
+\end{itemize}
+\vspace{-0.6cm}
+%-----------------------------------
+%	SUBSECTION 2
+%-----------------------------------
+\subsection{Response rates}\vspace{-0.3cm}
+
+The response rates for completion of the food diary (three or four days) were 56\%, 53\%, 53\%, for years 1 to 4 combined, 5 to 6 combined and 7 to 8 combined, respectively.
+A total of 6,155 adults aged 19 years and over were kept in our analysis.
+\vspace{-1.2cm}
+
+\subsection{Strata and weightings}\vspace{-0.3cm}
+
+The strata that used to calibrate proportions in the sample include: age-group (1.5-3, 4-6, 7-10, 11-15, 16-18, 19-24, 25-29, 30-39, 40-49, 50-59, 60-64, 65-69, and over 70 years); sex (men or women); and regions (Northern Ireland, Scotland, Wales, and the nine regions of England).
+
+It is necessary to apply weighting factors to the data collected in the NDNS RP for two reasons: to remove any bias in the observed results which may be due to differences in the probability of households and individuals being selected to take part; and to attempt to reduce differential non-response bias by age, sex and geographical region.
 
@@
 
-\section{Latent Class Growth Analysis (LCGA)}
-
-%----------------------------------------------------------------------------------------
-%	SECTION 2
-%----------------------------------------------------------------------------------------
-
-\section{Survey Data}
-
-%-----------------------------------
-%	SUBSECTION 1
-%-----------------------------------
-\subsection{Survey Selection Method}
-
-The NDNS RP participants were drawn from the UK Postcode Address File, a list of all the addresses in the UK. The addresses were clustered into Primary Sampling Units (PSUs)
-
-%-----------------------------------
-%	SUBSECTION 2
-%-----------------------------------
-\subsection{Response rates}
+\section{Latent Class Growth Analysis (LCGA)}\vspace{-0.3cm}

### 2018-07-24 paper/Chapters/Chapter2.tex
strata weighting etc. added

@@
 Since we planed to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical, we then dichotomised the responses according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e.
-if within an hour if there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was higher or equal to 50\% of total energy.
+if within an hour there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was lower or higher/equal to 50\% of total energy intake within that hour.
 Consequently, for each day of the recording, there were 24 data points generated by the dairy, each data point included one of the following responses:
@@
 
-The response rates for completion of the food diary (three or four days) were 56\%, 53\%, 53\%, for years 1 to 4 combined, 5 to 6 combined and 7 to 8 combined, respectively.
+The response rates for completion of the food diary (three or four days) were 56\%, 53\%, 53\%, for years 1 to 4, 5 to 6, and 7 to 8, respectively.
 A total of 6,155 adults aged 19 years and over were kept in our analysis.
-\vspace{-1.2cm}
+\vspace{-0.6cm}
 
@@
 
+It is necessary to apply weighting factors to the data collected in the NDNS RP for two reasons: to remove any bias in the observed results which may be due to differences in the probability of households and individuals being selected to take part; and to attempt to reduce differential non-response bias by age, sex and geographical region.
+
 The strata that used to calibrate proportions in the sample include: age-group (1.5-3, 4-6, 7-10, 11-15, 16-18, 19-24, 25-29, 30-39, 40-49, 50-59, 60-64, 65-69, and over 70 years); sex (men or women); and regions (Northern Ireland, Scotland, Wales, and the nine regions of England).
 
-It is necessary to apply weighting factors to the data collected in the NDNS RP for two reasons: to remove any bias in the observed results which may be due to differences in the probability of households and individuals being selected to take part; and to attempt to reduce differential non-response bias by age, sex and geographical region.
+Two steps of weighting system are designed in the NDNS RP to assure that the combined sample will be representative of the UK population:
+
+\begin{enumerate}
+	\item An overall selection weight, which is the product of the address, dwelling unit, catering(household) unit, and individual selection weights, was generated to correct for the unequal selection probabilities.
+These weights are the inverse of the selection probabilities at each level of the random sampling process and they can be used to compensate for differences in the chance of selection of an individual.
+	\item An iterative procedure was used to adjust the selection weights until the distribution of the weighted sample matched that of the population for age-group, sex and geographical region.
+Population distributions were taken from the mid-year population estimates \parencite{OfficeofNationalStat}.
+\end{enumerate}
+
+Another set of weights were generated to correct for differential non-response (either due to refusal or inability) to giving a blood sample.
+Response to the blood sample in adults were 51\%, 57\%, and 50\% for years 1 to 4, 5 to 6, and 7 to 8, respectively.
+In creating the blood sample weight, a logistic regression was used by the NDNS RP study team to model the relationship between response to giving blood sample and a set of predictor variables (socio-demographic, participant and catering/household unit characteristics).
+The model generated a predicted probability for each participant, which is the probability would provide blood sample, given the characteristics of the individual and the household unit.
+Participants with characteristics associated with non-response were under-represented in the blood sample and therefore receive a low predicted probability.
+The inverse of these predicted probablities were used as a set of non-response weights so that participants with a low predicted probability got a larger weight, increasing their representation in the sample.
+Then the blood sample weights were re-scaled so that the sum of the weights equalled the number of participants who had a nurse visit.
+The final blood weights should therefore make the blood sample participants representative of all eligible persons in the population.
+
+Further details of the weighting system developed by the NDNS RP are described in the Appendix B of the reports published by Public Health England (PHE) \parencite{bates2014national,roberts2018national}.
 
@@
 \section{Latent Class Growth Analysis (LCGA)}\vspace{-0.3cm}
+
+\section{Association between latent classes and other variables}\vspace{-0.3cm}

### 2018-07-28 phrases.Rmd
table 1

@@
 
+-  jargon ['dʒɑ:ɡən, -ɡɔn]
+
+```
+======== 辞典翻译: jargon ========
+  n. 行话，术语；黄锆石
+============ 网络释义 ============
+----------- jargon -----------
+  行话
+  专门术语
+  术语
+------ phonemic jargon -------
+  音韵性乱语
+------ Computer Jargon -------
+  电脑流行语
+  行话
+```
+
 # Sentences
@@
 lar disease outcomes (10).
+
+## lumley2011complex - Complex surveys: a guide to analysis using R
+
+- In everyday speech, "taking a random sample" of 1000 individuals means a sampling procedure when any subset of 1000 people from the population is equally likely to be selected.
+
+- The expected value of the estimate is the value of the estimate when we select person $i$, times the probability of selecting person $i$, added up over all peole in the population.
+
+- Sampling weights: A sampling weight of 1000 means that the observation represents 1000 individuals in the population.

### 2018-07-28 results/Summary of survey analysis.Rmd
table 1

---
title: "Summary of Survey Analysis"
author: "Chaochen Wang"
date: "27 July 2018"
output:
  html_document:
    nature:
      highlightLines: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(RColorBrewer)
library(plyr)
library(tidyverse)
library(dplyr)
library(epiDisplay)
library(scales)
library(readr)
library(kableExtra)
```

# Multilevel classes results (2by2)

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/CW2CB2results.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "P value [note]")

dt[28, 1] <- c("Hypertension (%) [note]")
dt[32, 1] <- c("Carbohydrate percent (%) [note]")
dt[35, 1] <- c("DM [note]")

kable(dt,  align = "l", escape = F, row.names = FALSE,
              format = "html", caption = "Means, percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
                       "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
                       "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes. For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 "DM was defined by A1C > 6.5%."), 
               notation = "symbol")
```

# Multilevel classes results (3by2)

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/CW3CB2results.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "P value [note]")

dt[28, 1] <- c("Hypertension (%) [note]")
dt[32, 1] <- c("Carbohydrate percent (%) [note]")
dt[35, 1] <- c("DM [note]")

kable(dt,  align = "l", escape = F, row.names = FALSE,
              format = "html", caption = "Means, percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
                       "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
                       "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes. For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 "DM was defined by A1C > 6.5%."), 
               notation = "symbol")
```

# LCGA 2 classes results

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/LCGA2Cresults.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "P value [note]")

dt[28, 1] <- c("Hypertension (%) [note]")
dt[32, 1] <- c("Carbohydrate percent (%) [note]")
dt[35, 1] <- c("DM [note]")

kable(dt,  align = "l", escape = F, row.names = FALSE,
              format = "html", caption = "Means, percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
                       "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
                       "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes. For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 "DM was defined by A1C > 6.5%."), 
               notation = "symbol")
```

# LCGA 3 classes results

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/LCGA3Cresults.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "Latent class = 3", "P value [note]")

dt[28, 1] <- c("Hypertension (%) [note]")
dt[32, 1] <- c("Carbohydrate percent (%) [note]")
dt[35, 1] <- c("DM [note]")

kable(dt,  align = "l", escape = F, row.names = FALSE,
              format = "html", caption = "Means, percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
                       "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
                       "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across >2 classes. For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 "DM was defined by A1C > 6.5%."), 
               notation = "symbol")
```

### 2018-07-28 results/posterior analysis.Rmd
table 1

---
title: "Svyset analysis"
author: "Chaochen Wang"
date: "25 July 2018"
output:
  html_document:
    nature:
      highlightLines: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, message=FALSE}
statapath <- "/usr/local/stata15/stata" # <- Ubuntu path to stata
#statapath <- "D:/software/STATA/Stata-64.exe" # <- Windows STATA path modify if needed
knitr::opts_chunk$set(engine.path = list(
  stata = statapath
))
library(naniar)
library(epiDisplay)
library(readr)
library(plyr)
library(dplyr)
library(tidyverse)
library(haven)
library(survey)
 # install packages if needed
```

# Read the datasets and prepare datasets

## CW2CB2 data set (2by2 multilevel classes)

```{r cache=TRUE, message=FALSE}
CW2CB2 <- read_table2("~/Documents/LSHTMproject/results/50NDNS_CW2CB2.txt",  
                              col_names = FALSE)# change the path to your own path

names(CW2CB2) <- c("H0", "H1", "H2", "H3", "H4", "H5", "H6", "H7",
                   "H8", "H9", "H10", "H11", "H12", "H13", "H14",
                   "H15", "H16", "H17", "H18", "H19", "H20", "H21",
                   "H22", "H23", "ID_DAY", "AGE", "SEX", "CPROB1",
                   "CPROB2", "CPROB3", "CPROB4",
                   # "CPROB5",
                   # "CPROB6",
                   "CB", "CW", "MLCJOINT", "ID")
CW2CB2_reg <- CW2CB2[!duplicated(CW2CB2$ID), ]

CW2CB2_reg <- CW2CB2_reg %>% 
  select(ID, AGE, SEX, CB) # extract only the CB variable (Between individual classes == 1 or 2)

tab1(CW2CB2_reg$CB, graph = FALSE)
```

## CW3CB2 data set (3by2 multilevel classes)

```{r message=FALSE, cache=TRUE}
CW3CB2 <- read_table2("~/Documents/LSHTMproject/results/50NDNS_CW3CB2.txt",  
                      col_names = FALSE)# change the path to your own path

names(CW3CB2) <- c("H0", "H1", "H2", "H3", "H4", "H5", "H6", "H7",
                   "H8", "H9", "H10", "H11", "H12", "H13", "H14",
                   "H15", "H16", "H17", "H18", "H19", "H20", "H21",
                   "H22", "H23", "ID_DAY", "AGE", "SEX", "CPROB1",
                   "CPROB2", "CPROB3", "CPROB4", "CPROB5", "CPROB6",
                   "CB", "CW", "MLCJOINT", "ID")
CW3CB2_reg <- CW3CB2[!duplicated(CW3CB2$ID), ]

CW3CB2_reg <- CW3CB2_reg %>% 
  select(ID, AGE, SEX, CB) # extract only the CB variable (Between individual classes == 1 or 2)

tab1(CW3CB2_reg$CB, graph = FALSE)
```

## LCGA data set (2 classes)

```{r message=FALSE, cache=TRUE, warning=FALSE}
CARB_50_LGCA_2CLASS <- read_table2("~/Documents/LSHTMproject/results/LCGA/CARB_50_LGCA_2CLASS.txt", 
    col_names = FALSE)# change the path to your own path

names(CARB_50_LGCA_2CLASS) <- c("H0_X",  "H1_X", "H2_X",  "H3_X", "H4_X",  "H5_X", "H6_X",  "H7_X",
  "H8_X",  "H9_X",  "H10_X",  "H11_X", "H12_X",  "H13_X", "H14_X",  "H15_X", "H16_X",  "H17_X",
  "H18_X",  "H19_X", "H20_X",  "H21_X", "H22_X",  "H23_X", "H0_Y",  "H1_Y", "H2_Y",  "H3_Y",
  "H4_Y",  "H5_Y", "H6_Y",  "H7_Y", "H8_Y",  "H9_Y", "H10_Y",  "H11_Y", "H12_Y",  "H13_Y",
  "H14_Y",  "H15_Y", "H16_Y",  "H17_Y", "H18_Y",  "H19_Y", "H20_Y",  "H21_Y",
  "H22_Y",  "H23_Y", "H0_X_X",  "H1_X_X", "H2_X_X",  "H3_X_X", "H4_X_X",  "H5_X_X",
  "H6_X_X",  "H7_X_X", "H8_X_X",  "H9_X_X", "H10_X_X",  "H11_X_X", "H12_X_X",  "H13_X_X",
  "H14_X_X",  "H15_X_X", "H16_X_X",  "H17_X_X", "H18_X_X",  "H19_X_X", "H20_X_X",  "H21_X_X",
  "H22_X_X",  "H23_X_X", "H0_Y_Y",  "H1_Y_Y", "H2_Y_Y",  "H3_Y_Y", "H4_Y_Y",  "H5_Y_Y",
  "H6_Y_Y",  "H7_Y_Y", "H8_Y_Y",  "H9_Y_Y", "H10_Y_Y",  "H11_Y_Y", "H12_Y_Y",  "H13_Y_Y",
  "H14_Y_Y",  "H15_Y_Y", "H16_Y_Y",  "H17_Y_Y", "H18_Y_Y",  "H19_Y_Y", "H20_Y_Y",  "H21_Y_Y",
  "H22_Y_Y",  "H23_Y_Y", "ID", "CPROB1",  "CPROB2",
  #"CPROB3",  #"CPROB4", 
  "C")

CARB_50_LGCA_2CLASS[CARB_50_LGCA_2CLASS == "*"] <- NA

LCGA_2class <- CARB_50_LGCA_2CLASS %>% 
  select(ID, C) # extract only the C variable (classes == 1 or 2)

tab1(LCGA_2class$C, graph = FALSE)
```

## LCGA data set (3 classes)

```{r message=FALSE, cache=TRUE, warning=FALSE}
CARB_50_LGCA_3CLASS <- read_table2("~/Documents/LSHTMproject/results/LCGA/CARB_50_LGCA_3CLASS.DAT", 
    col_names = FALSE)# change the path to your own path

names(CARB_50_LGCA_3CLASS) <- c("H0_X",  "H1_X", "H2_X",  "H3_X", "H4_X",  "H5_X", "H6_X",  "H7_X",
  "H8_X",  "H9_X",  "H10_X",  "H11_X", "H12_X",  "H13_X", "H14_X",  "H15_X", "H16_X",  "H17_X",
  "H18_X",  "H19_X", "H20_X",  "H21_X", "H22_X",  "H23_X", "H0_Y",  "H1_Y", "H2_Y",  "H3_Y",
  "H4_Y",  "H5_Y", "H6_Y",  "H7_Y", "H8_Y",  "H9_Y", "H10_Y",  "H11_Y", "H12_Y",  "H13_Y",
  "H14_Y",  "H15_Y", "H16_Y",  "H17_Y", "H18_Y",  "H19_Y", "H20_Y",  "H21_Y",
  "H22_Y",  "H23_Y", "H0_X_X",  "H1_X_X", "H2_X_X",  "H3_X_X", "H4_X_X",  "H5_X_X",
  "H6_X_X",  "H7_X_X", "H8_X_X",  "H9_X_X", "H10_X_X",  "H11_X_X", "H12_X_X",  "H13_X_X",
  "H14_X_X",  "H15_X_X", "H16_X_X",  "H17_X_X", "H18_X_X",  "H19_X_X", "H20_X_X",  "H21_X_X",
  "H22_X_X",  "H23_X_X", "H0_Y_Y",  "H1_Y_Y", "H2_Y_Y",  "H3_Y_Y", "H4_Y_Y",  "H5_Y_Y",
  "H6_Y_Y",  "H7_Y_Y", "H8_Y_Y",  "H9_Y_Y", "H10_Y_Y",  "H11_Y_Y", "H12_Y_Y",  "H13_Y_Y",
  "H14_Y_Y",  "H15_Y_Y", "H16_Y_Y",  "H17_Y_Y", "H18_Y_Y",  "H19_Y_Y", "H20_Y_Y",  "H21_Y_Y",
  "H22_Y_Y",  "H23_Y_Y", "ID", "CPROB1",  "CPROB2",
  "CPROB3",   "C")

CARB_50_LGCA_3CLASS[CARB_50_LGCA_3CLASS == "*"] <- NA

LCGA_3class <- CARB_50_LGCA_3CLASS %>% 
  select(ID, C) # extract only the C variable (classes == 1 or 2)

tab1(LCGA_3class$C, graph = FALSE)
```

## Individual data (BMI, WC, blood pressure, A1C etc.)

```{r message=FALSE, cache=TRUE, warning=FALSE}
# change the following path according to your own data folders

blood78 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr7-8a_indiv.dta")
blood56 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr5-6a_indiv.dta")
blood14 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr1-4a_indiv_uk.dta")

food14 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr1-4a_personleveldietarydata_uk.dta")

food56 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr5-6a_personleveldietarydata.dta")

food78 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr7-8a_personleveldietarydata.dta")

names(blood78)[names(blood78)=="seriali"] <- "ID"
names(blood56)[names(blood56)=="seriali"] <- "ID"
names(blood14)[names(blood14)=="seriali"] <- "ID"
names(food78)[names(food78)=="seriali"] <- "ID"
names(food56)[names(food56)=="seriali"] <- "ID"
names(food14)[names(food14)=="seriali"] <- "ID"

BMI78 <- blood78 %>% 
  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2, MVPAtime, 
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y78, wtn_Y78, wtb_Y78, cluster1, cluster2, cluster3, 
         cluster4, cluster5, area, gor) %>% 
  rename(wti = wti_Y78, wtn = wtn_Y78, wtb = wtb_Y78, drink = dnoft3) %>% 
  mutate(Years = "7-8") %>% 
  replace_with_na(replace = list(bmival = -1, 
                                 wstval = -1, 
                                 bpmedd2 = -1, 
                                 bpmedc2 = -1,
                                 hyper140_2 = -7, 
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 dnnow = -1,
                                 drink = -1,
                                 cigsta3 = -1, 
                                 MVPAtime = -4)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, MVPAtime = -1,
                                 drink = -8)) %>% 
    replace_with_na(replace = list(drink = -9,
                                 cigsta3 = -8))

BMI56 <- blood56 %>% 
  select(ID, Sex, age, area, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2, MVPAtime,
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y56, wtn_Y56, wtb_Y56, cluster1, cluster2, cluster3, 
         cluster4, cluster5, area, gor) %>% 
  mutate(Years = "5-6") %>% 
  rename(wti = wti_Y56, wtn = wtn_Y56, wtb = wtb_Y56, drink = dnoft3) %>% 
  replace_with_na(replace = list(bmival = -1, 
                                 wstval = -1, 
                                 bpmedd2 = -1, 
                                 bpmedc2 = -1,
                                 hyper140_2 = -7, 
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 dnnow = -1,
                                 drink = -1,
                                 cigsta3 = -1,
                                 MVPAtime = -1)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, 
                                 drink = -8)) %>% 
    replace_with_na(replace = list(drink = -9,
                                 cigsta3 = -8))

BMI14 <- blood14 %>% 
  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc, bpmedd, hyper140, hibp140, MVPAtime,
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_CY1234, wtn_CY1234, wtb_CY1234, cluster, area, gor) %>%
  rename(hyper140_2 = hyper140, hibp140_2 = hibp140, bpmedd2 = bpmedd, 
         bpmedc2 = bpmedc, cluster1 = cluster, 
         wti = wti_CY1234, wtn = wtn_CY1234, wtb =  wtb_CY1234, drink = dnoft3) %>% 
  mutate(cluster2 = NA, cluster3 = NA, cluster4 = NA, cluster5 = NA, Years = "1-4") %>% 
  replace_with_na(replace = list(bmival = -1, 
                                 wstval = -1, 
                                 bpmedd2 = -1, 
                                 bpmedc2 = -1,
                                 hyper140_2 = -7, 
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 dnnow = -1,
                                 drink = -1,
                                 cigsta3 = -1,
                                 MVPAtime = -4)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, MVPAtime = -1,
                                 drink = -8)) %>% 
  replace_with_na(replace = list(drink = -9,
                                 cigsta3 = -8))

BMI <- bind_rows(BMI14, BMI56, BMI78)

Energy14 <- food14 %>% 
  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, CHOpctotE)
Energy14$Country[Energy14$Country == "Northern Ireland"] <- "NI"

Energy56 <- food56 %>% 
  select(ID, Country, Surveyyear, EnergykJ, Carbohydrateg, CHOpctotE) %>% 
  rename(SurveyYear = Surveyyear)

Energy78 <- food78 %>% 
  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, CHOpctotE)

Energy <- bind_rows(Energy14, Energy56, Energy78)

CW2CB2_regss <- CW2CB2_reg %>% 
  left_join(BMI, by = "ID") %>% 
  left_join(Energy, by = "ID")## dataset for 2by2 multilevel latent classes

CW3CB2_regss <- CW3CB2_reg %>% 
  left_join(BMI, by = "ID") %>% 
  left_join(Energy, by = "ID")## dataset for 3by2 multilevel latent classes

LCGA_2class <- LCGA_2class %>% 
  left_join(BMI, by = "ID") %>% 
  left_join(Energy, by = "ID")## dataset for 2 classes LCGA

LCGA_3class <- LCGA_3class %>% 
  left_join(BMI, by = "ID") %>% 
  left_join(Energy, by = "ID")## dataset for 3 classes LCGA

rm(blood14, blood56, blood78, BMI14, BMI56, BMI78, BMI, food14, food56, food78, Energy14,    Energy56, Energy78, Energy, CW2CB2, CW2CB2_reg, CW3CB2, CW3CB2_reg, CARB_50_LGCA_2CLASS, CARB_50_LGCA_3CLASS)
```

# Rescale the weighting values

```{r message=FALSE, cache=TRUE, warning=FALSE}
# individual weighting
a <- sum(CW2CB2_regss[CW2CB2_regss$Years == "1-4",]$wti)
b <- sum(CW2CB2_regss[CW2CB2_regss$Years == "5-6",]$wti)
c <- sum(CW2CB2_regss[CW2CB2_regss$Years == "7-8",]$wti)

CW2CB2_regss$wti1to8 <- CW2CB2_regss$wti

CW2CB2_regss[CW2CB2_regss$Years == "1-4",]$wti1to8 <- CW2CB2_regss[CW2CB2_regss$Years == "1-4",]$wti*(a+b+c)*(1/2)/a
CW2CB2_regss[CW2CB2_regss$Years == "5-6",]$wti1to8 <- CW2CB2_regss[CW2CB2_regss$Years == "5-6",]$wti*(a+b+c)*(1/4)/b
CW2CB2_regss[CW2CB2_regss$Years == "7-8",]$wti1to8 <- CW2CB2_regss[CW2CB2_regss$Years == "7-8",]$wti*(a+b+c)*(1/4)/c
mean(CW2CB2_regss$wti1to8)

CW2CB2_regss$wti1to8 <- CW2CB2_regss$wti1to8/1.209816814
summ(CW2CB2_regss$wti1to8, graph = FALSE)
sum(CW2CB2_regss$wti1to8, graph = FALSE) #Check if the weighting sum up to the sample size we have

# Nurse weights

a <- sum(CW2CB2_regss[CW2CB2_regss$Years == "1-4",]$wtn)
b <- sum(CW2CB2_regss[CW2CB2_regss$Years == "5-6",]$wtn)
c <- sum(CW2CB2_regss[CW2CB2_regss$Years == "7-8",]$wtn)

CW2CB2_regss$wtn1to8 <- CW2CB2_regss$wtn

CW2CB2_regss[CW2CB2_regss$Years == "1-4",]$wtn1to8 <- CW2CB2_regss[CW2CB2_regss$Years == "1-4",]$wtn*(a+b+c)*(1/2)/a
CW2CB2_regss[CW2CB2_regss$Years == "5-6",]$wtn1to8 <- CW2CB2_regss[CW2CB2_regss$Years == "5-6",]$wtn*(a+b+c)*(1/4)/b
CW2CB2_regss[CW2CB2_regss$Years == "7-8",]$wtn1to8 <- CW2CB2_regss[CW2CB2_regss$Years == "7-8",]$wtn*(a+b+c)*(1/4)/c
mean(CW2CB2_regss$wtn1to8)

CW2CB2_regss$wtn1to8 <- CW2CB2_regss$wtn1to8/0.907003577
summ(CW2CB2_regss$wtn1to8, graph = FALSE)
sum(CW2CB2_regss$wtn1to8, graph = FALSE) #Check if the weighting sum up to the sample size we have

# Blood weights
a <- sum(CW2CB2_regss[CW2CB2_regss$Years == "1-4",]$wtb)
b <- sum(CW2CB2_regss[CW2CB2_regss$Years == "5-6",]$wtb)
c <- sum(CW2CB2_regss[CW2CB2_regss$Years == "7-8",]$wtb)

CW2CB2_regss$wtb1to8 <- CW2CB2_regss$wtb

CW2CB2_regss[CW2CB2_regss$Years == "1-4",]$wtb1to8 <- CW2CB2_regss[CW2CB2_regss$Years == "1-4",]$wtb*(a+b+c)*(1/2)/a
CW2CB2_regss[CW2CB2_regss$Years == "5-6",]$wtb1to8 <- CW2CB2_regss[CW2CB2_regss$Years == "5-6",]$wtb*(a+b+c)*(1/4)/b
CW2CB2_regss[CW2CB2_regss$Years == "7-8",]$wtb1to8 <- CW2CB2_regss[CW2CB2_regss$Years == "7-8",]$wtb*(a+b+c)*(1/4)/c
mean(CW2CB2_regss$wtb1to8)

CW2CB2_regss$wtb1to8 <- CW2CB2_regss$wtb1to8/0.4817444505
summ(CW2CB2_regss$wtb1to8, graph = FALSE)
sum(CW2CB2_regss$wtb1to8, graph = FALSE) #Check if the weighting sum up to the sample size we have

weightings <- CW2CB2_regss %>% select(ID, wti1to8, wtn1to8, wtb1to8)

# add the weightings to the other datasets
CW3CB2_regss <- CW3CB2_regss %>% 
  left_join(weightings, by = "ID")

LCGA_2class <- LCGA_2class %>% 
  left_join(weightings, by = "ID")

LCGA_3class <- LCGA_3class %>% 
  left_join(weightings, by = "ID")
```

# (BMI) survey designed analysis

## 2by2 multilevel LCA dataset (BMI)
```{r message=FALSE, cache=TRUE, warning=FALSE, eval=FALSE}
 # specifying a survey design

CW2CB2_regss$dnnow <- as.factor(CW2CB2_regss$dnnow)
CW2CB2_regss$cigsta3 <- as.factor(CW2CB2_regss$cigsta3)

cw2cb2 <- svydesign(id = ~area, strat = ~gor, weights=~wti1to8, data = CW2CB2_regss, nest = TRUE)

summary(svyglm(bmival ~ CB, design = cw2cb2))
summary(svyglm(bmival ~ CB + AGE + SEX + cigsta3 + dnnow, design = cw2cb2))
```

```
## Call:
## svyglm(formula = bmival ~ CB, design = cw2cb2)
## 
## Survey design:
## svydesign(id = ~area, strat = ~gor, weights = ~wti1to8, data = CW2CB2_regss, 
##     nest = TRUE)
## 
## Coefficients:
##             Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  26.6815     0.2917  91.468  < 2e-16 ***
## CB            0.5474     0.2026   2.702  0.00699 ** 
## ---
## Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
## 
## (Dispersion parameter for gaussian family taken to be 28.88983)
## 
## Number of Fisher Scoring iterations: 2
## 
## 
## Call:
## svyglm(formula = bmival ~ CB + AGE + SEX + cigsta3 + dnnow, design = cw2cb2)
## 
## Survey design:
## svydesign(id = ~area, strat = ~gor, weights = ~wti1to8, data = CW2CB2_regss, 
##     nest = TRUE)
## 
## Coefficients:
##             Estimate Std. Error t value Pr(>|t|)    
## (Intercept) 24.53607    0.49745  49.324  < 2e-16 ***
## CB           0.44258    0.20174   2.194   0.0285 *  
## AGE          0.04177    0.00582   7.176 1.33e-12 ***
## SEX         -0.21736    0.18620  -1.167   0.2433    
## cigsta32     1.18384    0.29947   3.953 8.22e-05 ***
## cigsta33     0.48760    0.24885   1.959   0.0503 .  
## dnnow2       0.42970    0.24531   1.752   0.0801 .  
## ---
## Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
## 
## (Dispersion parameter for gaussian family taken to be 27.97746)
## 
## Number of Fisher Scoring iterations: 2
```

After adjusting for age, sex, smoking, and drinking, subjects in latent class 2 were averagely with 0.748599 kg/m^2^ higher BMI compared with subjects in latent class 1.

### Compare with results in Stata (they are very similar, and we use Stata subsequently):

```{r engine='stata', echo=FALSE}
use "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW2CB2_regss.dta", clear

label define smoking 1 "current" 2 "ex-smoker" 3 "Never"
label values cigsta3 smoking
label define drinking 1 "no" 2 "yes"
label values dnnow drinking
label define gender 1 "Men" 2 "Women"
label values Sex gender

// weighting with individual weights, area is primary sampling unit, gor is the cluster variable

svyset area [pweight = wti1to8], strata(gor)

svydescribe wti
svy: mean bmival

// two-way table

svy: tabulate Sex CB, row se ci format(%7.3f)
svy: tabulate Sex CB, col se ci format(%7.3f)

// comparing means
svy: mean bmi, over(CB)

svy: regress bmival i.CB
svy: regress bmival i.CB age i.Sex i.cigsta3 i.dnnow

svy: regress wstval i.CB#i.Sex age  i.cigsta3 i.dnnow

svy: regress wst i.CB age i.cigsta3 i.dnnow if Sex == 1
svy: regress wst i.CB age i.cigsta3 i.dnnow if Sex == 2
```

## 3by2 multilevel LCA dataset (BMI)

```{r engine='stata', echo=FALSE}
use "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW3CB2_regss.dta", clear

label define smoking 1 "current" 2 "ex-smoker" 3 "Never"
label values cigsta3 smoking
label define drinking 1 "no" 2 "yes"
label values dnnow drinking
label define gender 1 "Men" 2 "Women"
label values Sex gender

svyset area [pweight = wti1to8], strata(gor)
svydescribe wti
svy: mean bmival
svy: mean bmival if CB == 1
svy: mean bmival if CB == 2

svy: regress bmival i.CB
svy: regress bmival i.CB age i.Sex i.cigsta3 i.dnnow
```

## 2 classes LCGA dataset (BMI)

```{r engine='stata', echo=FALSE}

use "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/LCGA_2class.dta", clear

label define smoking 1 "current" 2 "ex-smoker" 3 "Never"
label values cigsta3 smoking
label define drinking 1 "no" 2 "yes"
label values dnnow drinking
label define gender 1 "Men" 2 "Women"
label values Sex gender

svyset area [pweight = wti1to8], strata(gor)
svydescribe wti
svy: mean bmival
svy: mean bmival if C == 1
svy: mean bmival if C == 2

svy: regress bmival i.C
svy: regress bmival i.C age i.Sex i.cigsta3 i.dnnow
```

## 3 classes LCGA dataset (BMI)

```{r engine='stata', echo=FALSE}
use "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/LCGA_3class.dta", clear

label define smoking 1 "current" 2 "ex-smoker" 3 "Never"
label values cigsta3 smoking
label define drinking 1 "no" 2 "yes"
label values dnnow drinking
label define gender 1 "Men" 2 "Women"
label values Sex gender

svyset area [pweight = wti1to8], strata(gor)
svy: mean bmival
svy: mean bmival if C == 1
svy: mean bmival if C == 2
svy: mean bmival if C == 3
svy: regress bmival i.C
svy: regress bmival i.C age i.Sex i.cigsta3 i.dnnow
```

# (Waist Circumference) survey designed analysis

## 2by2 multilevel LCA dataset (WC)

```{r engine='stata', echo=FALSE}
use "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW2CB2_regss.dta", clear

label define smoking 1 "current" 2 "ex-smoker" 3 "Never"
label values cigsta3 smoking
label define drinking 1 "no" 2 "yes"
label values dnnow drinking
label define gender 1 "Men" 2 "Women"
label values Sex gender

svyset area [pweight = wti1to8], strata(gor)

//svydescribe wti
svy: mean wstval
svy: mean wstval if CB == 1
svy: mean wstval if CB == 2

svy: regress wst i.CB
svy: regress wst i.CB age i.Sex i.cigsta3 i.dnnow
svy: regress wstval i.CB#i.Sex age  i.cigsta3 i.dnnow

svy: regress wst i.CB age i.cigsta3 i.dnnow if Sex == 1
svy: regress wst i.CB age i.cigsta3 i.dnnow if Sex == 2
```

## 3by2 multilevel LCA dataset (WC)

```{r engine='stata', echo=FALSE}
use "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW3CB2_regss.dta", clear

label define smoking 1 "current" 2 "ex-smoker" 3 "Never"
label values cigsta3 smoking
label define drinking 1 "no" 2 "yes"
label values dnnow drinking
label define gender 1 "Men" 2 "Women"
label values Sex gender

svyset area [pweight = wti1to8], strata(gor)
//svydescribe wti
svy: mean wstval
svy: mean wstval if CB == 1
svy: mean wstval if CB == 2

svy: regress wstval i.CB
svy: regress wstval i.CB age i.Sex i.cigsta3 i.dnnow
svy: regress wstval i.CB#i.Sex age  i.cigsta3 i.dnnow

svy: regress wst i.CB age i.cigsta3 i.dnnow if Sex == 1
svy: regress wst i.CB age i.cigsta3 i.dnnow if Sex == 2
```

### 2018-07-28 Rcode/analysis8yrsA.R

@@ -9,6 +9,7 @@ setwd("/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/") # on Ubuntu
 
 library(epiDisplay)
 library(plyr)
+library(dplyr)
 library(tidyverse)
 
 
@@ -1331,4 +1332,236 @@ write_delim(CARB_255075, "CARB_255075.dat", na = ".", delim = " ")
 
 # posterior analysis classification with BMI etc. -------------------------
 
+setwd("/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/") # on Ubuntu
 
+
+library(epiDisplay)
+library(plyr)
+library(dplyr)
+library(tidyverse)
+
+
+library(haven)
+
+# 
+# data <- read_dta("ndns_rp_yr1-4a_foodleveldietarydata_uk.dta")
+# 
+# data56 <- read_dta("ndns_rp_yr5-6a_foodleveldietarydata.dta")
+# 
+# data78 <- read_dta("ndns_rp_yr7-8a_foodleveldietarydata.dta")
+
+library(readr)
+CW2CB2 <- read_table2("~/Documents/LSHTMproject/results/50NDNS_CW2CB2.txt", 
+                              col_names = FALSE)
+
+
+names(CW2CB2) <- c("H0",
+                   "H1",
+                   "H2",
+                   "H3",
+                   "H4",
+                   "H5",
+                   "H6",
+                   "H7",
+                   "H8",
+                   "H9",
+                   "H10",
+                   "H11",
+                   "H12",
+                   "H13",
+                   "H14",
+                   "H15",
+                   "H16",
+                   "H17",
+                   "H18",
+                   "H19",
+                   "H20",
+                   "H21",
+                   "H22",
+                   "H23",
+                   "ID_DAY",
+                   "AGE",
+                   "SEX",
+                   "CPROB1",
+                   "CPROB2",
+                   "CPROB3",
+                   "CPROB4",
+                   # "CPROB5",
+                   # "CPROB6",
+                   "CB",
+                   "CW",
+                   "MLCJOINT",
+                   "ID")
+
+
+CW3CB2 <- read_table2("~/Documents/LSHTMproject/results/50NDNS_CW3CB2.txt", 
[…]

### 2018-07-28 results/survey.R

@@ -1,0 +1,28 @@
+library(foreign)
+demo <- read.xport("/home/wangcc-me/Downloads/NHANES/demo_c.xpt")
+names(demo)
+
+
+library(survey)
+data(api)
+srs_design <- svydesign(id = ~1, fpc = ~fpc, data = apisrs)
+srs_design
+
+svytotal(~enroll, srs_design)
+svymean(~enroll, srs_design)
+
+# summ(apisrs$enroll)
+# sqrt(sd(apisrs$enroll))
+
+nofpc <- svydesign(id = ~1, weights = ~pw, data = apisrs)
+nofpc
+
+svytotal(~enroll, nofpc)
+svymean(~enroll, nofpc)
+
+
+svytotal(~stype, srs_design)
+
+
+strat_design <- svydesign(id = ~1, strata = ~stype, fpc = ~fpc, data = apistrat)
+strat_design

### 2018-07-28 CW3CB3_4.Rmd
tables 1 added

@@
 author: "Chaochen Wang"
-date: "19 July 2018"
+date: "Created at 2018-7-19, Updated at `r Sys.Date()`"
 output: 

### 2018-07-28 paper/Chapters/Chapter3.tex
tables 1 added

@@
 \section{Main Section 1}
+
+\begin{table}
+	\rowcolors{2}{gray!6}{white}	
+	\caption{\label{tab:}Means, percentages, and 95\% CIs of the characteristics by multilevel latent class analysis memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}
+		\centering
+		\fontsize{9}{10}\selectfont
+		\begin{tabular}[t]{lccc}
+			\hiderowcolors
+			\toprule
+			Variables & Latent class = 1 & Latent class = 2 & P value \textsuperscript{*}\\
+			\midrule
+			\showrowcolors
+			Total (\%) & 66.4  (64.8 , 68.1) & 33.6  (31.9 , 35.2) & \\
+			Countries (\%) &  &  & \\
+			\hspace{1em}England & 83.1  (80.9 , 85.1) & 85.4  (83.0 , 87.5) & 0.203\\
+			\hspace{1em}Northern Ireland & 3.0  (2.3 , 3.9) & 2.3  (1.7 , 3.1) & \\
+			\hspace{1em}Scotland & 8.9  (7.2 , 11.0) & 7.7  (5.9 , 9.9) & \\
+			\hspace{1em}Wales & 5.0  (4.1 , 6.0) & 4.6  (3.6 , 6.0) & \\
+			Age (years) & 47.3 (46.4, 48.2) & 50.1 (49.1, 51.1) & < 0.001\\
+			Sex (\%) &  &  & \\
+			\hspace{1em}Men & 47.3  (45.2 , 49.5) & 51.0  (48.1 , 53.9) & 0.048\\
+			\hspace{1em}Women & 52.7  (50.5 , 54.8) & 49.0  (46.1 , 51.9) & \\
+			Survey years (\%) &  &  & \\
+			\hspace{1em}1 & 13.1 (10.8, 15.8) & 15.0 (12.1, 18.5) & 0.365\\
+			\hspace{1em}2 & 12.3 (10.1, 14.9) & 11.9 (9.4, 14.2) & \\
+			\hspace{1em}3 & 12.0 (9.8, 14.8) & 10.4 (8.2, 13.1) & \\
+			\hspace{1em}4 & 13.2 (10.9, 16.0) & 11.4 (9.0, 14.2) & \\
+			\hspace{1em}5 & 13.0 (10.8, 15.7) & 13.9 (11.1, 17.3) & \\
+			\hspace{1em}6 & 12.0 (9.9, 14.4) & 11.1 (8.8, 13.9) & \\
+			\hspace{1em}7 & 12.3 (10.1,14.9) & 13.5 (10.9, 16.7) & \\
+			\hspace{1em}8 & 12.0 (9.9, 14.5) & 12.8 (10.3, 15.8) & \\
+			BMI (kg/m\textsuperscript{2}) & 27.2 (26.9, 27.5) & 27.7 (27.5, 28.1) & 0.007\\
+			WC (cm) & 92.6 (91.9, 93.3) & 94.2 (93.1, 95.2) & 0.013\\
+			Smoking status (\%) &  &  & \\
+			\hspace{1em}Current & 19.8  (18.2 , 21.4) & 23.8 (21.3 , 26.5) & < 0.001\\
+			\hspace{1em}Ex-smoker & 22.5  (20.8 , 24.2) & 28.0 (25.4 , 30.7) & \\
+			\hspace{1em}Never & 57.8  (55.7 , 59.8) & 48.2 (45.3 , 51.1) & \\
+			Current drinking status (\%) &  &  & \\
+			\hspace{1em}Yes & 23.1  (21.3 , 25.1) & 11.1  (9.5 , 13.0) & < 0.001\\
+			Hypertension (\%) \textsuperscript{\dag} &  &  & \\
+			\hspace{1em}Yes & 27.4  (25.0 , 29.9) & 32.6  (29.3 , 36.1) & 0.012\\
+			Total energy intake (KJ) & 7425.7 (7323.7, 7527.8) & 8149.9 (7997.3, 8302.7) & < 0.001\\
+			Carbohydrate intake (g) & 226.0 (222.8, 229.3) & 210 (206.1, 213.9) & < 0.001\\
+			Carbohydrate
+			percent (\%) \textsuperscript{\ddag} & 48.3 (48.0, 48.6) & 40.9 (40.6, 41.3) & < 0.001\\
+			Glucose (mmol/l) & 5.13 (5.09, 5.17) & 5.17 (5.11, 5.22) & 0.292\\
+			A1C (\%) & 5.49 (5.47, 5.52) & 5.47 (5.44,5.51) & 0.264\\
+			DM \textsuperscript{\S} & 4.1  (3.1 , 5.3 ) & 5.9  (4.3 , 8.0 ) & 0.061\\
+			Physical
+			activity (hours/day) \textsuperscript{\P} & 1.51 (1.39, 1.63) & 1.64 (1.45, 1.82) & 0.244\\
+			\bottomrule
+			\multicolumn{4}{l}{\textit{Note: }}\\
+			\multicolumn{4}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey}\\ 
+			\multicolumn{4}{l}{rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c;}\\ 
+			\multicolumn{4}{l}{DM, diabetes mellitus.}\\
+			\multicolumn{4}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights,}\\  
+			\multicolumn{4}{l}{the others are weighted by individual weights.}\\
+			\multicolumn{4}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
+			\multicolumn{4}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes.}\\
+			\multicolumn{4}{l}{For categorical variables, differences between latent classes were assessed using the adjusted}\\
+			\multicolumn{4}{l}{Pearson Chi-2 test for survey data.}\\
+			\multicolumn{4}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood}\\
+			\multicolumn{4}{l}{pressure >= 90 mmHg, or under treatment for hypertension.}\\
+			\multicolumn{4}{l}{\textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake}\\
+			\multicolumn{4}{l}{\textsuperscript{\S} DM was defined by A1C > 6.5\%.}\\
+			\multicolumn{4}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity}\\
+			\multicolumn{4}{l}{during the survey.}\\
+		\end{tabular}
+	\rowcolors{2}{white}{white}
+	\end{table}
 
@@
 \section{Main Section 2}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+	\caption{\label{tab:unnamed-chunk-2}Means, percentages, and 95\% CIs of the characteristics by latent class growth analysis memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}
+	\centering
+	\fontsize{9}{11}\selectfont
+	\begin{tabular}[t]{lcccc}
+		\hiderowcolors
+		\toprule
+		Variables & Latent class = 1 & Latent class = 2 & Latent class = 3 & P value \textsuperscript{*}\\
+		\midrule
+		\showrowcolors
+		Total (\%) & 28.4 (26.8, 30.1) & 7.0 (6.2, 7.9) & 64.6 (62.9, 66.2) & \\
+		Countries (\%) &  &  &  & \\
+		\hspace{1em}England & 81.4 (78.5, 84.0) & 87.5 (82.9, 91.0) & 84.6 (82.5, 86.4) & 0.004\\
+		\hspace{1em}Northern Ireland & 3.9 (2.9, 5.1) & 0.6 (0.3, 1.2) & 2.5 (2.0, 3.2) & \\
+		\hspace{1em}Scotland & 9.5 (7.4, 12.3) & 6.2 (3.5, 10.6) & 8.3 (6.7, 10.3) & \\
+		\hspace{1em}Wales & 5.2 (4.1, 6.6) & 5.7 (3.8, 8.5) & 4.6 (3.8, 5.6) & \\
+		Age (years) & 43.8 (42.4, 45.1) & 49.1 (47.2, 50.9) & 50.1 (49.3, 50.9) & < 0.001\\
+		Sex (\%) &  &  &  & \\
+		\hspace{1em}Men & 50.6 (47.3, 53.9) & 49.6 (43.7, 55.4) & 47.6 (45.4, 49.7) & 0.273\\
+		\hspace{1em}Women & 49.4 (46.1, 52.7) & 50.4 (44.6, 56.3) & 52.4 (50.3, 54.6) & \\
+		Survey years (\%) &  &  &  & \\
+		\hspace{1em}1 & 11.4 (8.8, 14.7) & 17.1 (12.4, 23.3) & 14.4 (11.9, 17.4) & 0.002\\
+		\hspace{1em}2 & 10.1 (7.8, 13.1) & 18.3 (13.3, 24.7) & 12.4 (10.2, 15.0) & \\
+		\hspace{1em}3 & 13.9 (10.8, 17.7) & 9.1 (5.7, 14.1) & 10.7 (8.6, 13.1) & \\
+		\hspace{1em}4 & 10.9 (8.5, 13.9) & 13.8 (9.7, 19.4) & 13.2 (10.9, 16.0) & \\
+		\hspace{1em}5 & 13.5 (10.6, 17.0) & 12.8 (8.4, 19.1) & 13.3 (11.0, 16.1) & \\
+		\hspace{1em}6 & 12.8 (10.1, 16.1) & 8.7 (5.7, 12.9) & 11.5 (9.5, 13.9) & \\
+		\hspace{1em}7 & 14.3 (11.5, 17.6) & 9.5 (6.5, 13.8) & 12.4 (10.2, 15.0) & \\
+		\hspace{1em}8 & 13.2 (10.5, 16.4) & 10.5 (7.4, 14.8) & 12.1 (9.9, 14.6) & \\
+		BMI (kg/m\textasciicircum{}2) & 27.5 (27.1, 27.9) & 27.0 (26.4, 27.6) & 27.4 (27.2, 27.6) & 0.433\\
+		WC (cm) & 93.3 (92.1, 94.5) & 92.9 (90.9, 95.0) & 93.1 (92.3, 93.8) & 0.928\\
+		Smoking status (\%) &  &  &  & \\
+		\hspace{1em}Current & 24.1 (21.5, 27.0) & 30.0 (24.8, 35.8) & 18.8 (17.2, 20.6) & < 0.001\\
+		\hspace{1em}Ex-smoker & 20.0 (17.6, 22.6) & 27.5 (22.4, 33.2) & 25.9 (24.1, 27.7) & \\
+		\hspace{1em}Never & 55.9 (52.7, 59.0) & 42.5 (36.6, 48.7) & 55.3 (53.2, 57.4) & \\
+		Current drinking status (\%) &  &  &  & \\
+		\hspace{1em}Yes & 24.6 (21.7, 27.7) & 18.3 (14.0, 23.6) & 16.8 (15.3, 18.4) & < 0.001\\
+		Hypertension (\%) \textsuperscript{\dag} &  &  &  & \\
+		\hspace{1em}Yes & 25.9 (22.3, 29.9) & 31.8 (25.3, 39.1) & 30.4 (27.9 32.8) & 0.111\\
+		Total energy intake (KJ) &  \Centerstack{ 6713.8 \\ (6575.7, 6851.8)}   &  \Centerstack{ 9256.0 \\ (8850.8, 9661.2)}   &  \Centerstack{7916.9 \\ (7814.0, 8019.9)}     & < 0.001\\
+		Carbohydrate intake (g) & 192.9 (188.5, 197.3) & 275.6 (263.4, 287.8) & 226.9 (223.9, 229.9) & < 0.001\\
+		Carbohydrate
+		percent (\%) \textsuperscript{\ddag} & 45.8 (45.3, 46.4) & 47.4 (46.5, 48.3) & 45.6 (45.3, 45.9) & 0.001\\
+		Glucose (mmol/l) & 5.16 (5.08, 5.23) & 5.09 (5.00, 5.18) & 5.14 (5.10, 5.19) & 0.537\\
+		A1C (\%) & 5.47 (5.42, 5.51) & 5.48 (5.42, 5.54) & 5.49 (5.47. 5.52) & 0.403\\
+		DM \textsuperscript{\S} & 5.9 (4.2, 8.2) & 1.1 (0.2, 5.2) & 4.7 (3.6, 6.0) & 0.053\\
+        Physical activity (hs/day) \textsuperscript{\P}& 1.31 (1.14, 1.49) & 1.82 (1.44, 2.19) & 1.62 (1.49, 1.76) & 0.018\\
+		\bottomrule
+		\multicolumn{5}{l}{\textit{Note: }}\\
+		\multicolumn{5}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey}\\
+		\multicolumn{5}{l}{rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c;}\\
+		\multicolumn{5}{l}{DM, diabetes mellitus; h, hour.}\\
+		\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights,}\\
+		\multicolumn{5}{l}{the others are weighted by individual weights.}\\
+		\multicolumn{5}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
+		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes}\\   
+		\multicolumn{5}{l}{with Bonferroni correction to account for multiple testing across >2 classes.}\\
+		\multicolumn{5}{l}{For categorical variables, differences between latent classes were assessed}\\
+		\multicolumn{5}{l}{using the adjusted Pearson Chi-2 test for survey data.}\\
+		\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic}\\ 
+		\multicolumn{5}{l}{blood pressure >= 90 mmHg, or under}\\
+		\multicolumn{5}{l}{treatment for hypertension.}\\
+		\multicolumn{5}{l}{\textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake}\\
+		\multicolumn{5}{l}{\textsuperscript{\S} DM was defined by A1C > 6.5\%.}\\
+		\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity}\\ 
+		\multicolumn{5}{l}{during the survey.}\\
+	\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}

### 2018-07-28 paper/Tables/2by2Table1.Rmd
tables 1 added

---
title: Tables in the project
mainfont: Arial
fontsize: 11pt
geometry: margin=0.8in
author:  
output: 
  pdf_document: 
    keep_tex: true
    number_sections: true
    latex_engine: xelatex
    # includes:  
    #   in_header: preamble-latex.tex
classoption: a4paper
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/CW2CB2results.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "P value [note]")

dt[28, 1] <- c("Hypertension (%) [note]")
dt[32, 1] <- c("Carbohydrate\npercent (%) [note]")
dt[35, 1] <- c("DM [note]")
dt[36, 1] <- c("Physical\nactivity (hours/day) [note]")

kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Means, percentages, and 95 percent CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", 
      booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey", 
                       "rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c;", 
                       "DM, diabetes mellitus.", 
                       "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights,", 
                       "the others are weighted by individual weights.", 
                       "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes. For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 "DM was defined by A1C > 6.5%.", 
                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey."), 
               notation = "symbol")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/LCGA3Cresults.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "Latent class = 3", "P value [note]")

dt[28, 1] <- c("Hypertension (%) [note]")
dt[32, 1] <- c("Carbohydrate\npercent (%) [note]")
dt[35, 1] <- c("DM [note]")
dt[36, 1] <- c("Physical\nactivity (hours/day) [note]")

kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Means, percentages, and 95 percent CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", 
      booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
   footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey", 
                       "rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c;", 
                       "DM, diabetes mellitus.", 
                       "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights,", 
                       "the others are weighted by individual weights.", 
                       "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across >2 classes. For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 "DM was defined by A1C > 6.5%.", 
                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey."), 
               notation = "symbol")
```

### 2018-07-28 paper/Tables/2by2Table1.tex
tables 1 added

--- 2018-07-28 paper/Chapters/Chapter3.tex
@@
-% Chapter Template
+\documentclass[11pt,a4paper]{article}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+    \setmainfont[]{Arial}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage[margin=0.8in]{geometry}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={Tables in the project},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{5}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-\chapter{Results} % Main chapter title
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
 
-\label{Chapter 3} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+%%% Change title format to be more compact
+\usepackage{titling}
 
-%----------------------------------------------------------------------------------------
-%	SECTION 1
-%----------------------------------------------------------------------------------------
+% Create subtitle command for use in maketitle
+\newcommand{\subtitle}[1]{
+  \posttitle{
+    \begin{center}\large#1\end{center}
+    }
+}
 
-\section{Main Section 1}
+\setlength{\droptitle}{-2em}
+
+  \title{Tables in the project}
+    \pretitle{\vspace{\droptitle}\centering\huge}
+  \posttitle{\par}
+    \author{}
+    \preauthor{}\postauthor{}
+    \date{}
+    \predate{}\postdate{}
+
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage[table]{xcolor}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+
+\begin{document}
+\maketitle
+
+\rowcolors{2}{gray!6}{white}
 
 \begin{table}
-	\rowcolors{2}{gray!6}{white}	
-	\caption{\label{tab:}Means, percentages, and 95\% CIs of the characteristics by multilevel latent class analysis memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}
+
+\caption{\label{tab:unnamed-chunk-1}Means, percentages, and 95 percent CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
 \centering
-		\fontsize{9}{10}\selectfont
-		\begin{tabular}[t]{lccc}
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{llll}
 \hiderowcolors
@@
 \hspace{1em}8 & 12.0 (9.9, 14.5) & 12.8 (10.3, 15.8) & \\
-			BMI (kg/m\textsuperscript{2}) & 27.2 (26.9, 27.5) & 27.7 (27.5, 28.1) & 0.007\\
+BMI (kg/m\textasciicircum{}2) & 27.2 (26.9, 27.5) & 27.7 (27.5, 28.1) & 0.007\\
 WC (cm) & 92.6 (91.9, 93.3) & 94.2 (93.1, 95.2) & 0.013\\
@@
 \end{tabular}
-	\rowcolors{2}{white}{white}
 \end{table}
 
-%-----------------------------------
-%	SUBSECTION 1
-%-----------------------------------
-\subsection{Subsection 1}
-
-%-----------------------------------
-%	SUBSECTION 2
-%-----------------------------------
-
-\subsection{Subsection 2}
-
-%----------------------------------------------------------------------------------------
-%	SECTION 2
-%----------------------------------------------------------------------------------------
-
-\section{Main Section 2}
+\rowcolors{2}{white}{white}
 
@@
 
-	\caption{\label{tab:unnamed-chunk-2}Means, percentages, and 95\% CIs of the characteristics by latent class growth analysis memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}
+\caption{\label{tab:unnamed-chunk-2}Means, percentages, and 95 percent CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
 \centering
 \fontsize{9}{11}\selectfont
-	\begin{tabular}[t]{lcccc}
+\begin{tabular}[t]{lllll}
 \hiderowcolors
@@
 \hspace{1em}Yes & 25.9 (22.3, 29.9) & 31.8 (25.3, 39.1) & 30.4 (27.9 32.8) & 0.111\\
-		Total energy intake (KJ) &  \Centerstack{ 6713.8 \\ (6575.7, 6851.8)}   &  \Centerstack{ 9256.0 \\ (8850.8, 9661.2)}   &  \Centerstack{7916.9 \\ (7814.0, 8019.9)}     & < 0.001\\
+Total energy intake (KJ) & 6713.8 (6575.7, 6851.8) & 9256.0 (8850.8, 9661.2) & 7916.9 (7814.0, 8019.9) & < 0.001\\
 Carbohydrate intake (g) & 192.9 (188.5, 197.3) & 275.6 (263.4, 287.8) & 226.9 (223.9, 229.9) & < 0.001\\
@@
 DM \textsuperscript{\S} & 5.9 (4.2, 8.2) & 1.1 (0.2, 5.2) & 4.7 (3.6, 6.0) & 0.053\\
-        Physical activity (hs/day) \textsuperscript{\P}& 1.31 (1.14, 1.49) & 1.82 (1.44, 2.19) & 1.62 (1.49, 1.76) & 0.018\\
+Physical
+activity (hours/day) \textsuperscript{\P} & 1.31 (1.14, 1.49) & 1.82 (1.44, 2.19) & 1.62 (1.49, 1.76) & 0.018\\
 \bottomrule
@@
 \multicolumn{5}{l}{rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c;}\\
-		\multicolumn{5}{l}{DM, diabetes mellitus; h, hour.}\\
+\multicolumn{5}{l}{DM, diabetes mellitus.}\\
 \multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights,}\\
@@
 \multicolumn{5}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
-		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes}\\   
-		\multicolumn{5}{l}{with Bonferroni correction to account for multiple testing across >2 classes.}\\
-		\multicolumn{5}{l}{For categorical variables, differences between latent classes were assessed}\\
+\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to}\\
+\multicolumn{5}{l}{account for multiple testing across >2 classes. For categorical variables, differences between latent classes were assessed}\\
 \multicolumn{5}{l}{using the adjusted Pearson Chi-2 test for survey data.}\\
-		\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic}\\ 
-		\multicolumn{5}{l}{blood pressure >= 90 mmHg, or under}\\
+\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under}\\
 \multicolumn{5}{l}{treatment for hypertension.}\\
@@
 \multicolumn{5}{l}{\textsuperscript{\S} DM was defined by A1C > 6.5\%.}\\
-		\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity}\\ 
-		\multicolumn{5}{l}{during the survey.}\\
+\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey.}\\
 \end{tabular}
@@
 \rowcolors{2}{white}{white}
+
+\end{document}

### 2018-07-28 results/Summary of survey analysis.Rmd
tables 1 added

@@
 dt[28, 1] <- c("Hypertension (%) [note]")
-dt[32, 1] <- c("Carbohydrate percent (%) [note]")
+dt[32, 1] <- c("Carbohydrate\npercent (%) [note]")
 dt[35, 1] <- c("DM [note]")
+dt[36, 1] <- c("Physical\nactivity (hours/day) [note]")
 
@@
                  "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
-                 "DM was defined by A1C > 6.5%."), 
+                 "DM was defined by A1C > 6.5%.", 
+                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey."), 
                notation = "symbol")

### 2018-07-28 results/posterior analysis.Rmd
tables 1 added

@@
 blood78 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr7-8a_indiv.dta")
+# blood78 <- read_dta("~/Documents/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr7-8a_indiv.dta")
+
 blood56 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr5-6a_indiv.dta")
@@
 BMI78 <- blood78 %>% 
-  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2, MVPAtime, 
+  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2,  
          Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y78, wtn_Y78, wtb_Y78, cluster1, cluster2, cluster3, 
@@
   rename(wti = wti_Y78, wtn = wtn_Y78, wtb = wtb_Y78, drink = dnoft3) %>% 
-  mutate(Years = "7-8") %>% 
+  mutate(Years = "7-8", MVPAtime = NA) %>% 
   replace_with_na(replace = list(bmival = -1, 
@@
                                  drink = -1,
-                                 cigsta3 = -1, 
-                                 MVPAtime = -4)) %>% 
-  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, MVPAtime = -1,
+                                 cigsta3 = -1)) %>% 
+  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1,
                                  drink = -8)) %>% 

### 2018-07-28 paper/Chapters/Chapter3.tex
adding fig level 1 tables for model selection

@@
 \label{Chapter 3} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+
+%
+%\rowcolors{2}{gray!6}{white}
+%
+%\begin{table}
+%%	\captionsetup{font=small}
+%	\caption{\label{tab:MLCA-level1}Level 1 classes comparison in the first step of MLCA. (All data, n = 6155, 24483 data points)}\vspace{-0.3cm}
+%	\centering
+%	\fontsize{9}{10}\selectfont
+%	\begin{tabular}[t]{cccccccc}
+%		\hiderowcolors
+%		\toprule
+%		\Centerstack{N of \\ classes} & \Centerstack{N of free \\ parameters} & log-likelihood & AIC & BIC & aBIC & Entropy & \Centerstack{ Lo-Mendel-Rubin \\ LRT}   \\
+%		\midrule
+%		\showrowcolors
+%		1 & 48 & -372017.3 & 744130.6 & 744519.7 & 744367.1 & -- & --\\
+%		2 & 97 & -368913.7 & 738021.4 & 738807.7 & 738499.4 & 0.777 & < 0.0001\\
+%		3 & 146 & -366665.0 & 733621.9 & 734805.4 & 734341.4 & 0.666 & < 0.0001\\
+%		4 & 195 & -365528.6 & 731447.1 & 733027.7 & 732408.0 & 0.658 & 0.8478\\
+%		5 & 244 & -364901.2 & 730290.3 & 732268.1 & 731492.7 & 0.648 & 0.7602\\
+%		6 & 293 & -363641.8 & 727869.5 & 730244.5 & 729313.4 & 0.701 & 0.7632\\
+%		7 & 342 & -362789.9 & 726263.7 & 729035.9 & 727949.0 & 0.729 & 0.7702\\
+%		8 & 391 & -362047.9 & 724877.9 & 728047.2 & 726804.6 & 0.737 & 0.8261\\
+%		\bottomrule
+%		\multicolumn{8}{l}{\textit{Note: }}\\
+%		\multicolumn{8}{l}{\textbf{Abbreviations:} MLCA, multilevel class analysis; N, number; AIC, Akaike information criterion; BIC, }\\
+%		\multicolumn{8}{l}{Bayesian information criterion; aBIC, adjusted BIC; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin}\\
+%		\multicolumn{8}{l}{LRT, likelihood ratio test comparing $q$ classes models with $q-1$ classes models.}\\
+%	\end{tabular}
+%\end{table}
+%
+%\rowcolors{2}{white}{white}
+
+\begin{figure}
+	%\vspace*{13cm}
+	\centering
+	\includegraphics{Figures/class1mlcalevel1.png}
+	\decoRule
+	\caption[Level 1 Classes in MLCA]{Carbohydrate temporal eating patterns at observational day level.}
+	\label{fig:MLCAfig1}
+\end{figure}
+%%\end{verbatim}
+
+\rowcolors{2}{gray!6}{white}
+\begin{table}
+
+	\caption{\label{tab:}Fit Criteria for Each Model Specification}
+	\centering
+	\fontsize{9}{11}\selectfont
+	\begin{tabular}[t]{lccccc}
+		\hiderowcolors
+		\toprule
+		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Number of level 1 classes} \\
+		\cmidrule(l{2pt}r{2pt}){2-6}
+		Model & 1 class & 2 classes & 3 classes & 4 classes & 5 classes\\
+		\midrule
+		\showrowcolors
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\textbf{Fixed effects model}}\\
+		\hspace{1em}No. of free parameters & 48 & 97 & 146 & 195 & 244\\
+		\hspace{1em}\hspace{1em}Log-likelihood & -372017.293 & -368913.708 & -366664.971 & -365528.553 & -364901.166\\
+		\hspace{1em}\hspace{1em}BIC & 744519.661 & 738807.672 & 734805.379 & 733027.723 & 732268.13\\
+		\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & --- & < 0.0001 & < 0.0001 & 0.8478 & 0.7602\\
+		\hspace{1em}\hspace{1em}Entropy & 1 & 0.777 & 0.666 & 0.658 & 0.648\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\textbf{Random effects model}}\\
+		\hspace{1em}2 between classes &  &  &  &  & \\
+		\hspace{1em}\hspace{1em}No. of free parameters &  & 195 & 293 & 391 & \\
+		\hspace{1em}\hspace{1em}Log-likelihood &  & -363460.153 & -361571.164 & -360297.394 & \\
+		\hspace{1em}\hspace{1em}BIC &  & 728890.925 & 726103.308 & 724546.13 & \\
+		\hspace{1em}\hspace{1em}Entropy &  & 0.834 & 0.798 & 0.784 & \\
+		\hspace{1em}3 between classes &  &  &  &  & \\
+		\hspace{1em}\hspace{1em}No. of free parameters &  & 293 & 440 & 587 & \\
+		\hspace{1em}\hspace{1em}Log-likelihood &  & -360910.13 & -358902.821 & -357404.521 & \\
+		\hspace{1em}\hspace{1em}BIC &  & 724781.241 & 722252.166 & 720741.109 & \\
+		\hspace{1em}\hspace{1em}Entropy &  & 0.824 & 0.793 & 0.824 & \\
+		\hspace{1em}4 between classes &  &  &  &  & \\
+		\hspace{1em}\hspace{1em}No. of free parameters &  & 391 & 587 & 783 & \\
+		\hspace{1em}\hspace{1em}Log-likelihood &  & -358684.859 & -356668.354 & -355235.955 & \\
+		\hspace{1em}\hspace{1em}BIC &  & 720078.473 & 719268.774 & 718384.699 & \\
+		\hspace{1em}\hspace{1em}Entropy &  & 0.816 & 0.817 & 0.806 & \\
+		\bottomrule
+		\multicolumn{6}{l}{\textit{Note: }}\\
+		\multicolumn{6}{l}{Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index;}\\ 
+		\multicolumn{6}{l}{Lo-Mendel-Rubin LRT, likelihood ratio test comparing $q$ classes models with $q-1$ classes models.}\\
+	\end{tabular}
+\end{table}
+\rowcolors{2}{white}{white}
 
@@
 
-\begin{table}
+\begin{table}[h]
 	\rowcolors{2}{gray!6}{white}	
-	\caption{\label{tab:}Means, percentages, and 95\% CIs of the characteristics by multilevel latent class analysis memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}
+	\caption{\label{tab:MLCAtab1}Means, percentages, and 95\% CIs of the characteristics  of carbohydrate temporal eating patterns by MLCA memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}
 		\centering
@@
 			\toprule
-			Variables & Latent class = 1 & Latent class = 2 & P value \textsuperscript{*}\\
+			 & Latent class = 1 & Latent class = 2 & P value \textsuperscript{*}\\
 			\midrule
@@
 			\multicolumn{4}{l}{\textit{Note: }}\\
-			\multicolumn{4}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey}\\ 
-			\multicolumn{4}{l}{rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c;}\\ 
-			\multicolumn{4}{l}{DM, diabetes mellitus.}\\
+			\multicolumn{4}{l}{\textbf{Abbreviations}: CI, confidence intervals; MLCA, multilevel latent class analysis; NDNS RP, national}\\ 
+			\multicolumn{4}{l}{dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; }\\
+			\multicolumn{4}{l}{A1C, haemoglobin A1c;DM, diabetes mellitus; h, hour.}\\
+			\multicolumn{4}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights,}\\
+			\multicolumn{4}{l}{the others are weighted by individual weights.}\\
+			\multicolumn{4}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
 			\multicolumn{4}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights,}\\  
@@
 
-	\caption{\label{tab:unnamed-chunk-2}Means, percentages, and 95\% CIs of the characteristics by latent class growth analysis memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}
+	\caption{\label{tab:LCGAtab1}Means, percentages, and 95\% CIs of the characteristics of carbohydrate temporal eating patterns by LCGA memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}
 	\centering
@@
 		\toprule
-		Variables & Latent class = 1 & Latent class = 2 & Latent class = 3 & P value \textsuperscript{*}\\
+		 & Latent class = 1 & Latent class = 2 & Latent class = 3 & P value \textsuperscript{*}\\
 		\midrule
@@
 		\multicolumn{5}{l}{\textit{Note: }}\\
-		\multicolumn{5}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey}\\
-		\multicolumn{5}{l}{rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c;}\\
-		\multicolumn{5}{l}{DM, diabetes mellitus; h, hour.}\\
+		\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; LCGA, latent class growth analysis; NDNS RP, national}\\ 
+		\multicolumn{5}{l}{dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; }\\
+		\multicolumn{5}{l}{A1C, haemoglobin A1c;DM, diabetes mellitus; h, hour.}\\
 		\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights,}\\

### 2018-07-28 paper/Tables/2by2Table1.Rmd
adding fig level 1 tables for model selection

@@
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
+# library(kableExtra)
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/ndns_level1only.csv", header = T)
+names(dt) <- c("N of classes", "N of free parameters","log-likelihood",  "AIC", "BIC", "aBIC", "Entropy", "Lo-Mendel-Rubin LRT")
+dt[1,8] <- "--"
+dt[2,8] <- "< 0.0001"
+dt[3,8] <- "< 0.0001"
+kable(dt, digits = 3, row.names = FALSE, align = "c",
+              format = "latex", caption = "Level 1 class selection. (All data, n = 6155, 24483 data points)", 
+      booktabs = T,linesep = "") %>%
+ kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+# row_spec(c(2,3), bold = T, color = "white", background = "#D7261E") %>% 
+  footnote(general = c("Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC;" ,
+                       "Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with", 
+                       "q-1 classes models."))
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE}
 dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/LCGA3Cresults.csv", header = T, row.names = NULL, colClasses = "character")
@@
 ```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Mixed_50_paper.csv", header = T)
+names(dt) <- c("Model", "1 class", "2 classes",  "3 classes", "4 classes", "5 classes")
+dt[is.na(dt)] <- ""
+# library(formattable)
+
+kable(dt, digits = 3, row.names = FALSE, align = "c",
+      format = "latex", caption = "Fit Criteria for Each Model Specification", 
+      booktabs = T, linesep = "") %>% 
+  kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+  add_header_above(c(" ", "Number of level 1 classes" = 5)) %>% 
+  group_rows("Fixed effects model", 1, 5) %>%
+  group_rows("Random effects model", 6, 20) %>%
+  add_indent(c(2:5,7:10,12:15,17:20)) %>% 
+  footnote(general = c("Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models."))
+
+```

### 2018-07-28 paper/Tables/2by2Table1.tex
adding fig level 1 tables for model selection

@@
 
-\caption{\label{tab:unnamed-chunk-2}Means, percentages, and 95 percent CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
+\caption{\label{tab:unnamed-chunk-2}Level 1 class selection. (All data, n = 6155, 24483 data points)}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{cccccccc}
+\hiderowcolors
+\toprule
+N of classes & N of free parameters & log-likelihood & AIC & BIC & aBIC & Entropy & Lo-Mendel-Rubin LRT\\
+\midrule
+\showrowcolors
+1 & 48 & -372017.3 & 744130.6 & 744519.7 & 744367.1 & -- & --\\
+2 & 97 & -368913.7 & 738021.4 & 738807.7 & 738499.4 & 0.777 & < 0.0001\\
+3 & 146 & -366665.0 & 733621.9 & 734805.4 & 734341.4 & 0.666 & < 0.0001\\
+4 & 195 & -365528.6 & 731447.1 & 733027.7 & 732408.0 & 0.658 & 0.8478\\
+5 & 244 & -364901.2 & 730290.3 & 732268.1 & 731492.7 & 0.648 & 0.7602\\
+6 & 293 & -363641.8 & 727869.5 & 730244.5 & 729313.4 & 0.701 & 0.7632\\
+7 & 342 & -362789.9 & 726263.7 & 729035.9 & 727949.0 & 0.729 & 0.7702\\
+8 & 391 & -362047.9 & 724877.9 & 728047.2 & 726804.6 & 0.737 & 0.8261\\
+\bottomrule
+\multicolumn{8}{l}{\textit{Note: }}\\
+\multicolumn{8}{l}{Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC;}\\
+\multicolumn{8}{l}{Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with}\\
+\multicolumn{8}{l}{q-1 classes models.}\\
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-3}Means, percentages, and 95 percent CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
 \centering
@@
 
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-4}Fit Criteria for Each Model Specification}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{cccccc}
+\hiderowcolors
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{6}{c}{Number of level 1 classes} \\
+\cmidrule(l{2pt}r{2pt}){2-7}
+Model & 1 class & 2 classes & 3 classes & 4 classes & 5 classes\\
+\midrule
+\showrowcolors
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Fixed effects model}}\\
+\hspace{1em}No. of free parameters & 48 & 97 & 146 & 195 & 244\\
+\hspace{1em}\hspace{1em}Log-likelihood & -372017.293 & -368913.708 & -366664.971 & -365528.553 & -364901.166\\
+\hspace{1em}\hspace{1em}BIC & 744519.661 & 738807.672 & 734805.379 & 733027.723 & 732268.13\\
+\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & --- & < 0.0001 & < 0.0001 & 0.8478 & 0.7602\\
+\hspace{1em}\hspace{1em}Entropy & 1 & 0.777 & 0.666 & 0.658 & 0.648\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Random effects model}}\\
+\hspace{1em}2 between classes &  &  &  &  & \\
+\hspace{1em}\hspace{1em}No. of free parameters &  & 195 & 293 & 391 & \\
+\hspace{1em}\hspace{1em}Log-likelihood &  & -363460.153 & -361571.164 & -360297.394 & \\
+\hspace{1em}\hspace{1em}BIC &  & 728890.925 & 726103.308 & 724546.13 & \\
+\hspace{1em}\hspace{1em}Entropy &  & 0.834 & 0.798 & 0.784 & \\
+\hspace{1em}3 between classes &  &  &  &  & \\
+\hspace{1em}\hspace{1em}No. of free parameters &  & 293 & 440 & 587 & \\
+\hspace{1em}\hspace{1em}Log-likelihood &  & -360910.13 & -358902.821 & -357404.521 & \\
+\hspace{1em}\hspace{1em}BIC &  & 724781.241 & 722252.166 & 720741.109 & \\
+\hspace{1em}\hspace{1em}Entropy &  & 0.824 & 0.793 & 0.824 & \\
+\hspace{1em}4 between classes &  &  &  &  & \\
+\hspace{1em}\hspace{1em}No. of free parameters &  & 391 & 587 & 783 & \\
+\hspace{1em}\hspace{1em}Log-likelihood &  & -358684.859 & -356668.354 & -355235.955 & \\
+\hspace{1em}\hspace{1em}BIC &  & 720078.473 & 719268.774 & 718384.699 & \\
+\hspace{1em}\hspace{1em}Entropy &  & 0.816 & 0.817 & 0.806 & \\
+\bottomrule
+\multicolumn{6}{l}{\textit{Note: }}\\
+\multicolumn{6}{l}{Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.}\\
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
 \end{document}

### 2018-07-28 paper/main.tex
aims and objectives
strata weighting etc. added
tables 1 added
adding fig level 1 tables for model selection

@@
 %consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
-]{MastersDoctoralThesis} % The class file specifying the document structure
+table]{MastersDoctoralThesis} % The class file specifying the document structure
 
@@
 \usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
+
+%\usepackage[table]{xcolor}
+\usepackage{colortbl} % to use colors for tables
+\usepackage[usestackEOL]{stackengine} %to change lines within a cell in the table
+\usepackage{caption} % to change the font of the table titles
+
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
+\cleardoublepage\makeatletter\@openrightfalse\makeatother
 
@@
 \textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
-\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
+\textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex \\
+%\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
 \textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
+\textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
 \textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
 \textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
+\textbf{HbA1c} & \textbf{H}emoglobin \textbf{A1c}: Glycated hemoglobin \\
 \textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
-\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
+\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
+%\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
 \textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
@@
 \textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
+\textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
 \end{abbreviations}

### 2018-07-28 paper/Figures/Figureforpaper.R

@@ -1,0 +1,177 @@
+library(readr)
+library(tidyverse)
+
+CW2CB2 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/50NDNS_CW2CB2.txt",
+                      col_names = FALSE)
+
+names(CW2CB2) <- c("H0",
+                   "H1",
+                   "H2",
+                   "H3",
+                   "H4",
+                   "H5",
+                   "H6",
+                   "H7",
+                   "H8",
+                   "H9",
+                   "H10",
+                   "H11",
+                   "H12",
+                   "H13",
+                   "H14",
+                   "H15",
+                   "H16",
+                   "H17",
+                   "H18",
+                   "H19",
+                   "H20",
+                   "H21",
+                   "H22",
+                   "H23",
+                   "ID_DAY",
+                   "AGE",
+                   "SEX",
+                   "CPROB1",
+                   "CPROB2",
+                   "CPROB3",
+                   "CPROB4",
+                   # "CPROB5",
+                   # "CPROB6",
+                   "CB",
+                   "CW",
+                   "MLCJOINT",
+                   "ID")
+
+pp <- CW2CB2 %>% 
+  group_by(CW) %>% 
+  summarise(H0_0 = sum(H0 == 0)/length(H0), 
+            H0_1 = sum(H0 == 1)/length(H0), 
+            H0_2 = sum(H0 == 2)/length(H0),
+            H1_0 = sum(H1 == 0)/length(H1),
+            H1_1 = sum(H1 == 1)/length(H1), 
+            H1_2 = sum(H1 == 2)/length(H1),
+            H2_0 = sum(H2 == 0)/length(H2),
+            H2_1 = sum(H2 == 1)/length(H2), 
+            H2_2 = sum(H2 == 2)/length(H2),
+            H3_0 = sum(H3 == 0)/length(H3),
+            H3_1 = sum(H3 == 1)/length(H3), 
+            H3_2 = sum(H3 == 2)/length(H3),
+            H4_0 = sum(H4 == 0)/length(H4),
+            H4_1 = sum(H4 == 1)/length(H4), 
+            H4_2 = sum(H4 == 2)/length(H4),
[…]

### 2018-07-29 results/Summary of all the analysis and links.Rmd
slots anlysis

---
title: "Summary of the analyses we have done"
author: "Chaochen Wang"
date: "29 July 2018, Updated at `r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
editor_options: 
  chunk_output_type: console
---

# Carbohydrate contribution of energy intake cut-off = 50%

- In these analyses, within each **hour of the day/time slot** of the day carbohydrates intake was defined as: 
    - not eating; 
    - eating and carbohydrates contributed less than 50% of energy;
    - eating and carbohydrates contributed higher or equal to 50% of energy.

## by 24 hours

### Multilevel LCA

[Rpubs link: http://Rpubs.com/winterwang/CW2CB3](http://Rpubs.com/winterwang/CW2CB3):

- **Proposed solutions:** 
    - 2 by 2 multilevel LCA solutions (Fig 3.1 & 3.2); 
        - **Type 1 days**: always having lunch at 1 pm, **high carb between 7-10 am, and 3-4 pm**; 
        - **Type 2 days**: probability of not having lunch close to 0.5, higher probabitlity of low carb intake than high carb.
    - Proportions of 2 types of days in person level classes: 
        - **Class 1 persons**: 52.5%, and 47.5%; 
        - **Class 2 persons**: 94.8% and 5.2% -> always have type 1 days, regularly having more food.

### Latent class growth analysis (LCGA)

[Rpubs link: http://Rpubs.com/winterwang/LGCA](http://Rpubs.com/winterwang/LGCA)

- Proposed solutions: Fig 3.
    - 3 classes: 
        - Class 1 (28.97%): inactive eaters (French style), high carb breakfast, low carb lunch and dinner, no snacks; 
        - Class 2 (6.11%):  active eaters, high carb intake through out the days; 
        - Class 3 (64.92%): typical British style eaters, high carb breakfast, morning snack, afternoon snack, and low carb lunch and dinner.

## by 7 time slots

- Time slots are defined as: 
    - **Breakfast:** 6 am to 9 am; 
    - **Morning snack:** 9 am to 12 noon; 
    - **Lunch:** 12 noon to 2 pm; 
    - **Afternoon snack:** 2 pm to 5 pm; 
    - **Dinner:** 5 pm to 8 pm; 
    - **Before bedtime snack:** 8 pm to 10 pm; 
    - **Midnight food:** 10pm to 6 am;

### Multilevel LCA

[Rpubs link: http://Rpubs.com/winterwang/NDNS7timeslots_multilevel](http://Rpubs.com/winterwang/NDNS7timeslots_multilevel)

- Proposed solutions: 
    - 3 by 3 multilevel LCA solutions (Fig 3.1 and 3.3): 
        - **Type 1 days**: **high carb** at breakfast, afternoon snack, and before bedtime snack;
        - **Type 2 days**: low carb through out the day, **high probability of not having breakfast**;
        - **Type 3 days**: high carb breakfast, low carb lunch and dinner, **not eating at night**.
    - Proportions of three types of days in person level classes:
        - **Class 1 persons (28.2%)**:  62.3%, 20.5%, and 17.2%; 
        - **Class 2 persons (28.9%)**:  40.0%, 42.0%, and 18.0%;
        - **Class 3 persons (42.8%)**:  25.8%, 50.0%, and 24.1%.

### Latent class growth analysis (LCGA)

[Rpubs link: http://Rpubs.com/winterwang/NDNSslots](http://Rpubs.com/winterwang/NDNSslots)

- Proposed solutions: Fig 4.
    - 3 classes: 
        - Class 1 (67.2%): high carb breakfast, low carb lunch and dinner; 
        - Class 2 (21.9%): high prob of skipping breakfast, not eating at night; 
        - Class 3 (10.9%): high carb all four days, snacking a alot.

# Carb-fibre ratio cut-off value = 0.1

- In these analyses, within each **hour of the day/time slot** of the day carbohydrates intake was defined as: 
    - not eating; 
    - eating and fibre-carbo ratio < 0.1; 
    - eating and fibre-carbo ratio > 0.1;
    - eating and no fibre or carbo.

## by 24 hours

<!-- ### Multilevel LCA -->

### Latent class growth analysis

[Rpubs link: http://rpubs.com/winterwang/FBCB](http://rpubs.com/winterwang/FBCB)

- Proposed solutions: Fig 3.
    - 3 classes: 
        - Class 1 (25.2%): inactive eaters (French style) no snacks; 
        - Class 2 (67.7%):  typical British style eaters;
        - Class 3 (7.1%):  active eaters

The probabilities of having food without any carb or fibre are low. This analysis is quite similar with LCGA conducted for the carb >=50% or <50%.

<!-- ## by 7 time slots -->

<!-- ### Multilevel LCA -->

<!-- ### Latent class growth analysis -->

### 2018-07-29 results/Timeslots/multilevel.Rmd
slots anlysis

---
title: "NDNS multilevel carb_50, 7 time slots"
author: "Chaochen Wang"
date: "29 July 2018, Updated at `r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
editor_options: 
  chunk_output_type: console
---

# Level 1 classes selection

- In this analysis, within each **time slot** of the day carbohydrates intake was defined as: 
    - not eating; 
    - eating and carbohydrates contributed less than 50% of energy;
    - eating and carbohydrates contributed higher or equal to 50% of energy.

- Time slots are defined as: 
    - **Breakfast:** 6 am to 9 am; 
    - **Morning snack:** 9 am to 12 noon; 
    - **Lunch:** 12 noon to 2 pm; 
    - **Afternoon snack:** 2 pm to 5 pm; 
    - **Dinner:** 5 pm to 8 pm; 
    - **Before bedtime snack:** 8 pm to 10 pm; 
    - **Midnight food:** 10pm to 6 am;

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(RColorBrewer)
library(plyr)
library(tidyverse)
library(dplyr)
library(epiDisplay)
library(scales)
library(readr)
rm(list=ls(all=TRUE))
# load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")

library(kableExtra)
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Level1_7slots.csv", header = T, colClasses = "character")
names(dt) <- c("N of classes", "N of free parameters","log-likelihood",  "AIC", "BIC", "aBIC", "Entropy", "Lo-Mendel-Rubin LRT")
# dt[1,8] <- "--"
dt[2,8] <- "< 0.0001"
dt[4,8] <- "< 0.0001"
dt[5,8] <- "< 0.0001"
kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Level 1 class selection. (All data, n = 6155, 24483 data points)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  # row_spec(c(2,3), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.")
```

## Fit information for each model (combination of level 1 and level 2 classes)

```{r echo=FALSE}
rm(list=ls(all=TRUE))
# load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")

library(kableExtra)
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Mixed_7slots.csv", header = T)
names(dt) <- c("Model", "1 class","2 classes",  "3 classes", "4 classes", "5 classes", "6 classes")
dt[is.na(dt)] <- ""
# library(formattable)
dt %>% 
  # mutate(
  #   `2 classes` = cell_spec(`2 classes`, color = ifelse())) %>% 
  kable(escape = F, 
        digits = 3, row.names = FALSE, align = "l",
        format = "html", caption = "Models Specification") %>% 
  add_header_above(c(" ", "Number of level 1 classes" = 6)) %>% 
  group_rows("Fixed effects model", 1, 5) %>%
  group_rows("Random effects model", 6, 20) %>%
  add_indent(c(2:5,7:10,12:15,17:20)) %>% 
  kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  #row_spec(c(2,3), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.")
```

# (CW = 2) Level 1 latent classes

## Visualisation of level 1 latent classes

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

CW2CB2 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW2CB2.txt",
                         col_names = FALSE)

names(CW2CB2) <- c("Breakfast", 
                   "Morning.snack",
                   "Lunch",
                   "Afternoon.snack",
                   "Dinner",
                   "Before.bedtime.snack",
                   "Midnight.food",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      # "CPROB5",
                      # "CPROB6",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")

pp <- CW2CB2 %>% 
  group_by(CW) %>% 
  summarise(Breakfast_0 = sum(Breakfast == 0)/length(Breakfast), 
            Breakfast_1 = sum(Breakfast == 1)/length(Breakfast), 
            Breakfast_2 = sum(Breakfast == 2)/length(Breakfast),
            Morning.snack_0 = sum(Morning.snack == 0)/length(Morning.snack),
            Morning.snack_1 = sum(Morning.snack == 1)/length(Morning.snack), 
            Morning.snack_2 = sum(Morning.snack == 2)/length(Morning.snack),
            Lunch_0 = sum(Lunch == 0)/length(Lunch),
            Lunch_1 = sum(Lunch == 1)/length(Lunch), 
            Lunch_2 = sum(Lunch == 2)/length(Lunch),
            Afternoon.snack_0 = sum(Afternoon.snack == 0)/length(Afternoon.snack),
            Afternoon.snack_1 = sum(Afternoon.snack == 1)/length(Afternoon.snack), 
            Afternoon.snack_2 = sum(Afternoon.snack == 2)/length(Afternoon.snack),
            Dinner_0 = sum(Dinner == 0)/length(Dinner),
            Dinner_1 = sum(Dinner == 1)/length(Dinner), 
            Dinner_2 = sum(Dinner == 2)/length(Dinner),
            Before.bedtime.snack_0 = sum(Before.bedtime.snack == 0)/length(Before.bedtime.snack),
            Before.bedtime.snack_1 = sum(Before.bedtime.snack == 1)/length(Before.bedtime.snack), 
            Before.bedtime.snack_2 = sum(Before.bedtime.snack == 2)/length(Before.bedtime.snack),
            Midnight.food_0 = sum(Midnight.food == 0)/length(Midnight.food),
            Midnight.food_1 = sum(Midnight.food == 1)/length(Midnight.food), 
            Midnight.food_2 = sum(Midnight.food == 2)/length(Midnight.food))

pp_long <- pp %>% 
  gather(Hour, Prob, -CW) %>% 
  separate(Hour, into = c("Slots", "Carbo"), sep = "_")

pp_long$Slots <- factor(pp_long$Slots, levels = c("Breakfast", 
                   "Morning.snack",
                   "Lunch",
                   "Afternoon.snack",
                   "Dinner",
                   "Before.bedtime.snack",
                   "Midnight.food"))
```

```{r echo=FALSE, fig.height=8, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
library(ggthemr)
ggthemr("fresh", layout = "scientific")
library(ggplot2)

ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Slots, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
    theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 1 days", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Slots, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
      theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 2 days", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

```

## Visualisation of level 2 latent classes (CB = 2)

```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}

# ndnsNNN <- read_csv("results/ndnsNNN.dat")
# dt <- ndnsNNN[, c(2,5)]
# names(dt) <- c("ID_DAY", "DayofWeek")
# 
# 
# CW2CB2 <- CW2CB2 %>% 
#   left_join(dt, by = "ID_DAY")
#

chart.data <- CW2CB2 %>% 
  group_by(CB, CW) %>% 
  tally %>% 
  group_by(CB) %>% 
  mutate(pct = n/sum(n))

chart.data <- ddply(chart.data, .(CB),
                     transform, pos = cumsum(pct) - (0.5 * pct))

chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"), 
                        labels = c("Class 2 days", "Class 1 days"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"), 
                        labels = c("Individual Class 1\n(56.3%)",  "Individual class 2\n(43.7%)"))

library(ggthemr)
ggthemr("dust", layout = "scientific")
ggplot() + 
  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
           stat="identity") + 
  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
            size=4, colour="white", family="Atlas Grotesk Medium") + 
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank(), 
        axis.title = element_text(size = 18), 
        axis.text = element_text(size = 15), 
        axis.line = element_line(colour = "black"), 
        plot.title=element_text(family="Atlas Grotesk Medium"),
        text=element_text(family="Atlas Grotesk Light")) + 
  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
  scale_y_continuous(labels=percent)
```

## Visualisation of level 2 latent classes (CB = 3)

```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}

CW2CB3 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW2CB3.txt",
                         col_names = FALSE)

names(CW2CB3) <- c("Breakfast", 
                   "Morning.snack",
                   "Lunch",
                   "Afternoon.snack",
                   "Dinner",
                   "Before.bedtime.snack",
                   "Midnight.food",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      "CPROB5",
                      "CPROB6",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")

chart.data <- CW2CB3 %>% 
  group_by(CB, CW) %>% 
  tally %>% 
  group_by(CB) %>% 
  mutate(pct = n/sum(n))

# chart.data$CW[chart.data$CW == 1] <- 0 
# chart.data$CW[chart.data$CW == 3] <- 1 
# chart.data$CW[chart.data$CW == 0] <- 3

chart.data <- chart.data[order(chart.data$CB, chart.data$CW),]
chart.data <- ddply(chart.data, .(CB), 
                    transform, pos = cumsum(pct) - (0.5 * pct))

chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"), 
                        labels = c("Class 2 days", "Class 1 days"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"), 
                        labels = c("Individual\nclass 1\n(42.4%)",  "Individual\nclass 2\n(29.5%)", 
                                   "Individual\nclass 3\n(28.1%)"))

library(ggthemr)
ggthemr("dust", layout = "scientific")
ggplot() + 
  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
           stat="identity") + 
  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
            size=4, colour="white", family="Atlas Grotesk Medium") + 
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank(), 
        axis.title = element_text(size = 18), 
        axis.text = element_text(size = 15), 
        axis.line = element_line(colour = "black"), 
        plot.title=element_text(family="Atlas Grotesk Medium"),
        text=element_text(family="Atlas Grotesk Light")) + 
  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
  scale_y_continuous(labels=percent)
```

## Visualisation of level 2 latent classes (CB = 4)

```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}

CW2CB4 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW2CB4.txt",
                         col_names = FALSE)

names(CW2CB4) <- c("Breakfast", 
                   "Morning.snack",
                   "Lunch",
                   "Afternoon.snack",
                   "Dinner",
                   "Before.bedtime.snack",
                   "Midnight.food",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      "CPROB5",
                      "CPROB6",
                      "CPROB7",
                      "CPROB8",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")

chart.data <- CW2CB4 %>% 
  group_by(CB, CW) %>% 
  tally %>% 
  group_by(CB) %>% 
  mutate(pct = n/sum(n))

# chart.data$CW[chart.data$CW == 1] <- 0 
# chart.data$CW[chart.data$CW == 3] <- 1 
# chart.data$CW[chart.data$CW == 0] <- 3

chart.data <- chart.data[order(chart.data$CB, chart.data$CW),]
chart.data <- ddply(chart.data, .(CB), 
                    transform, pos = cumsum(pct) - (0.5 * pct))

chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"), 
                        labels = c("Class 2 days", "Class 1 days"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3", "4"), 
                        labels = c("Individual\nclass 1\n(23.4%)",  "Individual\nclass 2\n(23.7%)", 
                                   "Individual\nclass 3\n(28.9%)", "Individual\nclass 4\n(23.9%)"))

library(ggthemr)
ggthemr("dust", layout = "scientific")
ggplot() + 
  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
           stat="identity") + 
  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
            size=4, colour="white", family="Atlas Grotesk Medium") + 
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank(), 
        axis.title = element_text(size = 18), 
        axis.text = element_text(size = 15), 
        axis.line = element_line(colour = "black"), 
        plot.title=element_text(family="Atlas Grotesk Medium"),
        text=element_text(family="Atlas Grotesk Light")) + 
  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
  scale_y_continuous(labels=percent)
```

# (CW = 3) Level 1 latent classes

## Visualisation of level 1 latent classes

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

CW3CB2 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB2.txt",
                         col_names = FALSE)

names(CW3CB2) <- c("Breakfast", 
                   "Morning.snack",
                   "Lunch",
                   "Afternoon.snack",
                   "Dinner",
                   "Before.bedtime.snack",
                   "Midnight.food",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      "CPROB5",
                      "CPROB6",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")

pp <- CW3CB2 %>% 
  group_by(CW) %>% 
  summarise(Breakfast_0 = sum(Breakfast == 0)/length(Breakfast), 
            Breakfast_1 = sum(Breakfast == 1)/length(Breakfast), 
            Breakfast_2 = sum(Breakfast == 2)/length(Breakfast),
            Morning.snack_0 = sum(Morning.snack == 0)/length(Morning.snack),
            Morning.snack_1 = sum(Morning.snack == 1)/length(Morning.snack), 
            Morning.snack_2 = sum(Morning.snack == 2)/length(Morning.snack),
            Lunch_0 = sum(Lunch == 0)/length(Lunch),
            Lunch_1 = sum(Lunch == 1)/length(Lunch), 
            Lunch_2 = sum(Lunch == 2)/length(Lunch),
            Afternoon.snack_0 = sum(Afternoon.snack == 0)/length(Afternoon.snack),
            Afternoon.snack_1 = sum(Afternoon.snack == 1)/length(Afternoon.snack), 
            Afternoon.snack_2 = sum(Afternoon.snack == 2)/length(Afternoon.snack),
            Dinner_0 = sum(Dinner == 0)/length(Dinner),
            Dinner_1 = sum(Dinner == 1)/length(Dinner), 
            Dinner_2 = sum(Dinner == 2)/length(Dinner),
            Before.bedtime.snack_0 = sum(Before.bedtime.snack == 0)/length(Before.bedtime.snack),
            Before.bedtime.snack_1 = sum(Before.bedtime.snack == 1)/length(Before.bedtime.snack), 
            Before.bedtime.snack_2 = sum(Before.bedtime.snack == 2)/length(Before.bedtime.snack),
            Midnight.food_0 = sum(Midnight.food == 0)/length(Midnight.food),
            Midnight.food_1 = sum(Midnight.food == 1)/length(Midnight.food), 
            Midnight.food_2 = sum(Midnight.food == 2)/length(Midnight.food))

pp_long <- pp %>% 
  gather(Hour, Prob, -CW) %>% 
  separate(Hour, into = c("Slots", "Carbo"), sep = "_")

pp_long$Slots <- factor(pp_long$Slots, levels = c("Breakfast", 
                   "Morning.snack",
                   "Lunch",
                   "Afternoon.snack",
                   "Dinner",
                   "Before.bedtime.snack",
                   "Midnight.food"))
```

```{r echo=FALSE, fig.height=8, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
library(ggthemr)
ggthemr("fresh", layout = "scientific")
library(ggplot2)

ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Slots, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
    theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 1 days", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Slots, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
      theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 2 days", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 3, ], aes(y = Prob, x=Slots, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
      theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 3 days", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

```

## Visualisation of level 2 latent classes (CB = 2)

```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}

# ndnsNNN <- read_csv("results/ndnsNNN.dat")
# dt <- ndnsNNN[, c(2,5)]
# names(dt) <- c("ID_DAY", "DayofWeek")
# 
# 
# CW2CB2 <- CW2CB2 %>% 
#   left_join(dt, by = "ID_DAY")
#

chart.data <- CW3CB2 %>% 
  group_by(CB, CW) %>% 
  tally %>% 
  group_by(CB) %>% 
  mutate(pct = n/sum(n))

chart.data <- ddply(chart.data, .(CB),
                     transform, pos = cumsum(pct) - (0.5 * pct))

chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"), 
                        labels = c("Class 3 days", "Class 2 days", "Class 1 days"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"), 
                        labels = c("Individual Class 1\n(35.3%)",  "Individual class 2\n(64.7%)"))

library(ggthemr)
ggthemr("dust", layout = "scientific")
ggplot() + 
  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
           stat="identity") + 
  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
            size=4, colour="white", family="Atlas Grotesk Medium") + 
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank(), 
        axis.title = element_text(size = 18), 
        axis.text = element_text(size = 15), 
        axis.line = element_line(colour = "black"), 
        plot.title=element_text(family="Atlas Grotesk Medium"),
        text=element_text(family="Atlas Grotesk Light")) + 
  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
  scale_y_continuous(labels=percent)
```

## Visualisation of level 2 latent classes (CB = 3)

```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}

CW3CB3 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB3.txt",
                         col_names = FALSE)

names(CW3CB3) <- c("Breakfast", 
                   "Morning.snack",
                   "Lunch",
                   "Afternoon.snack",
                   "Dinner",
                   "Before.bedtime.snack",
                   "Midnight.food",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      "CPROB5",
                      "CPROB6",
                      "CPROB7",
                      "CPROB8",
                      "CPROB9",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")

chart.data <- CW3CB3 %>% 
  group_by(CB, CW) %>% 
  tally %>% 
  group_by(CB) %>% 
  mutate(pct = n/sum(n))

# chart.data$CW[chart.data$CW == 1] <- 0 
# chart.data$CW[chart.data$CW == 3] <- 1 
# chart.data$CW[chart.data$CW == 0] <- 3

chart.data <- chart.data[order(chart.data$CB, chart.data$CW),]
chart.data <- ddply(chart.data, .(CB), 
                    transform, pos = cumsum(pct) - (0.5 * pct))

chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"), 
                        labels = c("Class 3 days", "Class 2 days", "Class 1 days"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"), 
                        labels = c("Individual\nclass 1\n(28.2%)",  "Individual\nclass 2\n(28.9%)", 
                                   "Individual\nclass 3\n(42.8%)"))

library(ggthemr)
ggthemr("dust", layout = "scientific")
ggplot() + 
  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
           stat="identity") + 
  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
            size=4, colour="white", family="Atlas Grotesk Medium") + 
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank(), 
        axis.title = element_text(size = 18), 
        axis.text = element_text(size = 15), 
        axis.line = element_line(colour = "black"), 
        plot.title=element_text(family="Atlas Grotesk Medium"),
        text=element_text(family="Atlas Grotesk Light")) + 
  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
  scale_y_continuous(labels=percent)
```

## Visualisation of level 2 latent classes (CB = 4)

```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}

CW3CB4 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB4.txt",
                         col_names = FALSE)

names(CW3CB4) <- c("Breakfast", 
                   "Morning.snack",
                   "Lunch",
                   "Afternoon.snack",
                   "Dinner",
                   "Before.bedtime.snack",
                   "Midnight.food",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      "CPROB5",
                      "CPROB6",
                      "CPROB7",
                      "CPROB8",
                      "CPROB9",
                      "CPROB10",
                      "CPROB11",
                      "CPROB12",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")

chart.data <- CW3CB4 %>% 
  group_by(CB, CW) %>% 
  tally %>% 
  group_by(CB) %>% 
  mutate(pct = n/sum(n))

# chart.data$CW[chart.data$CW == 1] <- 0 
# chart.data$CW[chart.data$CW == 3] <- 1 
# chart.data$CW[chart.data$CW == 0] <- 3

chart.data <- chart.data[order(chart.data$CB, chart.data$CW),]
chart.data <- ddply(chart.data, .(CB), 
                    transform, pos = cumsum(pct) - (0.5 * pct))

chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"), 
                        labels = c("Class 3 days", "Class 2 days", "Class 1 days"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3", "4"), 
                        labels = c("Individual\nclass 1\n(21.8%)",  "Individual\nclass 2\n(21.1%)", 
                                   "Individual\nclass 3\n(33.8%)", "Individual\nclass 4\n(23.3%)"))

library(ggthemr)
ggthemr("dust", layout = "scientific")
ggplot() + 
  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
           stat="identity") + 
  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
            size=4, colour="white", family="Atlas Grotesk Medium") + 
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank(), 
        axis.title = element_text(size = 18), 
        axis.text = element_text(size = 15), 
        axis.line = element_line(colour = "black"), 
        plot.title=element_text(family="Atlas Grotesk Medium"),
        text=element_text(family="Atlas Grotesk Light")) + 
  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
  scale_y_continuous(labels=percent)
```

### 2018-07-30 paper/Chapters/Chapter2.tex
LCGA method adding, 7 slots results updated

@@
 In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.
+\vspace{-0.3cm}
 
@@
 
+%LCGA is a statistical approach that models patterns in longitudinal data by classifying individuals into unobserved latent classes with more homogeneous patterns.
+LCGA is a special type of Growth Mixture Models (GMM), in which the variance of latent slope and intercept are fixed to zero within class, and allowed to vary only across classes.
+LCGA assumes that all individual growth trajectories within classes are homogeneous.
+
+LCGA is a semi‐parametric technique used to identify distinct subgroups of individuals following a similar pattern of change over time on a given variable.
+The analysis identifies distinct subgroups of individuals following a distinct pattern of change over time.
+LCGA is a special type of Growth Mixture Models (GMM), in which the variance of latent slope and intercept are fixed to zero within class, and allowed to vary only across classes.
+LCGA assumes that all individual growth trajectories within classes are homogeneous.
+
+In the NDNS RP data context, we considered a latent categorical variable $c_i$ representing the unobserved subpopulation membership (latent class variable) for participant $i, (c_i = 1,2,\cdots K)$.
+
 \section{Association between latent classes and other variables}\vspace{-0.3cm}

### 2018-07-30 results/Summary of all the analysis and links.Rmd
LCGA method adding, 7 slots results updated

@@
 author: "Chaochen Wang"
-date: "29 July 2018, Updated at `r Sys.Date()`"
+date: "29 July 2018 created, `r Sys.Date()` updated"
 output: 
@@
 
+### Table 1 for latent classes identified (24 hours)
+
+[Rpubs link:http://rpubs.com/winterwang/NDNStable1](http://rpubs.com/winterwang/NDNStable1)
+
 ## by 7 time slots
@@
     - Proportions of three types of days in person level classes:
-        - **Class 1 persons (28.2%)**:  62.3%, 20.5%, and 17.2%; 
+        - **Class 1 persons (28.2%)**:  62.3%, 20.5%, and 17.2%; -> higher BMI, WC, more DM than the other two groups
         - **Class 2 persons (28.9%)**:  40.0%, 42.0%, and 18.0%;
@@
         - Class 2 (21.9%): high prob of skipping breakfast, not eating at night; 
-        - Class 3 (10.9%): high carb all four days, snacking a alot.
+        - Class 3 (10.9%): high carb all four days, snacking frequently. -> also high physical activity, high prob in drinking and smoking
+
+### Table 1 for latent classes identified (7 time slots)
+
+[Rpubs link:http://rpubs.com/winterwang/tab1slots7](http://rpubs.com/winterwang/tab1slots7)
 

### 2018-07-30 results/Summary of survey analysis.Rmd
LCGA method adding, 7 slots results updated

@@
 ---
-title: "Summary of Survey Analysis"
+title: "Summary of Survey Analysis NDNS carb50, 24 hours"
 author: "Chaochen Wang"
-date: "27 July 2018"
+date: "27 July 2018 created, `r Sys.Date()` updated"
 output:

### 2018-07-30 results/Timeslots/multilevel.Rmd
LCGA method adding, 7 slots results updated

@@
 
-```{r echo=FALSE, fig.height=8, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+```{r echo=FALSE, fig.height=6, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
 library(ggthemr)
@@
 
-ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Slots, group = Carbo, color = Carbo)) + 
+pp_long$Time <- as.character(pp_long$Slots)
+pp_long$Time[pp_long$Slots == "Breakfast"] <- 7.5
+pp_long$Time[pp_long$Slots == "Morning.snack"] <- 10.5
+pp_long$Time[pp_long$Slots == "Lunch"] <- 13
+pp_long$Time[pp_long$Slots == "Afternoon.snack"] <- 15.5
+pp_long$Time[pp_long$Slots == "Dinner"] <- 18.5
+pp_long$Time[pp_long$Slots == "Before.bedtime.snack"] <- 21
+pp_long$Time[pp_long$Slots == "Midnight.food"] <- 26
+pp_long$Time <- as.numeric(pp_long$Time)
+
+ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo))  + 
+  scale_x_continuous(limits = c(6, 29),
+  breaks = seq(6, 29, by = 1)) +
+  annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
+            alpha = 0.5, fill = "grey") + 
+  annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
+             alpha = 0.5, fill = "grey") + 
+  annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00, 
+            alpha = 0.5, fill = "grey") + 
+  annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
+             alpha = 0.5, fill = "grey") +
   geom_point(size = 3) + 
@@
   ) + 
-    theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  labs(title = "Class 1 days", x = "Time slots of the day", y = "Probability",
+    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
+  labs(title = "Class 1 days", x = "Hours of the day (next day from hour 24)", y = "Probability",
        color = "Carbohydrate\nintake") + 
   scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
-  ylim(c(0,1))
+  ylim(c(0,1)) #+ 
+  # scale_x_discrete(labels = c("6","7","8","9","10","11","12","13","14",
+  #                             "15","16","17","18","19", "20","21","22",
+  #                             "23","0","1","2","3","4","5"))
 
-ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Slots, group = Carbo, color = Carbo)) + 
+ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo)) + 
+  scale_x_continuous(limits = c(6, 29),
+  breaks = seq(6, 29, by = 1)) +
+  annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
+            alpha = 0.5, fill = "grey") + 
+  annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
+             alpha = 0.5, fill = "grey") + 
+  annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00, 
+            alpha = 0.5, fill = "grey") + 
+  annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
+             alpha = 0.5, fill = "grey") +
   geom_point(size = 3) + 
@@
   ) + 
-      theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  labs(title = "Class 2 days", x = "Time slots of the day", y = "Probability",
+    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
+  labs(title = "Class 2 days", x = "Hours of the day (next day from hour 24)", y = "Probability",
        color = "Carbohydrate\nintake") + 
@@
 
-```{r echo=FALSE, fig.height=8, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
+```{r echo=FALSE,fig.height=6, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
 library(ggthemr)
@@
 
-ggplot(pp_long[pp_long$CW == 3, ], aes(y = Prob, x=Slots, group = Carbo, color = Carbo)) + 
+ggplot(pp_long[pp_long$CW == 3, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo)) + 
+  scale_x_continuous(limits = c(6, 29),
+  breaks = seq(6, 29, by = 1)) +
+  annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
+            alpha = 0.5, fill = "grey") + 
+  annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
+             alpha = 0.5, fill = "grey") + 
+  annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00, 
+            alpha = 0.5, fill = "grey") + 
+  annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
+             alpha = 0.5, fill = "grey") +
   geom_point(size = 3) + 
@@
   ) + 
-      theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  labs(title = "Class 3 days", x = "Time slots of the day", y = "Probability",
+    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
+  labs(title = "Class 3 days", x = "Hours of the day (next day from hour 24)", y = "Probability",
        color = "Carbohydrate\nintake") + 

### 2018-07-30 results/table1slots.Rmd
LCGA method adding, 7 slots results updated

---
title: "Summary of Survey Analysis NDNS carb50, 7 time slots"
author: "Chaochen Wang"
date: "30 July 2018 created, `r Sys.Date()` updated"
output:
  html_document:
    nature:
      highlightLines: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(RColorBrewer)
library(plyr)
library(epiDisplay)
library(tidyverse)
library(dplyr)
library(scales)
library(readr)
library(kableExtra)
library(haven)
library(naniar)
```

# Multilevel classes results (3by3)

```{r bigdataset, echo=FALSE, eval=FALSE, warning=FALSE}
# read the big data sets
blood78 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr7-8a_indiv.dta")
# blood78 <- read_dta("~/Documents/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr7-8a_indiv.dta")

blood56 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr5-6a_indiv.dta")
blood14 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr1-4a_indiv_uk.dta")

food14 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr1-4a_personleveldietarydata_uk.dta")

food56 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr5-6a_personleveldietarydata.dta")

food78 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr7-8a_personleveldietarydata.dta")

names(blood78)[names(blood78)=="seriali"] <- "ID"
names(blood56)[names(blood56)=="seriali"] <- "ID"
names(blood14)[names(blood14)=="seriali"] <- "ID"
names(food78)[names(food78)=="seriali"] <- "ID"
names(food56)[names(food56)=="seriali"] <- "ID"
names(food14)[names(food14)=="seriali"] <- "ID"

BMI78 <- blood78 %>% 
  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2,  
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y78, wtn_Y78, wtb_Y78, cluster1, cluster2, cluster3, 
         cluster4, cluster5, area, gor) %>% 
  rename(wti = wti_Y78, wtn = wtn_Y78, wtb = wtb_Y78, drink = dnoft3) %>% 
  mutate(Years = "7-8", MVPAtime = NA) %>% 
  replace_with_na(replace = list(bmival = -1, 
                                 wstval = -1, 
                                 bpmedd2 = -1, 
                                 bpmedc2 = -1,
                                 hyper140_2 = -7, 
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 dnnow = -1,
                                 drink = -1,
                                 cigsta3 = -1)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1,
                                 drink = -8)) %>% 
    replace_with_na(replace = list(drink = -9,
                                 cigsta3 = -8))

BMI56 <- blood56 %>% 
  select(ID, Sex, age, area, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2, MVPAtime,
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y56, wtn_Y56, wtb_Y56, cluster1, cluster2, cluster3, 
         cluster4, cluster5, area, gor) %>% 
  mutate(Years = "5-6") %>% 
  rename(wti = wti_Y56, wtn = wtn_Y56, wtb = wtb_Y56, drink = dnoft3) %>% 
  replace_with_na(replace = list(bmival = -1, 
                                 wstval = -1, 
                                 bpmedd2 = -1, 
                                 bpmedc2 = -1,
                                 hyper140_2 = -7, 
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 dnnow = -1,
                                 drink = -1,
                                 cigsta3 = -1,
                                 MVPAtime = -1)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, 
                                 drink = -8)) %>% 
    replace_with_na(replace = list(drink = -9,
                                 cigsta3 = -8))

BMI14 <- blood14 %>% 
  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc, bpmedd, hyper140, hibp140, MVPAtime,
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_CY1234, wtn_CY1234, wtb_CY1234, cluster, area, gor) %>%
  rename(hyper140_2 = hyper140, hibp140_2 = hibp140, bpmedd2 = bpmedd, 
         bpmedc2 = bpmedc, cluster1 = cluster, 
         wti = wti_CY1234, wtn = wtn_CY1234, wtb =  wtb_CY1234, drink = dnoft3) %>% 
  mutate(cluster2 = NA, cluster3 = NA, cluster4 = NA, cluster5 = NA, Years = "1-4") %>% 
  replace_with_na(replace = list(bmival = -1, 
                                 wstval = -1, 
                                 bpmedd2 = -1, 
                                 bpmedc2 = -1,
                                 hyper140_2 = -7, 
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 dnnow = -1,
                                 drink = -1,
                                 cigsta3 = -1,
                                 MVPAtime = -4)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, MVPAtime = -1,
                                 drink = -8)) %>% 
  replace_with_na(replace = list(drink = -9,
                                 cigsta3 = -8))

BMI <- bind_rows(BMI14, BMI56, BMI78)

Energy14 <- food14 %>% 
  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, CHOpctotE)
Energy14$Country[Energy14$Country == "Northern Ireland"] <- "NI"

Energy56 <- food56 %>% 
  select(ID, Country, Surveyyear, EnergykJ, Carbohydrateg, CHOpctotE) %>% 
  rename(SurveyYear = Surveyyear)

Energy78 <- food78 %>% 
  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, CHOpctotE)

Energy <- bind_rows(Energy14, Energy56, Energy78)

```

```{r combinedata, echo=FALSE, eval=FALSE, warning=FALSE}
# ready to combine with the classification data

CW3CB3 <- read_table2("~/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB3.txt",  
                              col_names = FALSE)# change the path to your own path

names(CW3CB3) <- c("Breakfast", "Morning.snack", "Lunch",
                   "Afternoon.snack", "Dinner", "Before.bedtime.snack",
                   "Midnight.food", "ID_DAY", "AGE", "SEX", "CPROB1",
                      "CPROB2", "CPROB3", "CPROB4", "CPROB5", "CPROB6", "CPROB7", "CPROB8", "CPROB9",
                      "CB", "CW", "MLCJOINT", "ID")
CW3CB3_reg <- CW3CB3[!duplicated(CW3CB3$ID), ]

CW3CB3_reg <- CW3CB3_reg %>% 
  select(ID, AGE, SEX, CB) # extract only the CB variable (Between individual classes == 1 or 2)

tab1(CW3CB3_reg$CB, graph = FALSE)

CW3CB3_regss <- CW3CB3_reg %>% 
  left_join(BMI, by = "ID") %>% 
  left_join(Energy, by = "ID")## dataset for 3by3 multilevel latent classes

Slots_LGCA_3CLASS <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/LGCA/NDNSslot_LGCA_3CLASS.txt",  col_names = FALSE)

Slots_LGCA_3CLASS[, 1:32] <- sapply(Slots_LGCA_3CLASS[, 1:32], as.numeric)
names(Slots_LGCA_3CLASS) <- c(
  "H6_9_X",  "H9_12_X",
  "H12_14_X",  "H14_17_X",
  "H17_20_X",  "H20_22_X",
  "H22_6_X",  
  "H6_9_Y",  "H9_12_Y",
  "H12_14_Y",  "H14_17_Y",
  "H17_20_Y",  "H20_22_Y",
  "H22_6_Y",  
  "H6_9_X_X",  "H9_12_X_X",
  "H12_14_X_X",  "H14_17_X_X",
  "H17_20_X_X",  "H20_22_X_X",
  "H22_6_X_X",  
  "H6_9_Y_Y",  "H9_12_Y_Y",
  "H12_14_Y_Y",  "H14_17_Y_Y",
  "H17_20_Y_Y",  "H20_22_Y_Y",
  "H22_6_Y_Y",  
  "ID",
  "CPROB1",  "CPROB2",
  "CPROB3",  #"CPROB4", 
  "C")

Slots_LGCA_3CLASS[Slots_LGCA_3CLASS == "*"] <- NA

LCGA_3class <- Slots_LGCA_3CLASS %>% 
  select(ID, C) # extract only the C variable (classes == 1 or 2)

tab1(LCGA_3class$C, graph = FALSE)

LCGA_3class <- LCGA_3class %>% 
  left_join(BMI, by = "ID") %>% 
  left_join(Energy, by = "ID")## dataset for 3 classes latent classes growth analysis

```

```{r rescale the weighting,eval=FALSE,message=FALSE, cache=TRUE, warning=FALSE}
# Rescale the weighting values
# individual weighting
a <- sum(CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wti)
b <- sum(CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wti)
c <- sum(CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wti)

CW3CB3_regss$wti1to8 <- CW3CB3_regss$wti

CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wti1to8 <- CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wti*(a+b+c)*(1/2)/a
CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wti1to8 <- CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wti*(a+b+c)*(1/4)/b
CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wti1to8 <- CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wti*(a+b+c)*(1/4)/c
mean(CW3CB3_regss$wti1to8)

CW3CB3_regss$wti1to8 <- CW3CB3_regss$wti1to8/1.209816814
summ(CW3CB3_regss$wti1to8, graph = FALSE)
sum(CW3CB3_regss$wti1to8, graph = FALSE) #Check if the weighting sum up to the sample size we have

# Nurse weights

a <- sum(CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wtn)
b <- sum(CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wtn)
c <- sum(CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wtn)

CW3CB3_regss$wtn1to8 <- CW3CB3_regss$wtn

CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wtn1to8 <- CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wtn*(a+b+c)*(1/2)/a
CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wtn1to8 <- CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wtn*(a+b+c)*(1/4)/b
CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wtn1to8 <- CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wtn*(a+b+c)*(1/4)/c
mean(CW3CB3_regss$wtn1to8)

CW3CB3_regss$wtn1to8 <- CW3CB3_regss$wtn1to8/0.907003577
summ(CW3CB3_regss$wtn1to8, graph = FALSE)
sum(CW3CB3_regss$wtn1to8, graph = FALSE) #Check if the weighting sum up to the sample size we have

# Blood weights
a <- sum(CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wtb)
b <- sum(CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wtb)
c <- sum(CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wtb)

CW3CB3_regss$wtb1to8 <- CW3CB3_regss$wtb

CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wtb1to8 <- CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wtb*(a+b+c)*(1/2)/a
CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wtb1to8 <- CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wtb*(a+b+c)*(1/4)/b
CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wtb1to8 <- CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wtb*(a+b+c)*(1/4)/c
mean(CW3CB3_regss$wtb1to8)

CW3CB3_regss$wtb1to8 <- CW3CB3_regss$wtb1to8/0.4817444505
summ(CW3CB3_regss$wtb1to8, graph = FALSE)
sum(CW3CB3_regss$wtb1to8, graph = FALSE) #Check if the weighting sum up to the sample size we have

weightings <- CW3CB3_regss %>% select(ID, wti1to8, wtn1to8, wtb1to8)

# add the weightings to the other datasets
# CW3CB3_regss <- CW3CB3_regss %>% 
#   left_join(weightings, by = "ID")

LCGA_3class <- LCGA_3class %>%
  left_join(weightings, by = "ID")

write_dta(LCGA_3class, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/LCGA_7slots3class.dta")
# write_dta(LCGA_2class, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/LCGA_2class.dta")
write_dta(CW3CB3_regss, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW3CB2_7regss.dta")
# write_dta(CW2CB2_regss, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW2CB2_regss.dta")
```

```{r tab1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Timeslots_CW3CB3results.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "Latent class = 3", "P value [note]")

dt[28, 1] <- c("Hypertension (%) [note]")
dt[32, 1] <- c("Carbohydrate\npercent (%) [note]")
dt[35, 1] <- c("DM [note]")
dt[36, 1] <- c("Physical\nactivity (hours/day) [note]")

kable(dt,  align = "l", escape = F, row.names = FALSE,
              format = "html", caption = "Means, percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
                       "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
                       "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across >2 classes. For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 "DM was defined by A1C > 6.5%.", 
                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey."), 
               notation = "symbol")
```

# LCGA results (3 classes)

```{r tab1LCGA, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Timeslots_LCGA2classesresults.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "Latent class = 3", "P value [note]")

dt[28, 1] <- c("Hypertension (%) [note]")
dt[32, 1] <- c("Carbohydrate\npercent (%) [note]")
dt[35, 1] <- c("DM [note]")
dt[36, 1] <- c("Physical\nactivity (hours/day) [note]")

kable(dt,  align = "l", escape = F, row.names = FALSE,
              format = "html", caption = "Means, percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
                       "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
                       "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across >2 classes. For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 "DM was defined by A1C > 6.5%.", 
                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey."), 
               notation = "symbol")
```

### 2018-07-30 paper/Chapters/Chapter2.tex
LCGA method added

@@
 The analysis identifies distinct subgroups of individuals following a distinct pattern of change over time.
-LCGA is a special type of Growth Mixture Models (GMM), in which the variance of latent slope and intercept are fixed to zero within class, and allowed to vary only across classes.
+LCGA is a special type of Growth Mixture Models (GMM) \parencite{jung2008introduction}, in which the variance of latent slope and intercept are fixed to zero within class, and allowed to vary only across classes.
 LCGA assumes that all individual growth trajectories within classes are homogeneous.
+The diagramme of the LCGA model in the current setting is illustrated in \textbf{Figure \ref{fig:LCGAdiagram}}:
 
-In the NDNS RP data context, we considered a latent categorical variable $c_i$ representing the unobserved subpopulation membership (latent class variable) for participant $i, (c_i = 1,2,\cdots K)$.
+\begin{figure}[H]
+	%\vspace*{13cm}
+	\centering
+	\includegraphics[width=10cm]{Figures/LCGAdiagramme.jpeg}
+	\decoRule
+	\caption[Diagramme for LCGA model]{Diagram for LCGA model.\\ \scriptsize{\textbf{Abbreviations:} g, latent class variable; i, intercept; l, linear term coefficient; q, quadratic term coefficient; c, cubic term coefficient; u1, u2, ...
+u96, repeated categorical outcomes of eating carbohydrates at each hour/time slots across four days of survey.}}
+	\label{fig:LCGAdiagram}
+\end{figure}\vspace{-0.6cm}
+
+In the NDNS RP data context, we considered a latent categorical variable $g_i$ representing the unobserved subpopulation membership (latent class variable) for participant $i, (g_{i} = 1,2,\cdots K)$.
+Then a LCGA model predicts the probability of the carbohydrate eating response $u_{ti}$ at time $t$ in latent class $K$ can be written as: \vspace{-0.3cm}
+
+\begin{equation}
+\begin{aligned}
+P(u_{ti} = 0/1/2 |g_i = K) &  = \frac{1}{1 + e^{-\text{logit}(u_{itK})}} \\
+\text{logit}(u_{itK}) & = \beta_{0K} + \beta_{1K}t_{i} + \beta_{2K}t^2_i + \beta_{3K}t^3_i + \epsilon_{i} \\ 
+\epsilon_{i} \sim N(0, \sigma^2) & \;i = 1,2,...6155
+\end{aligned}
+\end{equation}\vspace{-0.6cm}
+
+Where,
+
+\begin{itemize}
+	\item $u_{ti}=\left\{ \begin{array}{ll}  0 & \text{if particiant } i \text{ was not eating any food at time } t\\ 
+	 1 & \text{if particiant } i \text{ was eating food and contribution of energy} \\ 
+	   &  \text{from carbohydrate was lower than 50\% at time } t \\ 
+	 2 & \text{if participant } i \text{ was eating food and contribution of energy} \\ 
+	 &  \text{from carbohydrate was higher or equal to 50\% at time } t \end{array} \right.$
+	\item $\beta_{0K}, \beta_{1K}, \beta_{2K}, \beta_{3K}$  correspond to $i, l, q, c$ in \textbf{Figure \ref{fig:LCGAdiagram}}, i.e.
+the coefficients for intercept, linear, quadratic, and cubic term of time.
+\end{itemize}
+
+An LCGA model can be modelled using either a linear, quadratic, or cubic trend over time.
+However, in our case, it may not be appropriate to assume the probabilities of responses to eating carbohydrates on the logit scale to change on a linear, or quadratic trend over four days, we chose to fit a more flex time function-a cubic form of time.
 

### 2018-07-30 paper/Figures/Figureforpaper.R

@@ -175,3 +175,85 @@ cls2 <- ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=HourN, group = Carbo,
 
 library(cowplot)
 plot_grid(cls1, cls2, ncol = 1, labels = c('A', 'B'), rel_heights=c(1,1.2))
+
+
+
+
+# diagram for LCGA --------------------------------------------------------
+library(DiagrammeR)
+
+grViz("
+      digraph boxes_and_circles {
+      
+      # a 'graph' statement
+      graph [overlap = true, fontsize = 8]
+      
+      # several 'node' statements
+      node [fillcolor = grey, style = filled, 
+      fontname = Helvetica, shape = circle]
+      A [label = 'g'] 
+      B [label = 'q']
+      C [label = 'c']
+      D [label = 'i']
+      E [label = 'l']
+      
+
+      
+      node [shape = box, 
+      fillcolor = white, 
+      fontname = Helvetica]
+      F [label = 'u96']
+      G [label = 'u1']
+      H [label = 'u2']
+      I [label = 'u3']
+      J [label = '...']
+      
+      
+      # edge statements
+      A->B A->C A->D A->E   B->F C->F D->F E->F 
+      B->G C->G D->G E->G
+      B->H C->H D->H E->H
+      B->I C->I D->I E->I
+      B->J C->J D->J E->J
+      }")
+
+# 
+# grViz("
+# digraph {
+#       
+#       graph [ranksep = 1]
+#       'i' [shape = 'circle']
+#       's' [shape = 'circle']
+#       't1' [shape = 'square']
+#       't2' [shape = 'square']
+#       't3' [shape = 'square']
+#       't4' [shape = 'square']
+#       'x1' [shape = 'square']
+#       'x2' [shape = 'square']
+#       'c1' [shape = 'square']
+#       'c2' [shape = 'square']
+#       'c3' [shape = 'square']
+#       'c4' [shape = 'square']
+#       'i'->'t1' [style = 'dashed', label = '1']
+#       'i'->'t2' [style = 'dashed', label = '1']
+#       'i'->'t3' [style = 'dashed', label = '1']
+#       'i'->'t4' [style = 'dashed', label = '1']
+#       's'->'t1' [style = 'dashed', label = '0']
+#       's'->'t2' [style = 'dashed', label = '1']
+#       's'->'t3' [style = 'dashed', label = '2']
[…]

### 2018-07-31 paper/Chapters/Chapter2.tex
LCGA removed

--- 2018-07-24 paper/Chapters/Chapter2.tex
@@
 
-To produce a sequence of discrete responses about the carbohydrate intake we are interested, we calculated the energy consumption per hour for each participant.
-The percentage of energy that contributed by carbohydrate within each hour were calculated for every every participant, each single day.
+Time across a typical survey day was divided into 7 time slots in the dietary diary of NDNS RP: 6 am to 9 am, 9 am to 12 noon, 12 noon to 2 pm, 2 pm to 5 pm, 5 pm to 8 pm, 8 pm to 10 pm, and 10 pm to 6 am.
+To produce a sequence of discrete responses regarding the carbohydrate intake we are interested, the energy consumption within each time slot over the four days of survey for each participant were calculated.
+The percentages of energy that contributed by carbohydrate within each time slot were then estimated.
 Since we planed to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical, we then dichotomised the responses according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e.
-if within an hour there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was lower or higher/equal to 50\% of total energy intake within that hour.
-Consequently, for each day of the recording, there were 24 data points generated by the dairy, each data point included one of the following responses:
+if within a time slot there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was lower or higher/equal to 50\% of total energy intake within that time slot.
+Consequently, for each day of the recording, there were 7 data points generated by the diary, each data point included one of the following responses:
 
 \begin{itemize}
-	\item Not eating any food; 
+	\item Not eating any food (Energy intake = 0 kJ); 
 	\item Eating, and carbohydrate contributed less than 50\% of the total energy intake;
@@
 
-Overall, for years 1 to 8 combined, a sample of 39,300 address was selected from 1,438 PSUs. The sampling selection process was:
+Overall, for years 1 to 8 combined, a sample of 39,300 addresses was selected from 1,438 PSUs. The sampling selection process was:
 
@@
 However, in the NDNS RP data set, the assumption of independent observations is violated.
-Each individual completed their dietary diary for four consecutive days, their diary recordings were later converted into 4 sequences of categorical responses reflecting the type of carbohydrate consumption at each hour of the day.
-The 4 observed sequences (observations) are nested in the participants and therefore are not independent.
+Each individual completed their dietary diary for four consecutive days, their diary recordings were later converted into four sequences of categorical responses reflecting the type of carbohydrate consumption at each time slot of the day.
+The four observed sequences (observed days) are nested in the participants and therefore are not independent.
 This nested data structure requires multilevel techniques.
@@
 Multilevel latent class analysis accounts for the nested structure of the data by allowing latent class intercepts to vary across level 2 units and thereby examining if and how level 2 units influence the level 1 latent classes.
-These random intercepts allow the probability of
-membership in a particular level 1 (observations) latent class to vary across level 2 units (e.g., here in the current context are the individuals).
-Essentially this allows the probability that an observation will belong to a
-particular level 1 latent class to vary across Level 2 units (individuals). \vspace{-0.5cm}
+These random intercepts allow the probability of membership in a particular level 1 (observation days) latent class to vary across level 2 units (e.g., here in the current context are the individuals).
+Essentially this allows the probability that an observation day will belong to a
+particular day-level latent class to vary across individual levels.\vspace{-0.5cm}
 
@@
 Proposed by Vermunt \parencite{Vermunt, vermunt2008latent} and Asparouhov and Muth\'en \parencite{muthen2009multilevel},  a traditional, parametric approach can be applied using a logistic regression model.
+For example, let's assume that there are two types of observation days in the dietary survey--high and low carbohydrate eating days.
 In an unconditional logistic regression model, the probability of the outcome (i.e.
-being in latent class $k$) is constant within the 4-day survey for each individual (level 2).
-Therefore, say when we are fitting a model with $k (k = 1, \cdots, K)$ latent classes in level 1, then in each individual (level 2), there is a probability of being in latent class $k$.
-A random effect model consider the individual (level 2) to be drawn from a population of adults in the UK, and the probability of the outcome (i.e.
-being in latent class $k$) across individuals is considered to be a random variable \parencite{snijders2011multilevel}.
-The 2-level random intercept effect regression model can be expressed as:\vspace{-0.4cm}
+an observed high carbohydrate eating day vs.
+a low carbohydrate eating day) is constant within individual-level which means for each person throughout his/her survey there is some probability of following a high carbohydrate eating day.
+A random effect model considers the individuals (level 2) to be drawn from the adult population in the UK, and the probability of the outcome (i.e.
+high carbohydrate eating days) across individuals is considered to be a random variable \parencite{snijders2011multilevel}.
+
+Thus, for a binary outcome $C_{ij} = 0, 1$ (low $=0$ or high $=1$ carbohydrate eating days), where $i$ denotes the observation days $(i = 1, 2, 3, 4)$, and $j$ denotes the individual $(j = 1, 2, \cdots, 6155)$.
+The 2-level random intercept logistic regression model can be expressed as:\vspace{-0.4cm}
 
@@
 \begin{aligned}
-\text{logit}[P(C_{ij} = t)] & = \beta_{0j} & \textbf{(level 1)}  \\
-\beta_{0j} & = \gamma_0 + \gamma_1 w_j + u_{0j} & \textbf{(level 2)} \\ 
-\Rightarrow P(C_{ij} = t) & = \frac{\exp{(\gamma_0 + \gamma_1 w_j + u_{0j})}}{1 + \exp{(\gamma_0 + \gamma_1 w_j + u_{0j})}} \\
+\text{logit}[P(C_{ij} = 1)] & = \beta_{0j} + \beta_{1}x_{ij} \;\;\;\;\;\;\;\;\; \textbf{(day level)}  \\
+\beta_{0j} & = \gamma_0 + \gamma_1 w_j + u_{0j} \; \textbf{(individual level)} \\ 
+\Rightarrow P(C_{ij} = 1) & = \frac{\exp{(\gamma_0 + \beta_{1}x_{ij} + \gamma_1 w_j + u_{0j})}}{1 + \exp{(\gamma_0 + \beta_{1}x_{ij} + \gamma_1 w_j + u_{0j})}} \\
 \end{aligned}
@@
 \begin{itemize}
-	\item $P(C_{ij} = t)$ as the probability that the randomly selected $i$th observation of $j$th individual is belonging to latent class $t$;
-	\item $u_{0j}$ as the random intercept for $j$th individual; 
-	\item the random intercept are assumed be normally distributed (i.e.
+	\item $P(C_{ij} = 1)$ as the probability that the randomly selected $i$th observation day of $j$th individual is a high carbohydrate eating day;
+	\item $\beta_{0j}$ as the random intercept, for outcome $C_{ij} = 1$; 
+	\item the random deviation of the individuals $u_{0j}$ are assumed be normally distributed (i.e.
 $u_{0j} \sim N(0, \sigma_{u_0}^2)$), the magnitude of the $u_{0j}$ variance ($\sigma_{u_0}^2$) indicates the influence of the individuals (level 2);
-	\item $w_j$ is the predictor for individual (level 2), such as age, and/or sex.
+	\item $x_{ij}, w_j$ is the predictors for day level (weekdays or weekends) and individual level, such as age, and sex.
 \end{itemize}
 
-Same as in the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each hour, over 24 hours and during 4 consecutive days of survey period).
-Considering that the latent class indicators are indicator variables ($U_{ijk}$), the MLCA model can be written as follows:\vspace{-0.8cm}
+Same framework can be used to consider random effects in an LCA model, but instead of saying that $C_{ij}$ is either low or high carbohydrate eating days as if we already know, it is now replaced by a latent variable $G_{ij}$ which indicates the typologies of carbohydrate eating patterns.
+Then we can use the day-level data to assess the log-odds of belonging to $k$th type of carbohydrate eating pattern on a specific day of survey, and we allow the log-odds to vary across individuals.
+Therefore, for some persons the log-odds of having a $k$th type of carbohydrate eating pattern during the survey can be high, but for the other persons, the log-odds of following the $k$th type of carbohydrate eating pattern can be low.
+
+If the day-level LCA model (carbohydrate eating pattern typologies) is best defined by $T (T \geqslant 2)$ latent classes, then $T-1$ random intercept will be specified by a two-level multinomial logistic regression model.
+Similar to the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each time slots, throughout 4 consecutive days of survey period).
+Considering the latent class indicators are indicator variables ($U_{ijk}$), the MLCA model can be written as follows:\vspace{-0.8cm}
 
@@
 %\begin{aligned}
-P(U_{ij1} = s_1, U_{ij2} = s_2, \cdots, U_{ijk} = s_{K}) = \sum_{t=1}^{T}P(C_{ij}=t)\prod_{k=1}^{K}P(U_{ijk} = s_k | C_{ij} = t)
+P(U_{ij1} = s_1, U_{ij2} = s_2, \cdots, U_{ijk} = s_{K}) = \sum_{t=1}^{T}P(G_{ij}=t)\prod_{k=1}^{K}P(U_{ijk} = s_k | G_{ij} = t)
 %\end{aligned}
@@
 \begin{itemize}
-	\item $ U_{ijk} $ represents the response of eating \textcolor{red}{high/low} carbohydrate on $i$th day of the survey ($i \in (1,2,3,4)$) in subject $j$ (level 2) at the $k$th hour of the day ($k \in (1, 2, 3, \cdots, 24)$);
-	\item $C_{ij}$ denotes the latent class membership for subject $j$ on $i$th day of the survey;
-	\item A specific latent class is referred to as $t$, and the total number of level 1 latent classes is denoted by $T$;
+	\item $ U_{ijk} $ represents the response of eating carbohydrate (one of the following: not eating any food, $< 50\%$ of the energy, or $\geqslant 50\%$ of the energy) on $i$th day of the survey ($i \in (1,2,3,4)$) in $j$th individual at the $k$th time slot of the day ($k \in (1, 2, 3, \cdots, 7)$);
+	\item $G_{ij}$ denotes the latent class membership for $j$th individuals on $i$th day of the survey, the total number of day-level latent class is $T$;
+%	\item A specific latent class is referred to as $t$, and the total number of level 1 latent classes is denoted by $T$;
 	\item $P(U_{ijk} = s_k|C_{ij} = t)$ is the probability of a specific response pattern, conditional on membership in latent class $t$.
@@
 
-The $P(C_{ij} = t)$ in equation \ref{MLCA} is what we have already defined in equation \ref{randomLCA}.
+The $P(G_{ij} = t)$ in equation \ref{MLCA} is what we have already defined in equation \ref{randomLCA}: \vspace{-0.3cm}
+
+\begin{equation}
+P(G_{ij} = t) = \frac{\exp{(\gamma_0 + \beta_{1}x_{ij} + \gamma_1 w_j + u_{0j})}}{1 + \exp{(\gamma_0 + \beta_{1}x_{ij} + \gamma_1 w_j + u_{0j})}} 
+\end{equation}
 
@@
 In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.
+\vspace{-0.3cm}
 
-\section{Latent Class Growth Analysis (LCGA)}\vspace{-0.3cm}
+%\section{Latent Class Growth Analysis (LCGA)}\vspace{-0.3cm}
+%
+%%LCGA is a statistical approach that models patterns in longitudinal data by classifying individuals into unobserved latent classes with more homogeneous patterns.
+LCGA is a special type of Growth Mixture Models (GMM), in which the variance of latent slope and intercept are fixed to zero within class, and allowed to vary only across classes.
+LCGA assumes that all individual growth trajectories within classes are homogeneous.
+%
+%
+%LCGA is a semi‐parametric technique used to identify distinct subgroups of individuals following a similar pattern of change over time on a given variable.
+The analysis identifies distinct subgroups of individuals following a distinct pattern of change over time.
+LCGA is a special type of Growth Mixture Models (GMM) \parencite{jung2008introduction}, in which the variance of latent slope and intercept are fixed to zero within class, and allowed to vary only across classes.
+LCGA assumes that all individual growth trajectories within classes are homogeneous.
+The diagramme of the LCGA model in the current setting is illustrated in \textbf{Figure \ref{fig:LCGAdiagram}}:
+%
+%\begin{figure}[H]
+%	%\vspace*{13cm}
+%	\centering
+%	\includegraphics[width=10cm]{Figures/LCGAdiagramme.jpeg}
+%	\decoRule
+%	\caption[Diagramme for LCGA model]{Diagram for LCGA model.\\ \scriptsize{\textbf{Abbreviations:} g, latent class variable; i, intercept; l, linear term coefficient; q, quadratic term coefficient; c, cubic term coefficient; u1, u2, ...
+u96, repeated categorical outcomes of eating carbohydrates at each hour/time slots across four days of survey.}}
+%	\label{fig:LCGAdiagram}
+%\end{figure}\vspace{-0.6cm}
+%
+%In the NDNS RP data context, we considered a latent categorical variable $g_i$ representing the unobserved subpopulation membership (latent class variable) for participant $i, (g_{i} = 1,2,\cdots K)$.
+Then a LCGA model predicts the probability of the carbohydrate eating response $u_{ti}$ at time $t$ in latent class $K$ can be written as: \vspace{-0.3cm}
+%
+%\begin{equation}
+%\begin{aligned}
+%P(u_{ti} = 0/1/2 |g_i = K) &  = \frac{1}{1 + e^{-\text{logit}(u_{itK})}} \\
+%\text{logit}(u_{itK}) & = \beta_{0K} + \beta_{1K}t_{i} + \beta_{2K}t^2_i + \beta_{3K}t^3_i + \epsilon_{i} \\ 
+%\epsilon_{i} \sim N(0, \sigma^2) & \;i = 1,2,...6155
+%\end{aligned}
+%\end{equation}\vspace{-0.6cm}
+%
+%Where, 
+%
+%\begin{itemize}
+%	\item $u_{ti}=\left\{ \begin{array}{ll}  0 & \text{if particiant } i \text{ was not eating any food at time } t\\ 
+%	 1 & \text{if particiant } i \text{ was eating food and contribution of energy} \\ 
+%	   &  \text{from carbohydrate was lower than 50\% at time } t \\ 
+%	 2 & \text{if participant } i \text{ was eating food and contribution of energy} \\ 
+%	 &  \text{from carbohydrate was higher or equal to 50\% at time } t \end{array} \right.$
+%	\item $\beta_{0K}, \beta_{1K}, \beta_{2K}, \beta_{3K}$  correspond to $i, l, q, c$ in \textbf{Figure \ref{fig:LCGAdiagram}}, i.e.
+the coefficients for intercept, linear, quadratic, and cubic term of time.
+%\end{itemize}
+%
+%An LCGA model can be modelled using either a linear, quadratic, or cubic trend over time.
+However, in our case, it may not be appropriate to assume the probabilities of responses to eating carbohydrates on the logit scale to change on a linear, or quadratic trend over four days, we chose to fit a more flex time function-a cubic form of time.
+The assumption in a LCGA model is that the data trajectory (the curve of eating carbohydrate pattern) for the participant consisting of the repeated measurements over time $t$, are independent given the group, $g_i$.
 

### 2018-07-31 results/table1slots.Rmd
LCGA removed

@@
 Energy14 <- food14 %>% 
-  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, CHOpctotE)
+  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, CHOpctotE, Proteing, ProteinpctotE, 
+         Fatg, FatpctotE)
 Energy14$Country[Energy14$Country == "Northern Ireland"] <- "NI"
@@
 Energy56 <- food56 %>% 
-  select(ID, Country, Surveyyear, EnergykJ, Carbohydrateg, CHOpctotE) %>% 
+  select(ID, Country, Surveyyear, EnergykJ, Carbohydrateg, CHOpctotE, Proteing, ProteinpctotE, 
+         Fatg, FatpctotE) %>% 
   rename(SurveyYear = Surveyyear)
@@
 Energy78 <- food78 %>% 
-  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, CHOpctotE)
+  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, CHOpctotE, Proteing, ProteinpctotE, 
+         Fatg, FatpctotE)
 
@@
                       "CB", "CW", "MLCJOINT", "ID")
+
+dta_NDNS <- read_csv("/home/wangcc-me/Documents/LSHTMproject/Rcode/dta_NDNS.csv") # extract the day of week data
+
+CW3idday <- CW3CB3 %>% 
+  select(ID, ID_DAY, CW, CB, MLCJOINT, AGE, SEX)
+
+CW3idday$DayNo <- ave(CW3idday$ID_DAY, CW3idday$ID, FUN = seq_along) # adding the day no
+
+dta_DayofWeek <- dta_NDNS %>% 
+  select(id, id_dy, DayofWeek)
+
+dta_DayofWeek$DayNo <- unlist(strsplit(dta_DayofWeek$id_dy,"D"))[c(FALSE, TRUE)] # creating a day no
+names(dta_DayofWeek)[1] <- "ID"
+dta_DayofWeek$DayNo <- as.numeric(dta_DayofWeek$DayNo)
+
+CW3idday <-   CW3idday %>%  
+  left_join(dta_DayofWeek, by= c("ID", "DayNo"))
+
+CW3idday$DayofWeek[CW3idday$ID_DAY == 40714261000] <- "Saturday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 112050710000] <- "Tuesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 310122510000] <- "Wednesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 5050616100] <- "Monday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 50506161000] <- "Tuesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 505061610000] <- "Wednesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 7090824100] <- "Monday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 70908241000] <- "Tuesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 709082410000] <- "Wednesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 807021910000] <- "Monday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 812101310000] <- "Sunday"
+
+with(CW3idday, tabpct(DayofWeek, CW))
+with(CW3idday, chisq.test(DayofWeek, CW))
+
+CW3idday$Weekend <- ifelse((CW3idday$DayofWeek == "Sunday" | CW3idday$DayofWeek == "Saturday"), TRUE, FALSE)
+
+with(CW3idday, tabpct(Weekend, CW))
+with(CW3idday, chisq.test(Weekend, CW))
+
 CW3CB3_reg <- CW3CB3[!duplicated(CW3CB3$ID), ]

### 2018-08-01 paper/Chapters/Chapter2.tex
tables replaced with time slots versions

@@
 Similar to the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each time slots, throughout 4 consecutive days of survey period).
-Considering the latent class indicators are indicator variables ($U_{ijk}$), the MLCA model can be written as follows:\vspace{-0.8cm}
+Considering the latent class indicators are indicator variables ($U_{ijk}$), the MLCA model can be written as follows:\vspace{-1cm}
 
@@
 
-Another approach is using a non-parametric MLCA, in which separate latent class models are specified for level 1 and level 2.
+Since the parametric approach discussed above can be extremely computationally demanding \parencite{van2008using, vermunt2008latent}, an alternative approach is using a non-parametric MLCA \parencite{davidian2008growth}.
+In this approach, separate latent class models are specified for level 1 (observation days) and level 2 (individuals).
 Similar with the parametric MLCA approach, there are $T-1$ random intercepts, where $T$ is the number of level 1 latent classes.
@@
 This approach is less computationally demanding compared with the parametric approach.
-These level 2 latent
-classes reflect differences in the probability of belonging to a specific level 1 latent class, so that clusters (i.e., individuals) that contain observations with similar probabilities for the level 1 latent classes will be grouped together.
+These level 2 (individual) latent classes reflect differences in the probability of belonging to a specific day-level latent class, so that individuals that contain observation days with similar probabilities for the level 1 latent classes will be grouped together.
 The non-parametric MLCA model can be defined as follows: \vspace{-0.7cm}
@@
 \begin{itemize}
-	\item $CB_j$ is level 2 latent class membership for $j$th individual;
-	\item $\gamma_{tm}$ is level 1 and level 2 indicators. 
+	\item $CB_j$ is individual-level latent class membership for $j$th individual;
+	\item $\gamma_{tm}$ is day-level and individual-level indicators. 
 \end{itemize}
@@
 According to Finch and French's simulation study \parencite{finch2014multilevel}, non-parametric approach generally resulted in more accurate recovery of the underlying latent structure of the data at both levels and provided better latent class model.
-Specifically, we are interested in exploring meaningful individual (level 2) latent classes rather than their daily consumption classification.
-Therefore, non-parametric MLCA was employed 1) to identify latent classes of observations (level 1) based on the subjects' responses to the 4-day food and drink diary and 2) to form distinct latent classes of individuals (level 2) based on the distribution of observation-level latent classes within individuals.\vspace{-0.3cm}
+Specifically, we are interested in exploring both meaningful individual (level 2) latent classes and the daily carbohydrate consumption classification.
+Therefore, non-parametric MLCA was employed 1) to identify latent classes of observation days (level 1) based on the subjects' responses to the 4-day food and drink diary and 2) to form distinct latent classes of individuals (level 2) based on the distribution of observation-level latent classes within individuals.\vspace{-0.3cm}
 
@@
 $q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability.
-In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.
+In the step of performing multilevel LCA, where LMR-LRT is available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day-level and individual-level.
+MLCA models were fitted in Mplus 7.4 \parencite{muthen2005mplus}, the Mplus codes are shown in the Appendix xxx.
 \vspace{-0.3cm}
@@
 
-\section{Association between latent classes and other variables}\vspace{-0.3cm}
+\section{Association between day-level and individual-level latent classes and other variables}\vspace{-0.3cm}
+
+Day-level latent classes identified by MLCA steps were tabulated according to whether the diary was recorded during weekdays or not.
+A contingency table giving the frequency of responses across the 7 time slots of the survey days was produced.

### 2018-08-01 paper/Chapters/Chapter3.tex
tables replaced with time slots versions

--- 2018-07-10 paper/Chapters/Chapter3.tex
@@
 
-\section{Main Section 1}
+\section{Model selection, comparison, and interpretation}
 
+%
 %-----------------------------------
@@
 %-----------------------------------
-\subsection{Subsection 1}
+%\subsection{Subsection 1}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}[H]
+
+	\caption{\label{tab:mixmodels}Fit Criteria for Each Model Specification}\vspace{-0.3cm}
+	\centering
+	\fontsize{9}{11}\selectfont
+	\begin{tabular}[t]{lccccc}
+		\hiderowcolors
+		\toprule
+		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Number of day-level classes}} \\
+		\cmidrule(l{2pt}r{2pt}){2-6}
+		\textbf{Model} & \textbf{1 class} & \textbf{2 classes} & \textbf{3 classes} & \textbf{4 classes} & \textbf{5 classes}\\
+		\midrule
+		\showrowcolors
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\textbf{Fixed effects model}}\\
+		\hspace{1em}No. of free parameters & 14 & 29 & 44 & 59 & 74\\
+		\hspace{1em}\hspace{1em}Log-likelihood & -173793.306 & -172669.771 & -172039.204 & -171633.941 & -171377.292\\
+		\hspace{1em}\hspace{1em}BIC & 347728.092 & 345632.608 & 344523.06 & 343864.121 & 343502.409\\
+		\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & -- & $<$ 0.0001 & 1e-04 & $<$ 0.0001 & $<$ 0.0001\\
+		\hspace{1em}\hspace{1em}Entropy & 1 & 0.31 & 0.392 & 0.51 & 0.481\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\textbf{Random effects model}}\\
+		\hspace{1em}2 individual-level classes &  &  &  &  & \\
+		\hspace{1em}\hspace{1em}No. of free parameters &  & 59 & 89 & 119 & \\
+		\hspace{1em}\hspace{1em}Log-likelihood &  & -169331.132 & -168700.96 & -168366.193 & \\
+		\hspace{1em}\hspace{1em}BIC &  & 339258.502 & 338301.338 & 337934.968 & \\
+		\hspace{1em}\hspace{1em}Entropy &  & 0.581 & 0.569 & 0.555 & \\
+		\hspace{1em}3 individual-level classes &  &  &  &  & \\
+		\hspace{1em}\hspace{1em}No. of free parameters &  & 89 & 134 & 179 & \\
+		\hspace{1em}\hspace{1em}Log-likelihood &  & -166936.279 & -166348.815 & -166062.761 & \\
+		\hspace{1em}\hspace{1em}BIC &  & 334771.968 & 334051.799 & 333934.448 & \\
+		\hspace{1em}\hspace{1em}Entropy &  & 0.677 & 0.63 & 0.644 & \\
+		\hspace{1em}4 individual-level classes &  &  &  &  & \\
+		\hspace{1em}\hspace{1em}No. of free parameters &  & 119 & 179 &  & \\
+		\hspace{1em}\hspace{1em}Log-likelihood &  & -165441.731 & -164845.696 &  & \\
+		\hspace{1em}\hspace{1em}BIC &  & 332086.045 & 331500.318 &  & \\
+		\hspace{1em}\hspace{1em}Entropy &  & 0.729 & 0.659 &  & \\
+		\bottomrule
+		\multicolumn{6}{l}{\textit{Note: }}\\
+		\multicolumn{6}{l}{Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index;}\\ 
+		\multicolumn{6}{l}{Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.}\\
+	\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+	\caption{\label{tab:daylevel}Day Level Latent Class Solution for Three-Class Model (No Individual level Model)}\vspace{-0.3cm}
+	\centering
+	\fontsize{9}{11}\selectfont
+	\begin{tabular}[t]{llccccc}
+		\hiderowcolors
+		\toprule
+		\textbf{Time slots of} & \textbf{Responses of} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1\\(30.8\%)}} & \textbf{\Centerstack{Class 2\\(39.8\%)}} & \textbf{\Centerstack{Class 3\\(29.5\%)}} \\
+		\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
+		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & (\%) & \textbf{\Centerstack{High carbo- \\ hydrate day}} & \textbf{\Centerstack{Lower carbo-\\hydrate day}} & \textbf{Regular day}\\
+		\midrule
+		\showrowcolors
+		6 am – 9 am &  &  &  &  &  & \\
+		& Not eating & 7655 & 31.2 & 0.129 & 0.45 & 0.32\\
+		& Carbohydrate $<$ 50\%\textsuperscript{*} & 4500 & 18.4 & 0.13 & 0.267 & 0.128\\
+		& Carbohydrate $\geqslant$ 50\%\textsuperscript{\dag} & 12328 & 50.4 & 0.741 & 0.283 & 0.552\\
+		9 am – 12 am &  &  &  &  &  & \\
+		& Not eating & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
+		& Carbohydrate $<$ 50\% & 7227 & 29.5 & 0.158 & 0.492 & 0.173\\
+		& Carbohydrate $\geqslant$ 50\% & 11809 & 48.2 & 0.605 & 0.429 & 0.426\\
+		12 noon – 2 pm &  &  &  &  &  & \\
+		& Not eating & 4783 & 19.5 & 0.156 & 0.356 & 0.019\\
+		& Carbohydrate $<$ 50\% & 11112 & 45.4 & 0.405 & 0.413 & 0.56\\
+		& Carbohydrate $\geqslant$ 50\% & 8588 & 35.1 & 0.439 & 0.231 & 0.421\\
+		2 pm – 5 pm &  &  &  &  &  & \\
+		& Not eating & 6926 & 28.3 & 0.13 & 0.123 & 0.659\\
+		& Carbohydrate $<$ 50\% & 8277 & 33.8 & 0.249 & 0.602 & 0.076\\
+		& Carbohydrate $\geqslant$ 50\% & 9280 & 37.9 & 0.621 & 0.276 & 0.266\\
+		5 pm – 8 pm &  &  &  &  &  & \\
+		& Not eating & 3043 & 12.4 & 0.114 & 0.199 & 0.034\\
+		& Carbohydrate $<$ 50\% & 14240 & 58.2 & 0.516 & 0.59 & 0.639\\
+		& Carbohydrate $\geqslant$ 50\% & 7200 & 29.4 & 0.37 & 0.211 & 0.328\\
+		8 pm – 10 pm &  &  &  &  &  & \\
+		& Not eating & 8722 & 35.6 & 0.322 & 0.291 & 0.48\\
+		& Carbohydrate $<$ 50\% & 8898 & 36.3 & 0.266 & 0.551 & 0.212\\
+		& Carbohydrate $\geqslant$ 50\% & 6863 & 28.0 & 0.412 & 0.158 & 0.308\\
+		10 pm – 6 am &  &  &  &  &  & \\
+		& Not eating & 16295 & 66.6 & 0.68 & 0.59 & 0.751\\
+		& Carbohydrate $<$ 50\% & 4144 & 16.9 & 0.074 & 0.294 & 0.101\\
+		& Carbohydrate $\geqslant$ 50\% & 4044 & 16.5 & 0.246 & 0.115 & 0.148\\
+		\bottomrule
+		\multicolumn{7}{l}{\textit{Note: }}\\
+		\multicolumn{7}{l}{\textsuperscript{*} Carbohydrate $<$ 50\% indicates that within the time slot, carbohydrate contributed less }\\
+		\multicolumn{7}{l}{than 50\% total energy intake.}\\ 
+		\multicolumn{7}{l}{\textsuperscript{\dag} Carbohydrate $\geqslant$ 50\% indicates that within the time slot, carbohydrate contributed higher }\\
+		\multicolumn{7}{l}{or equal to 50\% total energy intake.}\\ 
+	\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
 
@@
 \section{Main Section 2}
+
+%
+%\rowcolors{2}{gray!6}{white}
+%
+%\begin{table}
+%	
+%	\caption{\label{tab:LCGAtab1}Means, percentages, and 95\% CIs of the characteristics of carbohydrate temporal eating patterns by LCGA memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}
+%	\centering
+%	\fontsize{9}{11}\selectfont
+%	\begin{tabular}[t]{lcccc}
+%		\hiderowcolors
+%		\toprule
+%		 & Latent class = 1 & Latent class = 2 & Latent class = 3 & P value \textsuperscript{*}\\
+%		\midrule
+%		\showrowcolors
+%		Total (\%) & 28.4 (26.8, 30.1) & 7.0 (6.2, 7.9) & 64.6 (62.9, 66.2) & \\
+%		Countries (\%) &  &  &  & \\
+%		\hspace{1em}England & 81.4 (78.5, 84.0) & 87.5 (82.9, 91.0) & 84.6 (82.5, 86.4) & 0.004\\
+%		\hspace{1em}Northern Ireland & 3.9 (2.9, 5.1) & 0.6 (0.3, 1.2) & 2.5 (2.0, 3.2) & \\
+%		\hspace{1em}Scotland & 9.5 (7.4, 12.3) & 6.2 (3.5, 10.6) & 8.3 (6.7, 10.3) & \\
+%		\hspace{1em}Wales & 5.2 (4.1, 6.6) & 5.7 (3.8, 8.5) & 4.6 (3.8, 5.6) & \\
+%		Age (years) & 43.8 (42.4, 45.1) & 49.1 (47.2, 50.9) & 50.1 (49.3, 50.9) & $<$ 0.001\\
+%		Sex (\%) &  &  &  & \\
+%		\hspace{1em}Men & 50.6 (47.3, 53.9) & 49.6 (43.7, 55.4) & 47.6 (45.4, 49.7) & 0.273\\
+%		\hspace{1em}Women & 49.4 (46.1, 52.7) & 50.4 (44.6, 56.3) & 52.4 (50.3, 54.6) & \\
+%		Survey years (\%) &  &  &  & \\
+%		\hspace{1em}1 & 11.4 (8.8, 14.7) & 17.1 (12.4, 23.3) & 14.4 (11.9, 17.4) & 0.002\\
+%		\hspace{1em}2 & 10.1 (7.8, 13.1) & 18.3 (13.3, 24.7) & 12.4 (10.2, 15.0) & \\
+%		\hspace{1em}3 & 13.9 (10.8, 17.7) & 9.1 (5.7, 14.1) & 10.7 (8.6, 13.1) & \\
+%		\hspace{1em}4 & 10.9 (8.5, 13.9) & 13.8 (9.7, 19.4) & 13.2 (10.9, 16.0) & \\
+%		\hspace{1em}5 & 13.5 (10.6, 17.0) & 12.8 (8.4, 19.1) & 13.3 (11.0, 16.1) & \\
+%		\hspace{1em}6 & 12.8 (10.1, 16.1) & 8.7 (5.7, 12.9) & 11.5 (9.5, 13.9) & \\
+%		\hspace{1em}7 & 14.3 (11.5, 17.6) & 9.5 (6.5, 13.8) & 12.4 (10.2, 15.0) & \\
+%		\hspace{1em}8 & 13.2 (10.5, 16.4) & 10.5 (7.4, 14.8) & 12.1 (9.9, 14.6) & \\
+%		BMI (kg/m\textasciicircum{}2) & 27.5 (27.1, 27.9) & 27.0 (26.4, 27.6) & 27.4 (27.2, 27.6) & 0.433\\
+%		WC (cm) & 93.3 (92.1, 94.5) & 92.9 (90.9, 95.0) & 93.1 (92.3, 93.8) & 0.928\\
+%		Smoking status (\%) &  &  &  & \\
+%		\hspace{1em}Current & 24.1 (21.5, 27.0) & 30.0 (24.8, 35.8) & 18.8 (17.2, 20.6) & $<$ 0.001\\
+%		\hspace{1em}Ex-smoker & 20.0 (17.6, 22.6) & 27.5 (22.4, 33.2) & 25.9 (24.1, 27.7) & \\
+%		\hspace{1em}Never & 55.9 (52.7, 59.0) & 42.5 (36.6, 48.7) & 55.3 (53.2, 57.4) & \\
+%		Current drinking status (\%) &  &  &  & \\
+%		\hspace{1em}Yes & 24.6 (21.7, 27.7) & 18.3 (14.0, 23.6) & 16.8 (15.3, 18.4) & $<$ 0.001\\
+%		Hypertension (\%) \textsuperscript{\dag} &  &  &  & \\
+%		\hspace{1em}Yes & 25.9 (22.3, 29.9) & 31.8 (25.3, 39.1) & 30.4 (27.9 32.8) & 0.111\\
+%		Total energy intake (KJ) &  \Centerstack{ 6713.8 \\ (6575.7, 6851.8)}   &  \Centerstack{ 9256.0 \\ (8850.8, 9661.2)}   &  \Centerstack{7916.9 \\ (7814.0, 8019.9)}     & $<$ 0.001\\
+%		Carbohydrate intake (g) & 192.9 (188.5, 197.3) & 275.6 (263.4, 287.8) & 226.9 (223.9, 229.9) & $<$ 0.001\\
+%		Carbohydrate
+%		percent (\%) \textsuperscript{\ddag} & 45.8 (45.3, 46.4) & 47.4 (46.5, 48.3) & 45.6 (45.3, 45.9) & 0.001\\
+%		Glucose (mmol/l) & 5.16 (5.08, 5.23) & 5.09 (5.00, 5.18) & 5.14 (5.10, 5.19) & 0.537\\
+%		A1C (\%) & 5.47 (5.42, 5.51) & 5.48 (5.42, 5.54) & 5.49 (5.47. 5.52) & 0.403\\
+%		DM \textsuperscript{\S} & 5.9 (4.2, 8.2) & 1.1 (0.2, 5.2) & 4.7 (3.6, 6.0) & 0.053\\
+%        Physical activity (hs/day) \textsuperscript{\P}& 1.31 (1.14, 1.49) & 1.82 (1.44, 2.19) & 1.62 (1.49, 1.76) & 0.018\\
+%		\bottomrule
+%		\multicolumn{5}{l}{\textit{Note: }}\\
+%		\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; LCGA, latent class growth analysis; NDNS RP, national}\\ 
+%		\multicolumn{5}{l}{dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; }\\
+%		\multicolumn{5}{l}{A1C, haemoglobin A1c;DM, diabetes mellitus; h, hour.}\\
+%		\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights,}\\
+%		\multicolumn{5}{l}{the others are weighted by individual weights.}\\
+%		\multicolumn{5}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
+%		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes}\\   
+%		\multicolumn{5}{l}{with Bonferroni correction to account for multiple testing across >2 classes.}\\
+%		\multicolumn{5}{l}{For categorical variables, differences between latent classes were assessed}\\
+%		\multicolumn{5}{l}{using the adjusted Pearson Chi-2 test for survey data.}\\
+%		\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure $\geqslant$ 140 mmHg or diastolic}\\ 
+%		\multicolumn{5}{l}{blood pressure $\geqslant$ 90 mmHg, or under}\\
+%		\multicolumn{5}{l}{treatment for hypertension.}\\
+%		\multicolumn{5}{l}{\textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake}\\
+%		\multicolumn{5}{l}{\textsuperscript{\S} DM was defined by A1C > 6.5\%.}\\
+%		\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity}\\ 
+%		\multicolumn{5}{l}{during the survey.}\\
+%	\end{tabular}
+%\end{table}
+
+\rowcolors{2}{white}{white}

### 2018-08-01 paper/Tables/2by2Table1.Rmd
tables replaced with time slots versions

@@
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Mixed_50_paper.csv", header = T)
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Mixed_7slots.csv", header = T)
+dt <- dt[,-7]
 names(dt) <- c("Model", "1 class", "2 classes",  "3 classes", "4 classes", "5 classes")
@@
 ```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/timeslots_cw3cb3_univariate.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c("Time slots of the day", "Responses of carbohydrate intake", "Frequency", "Precentages (%)", 
+               "Class 1 (30.8%)", "Class 2 (39.8%)", "Class 3 (29.5%)")
+
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "Day Level Latent Class Solution for Three-Class Model (No Individual level Model)", booktabs = T,linesep = "") %>%
+ kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+    add_header_above(c(" ", " ", " ", " ", "High carbohydrate day", "Lower carbohydrate day", "Regular day"))
+
+```

### 2018-08-01 paper/Tables/2by2Table1.tex
tables replaced with time slots versions

@@
 \toprule
-\multicolumn{1}{c}{ } & \multicolumn{6}{c}{Number of level 1 classes} \\
-\cmidrule(l{2pt}r{2pt}){2-7}
+\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Number of level 1 classes} \\
+\cmidrule(l{2pt}r{2pt}){2-6}
 Model & 1 class & 2 classes & 3 classes & 4 classes & 5 classes\\
@@
 \multicolumn{6}{l}{\textbf{Fixed effects model}}\\
-\hspace{1em}No. of free parameters & 48 & 97 & 146 & 195 & 244\\
-\hspace{1em}\hspace{1em}Log-likelihood & -372017.293 & -368913.708 & -366664.971 & -365528.553 & -364901.166\\
-\hspace{1em}\hspace{1em}BIC & 744519.661 & 738807.672 & 734805.379 & 733027.723 & 732268.13\\
-\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & --- & < 0.0001 & < 0.0001 & 0.8478 & 0.7602\\
-\hspace{1em}\hspace{1em}Entropy & 1 & 0.777 & 0.666 & 0.658 & 0.648\\
+\hspace{1em}No. of free parameters & 14 & 29 & 44 & 59 & 74\\
+\hspace{1em}\hspace{1em}Log-likelihood & -173793.306 & -172669.771 & -172039.204 & -171633.941 & -171377.292\\
+\hspace{1em}\hspace{1em}BIC & 347728.092 & 345632.608 & 344523.06 & 343864.121 & 343502.409\\
+\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & -- & < 0.0001 & 1e-04 & < 0.0001 & < 0.0001\\
+\hspace{1em}\hspace{1em}Entropy & 1 & 0.31 & 0.392 & 0.51 & 0.481\\
 \addlinespace[0.3em]
@@
 \hspace{1em}2 between classes &  &  &  &  & \\
-\hspace{1em}\hspace{1em}No. of free parameters &  & 195 & 293 & 391 & \\
-\hspace{1em}\hspace{1em}Log-likelihood &  & -363460.153 & -361571.164 & -360297.394 & \\
-\hspace{1em}\hspace{1em}BIC &  & 728890.925 & 726103.308 & 724546.13 & \\
-\hspace{1em}\hspace{1em}Entropy &  & 0.834 & 0.798 & 0.784 & \\
+\hspace{1em}\hspace{1em}No. of free parameters &  & 59 & 89 & 119 & \\
+\hspace{1em}\hspace{1em}Log-likelihood &  & -169331.132 & -168700.96 & -168366.193 & \\
+\hspace{1em}\hspace{1em}BIC &  & 339258.502 & 338301.338 & 337934.968 & \\
+\hspace{1em}\hspace{1em}Entropy &  & 0.581 & 0.569 & 0.555 & \\
 \hspace{1em}3 between classes &  &  &  &  & \\
-\hspace{1em}\hspace{1em}No. of free parameters &  & 293 & 440 & 587 & \\
-\hspace{1em}\hspace{1em}Log-likelihood &  & -360910.13 & -358902.821 & -357404.521 & \\
-\hspace{1em}\hspace{1em}BIC &  & 724781.241 & 722252.166 & 720741.109 & \\
-\hspace{1em}\hspace{1em}Entropy &  & 0.824 & 0.793 & 0.824 & \\
+\hspace{1em}\hspace{1em}No. of free parameters &  & 89 & 134 & 179 & \\
+\hspace{1em}\hspace{1em}Log-likelihood &  & -166936.279 & -166348.815 & -166062.761 & \\
+\hspace{1em}\hspace{1em}BIC &  & 334771.968 & 334051.799 & 333934.448 & \\
+\hspace{1em}\hspace{1em}Entropy &  & 0.677 & 0.63 & 0.644 & \\
 \hspace{1em}4 between classes &  &  &  &  & \\
-\hspace{1em}\hspace{1em}No. of free parameters &  & 391 & 587 & 783 & \\
-\hspace{1em}\hspace{1em}Log-likelihood &  & -358684.859 & -356668.354 & -355235.955 & \\
-\hspace{1em}\hspace{1em}BIC &  & 720078.473 & 719268.774 & 718384.699 & \\
-\hspace{1em}\hspace{1em}Entropy &  & 0.816 & 0.817 & 0.806 & \\
+\hspace{1em}\hspace{1em}No. of free parameters &  & 119 & 179 &  & \\
+\hspace{1em}\hspace{1em}Log-likelihood &  & -165441.731 & -164845.696 &  & \\
+\hspace{1em}\hspace{1em}BIC &  & 332086.045 & 331500.318 &  & \\
+\hspace{1em}\hspace{1em}Entropy &  & 0.729 & 0.659 &  & \\
 \bottomrule
@@
 
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-5}Day Level Latent Class Solution for Three-Class Model (No Individual level Model)}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{lllllll}
+\hiderowcolors
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{High carbohydrate day} & \multicolumn{1}{c}{Lower carbohydrate day} & \multicolumn{1}{c}{Regular day} \\
+\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
+Time slots of the day & Responses of carbohydrate intake & Frequency & Precentages (\%) & Class 1 (30.8\%) & Class 2 (39.8\%) & Class 3 (29.5\%)\\
+\midrule
+\showrowcolors
+6 am – 9 am &  &  &  &  &  & \\
+ & Not eating & 7655 & 31.2 & 0.129 & 0.45 & 0.32\\
+ & Eating, Carbohydrate < 50\% & 4500 & 18.4 & 0.13 & 0.267 & 0.128\\
+ & Eating, Carbohydrate >= 50\% & 12328 & 50.4 & 0.741 & 0.283 & 0.552\\
+9 am – 12 am &  &  &  &  &  & \\
+ & Not eating & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
+ & Eating, Carbohydrate < 50\% & 7227 & 29.5 & 0.158 & 0.492 & 0.173\\
+ & Eating, Carbohydrate >= 50\% & 11809 & 48.2 & 0.605 & 0.429 & 0.426\\
+12 noon – 2 pm &  &  &  &  &  & \\
+ & Not eating & 4783 & 19.5 & 0.156 & 0.356 & 0.019\\
+ & Eating, Carbohydrate < 50\% & 11112 & 45.4 & 0.405 & 0.413 & 0.56\\
+ & Eating, Carbohydrate >= 50\% & 8588 & 35.1 & 0.439 & 0.231 & 0.421\\
+2 pm – 5 pm &  &  &  &  &  & \\
+ & Not eating & 6926 & 28.3 & 0.13 & 0.123 & 0.659\\
+ & Eating, Carbohydrate < 50\% & 8277 & 33.8 & 0.249 & 0.602 & 0.076\\
+ & Eating, Carbohydrate >= 50\% & 9280 & 37.9 & 0.621 & 0.276 & 0.266\\
+5 pm – 8 pm &  &  &  &  &  & \\
+ & Not eating & 3043 & 12.4 & 0.114 & 0.199 & 0.034\\
+ & Eating, Carbohydrate < 50\% & 14240 & 58.2 & 0.516 & 0.59 & 0.639\\
+ & Eating, Carbohydrate >= 50\% & 7200 & 29.4 & 0.37 & 0.211 & 0.328\\
+8 pm – 10 pm &  &  &  &  &  & \\
+ & Not eating & 8722 & 35.6 & 0.322 & 0.291 & 0.48\\
+ & Eating, Carbohydrate < 50\% & 8898 & 36.3 & 0.266 & 0.551 & 0.212\\
+ & Eating, Carbohydrate >= 50\% & 6863 & 28.0 & 0.412 & 0.158 & 0.308\\
+10 pm – 6 am &  &  &  &  &  & \\
+ & Not eating & 16295 & 66.6 & 0.68 & 0.59 & 0.751\\
+ & Eating, Carbohydrate < 50\% & 4144 & 16.9 & 0.074 & 0.294 & 0.101\\
+ & Eating, Carbohydrate >= 50\% & 4044 & 16.5 & 0.246 & 0.115 & 0.148\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
 \end{document}

### 2018-08-01 results/Timeslots/multilevel.Rmd
tables replaced with time slots versions

@@
 library(plyr)
+library(epiDisplay)
 library(tidyverse)
 library(dplyr)
-library(epiDisplay)
+
 library(scales)
@@
                       "CPROB6",
+                      # "CPROB7",
+                      # "CPROB8",
+                      # "CPROB9",
                       "CB",
@@
 
-## Visualisation of level 2 latent classes (CB = 2)
+<!-- ## Visualisation of level 2 latent classes (CB = 2) -->
 
-```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}
+<!-- ```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE} -->
 
-# ndnsNNN <- read_csv("results/ndnsNNN.dat")
-# dt <- ndnsNNN[, c(2,5)]
-# names(dt) <- c("ID_DAY", "DayofWeek")
-# 
-# 
-# CW2CB2 <- CW2CB2 %>% 
-#   left_join(dt, by = "ID_DAY")
-#
+<!-- # ndnsNNN <- read_csv("results/ndnsNNN.dat") -->
+<!-- # dt <- ndnsNNN[, c(2,5)] -->
+<!-- # names(dt) <- c("ID_DAY", "DayofWeek") -->
+<!-- #  -->
+<!-- #  -->
+<!-- # CW2CB2 <- CW2CB2 %>%  -->
+<!-- #   left_join(dt, by = "ID_DAY") -->
+<!-- #  -->
 
-chart.data <- CW3CB2 %>% 
-  group_by(CB, CW) %>% 
-  tally %>% 
-  group_by(CB) %>% 
-  mutate(pct = n/sum(n))
+<!-- chart.data <- CW3CB2 %>%  -->
+<!--   group_by(CB, CW) %>%  -->
+<!--   tally %>%  -->
+<!--   group_by(CB) %>%  -->
+<!--   mutate(pct = n/sum(n)) -->
 
-chart.data <- ddply(chart.data, .(CB),
-                     transform, pos = cumsum(pct) - (0.5 * pct))
+<!-- chart.data <- ddply(chart.data, .(CB), -->
+<!--                      transform, pos = cumsum(pct) - (0.5 * pct)) -->
 
-chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"), 
-                        labels = c("Class 3 days", "Class 2 days", "Class 1 days"))
-chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"), 
-                        labels = c("Individual Class 1\n(35.3%)",  "Individual class 2\n(64.7%)"))
+<!-- chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"),  -->
+<!--                         labels = c("Class 3 days", "Class 2 days", "Class 1 days")) -->
+<!-- chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"),  -->
+<!--                         labels = c("Individual Class 1\n(35.3%)",  "Individual class 2\n(64.7%)")) -->
 
-library(ggthemr)
-ggthemr("dust", layout = "scientific")
-ggplot() + 
-  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
-           stat="identity") + 
-  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
-            size=4, colour="white", family="Atlas Grotesk Medium") + 
-  theme(legend.position="bottom", legend.direction="horizontal",
-        legend.title = element_blank(), 
-        axis.title = element_text(size = 18), 
-        axis.text = element_text(size = 15), 
-        axis.line = element_line(colour = "black"), 
-        plot.title=element_text(family="Atlas Grotesk Medium"),
-        text=element_text(family="Atlas Grotesk Light")) + 
-  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
-  scale_y_continuous(labels=percent)
-```
+<!-- library(ggthemr) -->
+<!-- ggthemr("dust", layout = "scientific") -->
+<!-- ggplot() +  -->
+<!--   geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6, -->
+<!--            stat="identity") +  -->
+<!--   geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")), -->
+<!--             size=4, colour="white", family="Atlas Grotesk Medium") +  -->
+<!--   theme(legend.position="bottom", legend.direction="horizontal", -->
+<!--         legend.title = element_blank(),  -->
+<!--         axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 15),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         plot.title=element_text(family="Atlas Grotesk Medium"), -->
+<!--         text=element_text(family="Atlas Grotesk Light")) +  -->
+<!--   labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") + -->
+<!--   scale_y_continuous(labels=percent) -->
+<!-- ``` -->
 

### 2018-08-01 results/table1slots.Rmd
tables replaced with time slots versions

@@
     toc_float: yes
+editor_options: 
+  chunk_output_type: console
 ---
@@
   select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2,  
-         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y78, wtn_Y78, wtb_Y78, cluster1, cluster2, cluster3, 
+         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y78, wtn_Y78, wtb_Y78, ethgrp5, ethgrp2,
+         cluster1, cluster2, cluster3, nssec8, paidemployment, qual7, eqvinc, MarSt2,
          cluster4, cluster5, area, gor) %>% 
   rename(wti = wti_Y78, wtn = wtn_Y78, wtb = wtb_Y78, drink = dnoft3) %>% 
-  mutate(Years = "7-8", MVPAtime = NA) %>% 
-  replace_with_na(replace = list(bmival = -1, 
-                                 wstval = -1, 
-                                 bpmedd2 = -1, 
+  mutate(Years = "7-8", MVPAtime = NA, MarStat = NA) %>% 
+  replace_with_na(replace = list(bmival = -1, qual7 = -8,
+                                 wstval = -1, eqvinc = -1,
+                                 bpmedd2 = -1, MarSt2 = -1,
                                  bpmedc2 = -1,
@@
                                  drink = -1,
-                                 cigsta3 = -1)) %>% 
-  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1,
-                                 drink = -8)) %>% 
-    replace_with_na(replace = list(drink = -9,
-                                 cigsta3 = -8))
+                                 ethgrp5 = -4,
+                                 ethgrp2 = -4,
+                                 cigsta3 = -1, 
+                                 nssec8 = -9, 
+                                 paidemployment = -1)) %>% 
+  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, nssec8 = 99, qual7 = -1,
+                                 drink = -8, ethgrp2 = -9, ethgrp5 = -9)) %>% 
+    replace_with_na(replace = list(drink = -9, ethgrp2 = -8, ethgrp5 = -8,
+                                 cigsta3 = -8)) %>% 
+  replace_with_na(replace = list(ethgrp2 = -1, ethgrp5 = -1))
 
@@
   select(ID, Sex, age, area, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2, MVPAtime,
-         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y56, wtn_Y56, wtb_Y56, cluster1, cluster2, cluster3, 
+         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y56, wtn_Y56, wtb_Y56, ethgrp5, ethgrp2, qual7,
+         cluster1, cluster2, cluster3, nssec8, paidemployment, eqvinc, MarSt2,
          cluster4, cluster5, area, gor) %>% 
-  mutate(Years = "5-6") %>% 
+  mutate(Years = "5-6", MarStat = NA) %>% 
   rename(wti = wti_Y56, wtn = wtn_Y56, wtb = wtb_Y56, drink = dnoft3) %>% 
-  replace_with_na(replace = list(bmival = -1, 
-                                 wstval = -1, 
-                                 bpmedd2 = -1, 
-                                 bpmedc2 = -1,
+  replace_with_na(replace = list(bmival = -1, paidemployment = -9,
+                                 wstval = -1, qual7 = -8,
+                                 bpmedd2 = -1, eqvinc = -1,
+                                 bpmedc2 = -1, MarSt2 = -1,
                                  hyper140_2 = -7, 
@@
                                  drink = -1,
+                                 ethgrp5 = -4,
+                                 ethgrp2 = -4,
                                  cigsta3 = -1,
-                                 MVPAtime = -1)) %>% 
-  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, 
-                                 drink = -8)) %>% 
-    replace_with_na(replace = list(drink = -9,
+                                 MVPAtime = -1, 
+                                 nssec8 = -9)) %>% 
+  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, paidemployment = -8,
+                                 drink = -8, nssec8 = 99)) %>% 
+    replace_with_na(replace = list(drink = -9, paidemployment = -1, qual7 = -1,
                                  cigsta3 = -8))
@@
   select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc, bpmedd, hyper140, hibp140, MVPAtime,
-         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_CY1234, wtn_CY1234, wtb_CY1234, cluster, area, gor) %>%
+         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_CY1234, wtn_CY1234, wtb_CY1234, ethgr5, ethgr2,
+         cluster, area, gor, nssec8, paidemployment, qual7, eqvinc, MarSt2, MarStat) %>%
   rename(hyper140_2 = hyper140, hibp140_2 = hibp140, bpmedd2 = bpmedd, 
-         bpmedc2 = bpmedc, cluster1 = cluster, 
+         bpmedc2 = bpmedc, cluster1 = cluster, ethgrp5 = ethgr5, ethgrp2 = ethgr2, 
          wti = wti_CY1234, wtn = wtn_CY1234, wtb =  wtb_CY1234, drink = dnoft3) %>% 
   mutate(cluster2 = NA, cluster3 = NA, cluster4 = NA, cluster5 = NA, Years = "1-4") %>% 
-  replace_with_na(replace = list(bmival = -1, 
-                                 wstval = -1, 
-                                 bpmedd2 = -1, 
-                                 bpmedc2 = -1,
-                                 hyper140_2 = -7, 
+  replace_with_na(replace = list(bmival = -1, paidemployment = -9, 
+                                 wstval = -1, qual7 = -8,
+                                 bpmedd2 = -1, eqvinc = -1,
+                                 bpmedc2 = -1, MarSt2 = -4, 
+                                 hyper140_2 = -7, MarStat = -4,
                                  # hyper140_2 = -1, 
@@
                                  drink = -1,
+                                 ethgrp5 = -4,
+                                 ethgrp2 = -4,
                                  cigsta3 = -1,
-                                 MVPAtime = -4)) %>% 
-  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, MVPAtime = -1,
-                                 drink = -8)) %>% 
-  replace_with_na(replace = list(drink = -9,
-                                 cigsta3 = -8))
+                                 MVPAtime = -4, 
+                                 nssec8 = -8)) %>% 
+  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, MVPAtime = -1, paidemployment = -8,
+                                 drink = -8, nssec8 = -1, qual7 = -1, MarSt2 = -1)) %>% 
+  replace_with_na(replace = list(drink = -9, paidemployment = -4,
+                                 cigsta3 = -8, nssec8 = 99)) %>% 
+  replace_with_na(replace = list(paidemployment = -1))
 
@@
 
-CW3CB3 <- read_table2("~/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB3.txt",  
+CW3CB3 <- read_table2("~/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB2.txt",  
                               col_names = FALSE)# change the path to your own path
@@
                    "Midnight.food", "ID_DAY", "AGE", "SEX", "CPROB1",
-                      "CPROB2", "CPROB3", "CPROB4", "CPROB5", "CPROB6", "CPROB7", "CPROB8", "CPROB9",
+                      "CPROB2", "CPROB3", "CPROB4", "CPROB5", "CPROB6", 
                       "CB", "CW", "MLCJOINT", "ID")
@@
 # write_dta(LCGA_2class, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/LCGA_2class.dta")
-write_dta(CW3CB3_regss, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW3CB2_7regss.dta")
+write_dta(CW3CB3_regss, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW3CB3_7regss.dta")
 # write_dta(CW2CB2_regss, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW2CB2_regss.dta")
 ```
+
+## Association between day-level classes and weekdays
+
+```{r dayweek, echo=FALSE, message=FALSE}
+
+CW3CB3 <- read_table2("~/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB2.txt",  
+                              col_names = FALSE)# change the path to your own path
+
+names(CW3CB3) <- c("Breakfast", "Morning.snack", "Lunch",
+                   "Afternoon.snack", "Dinner", "Before.bedtime.snack",
+                   "Midnight.food", "ID_DAY", "AGE", "SEX", "CPROB1",
+                      "CPROB2", "CPROB3", "CPROB4", "CPROB5", "CPROB6", 
+                      "CB", "CW", "MLCJOINT", "ID")
+
+dta_NDNS <- read_csv("/home/wangcc-me/Documents/LSHTMproject/Rcode/dta_NDNS.csv") # extract the day of week data
+
+CW3idday <- CW3CB3 %>% 
+  select(ID, ID_DAY, CW, CB, MLCJOINT, AGE, SEX)
+
+CW3idday$DayNo <- ave(CW3idday$ID_DAY, CW3idday$ID, FUN = seq_along) # adding the day no
+
+dta_DayofWeek <- dta_NDNS %>% 
+  select(id, id_dy, DayofWeek)
+
+dta_DayofWeek$DayNo <- unlist(strsplit(dta_DayofWeek$id_dy,"D"))[c(FALSE, TRUE)] # creating a day no
+names(dta_DayofWeek)[1] <- "ID"
+dta_DayofWeek$DayNo <- as.numeric(dta_DayofWeek$DayNo)
+
+CW3idday <-   CW3idday %>%  
+  left_join(dta_DayofWeek, by= c("ID", "DayNo"))
+
+CW3idday$DayofWeek[CW3idday$ID_DAY == 40714261000] <- "Saturday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 112050710000] <- "Tuesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 310122510000] <- "Wednesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 5050616100] <- "Monday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 50506161000] <- "Tuesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 505061610000] <- "Wednesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 7090824100] <- "Monday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 70908241000] <- "Tuesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 709082410000] <- "Wednesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 807021910000] <- "Monday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 812101310000] <- "Sunday"
+
+with(CW3idday, tabpct(DayofWeek, CW))
+with(CW3idday, chisq.test(DayofWeek, CW))
+
+CW3idday$Weekend <- ifelse((CW3idday$DayofWeek == "Sunday" | CW3idday$DayofWeek == "Saturday"), TRUE, FALSE)
+
+with(CW3idday, tabpct(Weekend, CW))
+with(CW3idday, chisq.test(Weekend, CW))
+
+CW3CB3_reg <- CW3CB3[!duplicated(CW3CB3$ID), ]
+
+CW3CB3_reg <- CW3CB3_reg %>% 
+  select(ID, AGE, SEX, CB) # extract only the CB variable (Between individual classes == 1 or 2)
+```
+
+## Social economic
 
@@
 
-dt[28, 1] <- c("Hypertension (%) [note]")
-dt[32, 1] <- c("Carbohydrate\npercent (%) [note]")
-dt[35, 1] <- c("DM [note]")
-dt[36, 1] <- c("Physical\nactivity (hours/day) [note]")
+# 
+# dt[28, 1] <- c("Hypertension (%) [note]")
+# dt[32, 1] <- c("Carbohydrate\npercent (%) [note]")
+# dt[35, 1] <- c("DM [note]")
+# dt[36, 1] <- c("Physical\nactivity (hours/day) [note]")
+dt[20, 1] <- c("Paid employment[note] (%)")
+dt[23, 1] <- c("Live with partner[note] (%)")
 
 kable(dt,  align = "l", escape = F, row.names = FALSE,
-              format = "html", caption = "Means, percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
+              format = "html", caption = "Means, row percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
  kable_styling(font_size = 16, 
@@
         position = "center", full_width = FALSE) %>% 
-  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
-  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.",
+  add_indent(c(3:6, 9, 10, 12:19, 21, 22, 24, 25, 28, 29, 31, 32)) %>% 
+  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;"
+                       # " BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
+                       # "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
+                       # "Glucose and A1C levels are estimated in subgroups of people without diabetes."
+                       )) %>% 
+  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across >2 classes.
+For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
+                 "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
+                 "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
+                 # "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
+                 # "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
+                 # "DM was defined by A1C > 6.5%.", 
+                 # "Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey."
+                 ), 
+               notation = "symbol")
+```
+
+## Anthropometric measurements and biochemical analysis
+
+```{r tab2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Timeslots_CW3CB3table2_bmiDM.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "Latent class = 3", "P value [note]")
+
+# 
+dt[9, 1] <- c("Hypertension[note] (%)")
+dt[12, 1] <- c("Carbohydrate percent[note] (%)")
+
+dt[21, 1] <- c("Physical\nactivity (hours/day) [note]")
+dt[20, 1] <- c("DM [note]")
+# dt[20, 1] <- c("Paid employment[note] (%)")
+# dt[23, 1] <- c("Live with partner[note] (%)")
+
+kable(dt,  align = "l", escape = F, row.names = FALSE,
+              format = "html", caption = "Means, column percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
+ kable_styling(font_size = 16, 
+        bootstrap_options = c("striped", "hover", "condensed"),
+        position = "center", full_width = FALSE) %>% 
+  add_indent(c(4:6,8,10)) %>% 
+  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;",
+                        " BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
                         "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
@@
 For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
+                 # "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
+                 # "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
                  "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.",
@@
                  "DM was defined by A1C > 6.5%.",
-                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey."), 
+                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey."
+                 ), 
                notation = "symbol")
@@
 
-# LCGA results (3 classes)
+<!-- # LCGA results (3 classes) -->
 
-```{r tab1LCGA, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Timeslots_LCGA2classesresults.csv", header = T, row.names = NULL, colClasses = "character")
-names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "Latent class = 3", "P value [note]")
+<!-- ```{r tab1LCGA, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE} -->
+<!-- dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Timeslots_LCGA2classesresults.csv", header = T, row.names = NULL, colClasses = "character") -->
+<!-- names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "Latent class = 3", "P value [note]") -->
 
-dt[28, 1] <- c("Hypertension (%) [note]")
-dt[32, 1] <- c("Carbohydrate\npercent (%) [note]")
-dt[35, 1] <- c("DM [note]")
-dt[36, 1] <- c("Physical\nactivity (hours/day) [note]")
+<!-- dt[28, 1] <- c("Hypertension (%) [note]") -->
+<!-- dt[32, 1] <- c("Carbohydrate\npercent (%) [note]") -->
+<!-- dt[35, 1] <- c("DM [note]") -->
+<!-- dt[36, 1] <- c("Physical\nactivity (hours/day) [note]") -->
 
-kable(dt,  align = "l", escape = F, row.names = FALSE,
-              format = "html", caption = "Means, percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
- kable_styling(font_size = 16, 
-        bootstrap_options = c("striped", "hover", "condensed"),
-        position = "center", full_width = FALSE) %>% 
-  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
-  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.",
-                       "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
-                       "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
-  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across >2 classes.
-For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
-                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
-                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
-                 "DM was defined by A1C > 6.5%.", 
-                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey."), 
-               notation = "symbol")
-```
+<!-- kable(dt,  align = "l", escape = F, row.names = FALSE, -->
+<!--               format = "html", caption = "Means, percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>% -->
+<!--  kable_styling(font_size = 16,  -->
+<!--         bootstrap_options = c("striped", "hover", "condensed"), -->
+<!--         position = "center", full_width = FALSE) %>%  -->
+<!--   add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>%  -->
+<!--   footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.",  -->
+<!--                        "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.",  -->
+<!--                        "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>%  -->
+<!--   add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across >2 classes.
+For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.", -->
+<!--                  "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.",  -->
+<!--                  "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake", -->
+<!--                  "DM was defined by A1C > 6.5%.",  -->
+<!--                  "Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey."),  -->
+<!--                notation = "symbol") -->
+<!-- ``` -->

### 2018-08-02 paper/Chapters/Chapter3.tex
level1 level2 fig added

@@
 		\toprule
-		\textbf{Time slots of} & \textbf{Responses of} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1\\(30.8\%)}} & \textbf{\Centerstack{Class 2\\(39.8\%)}} & \textbf{\Centerstack{Class 3\\(29.5\%)}} \\
+		\textbf{Time slots of} & \textbf{Responses of} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1\\(39.5\%)}} & \textbf{\Centerstack{Class 2\\(20.4\%)}} & \textbf{\Centerstack{Class 3\\(40.1\%)}} \\
 		\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
-		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & (\%) & \textbf{\Centerstack{High carbo- \\ hydrate day}} & \textbf{\Centerstack{Lower carbo-\\hydrate day}} & \textbf{Regular day}\\
+		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & (\%) & \textbf{\Centerstack{High carbo- \\ hydrate day}} & \textbf{\Centerstack{Low carbo-\\hydrate day}} & \textbf{\Centerstack{Regular\\meals day}}\\
 		\midrule
@@
 		6 am – 9 am &  &  &  &  &  & \\
-		& Not eating & 7655 & 31.2 & 0.129 & 0.45 & 0.32\\
-		& Carbohydrate $<$ 50\%\textsuperscript{*} & 4500 & 18.4 & 0.13 & 0.267 & 0.128\\
+		& Not eating & 7655 & 31.2 & 0.129 & 0.450 & 0.320\\
+		& Carbohydrate $<$ 50\%\textsuperscript{*} & 4500 & 18.4 & 0.130 & 0.267 & 0.128\\
 		& Carbohydrate $\geqslant$ 50\%\textsuperscript{\dag} & 12328 & 50.4 & 0.741 & 0.283 & 0.552\\
@@
 		& Not eating & 4783 & 19.5 & 0.156 & 0.356 & 0.019\\
-		& Carbohydrate $<$ 50\% & 11112 & 45.4 & 0.405 & 0.413 & 0.56\\
+		& Carbohydrate $<$ 50\% & 11112 & 45.4 & 0.405 & 0.413 & 0.560\\
 		& Carbohydrate $\geqslant$ 50\% & 8588 & 35.1 & 0.439 & 0.231 & 0.421\\
 		2 pm – 5 pm &  &  &  &  &  & \\
-		& Not eating & 6926 & 28.3 & 0.13 & 0.123 & 0.659\\
+		& Not eating & 6926 & 28.3 & 0.130 & 0.123 & 0.659\\
 		& Carbohydrate $<$ 50\% & 8277 & 33.8 & 0.249 & 0.602 & 0.076\\
@@
 		& Not eating & 3043 & 12.4 & 0.114 & 0.199 & 0.034\\
-		& Carbohydrate $<$ 50\% & 14240 & 58.2 & 0.516 & 0.59 & 0.639\\
-		& Carbohydrate $\geqslant$ 50\% & 7200 & 29.4 & 0.37 & 0.211 & 0.328\\
+		& Carbohydrate $<$ 50\% & 14240 & 58.2 & 0.516 & 0.590 & 0.639\\
+		& Carbohydrate $\geqslant$ 50\% & 7200 & 29.4 & 0.370 & 0.211 & 0.328\\
 		8 pm – 10 pm &  &  &  &  &  & \\
-		& Not eating & 8722 & 35.6 & 0.322 & 0.291 & 0.48\\
+		& Not eating & 8722 & 35.6 & 0.322 & 0.291 & 0.480\\
 		& Carbohydrate $<$ 50\% & 8898 & 36.3 & 0.266 & 0.551 & 0.212\\
@@
 		10 pm – 6 am &  &  &  &  &  & \\
-		& Not eating & 16295 & 66.6 & 0.68 & 0.59 & 0.751\\
+		& Not eating & 16295 & 66.6 & 0.680 & 0.590 & 0.751\\
 		& Carbohydrate $<$ 50\% & 4144 & 16.9 & 0.074 & 0.294 & 0.101\\
@@
 
-%-----------------------------------
+\begin{figure}
+	%\vspace*{13cm}
+	\centering
+	\includegraphics{Figures/level1.png}
+	\decoRule
+	\caption[Day Level Latent Classes.]{Day Level Latent Classes.}
+	\label{fig:level1}
+\end{figure}
+\vspace{-0.6cm}
+
+%---------------------------------
+
+--
 %	SUBSECTION 2
@@
 \section{Main Section 2}
+
+\begin{figure}
+	%\vspace*{13cm}
+	\centering
+	\includegraphics[width=13cm]{Figures/level2.png}
+	\decoRule
+	\caption[Individual Level Latent Classes.]{individual Level Latent Classes.}
+	\label{fig:level2}
+\end{figure}
+\vspace{-0.6cm}
 

### 2018-08-02 paper/Tables/2by2Table1.Rmd
level1 level2 fig added

@@
 ```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Daylevel.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c(" ", "High carbohydrate day", "Low carbohydrate day", "Regular meals day", "P value [note]")
+
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "Characteristics of different types of days according to carbohydrate intake", booktabs = T,linesep = "") %>%
+ kable_styling(latex_options = c("striped"), font_size = 9)
+
+```

### 2018-08-02 paper/Tables/2by2Table1.tex
level1 level2 fig added

@@
 
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-6}Characteristics of different types of days according to carbohydrate intake}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{lllll}
+\hiderowcolors
+\toprule
+  & High carbohydrate day & Low carbohydrate day & Regular meals day & P value [note]\\
+\midrule
+\showrowcolors
+n & 9667 & 5002 & 9814 & \\
+Country (\%) &  &  &  & <0.001\\
+England & 5627 (58.2) & 2972 (59.4) & 5291 (53.9) & \\
+NI & 1194 (12.4) & 527 (10.5) & 1400 (14.3) & \\
+Scotland & 1527 (15.8) & 813 (16.3) & 1774 (18.1) & \\
+Wales & 1318 (13.6) & 690 (13.8) & 1349 (13.7) & \\
+Day of Week (\%) &  &  &  & <0.001\\
+Monday & 1303 (13.5) & 715 (14.3) & 1370 (14.0) & \\
+Tuesday & 1266 (13.1) & 674 (13.5) & 1290 (13.1) & \\
+Wednesday & 1225 (12.7) & 740 (14.8) & 1233 (12.6) & \\
+Thursday & 1272 (13.2) & 752 (15.0) & 1425 (14.5) & \\
+Friday & 1458 (15.1) & 797 (15.9) & 1479 (15.1) & \\
+Saturday & 1537 (15.9) & 703 (14.1) & 1495 (15.2) & \\
+Sunday & 1605 (16.6) & 621 (12.4) & 1522 (15.5) & \\
+Weekend, Yes (\%) & 3142 (32.5) & 1324 (26.5) & 3017 (30.7) & <0.001\\
+Total energy (kJ) & 7539.98 (2875.87) & 7160.22 (2922.15) & 7439.68 (2978.91) & <0.001\\
+Carbohydrate (g) & 222.79 (89.84) & 209.70 (86.17) & 206.59 (84.42) & <0.001\\
+Protein (g) & 71.36 (29.79) & 69.55 (30.20) & 73.29 (32.94) & <0.001\\
+Fat (g) & 65.44 (33.27) & 63.94 (33.76) & 67.24 (34.73) & <0.001\\
+Alcohol (g) & 11.76 (27.31) & 8.85 (24.25) & 13.80 (33.00) & <0.001\\
+Total sugars (g) & 98.63 (56.03) & 88.03 (50.50) & 86.39 (50.96) & <0.001\\
+Starch (g) & 124.07 (55.84) & 121.59 (56.13) & 120.11 (54.62) & <0.001\\
+Non-Milk Extrinsic Sugar (g) & 59.45 (49.31) & 50.07 (43.41) & 50.41 (44.84) & <0.001\\
+Fruit (g) & 107.40 (137.97) & 103.15 (129.08) & 92.76 (126.02) & <0.001\\
+Yellow Red Green Vegetables (g) & 26.52 (46.44) & 26.84 (47.99) & 26.16 (45.99) & 0.681\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
 \end{document}

### 2018-08-02 results/Timeslots/multilevel.Rmd
level1 level2 fig added

@@
 
-# (CW = 2) Level 1 latent classes
+<!-- # (CW = 2) Level 1 latent classes  -->
 
-## Visualisation of level 1 latent classes
+<!-- ## Visualisation of level 1 latent classes  -->
 
-```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+<!-- ```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE} -->
 
-CW2CB2 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW2CB2.txt",
-                         col_names = FALSE)
+<!-- CW2CB2 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW2CB2.txt", -->
+<!--                          col_names = FALSE) -->
 
-names(CW2CB2) <- c("Breakfast", 
-                   "Morning.snack",
-                   "Lunch",
-                   "Afternoon.snack",
-                   "Dinner",
-                   "Before.bedtime.snack",
-                   "Midnight.food",
-                      "ID_DAY",
-                      "AGE",
-                      "SEX",
-                      "CPROB1",
-                      "CPROB2",
-                      "CPROB3",
-                      "CPROB4",
-                      # "CPROB5",
-                      # "CPROB6",
-                      "CB",
-                      "CW",
-                      "MLCJOINT",
-                      "ID")
+<!-- names(CW2CB2) <- c("Breakfast",  -->
+<!--                    "Morning.snack", -->
+<!--                    "Lunch", -->
+<!--                    "Afternoon.snack", -->
+<!--                    "Dinner", -->
+<!--                    "Before.bedtime.snack", -->
+<!--                    "Midnight.food", -->
+<!--                       "ID_DAY", -->
+<!--                       "AGE", -->
+<!--                       "SEX", -->
+<!--                       "CPROB1", -->
+<!--                       "CPROB2", -->
+<!--                       "CPROB3", -->
+<!--                       "CPROB4", -->
+<!--                       # "CPROB5", -->
+<!--                       # "CPROB6", -->
+<!--                       "CB", -->
+<!--                       "CW", -->
+<!--                       "MLCJOINT", -->
+<!--                       "ID") -->
 
-pp <- CW2CB2 %>% 
-  group_by(CW) %>% 
-  summarise(Breakfast_0 = sum(Breakfast == 0)/length(Breakfast), 
-            Breakfast_1 = sum(Breakfast == 1)/length(Breakfast), 
-            Breakfast_2 = sum(Breakfast == 2)/length(Breakfast),
-            Morning.snack_0 = sum(Morning.snack == 0)/length(Morning.snack),
-            Morning.snack_1 = sum(Morning.snack == 1)/length(Morning.snack), 
-            Morning.snack_2 = sum(Morning.snack == 2)/length(Morning.snack),
-            Lunch_0 = sum(Lunch == 0)/length(Lunch),
-            Lunch_1 = sum(Lunch == 1)/length(Lunch), 
-            Lunch_2 = sum(Lunch == 2)/length(Lunch),
-            Afternoon.snack_0 = sum(Afternoon.snack == 0)/length(Afternoon.snack),
-            Afternoon.snack_1 = sum(Afternoon.snack == 1)/length(Afternoon.snack), 
-            Afternoon.snack_2 = sum(Afternoon.snack == 2)/length(Afternoon.snack),
-            Dinner_0 = sum(Dinner == 0)/length(Dinner),
-            Dinner_1 = sum(Dinner == 1)/length(Dinner), 
-            Dinner_2 = sum(Dinner == 2)/length(Dinner),
-            Before.bedtime.snack_0 = sum(Before.bedtime.snack == 0)/length(Before.bedtime.snack),
-            Before.bedtime.snack_1 = sum(Before.bedtime.snack == 1)/length(Before.bedtime.snack), 
-            Before.bedtime.snack_2 = sum(Before.bedtime.snack == 2)/length(Before.bedtime.snack),
-            Midnight.food_0 = sum(Midnight.food == 0)/length(Midnight.food),
-            Midnight.food_1 = sum(Midnight.food == 1)/length(Midnight.food), 
-            Midnight.food_2 = sum(Midnight.food == 2)/length(Midnight.food))
+<!-- pp <- CW2CB2 %>%  -->
+<!--   group_by(CW) %>%  -->
+<!--   summarise(Breakfast_0 = sum(Breakfast == 0)/length(Breakfast),  -->
+<!--             Breakfast_1 = sum(Breakfast == 1)/length(Breakfast),  -->
+<!--             Breakfast_2 = sum(Breakfast == 2)/length(Breakfast), -->
+<!--             Morning.snack_0 = sum(Morning.snack == 0)/length(Morning.snack), -->
+<!--             Morning.snack_1 = sum(Morning.snack == 1)/length(Morning.snack),  -->
+<!--             Morning.snack_2 = sum(Morning.snack == 2)/length(Morning.snack), -->
+<!--             Lunch_0 = sum(Lunch == 0)/length(Lunch), -->
+<!--             Lunch_1 = sum(Lunch == 1)/length(Lunch),  -->
+<!--             Lunch_2 = sum(Lunch == 2)/length(Lunch), -->
+<!--             Afternoon.snack_0 = sum(Afternoon.snack == 0)/length(Afternoon.snack), -->
+<!--             Afternoon.snack_1 = sum(Afternoon.snack == 1)/length(Afternoon.snack),  -->
+<!--             Afternoon.snack_2 = sum(Afternoon.snack == 2)/length(Afternoon.snack), -->
+<!--             Dinner_0 = sum(Dinner == 0)/length(Dinner), -->
+<!--             Dinner_1 = sum(Dinner == 1)/length(Dinner),  -->
+<!--             Dinner_2 = sum(Dinner == 2)/length(Dinner), -->
+<!--             Before.bedtime.snack_0 = sum(Before.bedtime.snack == 0)/length(Before.bedtime.snack), -->
+<!--             Before.bedtime.snack_1 = sum(Before.bedtime.snack == 1)/length(Before.bedtime.snack),  -->
+<!--             Before.bedtime.snack_2 = sum(Before.bedtime.snack == 2)/length(Before.bedtime.snack), -->
+<!--             Midnight.food_0 = sum(Midnight.food == 0)/length(Midnight.food), -->
+<!--             Midnight.food_1 = sum(Midnight.food == 1)/length(Midnight.food),  -->
+<!--             Midnight.food_2 = sum(Midnight.food == 2)/length(Midnight.food)) -->
 
-pp_long <- pp %>% 
-  gather(Hour, Prob, -CW) %>% 
-  separate(Hour, into = c("Slots", "Carbo"), sep = "_")
+<!-- pp_long <- pp %>%  -->
+<!--   gather(Hour, Prob, -CW) %>%  -->
+<!--   separate(Hour, into = c("Slots", "Carbo"), sep = "_")  -->
 
-pp_long$Slots <- factor(pp_long$Slots, levels = c("Breakfast", 
-                   "Morning.snack",
-                   "Lunch",
-                   "Afternoon.snack",
-                   "Dinner",
-                   "Before.bedtime.snack",
-                   "Midnight.food"))
-```
+<!-- pp_long$Slots <- factor(pp_long$Slots, levels = c("Breakfast",  -->
+<!--                    "Morning.snack", -->
+<!--                    "Lunch", -->
+<!--                    "Afternoon.snack", -->
+<!--                    "Dinner", -->
+<!--                    "Before.bedtime.snack", -->
+<!--                    "Midnight.food")) -->
+<!-- ``` -->
 
-```{r echo=FALSE, fig.height=6, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
-library(ggthemr)
-ggthemr("fresh", layout = "scientific")
-library(ggplot2)
+<!-- ```{r echo=FALSE, fig.height=6, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE} -->
+<!-- library(ggthemr) -->
+<!-- ggthemr("fresh", layout = "scientific") -->
+<!-- library(ggplot2) -->
 
-pp_long$Time <- as.character(pp_long$Slots)
-pp_long$Time[pp_long$Slots == "Breakfast"] <- 7.5
-pp_long$Time[pp_long$Slots == "Morning.snack"] <- 10.5
-pp_long$Time[pp_long$Slots == "Lunch"] <- 13
-pp_long$Time[pp_long$Slots == "Afternoon.snack"] <- 15.5
-pp_long$Time[pp_long$Slots == "Dinner"] <- 18.5
-pp_long$Time[pp_long$Slots == "Before.bedtime.snack"] <- 21
-pp_long$Time[pp_long$Slots == "Midnight.food"] <- 26
-pp_long$Time <- as.numeric(pp_long$Time)
+<!-- pp_long$Time <- as.character(pp_long$Slots) -->
+<!-- pp_long$Time[pp_long$Slots == "Breakfast"] <- 7.5 -->
+<!-- pp_long$Time[pp_long$Slots == "Morning.snack"] <- 10.5 -->
+<!-- pp_long$Time[pp_long$Slots == "Lunch"] <- 13 -->
+<!-- pp_long$Time[pp_long$Slots == "Afternoon.snack"] <- 15.5 -->
+<!-- pp_long$Time[pp_long$Slots == "Dinner"] <- 18.5 -->
+<!-- pp_long$Time[pp_long$Slots == "Before.bedtime.snack"] <- 21 -->
+<!-- pp_long$Time[pp_long$Slots == "Midnight.food"] <- 26 -->
+<!-- pp_long$Time <- as.numeric(pp_long$Time) -->
 
-ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo))  + 
-  scale_x_continuous(limits = c(6, 29),
-  breaks = seq(6, 29, by = 1)) +
-  annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
-            alpha = 0.5, fill = "grey") + 
-  annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
-             alpha = 0.5, fill = "grey") + 
-  annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00, 
-            alpha = 0.5, fill = "grey") + 
-  annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
-             alpha = 0.5, fill = "grey") +
-  geom_point(size = 3) + 
-  geom_line(size = 1.5) + 
-  theme(axis.title = element_text(size = 18), 
-        axis.text = element_text(size = 18), 
-        axis.line = element_line(colour = "black"), 
-        panel.border = element_blank(), 
-        panel.background = element_blank(), 
-        legend.text = element_text(size = 15), 
-        legend.title = element_text(size = 15) 
-        # legend.position = "bottom", 
-        # legend.direction = "horizontal"
-  ) + 
-    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  labs(title = "Class 1 days", x = "Hours of the day (next day from hour 24)", y = "Probability",
-       color = "Carbohydrate\nintake") + 
-  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
-  ylim(c(0,1)) #+ 
-  # scale_x_discrete(labels = c("6","7","8","9","10","11","12","13","14",
-  #                             "15","16","17","18","19", "20","21","22",
-  #                             "23","0","1","2","3","4","5"))
+<!-- ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo))  +  -->
+<!--   scale_x_continuous(limits = c(6, 29), -->
+<!--   breaks = seq(6, 29, by = 1)) + -->
+<!--   annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00,  -->
+<!--             alpha = 0.5, fill = "grey") +  -->
+<!--   annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00,  -->
+<!--              alpha = 0.5, fill = "grey") +  -->
+<!--   annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00,  -->
+<!--             alpha = 0.5, fill = "grey") +  -->
+<!--   annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00,  -->
+<!--              alpha = 0.5, fill = "grey") + -->
+<!--   geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--   ) +  -->
+<!--     # theme(axis.text.x = element_text(angle = 60, hjust = 1)) +  -->
+<!--   labs(title = "Class 1 days", x = "Hours of the day (next day from hour 24)", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) +  -->
+<!--   ylim(c(0,1)) #+  -->
+<!--   # scale_x_discrete(labels = c("6","7","8","9","10","11","12","13","14", -->
+<!--   #                             "15","16","17","18","19", "20","21","22", -->
+<!--   #                             "23","0","1","2","3","4","5")) -->
 
-ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo)) + 
-  scale_x_continuous(limits = c(6, 29),
-  breaks = seq(6, 29, by = 1)) +
-  annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
-            alpha = 0.5, fill = "grey") + 
-  annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
-             alpha = 0.5, fill = "grey") + 
-  annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00, 
-            alpha = 0.5, fill = "grey") + 
-  annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
-             alpha = 0.5, fill = "grey") +
-  geom_point(size = 3) + 
-  geom_line(size = 1.5) + 
-  theme(axis.title = element_text(size = 18), 
-        axis.text = element_text(size = 18), 
-        axis.line = element_line(colour = "black"), 
-        panel.border = element_blank(), 
-        panel.background = element_blank(), 
-        legend.text = element_text(size = 15), 
-        legend.title = element_text(size = 15) 
-        # legend.position = "bottom", 
-        # legend.direction = "horizontal"
-  ) + 
-    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  labs(title = "Class 2 days", x = "Hours of the day (next day from hour 24)", y = "Probability",
-       color = "Carbohydrate\nintake") + 
-  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
-  ylim(c(0,1))
+<!-- ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo)) +  -->
+<!--   scale_x_continuous(limits = c(6, 29), -->
+<!--   breaks = seq(6, 29, by = 1)) + -->
+<!--   annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00,  -->
+<!--             alpha = 0.5, fill = "grey") +  -->
+<!--   annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00,  -->
+<!--              alpha = 0.5, fill = "grey") +  -->
+<!--   annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00,  -->
+<!--             alpha = 0.5, fill = "grey") +  -->
+<!--   annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00,  -->
+<!--              alpha = 0.5, fill = "grey") + -->
+<!--   geom_point(size = 3) +  -->
+<!--   geom_line(size = 1.5) +  -->
+<!--   theme(axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 18),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         panel.border = element_blank(),  -->
+<!--         panel.background = element_blank(),  -->
+<!--         legend.text = element_text(size = 15),  -->
+<!--         legend.title = element_text(size = 15)  -->
+<!--         # legend.position = "bottom",  -->
+<!--         # legend.direction = "horizontal" -->
+<!--   ) +  -->
+<!--     # theme(axis.text.x = element_text(angle = 60, hjust = 1)) +  -->
+<!--   labs(title = "Class 2 days", x = "Hours of the day (next day from hour 24)", y = "Probability", -->
+<!--        color = "Carbohydrate\nintake") +  -->
+<!--   scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) +  -->
+<!--   ylim(c(0,1)) -->
 
-```
+<!-- ``` -->
 
-## Visualisation of level 2 latent classes (CB = 2)
+<!-- ## Visualisation of level 2 latent classes (CB = 2) -->
 
-```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}
+<!-- ```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE} -->
 
-# ndnsNNN <- read_csv("results/ndnsNNN.dat")
-# dt <- ndnsNNN[, c(2,5)]
-# names(dt) <- c("ID_DAY", "DayofWeek")
-# 
-# 
-# CW2CB2 <- CW2CB2 %>% 
-#   left_join(dt, by = "ID_DAY")
-#
+<!-- # ndnsNNN <- read_csv("results/ndnsNNN.dat") -->
+<!-- # dt <- ndnsNNN[, c(2,5)] -->
+<!-- # names(dt) <- c("ID_DAY", "DayofWeek") -->
+<!-- #  -->
+<!-- #  -->
+<!-- # CW2CB2 <- CW2CB2 %>%  -->
+<!-- #   left_join(dt, by = "ID_DAY") -->
+<!-- #  -->
 
-chart.data <- CW2CB2 %>% 
-  group_by(CB, CW) %>% 
-  tally %>% 
-  group_by(CB) %>% 
-  mutate(pct = n/sum(n))
+<!-- chart.data <- CW2CB2 %>%  -->
+<!--   group_by(CB, CW) %>%  -->
+<!--   tally %>%  -->
+<!--   group_by(CB) %>%  -->
+<!--   mutate(pct = n/sum(n)) -->
 
-chart.data <- ddply(chart.data, .(CB),
-                     transform, pos = cumsum(pct) - (0.5 * pct))
+<!-- chart.data <- ddply(chart.data, .(CB), -->
+<!--                      transform, pos = cumsum(pct) - (0.5 * pct)) -->
 
-chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"), 
-                        labels = c("Class 2 days", "Class 1 days"))
-chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"), 
-                        labels = c("Individual Class 1\n(56.3%)",  "Individual class 2\n(43.7%)"))
+<!-- chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"),  -->
+<!--                         labels = c("Class 2 days", "Class 1 days")) -->
+<!-- chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"),  -->
+<!--                         labels = c("Individual Class 1\n(56.3%)",  "Individual class 2\n(43.7%)")) -->
 
-library(ggthemr)
-ggthemr("dust", layout = "scientific")
-ggplot() + 
-  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
-           stat="identity") + 
-  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
-            size=4, colour="white", family="Atlas Grotesk Medium") + 
-  theme(legend.position="bottom", legend.direction="horizontal",
-        legend.title = element_blank(), 
-        axis.title = element_text(size = 18), 
-        axis.text = element_text(size = 15), 
-        axis.line = element_line(colour = "black"), 
-        plot.title=element_text(family="Atlas Grotesk Medium"),
-        text=element_text(family="Atlas Grotesk Light")) + 
-  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
-  scale_y_continuous(labels=percent)
-```
+<!-- library(ggthemr) -->
+<!-- ggthemr("dust", layout = "scientific") -->
+<!-- ggplot() +  -->
+<!--   geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6, -->
+<!--            stat="identity") +  -->
+<!--   geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")), -->
+<!--             size=4, colour="white", family="Atlas Grotesk Medium") +  -->
+<!--   theme(legend.position="bottom", legend.direction="horizontal", -->
+<!--         legend.title = element_blank(),  -->
+<!--         axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 15),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         plot.title=element_text(family="Atlas Grotesk Medium"), -->
+<!--         text=element_text(family="Atlas Grotesk Light")) +  -->
+<!--   labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") + -->
+<!--   scale_y_continuous(labels=percent) -->
+<!-- ``` -->
 
-## Visualisation of level 2 latent classes (CB = 3)
+<!-- ## Visualisation of level 2 latent classes (CB = 3) -->
 
-```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}
+<!-- ```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE} -->
 
-CW2CB3 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW2CB3.txt",
-                         col_names = FALSE)
+<!-- CW2CB3 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW2CB3.txt", -->
+<!--                          col_names = FALSE) -->
 
-names(CW2CB3) <- c("Breakfast", 
-                   "Morning.snack",
-                   "Lunch",
-                   "Afternoon.snack",
-                   "Dinner",
-                   "Before.bedtime.snack",
-                   "Midnight.food",
-                      "ID_DAY",
-                      "AGE",
-                      "SEX",
-                      "CPROB1",
-                      "CPROB2",
-                      "CPROB3",
-                      "CPROB4",
-                      "CPROB5",
-                      "CPROB6",
-                      "CB",
-                      "CW",
-                      "MLCJOINT",
-                      "ID")
+<!-- names(CW2CB3) <- c("Breakfast",  -->
+<!--                    "Morning.snack", -->
+<!--                    "Lunch", -->
+<!--                    "Afternoon.snack", -->
+<!--                    "Dinner", -->
+<!--                    "Before.bedtime.snack", -->
+<!--                    "Midnight.food", -->
+<!--                       "ID_DAY", -->
+<!--                       "AGE", -->
+<!--                       "SEX", -->
+<!--                       "CPROB1", -->
+<!--                       "CPROB2", -->
+<!--                       "CPROB3", -->
+<!--                       "CPROB4", -->
+<!--                       "CPROB5", -->
+<!--                       "CPROB6", -->
+<!--                       "CB", -->
+<!--                       "CW", -->
+<!--                       "MLCJOINT", -->
+<!--                       "ID") -->
 
-chart.data <- CW2CB3 %>% 
-  group_by(CB, CW) %>% 
-  tally %>% 
-  group_by(CB) %>% 
-  mutate(pct = n/sum(n))
+<!-- chart.data <- CW2CB3 %>%  -->
+<!--   group_by(CB, CW) %>%  -->
+<!--   tally %>%  -->
+<!--   group_by(CB) %>%  -->
+<!--   mutate(pct = n/sum(n)) -->
 
-# chart.data$CW[chart.data$CW == 1] <- 0 
-# chart.data$CW[chart.data$CW == 3] <- 1 
-# chart.data$CW[chart.data$CW == 0] <- 3
+<!-- # chart.data$CW[chart.data$CW == 1] <- 0  -->
+<!-- # chart.data$CW[chart.data$CW == 3] <- 1  -->
+<!-- # chart.data$CW[chart.data$CW == 0] <- 3  -->
 
-chart.data <- chart.data[order(chart.data$CB, chart.data$CW),]
-chart.data <- ddply(chart.data, .(CB), 
-                    transform, pos = cumsum(pct) - (0.5 * pct))
+<!-- chart.data <- chart.data[order(chart.data$CB, chart.data$CW),] -->
+<!-- chart.data <- ddply(chart.data, .(CB),  -->
+<!--                     transform, pos = cumsum(pct) - (0.5 * pct))  -->
 
-chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"), 
-                        labels = c("Class 2 days", "Class 1 days"))
-chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"), 
-                        labels = c("Individual\nclass 1\n(42.4%)",  "Individual\nclass 2\n(29.5%)", 
-                                   "Individual\nclass 3\n(28.1%)"))
+<!-- chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"),  -->
+<!--                         labels = c("Class 2 days", "Class 1 days")) -->
+<!-- chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"),  -->
+<!--                         labels = c("Individual\nclass 1\n(42.4%)",  "Individual\nclass 2\n(29.5%)",  -->
+<!--                                    "Individual\nclass 3\n(28.1%)")) -->
 
-library(ggthemr)
-ggthemr("dust", layout = "scientific")
-ggplot() + 
-  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
-           stat="identity") + 
-  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
-            size=4, colour="white", family="Atlas Grotesk Medium") + 
-  theme(legend.position="bottom", legend.direction="horizontal",
-        legend.title = element_blank(), 
-        axis.title = element_text(size = 18), 
-        axis.text = element_text(size = 15), 
-        axis.line = element_line(colour = "black"), 
-        plot.title=element_text(family="Atlas Grotesk Medium"),
-        text=element_text(family="Atlas Grotesk Light")) + 
-  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
-  scale_y_continuous(labels=percent)
-```
+<!-- library(ggthemr) -->
+<!-- ggthemr("dust", layout = "scientific") -->
+<!-- ggplot() +  -->
+<!--   geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6, -->
+<!--            stat="identity") +  -->
+<!--   geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")), -->
+<!--             size=4, colour="white", family="Atlas Grotesk Medium") +  -->
+<!--   theme(legend.position="bottom", legend.direction="horizontal", -->
+<!--         legend.title = element_blank(),  -->
+<!--         axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 15),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         plot.title=element_text(family="Atlas Grotesk Medium"), -->
+<!--         text=element_text(family="Atlas Grotesk Light")) +  -->
+<!--   labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") + -->
+<!--   scale_y_continuous(labels=percent) -->
+<!-- ``` -->
 
-## Visualisation of level 2 latent classes (CB = 4)
+<!-- ## Visualisation of level 2 latent classes (CB = 4) -->
 
-```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}
+<!-- ```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE} -->
 
-CW2CB4 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW2CB4.txt",
-                         col_names = FALSE)
+<!-- CW2CB4 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW2CB4.txt", -->
+<!--                          col_names = FALSE) -->
 
-names(CW2CB4) <- c("Breakfast", 
-                   "Morning.snack",
-                   "Lunch",
-                   "Afternoon.snack",
-                   "Dinner",
-                   "Before.bedtime.snack",
-                   "Midnight.food",
-                      "ID_DAY",
-                      "AGE",
-                      "SEX",
-                      "CPROB1",
-                      "CPROB2",
-                      "CPROB3",
-                      "CPROB4",
-                      "CPROB5",
-                      "CPROB6",
-                      "CPROB7",
-                      "CPROB8",
-                      "CB",
-                      "CW",
-                      "MLCJOINT",
-                      "ID")
+<!-- names(CW2CB4) <- c("Breakfast",  -->
+<!--                    "Morning.snack", -->
+<!--                    "Lunch", -->
+<!--                    "Afternoon.snack", -->
+<!--                    "Dinner", -->
+<!--                    "Before.bedtime.snack", -->
+<!--                    "Midnight.food", -->
+<!--                       "ID_DAY", -->
+<!--                       "AGE", -->
+<!--                       "SEX", -->
+<!--                       "CPROB1", -->
+<!--                       "CPROB2", -->
+<!--                       "CPROB3", -->
+<!--                       "CPROB4", -->
+<!--                       "CPROB5", -->
+<!--                       "CPROB6", -->
+<!--                       "CPROB7", -->
+<!--                       "CPROB8", -->
+<!--                       "CB", -->
+<!--                       "CW", -->
+<!--                       "MLCJOINT", -->
+<!--                       "ID") -->
 
-chart.data <- CW2CB4 %>% 
-  group_by(CB, CW) %>% 
-  tally %>% 
-  group_by(CB) %>% 
-  mutate(pct = n/sum(n))
+<!-- chart.data <- CW2CB4 %>%  -->
+<!--   group_by(CB, CW) %>%  -->
+<!--   tally %>%  -->
+<!--   group_by(CB) %>%  -->
+<!--   mutate(pct = n/sum(n)) -->
 
-# chart.data$CW[chart.data$CW == 1] <- 0 
-# chart.data$CW[chart.data$CW == 3] <- 1 
-# chart.data$CW[chart.data$CW == 0] <- 3
+<!-- # chart.data$CW[chart.data$CW == 1] <- 0  -->
+<!-- # chart.data$CW[chart.data$CW == 3] <- 1  -->
+<!-- # chart.data$CW[chart.data$CW == 0] <- 3  -->
 
-chart.data <- chart.data[order(chart.data$CB, chart.data$CW),]
-chart.data <- ddply(chart.data, .(CB), 
-                    transform, pos = cumsum(pct) - (0.5 * pct))
+<!-- chart.data <- chart.data[order(chart.data$CB, chart.data$CW),] -->
+<!-- chart.data <- ddply(chart.data, .(CB),  -->
+<!--                     transform, pos = cumsum(pct) - (0.5 * pct))  -->
 
-chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"), 
-                        labels = c("Class 2 days", "Class 1 days"))
-chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3", "4"), 
-                        labels = c("Individual\nclass 1\n(23.4%)",  "Individual\nclass 2\n(23.7%)", 
-                                   "Individual\nclass 3\n(28.9%)", "Individual\nclass 4\n(23.9%)"))
+<!-- chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"),  -->
+<!--                         labels = c("Class 2 days", "Class 1 days")) -->
+<!-- chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3", "4"),  -->
+<!--                         labels = c("Individual\nclass 1\n(23.4%)",  "Individual\nclass 2\n(23.7%)",  -->
+<!--                                    "Individual\nclass 3\n(28.9%)", "Individual\nclass 4\n(23.9%)")) -->
 
-library(ggthemr)
-ggthemr("dust", layout = "scientific")
-ggplot() + 
-  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
-           stat="identity") + 
-  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
-            size=4, colour="white", family="Atlas Grotesk Medium") + 
-  theme(legend.position="bottom", legend.direction="horizontal",
-        legend.title = element_blank(), 
-        axis.title = element_text(size = 18), 
-        axis.text = element_text(size = 15), 
-        axis.line = element_line(colour = "black"), 
-        plot.title=element_text(family="Atlas Grotesk Medium"),
-        text=element_text(family="Atlas Grotesk Light")) + 
-  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
-  scale_y_continuous(labels=percent)
-```
+<!-- library(ggthemr) -->
+<!-- ggthemr("dust", layout = "scientific") -->
+<!-- ggplot() +  -->
+<!--   geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6, -->
+<!--            stat="identity") +  -->
+<!--   geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")), -->
+<!--             size=4, colour="white", family="Atlas Grotesk Medium") +  -->
+<!--   theme(legend.position="bottom", legend.direction="horizontal", -->
+<!--         legend.title = element_blank(),  -->
+<!--         axis.title = element_text(size = 18),  -->
+<!--         axis.text = element_text(size = 15),  -->
+<!--         axis.line = element_line(colour = "black"),  -->
+<!--         plot.title=element_text(family="Atlas Grotesk Medium"), -->
+<!--         text=element_text(family="Atlas Grotesk Light")) +  -->
+<!--   labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") + -->
+<!--   scale_y_continuous(labels=percent) -->
+<!-- ``` -->
 
@@
 
-<!-- ## Visualisation of level 2 latent classes (CB = 2) -->
+## Visualisation of level 2 latent classes (CB = 2)
 
-<!-- ```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE} -->
+```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}
 
-<!-- # ndnsNNN <- read_csv("results/ndnsNNN.dat") -->
-<!-- # dt <- ndnsNNN[, c(2,5)] -->
-<!-- # names(dt) <- c("ID_DAY", "DayofWeek") -->
-<!-- #  -->
-<!-- #  -->
-<!-- # CW2CB2 <- CW2CB2 %>%  -->
-<!-- #   left_join(dt, by = "ID_DAY") -->
-<!-- #  -->
+CW3CB2 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB2.txt",
+                      col_names = FALSE)
 
-<!-- chart.data <- CW3CB2 %>%  -->
-<!--   group_by(CB, CW) %>%  -->
-<!--   tally %>%  -->
-<!--   group_by(CB) %>%  -->
-<!--   mutate(pct = n/sum(n)) -->
+names(CW3CB2) <- c("Breakfast", "Morning.snack", "Lunch",
+                   "Afternoon.snack", "Dinner", "Before.bedtime.snack",
+                   "Midnight.food", "ID_DAY", "AGE", "SEX",
+                   "CPROB1", "CPROB2", "CPROB3", "CPROB4",
+                   "CPROB5", "CPROB6",
+                   # "CPROB7",
+                   # "CPROB8",
+                   # "CPROB9",
+                   "CB", "CW", "MLCJOINT", "ID")
 
-<!-- chart.data <- ddply(chart.data, .(CB), -->
-<!--                      transform, pos = cumsum(pct) - (0.5 * pct)) -->
+CW3CB3 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB3.txt",
+                      col_names = FALSE)
 
-<!-- chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"),  -->
-<!--                         labels = c("Class 3 days", "Class 2 days", "Class 1 days")) -->
-<!-- chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"),  -->
-<!--                         labels = c("Individual Class 1\n(35.3%)",  "Individual class 2\n(64.7%)")) -->
+names(CW3CB3) <- c("Breakfast",  "Morning.snack", "Lunch",
+                   "Afternoon.snack", "Dinner", "Before.bedtime.snack",
+                   "Midnight.food", "ID_DAY", "AGE", "SEX",
+                   "CPROB1", "CPROB2", "CPROB3", "CPROB4",
+                   "CPROB5", "CPROB6", "CPROB7", "CPROB8",
+                   "CPROB9", "CB", "CW", "MLCJOINT", "ID")
 
-<!-- library(ggthemr) -->
-<!-- ggthemr("dust", layout = "scientific") -->
-<!-- ggplot() +  -->
-<!--   geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6, -->
-<!--            stat="identity") +  -->
-<!--   geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")), -->
-<!--             size=4, colour="white", family="Atlas Grotesk Medium") +  -->
-<!--   theme(legend.position="bottom", legend.direction="horizontal", -->
-<!--         legend.title = element_blank(),  -->
-<!--         axis.title = element_text(size = 18),  -->
-<!--         axis.text = element_text(size = 15),  -->
-<!--         axis.line = element_line(colour = "black"),  -->
-<!--         plot.title=element_text(family="Atlas Grotesk Medium"), -->
-<!--         text=element_text(family="Atlas Grotesk Light")) +  -->
-<!--   labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") + -->
-<!--   scale_y_continuous(labels=percent) -->
-<!-- ``` -->
+# tab1(CW3CB2$CW)
+# tab1(CW3CB3$CW)
+
+CW3CB3$CW_new <- 0
+CW3CB3$CW_new[CW3CB3$CW == 1] <- 3
+CW3CB3$CW_new[CW3CB3$CW == 2] <- 1
+CW3CB3$CW_new[CW3CB3$CW == 3] <- 2
+
+CB2_in_CW3CB2 <- CW3CB2 %>% 
+  select(ID, ID_DAY, CW, CB) %>% 
+  rename(CW3_in_2 = CW, CB2_in_2 = CB)
+CW3CB3 <- CW3CB3 %>% 
+  left_join(CB2_in_CW3CB2, by = "ID_DAY")
+
+chart.data <- CW3CB3 %>%
+  group_by(CB2_in_2, CW_new) %>%
+  tally %>%
+  group_by(CB2_in_2) %>%
+  mutate(pct = n/sum(n))
+
+chart.data <- chart.data[order(chart.data$CB2_in_2, chart.data$CW_new),]
+
+chart.data <- ddply(chart.data, .(CB2_in_2),
+                     transform, pos = cumsum(pct) - (0.5 * pct))
+
+chart.data$CW_new <- factor(chart.data$CW_new, levels = c("3", "2", "1"),
+                        labels = c("Regular\nmeals day", "low carbo-\nhydrate day", "High carbo-\nhydrate day"))
+chart.data$CB2_in_2 <- factor(chart.data$CB2_in_2, levels = c("1", "2"),
+                        labels = c("Individual Class 1\n(35.3%)",  "Individual class 2\n(64.7%)"))
+
+library(ggthemr)
+ggthemr("dust", layout = "scientific")
+ggplot() +
+  geom_bar(aes(y = pct, x = CB2_in_2, fill = CW_new), data = chart.data, width = 0.6,
+           stat="identity") +
+  geom_text(data=chart.data, aes(x = CB2_in_2, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
+            size=4, colour="white", family="Atlas Grotesk Medium") +
+  theme(legend.position="bottom", legend.direction="horizontal",
+        legend.title = element_blank(),
+        axis.title = element_text(size = 18),
+        axis.text = element_text(size = 15),
+        axis.line = element_line(colour = "black"),
+        plot.title=element_text(family="Atlas Grotesk Medium"),
+        text=element_text(family="Atlas Grotesk Light")) +
+  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
+  scale_y_continuous(labels=percent)
+```
 
@@
 
-# chart.data$CW[chart.data$CW == 1] <- 0 
-# chart.data$CW[chart.data$CW == 3] <- 1 
-# chart.data$CW[chart.data$CW == 0] <- 3
+chart.data$CW_new <- 0
+chart.data$CW_new[chart.data$CW == 1] <- 3
+chart.data$CW_new[chart.data$CW == 2] <- 1
+chart.data$CW_new[chart.data$CW == 3] <- 2
 
-chart.data <- chart.data[order(chart.data$CB, chart.data$CW),]
+chart.data <- chart.data[order(chart.data$CB, chart.data$CW_new),]
 chart.data <- ddply(chart.data, .(CB), 
@@
 
-chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"), 
-                        labels = c("Class 3 days", "Class 2 days", "Class 1 days"))
+chart.data$CW_new <- factor(chart.data$CW_new, levels = c("3", "2", "1"), 
+                        labels = c("Regular\nmeals day", "low carbo-\nhydrate day", "High carbo-\nhydrate day"))
 chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"), 
-                        labels = c("Individual\nclass 1\n(28.2%)",  "Individual\nclass 2\n(28.9%)", 
-                                   "Individual\nclass 3\n(42.8%)"))
+                        labels = c("Individual\nclass 1\n(28.0%)",  "Individual\nclass 2\n(28.6%)", "Individual\nclass 3\n(43.4%)"))
 
@@
 ggplot() + 
-  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
+  geom_bar(aes(y = pct, x = CB, fill = CW_new), data = chart.data, width = 0.6,
            stat="identity") + 
@@
 
-chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"), 
+chart.data$CW_new <- factor(chart.data$CW_new, levels = c("3", "2", "1"), 
                         labels = c("Class 3 days", "Class 2 days", "Class 1 days"))

### 2018-08-02 results/table1slots.Rmd
level1 level2 fig added

@@
 # write_dta(LCGA_2class, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/LCGA_2class.dta")
-write_dta(CW3CB3_regss, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW3CB3_7regss.dta")
+write_dta(CW3CB3_regss, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW3CB2_7regss.dta")
 # write_dta(CW2CB2_regss, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW2CB2_regss.dta")
@@
 CW3idday$DayofWeek[CW3idday$ID_DAY == 812101310000] <- "Sunday"
+
+CW3idday <- CW3idday %>% 
+  mutate(DayofWeek = factor(DayofWeek, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")))
 

### 2018-08-02 Rcode/Check the distribution of level 1 solutions.R

@@ -1,0 +1,14 @@
+CW3CB2_CW3 <- CW3CB2 %>% 
+  select(ID_DAY, CW, CB) %>% 
+  rename(CW3_2 = CW, CB2_2 = CB)
+
+CW3CB3 <- CW3CB3 %>% 
+  left_join(CW3CB2_CW3, by = "ID_DAY")
+
+
+with(CW3CB3, tabpct(CB, CW))
+with(CW3CB3, tabpct(CB2_2, CW3_2))
+with(CW3CB3, tabpct(CB, CW3_2))
+
+
+

### 2018-08-02 Rcode/Energy and classes.R

@@ -1,0 +1,128 @@
+
+library(RColorBrewer)
+library(plyr)
+library(epiDisplay)
+library(tidyverse)
+library(dplyr)
+library(scales)
+library(readr)
+library(kableExtra)
+library(haven)
+library(naniar)
+
+
+
+
+
+
+CW3idday <- read_csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/CW3idday.csv")
+CW3idday$DayofWeek[CW3idday$ID_DAY == 31012251000] <- "Tuesday"
+Energy_slots <- read_csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Energy_slots.csv")
+Energy_slots <- Energy_slots %>% 
+  rename(ID = id)
+
+
+CW3idday$CW_new <- 0
+CW3idday$CW_new[CW3idday$CW == 1] <- 3
+CW3idday$CW_new[CW3idday$CW == 2] <- 1
+CW3idday$CW_new[CW3idday$CW == 3] <- 2
+
+
+
+
+
+Energy <- Energy_slots %>% 
+  left_join(CW3idday, by = c("ID", "DayofWeek"))
+
+
+
+Energy$Slot3g <- as.character(Energy$TimeSlot)
+Energy$Slot3g[Energy$TimeSlot == "[6,9)" | Energy$TimeSlot == "[9,12)"] <- "Before 12 noon"
+Energy$Slot3g[Energy$TimeSlot == "[12,14)" | Energy$TimeSlot == "[14,17)" | 
+                Energy$TimeSlot == "[17,20)"] <- "Between 12 noon to 8 pm"
+Energy$Slot3g[Energy$TimeSlot == "[22, 6)" | Energy$TimeSlot == "[20,22)"] <- "After 8 pm"
+
+Energy$Slot3g <- factor(Energy$Slot3g, levels = c("Before 12 noon", 
+                                                  "Between 12 noon to 8 pm", 
+                                                  "After 8 pm"))
+
+
+
+Energy$TimeSlot <- factor(Energy$TimeSlot, levels = c("[6,9)", "[9,12)", "[12,14)", "[14,17)",
+                                                      "[17,20)", "[20,22)", "[22, 6)"))
+
+
+FoodbyCW <- Energy %>% 
+  group_by(CW_new, TimeSlot) %>% 
[…]

### 2018-08-02 Rcode/analysis8yrsA.R

@@ -1565,3 +1565,241 @@ write_dta(LCGA_3class, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_s
 write_dta(LCGA_2class, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/LCGA_2class.dta")
 write_dta(CW3CB2_regss, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW3CB2_regss.dta")
 write_dta(CW2CB2_regss, "/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/CW2CB2_regss.dta")
+
+
+
+
+# CW3CB2CB3 and weekdays weekends & CW3----------------------------------------------------------
+
+CW3CB2 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB2.txt",
+                      col_names = FALSE)
+
+names(CW3CB2) <- c("Breakfast", "Morning.snack", "Lunch",
+                   "Afternoon.snack", "Dinner", "Before.bedtime.snack",
+                   "Midnight.food", "ID_DAY", "AGE", "SEX",
+                   "CPROB1", "CPROB2", "CPROB3", "CPROB4",
+                   "CPROB5", "CPROB6",
+                   # "CPROB7",
+                   # "CPROB8",
+                   # "CPROB9",
+                   "CB", "CW", "MLCJOINT", "ID")
+
+
+CW3CB3 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB3.txt",
+                      col_names = FALSE)
+
+names(CW3CB3) <- c("Breakfast",  "Morning.snack", "Lunch",
+                   "Afternoon.snack", "Dinner", "Before.bedtime.snack",
+                   "Midnight.food", "ID_DAY", "AGE", "SEX",
+                   "CPROB1", "CPROB2", "CPROB3", "CPROB4",
+                   "CPROB5", "CPROB6", "CPROB7", "CPROB8",
+                   "CPROB9", "CB", "CW", "MLCJOINT", "ID")
+
+tab1(CW3CB2$CW)
+tab1(CW3CB3$CW)
+
+CW3CB3$CW_new <- 0
[…]

### 2018-08-02 Rcode/daylevelconsumption_feature.R

@@ -1,0 +1,136 @@
+library(RColorBrewer)
+library(plyr)
+library(epiDisplay)
+library(tidyverse)
+library(dplyr)
+library(scales)
+library(readr)
+library(kableExtra)
+library(haven)
+library(naniar)
+
+
+food14 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr1-4a_dayleveldietarydata_nutrients_uk.dta")
+
+food56 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr5-6a_dayleveldietarydata_nutrients.dta")
+
+food78 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr7-8a_dayleveldietarydata_nutrients.dta")
+
+
+names(food14)
+
+
+names(food78)[names(food78)=="seriali"] <- "ID"
+names(food56)[names(food56)=="seriali"] <- "ID"
+names(food14)[names(food14)=="seriali"] <- "ID"
+
+
+
+Energy14 <- food14 %>% 
+  select(ID, DayofWeek, Country, SurveyYear, EnergykJ, Carbohydrateg, Proteing, 
+         Fatg, Alcoholg, Totalsugarsg, Starchg, Nonmilkextrinsicsugarsg, Fruitg, 
+         FoodQuantity, YellowRedGreeng)
+Energy14$Country[Energy14$Country == "Northern Ireland"] <- "NI"
+
+Energy56 <- food56 %>% 
+  select(ID, DayofWeek, Country, Surveyyear, EnergykJ, Carbohydrateg, Proteing, 
+         Fatg, Alcoholg, Totalsugarsg, Starchg, Nonmilkextrinsicsugarsg, Fruitg, 
+         FoodQuantity, YellowRedGreeng) %>% 
+  rename(SurveyYear = Surveyyear)
+
+Energy78 <- food78 %>% 
+  select(ID, DayofWeek, Country, SurveyYear, EnergykJ, Carbohydrateg, Proteing, 
+         Fatg, Alcoholg, Totalsugarsg, Starchg, Nonmilkextrinsicsugarsg, Fruitg, 
+         UsualDrinkQuantity, YellowRedGreeng) %>% 
+  rename(FoodQuantity = UsualDrinkQuantity)
+
+
[…]

### 2018-08-02 paper/Figures/Figureforpaper.R

@@ -257,3 +257,316 @@ grViz("
 #       {rank = 'same'; t1; t2; t3; t4;}
 #       }
 #       ")
+
+# Time slots level 1 classes ----------------------------------------------
+
+
+CW3CB2 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB2.txt",
+                      col_names = FALSE)
+
+names(CW3CB2) <- c("Breakfast", 
+                   "Morning.snack",
+                   "Lunch",
+                   "Afternoon.snack",
+                   "Dinner",
+                   "Before.bedtime.snack",
+                   "Midnight.food",
+                   "ID_DAY",
+                   "AGE",
+                   "SEX",
+                   "CPROB1",
+                   "CPROB2",
+                   "CPROB3",
+                   "CPROB4",
+                   "CPROB5",
+                   "CPROB6",
+                   # "CPROB7",
+                   # "CPROB8",
+                   # "CPROB9",
+                   "CB",
+                   "CW",
+                   "MLCJOINT",
+                   "ID")
+
+pp <- CW3CB2 %>% 
+  group_by(CW) %>% 
+  summarise(Breakfast_0 = sum(Breakfast == 0)/length(Breakfast), 
+            Breakfast_1 = sum(Breakfast == 1)/length(Breakfast), 
+            Breakfast_2 = sum(Breakfast == 2)/length(Breakfast),
+            Morning.snack_0 = sum(Morning.snack == 0)/length(Morning.snack),
+            Morning.snack_1 = sum(Morning.snack == 1)/length(Morning.snack), 
+            Morning.snack_2 = sum(Morning.snack == 2)/length(Morning.snack),
+            Lunch_0 = sum(Lunch == 0)/length(Lunch),
+            Lunch_1 = sum(Lunch == 1)/length(Lunch), 
+            Lunch_2 = sum(Lunch == 2)/length(Lunch),
+            Afternoon.snack_0 = sum(Afternoon.snack == 0)/length(Afternoon.snack),
+            Afternoon.snack_1 = sum(Afternoon.snack == 1)/length(Afternoon.snack), 
+            Afternoon.snack_2 = sum(Afternoon.snack == 2)/length(Afternoon.snack),
+            Dinner_0 = sum(Dinner == 0)/length(Dinner),
+            Dinner_1 = sum(Dinner == 1)/length(Dinner), 
+            Dinner_2 = sum(Dinner == 2)/length(Dinner),
[…]

### 2018-08-03 paper/Appendices/Appendix0_10.Rmd
results MLCA almost done

@@
 ```
+
+```
+Mplus VERSION 7.4
+MUTHEN & MUTHEN
+07/28/2018   9:55 AM
+
+INPUT INSTRUCTIONS
+
+  TITLE:    3-class at level 1 (CW), 3-classes at level 2 (CB) random effects model - non-pa
+            ordered polytomous variables for carb intake at each time slot over four
+            days of NDNS survey 2008/09 - 2015/16
+            variable 0 = not eating
+                     1 = eating & carb provided < 50% calorie
+                     2 = eating & carb provided >= 50% calorie
+
+  DATA:     File is H:\summer_project\Mplus\TimeSlots\NDNS_Tslots.dat;
+
+  VARIABLE: NAMES = id id_dy Age Sex H6_9 H9_12 H12_14 H14_17 H17_20
+                    H20_22 H22_6;
+
+            USEVAR = H6_9 H9_12 H12_14 H14_17 H17_20
+                    H20_22 H22_6;
+
+            auxiliary = Age Sex;
+
+            CATEGORICAL =  H6_9 H9_12 H12_14 H14_17 H17_20
+                    H20_22 H22_6;
+
+            CLUSTER = id;
+
+            IDVARIABLE = id_dy;
+
+            BETWEEN = CB;
+
+            WITHIN = H6_9 H9_12 H12_14 H14_17 H17_20
+                    H20_22 H22_6;
+
+            CLASSES = CB(3) CW(3);
+
+            MISSING are .;
+
+  ANALYSIS:
+  type = mixture twolevel;
+  starts = 50 25;
+  process = 8(starts);
+
+  MODEL:
+  %within%
+  %overall%
+  %between%
+  %overall%
+  CW ON CB;
+
+  Savedata:
+    file is H:\summer_project\Mplus\TimeSlots\Multilevel\NDNSslot_CW3CB3.txt;
+    save is cprob;
+    format is free;
+
+3-class at level 1 (CW), 3-classes at level 2 (CB) random effects model - non-par
+ordered polytomous variables for carb intake at each time slot over four
+days of NDNS survey 2008/09 - 2015/16
+variable 0 = not eating
+1 = eating & carb provided < 50% calorie
+2 = eating & carb provided >= 50% calorie
+
+SUMMARY OF ANALYSIS
+
+Number of groups                                                 1
+Number of observations                                       24483
+
+Number of dependent variables                                    7
+Number of independent variables                                  0
+Number of continuous latent variables                            0
+Number of categorical latent variables                           2
+
+Observed dependent variables
+
+  Binary and ordered categorical (ordinal)
+   H6_9        H9_12       H12_14      H14_17      H17_20      H20_22
+   H22_6
+
+Observed auxiliary variables
+   AGE         SEX
+
+Categorical latent variables
+   CB          CW
+
+Variables with special functions
+
+  Cluster variable      ID
+  ID variable           ID_DY
+
+  Within variables
+   H6_9        H9_12       H12_14      H14_17      H17_20      H20_22
+   H22_6
+
+Estimator                                                      MLR
+Information matrix                                        OBSERVED
+Optimization Specifications for the Quasi-Newton Algorithm for
+Continuous Outcomes
+  Maximum number of iterations                                 100
+  Convergence criterion                                  0.100D-05
+Optimization Specifications for the EM Algorithm
+  Maximum number of iterations                                 500
+  Convergence criteria
+    Loglikelihood change                                 0.100D-02
+    Relative loglikelihood change                        0.100D-05
+    Derivative                                           0.100D-02
+Optimization Specifications for the M step of the EM Algorithm for
+Categorical Latent variables
+  Number of M step iterations                                    1
+  M step convergence criterion                           0.100D-02
+  Basis for M step termination                           ITERATION
+Optimization Specifications for the M step of the EM Algorithm for
+Censored, Binary or Ordered Categorical (Ordinal), Unordered
+Categorical (Nominal) and Count Outcomes
+  Number of M step iterations                                    1
+  M step convergence criterion                           0.100D-02
+  Basis for M step termination                           ITERATION
+  Maximum value for logit thresholds                            15
+  Minimum value for logit thresholds                           -15
+  Minimum expected cell size for chi-square              0.100D-01
+Maximum number of iterations for H1                           2000
+Convergence criterion for H1                             0.100D-03
+Optimization algorithm                                         EMA
+Integration Specifications
+  Type                                                    STANDARD
+  Number of integration points                                  15
+  Dimensions of numerical integration                            0
+  Adaptive quadrature                                           ON
+Random Starts Specifications
+  Number of initial stage random starts                         50
+  Number of final stage optimizations                           25
+  Number of initial stage iterations                            10
+  Initial stage convergence criterion                    0.100D+01
+  Random starts scale                                    0.500D+01
+  Random seed for generating random starts                       0
+Parameterization                                             LOGIT
+Link                                                         LOGIT
+Cholesky                                                       OFF
+
+Input data file(s)
+  H:\summer_project\Mplus\TimeSlots\NDNS_Tslots.dat
+Input data format  FREE
+
+SUMMARY OF DATA
+
+     Number of missing data patterns             1
+     Number of y missing data patterns           0
+     Number of u missing data patterns           1
+     Number of clusters                       6155
+
+COVARIANCE COVERAGE OF DATA
+
+Minimum covariance coverage value   0.100
+
+UNIVARIATE PROPORTIONS AND COUNTS FOR CATEGORICAL VARIABLES
+
+    H6_9
+      Category 1    0.313         7655.000
+      Category 2    0.184         4500.000
+      Category 3    0.504        12328.000
+    H9_12
+      Category 1    0.222         5447.000
+      Category 2    0.295         7227.000
+      Category 3    0.482        11809.000
+    H12_14
+      Category 1    0.195         4783.000
+      Category 2    0.454        11112.000
+      Category 3    0.351         8588.000
+    H14_17
+      Category 1    0.283         6926.000
+      Category 2    0.338         8277.000
+      Category 3    0.379         9280.000
+    H17_20
+      Category 1    0.124         3043.000
+      Category 2    0.582        14240.000
+      Category 3    0.294         7200.000
+    H20_22
+      Category 1    0.356         8722.000
+      Category 2    0.363         8898.000
+      Category 3    0.280         6863.000
+    H22_6
+      Category 1    0.666        16295.000
+      Category 2    0.169         4144.000
+      Category 3    0.165         4044.000
+
+RANDOM STARTS RESULTS RANKED FROM THE BEST TO THE WORST LOGLIKELIHOOD VALUES
+
+Final stage loglikelihood values at local maxima, seeds, and initial stage start numbers:
+
+         -166348.815  153942           31
+         -166348.815  573096           20
+         -166348.815  253358           2
+         -166348.816  318230           46
+         -166348.816  246261           38
+         -166348.873  285380           1
+         -166348.908  903420           5
+         -166349.394  120506           45
+         -166349.394  966014           37
+         -166349.394  207896           25
+         -166349.395  195873           6
+         -166349.513  68985            17
+         -166349.514  366706           29
+         -166352.737  76974            16
+         -166357.057  127215           9
+         -166482.723  533738           11
+         -166495.844  645664           39
+         -166668.918  372176           23
+
+THE BEST LOGLIKELIHOOD VALUE HAS BEEN REPLICATED.  RERUN WITH AT LEAST TWICE THE
+RANDOM STARTS TO CHECK THAT THE BEST LOGLIKELIHOOD IS STILL OBTAINED AND REPLICATED.
+
+THE MODEL ESTIMATION TERMINATED NORMALLY
+
+MODEL FIT INFORMATION
+
+Number of Free Parameters                      134
+
+Loglikelihood
+
+          H0 Value                     -166348.815
+          H0 Scaling Correction Factor      1.8182
+            for MLR
+
+Information Criteria
+
+          Akaike (AIC)                  332965.630
+          Bayesian (BIC)                334051.799
+          Sample-Size Adjusted BIC      333625.950
+            (n* = (n + 2) / 24)
+
+MODEL RESULTS USE THE LATENT CLASS VARIABLE ORDER
+
+   CB  CW
+
+  Latent Class Variable Patterns
+
+         CB        CW
+      Class     Class
+
+         1         1
+         1         2
+         1         3
+         2         1
+         2         2
+         2         3
+         3         1
+         3         2
+         3         3
+
+FINAL CLASS COUNTS AND PROPORTIONS FOR THE LATENT CLASS PATTERNS
+BASED ON ESTIMATED POSTERIOR PROBABILITIES
+
+  Latent Class
+    Pattern
+
+    1  1       4050.97975          0.16546
+    1  2       1561.55249          0.06378
+    1  3       1286.46696          0.05255
+    2  1       2746.94031          0.11220
+    2  2       3011.00217          0.12298
+    2  3       1341.59686          0.05480
+    3  1       2748.25320          0.11225
+    3  2       4770.55950          0.19485
+    3  3       2965.64876          0.12113
+
+FINAL CLASS COUNTS AND PROPORTIONS FOR EACH LATENT CLASS VARIABLE
+BASED ON ESTIMATED POSTERIOR PROBABILITIES
+
+  Latent Class
+    Variable    Class
+
+    CB             1      6898.99902          0.28179
+                   2      7099.53906          0.28998
+                   3     10484.46094          0.42823
+    CW             1      9546.17285          0.38991
+                   2      9343.11426          0.38162
+                   3      5593.71240          0.22847
+
+FINAL CLASS COUNTS AND PROPORTIONS FOR THE LATENT CLASS PATTERNS
+BASED ON THEIR MOST LIKELY LATENT CLASS PATTERN
+
+Class Counts and Proportions
+
+  Latent Class
+    Pattern
+
+    1  1             4262          0.17408
+    1  2             1406          0.05743
+    1  3             1178          0.04812
+    2  1             2807          0.11465
+    2  2             2946          0.12033
+    2  3             1260          0.05146
+    3  1             2745          0.11212
+    3  2             5315          0.21709
+    3  3             2564          0.10473
+
+FINAL CLASS COUNTS AND PROPORTIONS FOR EACH LATENT CLASS VARIABLE
+BASED ON THEIR MOST LIKELY LATENT CLASS PATTERN
+
+  Latent Class
+    Variable    Class
+
+    CB             1            6846          0.27962
+                   2            7013          0.28644
+                   3           10624          0.43393
+    CW             1            9814          0.40085
+                   2            9667          0.39485
+                   3            5002          0.20431
+
+CLASSIFICATION QUALITY
+
+     Entropy                         0.630
+
+Average Latent Class Probabilities for Most Likely Latent Class Pattern (Row)
+by Latent Class Pattern (Column)
+
+  Latent Class Variable Patterns
+
+  Latent Class         CB        CW
+   Pattern No.      Class     Class
+
+         1             1         1
+         2             1         2
+         3             1         3
+         4             2         1
+         5             2         2
+         6             2         3
+         7             3         1
+         8             3         2
+         9             3         3
+
+           1        2        3        4        5        6        7        8        9
+
+    1   0.720    0.091    0.073    0.016    0.032    0.004    0.005    0.033    0.025
+    2   0.183    0.609    0.098    0.005    0.002    0.030    0.040    0.005    0.027
+    3   0.211    0.084    0.629    0.008    0.005    0.007    0.011    0.036    0.009
+    4   0.019    0.004    0.002    0.692    0.184    0.051    0.011    0.034    0.003
+    5   0.042    0.001    0.001    0.158    0.709    0.045    0.001    0.035    0.009
+    6   0.012    0.037    0.013    0.065    0.084    0.702    0.042    0.003    0.042
+    7   0.011    0.029    0.004    0.012    0.002    0.022    0.641    0.126    0.153
+    8   0.026    0.003    0.009    0.025    0.024    0.001    0.115    0.675    0.123
+    9   0.046    0.024    0.004    0.003    0.010    0.018    0.079    0.174    0.642
+
+MODEL RESULTS
+
+                                                    Two-Tailed
+                    Estimate       S.E.  Est./S.E.    P-Value
+
+Within Level
+
+Latent Class Pattern 1 1
+
+ Thresholds
+    H6_9$1            -0.718      0.218     -3.294      0.001
+    H6_9$2             0.973      0.299      3.258      0.001
+    H9_12$1           -2.516      0.463     -5.433      0.000
+    H9_12$2            0.675      0.132      5.118      0.000
+    H12_14$1          -1.025      0.145     -7.057      0.000
+    H12_14$2           1.240      0.116     10.725      0.000
+    H14_17$1          -1.566      0.149    -10.520      0.000
+    H14_17$2           1.090      0.100     10.909      0.000
+    H17_20$1          -1.998      0.125    -16.000      0.000
+    H17_20$2           1.549      0.100     15.556      0.000
+    H20_22$1          -0.933      0.085    -10.914      0.000
+    H20_22$2           1.829      0.103     17.770      0.000
+    H22_6$1            0.253      0.083      3.046      0.002
+    H22_6$2            2.308      0.117     19.691      0.000
+
+Latent Class Pattern 1 2
+
+ Thresholds
+    H6_9$1            -4.021      1.788     -2.249      0.025
+    H6_9$2            -0.115      0.259     -0.445      0.656
+    H9_12$1            0.167      0.373      0.448      0.654
+    H9_12$2            2.142      0.586      3.657      0.000
+    H12_14$1          -3.210      1.518     -2.115      0.034
+    H12_14$2           0.858      0.167      5.124      0.000
+    H14_17$1           0.044      0.384      0.114      0.909
+    H14_17$2           1.617      0.293      5.509      0.000
+    H17_20$1          -2.109      0.390     -5.409      0.000
+    H17_20$2           1.399      0.196      7.126      0.000
+    H20_22$1          -0.367      0.174     -2.109      0.035
+    H20_22$2           2.347      0.382      6.151      0.000
+    H22_6$1            0.754      0.259      2.912      0.004
+    H22_6$2            2.542      0.264      9.646      0.000
+
+Latent Class Pattern 1 3
+
+ Thresholds
+    H6_9$1           -15.000      0.000    999.000    999.000
+    H6_9$2             2.357      0.783      3.011      0.003
+    H9_12$1           -1.433      0.372     -3.850      0.000
+    H9_12$2           -0.604      0.279     -2.166      0.030
+    H12_14$1          -1.988      0.257     -7.749      0.000
+    H12_14$2           0.524      0.125      4.209      0.000
+    H14_17$1          -1.027      0.232     -4.436      0.000
+    H14_17$2           0.274      0.131      2.087      0.037
+    H17_20$1          -2.665      0.310     -8.605      0.000
+    H17_20$2           0.707      0.112      6.322      0.000
+    H20_22$1          -0.527      0.152     -3.462      0.001
+    H20_22$2           0.702      0.138      5.102      0.000
+    H22_6$1            1.119      0.185      6.062      0.000
+    H22_6$2            1.748      0.183      9.544      0.000
+
+Latent Class Pattern 2 1
+
+ Thresholds
+    H6_9$1             1.663      0.199      8.370      0.000
+    H6_9$2             1.839      0.198      9.274      0.000
+    H9_12$1           -2.150      0.281     -7.643      0.000
+    H9_12$2           -0.869      0.140     -6.190      0.000
+    H12_14$1          -1.978      0.191    -10.349      0.000
+    H12_14$2           0.323      0.078      4.139      0.000
+    H14_17$1           0.237      0.183      1.293      0.196
+    H14_17$2           0.782      0.123      6.352      0.000
+    H17_20$1          -2.936      0.428     -6.853      0.000
+    H17_20$2           0.632      0.081      7.807      0.000
+    H20_22$1           0.028      0.142      0.194      0.846
+    H20_22$2           0.868      0.086     10.145      0.000
+    H22_6$1            0.658      0.109      6.010      0.000
+    H22_6$2            1.326      0.100     13.215      0.000
+
+Latent Class Pattern 2 2
+
+ Thresholds
+    H6_9$1             1.640      0.171      9.619      0.000
+    H6_9$2             1.906      0.179     10.678      0.000
+    H9_12$1           -1.954      0.347     -5.636      0.000
+    H9_12$2           -0.360      0.127     -2.842      0.004
+    H12_14$1          -0.016      0.189     -0.084      0.933
+    H12_14$2           0.948      0.135      7.029      0.000
+    H14_17$1          -1.906      0.301     -6.327      0.000
+    H14_17$2           0.371      0.080      4.614      0.000
+    H17_20$1          -0.812      0.116     -7.030      0.000
+    H17_20$2           0.910      0.089     10.259      0.000
+    H20_22$1          -0.742      0.089     -8.318      0.000
+    H20_22$2           0.998      0.085     11.705      0.000
+    H22_6$1            0.298      0.083      3.608      0.000
+    H22_6$2            1.337      0.099     13.475      0.000
+
+Latent Class Pattern 2 3
+
+ Thresholds
+    H6_9$1            -1.072      0.500     -2.144      0.032
+    H6_9$2            -0.309      0.346     -0.892      0.372
+    H9_12$1            2.441      1.044      2.339      0.019
+    H9_12$2            3.599      1.983      1.815      0.069
+    H12_14$1          -1.029      0.211     -4.880      0.000
+    H12_14$2           0.603      0.123      4.913      0.000
+    H14_17$1          -0.010      0.243     -0.041      0.967
+    H14_17$2           0.784      0.157      4.977      0.000
+    H17_20$1          -0.953      0.203     -4.684      0.000
+    H17_20$2           0.779      0.135      5.784      0.000
+    H20_22$1          -0.105      0.210     -0.500      0.617
+    H20_22$2           1.203      0.135      8.914      0.000
+    H22_6$1            0.582      0.299      1.950      0.051
+    H22_6$2            1.370      0.206      6.653      0.000
+
+Latent Class Pattern 3 1
+
+ Thresholds
+    H6_9$1            -4.593      1.699     -2.703      0.007
+    H6_9$2            -2.975      0.428     -6.957      0.000
+    H9_12$1           -0.322      0.207     -1.553      0.120
+    H9_12$2            0.398      0.363      1.095      0.274
+    H12_14$1          -5.060      3.668     -1.380      0.168
+    H12_14$2           0.307      0.100      3.080      0.002
+    H14_17$1           0.186      0.530      0.351      0.726
+    H14_17$2           0.317      0.245      1.295      0.195
+    H17_20$1          -4.019      0.957     -4.199      0.000
+    H17_20$2           0.747      0.093      7.987      0.000
+    H20_22$1          -0.233      0.132     -1.767      0.077
+    H20_22$2           0.607      0.109      5.571      0.000
+    H22_6$1            1.304      0.146      8.918      0.000
+    H22_6$2            1.850      0.160     11.579      0.000
+
+Latent Class Pattern 3 2
+
+ Thresholds
+    H6_9$1            -1.232      0.195     -6.305      0.000
+    H6_9$2            -0.858      0.169     -5.068      0.000
+    H9_12$1           -4.377      1.937     -2.260      0.024
+    H9_12$2           -1.488      0.316     -4.717      0.000
+    H12_14$1          -1.727      0.227     -7.611      0.000
+    H12_14$2           0.302      0.082      3.666      0.000
+    H14_17$1          -1.834      0.237     -7.730      0.000
+    H14_17$2          -0.294      0.186     -1.582      0.114
+    H17_20$1          -2.588      0.487     -5.313      0.000
+    H17_20$2           0.631      0.062     10.187      0.000
+    H20_22$1          -0.920      0.078    -11.852      0.000
+    H20_22$2           0.462      0.073      6.308      0.000
+    H22_6$1            0.640      0.119      5.361      0.000
+    H22_6$2            1.162      0.129      9.039      0.000
+
+Latent Class Pattern 3 3
+
+ Thresholds
+    H6_9$1            -4.941      5.813     -0.850      0.395
+    H6_9$2            -2.680      0.887     -3.024      0.002
+    H9_12$1           -0.765      0.640     -1.195      0.232
+    H9_12$2            1.164      0.920      1.265      0.206
+    H12_14$1          -1.415      0.439     -3.226      0.001
+    H12_14$2           0.566      0.085      6.626      0.000
+    H14_17$1          -2.052      0.650     -3.158      0.002
+    H14_17$2           0.612      0.210      2.909      0.004
+    H17_20$1          -1.627      0.427     -3.810      0.000
+    H17_20$2           0.713      0.103      6.935      0.000
+    H20_22$1          -0.850      0.329     -2.585      0.010
+    H20_22$2           0.685      0.134      5.104      0.000
+    H22_6$1            1.237      0.195      6.349      0.000
+    H22_6$2            1.893      0.179     10.582      0.000
+
+Between Level
+
+Categorical Latent Variables
+
+Within Level
+
+ Intercepts
+    CW#1              -0.076      0.366     -0.208      0.835
+    CW#2               0.475      0.309      1.539      0.124
+
+Between Level
+
+ CW#1       ON
+    CB#1               1.223      0.473      2.585      0.010
+    CB#2               0.793      0.441      1.796      0.073
+
+ CW#2       ON
+    CB#1              -0.282      0.535     -0.526      0.599
+    CB#2               0.333      0.455      0.733      0.464
+
+ Means
+    CB#1              -0.417      0.100     -4.178      0.000
+    CB#2              -0.386      0.067     -5.770      0.000
+
+QUALITY OF NUMERICAL RESULTS
+
+     Condition Number for the Information Matrix              0.428E-04
+       (ratio of smallest to largest eigenvalue)
+
+SAVEDATA INFORMATION
+
+  Save file
+    H:\summer_project\Mplus\TimeSlots\Multilevel\NDNSslot_CW3CB3.txt
+
+  Order of variables
+
+    H6_9
+    H9_12
+    H12_14
+    H14_17
+    H17_20
+    H20_22
+    H22_6
+    ID_DY
+    AGE
+    SEX
+    CPROB1
+    CPROB2
+    CPROB3
+    CPROB4
+    CPROB5
+    CPROB6
+    CPROB7
+    CPROB8
+    CPROB9
+    CB
+    CW
+    MLCJOINT
+    ID
+
+  Save file format           Free
+
+  Save file record length    10000
+
+DIAGRAM INFORMATION
+
+  Mplus diagrams are currently not available for Mixture analysis.
+  No diagram output was produced.
+
+     Beginning Time:  09:55:10
+        Ending Time:  10:02:01
+       Elapsed Time:  00:06:51
+
+MUTHEN & MUTHEN
+3463 Stoner Ave.
+Los Angeles, CA  90066
+
+Tel: (310) 391-9971
+Fax: (310) 391-8971
+Web: www.StatModel.com
+Support: Support@StatModel.com
+
+Copyright (c) 1998-2015 Muthen & Muthen
+```

### 2018-08-03 paper/Appendices/Appendix0_10.tex
results MLCA almost done

@@
 
+\begin{verbatim}
+Mplus VERSION 7.4
+MUTHEN & MUTHEN
+07/28/2018   9:55 AM
+
+INPUT INSTRUCTIONS
+
+  TITLE:    3-class at level 1 (CW), 3-classes at level 2 (CB) random effects model - non-pa
+            ordered polytomous variables for carb intake at each time slot over four
+            days of NDNS survey 2008/09 - 2015/16
+            variable 0 = not eating
+                     1 = eating & carb provided < 50% calorie
+                     2 = eating & carb provided >= 50% calorie
+
+  DATA:     File is H:\summer_project\Mplus\TimeSlots\NDNS_Tslots.dat;
+
+  VARIABLE: NAMES = id id_dy Age Sex H6_9 H9_12 H12_14 H14_17 H17_20
+                    H20_22 H22_6;
+
+            USEVAR = H6_9 H9_12 H12_14 H14_17 H17_20
+                    H20_22 H22_6;
+
+            auxiliary = Age Sex;
+
+            CATEGORICAL =  H6_9 H9_12 H12_14 H14_17 H17_20
+                    H20_22 H22_6;
+
+            CLUSTER = id;
+
+            IDVARIABLE = id_dy;
+
+            BETWEEN = CB;
+
+            WITHIN = H6_9 H9_12 H12_14 H14_17 H17_20
+                    H20_22 H22_6;
+
+            CLASSES = CB(3) CW(3);
+
+            MISSING are .;
+
+  ANALYSIS:
+  type = mixture twolevel;
+  starts = 50 25;
+  process = 8(starts);
+
+  MODEL:
+  %within%
+  %overall%
+  %between%
+  %overall%
+  CW ON CB;
+
+  Savedata:
+    file is H:\summer_project\Mplus\TimeSlots\Multilevel\NDNSslot_CW3CB3.txt;
+    save is cprob;
+    format is free;
+
+3-class at level 1 (CW), 3-classes at level 2 (CB) random effects model - non-par
+ordered polytomous variables for carb intake at each time slot over four
+days of NDNS survey 2008/09 - 2015/16
+variable 0 = not eating
+1 = eating & carb provided < 50% calorie
+2 = eating & carb provided >= 50% calorie
+
+SUMMARY OF ANALYSIS
+
+Number of groups                                                 1
+Number of observations                                       24483
+
+Number of dependent variables                                    7
+Number of independent variables                                  0
+Number of continuous latent variables                            0
+Number of categorical latent variables                           2
+
+Observed dependent variables
+
+  Binary and ordered categorical (ordinal)
+   H6_9        H9_12       H12_14      H14_17      H17_20      H20_22
+   H22_6
+
+Observed auxiliary variables
+   AGE         SEX
+
+Categorical latent variables
+   CB          CW
+
+Variables with special functions
+
+  Cluster variable      ID
+  ID variable           ID_DY
+
+  Within variables
+   H6_9        H9_12       H12_14      H14_17      H17_20      H20_22
+   H22_6
+
+Estimator                                                      MLR
+Information matrix                                        OBSERVED
+Optimization Specifications for the Quasi-Newton Algorithm for
+Continuous Outcomes
+  Maximum number of iterations                                 100
+  Convergence criterion                                  0.100D-05
+Optimization Specifications for the EM Algorithm
+  Maximum number of iterations                                 500
+  Convergence criteria
+    Loglikelihood change                                 0.100D-02
+    Relative loglikelihood change                        0.100D-05
+    Derivative                                           0.100D-02
+Optimization Specifications for the M step of the EM Algorithm for
+Categorical Latent variables
+  Number of M step iterations                                    1
+  M step convergence criterion                           0.100D-02
+  Basis for M step termination                           ITERATION
+Optimization Specifications for the M step of the EM Algorithm for
+Censored, Binary or Ordered Categorical (Ordinal), Unordered
+Categorical (Nominal) and Count Outcomes
+  Number of M step iterations                                    1
+  M step convergence criterion                           0.100D-02
+  Basis for M step termination                           ITERATION
+  Maximum value for logit thresholds                            15
+  Minimum value for logit thresholds                           -15
+  Minimum expected cell size for chi-square              0.100D-01
+Maximum number of iterations for H1                           2000
+Convergence criterion for H1                             0.100D-03
+Optimization algorithm                                         EMA
+Integration Specifications
+  Type                                                    STANDARD
+  Number of integration points                                  15
+  Dimensions of numerical integration                            0
+  Adaptive quadrature                                           ON
+Random Starts Specifications
+  Number of initial stage random starts                         50
+  Number of final stage optimizations                           25
+  Number of initial stage iterations                            10
+  Initial stage convergence criterion                    0.100D+01
+  Random starts scale                                    0.500D+01
+  Random seed for generating random starts                       0
+Parameterization                                             LOGIT
+Link                                                         LOGIT
+Cholesky                                                       OFF
+
+Input data file(s)
+  H:\summer_project\Mplus\TimeSlots\NDNS_Tslots.dat
+Input data format  FREE
+
+SUMMARY OF DATA
+
+     Number of missing data patterns             1
+     Number of y missing data patterns           0
+     Number of u missing data patterns           1
+     Number of clusters                       6155
+
+COVARIANCE COVERAGE OF DATA
+
+Minimum covariance coverage value   0.100
+
+UNIVARIATE PROPORTIONS AND COUNTS FOR CATEGORICAL VARIABLES
+
+    H6_9
+      Category 1    0.313         7655.000
+      Category 2    0.184         4500.000
+      Category 3    0.504        12328.000
+    H9_12
+      Category 1    0.222         5447.000
+      Category 2    0.295         7227.000
+      Category 3    0.482        11809.000
+    H12_14
+      Category 1    0.195         4783.000
+      Category 2    0.454        11112.000
+      Category 3    0.351         8588.000
+    H14_17
+      Category 1    0.283         6926.000
+      Category 2    0.338         8277.000
+      Category 3    0.379         9280.000
+    H17_20
+      Category 1    0.124         3043.000
+      Category 2    0.582        14240.000
+      Category 3    0.294         7200.000
+    H20_22
+      Category 1    0.356         8722.000
+      Category 2    0.363         8898.000
+      Category 3    0.280         6863.000
+    H22_6
+      Category 1    0.666        16295.000
+      Category 2    0.169         4144.000
+      Category 3    0.165         4044.000
+
+RANDOM STARTS RESULTS RANKED FROM THE BEST TO THE WORST LOGLIKELIHOOD VALUES
+
+Final stage loglikelihood values at local maxima, seeds, and initial stage start numbers:
+
+         -166348.815  153942           31
+         -166348.815  573096           20
+         -166348.815  253358           2
+         -166348.816  318230           46
+         -166348.816  246261           38
+         -166348.873  285380           1
+         -166348.908  903420           5
+         -166349.394  120506           45
+         -166349.394  966014           37
+         -166349.394  207896           25
+         -166349.395  195873           6
+         -166349.513  68985            17
+         -166349.514  366706           29
+         -166352.737  76974            16
+         -166357.057  127215           9
+         -166482.723  533738           11
+         -166495.844  645664           39
+         -166668.918  372176           23
+
+THE BEST LOGLIKELIHOOD VALUE HAS BEEN REPLICATED.  RERUN WITH AT LEAST TWICE THE
+RANDOM STARTS TO CHECK THAT THE BEST LOGLIKELIHOOD IS STILL OBTAINED AND REPLICATED.
+
+THE MODEL ESTIMATION TERMINATED NORMALLY
+
+MODEL FIT INFORMATION
+
+Number of Free Parameters                      134
+
+Loglikelihood
+
+          H0 Value                     -166348.815
+          H0 Scaling Correction Factor      1.8182
+            for MLR
+
+Information Criteria
+
+          Akaike (AIC)                  332965.630
+          Bayesian (BIC)                334051.799
+          Sample-Size Adjusted BIC      333625.950
+            (n* = (n + 2) / 24)
+
+MODEL RESULTS USE THE LATENT CLASS VARIABLE ORDER
+
+   CB  CW
+
+  Latent Class Variable Patterns
+
+         CB        CW
+      Class     Class
+
+         1         1
+         1         2
+         1         3
+         2         1
+         2         2
+         2         3
+         3         1
+         3         2
+         3         3
+
+FINAL CLASS COUNTS AND PROPORTIONS FOR THE LATENT CLASS PATTERNS
+BASED ON ESTIMATED POSTERIOR PROBABILITIES
+
+  Latent Class
+    Pattern
+
+    1  1       4050.97975          0.16546
+    1  2       1561.55249          0.06378
+    1  3       1286.46696          0.05255
+    2  1       2746.94031          0.11220
+    2  2       3011.00217          0.12298
+    2  3       1341.59686          0.05480
+    3  1       2748.25320          0.11225
+    3  2       4770.55950          0.19485
+    3  3       2965.64876          0.12113
+
+FINAL CLASS COUNTS AND PROPORTIONS FOR EACH LATENT CLASS VARIABLE
+BASED ON ESTIMATED POSTERIOR PROBABILITIES
+
+  Latent Class
+    Variable    Class
+
+    CB             1      6898.99902          0.28179
+                   2      7099.53906          0.28998
+                   3     10484.46094          0.42823
+    CW             1      9546.17285          0.38991
+                   2      9343.11426          0.38162
+                   3      5593.71240          0.22847
+
+FINAL CLASS COUNTS AND PROPORTIONS FOR THE LATENT CLASS PATTERNS
+BASED ON THEIR MOST LIKELY LATENT CLASS PATTERN
+
+Class Counts and Proportions
+
+  Latent Class
+    Pattern
+
+    1  1             4262          0.17408
+    1  2             1406          0.05743
+    1  3             1178          0.04812
+    2  1             2807          0.11465
+    2  2             2946          0.12033
+    2  3             1260          0.05146
+    3  1             2745          0.11212
+    3  2             5315          0.21709
+    3  3             2564          0.10473
+
+FINAL CLASS COUNTS AND PROPORTIONS FOR EACH LATENT CLASS VARIABLE
+BASED ON THEIR MOST LIKELY LATENT CLASS PATTERN
+
+  Latent Class
+    Variable    Class
+
+    CB             1            6846          0.27962
+                   2            7013          0.28644
+                   3           10624          0.43393
+    CW             1            9814          0.40085
+                   2            9667          0.39485
+                   3            5002          0.20431
+
+CLASSIFICATION QUALITY
+
+     Entropy                         0.630
+
+Average Latent Class Probabilities for Most Likely Latent Class Pattern (Row)
+by Latent Class Pattern (Column)
+
+  Latent Class Variable Patterns
+
+  Latent Class         CB        CW
+   Pattern No.      Class     Class
+
+         1             1         1
+         2             1         2
+         3             1         3
+         4             2         1
+         5             2         2
+         6             2         3
+         7             3         1
+         8             3         2
+         9             3         3
+
+           1        2        3        4        5        6        7        8        9
+
+    1   0.720    0.091    0.073    0.016    0.032    0.004    0.005    0.033    0.025
+    2   0.183    0.609    0.098    0.005    0.002    0.030    0.040    0.005    0.027
+    3   0.211    0.084    0.629    0.008    0.005    0.007    0.011    0.036    0.009
+    4   0.019    0.004    0.002    0.692    0.184    0.051    0.011    0.034    0.003
+    5   0.042    0.001    0.001    0.158    0.709    0.045    0.001    0.035    0.009
+    6   0.012    0.037    0.013    0.065    0.084    0.702    0.042    0.003    0.042
+    7   0.011    0.029    0.004    0.012    0.002    0.022    0.641    0.126    0.153
+    8   0.026    0.003    0.009    0.025    0.024    0.001    0.115    0.675    0.123
+    9   0.046    0.024    0.004    0.003    0.010    0.018    0.079    0.174    0.642
+
+MODEL RESULTS
+
+                                                    Two-Tailed
+                    Estimate       S.E.  Est./S.E.    P-Value
+
+Within Level
+
+Latent Class Pattern 1 1
+
+ Thresholds
+    H6_9$1            -0.718      0.218     -3.294      0.001
+    H6_9$2             0.973      0.299      3.258      0.001
+    H9_12$1           -2.516      0.463     -5.433      0.000
+    H9_12$2            0.675      0.132      5.118      0.000
+    H12_14$1          -1.025      0.145     -7.057      0.000
+    H12_14$2           1.240      0.116     10.725      0.000
+    H14_17$1          -1.566      0.149    -10.520      0.000
+    H14_17$2           1.090      0.100     10.909      0.000
+    H17_20$1          -1.998      0.125    -16.000      0.000
+    H17_20$2           1.549      0.100     15.556      0.000
+    H20_22$1          -0.933      0.085    -10.914      0.000
+    H20_22$2           1.829      0.103     17.770      0.000
+    H22_6$1            0.253      0.083      3.046      0.002
+    H22_6$2            2.308      0.117     19.691      0.000
+
+Latent Class Pattern 1 2
+
+ Thresholds
+    H6_9$1            -4.021      1.788     -2.249      0.025
+    H6_9$2            -0.115      0.259     -0.445      0.656
+    H9_12$1            0.167      0.373      0.448      0.654
+    H9_12$2            2.142      0.586      3.657      0.000
+    H12_14$1          -3.210      1.518     -2.115      0.034
+    H12_14$2           0.858      0.167      5.124      0.000
+    H14_17$1           0.044      0.384      0.114      0.909
+    H14_17$2           1.617      0.293      5.509      0.000
+    H17_20$1          -2.109      0.390     -5.409      0.000
+    H17_20$2           1.399      0.196      7.126      0.000
+    H20_22$1          -0.367      0.174     -2.109      0.035
+    H20_22$2           2.347      0.382      6.151      0.000
+    H22_6$1            0.754      0.259      2.912      0.004
+    H22_6$2            2.542      0.264      9.646      0.000
+
+Latent Class Pattern 1 3
+
+ Thresholds
+    H6_9$1           -15.000      0.000    999.000    999.000
+    H6_9$2             2.357      0.783      3.011      0.003
+    H9_12$1           -1.433      0.372     -3.850      0.000
+    H9_12$2           -0.604      0.279     -2.166      0.030
+    H12_14$1          -1.988      0.257     -7.749      0.000
+    H12_14$2           0.524      0.125      4.209      0.000
+    H14_17$1          -1.027      0.232     -4.436      0.000
+    H14_17$2           0.274      0.131      2.087      0.037
+    H17_20$1          -2.665      0.310     -8.605      0.000
+    H17_20$2           0.707      0.112      6.322      0.000
+    H20_22$1          -0.527      0.152     -3.462      0.001
+    H20_22$2           0.702      0.138      5.102      0.000
+    H22_6$1            1.119      0.185      6.062      0.000
+    H22_6$2            1.748      0.183      9.544      0.000
+
+Latent Class Pattern 2 1
+
+ Thresholds
+    H6_9$1             1.663      0.199      8.370      0.000
+    H6_9$2             1.839      0.198      9.274      0.000
+    H9_12$1           -2.150      0.281     -7.643      0.000
+    H9_12$2           -0.869      0.140     -6.190      0.000
+    H12_14$1          -1.978      0.191    -10.349      0.000
+    H12_14$2           0.323      0.078      4.139      0.000
+    H14_17$1           0.237      0.183      1.293      0.196
+    H14_17$2           0.782      0.123      6.352      0.000
+    H17_20$1          -2.936      0.428     -6.853      0.000
+    H17_20$2           0.632      0.081      7.807      0.000
+    H20_22$1           0.028      0.142      0.194      0.846
+    H20_22$2           0.868      0.086     10.145      0.000
+    H22_6$1            0.658      0.109      6.010      0.000
+    H22_6$2            1.326      0.100     13.215      0.000
+
+Latent Class Pattern 2 2
+
+ Thresholds
+    H6_9$1             1.640      0.171      9.619      0.000
+    H6_9$2             1.906      0.179     10.678      0.000
+    H9_12$1           -1.954      0.347     -5.636      0.000
+    H9_12$2           -0.360      0.127     -2.842      0.004
+    H12_14$1          -0.016      0.189     -0.084      0.933
+    H12_14$2           0.948      0.135      7.029      0.000
+    H14_17$1          -1.906      0.301     -6.327      0.000
+    H14_17$2           0.371      0.080      4.614      0.000
+    H17_20$1          -0.812      0.116     -7.030      0.000
+    H17_20$2           0.910      0.089     10.259      0.000
+    H20_22$1          -0.742      0.089     -8.318      0.000
+    H20_22$2           0.998      0.085     11.705      0.000
+    H22_6$1            0.298      0.083      3.608      0.000
+    H22_6$2            1.337      0.099     13.475      0.000
+
+Latent Class Pattern 2 3
+
+ Thresholds
+    H6_9$1            -1.072      0.500     -2.144      0.032
+    H6_9$2            -0.309      0.346     -0.892      0.372
+    H9_12$1            2.441      1.044      2.339      0.019
+    H9_12$2            3.599      1.983      1.815      0.069
+    H12_14$1          -1.029      0.211     -4.880      0.000
+    H12_14$2           0.603      0.123      4.913      0.000
+    H14_17$1          -0.010      0.243     -0.041      0.967
+    H14_17$2           0.784      0.157      4.977      0.000
+    H17_20$1          -0.953      0.203     -4.684      0.000
+    H17_20$2           0.779      0.135      5.784      0.000
+    H20_22$1          -0.105      0.210     -0.500      0.617
+    H20_22$2           1.203      0.135      8.914      0.000
+    H22_6$1            0.582      0.299      1.950      0.051
+    H22_6$2            1.370      0.206      6.653      0.000
+
+Latent Class Pattern 3 1
+
+ Thresholds
+    H6_9$1            -4.593      1.699     -2.703      0.007
+    H6_9$2            -2.975      0.428     -6.957      0.000
+    H9_12$1           -0.322      0.207     -1.553      0.120
+    H9_12$2            0.398      0.363      1.095      0.274
+    H12_14$1          -5.060      3.668     -1.380      0.168
+    H12_14$2           0.307      0.100      3.080      0.002
+    H14_17$1           0.186      0.530      0.351      0.726
+    H14_17$2           0.317      0.245      1.295      0.195
+    H17_20$1          -4.019      0.957     -4.199      0.000
+    H17_20$2           0.747      0.093      7.987      0.000
+    H20_22$1          -0.233      0.132     -1.767      0.077
+    H20_22$2           0.607      0.109      5.571      0.000
+    H22_6$1            1.304      0.146      8.918      0.000
+    H22_6$2            1.850      0.160     11.579      0.000
+
+Latent Class Pattern 3 2
+
+ Thresholds
+    H6_9$1            -1.232      0.195     -6.305      0.000
+    H6_9$2            -0.858      0.169     -5.068      0.000
+    H9_12$1           -4.377      1.937     -2.260      0.024
+    H9_12$2           -1.488      0.316     -4.717      0.000
+    H12_14$1          -1.727      0.227     -7.611      0.000
+    H12_14$2           0.302      0.082      3.666      0.000
+    H14_17$1          -1.834      0.237     -7.730      0.000
+    H14_17$2          -0.294      0.186     -1.582      0.114
+    H17_20$1          -2.588      0.487     -5.313      0.000
+    H17_20$2           0.631      0.062     10.187      0.000
+    H20_22$1          -0.920      0.078    -11.852      0.000
+    H20_22$2           0.462      0.073      6.308      0.000
+    H22_6$1            0.640      0.119      5.361      0.000
+    H22_6$2            1.162      0.129      9.039      0.000
+
+Latent Class Pattern 3 3
+
+ Thresholds
+    H6_9$1            -4.941      5.813     -0.850      0.395
+    H6_9$2            -2.680      0.887     -3.024      0.002
+    H9_12$1           -0.765      0.640     -1.195      0.232
+    H9_12$2            1.164      0.920      1.265      0.206
+    H12_14$1          -1.415      0.439     -3.226      0.001
+    H12_14$2           0.566      0.085      6.626      0.000
+    H14_17$1          -2.052      0.650     -3.158      0.002
+    H14_17$2           0.612      0.210      2.909      0.004
+    H17_20$1          -1.627      0.427     -3.810      0.000
+    H17_20$2           0.713      0.103      6.935      0.000
+    H20_22$1          -0.850      0.329     -2.585      0.010
+    H20_22$2           0.685      0.134      5.104      0.000
+    H22_6$1            1.237      0.195      6.349      0.000
+    H22_6$2            1.893      0.179     10.582      0.000
+
+Between Level
+
+Categorical Latent Variables
+
+Within Level
+
+ Intercepts
+    CW#1              -0.076      0.366     -0.208      0.835
+    CW#2               0.475      0.309      1.539      0.124
+
+Between Level
+
+ CW#1       ON
+    CB#1               1.223      0.473      2.585      0.010
+    CB#2               0.793      0.441      1.796      0.073
+
+ CW#2       ON
+    CB#1              -0.282      0.535     -0.526      0.599
+    CB#2               0.333      0.455      0.733      0.464
+
+ Means
+    CB#1              -0.417      0.100     -4.178      0.000
+    CB#2              -0.386      0.067     -5.770      0.000
+
+QUALITY OF NUMERICAL RESULTS
+
+     Condition Number for the Information Matrix              0.428E-04
+       (ratio of smallest to largest eigenvalue)
+
+SAVEDATA INFORMATION
+
+  Save file
+    H:\summer_project\Mplus\TimeSlots\Multilevel\NDNSslot_CW3CB3.txt
+
+  Order of variables
+
+    H6_9
+    H9_12
+    H12_14
+    H14_17
+    H17_20
+    H20_22
+    H22_6
+    ID_DY
+    AGE
+    SEX
+    CPROB1
+    CPROB2
+    CPROB3
+    CPROB4
+    CPROB5
+    CPROB6
+    CPROB7
+    CPROB8
+    CPROB9
+    CB
+    CW
+    MLCJOINT
+    ID
+
+  Save file format           Free
+
+  Save file record length    10000
+
+DIAGRAM INFORMATION
+
+  Mplus diagrams are currently not available for Mixture analysis.
+  No diagram output was produced.
+
+     Beginning Time:  09:55:10
+        Ending Time:  10:02:01
+       Elapsed Time:  00:06:51
+
+MUTHEN & MUTHEN
+3463 Stoner Ave.
+Los Angeles, CA  90066
+
+Tel: (310) 391-9971
+Fax: (310) 391-8971
+Web: www.StatModel.com
+Support: Support@StatModel.com
+
+Copyright (c) 1998-2015 Muthen & Muthen
+\end{verbatim}
+
 \end{document}

### 2018-08-03 paper/Chapters/Chapter2.tex
results MLCA almost done

@@
 Essentially this allows the probability that an observation day will belong to a
-particular day-level latent class to vary across individual levels.\vspace{-0.5cm}
+particular day level latent class to vary across individual levels.\vspace{-0.5cm}
 
@@
 an observed high carbohydrate eating day vs.
-a low carbohydrate eating day) is constant within individual-level which means for each person throughout his/her survey there is some probability of following a high carbohydrate eating day.
+a low carbohydrate eating day) is constant within individual level which means for each person throughout his/her survey there is some probability of following a high carbohydrate eating day.
 A random effect model considers the individuals (level 2) to be drawn from the adult population in the UK, and the probability of the outcome (i.e.
@@
 Same framework can be used to consider random effects in an LCA model, but instead of saying that $C_{ij}$ is either low or high carbohydrate eating days as if we already know, it is now replaced by a latent variable $G_{ij}$ which indicates the typologies of carbohydrate eating patterns.
-Then we can use the day-level data to assess the log-odds of belonging to $k$th type of carbohydrate eating pattern on a specific day of survey, and we allow the log-odds to vary across individuals.
+Then we can use the day level data to assess the log-odds of belonging to $k$th type of carbohydrate eating pattern on a specific day of survey, and we allow the log-odds to vary across individuals.
 Therefore, for some persons the log-odds of having a $k$th type of carbohydrate eating pattern during the survey can be high, but for the other persons, the log-odds of following the $k$th type of carbohydrate eating pattern can be low.
 
-If the day-level LCA model (carbohydrate eating pattern typologies) is best defined by $T (T \geqslant 2)$ latent classes, then $T-1$ random intercept will be specified by a two-level multinomial logistic regression model.
+If the day level LCA model (carbohydrate eating pattern typologies) is best defined by $T (T \geqslant 2)$ latent classes, then $T-1$ random intercept will be specified by a two-level multinomial logistic regression model.
 Similar to the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each time slots, throughout 4 consecutive days of survey period).
@@
 	\item $ U_{ijk} $ represents the response of eating carbohydrate (one of the following: not eating any food, $< 50\%$ of the energy, or $\geqslant 50\%$ of the energy) on $i$th day of the survey ($i \in (1,2,3,4)$) in $j$th individual at the $k$th time slot of the day ($k \in (1, 2, 3, \cdots, 7)$);
-	\item $G_{ij}$ denotes the latent class membership for $j$th individuals on $i$th day of the survey, the total number of day-level latent class is $T$;
+	\item $G_{ij}$ denotes the latent class membership for $j$th individuals on $i$th day of the survey, the total number of day level latent class is $T$;
 %	\item A specific latent class is referred to as $t$, and the total number of level 1 latent classes is denoted by $T$;
@@
 This approach is less computationally demanding compared with the parametric approach.
-These level 2 (individual) latent classes reflect differences in the probability of belonging to a specific day-level latent class, so that individuals that contain observation days with similar probabilities for the level 1 latent classes will be grouped together.
+These level 2 (individual) latent classes reflect differences in the probability of belonging to a specific day level latent class, so that individuals that contain observation days with similar probabilities for the level 1 latent classes will be grouped together.
 The non-parametric MLCA model can be defined as follows: \vspace{-0.7cm}
@@
 \begin{itemize}
-	\item $CB_j$ is individual-level latent class membership for $j$th individual;
-	\item $\gamma_{tm}$ is day-level and individual-level indicators. 
+	\item $CB_j$ is individual level latent class membership for $j$th individual;
+	\item $\gamma_{tm}$ is day level and individual level indicators. 
 \end{itemize}
@@
 	\item Next, a series of MLCA models were fitted to account for the multi-level structrure of the data.
-In these models, the number of observational-level classes was based on the best fitting LCA model from the first step, and the LCA model at the individual-level was estimated to identify the number of individual-level latent classes;
-	\item Thirdly, when number of individual-level latent classes is defined based on the previous stage, observational-level classes was modified (one class lower and one class higher than in the second step), to see the effect of changing level 1 classes and confirm the best fitting model.
+In these models, the number of observational-level classes was based on the best fitting LCA model from the first step, and the LCA model at the individual level was estimated to identify the number of individual level latent classes;
+	\item Thirdly, when number of individual level latent classes is defined based on the previous stage, observational-level classes was modified (one class lower and one class higher than in the second step), to see the effect of changing level 1 classes and confirm the best fitting model.
 \end{itemize}
@@
 $q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability.
-In the step of performing multilevel LCA, where LMR-LRT is available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day-level and individual-level.
-MLCA models were fitted in Mplus 7.4 \parencite{muthen2005mplus}, the Mplus codes are shown in the Appendix xxx.
+In the step of performing multilevel LCA, where LMR-LRT is available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day level and individual level.
+MLCA models were fitted in Mplus 7.4 \parencite{muthen2005mplus}, the Mplus codes are shown in \textbf{Appendix \ref{AppendixB}}.
 \vspace{-0.3cm}
@@
 
-\section{Association between day-level and individual-level latent classes and other variables}\vspace{-0.3cm}
+\section{Day level latent classes and their characteristics}\vspace{-0.3cm}
 
-Day-level latent classes identified by MLCA steps were tabulated according to whether the diary was recorded during weekdays or not.
+Day level latent classes identified by MLCA steps were tabulated according to whether the diary was recorded during weekdays or not.
 A contingency table giving the frequency of responses across the 7 time slots of the survey days was produced.

### 2018-08-03 paper/Chapters/Chapter3.tex
results MLCA almost done

@@
 
-\section{Model selection, comparison, and interpretation}
+\section{Model selection, and interpretation}\vspace{-0.4cm}
 
-%
-%-----------------------------------
-%	SUBSECTION 1
-%-----------------------------------
-%\subsection{Subsection 1}
+A series of traditional LCA of the responses to carbohydrate intake within 7 time slots of day was first examined.
+These initial analyses ignored the clustering of observation days within participants of the survey.
+\textbf{Table \ref{tab:mixmodels}} shows the latent class solutions for one to five classes (see rows under the Fixed effects model section).
+The BIC declines with the number of day level classes increases.
+However, the improvement of BIC dropped to less than 1000 from 3 classes to 4 classes solutions (658.9) and from 4 classes to 5 classses solutions (361.7).
+Entropy index indicates that the 4 classes model could explain about 51\% percent of the data, while \textit{p} values of Lo-Mendell-Rubun LRT suggest that the more classes we fit, the better model we will have until up to 6 classes (\textit{p} = 0.06 and is not shown in the table).
+However, from the parsimony point of view, we extend the model with random effects building on 2 classes, 3 classes and 4 classes solutions.
+
+The results of the random effect included models are presented in \textbf{Table \ref{tab:mixmodels}} under the Random effects model section.
+It is obvious that the BIC improves with the addition of the random effects which account for the nested structure of the data.
+Entropy indicates that 4 classes in individual level and 2 classes in the day level may be the best solution mathematically.
+However, after these solutions were checked in more details, the potentially most substantively interpretable model was found to be the 3$\times$3 random effect model, which is the model with 3 latent classes in the day level, and 3 latent classes in the individual level.
+We must emphasize that different researchers may have made decision slightly different from ours, we provided the descriptions and figures for other solutions in the \textbf{Appendix xxx} for reference.
+
+In this 3 classes solution we have chosen in the day level, there were 39.5\%, 20.4\%, and 40.1\% classified into 3 latent groups.
+The overall counts and percentages for each responses within every time slot and the distributions of the solution are presented in \textbf{Table \ref{tab:daylevel}}.
+The trajectories illustrating the change of the probabilities of each response to carbohydrate eating during the hours of the day are shown separately by the three types of days in \textbf{Figure \ref{fig:level1}}.
 
@@
 
-	\caption{\label{tab:mixmodels}Fit Criteria for Each Model Specification}\vspace{-0.3cm}
+	\caption{\label{tab:mixmodels}Fit criteria for each model specification.}\vspace{-0.3cm}
 	\centering
@@
 		\toprule
-		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Number of day-level classes}} \\
+		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Number of day level classes}} \\
 		\cmidrule(l{2pt}r{2pt}){2-6}
@@
 		\hspace{1em}\hspace{1em}Log-likelihood & -173793.306 & -172669.771 & -172039.204 & -171633.941 & -171377.292\\
-		\hspace{1em}\hspace{1em}BIC & 347728.092 & 345632.608 & 344523.06 & 343864.121 & 343502.409\\
-		\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & -- & $<$ 0.0001 & 1e-04 & $<$ 0.0001 & $<$ 0.0001\\
-		\hspace{1em}\hspace{1em}Entropy & 1 & 0.31 & 0.392 & 0.51 & 0.481\\
+		\hspace{1em}\hspace{1em}BIC & 347728.092 & 345632.608 & 344523.060 & 343864.121 & 343502.409\\
+		\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & -- & $<$ 0.0001 & $<$ 0.0001 & $<$ 0.0001 & $<$ 0.0001\\
+		\hspace{1em}\hspace{1em}Entropy & 1 & 0.310 & 0.392 & 0.510 & 0.481\\
 		\addlinespace[0.3em]
 		\multicolumn{6}{l}{\textbf{Random effects model}}\\
-		\hspace{1em}2 individual-level classes &  &  &  &  & \\
+		\hspace{1em}2 individual level classes &  &  &  &  & \\
 		\hspace{1em}\hspace{1em}No. of free parameters &  & 59 & 89 & 119 & \\
@@
 		\hspace{1em}\hspace{1em}Entropy &  & 0.581 & 0.569 & 0.555 & \\
-		\hspace{1em}3 individual-level classes &  &  &  &  & \\
+		\hspace{1em}3 individual level classes &  &  &  &  & \\
 		\hspace{1em}\hspace{1em}No. of free parameters &  & 89 & 134 & 179 & \\
@@
 		\hspace{1em}\hspace{1em}BIC &  & 334771.968 & 334051.799 & 333934.448 & \\
-		\hspace{1em}\hspace{1em}Entropy &  & 0.677 & 0.63 & 0.644 & \\
-		\hspace{1em}4 individual-level classes &  &  &  &  & \\
+		\hspace{1em}\hspace{1em}Entropy &  & 0.677 & 0.630 & 0.644 & \\
+		\hspace{1em}4 individual level classes &  &  &  &  & \\
 		\hspace{1em}\hspace{1em}No. of free parameters &  & 119 & 179 &  & \\
@@
 		\multicolumn{6}{l}{\textit{Note: }}\\
-		\multicolumn{6}{l}{Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index;}\\ 
-		\multicolumn{6}{l}{Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.}\\
+		\multicolumn{6}{l}{\textbf{Abbreviation}: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index;}\\ 
+		\multicolumn{6}{l}{Lo-Mendel-Rubin LRT, likelihood ratio test comparing $q$ classes models with $q-1$ classes models.}\\
 	\end{tabular}
@@
 
+Class 1 days \textbf{(Figure \ref{fig:level1}-A)} were given the name of "high carbohydrate day" since in these days of survey, the probabilities of carbohydrate contributed higher or equal to 50\% of the energy consumed were always higher than that in the other two types of days.
+Specifically, these days were characterised with probabilities of over 0.6 in time slots between 6 am to 9 am, 9 am to 12 am, and also 2 pm to 5 pm, during which the time slots may be interpreted as breakfast, morning snack, and afternoon snack time periods for many participants.
+Moreover, even during late night time period, such as 8 pm to 10 pm, and 10 pm to 6 am time slots, the probabilities of having higher carbohydrate contained food were still as high as 0.412, and 0.246, respectively.
+
 \rowcolors{2}{gray!6}{white}
 
-\begin{table}
+\begin{table}[H]
 
-	\caption{\label{tab:daylevel}Day Level Latent Class Solution for Three-Class Model (No Individual level Model)}\vspace{-0.3cm}
+	\caption{\label{tab:daylevel}Day level latent class solution for three classes solution. (No Individual level Model)}\vspace{-0.3cm}
 	\centering
@@
 		\toprule
-		\textbf{Time slots of} & \textbf{Responses of} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1\\(39.5\%)}} & \textbf{\Centerstack{Class 2\\(20.4\%)}} & \textbf{\Centerstack{Class 3\\(40.1\%)}} \\
+		\textbf{Time slots of} & \textbf{Responses to} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1\\(39.5\%)}} & \textbf{\Centerstack{Class 2\\(20.4\%)}} & \textbf{\Centerstack{Class 3\\(40.1\%)}} \\
 		\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
@@
 		6 am – 9 am &  &  &  &  &  & \\
-		& Not eating & 7655 & 31.2 & 0.129 & 0.450 & 0.320\\
+		& Not eating any food & 7655 & 31.2 & 0.129 & 0.450 & 0.320\\
 		& Carbohydrate $<$ 50\%\textsuperscript{*} & 4500 & 18.4 & 0.130 & 0.267 & 0.128\\
@@
 		9 am – 12 am &  &  &  &  &  & \\
-		& Not eating & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
+		& Not eating any food & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
 		& Carbohydrate $<$ 50\% & 7227 & 29.5 & 0.158 & 0.492 & 0.173\\
@@
 		12 noon – 2 pm &  &  &  &  &  & \\
-		& Not eating & 4783 & 19.5 & 0.156 & 0.356 & 0.019\\
+		& Not eating any food & 4783 & 19.5 & 0.156 & 0.356 & 0.019\\
 		& Carbohydrate $<$ 50\% & 11112 & 45.4 & 0.405 & 0.413 & 0.560\\
@@
 		2 pm – 5 pm &  &  &  &  &  & \\
-		& Not eating & 6926 & 28.3 & 0.130 & 0.123 & 0.659\\
+		& Not eating any food & 6926 & 28.3 & 0.130 & 0.123 & 0.659\\
 		& Carbohydrate $<$ 50\% & 8277 & 33.8 & 0.249 & 0.602 & 0.076\\
@@
 		5 pm – 8 pm &  &  &  &  &  & \\
-		& Not eating & 3043 & 12.4 & 0.114 & 0.199 & 0.034\\
+		& Not eating any food & 3043 & 12.4 & 0.114 & 0.199 & 0.034\\
 		& Carbohydrate $<$ 50\% & 14240 & 58.2 & 0.516 & 0.590 & 0.639\\
@@
 		8 pm – 10 pm &  &  &  &  &  & \\
-		& Not eating & 8722 & 35.6 & 0.322 & 0.291 & 0.480\\
+		& Not eating any food & 8722 & 35.6 & 0.322 & 0.291 & 0.480\\
 		& Carbohydrate $<$ 50\% & 8898 & 36.3 & 0.266 & 0.551 & 0.212\\
@@
 		10 pm – 6 am &  &  &  &  &  & \\
-		& Not eating & 16295 & 66.6 & 0.680 & 0.590 & 0.751\\
+		& Not eating any food & 16295 & 66.6 & 0.680 & 0.590 & 0.751\\
 		& Carbohydrate $<$ 50\% & 4144 & 16.9 & 0.074 & 0.294 & 0.101\\
@@
 \rowcolors{2}{white}{white}
+\vspace{-0.3cm}
 
-\begin{figure}
+Class 2 days \textbf{(Figure \ref{fig:level1}-B)} were named as "low carbohydrate day" because first of all, in these days the possibility of participants skipping breakfast was 0.45.
+And after 9 am, within class 2 days, the probability of having food with lower carbohydrate (contributed less than 50\% of total energy intake), was always higher than having higher carbohydrate contained food.
+In these days, participants also turned to have morning snacks (with only 0.079 possibility of Not eating any food and similar probabilities of having either high or low carbohydrate contained food).
+This phenomenon may also be interpreted as having a long and late breakfast in these mornings.
+The probability of Not eating any food was lowest for class 2 days during the midnights time slot (10 pm to 6 am), with about 0.590 compared with 0.680 and 0.751 during the class 1 and class 3 days.
+
+\begin{figure}[H]
 	%\vspace*{13cm}
 	\centering
-	\includegraphics{Figures/level1.png}
+	\includegraphics[width=14cm]{Figures/level1.png}
 	\decoRule
-	\caption[Day Level Latent Classes.]{Day Level Latent Classes.}
+	\caption[Day Level Latent Class Solution.]{Day Level Latent Classes Solution.}
 	\label{fig:level1}
@@
 
+Class 3 days \textbf{(Figure \ref{fig:level1}-C)} were called "regular meals day" due to the following reasons: 1) participants recordings showed that in these days there was almost 0 possibility of not eating any food at lunch (0.019 between 12 noon and 2 pm) or dinner (0.034 between 5 pm and 8 pm); 2) the probabilities of not having morning snack (9 am to 12 am) and afternoon snack (2 pm to 5 pm) were also the highest among the three types of days (0.401 and 0.659).
+3) during these days, participants may have some high carbohydrate contained food between 8 pm and 10 pm (0.308), but the probability of not eating any food during 10 pm to 6 am next morning was 0.751, the highest among the three types of days.
+\vspace{-0.5cm}
+
+\subsection{Features of the three carbohydrate eating time patterns}
+
+The details of the characteristics of the three types of carbohydrate eating time pattern were listed in\textbf{ Table \ref{tab:day-level-features}}.
+Specifically, regular meals day turned to be recorded slightly more often in Northern Ireland, and Scotland.
+In terms of day of week distribution in the three types of days, there is strong evidence (\textit{p} < 0.001) that high carbohydrate days appeared more frequently in weekends (32.5\%) compared with low carbohydrate day (26.5\%) and regular meals day (30.7\%).
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+	\caption{\label{tab:day-level-features}Means (standard deviations), and counts (\%) of the characteristics of different types of days according to carbohydrate intake.}
+	\centering
+	\fontsize{9}{11}\selectfont
+	\begin{tabular}[t]{lcccc}
+		\hiderowcolors
+		\toprule
+		& \textbf{\Centerstack{High carbo-\\hydrate day}} & \textbf{\Centerstack{Low carbo-\\hydrate day}} & \textbf{\Centerstack{Regular\\meals day}} & \textbf{\textit{P} value}\textsuperscript{*}\\
+		\midrule
+		\showrowcolors
+		Counts (\%) & 9667 (39.5) & 5002 (20.4\%) & 9814 (40.1\%) & \\
+		Country (\%) &  &  &  & < 0.001\\
+		\hspace{1em}England & 5627 (58.2) & 2972 (59.4) & 5291 (53.9) & \\
+		\hspace{1em}Northern Ireland & 1194 (12.4) & 527 (10.5) & 1400 (14.3) & \\
+		\hspace{1em}Scotland & 1527 (15.8) & 813 (16.3) & 1774 (18.1) & \\
+		\hspace{1em}Wales & 1318 (13.6) & 690 (13.8) & 1349 (13.7) & \\
+		Day of Week (\%) &  &  &  & < 0.001\\
+		\hspace{1em}Monday & 1303 (13.5) & 715 (14.3) & 1370 (14.0) & \\
+		\hspace{1em}Tuesday & 1266 (13.1) & 674 (13.5) & 1290 (13.1) & \\
+		\hspace{1em}Wednesday & 1225 (12.7) & 740 (14.8) & 1233 (12.6) & \\
+		\hspace{1em}Thursday & 1272 (13.2) & 752 (15.0) & 1425 (14.5) & \\
+		\hspace{1em}Friday & 1458 (15.1) & 797 (15.9) & 1479 (15.1) & \\
+		\hspace{1em}Saturday & 1537 (15.9) & 703 (14.1) & 1495 (15.2) & \\
+		\hspace{1em}Sunday & 1605 (16.6) & 621 (12.4) & 1522 (15.5) & \\
+		\hspace{1em}Weekend, Yes (\%) & 3142 (32.5) & 1324 (26.5) & 3017 (30.7) & < 0.001\\
+		Total energy (kJ) & 7539.98 (2875.87) & 7160.22 (2922.15) & 7439.68 (2978.91) & < 0.001\\
+		Carbohydrate (g) & 222.79 (89.84) & 209.70 (86.17) & 206.59 (84.42) & < 0.001\\
+		Protein (g) & 71.36 (29.79) & 69.55 (30.20) & 73.29 (32.94) & < 0.001\\
+		Fat (g) & 65.44 (33.27) & 63.94 (33.76) & 67.24 (34.73) & < 0.001\\
+		Alcohol (g) & 11.76 (27.31) & 8.85 (24.25) & 13.80 (33.00) & < 0.001\\
+		Total sugars (g) & 98.63 (56.03) & 88.03 (50.50) & 86.39 (50.96) & < 0.001\\
+		Starch (g) & 124.07 (55.84) & 121.59 (56.13) & 120.11 (54.62) & < 0.001\\
+		Non-milk extrinsic sugar\textsuperscript{\dag} & 59.45 (49.31) & 50.07 (43.41) & 50.41 (44.84) & < 0.001\\
+		Fruit (g) & 107.40 (137.97) & 103.15 (129.08) & 92.76 (126.02) & < 0.001\\
+		Yellow Red Green Vegetables (g) & 26.52 (46.44) & 26.84 (47.99) & 26.16 (45.99) & 0.681\\
+		\bottomrule
+		\multicolumn{5}{l}{\textit{Note: }}\\
+		\multicolumn{5}{l}{\textsuperscript{*} \textit{P} values were obtained from Pearson $\chi^2$ test for categorical variables, and one-way ANOVA }\\
+		\multicolumn{5}{l}{comparing the means in multiple groups for continuous variables;}\\
+		\multicolumn{5}{l}{\textsuperscript{\dag} Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey,}\\ 
+		\multicolumn{5}{l}{ glucose, fructose and glucose syrups, sugars added to food and sugars in fruit juices.}\\
+	\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
+As expected, consumption of total energy (7539.98 kJ), total carbohydrate (222.79 g), total sugar (98.63 g), starch (124.07 g), and non-milk extrinsic sugar (59.45 g) were highest among high carbohydrate days (all \textit{p} < 0.0001).
+On the other hand, the consumption of protein (73.29 g), total fat (67.24 g), and alcohol (13.80 g) were the highest in the so-called regular meals days.
+Moreover, in high carbohydrate days, participants turned to also consume the highest amount of fruit (107.40 g).
+There is no evidence of any difference for the consumption of yellow, red, or green vegetables across the three types of days (\textit{p} = 0.681).
+
 %---------------------------------
-
---
 %	SUBSECTION 2
@@
 
-\subsection{Subsection 2}
+\subsection{Individual level LCA solution}
+
+In the random effect models we utilized the non-parametric approach, in which we added a level 2 (individual level) latent classes based on the random means from the level 1 (day level) latent class solution.
+The results of the individual level LCA solution for 3 classes are presented in \textbf{Figure \ref{fig:CB2level2}}, and \textbf{\ref{fig:level2}}.
+
+With two individual level latent classes \textbf{(Figure \ref{fig:CB2level2})}, one individual class is comprised of individuals with a relatively slightly higher proportion of having "low carbohydrate day" (22.1\%) compared to the other (17.4\%).
+This class represents nearly 65\% of the individuals.
+
+\begin{figure}[H]
+	%\vspace*{13cm}
+	\centering
+	\includegraphics[width=13cm]{Figures/CB2level2.png}
+	\decoRule
+	\caption[Multilevel Latent Class Solution ($3\times2$).]{Multilevel Latent Class Solution, 3 classes in day level, 2 classes in individual level.}
+	\label{fig:CB2level2}
+\end{figure}
+
+With three individual level latent classes \textbf{(Figure \ref{fig:level2})}, a low-carbohydrate eaters class, moderate-carbohydrate eaters class, and high-carbohydrate eaters class emerges.
+43.1\% participants were identified as high-carbohydrate eaters, in these individuals, about 50\% of the days (2 out of 4 days) of their dietary diary were classified as having high carbohydrate days.
+Nearly 1 out of 4 days of their dietary diary were either "regular meals day" or "low carbohydrate day".
+
+\begin{figure}[H]
+	%\vspace*{13cm}
+	\centering
+	\includegraphics[width=13cm]{Figures/level2.png}
+	\decoRule
+	\caption[Multilevel Latent Class Solution ($3\times3$).]{Multilevel Latent Class Solution, 3 classes in day level, 3 classes in individual level.}
+	\label{fig:level2}
+\end{figure}
+\vspace{-0.6cm}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}[H]
+
+\caption{\label{tab:Level2tab1}Weighted means, percentages, and
+95\% CIs of the social, economical characteristics by latent class memberships in the UK
+adults. (NDNS RP 2008/09-2015/16, sample size = 6155)} \centering
+\fontsize{9}{11}\selectfont
+
+\begin{tabular}[t]{lcccc}
+	\hiderowcolors
+	\toprule
+	\textbf{Variables} & \textbf{\Centerstack{Individual class 1\\(n = 1730)}} & \textbf{\Centerstack{Individual class 2\\(n = 1772)}} & \textbf{\Centerstack{Individual class 3\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
+	\midrule
+	\showrowcolors
+	Total (\%) & 28.4 (26.9, 29.9) & 28.7 (27.1, 30.3) & 43.0 (41.3, 44.7) & \\
+	Countries (\%) &  &  &  & 0.007\\
+	\hspace{1em}England & 84.5 (81.7, 86.9) & 82.0 (79.3, 84.5) & 84.7 (82.3, 86.8) & \\
+	\hspace{1em}Northern Ireland & 2.1 (1.6, 2.8) & 4.2 (3.2, 5.6) & 2.2 (1.7, 3.0) & \\
+	\hspace{1em}Scotland & 9.1 (7.0, 11.8) & 8.6 (6.7, 11.1) & 8.0 (6.3, 10.2) & \\
+	\hspace{1em}Wales & 4.3 (3.3, 5.6) & 5.1 (4.0, 6.4) & 5.1 (4.0, 6.4) & \\
+	Age (years) & 51.0 (49.9, 52.1) & 40.3 (39.1, 41.6) & 51.7 (50.7, 52.7) & < 0.001\\
+	Sex (\%) &  &  &  & 0.119\\
+	\hspace{1em}Men & 50.0 (46.9, 53.1) & 50.2 (47.0, 53.5) & 46.6 (44.0, 49.1) & \\
+	\hspace{1em}Women & 50.0 (46.9, 53.1) & 49.8 (46.5, 53.0) & 53.4 (50.9, 56.0) & \\
+	Survey years (\% in rows) &  &  &  & 0.015\\
+	\hspace{1em}1 & 32.5 (28.4, 36.9) & 26.3 (21.9, 31.2) & 41.2 (36.6, 46.0) & \\
+	\hspace{1em}2 & 26.8 (22.6, 31.3) & 22.6 (18.6, 27.3) & 50.6 (45.8, 55.4) & \\
+	\hspace{1em}3 & 22.6 (18.8, 26.9) & 33.7 (28.6, 39.2) & 43.6 (38.7, 48.7) & \\
+	\hspace{1em}4 & 27.9 (24.1, 32.2) & 27.6 (23.8, 31.8) & 44.4 (40.2, 48.7) & \\
+	\hspace{1em}5 & 27.9 (24.2, 32.0) & 28.7 (24.4, 33.5) & 43.3 (38.2, 48.6) & \\
+	\hspace{1em}6 & 28.0 (24.0, 32.4) & 31.5 (26.9, 36.6) & 40.5 (35.8, 45.3) & \\
+	\hspace{1em}7 & 29.1 (25.2, 33.4) & 29.0 (24.5, 34.0) & 41.8 (37.1, 46.7) & \\
+	\hspace{1em}8 & 31.1 (27.3, 35.3) & 30.5 (25.9, 35.5) & 38.4 (34.1, 42.8) & \\
+	Paid employment\textsuperscript{\dag} (\%) &  &  &  & 0.907\\
+	\hspace{1em}Yes & 40.3 (37.0, 43.6) & 40.8 (37.1, 44.5) & 39.8 (37.1, 42.6) & \\
+	\hspace{1em}No & 59.7 (56.4, 63.0) & 59.2 (55.5, 62.9) & 60.2 (57.4, 62.9) & \\
+	Live with partner\textsuperscript{\ddag} (\%) &  &  &  & < 0.001\\
+	\hspace{1em}Yes & 56.9 (53.6, 60.1) & 38.4 (35.2, 41.8) & 61.3 (58.7, 63.7) & \\
+	\hspace{1em}No & 43.1 (39.9, 46.4) & 61.6 (58.2, 64.8)) & 38.7 (36.3, 41,3) & \\
+	Household Income, \textsterling/year & \Centerstack{36558.53\\(34800.21, 38316.84)} & \Centerstack{27180.80\\(25597.95, 28763.65)} & \Centerstack{32171.58\\(31024.96, 33318.2)} & < 0.001\\
+	Ethnicity (\%) &  &  &  & \\
+	\hspace{1em}White & 94.2 (92.4, 95.6) & 79.5 (76.4, 82.3) & 91.9 (90.1, 93.4) & < 0.001\\
+	\hspace{1em}Non-White & 5.8 (4.4, 7.6) & 20.5 (17.7, 23.6) & 8.1 (6.6, 9.9) & \\
+	Education (\%) &  &  &  & \\
+	\hspace{1em}Degree or higher & 29.0 (26.1, 32.1) & 23.3 (20.5, 26.3) & 26.2 (24.1, 28.5) & 0.019\\
+	\hspace{1em}Lower than degree & 71.0 (67.9, 73.9) & 76.7 (73.7, 79.5) & 73.8 (71.5, 75.9) & \\
+	\bottomrule
+	\multicolumn{5}{l}{\textit{Note: }}\\
+	\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme.}\\
+	\multicolumn{5}{l}{Variables were weighted by individual weights.}\\
+	\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes with}\\ 
+	\multicolumn{5}{l}{Bonferroni correction to account for multiple testing across $>$ 2 classes. For categorical variables,}\\
+	\multicolumn{5}{l}{ differences between latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.} \\
+	\multicolumn{5}{l}{\textsuperscript{\dag} Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey.}\\
+	\multicolumn{5}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil} \\
+	\multicolumn{5}{l}{partnership.}\\
+\end{tabular}
+
+\end{table} 
+\rowcolors{2}{white}{white}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}[H]
+
+	\caption{\label{tab:tab2}Weighted means, percentages, and 95\% CIs of the anthropometric measurements, average main nutrients intake and biochemical characteristics by latent class memberships in the UK adults.
+\\(NDNS RP 2008/09-2015/16, sample size = 6155).}
+	\centering
+	\fontsize{9}{11}\selectfont
+	\begin{tabular}[t]{lcccc}
+		\hiderowcolors
+		\toprule
+		\textbf{Variables} & \textbf{\Centerstack{Individual class 1\\(n = 1730)}} & \textbf{\Centerstack{Individual class 2\\(n = 1772)}} & \textbf{\Centerstack{Individual class 3\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
+		\midrule
+		\showrowcolors
+		BMI (kg/m\textsuperscript{2}) & 27.8 (27.4, 28.2) & 27.2 (26.7, 27.7) & 27.3 (26.9, 27.6) & 0.006\\
+		WC (cm) & 94.6 (93.5, 95.6) & 92.3 (91.0, 93.5) & 92.2 (91.4, 93.1) & 0.001\\
+		Smoking status (\%) &  &  &  & \\
+		\hspace{1em}Current & 20.4 (18.0, 23.0) & 27.8 (25.0, 30.9) & 17.1 (15.4, 19.0) & < 0.001\\
+		\hspace{1em}Ex-smoker & 29.3 (26.5, 32.2) & 16.8 (14.6, 19.2) & 26.1 (24.9, 28.3) & \\
+		\hspace{1em}Never & 50.3 (47.2, 32.2) & 55.4 (52.2, 58.6) & 56.8 (54.3, 59.3) & \\
+		Current drinking status (\%) &  &  &  & \\
+		\hspace{1em}Yes & 11.8 (10.0, 13.8) & 24.0 (21.2, 27.1) & 20.6 (18.7, 22.8) & < 0.001\\
+		Hypertension\textsuperscript{\dag} (\%) &  &  &  & \\
+		\hspace{1em}Yes & 33.4 (29.9, 37.1) & 21.1 (17.7, 24.9) & 31.2 (28.3, 34.2) & < 0.001\\
+		Total energy intake (kJ) & \Centerstack{7985.8\\(7823.3, 8146.295)} & \Centerstack{7341.8\\(7825.3, 8146.3)} & \Centerstack{7677.0\\(7555.8, 7799,8)} & < 0.001\\
+		Carbohydrate percent\textsuperscript{\ddag} (\%) & 203.8 (199.8, 207.8) & 218.3 (212.9, 223.7) & 233.4 (229.6, 237.2) & < 0.001\\
+		Carbohydrate percent (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
+		Protein intake (g) & 79.9 (77.9, 81.8) & 69.3 (67.6, 71.0) & 73.7 (72.5, 74.8) & < 0.001\\
+		Protein percent (\%) & 17.2 (16.9, 17.5) & 16.3 (16.0, 16.6) & 16.5 (16.3, 16.6) & < 0.001\\
+		Fat intake (g) & 74.7 (73.1, 76.4) & 63.8 (62.1, 65.5) & 65.7 (64.4, 67.0) & < 0.001\\
+		Fat percent (\%) & 35.4 (34.9, 35.8) & 32.5 (32.1, 32.9) & 32.0 (31.7, 32.3) & < 0.001\\
+		Glucose (mmol/l) & 5.20 (5.15, 5.26) & 5.09 (5.02, 5.17) & 5.13 (5.09, 5.12) & 0.051\\
+		A1C (\%) & 5.49 (5.45, 5.52) & 5.44 (5.40, 5.48) & 5.52 (5.49, 5.55) & 0.012\\
+		DM \textsuperscript{\S} & 6.9 (5.0, 9.3) & 3.5 (2.3, 5.3) & 4.1 (2.9, 5.6) & 0.011\\
+		Physical
+		activity (hours/day) \textsuperscript{\P} & 1.63 (1.43, 1.83) & 1.32 (1.15, 1.49) & 1.65 (1.49, 1.81) & 0.016\\
+		\bottomrule
+		\multicolumn{5}{l}{\textit{Note: }}\\
+		\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
+		\multicolumn{5}{l}{ BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.}\\
+		\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) were weighted by blood sample weights, the others were}\\ 
+		\multicolumn{5}{l}{weighted by nurse visiting weights.}\\
+		\multicolumn{5}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
+		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes}\\ 
+		\multicolumn{5}{l}{with Bonferroni correction to accountfor multiple testing across $>$ 2 classes. For categorical variables, }\\
+		\multicolumn{5}{l}{differences between latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.}\\ 
+		\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure $\geqslant$ 140 mmHg or diastolic blood pressure }\\
+		\multicolumn{5}{l}{$\geqslant$ 90 mmHg, or under treatment for hypertension.}\\
+		\multicolumn{5}{l}{\textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake}\\  
+		\multicolumn{5}{l}{\textsuperscript{\S} DM was defined by A1C $>$ 6.5\%.}\\
+		\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity}\\
+		\multicolumn{5}{l}{including both work-related and recreational activities during the survey.}\\
+	\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
 
@@
 
-\section{Main Section 2}
+\section{Association between individual level latent classes and hypertension}
 
-\begin{figure}
-	%\vspace*{13cm}
-	\centering
-	\includegraphics[width=13cm]{Figures/level2.png}
-	\decoRule
-	\caption[Individual Level Latent Classes.]{individual Level Latent Classes.}
-	\label{fig:level2}
-\end{figure}
-\vspace{-0.6cm}
+\section{Association between individual level latent classes and obesity}
 
-%
-%\rowcolors{2}{gray!6}{white}
-%
-%\begin{table}
-%	
-%	\caption{\label{tab:LCGAtab1}Means, percentages, and 95\% CIs of the characteristics of carbohydrate temporal eating patterns by LCGA memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}
-%	\centering
-%	\fontsize{9}{11}\selectfont
-%	\begin{tabular}[t]{lcccc}
-%		\hiderowcolors
-%		\toprule
-%		 & Latent class = 1 & Latent class = 2 & Latent class = 3 & P value \textsuperscript{*}\\
-%		\midrule
-%		\showrowcolors
-%		Total (\%) & 28.4 (26.8, 30.1) & 7.0 (6.2, 7.9) & 64.6 (62.9, 66.2) & \\
-%		Countries (\%) &  &  &  & \\
-%		\hspace{1em}England & 81.4 (78.5, 84.0) & 87.5 (82.9, 91.0) & 84.6 (82.5, 86.4) & 0.004\\
-%		\hspace{1em}Northern Ireland & 3.9 (2.9, 5.1) & 0.6 (0.3, 1.2) & 2.5 (2.0, 3.2) & \\
-%		\hspace{1em}Scotland & 9.5 (7.4, 12.3) & 6.2 (3.5, 10.6) & 8.3 (6.7, 10.3) & \\
-%		\hspace{1em}Wales & 5.2 (4.1, 6.6) & 5.7 (3.8, 8.5) & 4.6 (3.8, 5.6) & \\
-%		Age (years) & 43.8 (42.4, 45.1) & 49.1 (47.2, 50.9) & 50.1 (49.3, 50.9) & $<$ 0.001\\
-%		Sex (\%) &  &  &  & \\
-%		\hspace{1em}Men & 50.6 (47.3, 53.9) & 49.6 (43.7, 55.4) & 47.6 (45.4, 49.7) & 0.273\\
-%		\hspace{1em}Women & 49.4 (46.1, 52.7) & 50.4 (44.6, 56.3) & 52.4 (50.3, 54.6) & \\
-%		Survey years (\%) &  &  &  & \\
-%		\hspace{1em}1 & 11.4 (8.8, 14.7) & 17.1 (12.4, 23.3) & 14.4 (11.9, 17.4) & 0.002\\
-%		\hspace{1em}2 & 10.1 (7.8, 13.1) & 18.3 (13.3, 24.7) & 12.4 (10.2, 15.0) & \\
-%		\hspace{1em}3 & 13.9 (10.8, 17.7) & 9.1 (5.7, 14.1) & 10.7 (8.6, 13.1) & \\
-%		\hspace{1em}4 & 10.9 (8.5, 13.9) & 13.8 (9.7, 19.4) & 13.2 (10.9, 16.0) & \\
-%		\hspace{1em}5 & 13.5 (10.6, 17.0) & 12.8 (8.4, 19.1) & 13.3 (11.0, 16.1) & \\
-%		\hspace{1em}6 & 12.8 (10.1, 16.1) & 8.7 (5.7, 12.9) & 11.5 (9.5, 13.9) & \\
-%		\hspace{1em}7 & 14.3 (11.5, 17.6) & 9.5 (6.5, 13.8) & 12.4 (10.2, 15.0) & \\
-%		\hspace{1em}8 & 13.2 (10.5, 16.4) & 10.5 (7.4, 14.8) & 12.1 (9.9, 14.6) & \\
-%		BMI (kg/m\textasciicircum{}2) & 27.5 (27.1, 27.9) & 27.0 (26.4, 27.6) & 27.4 (27.2, 27.6) & 0.433\\
-%		WC (cm) & 93.3 (92.1, 94.5) & 92.9 (90.9, 95.0) & 93.1 (92.3, 93.8) & 0.928\\
-%		Smoking status (\%) &  &  &  & \\
-%		\hspace{1em}Current & 24.1 (21.5, 27.0) & 30.0 (24.8, 35.8) & 18.8 (17.2, 20.6) & $<$ 0.001\\
-%		\hspace{1em}Ex-smoker & 20.0 (17.6, 22.6) & 27.5 (22.4, 33.2) & 25.9 (24.1, 27.7) & \\
-%		\hspace{1em}Never & 55.9 (52.7, 59.0) & 42.5 (36.6, 48.7) & 55.3 (53.2, 57.4) & \\
-%		Current drinking status (\%) &  &  &  & \\
-%		\hspace{1em}Yes & 24.6 (21.7, 27.7) & 18.3 (14.0, 23.6) & 16.8 (15.3, 18.4) & $<$ 0.001\\
-%		Hypertension (\%) \textsuperscript{\dag} &  &  &  & \\
-%		\hspace{1em}Yes & 25.9 (22.3, 29.9) & 31.8 (25.3, 39.1) & 30.4 (27.9 32.8) & 0.111\\
-%		Total energy intake (KJ) &  \Centerstack{ 6713.8 \\ (6575.7, 6851.8)}   &  \Centerstack{ 9256.0 \\ (8850.8, 9661.2)}   &  \Centerstack{7916.9 \\ (7814.0, 8019.9)}     & $<$ 0.001\\
-%		Carbohydrate intake (g) & 192.9 (188.5, 197.3) & 275.6 (263.4, 287.8) & 226.9 (223.9, 229.9) & $<$ 0.001\\
-%		Carbohydrate
-%		percent (\%) \textsuperscript{\ddag} & 45.8 (45.3, 46.4) & 47.4 (46.5, 48.3) & 45.6 (45.3, 45.9) & 0.001\\
-%		Glucose (mmol/l) & 5.16 (5.08, 5.23) & 5.09 (5.00, 5.18) & 5.14 (5.10, 5.19) & 0.537\\
-%		A1C (\%) & 5.47 (5.42, 5.51) & 5.48 (5.42, 5.54) & 5.49 (5.47. 5.52) & 0.403\\
-%		DM \textsuperscript{\S} & 5.9 (4.2, 8.2) & 1.1 (0.2, 5.2) & 4.7 (3.6, 6.0) & 0.053\\
-%        Physical activity (hs/day) \textsuperscript{\P}& 1.31 (1.14, 1.49) & 1.82 (1.44, 2.19) & 1.62 (1.49, 1.76) & 0.018\\
-%		\bottomrule
-%		\multicolumn{5}{l}{\textit{Note: }}\\
-%		\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; LCGA, latent class growth analysis; NDNS RP, national}\\ 
-%		\multicolumn{5}{l}{dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; }\\
-%		\multicolumn{5}{l}{A1C, haemoglobin A1c;DM, diabetes mellitus; h, hour.}\\
-%		\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights,}\\
-%		\multicolumn{5}{l}{the others are weighted by individual weights.}\\
-%		\multicolumn{5}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
-%		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes}\\   
-%		\multicolumn{5}{l}{with Bonferroni correction to account for multiple testing across >2 classes.}\\
-%		\multicolumn{5}{l}{For categorical variables, differences between latent classes were assessed}\\
-%		\multicolumn{5}{l}{using the adjusted Pearson Chi-2 test for survey data.}\\
-%		\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure $\geqslant$ 140 mmHg or diastolic}\\ 
-%		\multicolumn{5}{l}{blood pressure $\geqslant$ 90 mmHg, or under}\\
-%		\multicolumn{5}{l}{treatment for hypertension.}\\
-%		\multicolumn{5}{l}{\textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake}\\
-%		\multicolumn{5}{l}{\textsuperscript{\S} DM was defined by A1C > 6.5\%.}\\
-%		\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity}\\ 
-%		\multicolumn{5}{l}{during the survey.}\\
-%	\end{tabular}
-%\end{table}
-
-\rowcolors{2}{white}{white}
+\section{Association between individual level latent classes and diabetes}

### 2018-08-03 paper/Chapters/Chapter4.tex
introduction example of diary added
results MLCA almost done

--- 2018-07-10 paper/Chapters/Chapter3.tex
@@
 
-\chapter{Results} % Main chapter title
+\chapter{Discussion and Conclusion} % Main chapter title
 
-\label{Chapter 3} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+\label{Chapter 4} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+
+\begin{itemize}
+	\item MLCA ignored the order of observation days.
+	\item We used the maximum probability rule and ignored that these are just probabilities.
+\end{itemize}
 

### 2018-08-03 paper/Tables/2by2Table1.Rmd
results MLCA almost done

--- 2018-07-28 paper/Tables/2by2Table1.Rmd
@@
 
+# Multilevel 2by2 table 1
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
@@
 
+# Day level only models
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
@@
 
+# LCGA models table 1
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
@@
 
+# Model fit criteria
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Mixed_50_paper.csv", header = T)
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Mixed_7slots.csv", header = T)
+dt <- dt[,-7]
 names(dt) <- c("Model", "1 class", "2 classes",  "3 classes", "4 classes", "5 classes")
@@
 ```
+
+# Day level solution 1
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/timeslots_cw3cb3_univariate.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c("Time slots of the day", "Responses of carbohydrate intake", "Frequency", "Precentages (%)", 
+               "Class 1 (30.8%)", "Class 2 (39.8%)", "Class 3 (29.5%)")
+
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "Day Level Latent Class Solution for Three-Class Model (No Individual level Model)", booktabs = T,linesep = "") %>%
+ kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+    add_header_above(c(" ", " ", " ", " ", "High carbohydrate day", "Lower carbohydrate day", "Regular day"))
+
+```
+
+# Day level solution characteristics
+
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Daylevel.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c(" ", "High carbohydrate day", "Low carbohydrate day", "Regular meals day", "P value[note]")
+
+dt[23, 1] <- c("Non-milk extrinsic sugar[note]")
+# dt[32, 1] <- c("Carbohydrate\npercent (%) [note]")
+# dt[35, 1] <- c("DM [note]")
+# dt[36, 1] <- c("Physical\nactivity (hours/day) [note]")
+
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "Means (sd), and counts  of the characteristics of different types of days according to carbohydrate intake.", booktabs = T,linesep = "") %>%
+    add_indent(c(3:6, 8:15)) %>% 
+ kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+  add_footnote(c("P values were obtained from chi-square test for categorical variables, and one-way ANOVA comparing the means in multiple groups for continuous variables;", 
+                       "Non-milk extrinsic sugar is defined as:"),  notation = "symbol")
+
+```
+
+# Social economic
+
+```{r tab1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Timeslots_CW3CB3results.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c("Variables", "Individual class 1 (n = 1730)", "Individual class = 2 (n = 1772)", "Individual class = 3 (n = 2653)", "P value [note]")
+
+# 
+# dt[28, 1] <- c("Hypertension (%) [note]")
+# dt[32, 1] <- c("Carbohydrate\npercent (%) [note]")
+# dt[35, 1] <- c("DM [note]")
+# dt[36, 1] <- c("Physical\nactivity (hours/day) [note]")
+dt[20, 1] <- c("Paid employment[note] (%)")
+dt[23, 1] <- c("Live with partner[note] (%)")
+
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "Means, row percentages, and 95 CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
+ kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+  add_indent(c(3:6, 9, 10, 12:19, 21, 22, 24, 25, 28, 29, 31, 32)) %>% 
+  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;"
+                       # " BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
+                       # "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
+                       # "Glucose and A1C levels are estimated in subgroups of people without diabetes."
+                       )) %>% 
+  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across >2 classes.
+For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
+                 "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
+                 "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
+                 # "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
+                 # "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
+                 # "DM was defined by A1C > 6.5%.", 
+                 # "Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey."
+                 ), 
+               notation = "symbol")
+```
+
+## Anthropometric measurements and biochemical analysis
+
+```{r tab2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Timeslots_CW3CB3table2_bmiDM.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c("Variables", "Individual class 1 (n = 1730)", "Individual class (n = 1772)", "Individual class 3 (n = 2653)", "P value[note]")
+
+# 
+dt[9, 1] <- c("Hypertension[note] (%)")
+dt[12, 1] <- c("Carbohydrate percent[note] (%)")
+
+dt[21, 1] <- c("Physical\nactivity (hours/day) [note]")
+dt[20, 1] <- c("DM [note]")
+# dt[20, 1] <- c("Paid employment[note] (%)")
+# dt[23, 1] <- c("Live with partner[note] (%)")
+
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "Means, percentages, and 95 CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
+ kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+  add_indent(c(4:6,8,10)) %>% 
+  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;",
+                        " BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
+                        "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
+                        "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
+  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across >2 classes.
+For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
+                 # "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
+                 # "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
+                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.",
+                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
+                 "DM was defined by A1C > 6.5%.",
+                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the survey."
+                 ), 
+               notation = "symbol")
+```

### 2018-08-03 paper/Tables/2by2Table1.tex
results MLCA almost done

--- 2018-08-01 paper/Tables/2by2Table1.tex
@@
 
+\section{Multilevel 2by2 table 1}\label{multilevel-2by2-table-1}
+
 \rowcolors{2}{gray!6}{white}
@@
 
+\section{Day level only models}\label{day-level-only-models}
+
 \rowcolors{2}{gray!6}{white}
@@
 \rowcolors{2}{white}{white}
+
+\section{LCGA models table 1}\label{lcga-models-table-1}
 
@@
 
+\section{Model fit criteria}\label{model-fit-criteria}
+
 \rowcolors{2}{gray!6}{white}
@@
 \rowcolors{2}{white}{white}
+
+\section{Day level solution 1}\label{day-level-solution-1}
 
@@
 
+\section{Day level solution
+characteristics}\label{day-level-solution-characteristics}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-6}Means (sd), and counts  of the characteristics of different types of days according to carbohydrate intake.}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{lllll}
+\hiderowcolors
+\toprule
+  & High carbohydrate day & Low carbohydrate day & Regular meals day & P value\textsuperscript{*}\\
+\midrule
+\showrowcolors
+Counts & 9667 (39.5) & 5002 (20.4\%) & 9814 (40.1\%) & \\
+Country (\%) &  &  &  & < 0.001\\
+\hspace{1em}England & 5627 (58.2) & 2972 (59.4) & 5291 (53.9) & \\
+\hspace{1em}NI & 1194 (12.4) & 527 (10.5) & 1400 (14.3) & \\
+\hspace{1em}Scotland & 1527 (15.8) & 813 (16.3) & 1774 (18.1) & \\
+\hspace{1em}Wales & 1318 (13.6) & 690 (13.8) & 1349 (13.7) & \\
+Day of Week (\%) &  &  &  & < 0.001\\
+\hspace{1em}Monday & 1303 (13.5) & 715 (14.3) & 1370 (14.0) & \\
+\hspace{1em}Tuesday & 1266 (13.1) & 674 (13.5) & 1290 (13.1) & \\
+\hspace{1em}Wednesday & 1225 (12.7) & 740 (14.8) & 1233 (12.6) & \\
+\hspace{1em}Thursday & 1272 (13.2) & 752 (15.0) & 1425 (14.5) & \\
+\hspace{1em}Friday & 1458 (15.1) & 797 (15.9) & 1479 (15.1) & \\
+\hspace{1em}Saturday & 1537 (15.9) & 703 (14.1) & 1495 (15.2) & \\
+\hspace{1em}Sunday & 1605 (16.6) & 621 (12.4) & 1522 (15.5) & \\
+\hspace{1em}Weekend, Yes (\%) & 3142 (32.5) & 1324 (26.5) & 3017 (30.7) & < 0.001\\
+Total energy (kJ) & 7539.98 (2875.87) & 7160.22 (2922.15) & 7439.68 (2978.91) & < 0.001\\
+Carbohydrate (g) & 222.79 (89.84) & 209.70 (86.17) & 206.59 (84.42) & < 0.001\\
+Protein (g) & 71.36 (29.79) & 69.55 (30.20) & 73.29 (32.94) & < 0.001\\
+Fat (g) & 65.44 (33.27) & 63.94 (33.76) & 67.24 (34.73) & < 0.001\\
+Alcohol (g) & 11.76 (27.31) & 8.85 (24.25) & 13.80 (33.00) & < 0.001\\
+Total sugars (g) & 98.63 (56.03) & 88.03 (50.50) & 86.39 (50.96) & < 0.001\\
+Starch (g) & 124.07 (55.84) & 121.59 (56.13) & 120.11 (54.62) & < 0.001\\
+Non-milk extrinsic sugar\textsuperscript{\dag} & 59.45 (49.31) & 50.07 (43.41) & 50.41 (44.84) & < 0.001\\
+Fruit (g) & 107.40 (137.97) & 103.15 (129.08) & 92.76 (126.02) & < 0.001\\
+Yellow Red Green Vegetables (g) & 26.52 (46.44) & 26.84 (47.99) & 26.16 (45.99) & 0.681\\
+\bottomrule
+\multicolumn{5}{l}{\textsuperscript{*} P values were obtained from chi-square test for categorical variables, and one-way ANOVA comparing the}\\
+\multicolumn{5}{l}{means in multiple groups for continuous variables;}\\
+\multicolumn{5}{l}{\textsuperscript{\dag} Non-milk extrinsic sugar is defined as:}\\
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
+\section{Social economic}\label{social-economic}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:tab1}Means, row percentages, and 95 CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{lllll}
+\hiderowcolors
+\toprule
+Variables & Individual class 1 (n = 1730) & Individual class = 2 (n = 1772) & Individual class = 3 (n = 2653) & P value \textsuperscript{*}\\
+\midrule
+\showrowcolors
+Total (\%) & 28.4 (26.9, 29.9) & 28.7 (27.1, 30.3) & 43.0 (41.3, 44.7) & \\
+Countries (\%) &  &  &  & 0.007\\
+\hspace{1em}England & 84.5 (81.7, 86.9) & 82.0 (79.3, 84.5) & 84.7 (82.3, 86.8) & \\
+\hspace{1em}Northern Ireland & 2.1 (1.6, 2.8) & 4.2 (3.2, 5.6) & 2.2 (1.7, 3.0) & \\
+\hspace{1em}Scotland & 9.1 (7.0, 11.8) & 8.6 (6.7, 11.1) & 8.0 (6.3, 10.2) & \\
+\hspace{1em}Wales & 4.3 (3.3, 5.6) & 5.1 (4.0, 6.4) & 5.1 (4.0, 6.4) & \\
+Age (years) & 51.0 (49.9, 52.1) & 40.3 (39.1, 41.6) & 51.7 (50.7, 52.7) & < 0.001\\
+Sex (\%) &  &  &  & 0.119\\
+\hspace{1em}Men & 50.0 (46.9, 53.1) & 50.2 (47.0, 53.5) & 46.6 (44.0, 49.1) & \\
+\hspace{1em}Women & 50.0 (46.9, 53.1) & 49.8 (46.5, 53.0) & 53.4 (50.9, 56.0) & \\
+Survey years (\% in rows) &  &  &  & 0.015\\
+\hspace{1em}1 & 32.5 (28.4, 36.9) & 26.3 (21.9, 31.2) & 41.2 (36.6, 46.0) & \\
+\hspace{1em}2 & 26.8 (22.6, 31.3) & 22.6 (18.6, 27.3) & 50.6 (45.8, 55.4) & \\
+\hspace{1em}3 & 22.6 (18.8, 26.9) & 33.7 (28.6, 39.2) & 43.6 (38.7, 48.7) & \\
+\hspace{1em}4 & 27.9 (24.1, 32.2) & 27.6 (23.8, 31.8) & 44.4 (40.2, 48.7) & \\
+\hspace{1em}5 & 27.9 (24.2, 32.0) & 28.7 (24.4, 33.5) & 43.3 (38.2, 48.6) & \\
+\hspace{1em}6 & 28.0 (24.0, 32.4) & 31.5 (26.9, 36.6) & 40.5 (35.8, 45.3) & \\
+\hspace{1em}7 & 29.1 (25.2, 33.4) & 29.0 (24.5, 34.0) & 41.8 (37.1, 46.7) & \\
+\hspace{1em}8 & 31.1 (27.3, 35.3) & 30.5 (25.9, 35.5) & 38.4 (34.1, 42.8) & \\
+Paid employment\textsuperscript{\dag} (\%) &  &  &  & 0.907\\
+\hspace{1em}Yes & 40.3 (37.0, 43.6) & 40.8 (37.1, 44.5) & 39.8 (37.1, 42.6) & \\
+\hspace{1em}No & 59.7 (56.4, 63.0) & 59.2 (55.5, 62.9) & 60.2 (57.4, 62.9) & \\
+Live with partner\textsuperscript{\ddag} (\%) &  &  &  & < 0.001\\
+\hspace{1em}Yes & 56.9 (53.6, 60.1) & 38.4 (35.2, 41.8) & 61.3 (58.7, 63.7) & \\
+\hspace{1em}No & 43.1 (39.9, 46.4) & 61.6 (58.2, 64.8)) & 38.7 (36.3, 41,3) & \\
+Household Income, GBP/year & 36558.53 (34800.21, 38316.84) & 27180.80 (25597.95, 28763.65) & 32171.58 (31024.96, 33318.2) & < 0.001\\
+Ethnicity (\%) &  &  &  & \\
+\hspace{1em}White & 94.2 (92.4, 95.6) & 79.5 (76.4, 82.3) & 91.9 (90.1, 93.4) & < 0.001\\
+\hspace{1em}Non-White & 5.8 (4.4, 7.6) & 20.5 (17.7, 23.6) & 8.1 (6.6, 9.9) & \\
+Education (\%) &  &  &  & \\
+\hspace{1em}Degree or higher & 29.0 (26.1, 32.1) & 23.3 (20.5, 26.3) & 26.2 (24.1, 28.5) & 0.019\\
+\hspace{1em}Lower than degree & 71.0 (67.9, 73.9) & 76.7 (73.7, 79.5) & 73.8 (71.5, 75.9) & \\
+\bottomrule
+\multicolumn{5}{l}{\textit{Note: }}\\
+\multicolumn{5}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
+\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account for multiple}\\
+\multicolumn{5}{l}{testing across >2 classes. For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for}\\
+\multicolumn{5}{l}{survey data.}\\
+\multicolumn{5}{l}{\textsuperscript{\dag} Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey.}\\
+\multicolumn{5}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership.}\\
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
+\subsection{Anthropometric measurements and biochemical
+analysis}\label{anthropometric-measurements-and-biochemical-analysis}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:tab2}Means, percentages, and 95 CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{lllll}
+\hiderowcolors
+\toprule
+Variables & Individual class 1 (n = 1730) & Individual class (n = 1772) & Individual class 3 (n = 2653) & P value\textsuperscript{*}\\
+\midrule
+\showrowcolors
+BMI (kg/m2) & 27.8 (27.4, 28.2) & 27.2 (26.7, 27.7) & 27.3 (26.9, 27.6) & 0.006\\
+WC (cm) & 94.6 (93.5, 95.6) & 92.3 (91.0, 93.5) & 92.2 (91.4, 93.1) & 0.001\\
+Smoking status (\%) &  &  &  & \\
+\hspace{1em}Current & 20.4 (18.0, 23.0) & 27.8 (25.0, 30.9) & 17.1 (15.4, 19.0) & < 0.001\\
+\hspace{1em}Ex-smoker & 29.3 (26.5, 32.2) & 16.8 (14.6, 19.2) & 26.1 (24.9, 28.3) & \\
+\hspace{1em}Never & 50.3 (47.2, 32.2) & 55.4 (52.2, 58.6) & 56.8 (54.3, 59.3) & \\
+Current drinking status (\%) &  &  &  & \\
+\hspace{1em}Yes & 11.8 (10.0, 13.8) & 24.0 (21.2, 27.1) & 20.6 (18.7, 22.8) & < 0.001\\
+Hypertension\textsuperscript{\dag} (\%) &  &  &  & \\
+\hspace{1em}Yes & 33.4 (29.9, 37.1) & 21.1 (17.7, 24.9) & 31.2 (28.3, 34.2) & < 0.001\\
+Total energy intake (kJ) & 7985.8 (7823.3, 8146.295) & 7341.8 (7825.3, 8146.3) & 7677 (7555.8, 7799,8) & < 0.001\\
+Carbohydrate percent\textsuperscript{\ddag} (\%) & 203.8 (199.8, 207.8) & 218.3 (212.9, 223.7) & 233.4 (229.6, 237.2) & < 0.001\\
+Carbohydrate percent (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
+Protein intake (g) & 79.9 (77.9, 81.8) & 69.3 (67.6, 71.0) & 73.7 (72.5, 74.8) & < 0.001\\
+Protein percent (\%) & 17.2 (16.9, 17.5) & 16.3 (16.0, 16.6) & 16.5 (16.3, 16.6) & < 0.001\\
+Fat intake (g) & 74.7 (73.1, 76.4) & 63.8 (62.1, 65.5) & 65.7 (64.4, 67.0) & < 0.001\\
+Fat percent (\%) & 35.4 (34.9, 35.8) & 32.5 (32.1, 32.9) & 32.0 (31.7, 32.3) & < 0.001\\
+Glucose (mmol/l) & 5.20 (5.15, 5.26) & 5.09 (5.02, 5.17) & 5.13 (5.09, 5.12) & 0.051\\
+A1C (\%) & 5.49 (5.45, 5.52) & 5.44 (5.40, 5.48) & 5.52 (5.49, 5.55) & 0.012\\
+DM \textsuperscript{\S} & 6.9 (5.0, 9.3) & 3.5 (2.3, 5.3) & 4.1 (2.9, 5.6) & 0.011\\
+Physical
+activity (hours/day) \textsuperscript{\P} & 1.63 (1.43, 1.83) & 1.32 (1.15, 1.49) & 1.65 (1.49, 1.81) & 0.016\\
+\bottomrule
+\multicolumn{5}{l}{\textit{Note: }}\\
+\multicolumn{5}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
+\multicolumn{5}{l}{ BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.}\\
+\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.}\\
+\multicolumn{5}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
+\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account}\\
+\multicolumn{5}{l}{for multiple testing across >2 classes. For categorical variables, differences between latent classes were assessed using the adjusted}\\
+\multicolumn{5}{l}{Pearson Chi-2 test for survey data.}\\
+\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for}\\
+\multicolumn{5}{l}{hypertension.}\\
+\multicolumn{5}{l}{\textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake}\\
+\multicolumn{5}{l}{\textsuperscript{\S} DM was defined by A1C > 6.5\%.}\\
+\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and}\\
+\multicolumn{5}{l}{recreational activities during the survey.}\\
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
 \end{document}

### 2018-08-03 Rcode/daylevelconsumption_feature.R

@@ -66,8 +66,8 @@ names(CW3CB3) <- c("Breakfast", "Morning.snack", "Lunch",
 dta_NDNS <- read_csv("/home/wangcc-me/Documents/LSHTMproject/Rcode/dta_NDNS.csv") # extract the day of week data
 
 CW3idday <- CW3CB3 %>% 
-  select(ID.x, ID_DAY, CW, CB, MLCJOINT, AGE, SEX) %>% 
-  rename(ID = ID.x)
+  select(ID, ID_DAY, CW, CB, MLCJOINT, AGE, SEX)
+  
 
 CW3idday$DayNo <- ave(CW3idday$ID_DAY, CW3idday$ID, FUN = seq_along) # adding the day no 
 
@@ -105,7 +105,8 @@ CW3idday <- CW3idday %>%
 
 write.csv(CW3idday, file = "/home/wangcc-me/Documents/LSHTMproject/Tablecsv/CW3idday.csv")
 
-CW3idday$Weekend <- ifelse((CW3idday$DayofWeek == "Sunday" | CW3idday$DayofWeek == "Saturday"), TRUE, FALSE)
+CW3idday$Weekend <- ifelse((CW3idday$DayofWeek == "Sunday" | 
+                              CW3idday$DayofWeek == "Saturday"), TRUE, FALSE)
 # association of day level nutrients and CW3 ------------------------------
 
 # 

### 2018-08-03 paper/Figures/Figureforpaper.R

@@ -380,7 +380,7 @@ cls1 <- ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Time, group = Carbo,
   ) + 
   scale_linetype_manual(values=c("dotdash", "dashed", "solid")) + 
   # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  labs(title = "Class 1 days - High carbohydrate days (39.5%)", x = "", y = "Probability",
+  labs(title = "Class 1 days - High carbohydrate day (39.5%)", x = "", y = "Probability",
        color = "Carbohydrate\nintake") + 
   # scale_shape_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
   ylim(c(0,1)) #+ 
@@ -423,7 +423,7 @@ cls2 <- ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Time, group = Carbo,
   ) + 
   scale_linetype_manual(values=c("dotdash", "dashed", "solid")) + 
   # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  labs(title = "Class 2 days - Low carbohydrate days (20.4%)", x = "", y = "Probability",
+  labs(title = "Class 2 days - Low carbohydrate day (20.4%)", x = "", y = "Probability",
        color = "Carbohydrate\nintake") + 
   # scale_shape_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
   ylim(c(0,1)) #+ 
@@ -467,11 +467,11 @@ cls3 <- ggplot(pp_long[pp_long$CW == 3, ], aes(y = Prob, x=Time, group = Carbo,
         legend.direction = "horizontal"
   ) + 
   scale_shape_manual(values=c(21,23,24), 
-                     labels =  c("Not eating\nanyfood", "Carbohydrate < 50%", "Carbohydrate >= 50%")) + 
+                     labels =  c("Not eating\nany food", "Carbohydrate < 50%", "Carbohydrate >= 50%")) + 
       scale_linetype_manual(values=c("dotdash", "dashed", "solid"),
-                            labels =  c("Not eating\nanyfood", "Carbohydrate < 50%", "Carbohydrate >= 50%")) + 
+                            labels =  c("Not eating\nany food", "Carbohydrate < 50%", "Carbohydrate >= 50%")) + 
   # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
[…]

### 2018-08-03 paper/Chapters/Chapter2.tex
tables figs of MLCA done, classes and bmi, dm, hyt estimates needed

@@
 In the step of performing multilevel LCA, where LMR-LRT is available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day level and individual level.
-MLCA models were fitted in Mplus 7.4 \parencite{muthen2005mplus}, the Mplus codes are shown in \textbf{Appendix \ref{AppendixB}}.
+MLCA models were fitted in Mplus 7.4 \parencite{muthen2005mplus}, the Mplus codes and outputs are shown in \textbf{Appendix \ref{AppendixB}}.
 \vspace{-0.3cm}
@@
 
-\section{Day level latent classes and their characteristics}\vspace{-0.3cm}
+\section{Characteristics of dietary diary and population}\vspace{-0.3cm}
 
@@
 A contingency table giving the frequency of responses across the 7 time slots of the survey days was produced.
+Descriptive statistics for the dietary day level recordings according to the latent classes were presented.
+
+\section{Association between individual level latent classes and the prevalence of hypertension, obesity, and diabetes}

### 2018-08-03 paper/Chapters/Chapter3.tex
tables figs of MLCA done, classes and bmi, dm, hyt estimates needed

@@
 This class represents nearly 65\% of the individuals.
+However, we believe these individual classes are not very distinguishable to each other.
 
@@
 
-With three individual level latent classes \textbf{(Figure \ref{fig:level2})}, a low-carbohydrate eaters class, moderate-carbohydrate eaters class, and high-carbohydrate eaters class emerges.
+With three individual level latent classes \textbf{(Figure \ref{fig:level2})}, a low-carbohydrate eaters class, a moderate-carbohydrate eaters class, and a high-carbohydrate eaters class emerges.
 43.1\% participants were identified as high-carbohydrate eaters, in these individuals, about 50\% of the days (2 out of 4 days) of their dietary diary were classified as having high carbohydrate days.
 Nearly 1 out of 4 days of their dietary diary were either "regular meals day" or "low carbohydrate day".
+28.1\% participants fell into the low carbohydrate eaters class in the left hand side of \textbf{Figure \ref{fig:level2}}, their recordings of food intake showed that in more than 60\% of their days, they were having "regular meals" which was characterised as with highest amount of fat and alcohol consumptions as already described in \textbf{Table \ref{tab:day-level-features}}.
 
@@
 
+The social-economic characteristics of the
+
 \rowcolors{2}{gray!6}{white}
@@
 \caption{\label{tab:Level2tab1}Weighted means, percentages, and
-95\% CIs of the social, economical characteristics by latent class memberships in the UK
+95\% CIs of the social-economic characteristics by latent class memberships in the UK
 adults. (NDNS RP 2008/09-2015/16, sample size = 6155)} \centering
@@
 	\toprule
-	\textbf{Variables} & \textbf{\Centerstack{Individual class 1\\(n = 1730)}} & \textbf{\Centerstack{Individual class 2\\(n = 1772)}} & \textbf{\Centerstack{Individual class 3\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
+	\textbf{Variables} & \textbf{\Centerstack{Low carbo-\\hydrate eaters\\(n = 1730)}} & \textbf{\Centerstack{Moderate carbo-\\hydrate eaters\\(n = 1772)}} & \textbf{\Centerstack{High carbo\\hydrate eaters\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
 	\midrule
@@
 	\hspace{1em}No & 43.1 (39.9, 46.4) & 61.6 (58.2, 64.8)) & 38.7 (36.3, 41,3) & \\
-	Household Income, \textsterling/year & \Centerstack{36558.53\\(34800.21, 38316.84)} & \Centerstack{27180.80\\(25597.95, 28763.65)} & \Centerstack{32171.58\\(31024.96, 33318.2)} & < 0.001\\
+	Household Income, \textsterling/year & \Centerstack{36558.5\\(34800.2, 38316.8)} & \Centerstack{27180.8\\(25597.9, 28763.7)} & \Centerstack{32171.6\\(31024.9, 33318.2)} & < 0.001\\
 	Ethnicity (\%) &  &  &  & \\
@@
 	\multicolumn{5}{l}{\textit{Note: }}\\
-	\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme.}\\
+	\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling}\\
+	\multicolumn{5}{l}{programme} \\
 	\multicolumn{5}{l}{Variables were weighted by individual weights.}\\
@@
 	\multicolumn{5}{l}{ differences between latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.} \\
-	\multicolumn{5}{l}{\textsuperscript{\dag} Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey.}\\
-	\multicolumn{5}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil} \\
-	\multicolumn{5}{l}{partnership.}\\
+	\multicolumn{5}{l}{\textsuperscript{\dag} Paid employment was defined as being in paid employment during the last 4 weeks prior to }\\
+	\multicolumn{5}{l}{the survey.}\\
+	\multicolumn{5}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally  } \\
+	\multicolumn{5}{l}{recognised civil partnership.}\\
 \end{tabular}
@@
 		\toprule
-		\textbf{Variables} & \textbf{\Centerstack{Individual class 1\\(n = 1730)}} & \textbf{\Centerstack{Individual class 2\\(n = 1772)}} & \textbf{\Centerstack{Individual class 3\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
+	\textbf{Variables} & \textbf{\Centerstack{Low carbo-\\hydrate eaters\\(n = 1730)}} & \textbf{\Centerstack{Moderate carbo-\\hydrate eaters\\(n = 1772)}} & \textbf{\Centerstack{High carbo\\hydrate eaters\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
 		\midrule
@@
 		\hspace{1em}Yes & 33.4 (29.9, 37.1) & 21.1 (17.7, 24.9) & 31.2 (28.3, 34.2) & < 0.001\\
-		Total energy intake (kJ) & \Centerstack{7985.8\\(7823.3, 8146.295)} & \Centerstack{7341.8\\(7825.3, 8146.3)} & \Centerstack{7677.0\\(7555.8, 7799,8)} & < 0.001\\
-		Carbohydrate percent\textsuperscript{\ddag} (\%) & 203.8 (199.8, 207.8) & 218.3 (212.9, 223.7) & 233.4 (229.6, 237.2) & < 0.001\\
-		Carbohydrate percent (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
+		Total energy intake (kJ) & \Centerstack{7985.8\\(7823.3, 8146.3)} & \Centerstack{7341.8\\(7825.3, 8146.3)} & \Centerstack{7677.0\\(7555.8, 7799.8)} & < 0.001\\
+		Carbohydrate intake (g) & \Centerstack{203.8\\(199.8, 207.8)} & \Centerstack{218.3\\(212.9, 223.7)} & \Centerstack{233.4\\(229.6, 237.2)} & < 0.001\\
+		Carbohydrate percent\textsuperscript{\ddag} (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
 		Protein intake (g) & 79.9 (77.9, 81.8) & 69.3 (67.6, 71.0) & 73.7 (72.5, 74.8) & < 0.001\\
@@
 		\multicolumn{5}{l}{\textit{Note: }}\\
-		\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
-		\multicolumn{5}{l}{ BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.}\\
-		\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) were weighted by blood sample weights, the others were}\\ 
-		\multicolumn{5}{l}{weighted by nurse visiting weights.}\\
+		\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling }\\
+		\multicolumn{5}{l}{programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, }\\
+		\multicolumn{5}{l}{diabetes mellitus.} \\
+		\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) were weighted by blood sample weights,}\\ 
+		\multicolumn{5}{l}{ the other variables were weighted by nurse visiting weights.}\\
 		\multicolumn{5}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
-		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes}\\ 
+		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes}\\ 
 		\multicolumn{5}{l}{with Bonferroni correction to accountfor multiple testing across $>$ 2 classes. For categorical variables, }\\

### 2018-08-03 paper/Tables/2by2Table1.tex
tables figs of MLCA done, classes and bmi, dm, hyt estimates needed

@@
 Total energy intake (kJ) & 7985.8 (7823.3, 8146.295) & 7341.8 (7825.3, 8146.3) & 7677 (7555.8, 7799,8) & < 0.001\\
-Carbohydrate percent\textsuperscript{\ddag} (\%) & 203.8 (199.8, 207.8) & 218.3 (212.9, 223.7) & 233.4 (229.6, 237.2) & < 0.001\\
-Carbohydrate percent (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
+Carbohydrate intake (g) & 203.8 (199.8, 207.8) & 218.3 (212.9, 223.7) & 233.4 (229.6, 237.2) & < 0.001\\
+Carbohydrate percent\textsuperscript{\ddag} (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
 Protein intake (g) & 79.9 (77.9, 81.8) & 69.3 (67.6, 71.0) & 73.7 (72.5, 74.8) & < 0.001\\

### 2018-08-03 paper/Figures/Figureforpaper.R

@@ -550,8 +550,9 @@ chart.data <- ddply(chart.data, .(CB),
 chart.data$CW_new <- factor(chart.data$CW_new, levels = c("3", "2", "1"), 
                             labels = c("Regular\nmeals day", "Low carbo-\nhydrate day", "High carbo-\nhydrate day"))
 chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"), 
-                        labels = c("Individual\nclass 1\n(28.1%)",  
-                                   "Individual\nclass 2\n(28.8%)", "Individual\nclass 3\n(43.1%)"))
+                        labels = c("Low carbo-\nhydrate eaters\n(28.1%)",  
+                                   "Moderate carbo-\nhydrate eaters\n(28.8%)", 
+                                   "High carbo-\nhydrate eaters\n(43.1%)"))
 
 
 

### 2018-08-05 paper/Chapters/Chapter2.tex
method updated regression models started writing some variables changed to log-transformed

@@
 %-----------------------------------
-\subsection{Survey Selection Method}\vspace{-0.3cm}
+\subsection{Survey selection method}\vspace{-0.3cm}
 
@@
 
-The response rates for completion of the food diary (three or four days) were 56\%, 53\%, 53\%, for years 1 to 4, 5 to 6, and 7 to 8, respectively.
-A total of 6,155 adults aged 19 years and over were kept in our analysis.
+The response rates for completion of the dietary diary (three or four days) were 56\%, 53\%, 53\%, for years 1 to 4, 5 to 6, and 7 to 8, respectively.
+A total of 6,155 adults aged 19 years and over were kept in our analyses.
 \vspace{-0.6cm}
@@
 
-Another set of weights were generated to correct for differential non-response (either due to refusal or inability) to giving a blood sample.
-Response to the blood sample in adults were 51\%, 57\%, and 50\% for years 1 to 4, 5 to 6, and 7 to 8, respectively.
-In creating the blood sample weight, a logistic regression was used by the NDNS RP study team to model the relationship between response to giving blood sample and a set of predictor variables (socio-demographic, participant and catering/household unit characteristics).
-The model generated a predicted probability for each participant, which is the probability would provide blood sample, given the characteristics of the individual and the household unit.
-Participants with characteristics associated with non-response were under-represented in the blood sample and therefore receive a low predicted probability.
-The inverse of these predicted probablities were used as a set of non-response weights so that participants with a low predicted probability got a larger weight, increasing their representation in the sample.
-Then the blood sample weights were re-scaled so that the sum of the weights equalled the number of participants who had a nurse visit.
-The final blood weights should therefore make the blood sample participants representative of all eligible persons in the population.
+Another two sets of weights were generated to correct for differential non-response (either due to refusal or inability) to 1) nurse visit, and 2) giving a blood sample.
+Response rates to the nurse visit among those completed a dietary diary was approximately 75\%, to blood sample in adults were 51\%, 57\%, and 50\% for years 1 to 4, 5 to 6, and 7 to 8, respectively.
+In creating the nurse/blood sample weight, a logistic regression model was used by the NDNS RP study team to model the relationship between response to nurse visit/giving blood sample and a set of predictor variables (socio-demographic, participant and catering/household unit characteristics).
+The model generated a predicted probability for each participant, which is the probability would agree to a nurse visit/provide blood sample, given the characteristics of the individual and the household unit.
+Participants with characteristics associated with non-response were under-represented in the sample and therefore receive a low predicted probability.
+The inverse of these predicted probabilities were used as a set of non-response weights so that participants with a low predicted probability got a larger weight, increasing their representation in the sample.
+Then the nurse/blood sample weights were re-scaled so that the sum of the weights equalled the number of participants who had a nurse visit/who provided a blood sample.
+The final nurse/blood weights should therefore make the sample participants representative of all eligible persons in the population.
 
-Further details of the weighting system developed by the NDNS RP are described in the Appendix B of the reports published by Public Health England (PHE) \parencite{bates2014national,roberts2018national}.
+Further details of the weighting system developed by the NDNS RP are described in the Appendix B of the reports published by Public Health England (PHE) \parencite{bates2014national,roberts2018national,NDNSofficial}.\vspace{-0.6cm}
+
+\subsection{Socio-demographic status, lifestyle, physical activity, anthropometric measurements and biochemical analysis}\vspace{-0.3cm}
+
+Computer assisted personal interviews were conducted for the selected individuals by trained interviewers to collect background information on smoking habits (current, past, never smokers), ethnicity (white, non-white), education level, living with a partner or not and other socio-demographic related variables.
+Participants also had their height, weight, blood pressure, waist circumferences (WC) measured by the nurse.
+
+Specifically, blood pressure was measured in a sitting position using an automated, validated machine, the Omron HEM907, after a five minute rest.
+The means of second and third readings, taken at one minute intervals, were used in the current report.
+Hypertension was defined as a systolic blood pressure of 140 mmHg or above, and/or diastolic blood pressure of 90 mmHg or above, and/or taking any medication specifically to reduce blood pressure.
+
+A self-completion questionnaire - the Recent Physical Activity Questionnaire  \parencite{besson2009estimating} (RPAQ, developed by the MRC Epidemiology Unit Cambridge) was used to estimate physical activity from year 2 of the survey.
+The RPAQ was designed to assess usual physical activity in the last month in four domains: home, work, commuting to work, and leisure activities.
+Detailed descriptions of the assessment of adult physical activity in the NDNS RP and the processing of data are available in Appendices G and V of the published reports \parencite{bates2014national,roberts2018national,NDNSofficial}.
+
+Blood samples were stored at 4 $^\circ$C, and sent directly by post to the Department of Haematology and Department of Clinical Biochemistry and Immunology, Addenbrooke's Hospital, Cambridge within tow hours of their collection.
+Serum samples were obtained by centrifugation of the coagulated blood sample.
+Serum total, High Density Lipoprotein (HDL) and Low Density Lipoprotein (LDL) cholesterol, triglycerides, blood glucose, haemoglobin A1C were measured.
+A1C value of 6.5\% was used as the cut off point for diagnosing diabetes.
+
+Body mass index (BMI) was calculated as weight in kilograms and weight in kilograms divided by height in square meters.
+BMI was then categorised into less than 25 kg/m\textsuperscript{2} (normal weight), 25 to 30 kg/m\textsuperscript{2} (overweight), and higher or equal to 30 kg/m\textsuperscript{2} (obese).
+
+\subsection{Ethics approval}\vspace{-0.3cm}
+
+Ethics approval for the survey was obtained form the Oxfordshire A Research Ethics Committee.
+The letters of approval for the original submission and subsequent substantial amendments, together with approved documents, were sent to all Local Research Ethics Committees covering areas where fieldwork was being conducted.
+Research governance approval was sought for all participating NHS laboratories and obtained where required by the Research and Development Committee for each laboratory.
+Ethics approval for the current project was obtained from the MSc Research Ethics Committee of London School of Hygiene \& Tropical Medicine (LSHTM MSc Ethics Ref: 15624).
 
@@
 %-----------------------------------
-\section{Latent Class Analysis (LCA)}\vspace{-0.3cm}
+\section[Statistical methods]{Statistical methods}
+
+\subsection{Latent Class Analysis (LCA)}\vspace{-0.3cm}
 
@@
 
-\section{Multilevel Latent Class Analysis (MLCA)}\vspace{-0.3cm}
+\subsection{Multilevel Latent Class Analysis (MLCA)}\vspace{-0.3cm}
 
@@
 
-\subsection{Parametric approach}\vspace{-0.3cm}
+\subsubsection{Parametric approach}\vspace{-0.3cm}
 
@@
 
-\section{Strategy of conducting MLCA in the current analysis}\vspace{-0.3cm}
+\subsection{Strategy of conducting MLCA in the current analysis}\vspace{-0.3cm}
 
@@
 
-\section{Characteristics of dietary diary and population}\vspace{-0.3cm}
+\subsection{Characteristics of day level latent classes and individual level latent classes}\vspace{-0.3cm}
 
-Day level latent classes identified by MLCA steps were tabulated according to whether the diary was recorded during weekdays or not.
+Day level latent classes identified by the first step of MLCA were tabulated according to day of week and also whether the diary was recorded during weekdays or not.
 A contingency table giving the frequency of responses across the 7 time slots of the survey days was produced.
-Descriptive statistics for the dietary day level recordings according to the latent classes were presented.
+Descriptive statistics for the dietary day level recordings according to the latent class memberships were presented.
+Pearson $\chi^2$ test was used ot compare the distribution of categorical variables.
+One-way Analysis of Variance (ANOVA) was used to compare the means across the multiple groups for continuous variables.
 
-\section{Association between individual level latent classes and the prevalence of hypertension, obesity, and diabetes}
+Person level point estimates and 95\% confidence intervals (CIs) were determined by applying individual, nurse visiting, and blood sample weights accordingly which accounted for the probability of participant selection and the clustered survey design.
+Descriptive statistics for sample characteristics are presented as weighted means (95\% CI) or weighted percentages (95\%CI).
+After examining the distribution of the data, the following variables were log-transformed to improve normality: blood glucose, A1C, TC, LDL, HDL, TG, and average physical activity duration per day.
+Weighted geometric means (95\% CI) were used for all log-transformed variables.
+For continuous variables, the \textit{F} test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across $>$ 2 classes.
+For categorical variables, differences between latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.\vspace{-0.5cm}
+
+\subsection{Association between individual level latent classes and the prevalence of hypertension, obesity, and diabetes}\vspace{-0.3cm}
+
+Multiple linear regression model (for WC), multinomial logistic regression model (for BMI categories), logistic regression models (for hypertension, and diabetes) were used to test for associations between individual level carbohydrate eating latent classes and WC, obesity, hypertension, and diabetes, separately.

### 2018-08-05 paper/Chapters/Chapter3.tex
method updated regression models started writing some variables changed to log-transformed

@@
 
-\section{Model selection, and interpretation}\vspace{-0.4cm}
+\subsection{Model selection, and interpretation}\vspace{-0.4cm}
 
@@
 		\bottomrule
-		\multicolumn{6}{l}{\textit{Note: }}\\
-		\multicolumn{6}{l}{\textbf{Abbreviation}: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index;}\\ 
-		\multicolumn{6}{l}{Lo-Mendel-Rubin LRT, likelihood ratio test comparing $q$ classes models with $q-1$ classes models.}\\
+		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
+		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviation}: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index;}}\\ 
+		\multicolumn{6}{l}{{\scriptsize Lo-Mendel-Rubin LRT, likelihood ratio test comparing $q$ classes models with $q-1$ classes models.}}\\
 	\end{tabular}
@@
 \rowcolors{2}{white}{white}
+\vspace{-0.5cm}
 
@@
 		\bottomrule
-		\multicolumn{7}{l}{\textit{Note: }}\\
-		\multicolumn{7}{l}{\textsuperscript{*} Carbohydrate $<$ 50\% indicates that within the time slot, carbohydrate contributed less }\\
-		\multicolumn{7}{l}{than 50\% total energy intake.}\\ 
-		\multicolumn{7}{l}{\textsuperscript{\dag} Carbohydrate $\geqslant$ 50\% indicates that within the time slot, carbohydrate contributed higher }\\
-		\multicolumn{7}{l}{or equal to 50\% total energy intake.}\\ 
+		\multicolumn{7}{l}{{\scriptsize \textit{Note: }}}\\
+		\multicolumn{7}{l}{{\scriptsize \textsuperscript{*} Carbohydrate $<$ 50\% indicates that within the time slot, carbohydrate contributed $<$ 50\% total energy intake.}}\\
+		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\dag} Carbohydrate $\geqslant$ 50\% indicates that within the time slot, carbohydrate contributed $\geqslant$ 50\% total energy intake.}}\\
+		\multicolumn{7}{l}{}\\ 
 	\end{tabular}
@@
 		\bottomrule
-		\multicolumn{5}{l}{\textit{Note: }}\\
-		\multicolumn{5}{l}{\textsuperscript{*} \textit{P} values were obtained from Pearson $\chi^2$ test for categorical variables, and one-way ANOVA }\\
-		\multicolumn{5}{l}{comparing the means in multiple groups for continuous variables;}\\
-		\multicolumn{5}{l}{\textsuperscript{\dag} Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey,}\\ 
-		\multicolumn{5}{l}{ glucose, fructose and glucose syrups, sugars added to food and sugars in fruit juices.}\\
+		\multicolumn{5}{l}{{\scriptsize \textit{Note: }}}\\
+		\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from Pearson $\chi^2$ test for categorical variables, and one-way ANOVA comparing the means}}\\
+		\multicolumn{5}{l}{{\scriptsize  in multiple groups for continuous variables;}}\\
+		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\dag} Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey, glucose, fructose}}\\ 
+		\multicolumn{5}{l}{{\scriptsize and sglucose syrups, sugars added to food and sugars in fruit juices.}}\\
 	\end{tabular}
@@
 Moreover, in high carbohydrate days, participants turned to also consume the highest amount of fruit (107.40 g).
-There is no evidence of any difference for the consumption of yellow, red, or green vegetables across the three types of days (\textit{p} = 0.681).
+There was no evidence of any difference for the consumption of yellow, red, or green vegetables across the three types of days (\textit{p} = 0.681).
 
@@
 In the random effect models we utilized the non-parametric approach, in which we added a level 2 (individual level) latent classes based on the random means from the level 1 (day level) latent class solution.
-The results of the individual level LCA solution for 3 classes are presented in \textbf{Figure \ref{fig:CB2level2}}, and \textbf{\ref{fig:level2}}.
+The results of the individual level LCA solution for 2 and 3 classes are presented in \textbf{Figure \ref{fig:CB2level2}}, and \textbf{\ref{fig:level2}}.
 
@@
 
-The social-economic characteristics of the
+The social-demographic characteristics of the UK adults according to their individual level latent class membership are shown in \textbf{Table \ref{tab:Level2tab1}}.
+Moderate carbohydrate eaters were relatively younger (\textit{p} < 0.001), and slightly less from England (\textit{p} = 0.007).
+Gender distribution across the three types of carbohydrate eaters were fairly even (\textit{p} = 0.119).
+Distribution of the carbohydrate eaters types was changing with the year of survey.
+Low carbohydrate eaters represented 32.5\% of the population in the first year of survey, but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year.
+Proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year of the survey, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015).
+There was no evidence of
 
@@
 \caption{\label{tab:Level2tab1}Weighted means, percentages, and
-95\% CIs of the social-economic characteristics by latent class memberships in the UK
+95\% CIs of the social-demographic characteristics by latent class memberships in the UK
 adults. (NDNS RP 2008/09-2015/16, sample size = 6155)} \centering
@@
 	\toprule
-	\textbf{Variables} & \textbf{\Centerstack{Low carbo-\\hydrate eaters\\(n = 1730)}} & \textbf{\Centerstack{Moderate carbo-\\hydrate eaters\\(n = 1772)}} & \textbf{\Centerstack{High carbo\\hydrate eaters\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
+	\textbf{Variables} & \textbf{\Centerstack{Low carbo-\\hydrate eaters\\(n = 1730)}} & \textbf{\Centerstack{Moderate carbo-\\hydrate eaters\\(n = 1772)}} & \textbf{\Centerstack{High carbo-\\hydrate eaters\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
 	\midrule
@@
 	\bottomrule
-	\multicolumn{5}{l}{\textit{Note: }}\\
-	\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling}\\
-	\multicolumn{5}{l}{programme} \\
-	\multicolumn{5}{l}{Variables were weighted by individual weights.}\\
-	\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes with}\\ 
-	\multicolumn{5}{l}{Bonferroni correction to account for multiple testing across $>$ 2 classes. For categorical variables,}\\
-	\multicolumn{5}{l}{ differences between latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.} \\
-	\multicolumn{5}{l}{\textsuperscript{\dag} Paid employment was defined as being in paid employment during the last 4 weeks prior to }\\
-	\multicolumn{5}{l}{the survey.}\\
-	\multicolumn{5}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally  } \\
-	\multicolumn{5}{l}{recognised civil partnership.}\\
+	\multicolumn{5}{l}{{\scriptsize \textit{Note: }}}\\
+	\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
+	\multicolumn{5}{l}{{\scriptsize Variables were weighted by individual weights.}}\\
+	\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes with Bonferroni}}\\ 
+	\multicolumn{5}{l}{{\scriptsize correction to account for multiple testing across $>$ 2 classes. For categorical variables, differences between}}\\
+	\multicolumn{5}{l}{{\scriptsize  latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.}} \\
+	\multicolumn{5}{l}{{\scriptsize \textsuperscript{\dag} Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey.} }\\
+	\multicolumn{5}{l}{{\scriptsize \textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil}} \\
+	\multicolumn{5}{l}{{\scriptsize partnership.}}\\
 \end{tabular}
@@
 \rowcolors{2}{white}{white}
+
+difference in employment status across three types of carbohydrate eaters.
+However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with a partner (\textit{p} < 0.001); low carbohydrate eaters were with the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.
+
+Weighted means, percentages of anthropometric measurements, average of main nutrient intake as well as biochemical characteristic profiles of latent carbohydrate eaters groups are given in \textbf{Table \ref{tab:tab2}}.
+Low carbohydrate eaters were with higher BMI (27.8 kg/m\textsuperscript{2}) and larger WC (94.6 cm) compared with 27.2, 27.3 kg/m\textsuperscript{2}, and 92.3, 92.2 cm in moderate and high carbohydrate eaters.
+High carbohydrate eaters had the lowest prevalence of being a current smoker (17.1\%).
+Average total energy intake over the 4 days of dietary survey was the highest (7985.8 kJ) in the low carbohydrate eaters group.
+As expected, the mean total carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively.
+Energy contribution from carbohydrate was close to 50\% in the high carbohydrate eaters, but only 40.6\% in the low carbohydrate eaters.
+It is noteworthy that low carbohydrate eaters consumed the highest average amount of protein (79.9 g, 17.2\% of total energy), fat (74.7g, 35.4\% of total energy), and alcohol (20.8 g, 6.8\% of total energy).
+
+From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetes (diagnosed by A1C > 6.5\%), while the number in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011).
+Borderline significance (\textit{p} = 0.051) suggested that fasting blood glucose level may be slightly higher in low carbohydrate eaters.
+Cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.
 
@@
 		\toprule
-	\textbf{Variables} & \textbf{\Centerstack{Low carbo-\\hydrate eaters\\(n = 1730)}} & \textbf{\Centerstack{Moderate carbo-\\hydrate eaters\\(n = 1772)}} & \textbf{\Centerstack{High carbo\\hydrate eaters\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
+	\textbf{Variables} & \textbf{\Centerstack{Low carbo-\\hydrate eaters\\(n = 1730)}} & \textbf{\Centerstack{Moderate carbo-\\hydrate eaters\\(n = 1772)}} & \textbf{\Centerstack{High carbo-\\hydrate eaters\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
 		\midrule
@@
 		BMI (kg/m\textsuperscript{2}) & 27.8 (27.4, 28.2) & 27.2 (26.7, 27.7) & 27.3 (26.9, 27.6) & 0.006\\
-		WC (cm) & 94.6 (93.5, 95.6) & 92.3 (91.0, 93.5) & 92.2 (91.4, 93.1) & 0.001\\
+		WC (cm) &&&& \\ 
+		\hspace{1em}Men &  98.9 (97.4, 100.5) & 95.9 (94.1, 97.8) &  98.1 (96.9, 99.2) & 0.056\\
+		\hspace{1em}Women & 89.9 (88.7, 91.3) &  88.7 (87.1, 90.3) &  87.2 (86.1, 88.2) & 0.005\\
 		Smoking status (\%) &  &  &  & \\
@@
 		\hspace{1em}Never & 50.3 (47.2, 32.2) & 55.4 (52.2, 58.6) & 56.8 (54.3, 59.3) & \\
-		Current drinking status (\%) &  &  &  & \\
-		\hspace{1em}Yes & 11.8 (10.0, 13.8) & 24.0 (21.2, 27.1) & 20.6 (18.7, 22.8) & < 0.001\\
-		Hypertension\textsuperscript{\dag} (\%) &  &  &  & \\
-		\hspace{1em}Yes & 33.4 (29.9, 37.1) & 21.1 (17.7, 24.9) & 31.2 (28.3, 34.2) & < 0.001\\
+		Hypertension\textsuperscript{\dag}, Yes (\%) & 33.4 (29.9, 37.1) & 21.1 (17.7, 24.9) & 31.2 (28.3, 34.2) & < 0.001\\
 		Total energy intake (kJ) & \Centerstack{7985.8\\(7823.3, 8146.3)} & \Centerstack{7341.8\\(7825.3, 8146.3)} & \Centerstack{7677.0\\(7555.8, 7799.8)} & < 0.001\\
@@
 		Fat percent (\%) & 35.4 (34.9, 35.8) & 32.5 (32.1, 32.9) & 32.0 (31.7, 32.3) & < 0.001\\
-		Glucose (mmol/l) & 5.20 (5.15, 5.26) & 5.09 (5.02, 5.17) & 5.13 (5.09, 5.12) & 0.051\\
-		A1C (\%) & 5.49 (5.45, 5.52) & 5.44 (5.40, 5.48) & 5.52 (5.49, 5.55) & 0.012\\
+		Alcohol intake (g) & 20.8 (18.3, 23.2) &  10.7 (9.4, 11.9) & 8.9 (8.1, 9.8) & < 0.001 \\
+		Alcohol percent (\%) &  6.8 (6.3, 7.4) &  3.8 (3.4, 4.3) & 3.2 (2.9, 3.4)& < 0.001 \\
+		Glucose (mmol/l) & 5.17 (5.12, 5.23) & 5.05 (4.99, 5.13) & 5.10 (5.05, 5.15) & 0.027\\
+		A1C (\%) & 5.47 (5.44, 5.51) & 5.43 (5.39, 5.47) & 5.50 (5.48, 5.53) & 0.010\\
 		DM \textsuperscript{\S} & 6.9 (5.0, 9.3) & 3.5 (2.3, 5.3) & 4.1 (2.9, 5.6) & 0.011\\
+		TC (mmol/l) & 4.95 (4.84, 5.05) & 4.72 (4.62, 4.83) & 4.95 (4.87, 5.03) & 0.001 \\
+		HDL (mmol/l) & 1.39 (1.35, 1.43)& 1.32 (1.28, 1.35) & 1.39 (1.36, 1.42)& 0.003 \\ 
+		LDL (mmol/l) &  2.88 (2.79, 2.97) & 2.77 (2.68, 2.86) & 2.93 (2.86, 3.00)& 0.024 \\ 
+		TG (mmol/l) &  1.14 (1.08, 1.19) &  1.11 (1.05, 1.17) & 1.10 (1.06, 1.15) & 0.629\\
 		Physical
-		activity (hours/day) \textsuperscript{\P} & 1.63 (1.43, 1.83) & 1.32 (1.15, 1.49) & 1.65 (1.49, 1.81) & 0.016\\
+		activity (hours/day) \textsuperscript{\P} & 1.08 (0.97, 1.19) & 0.87 (0.77, 0.97)  & 1.07 (0.98, 1.16) & 0.005 \\
 		\bottomrule
-		\multicolumn{5}{l}{\textit{Note: }}\\
-		\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling }\\
-		\multicolumn{5}{l}{programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, }\\
-		\multicolumn{5}{l}{diabetes mellitus.} \\
-		\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) were weighted by blood sample weights,}\\ 
-		\multicolumn{5}{l}{ the other variables were weighted by nurse visiting weights.}\\
-		\multicolumn{5}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
-		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes}\\ 
-		\multicolumn{5}{l}{with Bonferroni correction to accountfor multiple testing across $>$ 2 classes. For categorical variables, }\\
-		\multicolumn{5}{l}{differences between latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.}\\ 
-		\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure $\geqslant$ 140 mmHg or diastolic blood pressure }\\
-		\multicolumn{5}{l}{$\geqslant$ 90 mmHg, or under treatment for hypertension.}\\
-		\multicolumn{5}{l}{\textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake}\\  
-		\multicolumn{5}{l}{\textsuperscript{\S} DM was defined by A1C $>$ 6.5\%.}\\
-		\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity}\\
-		\multicolumn{5}{l}{including both work-related and recreational activities during the survey.}\\
+%		\multicolumn{5}{l}{\textit{Note: }}\\
+		\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}}\\
+		\multicolumn{5}{l}{{\scriptsize BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus; TC, total cholesterol, }}\\
+		\multicolumn{5}{l}{{\scriptsize HDL, high density lipoproteins; LDL, low density lipoproteins; TG, triglycerides.}} \\
+		\multicolumn{5}{l}{{\scriptsize Glucose, A1C, TC, HDL, LDL, TG, and physical activity were expressed in geometric means (95\% CI) because }} \\
+		\multicolumn{5}{l}{ the data was positively skewed.} \\
+		\multicolumn{5}{l}{{\scriptsize Variables from the blood tests (glucose and A1C) were weighted by blood sample weights, the other variables were}}\\ 
+		\multicolumn{5}{l}{{\scriptsize  weighted by nurse visiting weights. Glucose and A1C levels are estimated in subgroups of people without diabetes.}}\\
+		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes with}\\ 
+		\multicolumn{5}{l}{{\scriptsize  Bonferroni correction to account for multiple testing across $>$ 2 classes. For categorical variables, differences}}\\
+		\multicolumn{5}{l}{{\scriptsize  between latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.}}\\ 
+		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\dag} Hypertension was defined as either systolic blood pressure $\geqslant$ 140 mmHg or diastolic blood pressure $\geqslant$ 90 mmHg,}}\\
+		\multicolumn{5}{l}{{\scriptsize or under treatment for hypertension.}}\\
+		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake.}}\\  
+		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\S} DM was defined by A1C $>$ 6.5\%.}}\\
+		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both }}\\
+		\multicolumn{5}{l}{{\scriptsize work-related and recreational activities during the survey.}}\\
 	\end{tabular}
@@
 
-\section{Association between individual level latent classes and hypertension}
+\subsection{Association between individual level latent classes and hypertension, obesity, and diabetes.}
 
-\section{Association between individual level latent classes and obesity}
-
-\section{Association between individual level latent classes and diabetes}
+%
+%
+%
+%\section{Association between individual level latent classes and obesity}
+%
+%
+%
+%\section{Association between individual level latent classes and diabetes}

### 2018-08-05 paper/main.tex
LCGA removed
method updated regression models started writing some variables changed to log-transformed

@@
 \usepackage{caption} % to change the font of the table titles
-
+\usepackage{amssymb} % to use \leqslant
 %----------------------------------------------------------------------------------------
@@
 
-\thesistitle{The timing of carbohydrate intake in UK adults, using the National Dietary and Nutrition Survey (NDNS) 2008-2014 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+\thesistitle{The timing of carbohydrate intake in UK adults, using the National Dietary and Nutrition Survey (NDNS) 2008/09-2015/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
 \supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
@@
 
-\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
-\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
+%\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
+%\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
 \textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex \\
@@
 \textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
-\textbf{HbA1c} & \textbf{H}emoglobin \textbf{A1c}: Glycated hemoglobin \\
+\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated hemoglobin \\
 \textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
-\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
+%\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
 %\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
 \textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
-\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
-\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
+%\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
+%\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
 \textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
-\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
+%\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
 \textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\

### 2018-08-05 results/table1slots.Rmd
method updated regression models started writing some variables changed to log-transformed

--- 2018-08-01 results/table1slots.Rmd
@@
          cluster1, cluster2, cluster3, nssec8, paidemployment, qual7, eqvinc, MarSt2,
-         cluster4, cluster5, area, gor) %>% 
+         cluster4, cluster5, area, gor, LDL, HDL, Chol, Trig) %>% 
   rename(wti = wti_Y78, wtn = wtn_Y78, wtb = wtb_Y78, drink = dnoft3) %>% 
@@
                                  A1C  = -1, 
+                                 LDL = -1, HDL = -1, Chol = -1, Trig = -1,
                                  dnnow = -1,
@@
          cluster1, cluster2, cluster3, nssec8, paidemployment, eqvinc, MarSt2,
-         cluster4, cluster5, area, gor) %>% 
+         cluster4, cluster5, area, gor, LDL, HDL, Chol, Trig) %>% 
   mutate(Years = "5-6", MarStat = NA) %>% 
@@
                                  ethgrp2 = -4,
+                                 LDL = -1, HDL = -1, Chol = -1, Trig = -1,
                                  cigsta3 = -1,
@@
          Glucose, A1C, cigsta3, dnoft3, dnnow, wti_CY1234, wtn_CY1234, wtb_CY1234, ethgr5, ethgr2,
-         cluster, area, gor, nssec8, paidemployment, qual7, eqvinc, MarSt2, MarStat) %>%
+         cluster, area, gor, nssec8, paidemployment, qual7, eqvinc, MarSt2, MarStat, LDL, HDL, Chol, Trig) %>%
   rename(hyper140_2 = hyper140, hibp140_2 = hibp140, bpmedd2 = bpmedd, 
@@
                                  dnnow = -1,
+                                 LDL = -1, HDL = -1, Chol = -1, Trig = -1,
                                  drink = -1,
@@
 Energy14 <- food14 %>% 
-  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, CHOpctotE, Proteing, ProteinpctotE, 
+  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, 
+         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,
          Fatg, FatpctotE)
@@
 Energy56 <- food56 %>% 
-  select(ID, Country, Surveyyear, EnergykJ, Carbohydrateg, CHOpctotE, Proteing, ProteinpctotE, 
+  select(ID, Country, Surveyyear, EnergykJ, Carbohydrateg, 
+         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,
          Fatg, FatpctotE) %>% 
@@
 Energy78 <- food78 %>% 
-  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, CHOpctotE, Proteing, ProteinpctotE, 
+  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, 
+         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,
          Fatg, FatpctotE)
@@
 
-CW3CB3 <- read_table2("~/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB2.txt",  
+CW3CB3 <- read_table2("~/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB3.txt",  
                               col_names = FALSE)# change the path to your own path
@@
                       "CPROB2", "CPROB3", "CPROB4", "CPROB5", "CPROB6", 
+                      "CPROB7", "CPROB8", "CPROB9", 
                       "CB", "CW", "MLCJOINT", "ID")
@@
 
+CW3idday <- CW3idday %>% 
+  mutate(DayofWeek = factor(DayofWeek, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")))
+
 with(CW3idday, tabpct(DayofWeek, CW))

### 2018-08-06 paper/Chapters/Chapter2.tex
hypetension tab1 added

@@
 Computer assisted personal interviews were conducted for the selected individuals by trained interviewers to collect background information on smoking habits (current, past, never smokers), ethnicity (white, non-white), education level, living with a partner or not and other socio-demographic related variables.
-Participants also had their height, weight, blood pressure, waist circumferences (WC) measured by the nurse.
+Participants also had their height, weight, blood pressure, waist circumferences (WC) measured by the nurses.
 
@@
 The means of second and third readings, taken at one minute intervals, were used in the current report.
-Hypertension was defined as a systolic blood pressure of 140 mmHg or above, and/or diastolic blood pressure of 90 mmHg or above, and/or taking any medication specifically to reduce blood pressure.
+Hypertension was defined as with systolic blood pressure of 140 mmHg or above, and/or diastolic blood pressure of 90 mmHg or above, and/or taking any medication specifically to reduce blood pressure.
 
@@
 Multiple linear regression model (for WC), multinomial logistic regression model (for BMI categories), logistic regression models (for hypertension, and diabetes) were used to test for associations between individual level carbohydrate eating latent classes and WC, obesity, hypertension, and diabetes, separately.
+
+Model fitting strategies

### 2018-08-06 paper/Chapters/Chapter3.tex
hypetension tab1 added

@@
 
-	\caption{\label{tab:daylevel}Day level latent class solution for three classes solution. (No Individual level Model)}\vspace{-0.3cm}
+	\caption{\label{tab:daylevel}Day level latent class solution for three classes LCA model. (No Individual level Model)}\vspace{-0.3cm}
 	\centering
@@
 		\multicolumn{7}{l}{{\scriptsize \textit{Note: }}}\\
+		\multicolumn{7}{l}{\scriptsize \textbf{Abbreviation:} LCA, latent class analysis}\\
 		\multicolumn{7}{l}{{\scriptsize \textsuperscript{*} Carbohydrate $<$ 50\% indicates that within the time slot, carbohydrate contributed $<$ 50\% total energy intake.}}\\
@@
 		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\dag} Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey, glucose, fructose}}\\ 
-		\multicolumn{5}{l}{{\scriptsize and sglucose syrups, sugars added to food and sugars in fruit juices.}}\\
+		\multicolumn{5}{l}{{\scriptsize and glucose syrups, sugars added to food and sugars in fruit juices.}}\\
 	\end{tabular}
@@
 Gender distribution across the three types of carbohydrate eaters were fairly even (\textit{p} = 0.119).
-Distribution of the carbohydrate eaters types was changing with the year of survey.
+Distribution of the carbohydrate eater types was changing with the year of survey.
 Low carbohydrate eaters represented 32.5\% of the population in the first year of survey, but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year.
@@
 	Total (\%) & 28.4 (26.9, 29.9) & 28.7 (27.1, 30.3) & 43.0 (41.3, 44.7) & \\
-	Countries (\%) &  &  &  & 0.007\\
+	Country (\%) &  &  &  & 0.007\\
 	\hspace{1em}England & 84.5 (81.7, 86.9) & 82.0 (79.3, 84.5) & 84.7 (82.3, 86.8) & \\
@@
 difference in employment status across three types of carbohydrate eaters.
-However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with a partner (\textit{p} < 0.001); low carbohydrate eaters were with the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.
+However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with a partner (\textit{p} < 0.001); moderate carbohydrate eaters had the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.
 
-Weighted means, percentages of anthropometric measurements, average of main nutrient intake as well as biochemical characteristic profiles of latent carbohydrate eaters groups are given in \textbf{Table \ref{tab:tab2}}.
-Low carbohydrate eaters were with higher BMI (27.8 kg/m\textsuperscript{2}) and larger WC (94.6 cm) compared with 27.2, 27.3 kg/m\textsuperscript{2}, and 92.3, 92.2 cm in moderate and high carbohydrate eaters.
-High carbohydrate eaters had the lowest prevalence of being a current smoker (17.1\%).
+Weighted means, percentages of anthropometric measurements, average of main nutrient intake, as well as biochemical characteristic profiles of latent carbohydrate eater groups are given in \textbf{Table \ref{tab:tab2}}.
+Low carbohydrate eaters were with higher BMI (27.8 kg/m\textsuperscript{2}) and larger WC (98.9/89.9 cm in men/women) compared with 27.2, 27.3 kg/m\textsuperscript{2}, and 95.9/88.7 (men/women), 98.1/87.2 (men/women) cm in moderate and high carbohydrate eaters.
+Moderate carbohydrate eaters had the highest prevalence of being a current smoker (27.8\%), shortest physical activity (geometric mean: 0.87 hours/day), and the lowest prevalence of hypertension (20.2\%).
+
 Average total energy intake over the 4 days of dietary survey was the highest (7985.8 kJ) in the low carbohydrate eaters group.
 As expected, the mean total carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively.
-Energy contribution from carbohydrate was close to 50\% in the high carbohydrate eaters, but only 40.6\% in the low carbohydrate eaters.
+Energy contribution from carbohydrate was close to 50\% in the high carbohydrate eaters, but was only 40.6\% in the low carbohydrate eaters.
 It is noteworthy that low carbohydrate eaters consumed the highest average amount of protein (79.9 g, 17.2\% of total energy), fat (74.7g, 35.4\% of total energy), and alcohol (20.8 g, 6.8\% of total energy).
 
-From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetes (diagnosed by A1C > 6.5\%), while the number in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011).
-Borderline significance (\textit{p} = 0.051) suggested that fasting blood glucose level may be slightly higher in low carbohydrate eaters.
+From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetes (diagnosed by A1C > 6.5\%), while the percentages of diabetes in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011).
+There were some evidence (\textit{p} = 0.027) that fasting blood glucose level may be slightly higher in non-diabetes low carbohydrate eaters, while the geometric mean for A1C was probably lower in moderate carbohydrate eaters (4.72, 95\%CI: 5.39, 5.47).
 Cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.
@@
 		\hspace{1em}Never & 50.3 (47.2, 32.2) & 55.4 (52.2, 58.6) & 56.8 (54.3, 59.3) & \\
-		Hypertension\textsuperscript{\dag}, Yes (\%) & 33.4 (29.9, 37.1) & 21.1 (17.7, 24.9) & 31.2 (28.3, 34.2) & < 0.001\\
+		Physical activity (hours/day) \textsuperscript{\P} & 1.08 (0.97, 1.19) & 0.87 (0.77, 0.97)  & 1.07 (0.98, 1.16) & 0.005 \\
+		Hypertension\textsuperscript{\dag}, Yes (\%) & 33.8 (30.2, 37.5) & 20.2 (17.0, 24.0) & 30.9 (26.9, 31.0) & < 0.001\\
 		Total energy intake (kJ) & \Centerstack{7985.8\\(7823.3, 8146.3)} & \Centerstack{7341.8\\(7825.3, 8146.3)} & \Centerstack{7677.0\\(7555.8, 7799.8)} & < 0.001\\
@@
 		TG (mmol/l) &  1.14 (1.08, 1.19) &  1.11 (1.05, 1.17) & 1.10 (1.06, 1.15) & 0.629\\
-		Physical
-		activity (hours/day) \textsuperscript{\P} & 1.08 (0.97, 1.19) & 0.87 (0.77, 0.97)  & 1.07 (0.98, 1.16) & 0.005 \\
 		\bottomrule
@@
 		\multicolumn{5}{l}{{\scriptsize Glucose, A1C, TC, HDL, LDL, TG, and physical activity were expressed in geometric means (95\% CI) because }} \\
-		\multicolumn{5}{l}{ the data was positively skewed.} \\
+		\multicolumn{5}{l}{ the data were positively skewed.} \\
 		\multicolumn{5}{l}{{\scriptsize Variables from the blood tests (glucose and A1C) were weighted by blood sample weights, the other variables were}}\\ 
@@
 		\multicolumn{5}{l}{{\scriptsize  between latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.}}\\ 
+		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both }}\\
+		\multicolumn{5}{l}{{\scriptsize work-related and recreational activities during the most recent month before the survey.}}\\
+
 		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\dag} Hypertension was defined as either systolic blood pressure $\geqslant$ 140 mmHg or diastolic blood pressure $\geqslant$ 90 mmHg,}}\\
@@
 		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\S} DM was defined by A1C $>$ 6.5\%.}}\\
-		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both }}\\
-		\multicolumn{5}{l}{{\scriptsize work-related and recreational activities during the survey.}}\\
 	\end{tabular}

### 2018-08-06 paper/Chapters/Chapter3.tex
tab1 hyper tab1 BMi

@@
 
-	\caption{\label{tab:daylevel}Day level latent class solution for three classes LCA model. (No Individual level Model)}\vspace{-0.3cm}
+	\caption{\label{tab:daylevel}Day level latent class solution for three classes LCA model. (No individual level model)}\vspace{-0.3cm}
 	\centering
@@
 
+\begin{sidewaystable}
+\rowcolors{2}{gray!6}{white}
+%\begin{table}
+	\caption{\label{tab:tab1hypetension}Weighted means, percentages, and 95 \% CIs of the characteristics by hypertension status in the UK adults. \\(NDNS RP 2008/09-2015/16, sample size = 6155)}
+	\centering
+	\fontsize{9}{11}\selectfont
+	\begin{tabular}[t]{lcccccc}
+		\hiderowcolors
+		\toprule
+		\multicolumn{1}{c}{ } & \multicolumn{3}{c}{\textbf{Men (n = 2537)}} & \multicolumn{3}{c}{\textbf{Women (n = 3618)}} \\
+		\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
+		& \textbf{Non-hypertensive} & \textbf{Hypertensive} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{Non-hypertensive} & \textbf{Hypertensive} & \textbf{\textit{P} value\textsuperscript{*}}\\
+		\midrule
+		\showrowcolors
+		Weighted prevalence (\%) & 69.6 (66.6, 72.5)  & 30.4 (27.5, 33.4) &  & 72.5 (69.8, 75.0) & 27.5 (25.0, 30.2) & \\
+		Age (years) & 43.2 (41.7, 44.7) & 59.9 (58.0, 61.7) & < 0.001 & 43.9 (42.7, 45.1) & 64.9 (63.4, 66.5) & < 0.001\\
+		Country (\%) &  &  & 0.109 &  &  & 0.631\\
+		\hspace{1em}England & 84.7 (80.9, 87.2) & 85.4 (81.2, 88.8) &  & 84.0 (81.0, 86.6) & 83.5 (79.1, 87.0) & \\
+		\hspace{1em}Northern Ireland & 3.3 (2.2, 4.8) & 1.6 (0.8, 3.1) &  & 2.5 (1.9, 3.5) & 2.6 (1.5, 4.3) & \\
+		\hspace{1em}Scotland & 8.6 (6.3, 11.7) & 7.1 (4.6, 10.9) &  & 8.7 (6.5, 11.7) & 7.9 (5.1, 11.8) & \\
+		\hspace{1em}Wales & 3.9 (2.7, 5.6) & 5.9 (4.0, 8.5) &  & 4.7 (3.7, 6.0) & 6.1 (4.3, 8.6) & \\
+		Ethnicity (\%) &  &  & 0.534 &  &  & 0.126\\
+		\hspace{1em}White & 89.6 (86.5, 92.0) & 91.1 (86.2, 94.4) &  & 85.7 (82.7, 88.3) & 90.2 (85.0, 93.7) & \\
+		\hspace{1em}Non-white & 10.4 (8.0, 13.5) & 8.9 (5.6, 13.8) &  & 14.3 (11.7, 17.3) & 9.8 (6.3, 15.0) & \\
+		Education (\%) &  &  & 0.006 &  &  & < 0.001\\
+		\hspace{1em}Degree or higher & 30.3 (26.6, 34.2) & 21.5 (17.3, 26.5) &  & 33.0 (29.9, 36.3) & 19.7 (15.8, 24.3) & \\
+		\hspace{1em}Lower than Degree & 69.7 (65.8, 73.4) & 78.5 (73.5, 82.7) &  & 67.0 (63.7, 70.1) & 80.3 (75.7, 84.2) & \\
+		Smoking status &  &  & < 0.001 &  &  & < 0.001\\
+		\hspace{1em}Current & 19.7 (16.6, 23.1) & 12.9 (9.5, 17.2) &  & 15.2 (13.1, 17.6) & 8.5 (6.2, 11.6) & \\
+		\hspace{1em}Ex-smoker & 24.2 (21.1, 27.6) & 38.8 (33.4, 44.5) &  & 21.6 (19.1, 24.4) & 32.2 (27.3, 37.4) & \\
+		\hspace{1em}Never & 56.2 (52.1, 60.1) & 48.3 (42.7, 54.0) &  & 63.2 (60.1, 66.2) & 59.3 (54.0, 64.4) & \\
+		Physical
+		activity (hours/day) \textsuperscript{\dag} & 1.52 (1.33, 1.72) & 1.29 (1.08, 1.53) & 0.134 & 0.81 (0.73, 0.89) & 0.53 (0.42, 0.64) & < 0.001\\
+		BMI (kg/m\textsuperscript{2}) & 26.8 (26.4, 27.2) & 29.5 (28.9, 29.9) & < 0.001 & 26.4 (26.1, 26.8) & 29.8 (29.2, 30.5) & < 0.001\\
+		WC (cm) & 95.0 (93.9, 96.2) & 104.6 (103.2, 106.1) & < 0.001 & 85.7 (84.8, 86.6) & 95.7 (94.2, 97.2) & < 0.001\\
+		Carbohydrate eating patterns (\%) &  &  & < 0.001 &  &  & < 0.001\\
+		\hspace{1em}Low & 28.3 (24.8, 32.2) & 37.1 (32.0, 42.5) &  & 26.9 (24.1, 29.9) & 32.0 (27.2, 37.2) & \\
+		\hspace{1em}Moderate & 30.8 (26.9, 35.0) & 19.3 (15.3, 24.1) &  & 29.6 (26.4, 33.0) & 18.4 (14.5, 22.9) & \\
+		\hspace{1em}High & 40.8 (36.9, 44.9) & 43.6 (38.2, 49.2) &  & 43.5 (40.3, 46.8) & 49.7 (44.1, 55.2) & \\
+		Total energy intake (kJ) & 9021.4 (8791.9, 9251.0) & 8366.2 (8094.9, 8637.4) & < 0.001 & 6802.6 (6681.1, 6924.0) & 6396.7 (6217.1, 6576.2) & < 0.001\\
+		Carbohydrate intake (g) & 259.2 (252.9, 265.3) & 235.3 (227.8, 242.8) & < 0.001 & 198.0 (194.2, 201.8) & 184.5 (178.8, 190.1) & < 0.001\\
+		\bottomrule
+		\multicolumn{7}{l}{\textit{Note: }}\\
+		\multicolumn{7}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
+		\multicolumn{7}{l}{ BMI body mass index; WC, waist circumference.}\\
+		\multicolumn{7}{l}{Variables are weighted by nurse visiting weights.}\\
+		\multicolumn{7}{l}{\textsuperscript{*} Significant sex-specific differences by hypertension status assessed using an \textit{F} test for continuous variables or design-adjusted Pearson $\chi^2$ test.}\\
+		\multicolumn{7}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}\\
+	\end{tabular}
+\rowcolors{2}{white}{white}
+\end{sidewaystable}
+
+\begin{sidewaystable}
+	\rowcolors{2}{gray!6}{white}
+
+%	\begin{table}
+
+		\caption{\label{tab:tab1BMI}Weighted means, percentages, and 95 \% CIs of the characteristics by BMI categories in the UK adults. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
+		\centering
+		\fontsize{9}{11}\selectfont
+		\begin{tabular}[t]{lcccccccc}
+			\hiderowcolors
+			\toprule
+			\multicolumn{1}{c}{ } & \multicolumn{4}{c}{\textbf{Men (n = 2537)}} & \multicolumn{4}{c}{\textbf{Women (n = 3618)}} \\
+			\cmidrule(l{2pt}r{2pt}){2-5} \cmidrule(l{2pt}r{2pt}){6-9}
+			& \textbf{Normal weight} & \textbf{Overweight} & \textbf{Obese} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{Normal weight} & \textbf{Overweight} & \textbf{Obese} & \textbf{\textit{P} value\textsuperscript{*}}\\
+			\midrule
+			\showrowcolors
+			Weighted prevalence (\%) & 30.9 (28.0, 33.9) & 43.4 (40.4, 46.4) & 25.7 (23.2, 28.4) &  & 41.7 (39.0, 44.4) & 30.9 (28.4, 33.5) & 27.4 (25.1, 29.9) & \\
+			BMI (kg/m\textsuperscript{2}) & 22.6 (22.3, 22.8) & 27.3 (27.2, 27.5) & 33.7 (33.3, 34.2) & < 0.001 & 22.2 (22.0, 22.4) & 27.3 (27.2, 27.5) & 35.0 (34.6, 35.4) & < 0.001\\
+			WC (cm) & 84.5 (83.6, 85.4) & 97.1 (96.4, 97.8) & 112.7 (111.6, 113.9) & < 0.001 & 76.9 (76.2, 77.5) & 89.0 (88.3, 89.7) & 103.7 (102.6, 104.7) & < 0.001\\
+			Age (years) & 40.3 (38.2, 42.4) & 49.6 (47.9, 51.2) & 50.4 (48.5, 52.3) & < 0.001 & 45.0 (43.4, 46.7) & 50.4 (48.6, 52.3) & 50.9 (49.1, 52.7) & < 0.001\\
+			Country (\%) &  &  &  & 0.236 &  &  &  & 0.589\\
+			\hspace{1em}England & 83.9 (79.2, 87.7) & 86.9 (83.6, 89.7) & 81.6 (76.7, 85.7) &  & 84.3 (80.4, 87.5) & 83.7 (79.7, 87.0) & 82.4 (78.2, 85.9) & \\
+			\hspace{1em}Northern Ireland & 3.3 (1.9, 5.8) & 2.3 (1.4, 3.6) & 3.2 (2.0, 4.9) &  & 3.0 (2.1, 4.2) & 2.2 (1.5, 3.2) & 3.4 (2.3, 5.0) & \\
+			\hspace{1em}Scotland & 9.1 (6.1, 13.5) & 6.5 (4.4, 9.7) & 9.0 (5.9, 13.3) &  & 9.0 (6.1, 13.0) & 9.0 (6.3, 12.8) & 8.5 (5.7, 12.6) & \\
+			\hspace{1em}Wales & 3.7 (2.3, 5.8) & 4.3 (3.1, 5.9) & 6.3 (4.0, 9.7) &  & 3.8 (2.9, 5.1) & 5.1 (3.6, 7.2) & 5.7 (4.2, 7.7) & \\
+			Ethnicity (\%) &  &  &  & 0.466 &  &  &  & 0.879\\
+			\hspace{1em}White & 88.7 (83.9, 92.2) & 89.1 (85.6, 91.9) & 91.9 (87.3, 94.9) &  & 88.4 (84.9, 91.19 & 88.6 (84.5, 91.7) & 87.3 (82.5, 90.9) & \\
+			\hspace{1em}Non-white & 11.3 (7.8, 16.1) & 10.9 (8.1, 14.4) & 8.1 (5.1, 12.7) &  & 11.6 (8.9, 15.1) & 11.4 (8.3, 15.5) & 12.7 (9.1, 17.5) & \\
+			Education (\%) &  &  &  & 0.022 &  &  &  & < 0.001\\
+			\hspace{1em}Degree or higher & 29.5 (24.5, 35.0) & 28.3 (24.3, 32.7) & 20.1 (16.0, 25.0) &  & 35.7 (31.8, 39.8) & 24.2 (20.4, 28.4) & 19.4 (16.1, 23.2) & \\
+			\hspace{1em}Lower than Degree & 70.5 (65.0, 75.5) & 71.7 (67.3, 75.7) & 79.9 (75.0, 84.0) &  & 64.3 (60.2, 68.2) & 75.8 (71.6, 79.6) & 80.6 (76.8, 83.9) & \\
+			Smoking status &  &  &  & < 0.001 &  &  &  & 0.042\\
+			\hspace{1em}Current  & 32.0  (26.8, 37.7) & 18.7 (15.5, 22.4) & 19.2 (15.0, 24.3) &  & 19.5 (16.4, 22.9) & 17.8 (14.8, 21.4) & 16.4 (13.1, 20.3) & \\
+			\hspace{1em}Ex-smoker & 17.3 (13.5, 22.0) & 28.6 (24.8, 32.7) & 32.9 (27.9, 38.4) &  & 19.0 (15.9, 22.5) & 24.4 (20.8, 28.3) & 26.9 (22.8, 31.6) & \\
+			\hspace{1em}Never & 50.6 (44.8, 56.4) & 52.7 (48.2, 57.1) & 47.9 (42.1, 53.7) &  & 61.6 (57.4, 65.5) & 57.8 (53.3, 62.2) & 56.7 (51.8, 61.4) & \\
+			Physical activity\textsuperscript{\dag} (hours/day) & 1.58 (1.33, 1.85) & 1.42 (1.24, 1.62) & 1.41 (1.15, 1.70) & 0.547 & 0.84 (0.74, 0.94) & 0.71 (0.62, 0.79) & 0.65 (0.53, 0.78) & 0.038\\
+			Carbohydrate eating patterns (\%) &  &  &  & 0.072 &  &  &  & 0.253\\
+			\hspace{1em}Low & 25.9 (21.0, 31.5) & 30.6 (26.6, 35.0) & 31.4 (26.6, 36.6) &  & 24.8 (21.5, 28.5) & 26.8 (22.8, 31.2) & 29.5 (25.3, 34.1) & \\
+			\hspace{1em}Moderate & 34.2 (28.6, 40.4) & 25.5 (21.9, 29.6) & 25.5 (20.6, 31.0) &  & 27.6 (23.8, 31.8) & 26.3 (22.3, 30.8) & 29.8 (25.4, 34.6) & \\
+			\hspace{1em}High & 39.9 (34.2, 45.8) & 43.8 (39.6, 48.2) & 43.1 (37.7, 48.7) &  & 47.6 (43.3, 51.9) & 46.9 (42.4, 51.4) & 40.7 (36.0, 45.6) & \\
+			Total energy intake (kJ) & \Centerstack{9351.2 \\ (8961.7, 9740.7)} & \Centerstack{8786.9 \\ (8595.1, 8978.7)} & \Centerstack{8465.3 \\ (8196.4, 8734.1)} & 0.001 & \Centerstack{7048.9 \\ (6894.4, 7203.4)} & \Centerstack{6570.1 \\(6406.2, 6734.0)} & \Centerstack{6566.4 \\ (6360.7, 6772.1)} & < 0.001\\
+			Carbohydrate intake (g) & \Centerstack{268.7 \\ (258.3, 279.2)} & \Centerstack{250.1\\ (244.1, 256.1)} & \Centerstack{239.1 \\ (231.3, 246.8)} & < 0.001 & \Centerstack{205.8 \\(200.2, 211.3)} & \Centerstack{190.1 \\ (185.3, 194.9)} & \Centerstack{189.8 \\ (183.7, 195.9)} & < 0.001\\
+			\bottomrule
+			\multicolumn{9}{l}{\textit{Note: }}\\
+			\multicolumn{9}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
+			\multicolumn{9}{l}{ BMI body mass index; WC, waist circumference.}\\
+			\multicolumn{9}{l}{Variables are weighted by nurse visiting weights.}\\
+			\multicolumn{9}{l}{\textsuperscript{*} Significant sex-specific differences by BMI categories assessed using an F test (with Bonferroni correction to account for multiple testing across $>$ 2 groups)} \\
+			\multicolumn{9}{l}{for continuous variables or design-adjusted Pearson $\chi^2$ test}\\
+			\multicolumn{9}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}\\
+		\end{tabular}
+%	\end{table}
+
+	\rowcolors{2}{white}{white}
+\end{sidewaystable}
+
 %

### 2018-08-06 paper/Tables/2by2Table1.Rmd
tables figs of MLCA done, classes and bmi, dm, hyt estimates needed
tab1 hyper tab1 BMi

@@
 dt[9, 1] <- c("Hypertension[note] (%)")
-dt[12, 1] <- c("Carbohydrate percent[note] (%)")
+dt[13, 1] <- c("Carbohydrate percent[note] (%)")
 
@@
 ```
+
+## Hypertension table 1
+
+```{r tab1hypetension, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/hypertensiontab1.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c(" ", "Non-hypertensive", "Hypertensive", "P value[note]", 
+               "Non-hypertensive", "Hypertensive", "P value")
+
+# 
+# dt[9, 1] <- c("Hypertension[note] (%)")
+# dt[13, 1] <- c("Carbohydrate percent[note] (%)")
+
+dt[17, 1] <- c("Physical\nactivity (hours/day) [note]")
+# dt[20, 1] <- c("DM [note]")
+# dt[20, 1] <- c("Paid employment[note] (%)")
+# dt[23, 1] <- c("Live with partner[note] (%)")
+
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
+ kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+  add_indent(c(3:6,8,9,11,12,14,15,16,21:23)) %>% 
+   add_header_above(c(" ", "Men (n = 2537)" = 3, "Women (n = 3618)" = 3)) %>% 
+  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;",
+                        " BMI body mass index; WC, waist circumference.", 
+                        "Variables are weighted by nurse visiting weights.")) %>% 
+  add_footnote(c("Significant sex-specific differences by hypertension status assessed using an F test for continuous variables or design-adjusted Pearson chi-square test",
+                 # "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
+                 # # "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
+                 # "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.",
+                 # "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
+                 # "DM was defined by A1C > 6.5%.",
+                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the survey."
+                 ), 
+               notation = "symbol")
+```
+
+## BMI
+
+```{r tab1BMI, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/BMItab1.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c(" ", "Normal weight", "Overweight", "Obese", "P value[note]", "Normal weight", "Overweight", "Obese", "P value")
+
+# 
+# dt[9, 1] <- c("Hypertension[note] (%)")
+# dt[13, 1] <- c("Carbohydrate percent[note] (%)")
+
+dt[17, 1] <- c("Physical\nactivity (hours/day) [note]")
+# dt[20, 1] <- c("DM [note]")
+# dt[20, 1] <- c("Paid employment[note] (%)")
+# dt[23, 1] <- c("Live with partner[note] (%)")
+
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
+ kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+  add_indent(c(6:9, 11,12, 14,15, 17:19, 22:24)) %>% 
+   add_header_above(c(" ", "Men (n = 2537)" = 4, "Women (n = 3618)" = 4)) %>% 
+  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;",  
+                       " BMI body mass index; WC, waist circumference.", 
+                       "Variables are weighted by nurse visiting weights.")) %>% 
+  add_footnote(c("Significant sex-specific differences by BMI categories assessed using an F test (with Bonferroni correction to account for multiple testing across $>$ 2 groups) for continuous variables or design-adjusted Pearson chi-square test",
+                 # "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
+                 # # "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
+                 # "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.",
+                 # "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
+                 # "DM was defined by A1C > 6.5%.",
+                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the survey."
+                 ), 
+               notation = "symbol")
+```
+
+## DM
+
+```{r tab1BMI, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/BMItab1.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c(" ", "Normal weight", "Overweight", "Obese", "P value[note]", "Normal weight", "Overweight", "Obese", "P value")
+
+# 
+# dt[9, 1] <- c("Hypertension[note] (%)")
+# dt[13, 1] <- c("Carbohydrate percent[note] (%)")
+
+dt[17, 1] <- c("Physical\nactivity (hours/day) [note]")
+# dt[20, 1] <- c("DM [note]")
+# dt[20, 1] <- c("Paid employment[note] (%)")
+# dt[23, 1] <- c("Live with partner[note] (%)")
+
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
+ kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+  add_indent(c(6:9, 11,12, 14,15, 17:19, 22:24)) %>% 
+   add_header_above(c(" ", "Men (n = 2537)" = 4, "Women (n = 3618)" = 4)) %>% 
+  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;",  
+                       " BMI body mass index; WC, waist circumference.", 
+                       "Variables are weighted by nurse visiting weights.")) %>% 
+  add_footnote(c("Significant sex-specific differences by BMI categories assessed using an F test (with Bonferroni correction to account for multiple testing across $>$ 2 groups) for continuous variables or design-adjusted Pearson chi-square test",
+                 # "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
+                 # # "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
+                 # "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.",
+                 # "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
+                 # "DM was defined by A1C > 6.5%.",
+                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the survey."
+                 ), 
+               notation = "symbol")
+```

### 2018-08-06 paper/Tables/2by2Table1.tex
tab1 hyper tab1 BMi

@@
 
+\subsection{Hypertension table 1}\label{hypertension-table-1}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:tab1hypetension}Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{lllllll}
+\hiderowcolors
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Men (n = 2537)} & \multicolumn{3}{c}{Women (n = 3618)} \\
+\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
+  & Non-hypertensive & Hypertensive & P value\textsuperscript{*} & Non-hypertensive & Hypertensive & P value\\
+\midrule
+\showrowcolors
+Age (years) & 43.2 (41.7, 44.7) & 59.9 (58.0, 61.7) & < 0.001 & 43.9 (42.7, 45.1) & 64.9 (63.4, 66.5) & < 0.001\\
+Country (\%) &  &  & 0.109 &  &  & 0.631\\
+\hspace{1em}England & 84.7 (80.9, 87.2) & 85.4 (81.2, 88.8) &  & 84.0 (81.0, 86.6) & 83.5 (79.1, 87.0) & \\
+\hspace{1em}Northern Ireland & 3.3 (2.2, 4.8) & 1.6 (0.8, 3.1) &  & 2.5 (1.9, 3.5) & 2.6 (1.5, 4.3) & \\
+\hspace{1em}Scotland & 8.6 (6.3, 11.7) & 7.1 (4.6, 10.9) &  & 8.7 (6.5, 11.7) & 7.9 (5.1, 11.8) & \\
+\hspace{1em}Wales & 3.9 (2.7, 5.6) & 5.9 (4.0, 8.5) &  & 4.7 (3.7, 6.0) & 6.1 (4.3, 8.6) & \\
+Ethnicity (\%) &  &  & 0.534 &  &  & 0.126\\
+\hspace{1em}White & 89.6 (86.5, 92.0) & 91.1 (86.2, 94.4) &  & 85.7 (82.7, 88.3) & 90.2 (85.0, 93.7) & \\
+\hspace{1em}Non-white & 10.4 (8.0, 13.5) & 8.9 (5.6, 13.8) &  & 14.3 (11.7, 17.3) & 9.8 (6.3, 15.0) & \\
+Education (\%) &  &  & 0.006 &  &  & < 0.001\\
+\hspace{1em}Degree or higher & 30.3 (26.6, 34.2) & 21.5 (17.3, 26.5) &  & 33.0 (29.9, 36.3) & 19.7 (15.8, 24.3) & \\
+\hspace{1em}Lower than Degree & 69.7 (65.8, 73.4) & 78.5 (73.5, 82.7) &  & 67.0 (63.7, 70.1) & 80.3 (75.7, 84.2) & \\
+Smoking status &  &  & < 0.001 &  &  & < 0.001\\
+\hspace{1em}Current & 19.7 (16.6, 23.1) & 12.9 (9.5, 17.2) &  & 15.2 (13.1, 17.6) & 8.5 (6.2, 11.6) & \\
+\hspace{1em}Ex-smoker & 24.2 (21.1, 27.6) & 38.8 (33.4, 44.5) &  & 21.6 (19.1, 24.4) & 32.2 (27.3, 37.4) & \\
+\hspace{1em}Never & 56.2 (52.1, 60.1) & 48.3 (42.7, 54.0) &  & 63.2 (60.1, 66.2) & 59.3 (54.0, 64.4) & \\
+Physical
+activity (hours/day) \textsuperscript{\dag} & 1.52 (1.33, 1.72) & 1.29 (1.08, 1.53) & 0.134 & 0.81 (0.73, 0.89) & 0.53 (0.42, 0.64) & < 0.001\\
+BMI (kg/m2) & 26.8 (26.4, 27.2) & 29.5 (28.9, 29.9) & < 0.001 & 26.4 (26.1, 26.8) & 29.8 (29.2, 30.5) & < 0.001\\
+WC (cm) & 95.0 (93.9, 96.2) & 104.6 (103.2, 106.1) & < 0.001 & 85.7 (84.8, 86.6) & 95.7 (94.2, 97.2) & < 0.001\\
+Carbohydrate eating patterns (\%) &  &  & < 0.001 &  &  & < 0.001\\
+\hspace{1em}Low & 28.3 (24.8, 32.2) & 37.1 (32.0, 42.5) &  & 26.9 (24.1, 29.9) & 32.0 (27.2, 37.2) & \\
+\hspace{1em}Moderate & 30.8 (26.9, 35.0) & 19.3 (15.3, 24.1) &  & 29.6 (26.4, 33.0) & 18.4 (14.5, 22.9) & \\
+\hspace{1em}High & 40.8 (36.9, 44.9) & 43.6 (38.2, 49.2) &  & 43.5 (40.3, 46.8) & 49.7 (44.1, 55.2) & \\
+Total energy intake (kJ) & 9021.4 (8791.9, 9251.0) & 8366.2 (8094.9, 8637.4) & < 0.001 & 6802.6 (6681.1, 6924.0) & 6396.7 (6217.1, 6576.2) & < 0.001\\
+Carbohydrate intake (g) & 259.2 (252.9, 265.3) & 235.3 (227.8, 242.8) & < 0.001 & 198.0 (194.2, 201.8) & 184.5 (178.8, 190.1) & < 0.001\\
+\bottomrule
+\multicolumn{7}{l}{\textit{Note: }}\\
+\multicolumn{7}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
+\multicolumn{7}{l}{ BMI body mass index; WC, waist circumference.}\\
+\multicolumn{7}{l}{Variables are weighted by nurse visiting weights.}\\
+\multicolumn{7}{l}{\textsuperscript{*} Significant sex-specific differences by hypertension status assessed using an F test for continuous variables or design-adjusted Pearson chi-square test}\\
+\multicolumn{7}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the survey.}\\
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
+\subsection{BMI}\label{bmi}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:tab1BMI}Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{lllllllll}
+\hiderowcolors
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Men (n = 2537)} & \multicolumn{4}{c}{Women (n = 3618)} \\
+\cmidrule(l{2pt}r{2pt}){2-5} \cmidrule(l{2pt}r{2pt}){6-9}
+  & Normal weight & Overweight & Obese & P value\textsuperscript{*} & Normal weight & Overweight & Obese & P value\\
+\midrule
+\showrowcolors
+Weighted prevalence (\%) & 30.9 (28.0, 33.9) & 43.4 (40.4, 46.4) & 25.7 (23.2, 28.4) &  & 41.7 (39.0, 44.4) & 30.9 (28.4, 33.5) & 27.4 (25.1, 29.9) & \\
+BMI (kg/m2) & 22.6 (22.3, 22.8) & 27.3 (27.2, 27.5) & 33.7 (33.3, 34.2) & < 0.001 & 22.2 (22.0, 22.4) & 27.3 (27.2, 27.5) & 35.0 (34.6, 35.4) & < 0.001\\
+WC (cm) & 84.5 (83.6, 85.4) & 97.1 (96.4, 97.8) & 112.7 (111.6, 113.9) & < 0.001 & 76.9 (76.2, 77.5) & 89.0 (88.3, 89.7) & 103.7 (102.6, 104.7) & < 0.001\\
+Age (years) & 40.3 (38.2, 42.4) & 49.6 (47.9, 51.2) & 50.4 (48.5, 52.3) & < 0.001 & 45.0 (43.4, 46.7) & 50.4 (48.6, 52.3) & 50.9 (49.1, 52.7) & < 0.001\\
+Country (\%) &  &  &  & 0.236 &  &  &  & 0.589\\
+\hspace{1em}England & 83.9 (79.2, 87.7) & 86.9 (83.6, 89.7) & 81.6 (76.7, 85.7) &  & 84.3 (80.4, 87.5) & 83.7 (79.7, 87.0) & 82.4 (78.2, 85.9) & \\
+\hspace{1em}Northern Ireland & 3.3 (1.9, 5.8) & 2.3 (1.4, 3.6) & 3.2 (2.0, 4.9) &  & 3.0 (2.1, 4.2) & 2.2 (1.5, 3.2) & 3.4 (2.3, 5.0) & \\
+\hspace{1em}Scotland & 9.1 (6.1, 13.5) & 6.5 (4.4, 9.7) & 9.0 (5.9, 13.3) &  & 9.0 (6.1, 13.0) & 9.0 (6.3, 12.8) & 8.5 (5.7, 12.6) & \\
+\hspace{1em}Wales & 3.7 (2.3, 5.8) & 4.3 (3.1, 5.9) & 6.3 (4.0, 9.7) &  & 3.8 (2.9, 5.1) & 5.1 (3.6, 7.2) & 5.7 (4.2, 7.7) & \\
+Ethnicity (\%) &  &  &  & 0.466 &  &  &  & 0.879\\
+\hspace{1em}White & 88.7 (83.9, 92.2) & 89.1 (85.6, 91.9) & 91.9 (87.3, 94.9) &  & 88.4 (84.9, 91.19 & 88.6 (84.5, 91.7) & 87.3 (82.5, 90.9) & \\
+\hspace{1em}Non-white & 11.3 (7.8, 16.1) & 10.9 (8.1, 14.4) & 8.1 (5.1, 12.7) &  & 11.6 (8.9, 15.1) & 11.4 (8.3, 15.5) & 12.7 (9.1, 17.5) & \\
+Education (\%) &  &  &  & 0.022 &  &  &  & < 0.001\\
+\hspace{1em}Degree or higher & 29.5 (24.5, 35.0) & 28.3 (24.3, 32.7) & 20.1 (16.0, 25.0) &  & 35.7 (31.8, 39.8) & 24.2 (20.4, 28.4) & 19.4 (16.1, 23.2) & \\
+\hspace{1em}Lower than Degree & 70.5 (65.0, 75.5) & 71.7 (67.3, 75.7) & 79.9 (75.0, 84.0) &  & 64.3 (60.2, 68.2) & 75.8 (71.6, 79.6) & 80.6 (76.8, 83.9) & \\
+Smoking status &  &  &  & < 0.001 &  &  &  & 0.042\\
+Physical
+\hspace{1em}activity (hours/day) \textsuperscript{\dag} & 32.0  (26.8, 37.7) & 18.7 (15.5, 22.4) & 19.2 (15.0, 24.3) &  & 19.5 (16.4, 22.9) & 17.8 (14.8, 21.4) & 16.4 (13.1, 20.3) & \\
+\hspace{1em}Ex-smoker & 17.3 (13.5, 22.0) & 28.6 (24.8, 32.7) & 32.9 (27.9, 38.4) &  & 19.0 (15.9, 22.5) & 24.4 (20.8, 28.3) & 26.9 (22.8, 31.6) & \\
+\hspace{1em}Never & 50.6 (44.8, 56.4) & 52.7 (48.2, 57.1) & 47.9 (42.1, 53.7) &  & 61.6 (57.4, 65.5) & 57.8 (53.3, 62.2) & 56.7 (51.8, 61.4) & \\
+Physical activity (hours/day) & 1.58 (1.33, 1.85) & 1.42 (1.24, 1.62) & 1.41 (1.15, 1.70) & 0.547 & 0.84 (0.74, 0.94) & 0.71 (0.62, 0.79) & 0.65 (0.53, 0.78) & 0.038\\
+Carbohydrate eating patterns (\%) &  &  &  & 0.072 &  &  &  & 0.253\\
+\hspace{1em}Low & 25.9 (21.0, 31.5) & 30.6 (26.6, 35.0) & 31.4 (26.6, 36.6) &  & 24.8 (21.5, 28.5) & 26.8 (22.8, 31.2) & 29.5 (25.3, 34.1) & \\
+\hspace{1em}Moderate & 34.2 (28.6, 40.4) & 25.5 (21.9, 29.6) & 25.5 (20.6, 31.0) &  & 27.6 (23.8, 31.8) & 26.3 (22.3, 30.8) & 29.8 (25.4, 34.6) & \\
+\hspace{1em}High & 39.9 (34.2, 45.8) & 43.8 (39.6, 48.2) & 43.1 (37.7, 48.7) &  & 47.6 (43.3, 51.9) & 46.9 (42.4, 51.4) & 40.7 (36.0, 45.6) & \\
+Total energy intake (kJ) & 9351.2 (8961.7, 9740.7) & 8786.9 (8595.1, 8978.7) & 8465.3 (8196.4, 8734.1) & 0.001 & 7048.9 (6894.4, 7203.4) & 6570.1 (6406.2, 6734.0) & 6566.4 (6360.7, 6772.1) & < 0.001\\
+Carbohydrate intake (g) & 268.7 (258.3, 279.2) & 250.1 (244.1, 256.1) & 239.1 (231.3, 246.8) & < 0.001 & 205.8 (200.2, 211.3) & 190.1 (185.3, 194.9) & 189.8 (183.7, 195.9) & < 0.001\\
+\bottomrule
+\multicolumn{9}{l}{\textit{Note: }}\\
+\multicolumn{9}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
+\multicolumn{9}{l}{ BMI body mass index; WC, waist circumference.}\\
+\multicolumn{9}{l}{Variables are weighted by nurse visiting weights.}\\
+\multicolumn{9}{l}{\textsuperscript{*} Significant sex-specific differences by BMI categories assessed using an F test (with Bonferroni correction to account for multiple testing across \$>\$ 2 groups) for continuous variables or design-adjusted Pearson chi-square}\\
+\multicolumn{9}{l}{test}\\
+\multicolumn{9}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the survey.}\\
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
 \end{document}

### 2018-08-07 paper/Chapters/Chapter2.tex
want to figure out how to do model diagnosis

@@
 
-\subsection{Socio-demographic status, lifestyle, physical activity, anthropometric measurements and biochemical analysis}\vspace{-0.3cm}
+\subsection{Socio-demographic status, lifestyle, physical activity, anthropometric measurements and biochemical analyses}\vspace{-0.3cm}
 
@@
 \vspace{-0.5cm}
-\subsection{Non-Parametric approach}\vspace{-0.3cm}
+\subsubsection{Non-Parametric approach}\vspace{-0.3cm}
 
@@
 
-Multiple linear regression model (for WC), multinomial logistic regression model (for BMI categories), logistic regression models (for hypertension, and diabetes) were used to test for associations between individual level carbohydrate eating latent classes and WC, obesity, hypertension, and diabetes, separately.
+Associations between individual level carbohydrate eating classes and the prevalence of hypertension, obesity as well as diabetes were explored in men and women separately.
+Point estimates of weighted means and proportions and 95\%CI of the characteristics were determined by applying either nurse visiting weights (for outcomes of hypertension, BMI, and WC) or blood sample weights (for outcomes of DM) accordingly.
+Similarly, the \textit{F} test (for continuous variables) and adjusted Pearson $\chi^2$ test (for categorical variables) were used to determine sex-specific differences by hypertension status, BMI categories, and DM diagnosis.
 
-Model fitting strategies
+Logistic regression models (for hypertension, and diabetes), multinomial logistic regression model (for BMI categories), and linear regression model (for WC), were used to test for associations between individual level carbohydrate eating classes and hypertension, obesity, WC, and diabetes, separately.
+
+For the multiple regression models, model fitting strategies are as follows:
+
+\begin{enumerate}
+	\item The crude association between the carbohydrate eating groups and the outcomes was first examined. 
+	\item Potential confounders of the association between carbohydrate eater groups (exposure) and the outcomes were selected depending on the descriptive statisitics conducted above, ie.
+those are associated with both the exposure and the outcome and not on the causal pathway were selected as potential factors.
+	\item Confounding and/or interaction effect from each of the potential factors were checked one by one. 
+	\item A preliminary model that includes all of the variables suggested to be confounders in the previous step was established. 
+	\item The remaining variables were added to the preliminary model one by one to see if any of them may be a confounder in condition of the presence of the other covariates. 
+	\item For logistic regression models, Goodness-of-fit (calibration) was assessed using the adapted \code{svylogitgof} command in Stata \parencite{archer2006goodness}.
+Other diagnostics (residual check,  Quadratic and cubic polynomial functions of continuous variables (such as age) were also tested to allow for nonlinear effects of these covariates on the binary outcomes.
+
+	\item For linear regression model (WC), assumptions were checked visually by QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance).
+Outliers, leverage, and Cook's distance were checked visually to see if there may be 1) any extreme values of the dependent variable; 2) any points that have extreme values of the predictor variables; and 3) points which exert particular influence on the parameters of the fitted regression model.
+	\item Since likelihood ratio test is not appropriate under survey designed regression models, adjusted Wald test with $p < 0.05$ were used as criteria for variable inclusion in the final model. 
+\end{enumerate}
+
+Data manipulation and preparation \textbf{(Appendix \ref{AppendixA})} were done in R version 3.5.1 \parencite{R3.5.1}.
+All statistical analyses, except for MLCA models, were performed with "svyset" command as implemented in Stata software version 15.1 \parencite{stata15}.
+All \textit{P} values were two-sided.

### 2018-08-07 paper/Chapters/Chapter3.tex
want to figure out how to do model diagnosis

@@
 Entropy index indicates that the 4 classes model could explain about 51\% percent of the data, while \textit{p} values of Lo-Mendell-Rubun LRT suggest that the more classes we fit, the better model we will have until up to 6 classes (\textit{p} = 0.06 and is not shown in the table).
-However, from the parsimony point of view, we extend the model with random effects building on 2 classes, 3 classes and 4 classes solutions.
+From the parsimony point of view, we extended the model with random effects building on 2 classes, 3 classes and 4 classes solutions.
 
@@
 
-In this 3 classes solution we have chosen in the day level, there were 39.5\%, 20.4\%, and 40.1\% classified into 3 latent groups.
+In the 3$\times$3 random effect model solution we have chosen, there were 39.5\%, 20.4\%, and 40.1\% observations classified into 3 latent groups in the day level.
 The overall counts and percentages for each responses within every time slot and the distributions of the solution are presented in \textbf{Table \ref{tab:daylevel}}.
@@
 Class 1 days \textbf{(Figure \ref{fig:level1}-A)} were given the name of "high carbohydrate day" since in these days of survey, the probabilities of carbohydrate contributed higher or equal to 50\% of the energy consumed were always higher than that in the other two types of days.
-Specifically, these days were characterised with probabilities of over 0.6 in time slots between 6 am to 9 am, 9 am to 12 am, and also 2 pm to 5 pm, during which the time slots may be interpreted as breakfast, morning snack, and afternoon snack time periods for many participants.
+Specifically, high carbohydrate days were characterised with probabilities of over 0.6 in time slots between 6 am to 9 am, 9 am to 12 am, and also 2 pm to 5 pm, during which the time slots may be interpreted as breakfast, morning snack, and afternoon snack time periods for many participants.
 Moreover, even during late night time period, such as 8 pm to 10 pm, and 10 pm to 6 am time slots, the probabilities of having higher carbohydrate contained food were still as high as 0.412, and 0.246, respectively.
@@
 Class 2 days \textbf{(Figure \ref{fig:level1}-B)} were named as "low carbohydrate day" because first of all, in these days the possibility of participants skipping breakfast was 0.45.
-And after 9 am, within class 2 days, the probability of having food with lower carbohydrate (contributed less than 50\% of total energy intake), was always higher than having higher carbohydrate contained food.
-In these days, participants also turned to have morning snacks (with only 0.079 possibility of Not eating any food and similar probabilities of having either high or low carbohydrate contained food).
-This phenomenon may also be interpreted as having a long and late breakfast in these mornings.
-The probability of Not eating any food was lowest for class 2 days during the midnights time slot (10 pm to 6 am), with about 0.590 compared with 0.680 and 0.751 during the class 1 and class 3 days.
+And after 9 am, within low carbohydrate days, the probability of having food contained lower carbohydrate (contributed less than 50\% of total energy intake), was always higher than having higher carbohydrate contained food.
+In these days, participants also turned to have morning snacks (with only 0.079 possibility of not eating any food and similar probabilities of having either high or low carbohydrate contained food).
+This phenomenon may also be interpreted as having a long and late breakfast (brunch) in these mornings.
+The probability of not eating any food was the lowest for low carbohydrate days during the midnight time slot (10 pm to 6 am), with probability of 0.590 compared with 0.680 and 0.751 in the class 1 and class 3 days, respectively.
 
@@
 
-Class 3 days \textbf{(Figure \ref{fig:level1}-C)} were called "regular meals day" due to the following reasons: 1) participants recordings showed that in these days there was almost 0 possibility of not eating any food at lunch (0.019 between 12 noon and 2 pm) or dinner (0.034 between 5 pm and 8 pm); 2) the probabilities of not having morning snack (9 am to 12 am) and afternoon snack (2 pm to 5 pm) were also the highest among the three types of days (0.401 and 0.659).
+Class 3 days \textbf{(Figure \ref{fig:level1}-C)} were called "regular meals day" due to the following reasons: 1) participants' dietary recordings showed that in these days there was almost 0 possibility of not eating any food at lunch (0.019 between 12 noon and 2 pm) and dinner (0.034 between 5 pm and 8 pm); 2) the probabilities of not eating during morning snack time (9 am to 12 am) and afternoon snack time (2 pm to 5 pm) were also the highest among the three types of days (0.401 and 0.659).
 3) during these days, participants may have some high carbohydrate contained food between 8 pm and 10 pm (0.308), but the probability of not eating any food during 10 pm to 6 am next morning was 0.751, the highest among the three types of days.
@@
 
-As expected, consumption of total energy (7539.98 kJ), total carbohydrate (222.79 g), total sugar (98.63 g), starch (124.07 g), and non-milk extrinsic sugar (59.45 g) were highest among high carbohydrate days (all \textit{p} < 0.0001).
+As expected, consumption of total energy (7539.98 kJ), total carbohydrate (222.79 g), total sugar (98.63 g), starch (124.07 g), and non-milk extrinsic sugar (59.45 g) were highest among high carbohydrate days (all \textit{p} < 0.001).
 On the other hand, the consumption of protein (73.29 g), total fat (67.24 g), and alcohol (13.80 g) were the highest in the so-called regular meals days.
-Moreover, in high carbohydrate days, participants turned to also consume the highest amount of fruit (107.40 g).
+Moreover, in high carbohydrate days, participants turned to consume the highest amount of fruit (107.40 g).
 There was no evidence of any difference for the consumption of yellow, red, or green vegetables across the three types of days (\textit{p} = 0.681).
@@
 With three individual level latent classes \textbf{(Figure \ref{fig:level2})}, a low-carbohydrate eaters class, a moderate-carbohydrate eaters class, and a high-carbohydrate eaters class emerges.
-43.1\% participants were identified as high-carbohydrate eaters, in these individuals, about 50\% of the days (2 out of 4 days) of their dietary diary were classified as having high carbohydrate days.
+43.1\% participants were identified as high-carbohydrate eaters, in these individuals, about 50\% of the days (2 out of 4 days) of their dietary diary could be classified as having high carbohydrate days.
 Nearly 1 out of 4 days of their dietary diary were either "regular meals day" or "low carbohydrate day".
 28.1\% participants fell into the low carbohydrate eaters class in the left hand side of \textbf{Figure \ref{fig:level2}}, their recordings of food intake showed that in more than 60\% of their days, they were having "regular meals" which was characterised as with highest amount of fat and alcohol consumptions as already described in \textbf{Table \ref{tab:day-level-features}}.
+Moderate carbohydrate eaters have comparable proportions (42.0\% vs.
+40.0\%) of having high carbohydrate days and regular meals day, 18.0\% of their dietary diary were identified as low carbohydrate days.
 
@@
 Moderate carbohydrate eaters were relatively younger (\textit{p} < 0.001), and slightly less from England (\textit{p} = 0.007).
-Gender distribution across the three types of carbohydrate eaters were fairly even (\textit{p} = 0.119).
-Distribution of the carbohydrate eater types was changing with the year of survey.
+Gender distribution across the three types of carbohydrate eaters was fairly even (\textit{p} = 0.119).
+Distribution of the carbohydrate eater types turned out to be changing with the year of survey.
 Low carbohydrate eaters represented 32.5\% of the population in the first year of survey, but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year.
 Proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year of the survey, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015).
-There was no evidence of
+There was no evidence of difference in employment status across three types of carbohydrate eaters.
+However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with a partner (\textit{p} < 0.001); moderate carbohydrate eaters had the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.
+
+Weighted means, percentages of anthropometric measurements, average of main nutrients intake, as well as biochemical characteristic profiles according to the latent carbohydrate eater groups are given in \textbf{Table \ref{tab:tab2}}.
+Low carbohydrate eaters had higher mean BMI (27.8 kg/m\textsuperscript{2}) and larger mean WC (98.9/89.9 cm in men/women) compared with 27.2, 27.3 kg/m\textsuperscript{2}, and 95.9/88.7 (men/women), 98.1/87.2 (men/women) cm in moderate and high carbohydrate eaters.
+Moderate carbohydrate eaters had the highest prevalence of being a current smoker (27.8\%), shortest time of daily physical activity (geometric mean: 0.87 hours/day), and the lowest prevalence of hypertension (20.2\%).
+
+Average total energy intake over the 4 days of dietary survey was the highest (7985.8 kJ) in the low carbohydrate eaters group.
+As expected, the mean of total carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively.
+Energy contribution from carbohydrate was close to 50\% in the high carbohydrate eaters, but was only 40.6\% in the low carbohydrate eaters.
+It is noteworthy that low carbohydrate eaters consumed the highest average amount of protein (79.9 g, 17.2\% of total energy), fat (74.7g, 35.4\% of total energy), and alcohol (20.8 g, 6.8\% of total energy).
+
+From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetic (diagnosed by A1C > 6.5\%), while the percentages of diabetes in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011), respectively.
+Although there was some evidence (\textit{p} = 0.027) that fasting blood glucose level may be slightly higher in non-diabetic low carbohydrate eaters, the geometric mean for A1C was probably lower in moderate carbohydrate eaters (4.72, 95\%CI: 5.39, 5.47).
+Cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.
 
@@
 \caption{\label{tab:Level2tab1}Weighted means, percentages, and
-95\% CIs of the social-demographic characteristics by latent class memberships in the UK
-adults. (NDNS RP 2008/09-2015/16, sample size = 6155)} \centering
+95\% CIs of the social-demographic characteristics by carbohydrate eating latent class memberships in the UK
+adults. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)} \centering
 \fontsize{9}{11}\selectfont
@@
 	\hspace{1em}No & 43.1 (39.9, 46.4) & 61.6 (58.2, 64.8)) & 38.7 (36.3, 41,3) & \\
-	Household Income, \textsterling/year & \Centerstack{36558.5\\(34800.2, 38316.8)} & \Centerstack{27180.8\\(25597.9, 28763.7)} & \Centerstack{32171.6\\(31024.9, 33318.2)} & < 0.001\\
+	Household income, \textsterling/year & \Centerstack{36558.5\\(34800.2, 38316.8)} & \Centerstack{27180.8\\(25597.9, 28763.7)} & \Centerstack{32171.6\\(31024.9, 33318.2)} & < 0.001\\
 	Ethnicity (\%) &  &  &  & \\
@@
 
-difference in employment status across three types of carbohydrate eaters.
-However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with a partner (\textit{p} < 0.001); moderate carbohydrate eaters had the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.
-
-Weighted means, percentages of anthropometric measurements, average of main nutrient intake, as well as biochemical characteristic profiles of latent carbohydrate eater groups are given in \textbf{Table \ref{tab:tab2}}.
-Low carbohydrate eaters were with higher BMI (27.8 kg/m\textsuperscript{2}) and larger WC (98.9/89.9 cm in men/women) compared with 27.2, 27.3 kg/m\textsuperscript{2}, and 95.9/88.7 (men/women), 98.1/87.2 (men/women) cm in moderate and high carbohydrate eaters.
-Moderate carbohydrate eaters had the highest prevalence of being a current smoker (27.8\%), shortest physical activity (geometric mean: 0.87 hours/day), and the lowest prevalence of hypertension (20.2\%).
-
-Average total energy intake over the 4 days of dietary survey was the highest (7985.8 kJ) in the low carbohydrate eaters group.
-As expected, the mean total carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively.
-Energy contribution from carbohydrate was close to 50\% in the high carbohydrate eaters, but was only 40.6\% in the low carbohydrate eaters.
-It is noteworthy that low carbohydrate eaters consumed the highest average amount of protein (79.9 g, 17.2\% of total energy), fat (74.7g, 35.4\% of total energy), and alcohol (20.8 g, 6.8\% of total energy).
-
-From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetes (diagnosed by A1C > 6.5\%), while the percentages of diabetes in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011).
-There were some evidence (\textit{p} = 0.027) that fasting blood glucose level may be slightly higher in non-diabetes low carbohydrate eaters, while the geometric mean for A1C was probably lower in moderate carbohydrate eaters (4.72, 95\%CI: 5.39, 5.47).
-Cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.
-
 \rowcolors{2}{gray!6}{white}
@@
 
-	\caption{\label{tab:tab2}Weighted means, percentages, and 95\% CIs of the anthropometric measurements, average main nutrients intake and biochemical characteristics by latent class memberships in the UK adults.
-\\(NDNS RP 2008/09-2015/16, sample size = 6155).}
+	\caption{\label{tab:tab2}Weighted means, percentages, and 95\% CIs of the anthropometric measurements, average main nutrients intake and biochemical characteristics by carbohydrate eating latent class memberships in the UK adults.
+(NDNS RP 2008/09-2015/16, sample size = 6155)}
 	\centering
@@
 		\hspace{1em}Lower than Degree & 69.7 (65.8, 73.4) & 78.5 (73.5, 82.7) &  & 67.0 (63.7, 70.1) & 80.3 (75.7, 84.2) & \\
+		Household income,\textsterling/year & 34006.5 (31972.9, 36040.1) & 32280.5 (29875.6, 34685.4) & 0.284 &  32741.5 (31009.9, 34473.1) & 27862.0 (25557.0, 30167.0)  &  < 0.001  \\
+		Live with partner\textsuperscript{\ddag}, Yes, (\%) & 56.1 (51.8, 61.4) & 66.6 (61.3, 71.5) & 0.002   & 48.7 (45.1, 52.3) & 58.9 (53.6, 63.9)  & 0.002    \\
 		Smoking status &  &  & < 0.001 &  &  & < 0.001\\
@@
 		WC (cm) & 95.0 (93.9, 96.2) & 104.6 (103.2, 106.1) & < 0.001 & 85.7 (84.8, 86.6) & 95.7 (94.2, 97.2) & < 0.001\\
+		DM\textsuperscript{\S} (\%) & 3.7 (2.4, 5.7) & 12.6 (8.9, 17.5) & < 0.001 & 1.8 (1.0, 3.3) & 7.9 (5.1, 11.9) & < 0.001 \\ 
 		Carbohydrate eating patterns (\%) &  &  & < 0.001 &  &  & < 0.001\\
@@
 		\multicolumn{7}{l}{\textsuperscript{*} Significant sex-specific differences by hypertension status assessed using an \textit{F} test for continuous variables or design-adjusted Pearson $\chi^2$ test.}\\
+		\multicolumn{7}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership.}\\
 		\multicolumn{7}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}\\
+		\multicolumn{7}{l}{\textsuperscript{\S}  DM was defined by A1C $>$ 6.5\%.}
 	\end{tabular}

### 2018-08-07 paper/main.tex
tab1 hyper tab1 BMi
want to figure out how to do model diagnosis

@@
 \usepackage{amssymb} % to use \leqslant
+\usepackage[clockwise]{rotating} % to rotate pages for wide tables
 %----------------------------------------------------------------------------------------
@@
 
-\thesistitle{The timing of carbohydrate intake in UK adults, using the National Dietary and Nutrition Survey (NDNS) 2008/09-2015/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+\thesistitle{The time patterns of carbohydrate intake in UK adults, using the National Dietary and Nutrition Survey (NDNS) 2008/09-2015/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
 \supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
@@
 \usepackage{color}
+%\usepackage{xcolor}
+%\definecolor{light-gray}{gray}{0.95}
+%\newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}
 

### 2018-08-08 Rcode/Surveyregression.R
try to do survey regression in R

@@ -1,0 +1,11 @@
+library(haven)
+CW3CB3_7regss <- read_dta("Rcode/CW3CB3_7regss.dta")
+library(survey)
+
+
+NDNSsvy <- svydesign(id = ~area, strat = ~gor, 
+                     weights=~wtn1to8, data = CW3CB3_7regss, nest = TRUE)
+# area and gor are the PSU and stratum identifiers
+# nest = TRUE is used to indicate that the PSU identifier needs to be 
+# interpreted as nested within stratum. (same PSU id is recycled in different strata)
+

### 2018-08-08 paper/Chapters/Chapter2.tex
some svyregress with BMI Waist

@@
 
-Logistic regression models (for hypertension, and diabetes), multinomial logistic regression model (for BMI categories), and linear regression model (for WC), were used to test for associations between individual level carbohydrate eating classes and hypertension, obesity, WC, and diabetes, separately.
+%multinomial logistic regression model (for BMI categories),
+
+Logistic regression models (for hypertension, and diabetes), and linear regression model (for WC, BMI), were used to test for associations between individual level carbohydrate eating classes and hypertension, diabetes, obesity, and WC, separately.
 
@@
 	\item Potential confounders of the association between carbohydrate eater groups (exposure) and the outcomes were selected depending on the descriptive statisitics conducted above, ie.
-those are associated with both the exposure and the outcome and not on the causal pathway were selected as potential factors.
+those are associated with both the exposure and the outcome and not on the causal pathway were selected as potential confounders.
+Those are strongly related with the outcomes but may not associated with carbohydrate eating groups may reduce the standard errors and so improve the precisions are also considered.
 	\item Confounding and/or interaction effect from each of the potential factors were checked one by one. 
@@
 	\item The remaining variables were added to the preliminary model one by one to see if any of them may be a confounder in condition of the presence of the other covariates. 
-	\item For logistic regression models, Goodness-of-fit (calibration) was assessed using the adapted \code{svylogitgof} command in Stata \parencite{archer2006goodness}.
-Other diagnostics (residual check,  Quadratic and cubic polynomial functions of continuous variables (such as age) were also tested to allow for nonlinear effects of these covariates on the binary outcomes.
-
-	\item For linear regression model (WC), assumptions were checked visually by QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance).
-Outliers, leverage, and Cook's distance were checked visually to see if there may be 1) any extreme values of the dependent variable; 2) any points that have extreme values of the predictor variables; and 3) points which exert particular influence on the parameters of the fitted regression model.
-	\item Since likelihood ratio test is not appropriate under survey designed regression models, adjusted Wald test with $p < 0.05$ were used as criteria for variable inclusion in the final model. 
+	\item For logistic regression models under survey data, goodness-of-fit (calibration) was assessed using the adapted \code{svylogitgof} command in Stata \parencite{archer2006goodness}.
+Other diagnostics for regular logistic regression models, such as estimating the pseudo-R\textsuperscript{2},  AIC or BIC, checking the standardized Pearson residuals, or covariate pattern residuals are currently not available for weighted survey data.
+	\item For linear regression models (WC, BMI), assumption of independent observations is violated as soon as we weighted the sample.
+General checking such as QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance) are not available as well.
+Outliers, leverage, and Cook's distance cannot be check either, however, samples with extreme weightings (if exist) are checked by removing them and refit the models as a sensitivity analysis.
+	\item Since under survey design data, the sampling-weighted least squares are not maximum likelihood, it would not be possible to compare models using likelihood ratio test.
+Instead, adjusted Wald tests with $p < 0.05$ were used as criteria for variable inclusion in the final model, and a useful tool to decide whether quadratic and cubic terms of continuous variables are necessary in improving the fitting of model.
 \end{enumerate}
@@
 Data manipulation and preparation \textbf{(Appendix \ref{AppendixA})} were done in R version 3.5.1 \parencite{R3.5.1}.
-All statistical analyses, except for MLCA models, were performed with "svyset" command as implemented in Stata software version 15.1 \parencite{stata15}.
-All \textit{P} values were two-sided.
+All statistical analyses, except for MLCA models, were performed with \code{svyset} command as implemented in Stata software version 15.1 \parencite{stata15}.
+All \textit{p} values were two-sided.

### 2018-08-08 paper/Chapters/Chapter3.tex
some svyregress with BMI Waist

@@
 		\multicolumn{7}{l}{\textit{Note: }}\\
-		\multicolumn{7}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
-		\multicolumn{7}{l}{ BMI body mass index; WC, waist circumference.}\\
+		\multicolumn{7}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}\\
 		\multicolumn{7}{l}{Variables are weighted by nurse visiting weights.}\\
@@
 		\centering
-		\fontsize{9}{11}\selectfont
+		\fontsize{8}{11}\selectfont
 		\begin{tabular}[t]{lcccccccc}
@@
 			\hspace{1em}Lower than Degree & 70.5 (65.0, 75.5) & 71.7 (67.3, 75.7) & 79.9 (75.0, 84.0) &  & 64.3 (60.2, 68.2) & 75.8 (71.6, 79.6) & 80.6 (76.8, 83.9) & \\
+            Household income, \textsterling/year & \Centerstack{33695.9 \\ (30462.3, 36929.7)} & \Centerstack{35059.6 \\ (32949.7, 37169.5)} & \Centerstack{30295.5 \\ (27948.5, 32642.6)} & 0.011 & \Centerstack{34594.1 \\ (32326.8, 36861.4)} & \Centerstack{29777.7 \\ (27808.3, 31747.2)} & \Centerstack{27230.6\\ (25259.1, 29202.0)} & < 0.001 \\
+            Live with partner\textsuperscript{\ddag}, Yes, (\%) & 40.3 (34.8, 46.1) & 65.3 (60.8, 69.6) & 65.6 (60.1, 70.8) & < 0.001 & 47.6 (43.2, 52.1) & 52.2 (47.5, 57.0) & 51.7 (46.7, 56.6) & 0.288 \\
 			Smoking status &  &  &  & < 0.001 &  &  &  & 0.042\\
@@
 			\multicolumn{9}{l}{\textit{Note: }}\\
-			\multicolumn{9}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
-			\multicolumn{9}{l}{ BMI body mass index; WC, waist circumference.}\\
+			\multicolumn{9}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}\\
 			\multicolumn{9}{l}{Variables are weighted by nurse visiting weights.}\\
-			\multicolumn{9}{l}{\textsuperscript{*} Significant sex-specific differences by BMI categories assessed using an F test (with Bonferroni correction to account for multiple testing across $>$ 2 groups)} \\
-			\multicolumn{9}{l}{for continuous variables or design-adjusted Pearson $\chi^2$ test}\\
+			\multicolumn{9}{l}{\textsuperscript{*} Significant sex-specific differences by BMI categories assessed using an \textit{F} test (with Bonferroni correction to account for multiple testing across $>$ 2 groups)} \\
+			\multicolumn{9}{l}{for continuous variables or design-adjusted Pearson $\chi^2$ test for categorical variables}\\
+			\multicolumn{9}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership.}\\
 			\multicolumn{9}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}\\

### 2018-08-08 Rcode/Surveyregression.R

@@ -9,3 +9,58 @@ NDNSsvy <- svydesign(id = ~area, strat = ~gor,
 # nest = TRUE is used to indicate that the PSU identifier needs to be 
 # interpreted as nested within stratum. (same PSU id is recycled in different strata)
 
+svymean(~age, subset(NDNSsvy, Sex == 1))
+
+
+# hypertension binomial ---------------------------------------------------
+
+m <- svyglm(hibp140_2 ~ factor(CB), design = subset(NDNSsvy, Sex == 1), 
+            family = quasibinomial())
+summary(m)
+
+
+# BMI(cont.) linear regression --------------------------------------------
+
+m.BMI <- svyglm(bmival ~  age, subset(NDNSsvy, Sex == 1))
+summary(m.BMI)
+nonmissing <- NDNSsvy[m.BMI$na.action]
+plot(m.BMI, panel = make.panel.svysmooth(nonmissing),
+     partial = TRUE, se = TRUE, 
+     smooth = make.panel.svysmooth(nonmissing))
+plot(svysmooth(bmival ~ age, subset(NDNSsvy, Sex == 1)))
+
+lines(svysmooth(bmival ~ age, subset(NDNSsvy, Sex == 2)))
+
+f.BMI <- svyglm(bmival ~ factor(CB) + age, subset(NDNSsvy, Sex == 2))
+summary(f.BMI)
+
+plot(m.BMI)
+
+
+
+# survey plots ------------------------------------------------------------
+
+svyboxplot(bmival~factor(CB), subset(NDNSsvy, Sex == 1), col="gray80",
+           varwidth=TRUE, ylab="Body mass index (kg/m^2)",
+           xlab="Carbohydrate eaters groups")
+svyboxplot(bmival~factor(CB), subset(NDNSsvy, Sex == 2), col="gray80",
+           varwidth=TRUE, ylab="Body mass index (kg/m^2)",
+           xlab="Carbohydrate eaters groups")
+svyboxplot(wstval~factor(CB), subset(NDNSsvy, Sex == 1), col="gray80",
+           varwidth=TRUE, ylab="Body mass index (kg/m^2)",
+           xlab="Carbohydrate eaters groups")
+
+svyboxplot(wstval~factor(CB), subset(NDNSsvy, Sex == 2), col="gray80",
[…]

### 2018-08-09 paper/Chapters/Chapter3.tex
regression table added

@@
 		\bottomrule
-		\multicolumn{7}{l}{\textit{Note: }}\\
-		\multicolumn{7}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}\\
-		\multicolumn{7}{l}{Variables are weighted by nurse visiting weights.}\\
-		\multicolumn{7}{l}{\textsuperscript{*} Significant sex-specific differences by hypertension status assessed using an \textit{F} test for continuous variables or design-adjusted Pearson $\chi^2$ test.}\\
-		\multicolumn{7}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership.}\\
-		\multicolumn{7}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}\\
-		\multicolumn{7}{l}{\textsuperscript{\S}  DM was defined by A1C $>$ 6.5\%.}
+		\multicolumn{7}{l}{{\scriptsize \textit{Note: }}}\\
+		\multicolumn{7}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}}\\
+		\multicolumn{7}{l}{{\scriptsize Variables are weighted by nurse visiting weights.}}\\
+		\multicolumn{7}{l}{{\scriptsize \textsuperscript{*} Significant sex-specific differences by hypertension status assessed using an \textit{F} test for continuous variables or design-adjusted Pearson $\chi^2$ test.}}\\
+		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership.}}\\
+		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}}\\
+		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\S}  DM was defined by A1C $>$ 6.5\%.}}
 	\end{tabular}
@@
 			\bottomrule
-			\multicolumn{9}{l}{\textit{Note: }}\\
-			\multicolumn{9}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}\\
-			\multicolumn{9}{l}{Variables are weighted by nurse visiting weights.}\\
-			\multicolumn{9}{l}{\textsuperscript{*} Significant sex-specific differences by BMI categories assessed using an \textit{F} test (with Bonferroni correction to account for multiple testing across $>$ 2 groups)} \\
-			\multicolumn{9}{l}{for continuous variables or design-adjusted Pearson $\chi^2$ test for categorical variables}\\
-			\multicolumn{9}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership.}\\
-			\multicolumn{9}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}\\
+			\multicolumn{9}{l}{{\scriptsize \textit{Note: }}}\\
+			\multicolumn{9}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}}\\
+			\multicolumn{9}{l}{{\scriptsize Variables are weighted by nurse visiting weights.}}\\
+			\multicolumn{9}{l}{{\scriptsize \textsuperscript{*} Significant sex-specific differences by BMI categories assessed using an \textit{F} test (with Bonferroni correction to account for multiple testing across $>$ 2 groups)}} \\
+			\multicolumn{9}{l}{{\scriptsize for continuous variables or design-adjusted Pearson $\chi^2$ test for categorical variables}}\\
+			\multicolumn{9}{l}{{\scriptsize \textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership.}}\\
+			\multicolumn{9}{l}{{\scriptsize \textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}}\\
 		\end{tabular}
@@
 	\rowcolors{2}{white}{white}
+\end{sidewaystable}
+
+\begin{sidewaystable}
+	\rowcolors{2}{gray!6}{white}
+
+%	\begin{table}
+
+		\caption{\label{tab:survgression}Associations of carbohydrate eating patterns with hypertension, BMI, WC, and DM in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
+		\centering
+		\fontsize{8}{11}\selectfont
+		\begin{tabular}[t]{lccccccccccc}
+			\hiderowcolors
+			\toprule
+			\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Men (n = 2537)} & \multicolumn{6}{c}{Women (n = 3618)} \\
+			\cmidrule(l{2pt}r{2pt}){2-6} \cmidrule(l{2pt}r{2pt}){7-12}
+			Models & Low & Moderate & P value\textsuperscript{*} & High & P value & Models & Low & Moderate & P value & High & P value\\
+			\midrule
+			\showrowcolors
+			\addlinespace[0.3em]
+			\multicolumn{12}{l}{\textbf{Hypertension}}\\
+			\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217 & Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
+			\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227 & Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
+			\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124 & Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
+			\addlinespace[0.3em]
+			\multicolumn{12}{l}{\textbf{Hypertension in non-diabetics}}\\
+			\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241 & Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
+			\hspace{1em}Model 1 & 1 & 0.69 (0.43, 1.09) & 0.11 & 0.78 (0.54, 1.14) & 0.197 & Model 1 & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
+			\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096 & Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
+			\addlinespace[0.3em]
+			\multicolumn{12}{l}{\textbf{BMI}}\\
+			\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426 & Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
+			\hspace{1em}Model 1\textsuperscript{\S} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0,43 (-1.13, 0.26) & 0.22 & Live with partner\textsuperscript{\P} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
+			\hspace{1em} &  &  &  &  &  & Live alone & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
+			\addlinespace[0.3em]
+			\multicolumn{12}{l}{\textbf{BMI in non-diabetics}}\\
+			\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557 & Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.04\\
+			\hspace{1em}Model 1 & -- & -0.10 (-0.97, 0.77) & 0.82 & -0.39 (-1.10, 0.31) & 0.269 & Live with partner & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
+			\hspace{1em} &  &  &  &  &  & Live alone & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
+			\addlinespace[0.3em]
+			\multicolumn{12}{l}{\textbf{WC}}\\
+			\hspace{1em}Crude model & -- & -3.00 (-5.49, -0.52) & 0.018 & -0.90 (-2.84, 1.04) & 0.364 & Crude model & -- & -1.28 (-3.26, 0.70) & 0.206 & -2.81 (-4.50, -1.12) & 0.001\\
+			\hspace{1em}Model 1\textsuperscript{**} & -- & 1.06 (-1.50, 3.64) & 0.415 & -1.55 (-3.42, 0.31) & 0.103 & Live with partner\textsuperscript{\dag\dag} & -- & 0.28 (-2.85, 3.41) & 0.861 & -4.71 (-7.00, -2.43) & < 0.001\\
+			\hspace{1em} &  &  &  &  &  & Live alone & -- & 3.17 (0.05, 6.30) & 0.047 & 0.73 (-1.84, 3.30) & 0.577\\
+			\addlinespace[0.3em]
+			\multicolumn{12}{l}{\textbf{WC in non-diabetics}}\\
+			\hspace{1em}Crude model & -- & -2.51 (-5.00, -0.21) & 0.048 & -0.51 (-2.47, 1.44) & 0.606 & Crude model & -- & -0.91 (-2.88, 1.07) & 0.368 & -2.41 (-4.06, -0.76) & 0.004\\
+			\hspace{1em}Model 1 & -- & 1.42 (-1.17, 4.01) & 0.283 & -1.29 (-3.18, 0.60) & 0.181 & Live with partner & -- & 1.11 (-2.02, 4.23) & 0.487 & -3.74 (-5.97, -1.51) & 0.001\\
+			\hspace{1em} &  &  &  &  &  & Live alone & -- & 3.08 (-0.09, 6.25) & 0.057 & 0.16 (-2.36, 2.69) & 0.899\\
+			\addlinespace[0.3em]
+			\multicolumn{12}{l}{\textbf{DM}}\\
+			\hspace{1em}Crude model & 1 & 0.39 (0.18, 0.83) & 0.016 & 0.78 (0.43, 1.42) & 0.416 & Crude model & 1 & 0.65 (0.28, 1.47) & 0.296 & 0.38 (0.18, 0.81) & 0.013\\
+			\hspace{1em}Model 1\textsuperscript{\ddag\ddag} & 1 & 0.27 (0.10, 0.73) & 0.012 & 0.78 (0.36, 1.68) & 0.529 & Model 1\textsuperscript{\S\S} & 1 & 1.05 (0.33, 3.35) & 0.928 & 0.52 (0.17, 1.59) & 0.255\\
+			\hspace{1em}Model 2 & 1 & 0.27 (0.10, 0.76) & 0.013 & 0.76 (0.35, 1.65) & 0.493 & Model 2 & 1 & 0.79 (0.25, 2.46) & 0.686 & 0.48 (0.18, 1.32) & 0.155\\
+			\bottomrule
+			\multicolumn{12}{l}{{\scriptsize \textit{Note: }}}\\
+			\multicolumn{12}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
+			\multicolumn{12}{l}{{\scriptsize DM was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the same with the corresponding Model 1s.}}\\
+			\multicolumn{12}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from either linear regression models or logistic regression models.}}\\
+			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or not, BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);}}\\
+			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);}}\\
+			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\S} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol consumption;}}\\
+			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\P} Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;}}\\
+			\multicolumn{12}{l}{{\scriptsize \textsuperscript{**} Adjusted for age, live with partner or not, average household income, education level, hypertension, smoking, total energy intake, alcohol consumption;}}\\
+			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\dag\dag} Adjusted for age, live with partner or not, education level, hypertension, total energy intake, alcoho consumpiont;}}\\
+			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\ddag\ddag} Adjusted for age, average household income, education level, BMI, hypertension, smoking status, total energy intake, ethnicity (white or non-white), alcohol consumption,}}\\
+			\multicolumn{12}{l}{{\scriptsize TC (mmol/l), LDL (mmol/l), HDL (mmol/l), TG (mmol/l);}}\\
+			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\S\S} Adjusted for age, education level, BMI, hypertension, smoking status, total energy intake, alcohol consumption, TC, LDL, HDL, TG.}}\\
+		\end{tabular}
+%	\end{table}
+
+	\rowcolors{2}{white}{white}
+
 \end{sidewaystable}

### 2018-08-09 paper/Tables/2by2Table1.Rmd
regression table added

@@
 kable(dt,  align = "l", row.names = FALSE,
-              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
+              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by BMI status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
  kable_styling(latex_options = c("striped"), font_size = 9) %>% 
@@
 
-```{r tab1BMI, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/BMItab1.csv", header = T, row.names = NULL, colClasses = "character")
-names(dt) <- c(" ", "Normal weight", "Overweight", "Obese", "P value[note]", "Normal weight", "Overweight", "Obese", "P value")
+```{r tab1DM, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/DMtab1.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c(" ", "Non-diabetes", "Diabetes", "P value[note]", 
+               "Non-diabetes", "Diabetes", "P value")
 
@@
 
-dt[17, 1] <- c("Physical\nactivity (hours/day) [note]")
+dt[18, 1] <- c("Physical\nactivity (hours/day) [note]")
 # dt[20, 1] <- c("DM [note]")
@@
 kable(dt,  align = "l", row.names = FALSE,
-              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
+              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by diabetic status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
  kable_styling(latex_options = c("striped"), font_size = 9) %>% 
-  add_indent(c(6:9, 11,12, 14,15, 17:19, 22:24)) %>% 
-   add_header_above(c(" ", "Men (n = 2537)" = 4, "Women (n = 3618)" = 4)) %>% 
+  add_indent(c(6:7, 9, 10, 12, 13, 15:17, 22:24)) %>% 
+   add_header_above(c(" ", "Men (n = 2537)" = 3, "Women (n = 3618)" = 3)) %>% 
   footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;",  
@@
                        "Variables are weighted by nurse visiting weights.")) %>% 
-  add_footnote(c("Significant sex-specific differences by BMI categories assessed using an F test (with Bonferroni correction to account for multiple testing across $>$ 2 groups) for continuous variables or design-adjusted Pearson chi-square test",
+  add_footnote(c("Significant sex-specific differences by diabetic status assessed using an F test (with Bonferroni correction to account for multiple testing across $>$ 2 groups) for continuous variables or design-adjusted Pearson chi-square test",
                  # "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
@@
 ```
+
+## Table 2 regressions in survey
+
+```{r survgression, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/SurveyReg.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c("Models", "Low", "Moderate", "P value[note]", "High", "P value", "Models", "Low", "Moderate", "P value", "High", "P value")
+dt[2, 1] <- c("Model 1[note]")
+dt[2, 7] <- c("Model 1[note]")
+dt[8, 1] <- c("Model 1[note]")
+dt[8, 7] <- c("Live with partner[note]")
+dt[14, 1] <- c("Model 1[note]")
+dt[14, 7] <- c("Live with partner[note]")
+dt[20, 1] <- c("Model 1[note]")
+dt[20, 7] <- c("Model 1[note]")
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "Associations of carbohydrate eating patterns with hypertension, BMI, WC, and DM in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
+ kable_styling(latex_options = c("striped"), font_size = 9) %>%
+  group_rows("Hypertension", 1, 3) %>%
+  group_rows("Hypertension in non-diabetics", 4, 6) %>% 
+  group_rows("BMI", 7, 9) %>%
+  group_rows("BMI in non-diabetics", 10, 12) %>%
+    group_rows("WC", 13, 15) %>%
+  group_rows("WC in non-diabetics", 16, 18) %>%
+  group_rows("DM", 19, 21) %>%
+   add_header_above(c(" ", "Men (n = 2537)" = 5, "Women (n = 3618)" = 6)) %>% 
+  footnote(general = c("Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.",
+                       "DM was defined by A1C > 6.5%. BMI was replaced with WC in Model 2s, other covariates remained the same with the corresponding Model 1s.")) %>% 
+  add_footnote(c("P values were obtained from wald tests from either linear regression models or logistic regression models.",
+                "Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or not, BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);",
+                "Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);", 
+                "Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol consumption;", 
+                "Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;", 
+                "Adjusted for age, live with partner or not, average household income, education level, hypertension, smoking, total energy intake, alcohol consumption;", 
+                "Adjusted for age, live with partner or not, education level, hypertension, total energy intake, alcoho consumpiont;", 
+                "Adjusted for age, average household income, education level, BMI, hypertension, smoking status, total energy intake, ethnicity (white or non-white), alcohol consumption, TC (mmol/l), LDL (mmol/l), HDL (mmol/l), TG (mmol/l);",
+                "Adjusted for age, education level, BMI, hypertension, smoking status, total energy intake, alcohol consumption, TC, LDL, HDL, TG."), 
+               notation = "symbol")
+```

### 2018-08-09 paper/Tables/2by2Table1.tex
regression table added

@@
 
-\caption{\label{tab:tab1BMI}Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
+\caption{\label{tab:tab1BMI}Weighted means, percentages, and 95 CIs of the characteristics by BMI status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
 \centering
@@
 
+\subsection{DM}\label{dm}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:tab1DM}Weighted means, percentages, and 95 CIs of the characteristics by diabetic status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{lllllll}
+\hiderowcolors
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Men (n = 2537)} & \multicolumn{3}{c}{Women (n = 3618)} \\
+\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
+  & Non-diabetes & Diabetes & P value\textsuperscript{*} & Non-diabetes & Diabetes & P value\\
+\midrule
+\showrowcolors
+Weighted prevalence (\%) & 94.1 (92.4, 95.4) & 5.9 (4.6, 7.6) &  & 96.4 (95.1, 97.4) & 3.6 (2.6, 4.9) & \\
+Age (years) & 46.6 (45.2, 48.0) & 59.6 (55.6, 63.6) & < 0.001 & 48.7 (47.4, 50.0) & 60.2 (55.7, 64.7) & < 0.001\\
+Country (\%) &  &  & 0.627 &  &  & 0.138\\
+England & 83.8 (80.4, 86.7) & 79.0 (66.1, 87.9) &  & 84.9 (81.9, 87.4) & 81.2 (64.8, 91.0) & \\
+Northern Ireland & 2.3 (1.3, 3.7) & 1.8 (0.2, 11.4) &  & 1.5 (0.9, 2.5) & 2.3 (2.2, 12.3) & \\
+\hspace{1em}Scotland & 9.4 (7.0, 12.5) & 14.4 (7.0, 27.4) &  & 8.6 (6.4, 11.4) & 11.4 (3.6, 31.1) & \\
+\hspace{1em}Wales & 4.6 (3.3, 6.3) & 4.8 (1.8, 12.3) &  & 5.1 (4.0, 6.4) & 2.0 (0.8, 5.2) & \\
+Ethnicity (\%) &  &  & 0.267 &  &  & \\
+\hspace{1em}White & 89.9 (86.9, 92.3) & 84.9 (71.9, 92.5) &  & 88.8 (85.8, 91.3) & 87.9 (73.1, 95.1) & \\
+\hspace{1em}Non-white & 10.1 (7.7, 13.1) & 15.1 (7.5, 28.1) &  & 11.2 (8.7, 14.2) & 12.1 (4.9, 26.9) & \\
+Education (\%) &  &  & 0.007 &  &  & 0.034\\
+\hspace{1em}Degree or higher & 28.2 (24.9, 31.7) & 12.4 (6.2, 23.2) &  & 27.7 (24.8, 30.8) & 11.8 (4.7, 26.7) & \\
+\hspace{1em}Lower than Degree & 71.8 (68.3, 75.1) & 87.6 (76.8, 93.8) &  & 72.3 (69.2, 75.2) & 88.2 (73.3, 95.3) & \\
+Smoking status &  &  & 0.275 &  &  & 0.958\\
+\hspace{1em}Current & 23.0 (19.9, 26.5) & 19.3 (10.6, 23.7) &  & 16.4 (14.3, 18.8) & 18.2 (8.3, 35.5) & \\
+\hspace{1em}Ex-smoker & 24.5 (21.5, 27.8) & 34.5 (23.1, 47.9) &  & 23.8 (21.2, 26.7) & 23.5 (12.9, 38.8) & \\
+\hspace{1em}Never & 52.5 (48.6, 56.3) & 46.2 (33.6, 59.3) &  & 59.7 (56.6, 62.8) & 58.3 (42.1, 72.9) & \\
+Physical
+activity (hours/day) \textsuperscript{\dag} & 1.53 (1.36, 1.71) & 1.07 (0.66, 1.59) & 0.094 & 0.76 (0.69, 0.84) & 0.38 (0.19, 0.60) & 0.002\\
+BMI (kg/m2) & 27.3 (26.9, 27.6) & 30.1 (28.8, 31.3) & < 0.001 & 26.9 (26.5, 27.3) & 33.5 (31.7, 35.4) & < 0.001\\
+WC (cm) & 96.9 (95.9, 97.9) & 108.5 (104.8, 112.3) & < 0.001 & 87.2 (86.3 88.1) & 107.1 (102.5, 111.8) & < 0.001\\
+Carbohydrate eating patterns (\%) &  &  & 0.057 &  &  & 0.037\\
+\hspace{1em}Low & 30.1 (26.8, 33.6) & 41.1 (29.2, 54.1) &  & 25.5 (22.8, 28.5) & 42.1 (27.1, 58.6) & \\
+\hspace{1em}Moderate & 28.9 (25.4, 32.8) & 15.3 (8.3, 26.5) &  & 26.1 (23.0, 29.3) & 27.7 (15.9, 43.8) & \\
+\hspace{1em}High & 41.0 (37.3, 44.7) & 43.6 (31.1, 57.0) &  & 48.4 (45.1, 51.7) & 30.2 (18.4, 45.3) & \\
+Total energy intake (kJ) & 9016.8 (8806.8, 9226.8) & 8237.1 (7561.3, 8913.0) & 0.033 & 6844.2 (6715.9, 6972.5) & 5659.9 (5090.0, 6229.7) & < 0.001\\
+Carbohydrate intake (g) & 257.7 (252.1, 263.3) & 236.8 (215.8, 257.8) & 0.062 & 199.8 (195.4, 204.3) & 163.9 (144.8, 183.0) & < 0.001\\
+Glucose (mmol/l) & 5.23 (5.17, 5.28) & 9.35 (8.73, 10.03) & < 0.001 & 4.99 (4.96, 5.03) & 8.46 (7.69, 9.31) & < 0.001\\
+A1C (\%) & 5.48 (5.45, 5.51) & 8.01 (7.68, 8.35) & < 0.001 & 5.47 (5.44, 5.49) & 7.68 (7.27, 8.11) & < 0.001\\
+TC (mmol/l) & 4.79 (4.70, 4.88) & 4.14 (3.86, 4.44) & < 0.001 & 5.02 (4.95, 5.09) & 4.53 (4.12, 4.98) & < 0.001\\
+HDL (mmol/l) & 1.24 (1.21, 1.27) & 1.05 (0.98, 1.13) & < 0.001 & 1.53 (1.50, 1.56) & 1.18 (1.06, 1.31) & < 0.001\\
+LDL (mmol/l) & 2.86 (2.78, 2.94) & 2.16 (1.94, 2.40) & < 0.001 & 2.92 (2.87, 2.99) & 2.48 (2.12, 2.91) & < 0.001\\
+TG (mmol/l) & 1.23 (1.18, 1.28) & 1.64 (1.41, 1.90) & < 0.001 & 0.99 (0.96, 1.02) & 1.46 (1.27, 1.68) & < 0.001\\
+\bottomrule
+\multicolumn{7}{l}{\textit{Note: }}\\
+\multicolumn{7}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
+\multicolumn{7}{l}{ BMI body mass index; WC, waist circumference.}\\
+\multicolumn{7}{l}{Variables are weighted by nurse visiting weights.}\\
+\multicolumn{7}{l}{\textsuperscript{*} Significant sex-specific differences by diabetic status assessed using an F test (with Bonferroni correction to account for multiple testing across \$>\$ 2 groups)}\\
+\multicolumn{7}{l}{for continuous variables or design-adjusted Pearson chi-square test}\\
+\multicolumn{7}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the}\\
+\multicolumn{7}{l}{survey.}\\
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
+\subsection{Table 2 regressions in
+survey}\label{table-2-regressions-in-survey}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:survgression}Associations of carbohydrate eating patterns with hypertension, BMI, WC, and DM in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{llllllllllll}
+\hiderowcolors
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Men (n = 2537)} & \multicolumn{6}{c}{Women (n = 3618)} \\
+\cmidrule(l{2pt}r{2pt}){2-6} \cmidrule(l{2pt}r{2pt}){7-12}
+Models & Low & Moderate & P value\textsuperscript{*} & High & P value & Models & Low & Moderate & P value & High & P value\\
+\midrule
+\showrowcolors
+\addlinespace[0.3em]
+\multicolumn{12}{l}{\textbf{Hypertension}}\\
+\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217 & Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
+\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227 & Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
+\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124 & Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
+\addlinespace[0.3em]
+\multicolumn{12}{l}{\textbf{Hypertension in non-diabetics}}\\
+\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241 & Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
+\hspace{1em}Model 1 & 1 & 0.69 (0.43, 1.09) & 0.11 & 0.78 (0.54, 1.14) & 0.197 & Model 1 & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
+\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096 & Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
+\addlinespace[0.3em]
+\multicolumn{12}{l}{\textbf{BMI}}\\
+\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426 & Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
+\hspace{1em}Model 1\textsuperscript{\S} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0,43 (-1.13, 0.26) & 0.22 & Live with partner\textsuperscript{\P} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
+\hspace{1em} &  &  &  &  &  & Live alone & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
+\addlinespace[0.3em]
+\multicolumn{12}{l}{\textbf{BMI in non-diabetics}}\\
+\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557 & Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.04\\
+\hspace{1em}Model 1 & -- & -0.10 (-0.97, 0.77) & 0.82 & -0.39 (-1.10, 0.31) & 0.269 & Live with partner & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
+\hspace{1em} &  &  &  &  &  & Live alone & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
+\addlinespace[0.3em]
+\multicolumn{12}{l}{\textbf{WC}}\\
+\hspace{1em}Crude model & -- & -3.00 (-5.49, -0.52) & 0.018 & -0.90 (-2.84, 1.04) & 0.364 & Crude model & -- & -1.28 (-3.26, 0.70) & 0.206 & -2.81 (-4.50, -1.12) & 0.001\\
+\hspace{1em}Model 1\textsuperscript{**} & -- & 1.06 (-1.50, 3.64) & 0.415 & -1.55 (-3.42, 0.31) & 0.103 & Live with partner\textsuperscript{\dag\dag} & -- & 0.28 (-2.85, 3.41) & 0.861 & -4.71 (-7.00, -2.43) & < 0.001\\
+\hspace{1em} &  &  &  &  &  & Live alone & -- & 3.17 (0.05, 6.30) & 0.047 & 0.73 (-1.84, 3.30) & 0.577\\
+\addlinespace[0.3em]
+\multicolumn{12}{l}{\textbf{WC in non-diabetics}}\\
+\hspace{1em}Crude model & -- & -2.51 (-5.00, -0.21) & 0.048 & -0.51 (-2.47, 1.44) & 0.606 & Crude model & -- & -0.91 (-2.88, 1.07) & 0.368 & -2.41 (-4.06, -0.76) & 0.004\\
+\hspace{1em}Model 1 & -- & 1.42 (-1.17, 4.01) & 0.283 & -1.29 (-3.18, 0.60) & 0.181 & Live with partner & -- & 1.11 (-2.02, 4.23) & 0.487 & -3.74 (-5.97, -1.51) & 0.001\\
+\hspace{1em} &  &  &  &  &  & Live alone & -- & 3.08 (-0.09, 6.25) & 0.057 & 0.16 (-2.36, 2.69) & 0.899\\
+\addlinespace[0.3em]
+\multicolumn{12}{l}{\textbf{DM}}\\
+\hspace{1em}Crude model & 1 & 0.39 (0.18, 0.83) & 0.016 & 0.78 (0.43, 1.42) & 0.416 & Crude model & 1 & 0.65 (0.28, 1.47) & 0.296 & 0.38 (0.18, 0.81) & 0.013\\
+\hspace{1em}Model 1\textsuperscript{\ddag\ddag} & 1 & 0.27 (0.10, 0.73) & 0.012 & 0.78 (0.36, 1.68) & 0.529 & Model 1\textsuperscript{\S\S} & 1 & 1.05 (0.33, 3.35) & 0.928 & 0.52 (0.17, 1.59) & 0.255\\
+\hspace{1em}Model 2 & 1 & 0.27 (0.10, 0.76) & 0.013 & 0.76 (0.35, 1.65) & 0.493 & Model 2 & 1 & 0.79 (0.25, 2.46) & 0.686 & 0.48 (0.18, 1.32) & 0.155\\
+\bottomrule
+\multicolumn{12}{l}{\textit{Note: }}\\
+\multicolumn{12}{l}{Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.}\\
+\multicolumn{12}{l}{DM was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the same with the corresponding Model 1s.}\\
+\multicolumn{12}{l}{\textsuperscript{*} P values were obtained from wald tests from either linear regression models or logistic regression models.}\\
+\multicolumn{12}{l}{\textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or not, BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);}\\
+\multicolumn{12}{l}{\textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);}\\
+\multicolumn{12}{l}{\textsuperscript{\S} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol consumption;}\\
+\multicolumn{12}{l}{\textsuperscript{\P} Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;}\\
+\multicolumn{12}{l}{\textsuperscript{**} Adjusted for age, live with partner or not, average household income, education level, hypertension, smoking, total energy intake, alcohol consumption;}\\
+\multicolumn{12}{l}{\textsuperscript{\dag\dag} Adjusted for age, live with partner or not, education level, hypertension, total energy intake, alcoho consumpiont;}\\
+\multicolumn{12}{l}{\textsuperscript{\ddag\ddag} Adjusted for age, average household income, education level, BMI, hypertension, smoking status, total energy intake, ethnicity (white or non-white), alcohol consumption, TC (mmol/l), LDL (mmol/l), HDL (mmol/l), TG}\\
+\multicolumn{12}{l}{(mmol/l);}\\
+\multicolumn{12}{l}{\textsuperscript{\S\S} Adjusted for age, education level, BMI, hypertension, smoking status, total energy intake, alcohol consumption, TC, LDL, HDL, TG.}\\
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
 \end{document}

### 2018-08-09 paper/main.tex
some svyregress with BMI Waist
regression table added

@@
 
-\thesistitle{The time patterns of carbohydrate intake in UK adults, using the National Dietary and Nutrition Survey (NDNS) 2008/09-2015/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+\thesistitle{The time patterns of carbohydrate intake in UK adults -- the National Dietary and Nutrition Survey (NDNS) 2008/09-2015/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
 \supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
@@
 \vspace*{.06\textheight}
-{\scshape\huge \bfseries \univname\par}\vspace{1.5cm} % University name
+{\scshape\LARGE \bfseries \univname\par}\vspace{1.5cm} % University name
 \textsc{\Large MSc Project Report \\ 2017-2018}\\[0.5cm] % Thesis type
@@
 \HRule \\[0.4cm] % Horizontal line
-{\Huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
-\HRule \\[1.5cm] % Horizontal line
+{\Huge \bfseries \ttitle\par}\vspace{0.3cm} % Thesis title
+\HRule \\[1cm] % Horizontal line
 
@@
 %\textit{in the}\\[0.4cm]
-\groupname\\\deptname\\[2cm] % Research group name and department name
+\groupname\\\deptname\\[1.8cm] % Research group name and department name
 
@@
 
-%\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
+\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
 %\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\

### 2018-08-09 paper/Chapters/Chapter3.tex
hypertension words added

--- 2018-08-08 paper/Chapters/Chapter3.tex
@@
 
-\subsection{Association between individual level latent classes and hypertension, obesity, and diabetes.}
+\subsection{Association between individual level latent classes and hypertension, and obesity.}\vspace{-0.3cm}
+
+\subsubsection{Hypertension}\vspace{-0.3cm}
+
+\textbf{Table \ref{tab:tab1hypetension}} presents the characteristics of men and women participants in the NDNS RP 2008/09-15/16 by hypertension status.
+The weighted prevalences of hypertension were 30.4\% in men and 27.5\% in women.
+Among both sexes, there were significant differences by hypertension status for age, education level, living with a partner or not, smoking status, BMI, WC, and prevalence of diabetes (\textit{p} < 0.01).
+Differences were also found for carbohydrate eating patterns defined previously, and total energy intake, as well as total carbohydrate intake (\textit{p} < 0.001).
+No difference was found among either men or women for geographic location, and ethnicity.
+Strong evidence of difference was found in women for average household income (32741.5 \textsterling/year in non-hypertensive vs.
+27862.0 \textsterling/year in hypertensive, \textit{p} < 0.001), and physical activity level (geometric mean: 0.81 hours/day in non-hypertensive compared with 0.53 hours/day in hypertensive, \textit{p} < 0.001) but not in men.
 
@@
 	\centering
-	\fontsize{9}{11}\selectfont
+	\fontsize{8}{11}\selectfont
 	\begin{tabular}[t]{lcccccc}
@@
 \end{sidewaystable}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+	\caption{\label{tab:tab2HYT} ORs (95\%CI) of carbohydrate eating patterns with hypertension with or without diabetes in the UK adults.\\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
+	\centering
+	\fontsize{9}{11}\selectfont
+	\begin{tabular}[t]{lccccc}
+		\hiderowcolors
+		\toprule
+		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
+		\cmidrule(l{2pt}r{2pt}){2-6}
+		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
+		\midrule
+		\showrowcolors
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension}}\\
+		\hspace{1em}\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217\\
+		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227\\
+		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension in non-diabetics}}\\
+		\hspace{1em}\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241\\
+		\hspace{1em}\hspace{1em}Model 1 & 1 & 0.69 (0.43, 1.09) & 0.11 & 0.78 (0.54, 1.14) & 0.197\\
+		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension}}\\
+		\hspace{1em}\hspace{1em}Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
+		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
+		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension in non-diabetics}}\\
+		\hspace{1em}\hspace{1em}Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
+		\hspace{1em}\hspace{1em}Model 1 & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
+		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
+		\bottomrule
+		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
+		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national}}\\
+		\multicolumn{6}{l}{{\scriptsize dietary and nutrition survey rolling programme.}}\\
+		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other}}\\
+		\multicolumn{6}{l}{{\scriptsize covariates remained the same with the corresponding Model 1s.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from either linear regression models or logistic}}\\ 
+		\multicolumn{6}{l}{{\scriptsize regression models.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level}}\\ 
+		\multicolumn{6}{l}{{\scriptsize (higher or equal to degree level or not), BMI, smoking status (current, ex-smoker, never)}}\\
+		\multicolumn{6}{l}{{\scriptsize , total energy intake (kJ);}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous),}}\\ 
+		\multicolumn{6}{l}{{\scriptsize education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);}}\\
+	\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
 
@@
 \end{sidewaystable}
+
+%
+%
+%\begin{sidewaystable}
+%	\rowcolors{2}{gray!6}{white}
+%	
+%%	\begin{table}
+%		
+%		\caption{\label{tab:survgression}Associations of carbohydrate eating patterns with hypertension, BMI, WC, and DM in the UK adults. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
+%		\centering
+%		\fontsize{8}{11}\selectfont
+%		\begin{tabular}[t]{lccccccccccc}
+%			\hiderowcolors
+%			\toprule
+%			\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Men (n = 2537)}} & \multicolumn{6}{c}{\textbf{Women (n = 3618)}} \\
+%			\cmidrule(l{2pt}r{2pt}){2-6} \cmidrule(l{2pt}r{2pt}){7-12}
+%			\textbf{Outcomes} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{Models} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
+%			\midrule
+%			\showrowcolors
+%			\addlinespace[0.3em]
+%			\multicolumn{12}{l}{\textbf{Hypertension}}\\
+%			\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217 & Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
+%			\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227 & Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
+%			\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124 & Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
+%			\addlinespace[0.3em]
+%			\multicolumn{12}{l}{\textbf{Hypertension in non-diabetics}}\\
+%			\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241 & Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
+%			\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.69 (0.43, 1.09) & 0.11 & 0.78 (0.54, 1.14) & 0.197 & Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
+%			\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096 & Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
+%			\addlinespace[0.3em]
+%			\multicolumn{12}{l}{\textbf{BMI}}\\
+%			\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426 & Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
+%			\hspace{1em}Model 1\textsuperscript{\S} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0,43 (-1.13, 0.26) & 0.22 & Live with partner\textsuperscript{\P} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
+%			\hspace{1em} &  &  &  &  &  & Live alone & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
+%			\addlinespace[0.3em]
+%			\multicolumn{12}{l}{\textbf{BMI in non-diabetics}}\\
+%			\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557 & Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.04\\
+%			\hspace{1em}Model 1 & -- & -0.10 (-0.97, 0.77) & 0.82 & -0.39 (-1.10, 0.31) & 0.269 & Live with partner & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
+%			\hspace{1em} &  &  &  &  &  & Live alone & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
+%			\addlinespace[0.3em]
+%			\multicolumn{12}{l}{\textbf{WC}}\\
+%			\hspace{1em}Crude model & -- & -3.00 (-5.49, -0.52) & 0.018 & -0.90 (-2.84, 1.04) & 0.364 & Crude model & -- & -1.28 (-3.26, 0.70) & 0.206 & -2.81 (-4.50, -1.12) & 0.001\\
+%			\hspace{1em}Model 1\textsuperscript{**} & -- & 1.06 (-1.50, 3.64) & 0.415 & -1.55 (-3.42, 0.31) & 0.103 & Live with partner\textsuperscript{\dag\dag} & -- & 0.28 (-2.85, 3.41) & 0.861 & -4.71 (-7.00, -2.43) & < 0.001\\
+%			\hspace{1em} &  &  &  &  &  & Live alone & -- & 3.17 (0.05, 6.30) & 0.047 & 0.73 (-1.84, 3.30) & 0.577\\
+%			\addlinespace[0.3em]
+%			\multicolumn{12}{l}{\textbf{WC in non-diabetics}}\\
+%			\hspace{1em}Crude model & -- & -2.51 (-5.00, -0.21) & 0.048 & -0.51 (-2.47, 1.44) & 0.606 & Crude model & -- & -0.91 (-2.88, 1.07) & 0.368 & -2.41 (-4.06, -0.76) & 0.004\\
+%			\hspace{1em}Model 1 & -- & 1.42 (-1.17, 4.01) & 0.283 & -1.29 (-3.18, 0.60) & 0.181 & Live with partner & -- & 1.11 (-2.02, 4.23) & 0.487 & -3.74 (-5.97, -1.51) & 0.001\\
+%			\hspace{1em} &  &  &  &  &  & Live alone & -- & 3.08 (-0.09, 6.25) & 0.057 & 0.16 (-2.36, 2.69) & 0.899\\
+%			\addlinespace[0.3em]
+%			\multicolumn{12}{l}{\textbf{DM}}\\
+%			\hspace{1em}Crude model & 1 & 0.39 (0.18, 0.83) & 0.016 & 0.78 (0.43, 1.42) & 0.416 & Crude model & 1 & 0.65 (0.28, 1.47) & 0.296 & 0.38 (0.18, 0.81) & 0.013\\
+%			\hspace{1em}Model 1\textsuperscript{\ddag\ddag} & 1 & 0.27 (0.10, 0.73) & 0.012 & 0.78 (0.36, 1.68) & 0.529 & Model 1\textsuperscript{\S\S} & 1 & 1.05 (0.33, 3.35) & 0.928 & 0.52 (0.17, 1.59) & 0.255\\
+%			\hspace{1em}Model 2 & 1 & 0.27 (0.10, 0.76) & 0.013 & 0.76 (0.35, 1.65) & 0.493 & Model 2 & 1 & 0.79 (0.25, 2.46) & 0.686 & 0.48 (0.18, 1.32) & 0.155\\
+%			\bottomrule
+%			\multicolumn{12}{l}{{\scriptsize \textit{Note: }}}\\
+%			\multicolumn{12}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
+%			\multicolumn{12}{l}{{\scriptsize DM was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the same with the corresponding Model 1s.}}\\
+%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from either linear regression models or logistic regression models.}}\\
+%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or not, BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);}}\\
+%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);}}\\
+%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\S} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol consumption;}}\\
+%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\P} Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;}}\\
+%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{**} Adjusted for age, live with partner or not, average household income, education level, hypertension, smoking, total energy intake, alcohol consumption;}}\\
+%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\dag\dag} Adjusted for age, live with partner or not, education level, hypertension, total energy intake, alcoho consumpiont;}}\\
+%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\ddag\ddag} Adjusted for age, average household income, education level, BMI, hypertension, smoking status, total energy intake, ethnicity (white or non-white), alcohol consumption,}}\\
+%			\multicolumn{12}{l}{{\scriptsize TC (mmol/l), LDL (mmol/l), HDL (mmol/l), TG (mmol/l);}}\\
+%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\S\S} Adjusted for age, education level, BMI, hypertension, smoking status, total energy intake, alcohol consumption, TC, LDL, HDL, TG.}}\\
+%		\end{tabular}
+%%	\end{table}
+%	
+%	\rowcolors{2}{white}{white}
+%	
+%\end{sidewaystable}
 

### 2018-08-09 paper/Tables/2by2Table1.Rmd
hypertension words added

@@
 ```
+
+## Table 2 regressions for hypertension
+
+```{r tab2HYT, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/hypertensionReg.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")
+dt[2, 1] <- c("Model 1[note]")
+# dt[3, 1] <- c("Model 2[note]")
+dt[8, 1] <- c("Model 1[note]")
+# dt[9, 1] <- c("Model 2[note]")
+
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "ORs (95CI) of carbohydrate eating patterns with hypertension with or without diabetes in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
+ kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+  group_rows("Men (n = 2537)", 1, 6) %>%
+  group_rows("Hypertension", 1, 3) %>% 
+  group_rows("Hypertension in non-diabetics", 4, 6) %>% 
+  group_rows("Women (n = 3618)", 7, 12) %>% 
+  group_rows("Hypertension", 7, 9) %>% 
+  group_rows("Hypertension in non-diabetics", 10, 12) %>% 
+  add_header_above(c(" ", "Carbohydrate eating patterns" = 5)) %>% 
+  footnote(general = c("Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national", 
+                       "dietary and nutrition survey rolling programme.",
+                       "Diabetes was defined by A1C > 6.5%. BMI was replaced with WC in Model 2s, other", 
+                       "covariates remained the same with the corresponding Model 1s.")) %>% 
+  add_footnote(c("P values were obtained from wald tests from either linear regression models or logistic regression models.",
+                "Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or not), BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);",
+                "Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);"),
+                notation = "symbol")
+```

### 2018-08-09 paper/Tables/2by2Table1.tex
hypertension words added

@@
 
+\subsection{Table 2 regressions for
+hypertension}\label{table-2-regressions-for-hypertension}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:tab2HYT}ORs (95CI) of carbohydrate eating patterns with hypertension with or without diabetes in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{llllll}
+\hiderowcolors
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Carbohydrate eating patterns} \\
+\cmidrule(l{2pt}r{2pt}){2-6}
+Model & Low & Moderate & P value\textsuperscript{*} & High & P value\\
+\midrule
+\showrowcolors
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Hypertension}}\\
+\hspace{1em}\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217\\
+\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227\\
+\hspace{1em}\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Hypertension in non-diabetics}}\\
+\hspace{1em}\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241\\
+\hspace{1em}\hspace{1em}Model 1 & 1 & 0.69 (0.43, 1.09) & 0.11 & 0.78 (0.54, 1.14) & 0.197\\
+\hspace{1em}\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Hypertension}}\\
+\hspace{1em}\hspace{1em}Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
+\hspace{1em}\hspace{1em}Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
+\hspace{1em}\hspace{1em}Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Hypertension in non-diabetics}}\\
+\hspace{1em}\hspace{1em}Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
+\hspace{1em}\hspace{1em}Model 1 & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
+\hspace{1em}\hspace{1em}Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
+\bottomrule
+\multicolumn{6}{l}{\textit{Note: }}\\
+\multicolumn{6}{l}{Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national}\\
+\multicolumn{6}{l}{dietary and nutrition survey rolling programme.}\\
+\multicolumn{6}{l}{Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other}\\
+\multicolumn{6}{l}{covariates remained the same with the corresponding Model 1s.}\\
+\multicolumn{6}{l}{\textsuperscript{*} P values were obtained from wald tests from either linear regression models or logistic regression models.}\\
+\multicolumn{6}{l}{\textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or}\\
+\multicolumn{6}{l}{not), BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);}\\
+\multicolumn{6}{l}{\textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking}\\
+\multicolumn{6}{l}{status, total energy intake (kJ), alcohol consumption (g/day);}\\
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
 \end{document}

### 2018-08-09 paper/Chapters/Chapter3.tex
BMI table hypertension results added

@@
 The weighted prevalences of hypertension were 30.4\% in men and 27.5\% in women.
-Among both sexes, there were significant differences by hypertension status for age, education level, living with a partner or not, smoking status, BMI, WC, and prevalence of diabetes (\textit{p} < 0.01).
-Differences were also found for carbohydrate eating patterns defined previously, and total energy intake, as well as total carbohydrate intake (\textit{p} < 0.001).
+Among both sexes, there were strong evidence of differences by hypertension status for age, education level, living with a partner or not, smoking status, BMI, WC, and prevalence of diabetes (\textit{p} < 0.01).
+Differences were also found for carbohydrate eating patterns defined previously, total energy intake, as well as total carbohydrate intake (\textit{p} < 0.001).
 No difference was found among either men or women for geographic location, and ethnicity.
@@
 27862.0 \textsterling/year in hypertensive, \textit{p} < 0.001), and physical activity level (geometric mean: 0.81 hours/day in non-hypertensive compared with 0.53 hours/day in hypertensive, \textit{p} < 0.001) but not in men.
+
+The sex-specific associations of carbohydrate eating patterns with hypertension with or without diabetes are shown in \textbf{Table \ref{tab:tab2HYT}}.
+In the crude models, moderate carbohydrate eaters had statistically significant lower odds of having hypertension than low carbohydrate eaters in both men and women irrespective to diabetes status.
+Among men, after adjustment for selected confounders, which includes: age, live with partner or not, education level, BMI, smoking status, and total energy intake, the odds ratio (OR) comparing moderate carbohydrate eaters was 0.68 (95\% CI: 0.43, 1.07) and remained borderline significant (\textit{p} = 0.093).
+95\% CI of the OR became narrower (OR: 0.64, 95\% CI: 0.41, 1.01, \textit{p} = 0.054) when BMI was replaced with WC in model 2.
+When diabetic men were excluded in the models, the ORs (95\%CI) for moderate and high carbohydrate eaters compared with low carbohydrate eaters were 0.65 (0.41, 1.03) and 0.73 (0.51, 1.06), respectively.
+The negative associations between carbohydrate eaters patterns were still observed in women, however, without any statistical evidence in the full adjusted models.
+\vspace{-0.3cm}
+
+\subsubsection{Obesity (BMI and WC)}\vspace{-0.3cm}
 
@@
 
-	\caption{\label{tab:tab2HYT} ORs (95\%CI) of carbohydrate eating patterns with hypertension with or without diabetes in the UK adults.\\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
+	\caption{\label{tab:tab2HYT} ORs (95\%CI) of carbohydrate eating patterns with hypertension in the UK adults, with or without diabetes .\\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
 	\centering
@@
 		\hspace{1em}\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241\\
-		\hspace{1em}\hspace{1em}Model 1 & 1 & 0.69 (0.43, 1.09) & 0.11 & 0.78 (0.54, 1.14) & 0.197\\
+		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.69 (0.43, 1.09) & 0.110 & 0.78 (0.54, 1.14) & 0.197\\
 		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096\\
@@
 		\hspace{1em}\hspace{1em}Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
-		\hspace{1em}\hspace{1em}Model 1 & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
+		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
 		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
@@
 		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
-		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national}}\\
-		\multicolumn{6}{l}{{\scriptsize dietary and nutrition survey rolling programme.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: OR, odds ratio; CI, confidence interval; BMI, body mass index; WC, waist}}\\
+		\multicolumn{6}{l}{{\scriptsize  circumference; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
 		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other}}\\
 		\multicolumn{6}{l}{{\scriptsize covariates remained the same with the corresponding Model 1s.}}\\
-		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from either linear regression models or logistic}}\\ 
-		\multicolumn{6}{l}{{\scriptsize regression models.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from logistic regression models.}}\\ 
 		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level}}\\ 
@@
 \end{sidewaystable}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+	\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults, with or without diabetes. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
+	\centering
+	\fontsize{9}{11}\selectfont
+	\begin{tabular}[t]{lccccc}
+		\hiderowcolors
+		\toprule
+		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
+		\cmidrule(l{2pt}r{2pt}){2-6}
+		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
+		\midrule
+		\showrowcolors
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
+		\hspace{1em}\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426\\
+		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0,43 (-1.13, 0.26) & 0.22\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
+		\hspace{1em}\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557\\
+		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.10 (-0.97, 0.77) & 0.82 & -0.39 (-1.10, 0.31) & 0.269\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
+		\hspace{1em}\hspace{1em}Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
+		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
+		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
+		\hspace{1em}\hspace{1em}Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.040\\
+		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
+		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
+		\bottomrule
+		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
+		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition}}\\
+		\multicolumn{6}{l}{{\scriptsize  survey rolling programme.}}\\
+		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the}}\\
+		\multicolumn{6}{l}{{\scriptsize  same with the corresponding Model 1s.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} P values were obtained from wald tests from linear regression models.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total }}\\
+		\multicolumn{6}{l}{{\scriptsize  energy intake, alcohol consumption;}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol}}\\ 
+		\multicolumn{6}{l}{{\scriptsize  consumption.}}\\
+	\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
 

### 2018-08-09 paper/Tables/2by2Table1.Rmd
BMI table hypertension results added

@@
 ```
+
+## Table 2 regressions for BMI
+
+```{r tab2BMI, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/BMItab2.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")
+
+dt[2, 1] <- c("Model 1[note]")
+# dt[3, 1] <- c("Model 2[note]")
+dt[6, 1] <- c("Live with partner[note]")
+# dt[9, 1] <- c("Model 2[note]")
+
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "Associations of carbohydrate eating patterns with BMI in the UK adults , with or without diabetes.
+(NDNS RP 2008/09-2015/16, sample size = 6155)", booktabs = T,linesep = "") %>%
+ kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+  group_rows("Men (n = 2537)", 1, 5) %>%
+  group_rows("BMI", 1, 2) %>% 
+  group_rows("BMI in non-diabetics", 3, 4) %>% 
+  group_rows("Women (n = 3618)", 5, 10) %>% 
+  group_rows("BMI", 5, 8) %>% 
+  group_rows("BMI in non-diabetics", 8, 10) %>% 
+  add_header_above(c(" ", "Carbohydrate eating patterns" = 5)) %>% 
+  footnote(general = c("Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national", 
+                       "dietary and nutrition survey rolling programme.",
+                       "Diabetes was defined by A1C > 6.5%. BMI was replaced with WC in Model 2s, other", 
+                       "covariates remained the same with the corresponding Model 1s.")) %>% 
+  add_footnote(c("P values were obtained from wald tests from linear regression models.",
+                "Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol consumption;", 
+                "Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;"),
+                notation = "symbol")
+```

### 2018-08-09 paper/Tables/2by2Table1.tex
BMI table hypertension results added

@@
 
+\subsection{Table 2 regressions for
+BMI}\label{table-2-regressions-for-bmi}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults , with or without diabetes. (NDNS RP 2008/09-2015/16, sample size = 6155)}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{llllll}
+\hiderowcolors
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Carbohydrate eating patterns} \\
+\cmidrule(l{2pt}r{2pt}){2-6}
+Model & Low & Moderate & P value\textsuperscript{*} & High & P value\\
+\midrule
+\showrowcolors
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{BMI}}\\
+\hspace{1em}\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426\\
+\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0,43 (-1.13, 0.26) & 0.22\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{BMI in non-diabetics}}\\
+\hspace{1em}\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557\\
+\hspace{1em}\hspace{1em}Model 1 & -- & -0.10 (-0.97, 0.77) & 0.82 & -0.39 (-1.10, 0.31) & 0.269\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{BMI}}\\
+\hspace{1em}\hspace{1em}\hspace{1em}Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
+\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
+\hspace{1em}\hspace{1em}Live alone & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{BMI in non-diabetics}}\\
+\hspace{1em}\hspace{1em}\hspace{1em}Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.04\\
+\hspace{1em}\hspace{1em}Live with partner & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
+\hspace{1em}\hspace{1em}Live alone & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
+\bottomrule
+\multicolumn{6}{l}{\textit{Note: }}\\
+\multicolumn{6}{l}{Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national}\\
+\multicolumn{6}{l}{dietary and nutrition survey rolling programme.}\\
+\multicolumn{6}{l}{Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other}\\
+\multicolumn{6}{l}{covariates remained the same with the corresponding Model 1s.}\\
+\multicolumn{6}{l}{\textsuperscript{*} P values were obtained from wald tests from linear regression models.}\\
+\multicolumn{6}{l}{\textsuperscript{\dag} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol}\\
+\multicolumn{6}{l}{consumption;}\\
+\multicolumn{6}{l}{\textsuperscript{\ddag} Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;}\\
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
 \end{document}

### 2018-08-10 paper/Chapters/Chapter3.tex
BMIWC descriptions

@@
 
+\textbf{Table \ref{tab:tab2BMI}} shows the characteristics for participants according to their obesity status stratified by sex.
+The survey design-weighted prevalence for being overweight and obese in the UK adults were estimated to be 43.4\% and 25.7\% in men, and 30.9\% and 27.4\% in women.
+As expected, WC increased significantly with the elevated BMI level in both men and women.
+Strong evidence of differences by obesity level
+
 \begin{sidewaystable}
@@
 
-\begin{table}
+\begin{table}[H]
 
-	\caption{\label{tab:tab2HYT} ORs (95\%CI) of carbohydrate eating patterns with hypertension in the UK adults, with or without diabetes .\\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
+	\caption{\label{tab:tab2HYT} ORs (95\%CI) of carbohydrate eating patterns with hypertension in the UK adults, with or without diabetes .\\ (NDNS RP 2008/09-2015/16, sample size = 6155)}\vspace{-0.3cm}
 	\centering
@@
 \end{table}
+\vspace{-0.5cm}
+\rowcolors{2}{white}{white}
 
-\rowcolors{2}{white}{white}
+were found for age, total energy intake, and carbohydrate intake in both sexes.
+Specifically, education level (\textit{p} = 0.022 for men, < 0.001 for women), average household income (\textit{p} = 0.011 for men, < 0.001 for women) were lower with increasing BMI.
+Living with partner or not was strongly positively associated with obesity in men but not in women.
+Men with obesity were found to have the lowest proportion of never being a smoker (47.9 \%), and the highest proportion of being ex-smoker (32.9\%).
+Association between smoking status and obesity in women was only with very weak evidence (\textit{p} = 0.042) but similar pattern as in men was also observed.
+No difference was found for length of physical activity across obesity levels in men,
 
@@
 
+while in women, somewhat weak inverse association (\textit{p}=0.038) was confirmed.
+Interestingly, predefined carbohydrate eating patterns were seemingly not associated with BMI in men (\textit{p} = 0.072) or in women (\textit{p} = 0.253).
+
+Association between the
+
 \rowcolors{2}{gray!6}{white}
@@
 
-	\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults, with or without diabetes. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
+	\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults, with or without diabetes. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)}\vspace{-0.3cm}
 	\centering
@@
 \end{table}
-
+\vspace{-0.3cm}
 \rowcolors{2}{white}{white}

### 2018-08-10 paper/Chapters/Chapter3.tex
BMI table 2 done

@@
 	\end{tabular}
+%\end{table}
 \rowcolors{2}{white}{white}
 \end{sidewaystable}
+
+were found for age, total energy intake, and carbohydrate intake in both sexes.
+Specifically, education level (\textit{p} = 0.022 for men, < 0.001 for women), average household income (\textit{p} = 0.011 for men, < 0.001 for women) were lower with increasing BMI.
+Living with partner or not was strongly positively associated with obesity in men but not in women.
+Men with obesity were found to have the lowest proportion of never being a smoker (47.9 \%), and the highest proportion of being ex-smoker (32.9\%).
+Association between smoking status and obesity in women was only with very weak evidence (\textit{p} = 0.042) but similar pattern as in men was also observed.
+No difference was found for length of physical activity across obesity levels in men,
 
@@
 \rowcolors{2}{white}{white}
-
-were found for age, total energy intake, and carbohydrate intake in both sexes.
-Specifically, education level (\textit{p} = 0.022 for men, < 0.001 for women), average household income (\textit{p} = 0.011 for men, < 0.001 for women) were lower with increasing BMI.
-Living with partner or not was strongly positively associated with obesity in men but not in women.
-Men with obesity were found to have the lowest proportion of never being a smoker (47.9 \%), and the highest proportion of being ex-smoker (32.9\%).
-Association between smoking status and obesity in women was only with very weak evidence (\textit{p} = 0.042) but similar pattern as in men was also observed.
-No difference was found for length of physical activity across obesity levels in men,
 
@@
 
-Association between the
+Results of the regression analyses showed inverse associations between latent classes of carbohydrate eating patterns and BMI among men \textbf{(Table \ref{tab:tab2BMI})}.
+However, the 95\%CI of the regression coefficients were all too wide and including the null value 0, indicating no statistically supported evidence of the association.
+Nonetheless, evidence of interaction effect of whether live a partner or not on the association between carbohydrate eating patterns and BMI was found (\textit{p} = 0.014 and 0.036 for women in total and women without diabetes).
+For women living with her partner, latent classes of carbohydrate eating patterns were negatively associated with BMI.
 
@@
 
-\begin{table}
+\begin{table}[H]
 
@@
 		\hspace{1em}\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426\\
-		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0,43 (-1.13, 0.26) & 0.22\\
+		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0.43 (-1.13, 0.26) & 0.220\\
 		\addlinespace[0.3em]
@@
 		\hspace{1em}\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557\\
-		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.10 (-0.97, 0.77) & 0.82 & -0.39 (-1.10, 0.31) & 0.269\\
+		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.10 (-0.97, 0.77) & 0.820 & -0.39 (-1.10, 0.31) & 0.269\\
 		\addlinespace[0.3em]
@@
 		\multicolumn{6}{l}{{\scriptsize  same with the corresponding Model 1s.}}\\
-		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} P values were obtained from wald tests from linear regression models.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from linear regression models.}}\\
 		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total }}\\
@@
 \rowcolors{2}{white}{white}
+
+Comparing with women eating low carbohydrate meals, women having a high carbohydrate eating pattern was averagely associated with 1.76 kg/m\textsuperscript{2} lower BMI.
+95\%CI for the difference was 0.73 to 2.78 kg/m\textsuperscript{2}, \textit{p} = 0.001.
+After excluding diabetic women, BMI was still 1.62 kg/m\textsuperscript{2} (95\%CI: 0.58, 2.65, \textit{p} = 0.002) lower in high carbohydrate eaters versus low carbohydrate eaters on average.
+On the contrary, latent classes of carbohydrate eating patterns were positively associated with women who lived alone, although the regression coefficients were not statistically different from 0.
 

### 2018-08-10 paper/Chapters/Chapter3.tex
WCtab2 added

@@
 95\% CIs of the social-demographic characteristics by carbohydrate eating latent class memberships in the UK
-adults. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)} \centering
+adults. \\ (NDNS RP 2008/09-15/16, sample size = 6155)} \centering
 \fontsize{9}{11}\selectfont
@@
 	\caption{\label{tab:tab2}Weighted means, percentages, and 95\% CIs of the anthropometric measurements, average main nutrients intake and biochemical characteristics by carbohydrate eating latent class memberships in the UK adults.
-(NDNS RP 2008/09-2015/16, sample size = 6155)}
+(NDNS RP 2008/09-15/16, sample size = 6155)}
 	\centering
@@
 %\begin{table}
-	\caption{\label{tab:tab1hypetension}Weighted means, percentages, and 95 \% CIs of the characteristics by hypertension status in the UK adults. \\(NDNS RP 2008/09-2015/16, sample size = 6155)}
+	\caption{\label{tab:tab1hypetension}Weighted means, percentages, and 95 \% CIs of the characteristics by hypertension status in the UK adults. \\(NDNS RP 2008/09-15/16, sample size = 6155)}
 	\centering
@@
 
-	\caption{\label{tab:tab2HYT} ORs (95\%CI) of carbohydrate eating patterns with hypertension in the UK adults, with or without diabetes .\\ (NDNS RP 2008/09-2015/16, sample size = 6155)}\vspace{-0.3cm}
+	\caption{\label{tab:tab2HYT} ORs (95\%CI) of carbohydrate eating patterns with hypertension in the UK adults, with or without diabetes .\\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
 	\centering
@@
 
-		\caption{\label{tab:tab1BMI}Weighted means, percentages, and 95 \% CIs of the characteristics by BMI categories in the UK adults. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
+		\caption{\label{tab:tab1BMI}Weighted means, percentages, and 95 \% CIs of the characteristics by BMI categories in the UK adults. \\ (NDNS RP 2008/09-15/16, sample size = 6155)}
 		\centering
@@
 Results of the regression analyses showed inverse associations between latent classes of carbohydrate eating patterns and BMI among men \textbf{(Table \ref{tab:tab2BMI})}.
-However, the 95\%CI of the regression coefficients were all too wide and including the null value 0, indicating no statistically supported evidence of the association.
-Nonetheless, evidence of interaction effect of whether live a partner or not on the association between carbohydrate eating patterns and BMI was found (\textit{p} = 0.014 and 0.036 for women in total and women without diabetes).
+However, the 95\%CI of the regression coefficients were all too wide and include the null value 0, indicating no statistically supported evidence of the association.
+But, evidence of interaction effect was found in whether live a partner or not on the association between carbohydrate eating patterns and BMI (\textit{p} for interaction = 0.014 and 0.036 for women in total and women without diabetes).
 For women living with her partner, latent classes of carbohydrate eating patterns were negatively associated with BMI.
+Compared with women eating low carbohydrate meals, women having
 
@@
 
-	\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults, with or without diabetes. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)}\vspace{-0.3cm}
+	\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults, with or without diabetes. \\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
 	\centering
@@
 		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
-		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition}}\\
-		\multicolumn{6}{l}{{\scriptsize  survey rolling programme.}}\\
-		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the}}\\
-		\multicolumn{6}{l}{{\scriptsize  same with the corresponding Model 1s.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
+		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%.}}\\
 		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from linear regression models.}}\\
@@
 		\multicolumn{6}{l}{{\scriptsize  energy intake, alcohol consumption;}}\\
-		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol}}\\ 
-		\multicolumn{6}{l}{{\scriptsize  consumption.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, average household income, education level, hypertension, smoking status, total energy}}\\ 
+		\multicolumn{6}{l}{{\scriptsize  intake, alcohol consumption.}}\\
 	\end{tabular}
@@
 
-Comparing with women eating low carbohydrate meals, women having a high carbohydrate eating pattern was averagely associated with 1.76 kg/m\textsuperscript{2} lower BMI.
-95\%CI for the difference was 0.73 to 2.78 kg/m\textsuperscript{2}, \textit{p} = 0.001.
+the high carbohydrate eating pattern were averagely associated with 1.76 kg/m\textsuperscript{2} lower BMI after adjusted for age, average household income, education level, smoking status, total energy intake and alcohol consumption.
+95\%CI for the adjusted BMI difference was 0.73 to 2.78 kg/m\textsuperscript{2}, \textit{p} = 0.001.
 After excluding diabetic women, BMI was still 1.62 kg/m\textsuperscript{2} (95\%CI: 0.58, 2.65, \textit{p} = 0.002) lower in high carbohydrate eaters versus low carbohydrate eaters on average.
 On the contrary, latent classes of carbohydrate eating patterns were positively associated with women who lived alone, although the regression coefficients were not statistically different from 0.
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}[H]
+
+	\caption{\label{tab:tab2WC}Associations of carbohydrate eating patterns with BMI in the UK adults , with or without diabetes. \\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
+	\centering
+	\fontsize{9}{11}\selectfont
+	\begin{tabular}[t]{lccccc}
+		\hiderowcolors
+		\toprule
+		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
+		\cmidrule(l{2pt}r{2pt}){2-6}
+		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
+		\midrule
+		\showrowcolors
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\hspace{1em}\textbf{WC}}\\
+		\hspace{1em}\hspace{1em}Crude model & -- & -3.00 (-5.49, -0.52) & 0.018 & -0.90 (-2.84, 1.04) & 0.364\\
+		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & 1.06 (-1.50, 3.64) & 0.415 & -1.55 (-3.42, 0.31) & 0.103\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\hspace{1em}\textbf{WC in non-diabetics}}\\
+		\hspace{1em}\hspace{1em}Crude model & -- & -2.51 (-5.00, -0.21) & 0.048 & -0.51 (-2.47, 1.44) & 0.606\\
+		\hspace{1em}\hspace{1em}Model 1 & -- & 1.42 (-1.17, 4.01) & 0.283 & -1.29 (-3.18, 0.60) & 0.181\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\hspace{1em}\textbf{WC}}\\
+		\hspace{1em}\hspace{1em}Crude model & -- & -1.28 (-3.26, 0.70) & 0.206 & -2.81 (-4.50, -1.12) & 0.001\\
+		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & 0.28 (-2.85, 3.41) & 0.861 & -4.71 (-7.00, -2.43) & < 0.001\\
+		\hspace{1em}\hspace{1em}Live alone & -- & 3.17 (0.05, 6.30) & 0.047 & 0.73 (-1.84, 3.30) & 0.577\\
+		\addlinespace[0.3em]
+		\multicolumn{6}{l}{\hspace{1em}\textbf{WC in non-diabetics}}\\
+		\hspace{1em}\hspace{1em}Crude model & -- & -0.91 (-2.88, 1.07) & 0.368 & -2.41 (-4.06, -0.76) & 0.004\\
+		\hspace{1em}\hspace{1em}Live with partner & -- & 1.11 (-2.02, 4.23) & 0.487 & -3.74 (-5.97, -1.51) & 0.001\\
+		\hspace{1em}\hspace{1em}Live alone & -- & 3.08 (-0.09, 6.25) & 0.057 & 0.16 (-2.36, 2.69) & 0.899\\
+		\bottomrule
+		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
+		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
+		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. }}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} P values were obtained from wald tests from linear regression models.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age, live with partner or not, average household income, education level, hypertension (yes or no),}}\\
+		\multicolumn{6}{l}{{\scriptsize smoking status, total energy intake, alcohol consumption;}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, education level, hypertension, smoking status, total energy intake, alcohol consumption.}}\\
+	\end{tabular}
+\end{table}
+\vspace{-0.3cm}
+\rowcolors{2}{white}{white}
+
+Similarly, when using WC as another measurement of obesity, compared with men who had low carbohydrate eating pattern, only those had a moderate carbohydrate eating pattern were found with about 3 cm smaller WC in the crude model \textbf{(Table \ref{tab:tab2WC})}.
+After adjustment for
 
@@
 %		
-%		\caption{\label{tab:survgression}Associations of carbohydrate eating patterns with hypertension, BMI, WC, and DM in the UK adults. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
+%		\caption{\label{tab:survgression}Associations of carbohydrate eating patterns with hypertension, BMI, WC, and DM in the UK adults. \\ (NDNS RP 2008/09-15/16, sample size = 6155)}
 %		\centering

### 2018-08-10 paper/Tables/2by2Table1.Rmd
WCtab2 added

@@
 ```
+
+## Table 2 regressions for WC
+
+```{r tab2WC,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/WCtab2.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")
+
+dt[2, 1] <- c("Model 1[note]")
+# dt[3, 1] <- c("Model 2[note]")
+dt[6, 1] <- c("Live with partner[note]")
+# dt[9, 1] <- c("Model 2[note]")
+
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "Associations of carbohydrate eating patterns with BMI in the UK adults , with or without diabetes.
+(NDNS RP 2008/09-15/16, sample size = 6155)", booktabs = T,linesep = "") %>%
+ kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+  group_rows("Men (n = 2537)", 1, 5) %>%
+  group_rows("WC", 1, 2) %>% 
+  group_rows("WC in non-diabetics", 3, 4) %>% 
+  group_rows("Women (n = 3618)", 5, 10) %>% 
+  group_rows("WC", 5, 8) %>% 
+  group_rows("WC in non-diabetics", 8, 10) %>% 
+  add_header_above(c(" ", "Carbohydrate eating patterns" = 5)) %>% 
+  footnote(general = c("Abbreviations: WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.", 
+                       "Diabetes was defined by A1C > 6.5%. ")) %>% 
+  add_footnote(c("P values were obtained from wald tests from linear regression models.",
+                "Adjusted for age, live with partner or not, average household income, education level, hypertension (yes or no), smoking status, total energy intake, alcohol consumption;", 
+                "Adjusted for age, education level, hypertension, smoking status, total energy intake, alcohol consumption."),
+                notation = "symbol")
+
+```

### 2018-08-10 paper/Tables/2by2Table1.tex
WCtab2 added

@@
 
+\subsection{Table 2 regressions for
+WC}\label{table-2-regressions-for-wc}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:tab2WC}Associations of carbohydrate eating patterns with BMI in the UK adults , with or without diabetes. (NDNS RP 2008/09-15/16, sample size = 6155)}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{llllll}
+\hiderowcolors
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Carbohydrate eating patterns} \\
+\cmidrule(l{2pt}r{2pt}){2-6}
+Model & Low & Moderate & P value\textsuperscript{*} & High & P value\\
+\midrule
+\showrowcolors
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{WC}}\\
+\hspace{1em}\hspace{1em}Crude model & -- & -3.00 (-5.49, -0.52) & 0.018 & -0.90 (-2.84, 1.04) & 0.364\\
+\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & 1.06 (-1.50, 3.64) & 0.415 & -1.55 (-3.42, 0.31) & 0.103\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{WC in non-diabetics}}\\
+\hspace{1em}\hspace{1em}Crude model & -- & -2.51 (-5.00, -0.21) & 0.048 & -0.51 (-2.47, 1.44) & 0.606\\
+\hspace{1em}\hspace{1em}Model 1 & -- & 1.42 (-1.17, 4.01) & 0.283 & -1.29 (-3.18, 0.60) & 0.181\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{WC}}\\
+\hspace{1em}\hspace{1em}\hspace{1em}Crude model & -- & -1.28 (-3.26, 0.70) & 0.206 & -2.81 (-4.50, -1.12) & 0.001\\
+\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & 0.28 (-2.85, 3.41) & 0.861 & -4.71 (-7.00, -2.43) & < 0.001\\
+\hspace{1em}\hspace{1em}Live alone & -- & 3.17 (0.05, 6.30) & 0.047 & 0.73 (-1.84, 3.30) & 0.577\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{WC in non-diabetics}}\\
+\hspace{1em}\hspace{1em}\hspace{1em}Crude model & -- & -0.91 (-2.88, 1.07) & 0.368 & -2.41 (-4.06, -0.76) & 0.004\\
+\hspace{1em}\hspace{1em}Live with partner & -- & 1.11 (-2.02, 4.23) & 0.487 & -3.74 (-5.97, -1.51) & 0.001\\
+\hspace{1em}\hspace{1em}Live alone & -- & 3.08 (-0.09, 6.25) & 0.057 & 0.16 (-2.36, 2.69) & 0.899\\
+\bottomrule
+\multicolumn{6}{l}{\textit{Note: }}\\
+\multicolumn{6}{l}{Abbreviations: WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.}\\
+\multicolumn{6}{l}{Diabetes was defined by A1C > 6.5\%. }\\
+\multicolumn{6}{l}{\textsuperscript{*} P values were obtained from wald tests from linear regression models.}\\
+\multicolumn{6}{l}{\textsuperscript{\dag} Adjusted for age, live with partner or not, average household income, education level, hypertension (yes or no), smoking status, total}\\
+\multicolumn{6}{l}{energy intake, alcohol consumption;}\\
+\multicolumn{6}{l}{\textsuperscript{\ddag} Adjusted for age, education level, hypertension, smoking status, total energy intake, alcohol consumption.}\\
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
 \end{document}

### 2018-08-10 paper/Chapters/Chapter2.tex
WCtab2 done describe

@@
 
-\subsection{Association between individual level latent classes and the prevalence of hypertension, obesity, and diabetes}\vspace{-0.3cm}
+\subsection{Association between individual level latent classes and the prevalence of hypertension, and measurements of obesity}\vspace{-0.3cm}
 
-Associations between individual level carbohydrate eating classes and the prevalence of hypertension, obesity as well as diabetes were explored in men and women separately.
-Point estimates of weighted means and proportions and 95\%CI of the characteristics were determined by applying either nurse visiting weights (for outcomes of hypertension, BMI, and WC) or blood sample weights (for outcomes of DM) accordingly.
-Similarly, the \textit{F} test (for continuous variables) and adjusted Pearson $\chi^2$ test (for categorical variables) were used to determine sex-specific differences by hypertension status, BMI categories, and DM diagnosis.
+Associations between individual level carbohydrate eating classes and hypertension (yes/no), body mass index (BMI, kg/m\textsuperscript{2}), and waist circumference (WC, cm) were explored in men and women separately.
+Point estimates of weighted means and proportions and 95\%CI of the characteristics were determined by applying either nurse visiting weights (for outcomes of hypertension, BMI, and WC) or blood sample weights (for diagnosis of DM) accordingly.
+Similarly, \textit{F} tests (for continuous variables) and adjusted Pearson $\chi^2$ tests (for categorical variables) were used to determine sex-specific differences by hypertension status, and BMI categories.
 
@@
 
-Logistic regression models (for hypertension, and diabetes), and linear regression model (for WC, BMI), were used to test for associations between individual level carbohydrate eating classes and hypertension, diabetes, obesity, and WC, separately.
+Survey-designed logistic regression models (for hypertension), and linear regression models (for WC, BMI), were used to test for associations between latent classes of carbohydrate eating patterns and hypertension, BMI, and WC, in the NDNS RP sample, separately.
+Since diabetic participants might or might not modify their carbohydrate eating habits, we also conducted all the above mentioned regression models restricted to those without diabetes.
 

### 2018-08-10 paper/Chapters/Chapter3.tex
WCtab2 done describe

@@
 However, the 95\%CI of the regression coefficients were all too wide and include the null value 0, indicating no statistically supported evidence of the association.
-But, evidence of interaction effect was found in whether live a partner or not on the association between carbohydrate eating patterns and BMI (\textit{p} for interaction = 0.014 and 0.036 for women in total and women without diabetes).
+But, evidence of interaction effect was found in whether live with a partner or not on the association between carbohydrate eating patterns and BMI (\textit{p} for interaction = 0.014 and 0.036 for women in total and without diabetes).
 For women living with her partner, latent classes of carbohydrate eating patterns were negatively associated with BMI.
@@
 		\hspace{1em}\hspace{1em}Crude model & -- & -2.51 (-5.00, -0.21) & 0.048 & -0.51 (-2.47, 1.44) & 0.606\\
-		\hspace{1em}\hspace{1em}Model 1 & -- & 1.42 (-1.17, 4.01) & 0.283 & -1.29 (-3.18, 0.60) & 0.181\\
+		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & 1.42 (-1.17, 4.01) & 0.283 & -1.29 (-3.18, 0.60) & 0.181\\
 		\addlinespace[0.3em]
@@
 		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & 0.28 (-2.85, 3.41) & 0.861 & -4.71 (-7.00, -2.43) & < 0.001\\
-		\hspace{1em}\hspace{1em}Live alone & -- & 3.17 (0.05, 6.30) & 0.047 & 0.73 (-1.84, 3.30) & 0.577\\
+		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 3.17 (0.05, 6.30) & 0.047 & 0.73 (-1.84, 3.30) & 0.577\\
 		\addlinespace[0.3em]
@@
 		\hspace{1em}\hspace{1em}Crude model & -- & -0.91 (-2.88, 1.07) & 0.368 & -2.41 (-4.06, -0.76) & 0.004\\
-		\hspace{1em}\hspace{1em}Live with partner & -- & 1.11 (-2.02, 4.23) & 0.487 & -3.74 (-5.97, -1.51) & 0.001\\
-		\hspace{1em}\hspace{1em}Live alone & -- & 3.08 (-0.09, 6.25) & 0.057 & 0.16 (-2.36, 2.69) & 0.899\\
+		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & 1.11 (-2.02, 4.23) & 0.487 & -3.74 (-5.97, -1.51) & 0.001\\
+		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 3.08 (-0.09, 6.25) & 0.057 & 0.16 (-2.36, 2.69) & 0.899\\
 		\bottomrule
@@
 
-Similarly, when using WC as another measurement of obesity, compared with men who had low carbohydrate eating pattern, only those had a moderate carbohydrate eating pattern were found with about 3 cm smaller WC in the crude model \textbf{(Table \ref{tab:tab2WC})}.
-After adjustment for
+Similarly, when using WC as another measurement of obesity, compared with men who had low carbohydrate eating pattern, only those had a moderate carbohydrate eating pattern were found with about 3 cm (95\%CI: 0.52, 5.49 cm, \textit{p} = 0.018) smaller WC in the crude model \textbf{(Table \ref{tab:tab2WC})}.
+After adjustment of age, living with partner or not, average household income, education level, hypertension, smoking status, total energy intake, and alcohol consumption, the association attenuated to no difference in men.
+Again, the interaction effect of whether living with partner or not on the association between carbohydrate eating patterns and WC was found in women in total and without diabetes.
+Among women who were living with her partner, high carbohydrate eaters had 4.71 cm (95\%CI: 2.43, 7.00, \textit{p} < 0.001) lower WC on average compared with low carbohydrate eaters.
+The association remained when restricted into non-diabetic women (-3.74 cm, 95\% CI: 1.51, 5.97, \textit{p} = 0.001).
+However, for women who lived without a partner, moderate carbohydrate eaters had 3.17 cm (95\%CI: 0.05, 6.30, \textit{p} = 0.043) larger WC compared with low carbohydrate eaters.
+The evidence for the positive association between moderate carbohydrate eaters and WC was weak and became borderline significant when excluding diabetic women.
 

### 2018-08-10 paper/Chapters/Chapter2.tex
methods DM removed

@@
 	\item The crude association between the carbohydrate eating groups and the outcomes was first examined. 
-	\item Potential confounders of the association between carbohydrate eater groups (exposure) and the outcomes were selected depending on the descriptive statisitics conducted above, ie.
-those are associated with both the exposure and the outcome and not on the causal pathway were selected as potential confounders.
+	\item Potential confounders of the association between carbohydrate eating groups (exposure) and the outcomes were selected depending on the descriptive statisitics conducted above, i.e.
+those are associated with both the exposure and the outcome and also not on the causal pathway were selected as potential confounders.
 Those are strongly related with the outcomes but may not associated with carbohydrate eating groups may reduce the standard errors and so improve the precisions are also considered.
 	\item Confounding and/or interaction effect from each of the potential factors were checked one by one.
+Interaction effect were tested using the adjusted Wald test comparing models with and without the interaction terms.
 	\item A preliminary model that includes all of the variables suggested to be confounders in the previous step was established. 
 	\item The remaining variables were added to the preliminary model one by one to see if any of them may be a confounder in condition of the presence of the other covariates. 
-	\item For logistic regression models under survey data, goodness-of-fit (calibration) was assessed using the adapted \code{svylogitgof} command in Stata \parencite{archer2006goodness}.
+	\item For logistic regression models (hypertension) under the survey data, goodness-of-fit was assessed using the adapted \code{svylogitgof} command in Stata \parencite{archer2006goodness}.
 Other diagnostics for regular logistic regression models, such as estimating the pseudo-R\textsuperscript{2},  AIC or BIC, checking the standardized Pearson residuals, or covariate pattern residuals are currently not available for weighted survey data.
@@
 General checking such as QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance) are not available as well.
-Outliers, leverage, and Cook's distance cannot be check either, however, samples with extreme weightings (if exist) are checked by removing them and refit the models as a sensitivity analysis.
+Outliers, leverage, and Cook's distance cannot be check either, however, samples with extreme weightings (if exist) were checked by removing them and refit the models as a sensitivity analysis.
 	\item Since under survey design data, the sampling-weighted least squares are not maximum likelihood, it would not be possible to compare models using likelihood ratio test.
-Instead, adjusted Wald tests with $p < 0.05$ were used as criteria for variable inclusion in the final model, and a useful tool to decide whether quadratic and cubic terms of continuous variables are necessary in improving the fitting of model.
+Instead, adjusted Wald tests with $p < 0.05$ were used as criteria for variable inclusion in the final model.
+Another Stata command \code{linktest} was also used to  decide whether quadratic and cubic terms of continuous variables were necessary in improving the fitting of model \parencite{pregibon1980goodness}.
 \end{enumerate}

### 2018-08-10 paper/Chapters/Chapter2.tex
results almost done

@@
 For homemade dishes, participants were asked to record on a separate page in the diary the individual ingredients and quantities for the whole dish along with a brief description of the cooking method and how much of dish they had consumed.
-In addition to details of what and how much was eaten, participants recorded for each eating occasion; when was it, where they were, who they were eating with.
+In each eating occasion, in addition to the details of what and how much was eaten, participants were also asked to record: when was it, where they were, and who they were eating with.
 An example, used as guidance for participants, of a food diary for one day is shown in \textbf{Appendix \ref{AppendixC}}.\vspace{-0.3cm}
@@
 \begin{itemize}
-	\item Total Energy intake = (protein(gramme) $\times$ 17) + (fat(gramme) $\times$ 37) + (carbohydrate(gramme) $\times$ 16) + (alcohol(gramme) $\times$ 29)  kJ;
+	\item Total energy intake = (protein(gramme) $\times$ 17) + (fat(gramme) $\times$ 37) + (carbohydrate(gramme) $\times$ 16) + (alcohol(gramme) $\times$ 29)  kJ;
 	\item Carbohydrate intake = total sugars (gramme) + starch (gramme); 
@@
 
-Time across a typical survey day was divided into 7 time slots in the dietary diary of NDNS RP: 6 am to 9 am, 9 am to 12 noon, 12 noon to 2 pm, 2 pm to 5 pm, 5 pm to 8 pm, 8 pm to 10 pm, and 10 pm to 6 am.
+Time across a typical survey day was divided into 7 time slots in the dietary diary of NDNS RP: 6 am to 9 am, 9 am to 12 noon, 12 noon to 2 pm, 2 pm to 5 pm, 5 pm to 8 pm, 8 pm to 10 pm, and 10 pm to 6 am next morning.
 To produce a sequence of discrete responses regarding the carbohydrate intake we are interested, the energy consumption within each time slot over the four days of survey for each participant were calculated.
@@
 The response rates for completion of the dietary diary (three or four days) were 56\%, 53\%, 53\%, for years 1 to 4, 5 to 6, and 7 to 8, respectively.
-A total of 6,155 adults aged 19 years and over were kept in our analyses.
+A total of 6,155 adults aged 19 years and older were kept in the current study.
 \vspace{-0.6cm}
@@
 \begin{enumerate}
-	\item An overall selection weight, which is the product of the address, dwelling unit, catering(household) unit, and individual selection weights, was generated to correct for the unequal selection probabilities.
+	\item An overall selection weight, which is the product of the address, dwelling unit, catering (household) unit, and individual selection weights, was generated to correct for the unequal selection probabilities.
 These weights are the inverse of the selection probabilities at each level of the random sampling process and they can be used to compensate for differences in the chance of selection of an individual.
@@
 
-Computer assisted personal interviews were conducted for the selected individuals by trained interviewers to collect background information on smoking habits (current, past, never smokers), ethnicity (white, non-white), education level, living with a partner or not and other socio-demographic related variables.
+Computer assisted personal interviews were conducted for the selected individuals by trained interviewers to collect background information on smoking habits (current, ex-smokers, and never), ethnicity (white, non-white), education level (lower than degree/degree or above level), living with a partner or not and other socio-demographic related variables.
 Participants also had their height, weight, blood pressure, waist circumferences (WC) measured by the nurses.
@@
 
-Blood samples were stored at 4 $^\circ$C, and sent directly by post to the Department of Haematology and Department of Clinical Biochemistry and Immunology, Addenbrooke's Hospital, Cambridge within tow hours of their collection.
+Blood samples were stored at 4 $^\circ$C, and sent directly by post to the Department of Haematology and Department of Clinical Biochemistry and Immunology, Addenbrooke's Hospital, Cambridge within two hours of their collection.
 Serum samples were obtained by centrifugation of the coagulated blood sample.
-Serum total, High Density Lipoprotein (HDL) and Low Density Lipoprotein (LDL) cholesterol, triglycerides, blood glucose, haemoglobin A1C were measured.
+Serum total, High Density Lipoprotein (HDL) and Low Density Lipoprotein (LDL) cholesterol, triglycerides (TG), fasting blood glucose, haemoglobin A1C were measured.
 A1C value of 6.5\% was used as the cut off point for diagnosing diabetes.
@@
 
-Equation \ref{LCA} indicates that responses for an observation to the measuring variables are independent of one another given its membership in latent class $t$.
+\textbf{Equation \ref{LCA}} indicates that responses for an observation to the measuring variables are independent of one another given its membership in latent class $t$.
 However, in the NDNS RP data set, the assumption of independent observations is violated.
@@
 an observed high carbohydrate eating day vs.
-a low carbohydrate eating day) is constant within individual level which means for each person throughout his/her survey there is some probability of following a high carbohydrate eating day.
-A random effect model considers the individuals (level 2) to be drawn from the adult population in the UK, and the probability of the outcome (i.e.
+a low carbohydrate eating day) is constant within individual level, which means for each person throughout his/her survey there is some probability of following a high carbohydrate eating day.
+A random effect considers the individuals (level 2) to be drawn from the adult population in the UK, and the probability of the outcome (i.e.
 high carbohydrate eating days) across individuals is considered to be a random variable \parencite{snijders2011multilevel}.
@@
 
-According to Finch and French's simulation study \parencite{finch2014multilevel}, non-parametric approach generally resulted in more accurate recovery of the underlying latent structure of the data at both levels and provided better latent class model.
-Specifically, we are interested in exploring both meaningful individual (level 2) latent classes and the daily carbohydrate consumption classification.
-Therefore, non-parametric MLCA was employed 1) to identify latent classes of observation days (level 1) based on the subjects' responses to the 4-day food and drink diary and 2) to form distinct latent classes of individuals (level 2) based on the distribution of observation-level latent classes within individuals.\vspace{-0.3cm}
+According to Finch and French's simulation study \parencite{finch2014multilevel}, non-parametric approach generally resulted in more accurate recovery of the underlying latent structure of the data at both levels and provided better latent class model compared with parametric approach.
+In the current project, we are interested in exploring both meaningful individual (level 2) latent classes and the daily (level 1) carbohydrate consumption classification.
+Therefore, non-parametric MLCA was employed 1) to identify latent classes of observation days (level 1) based on the subjects' responses to the 4-day food and drink diary and 2) to form distinct latent classes of individuals (level 2) based on the distribution of day-level carbohydrate eating temporal latent classes within individuals.\vspace{-0.3cm}
 
@@
 \begin{itemize}
-	\item Firstly, we ignored the multilevel structure of the data and estimated a series of traditional LC models to determine the number of classes at the observational-level;
+	\item Firstly, we ignored the multilevel structure of the data and estimated a series of traditional LC models to determine the number of classes at the observational day-level;
 	\item Next, a series of MLCA models were fitted to account for the multi-level structrure of the data.
-In these models, the number of observational-level classes was based on the best fitting LCA model from the first step, and the LCA model at the individual level was estimated to identify the number of individual level latent classes;
-	\item Thirdly, when number of individual level latent classes is defined based on the previous stage, observational-level classes was modified (one class lower and one class higher than in the second step), to see the effect of changing level 1 classes and confirm the best fitting model.
+In these models, the number of day-level classes was based on the best fitting LCA model from the first step, and the LCA model at the individual level was estimated to identify the number of individual level latent classes;
+	\item Thirdly, when number of individual level latent classes is defined based on the previous stage, day-level classes was modified (one class lower and one class higher than in the second step) to see the effect of changing level 1 classes and confirm the best fitting model.
 \end{itemize}
 
-The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compare $q$ vs.
+The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Bayesian information criterion (BIC), and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compares $q$ vs.
 $q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability.
@@
 
-Day level latent classes identified by the first step of MLCA were tabulated according to day of week and also whether the diary was recorded during weekdays or not.
+Day level latent classes identified by the first step of MLCA were tabulated according to day of week and also whether the diary was recorded during weekends or not.
 A contingency table giving the frequency of responses across the 7 time slots of the survey days was produced.
 Descriptive statistics for the dietary day level recordings according to the latent class memberships were presented.
-Pearson $\chi^2$ test was used ot compare the distribution of categorical variables.
+Pearson $\chi^2$ test was used to compare the distribution of categorical variables.
 One-way Analysis of Variance (ANOVA) was used to compare the means across the multiple groups for continuous variables.
@@
 Weighted geometric means (95\% CI) were used for all log-transformed variables.
-For continuous variables, the \textit{F} test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across $>$ 2 classes.
+For continuous variables, the \textit{F} test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across $>$ 2 classes when applicable.
 For categorical variables, differences between latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.\vspace{-0.5cm}

### 2018-08-11 paper/Chapters/Chapter3.tex
results checked again

@@
 \label{Chapter 3} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+
+\vspace{-0.7cm}
 
@@
 The overall counts and percentages for each responses within every time slot and the distributions of the solution are presented in \textbf{Table \ref{tab:daylevel}}.
-The trajectories illustrating the change of the probabilities of each response to carbohydrate eating during the hours of the day are shown separately by the three types of days in \textbf{Figure \ref{fig:level1}}.
+The trajectories illustrating the change of the probabilities of each response to carbohydrate eating during the hours of the day are shown separately by three types of days in \textbf{Figure \ref{fig:level1}}.
 
@@
 \rowcolors{2}{white}{white}
-\vspace{-0.3cm}
+\vspace{-0.6cm}
 
-Class 2 days \textbf{(Figure \ref{fig:level1}-B)} were named as "low carbohydrate day" because first of all, in these days the possibility of participants skipping breakfast was 0.45.
-And after 9 am, within low carbohydrate days, the probability of having food contained lower carbohydrate (contributed less than 50\% of total energy intake), was always higher than having higher carbohydrate contained food.
+Class 2 days \textbf{(Figure \ref{fig:level1}-B)} were named as "low carbohydrate day" because first of all, in these days the probability of participants skipping breakfast was 0.45.
+And after 9 am, within low carbohydrate days, the probability of having low carbohydrate contained food (carbohydrate contributed $<$ 50\% of total energy intake), was always higher than having high carbohydrate contained food (carbohydrate contributed $\geqslant$ 50\% of total energy intake).
 In these days, participants also turned to have morning snacks (with only 0.079 possibility of not eating any food and similar probabilities of having either high or low carbohydrate contained food).
 This phenomenon may also be interpreted as having a long and late breakfast (brunch) in these mornings.
-The probability of not eating any food was the lowest for low carbohydrate days during the midnight time slot (10 pm to 6 am), with probability of 0.590 compared with 0.680 and 0.751 in the class 1 and class 3 days, respectively.
+The probability of not eating any food was the lowest for low carbohydrate days during the midnight time slot (10 pm to 6 am), with probability of 0.590 compared with 0.680 and 0.751 in class 1 and class 3 days, respectively.
 
@@
 Class 3 days \textbf{(Figure \ref{fig:level1}-C)} were called "regular meals day" due to the following reasons: 1) participants' dietary recordings showed that in these days there was almost 0 possibility of not eating any food at lunch (0.019 between 12 noon and 2 pm) and dinner (0.034 between 5 pm and 8 pm); 2) the probabilities of not eating during morning snack time (9 am to 12 am) and afternoon snack time (2 pm to 5 pm) were also the highest among the three types of days (0.401 and 0.659).
-3) during these days, participants may have some high carbohydrate contained food between 8 pm and 10 pm (0.308), but the probability of not eating any food during 10 pm to 6 am next morning was 0.751, the highest among the three types of days.
+3) during these days, participants may have some high carbohydrate contained food between 8 pm and 10 pm (probability = 0.308), but the probability of not eating any food during 10 pm to 6 am next morning was 0.751, the highest among the three types of days.
 \vspace{-0.5cm}
 
-\subsection{Features of the three carbohydrate eating time patterns}
-
-The details of the characteristics of the three types of carbohydrate eating time pattern were listed in\textbf{ Table \ref{tab:day-level-features}}.
-Specifically, regular meals day turned to be recorded slightly more often in Northern Ireland, and Scotland.
-In terms of day of week distribution in the three types of days, there is strong evidence (\textit{p} < 0.001) that high carbohydrate days appeared more frequently in weekends (32.5\%) compared with low carbohydrate day (26.5\%) and regular meals day (30.7\%).
+\subsection{Features of the three types of carbohydrate eating temporal patterns}\vspace{-0.5cm}
 
@@
 
-\begin{table}
+\begin{table}[H]
 
-	\caption{\label{tab:day-level-features}Means (standard deviations), and counts (\%) of the characteristics of different types of days according to carbohydrate intake.}
+	\caption{\label{tab:day-level-features}Means (standard deviations), and counts (\%) of the characteristics of different types of days according to carbohydrate intake.}\vspace{-0.3cm}
 	\centering
@@
 
+The details of the characteristics of the three types of carbohydrate eating time pattern were listed in\textbf{ Table \ref{tab:day-level-features}}.
+Specifically, regular meals day turned to be recorded slightly more often in Northern Ireland, and Scotland.
+In terms of day of week distribution in the three types of days, there is strong evidence (\textit{p} < 0.001) that high carbohydrate days appeared more frequently in weekends (32.5\%) compared with low carbohydrate day (26.5\%) and regular meals day (30.7\%).
+
 As expected, consumption of total energy (7539.98 kJ), total carbohydrate (222.79 g), total sugar (98.63 g), starch (124.07 g), and non-milk extrinsic sugar (59.45 g) were highest among high carbohydrate days (all \textit{p} < 0.001).
@@
 Moreover, in high carbohydrate days, participants turned to consume the highest amount of fruit (107.40 g).
-There was no evidence of any difference for the consumption of yellow, red, or green vegetables across the three types of days (\textit{p} = 0.681).
+There was no evidence of any difference for the consumption of yellow, red, or green vegetables across the three types of days (\textit{p} = 0.681).\vspace{-0.6cm}
 
@@
 
-\subsection{Individual level LCA solution}
+\subsection{Individual level LCA solution}\vspace{-0.3cm}
 
@@
 
-\begin{figure}[H]
+\begin{figure}
 	%\vspace*{13cm}
 	\centering
-	\includegraphics[width=13cm]{Figures/CB2level2.png}
+	\includegraphics[width=11cm]{Figures/CB2level2.png}
 	\decoRule
@@
 Moderate carbohydrate eaters have comparable proportions (42.0\% vs.
-40.0\%) of having high carbohydrate days and regular meals day, 18.0\% of their dietary diary were identified as low carbohydrate days.
+40.0\%) of having high carbohydrate days and regular meals day, 18.0\% of their dietary diary were identified as low carbohydrate days.\vspace{-0.2cm}
 
-\begin{figure}[H]
+\begin{figure}
 	%\vspace*{13cm}
 	\centering
-	\includegraphics[width=13cm]{Figures/level2.png}
+	\includegraphics[width=11cm]{Figures/level2.png}
 	\decoRule
@@
 \end{figure}
-\vspace{-0.6cm}
 
@@
 Gender distribution across the three types of carbohydrate eaters was fairly even (\textit{p} = 0.119).
-Distribution of the carbohydrate eater types turned out to be changing with the year of survey.
+The distribution of the carbohydrate eater types turned out to be changing with the year of survey.
 Low carbohydrate eaters represented 32.5\% of the population in the first year of survey, but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year.
-Proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year of the survey, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015).
+Proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015).
 There was no evidence of difference in employment status across three types of carbohydrate eaters.
-However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with a partner (\textit{p} < 0.001); moderate carbohydrate eaters had the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.
+However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with partner (\textit{p} < 0.001); moderate carbohydrate eaters had the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.
+\vspace{-0.2cm}
 
@@
 Although there was some evidence (\textit{p} = 0.027) that fasting blood glucose level may be slightly higher in non-diabetic low carbohydrate eaters, the geometric mean for A1C was probably lower in moderate carbohydrate eaters (4.72, 95\%CI: 5.39, 5.47).
-Cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.
+Total cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.
 
@@
 In the crude models, moderate carbohydrate eaters had statistically significant lower odds of having hypertension than low carbohydrate eaters in both men and women irrespective to diabetes status.
-Among men, after adjustment for selected confounders, which includes: age, live with partner or not, education level, BMI, smoking status, and total energy intake, the odds ratio (OR) comparing moderate carbohydrate eaters was 0.68 (95\% CI: 0.43, 1.07) and remained borderline significant (\textit{p} = 0.093).
-95\% CI of the OR became narrower (OR: 0.64, 95\% CI: 0.41, 1.01, \textit{p} = 0.054) when BMI was replaced with WC in model 2.
+Among men, after adjustment for selected confounders, which includes: age, live with partner or not, education level, BMI, smoking status, and total energy intake, the odds ratio (OR) comparing moderate with low carbohydrate eaters was 0.68 (95\% CI: 0.43, 1.07) and remained borderline significant (\textit{p} = 0.093).
+95\% CI of the adjusted OR became narrower (OR: 0.64, 95\% CI: 0.41, 1.01, \textit{p} = 0.054) when BMI was replaced with WC in model 2.
 When diabetic men were excluded in the models, the ORs (95\%CI) for moderate and high carbohydrate eaters compared with low carbohydrate eaters were 0.65 (0.41, 1.03) and 0.73 (0.51, 1.06), respectively.
-The negative associations between carbohydrate eaters patterns were still observed in women, however, without any statistical evidence in the full adjusted models.
+The negative associations between carbohydrate eating patterns were still observed in women, however, without any statistical evidence in the full adjusted models.
 \vspace{-0.3cm}
@@
 For women living with her partner, latent classes of carbohydrate eating patterns were negatively associated with BMI.
-Compared with women eating low carbohydrate meals, women having
+Compared with women eating low carbohydrate meals, women having a high
 
@@
 
-the high carbohydrate eating pattern were averagely associated with 1.76 kg/m\textsuperscript{2} lower BMI after adjusted for age, average household income, education level, smoking status, total energy intake and alcohol consumption.
+  carbohydrate eating pattern were averagely associated with 1.76 kg/m\textsuperscript{2} lower BMI after adjusted for age, average household income, education level, smoking status, total energy intake and alcohol consumption.
 95\%CI for the adjusted BMI difference was 0.73 to 2.78 kg/m\textsuperscript{2}, \textit{p} = 0.001.
 After excluding diabetic women, BMI was still 1.62 kg/m\textsuperscript{2} (95\%CI: 0.58, 2.65, \textit{p} = 0.002) lower in high carbohydrate eaters versus low carbohydrate eaters on average.
-On the contrary, latent classes of carbohydrate eating patterns were positively associated with women who lived alone, although the regression coefficients were not statistically different from 0.
+On the contrary, latent classes of carbohydrate eating patterns were positively associated with BMI in women who live without a partner, although the regression coefficients were not statistically different from 0.
 
@@
 
-	\caption{\label{tab:tab2WC}Associations of carbohydrate eating patterns with BMI in the UK adults , with or without diabetes. \\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
+	\caption{\label{tab:tab2WC}Associations of carbohydrate eating patterns with WC in the UK adults , with or without diabetes. \\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
 	\centering
@@
 Among women who were living with her partner, high carbohydrate eaters had 4.71 cm (95\%CI: 2.43, 7.00, \textit{p} < 0.001) lower WC on average compared with low carbohydrate eaters.
-The association remained when restricted into non-diabetic women (-3.74 cm, 95\% CI: 1.51, 5.97, \textit{p} = 0.001).
+The association remained when restricted into non-diabetic women (-3.74 cm, 95\% CI: -5.97, -1.51,  \textit{p} = 0.001).
 However, for women who lived without a partner, moderate carbohydrate eaters had 3.17 cm (95\%CI: 0.05, 6.30, \textit{p} = 0.043) larger WC compared with low carbohydrate eaters.

### 2018-08-11 paper/Chapters/Chapter2.tex
introduction almost done

@@
 \begin{itemize}
-	\item Total energy intake = (protein(gramme) $\times$ 17) + (fat(gramme) $\times$ 37) + (carbohydrate(gramme) $\times$ 16) + (alcohol(gramme) $\times$ 29)  kJ;
-	\item Carbohydrate intake = total sugars (gramme) + starch (gramme); 
+	\item Total energy intake = (protein(gram) $\times$ 17) + (fat(gram) $\times$ 37) + (carbohydrate(gram) $\times$ 16) + (alcohol(gram) $\times$ 29)  kJ;
+	\item Carbohydrate intake = total sugars (gram) + starch (gram); 
 %	\item Total sugars = sum of all individual sugars (gramme).

### 2018-08-12 paper/main.tex
BMI table hypertension results added
BMI table 2 done
results almost done
results checked again
introduction done

@@
 \usepackage[clockwise]{rotating} % to rotate pages for wide tables
+%\usepackage{pdflscape} % to rotate page into landscape
+%\usepackage[paper = {portrait or landscape}, page size]{typearea}
+
 %----------------------------------------------------------------------------------------
@@
 }{% else
-\setlength{\parindent}{0pt}
+{\parindent}{0pt}
 \setlength{\parskip}{6pt plus 2pt minus 1pt}
@@
 
-\noindent Signed:\\
+\noindent Signed: \;\;\;\;\;\;\includegraphics[height=2.5\baselineskip]{Figures/signature.png}\\
 \rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
 
-\noindent Date:\\
+\noindent Date: \;\;\;\;\;\;\;\;\;\;\;\;2018-09-05\\
 \rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
@@
 \addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
-
+\vspace{0.8cm}
 I would like to thank my tutor and supervisor \supname, for his guidance, patience, and help while working on this project and also to Dr.
@@
 
-I also want to express my gratitude to my family for their unconditional support, understanding, and encouragement throughout this year. \\
+%I would also like to thank Aichi Medical Univeristy, and Egashira Hospitality Public Interest Foundation for funding my studentship at the London School of Hygiene and Tropical Medicine. \\
+
+Last but not the least, I want to express my gratitude to my family for their unconditional support, understanding, and encouragement throughout this year. \\
 
@@
 \textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
+\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated hemoglobin \\
 %\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
@@
 \textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
+\textbf{CI}  & \textbf{C}onfidence \textbf{I}nterval \\
 \textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
@@
 \textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
-\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated hemoglobin \\
+\textbf{HDL} & \textbf{H}igh \textbf{D}ensity \textbf{L}ipoprotein cholesterol \\
+\textbf{LDL} & \textbf{L}ow \textbf{D}ensity \textbf{L}ipoprotein cholesterol \\
 \textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
@@
 \textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
+\textbf{TC} & \textbf{T}otal \textbf{C}holesterol \\
+\textbf{TG} & \textbf{T}ri\textbf{g}lycerides \\
+\textbf{WC}   & \textbf{W}aist \textbf{C}ircumference \\
 \end{abbreviations}
@@
 % Uncomment the lines as you write the chapters
-
+\linespread{1.25}
 \include{Chapters/Chapter1}

### 2018-08-13 Rcode/carbohydrate intake by slots.Rmd
carb each time slot

---
title: "Carbohydrate intake in each time slot"
author: "Chaochen Wang"
# date: "12 August 2018"
date: "12 August 2018created, `r Sys.Date()` updated"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
editor_options: 
  chunk_output_type: console
---

```{r}
library(epiDisplay)
library(plyr)
library(tidyverse)
library(haven)
```

```{r}

# Change the data path accordingly ----------------------------------------

setwd("/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/") # on Ubuntu
data <- read_dta("ndns_rp_yr1-4a_foodleveldietarydata_uk.dta")

data56 <- read_dta("ndns_rp_yr5-6a_foodleveldietarydata.dta")

data78 <- read_dta("ndns_rp_yr7-8a_foodleveldietarydata.dta")

names(data)[names(data)=="seriali"] <- "id"
names(data56)[names(data56)=="seriali"] <- "id"
names(data78)[names(data78)=="seriali"] <- "id"

df14d <- data[,c(113,1,2,3,5,6,7,8,9,21, 22, 23, 24,53, 55,57,58,59,60,61,62,63,64,65)]
# extract variables needed
var <- names(df14d)

df56d <- data56 %>% 
  select(var)

df78d <- data78 %>% 
  select(var)

dfs1 <- rbind(df14d, df56d, df78d)

dfs2 <- dfs1[dfs1$Age>=19,] # keep adults only
rm(data, data56, data78)

# Calculate the time (minute and hour) when they eat ----------------------

dfs2$MealTime_chr <- as.character(dfs2$MealTime)
dfs2$MealTime_hm <- unlist(strsplit(dfs2$MealTime_chr," "))[c(FALSE, TRUE)]

dfs2$MealHourN <- as.numeric(unlist(strsplit(dfs2$MealTime_hm,":"))[c(TRUE, FALSE, FALSE)])
dfs2$MealMinN <- as.numeric(unlist(strsplit(dfs2$MealTime_hm,":"))[c(FALSE, TRUE, FALSE)])
dfs2$MealMinN0 <- (60*dfs2$MealHourN)+dfs2$MealMinN

dfs3 <- dfs2[order(dfs2$id,dfs2$DayNo,dfs2$MealMinN0),]

length(unique(dfs3$id)) ## number of participants = 6155

# create a variable combine id and day No ---------------------------------

dfs3 <- dfs3 %>% 
  mutate(id_dy = paste(id, DayNo, sep = "D"))

# For each subject, the total energy/carbohydrate intake for each eating time can be calculated --------

old<-Sys.time()
Energy <- ddply(dfs3, .(id_dy, id, SurveyYear, DayNo, Age, Sex, DiaryDaysCompleted, MealHourN, DayofWeek),  
                summarise, Tot_Energ = sum(EnergykJ), 
                Tot_Carb = sum(Carbohydrateg), 
                Tot_Sugar = sum(Totalsugarsg), 
                Tot_Starch = sum(Starchg), 
                Tot_Fibre = sum(Englystfibreg),
                Tot_Fat   = sum(Fatg), 
                Tot_Prot  = sum(Proteing), 
                Tot_Alc   = sum(Alcoholg), 
                Tot_NMES  = sum(Nonmilkextrinsicsugarsg))
new<-Sys.time()-old
print(new)

Energy <- Energy %>% 
  mutate(TimeSlot = cut(MealHourN, breaks = c(6, 9, 12, 14, 17, 20, 22), right = FALSE))

levels(Energy$TimeSlot) <- c(levels(Energy$TimeSlot), "[22, 6)")

Energy$TimeSlot[is.na(Energy$TimeSlot)] <- "[22, 6)"

tab1(Energy$TimeSlot)

old<-Sys.time()
Energy <- ddply(Energy, .(id_dy, id, SurveyYear, DayNo, Age, Sex, DiaryDaysCompleted, TimeSlot, DayofWeek),  
                summarise, Tot_Energ = sum(Tot_Energ), Tot_Carb = sum(Tot_Carb), Tot_Sugar = sum(Tot_Sugar),
                Tot_Starch = sum(Tot_Starch), Tot_Fibre = sum(Tot_Fibre), Tot_Fat   = sum(Tot_Fat), 
                Tot_Prot  = sum(Tot_Prot), 
                Tot_Alc   = sum(Tot_Alc), 
                Tot_NMES  = sum(Tot_NMES))
new<-Sys.time()-old
print(new)

Energy0 <- Energy[!(Energy$Tot_Energ == 0), ]
write.csv(Energy0, file = "Energy_slots.csv")
Energy_slots <- Energy0 %>% 
  rename(ID = id)

CW3idday <- read_csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/CW3idday.csv")
CW3idday$DayofWeek[CW3idday$ID_DAY == 31012251000] <- "Tuesday"

CW3idday$CW_new <- 0
CW3idday$CW_new[CW3idday$CW == 1] <- 3
CW3idday$CW_new[CW3idday$CW == 2] <- 1
CW3idday$CW_new[CW3idday$CW == 3] <- 2

Energy <- Energy_slots %>% 
  left_join(CW3idday, by = c("ID", "DayofWeek"))

Energy$Slot3g <- as.character(Energy$TimeSlot)
Energy$Slot3g[Energy$TimeSlot == "[6,9)" | Energy$TimeSlot == "[9,12)"] <- "Before 12 noon"
Energy$Slot3g[Energy$TimeSlot == "[12,14)" | Energy$TimeSlot == "[14,17)" | 
                Energy$TimeSlot == "[17,20)"] <- "Between 12 noon to 8 pm"
Energy$Slot3g[Energy$TimeSlot == "[22, 6)" | Energy$TimeSlot == "[20,22)"] <- "After 8 pm"

Energy$Slot3g <- factor(Energy$Slot3g, levels = c("Before 12 noon", 
                                                  "Between 12 noon to 8 pm", 
                                                  "After 8 pm"))

Energy$TimeSlot <- factor(Energy$TimeSlot, levels = c("[6,9)", "[9,12)", "[12,14)", "[14,17)",
                                                      "[17,20)", "[20,22)", "[22, 6)"))

```

### 2018-08-13 paper/Chapters/Chapter2.tex
carb each time slot

@@
 Since we planed to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical, we then dichotomised the responses according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e.
-if within a time slot there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was lower or higher/equal to 50\% of total energy intake within that time slot.
+if within a time slot where there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was lower or higher/equal to 50\% of total energy intake within that time slot.
 Consequently, for each day of the recording, there were 7 data points generated by the diary, each data point included one of the following responses:
@@
 
-Body mass index (BMI) was calculated as weight in kilograms and weight in kilograms divided by height in square meters.
+Body mass index (BMI) was calculated as weight in kilograms divided by height in square meters.
 BMI was then categorised into less than 25 kg/m\textsuperscript{2} (normal weight), 25 to 30 kg/m\textsuperscript{2} (overweight), and higher or equal to 30 kg/m\textsuperscript{2} (obese).
@@
 \begin{itemize}
+	\item $\text{logit}{x} = \frac{\log(x)}{\log(1-x)}$;
 	\item $P(C_{ij} = 1)$ as the probability that the randomly selected $i$th observation day of $j$th individual is a high carbohydrate eating day;
@@
 
-If the day level LCA model (carbohydrate eating pattern typologies) is best defined by $T (T \geqslant 2)$ latent classes, then $T-1$ random intercept will be specified by a two-level multinomial logistic regression model.
+If the day level LCA model (carbohydrate eating temporal pattern typologies) is best defined by $T (T \geqslant 2)$ latent classes, then $T-1$ random intercept will be specified by a two-level multinomial logistic regression model.
 Similar to the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each time slots, throughout 4 consecutive days of survey period).
@@
 
-\subsection{Strategy of conducting MLCA in the current analysis}\vspace{-0.3cm}
+\subsection{Strategy of conducting MLCA}\vspace{-0.3cm}
 
@@
 The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Bayesian information criterion (BIC), and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compares $q$ vs.
-$q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability.
-In the step of performing multilevel LCA, where LMR-LRT is available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day level and individual level.
+$q-1$ classes models, where $q$ is the number of latent classes and most importantly, 3) pattern interpretability.
+In the steps of performing multilevel LCA, where LMR-LRT is not available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day level and individual level.
 MLCA models were fitted in Mplus 7.4 \parencite{muthen2005mplus}, the Mplus codes and outputs are shown in \textbf{Appendix \ref{AppendixB}}.
@@
 
-Person level point estimates and 95\% confidence intervals (CIs) were determined by applying individual, nurse visiting, and blood sample weights accordingly which accounted for the probability of participant selection and the clustered survey design.
+Person level point estimates and 95\% confidence intervals (CIs) were determined by applying individual, nurse visiting, and blood sample weights accordingly which account for the probability of participant selection and the clustered survey design.
 Descriptive statistics for sample characteristics are presented as weighted means (95\% CI) or weighted percentages (95\%CI).
@@
 Survey-designed logistic regression models (for hypertension), and linear regression models (for WC, BMI), were used to test for associations between latent classes of carbohydrate eating patterns and hypertension, BMI, and WC, in the NDNS RP sample, separately.
-Since diabetic participants might or might not modify their carbohydrate eating habits, we also conducted all the above mentioned regression models restricted to those without diabetes.
+Since diabetic participants might or might not modify their carbohydrate eating habits, we also fitted all the above mentioned regression models restricted to those without diabetes.
 
@@
 	\item The crude association between the carbohydrate eating groups and the outcomes was first examined. 
-	\item Potential confounders of the association between carbohydrate eating groups (exposure) and the outcomes were selected depending on the descriptive statisitics conducted above, i.e.
+	\item Potential confounders of the association between carbohydrate eating groups (exposure) and the outcomes were selected depending on the descriptive statisitical analyses conducted above, i.e.
 those are associated with both the exposure and the outcome and also not on the causal pathway were selected as potential confounders.
-Those are strongly related with the outcomes but may not associated with carbohydrate eating groups may reduce the standard errors and so improve the precisions are also considered.
+Those are strongly related with the outcomes but may not associated with carbohydrate eating groups may reduce the standard errors and so improve the precisions are also considered in the linear regression models.
 	\item Confounding and/or interaction effect from each of the potential factors were checked one by one.

### 2018-08-13 paper/Chapters/Chapter4.tex
introduction done
carb each time slot

@@
 
+%----------------------------------------------------------------------------------------
+%	SECTION 1
+%----------------------------------------------------------------------------------------
+
+\section{Main Findings}
+
+\subsection{Carbohydrate eating patterns}
+
+Using multilevel LCA as a novel technique, and the NDNS RP dietary database, this project examined carbohydrate eating temporal patterns in the day level, based on which, individual level carbohydrate eating patterns were also defined subsequently.
+Among all of the dietary diaries, there were three distinct latent classes specifically for carbohydrate intake: 1) high probabilities of having high carbohydrate contained for across the hours of day (high carbohydrate day); 2) low carbohydrate food dominant through out the hours of day (low carbohydrate day); and 3) always having lunch and dinner day (regular meals day).
+
+For the first time, as far as we know, the non-parametric MLCA models successfully captured the day-to-day variability within individuals as expected and showed that from the perspective of carbohydrate eating pattern people were switching between different types of carbohydrate consumptions.
+The MLCA models allowed the probability of a certain type of carbohydrate eating day to vary across individuals.
+This properly accounted for the fact that for some people, their probability of following a regular meals day during the survey was much higher than the others (low carbohydrate eaters); and for some people, their probability of following high carbohydrate eating day during their survey were quite high (high carbohydrate eaters); while for the rest of the participants, they had similar probabilities of following either regular meals day or high carbohydrate eating day (moderate carbohydrate eaters).
+
+\subsection{Association between carbohydrate eating patterns and health outcomes}
+
+%----------------------------------------------------------------------------------------
+%	SECTION 2
+%----------------------------------------------------------------------------------------
+
+\section{Strengths and limitations}
+
 \begin{itemize}
@@
 
-%----------------------------------------------------------------------------------------
-%	SECTION 1
-%----------------------------------------------------------------------------------------
-
-\section{Main Section 1}
-
-%-----------------------------------
-%	SUBSECTION 1
-%-----------------------------------
-\subsection{Subsection 1}
-
-%-----------------------------------
-%	SUBSECTION 2
-%-----------------------------------
-
-\subsection{Subsection 2}
-
-%----------------------------------------------------------------------------------------
-%	SECTION 2
-%----------------------------------------------------------------------------------------
-
-\section{Main Section 2}
+\section{Conclusions}

### 2018-08-13 paper/main.tex
carb each time slot

@@
 
-\thesistitle{The time patterns of carbohydrate intake in UK adults -- the National Dietary and Nutrition Survey (NDNS) 2008/09-2015/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+\thesistitle{The time patterns of carbohydrate intake in UK adults -- the National Dietary and Nutrition Survey (NDNS) 2008/09-15/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
 \supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
@@
 \begin{itemize}
-\item This work was done wholly or mainly while in candidature for a MSc degree on Medical Statistics at this University.
-\item No part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution.
+\item This work was done wholly while in candidature for a MSc degree in Medical Statistics at London School of Hygiene and Tropical Medicine.
+\item No part of this thesis has previously been submitted for a degree or any other qualification at London School of Hygiene and Tropical Medicine or any other institution.
 \item Where I have consulted the published work of others, this is always clearly attributed.
@@
 
-\noindent Date: \;\;\;\;\;\;\;\;\;\;\;\;2018-09-05\\
+\noindent Date: \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;2018-09-05\\
 \rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
@@
 
-I would like to thank the team of the National Dietary and Nutrition Survey (NDNS) who have made their data available to the public for academic study. \\
+I would like to thank the team of the National Dietary and Nutrition Survey Rolling Programme (NDNS RP) who have made their data available to the public for academic study. \\
 

### 2018-08-13 Rcode/Energy and classes.R

@@ -12,6 +12,29 @@ library(naniar)
 
 
 
+personlevel <- read_dta("/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr1-4a_personleveldietarydata_uk.dta")
+personlevel56 <- read_dta("/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr5-6a_personleveldietarydata.dta")
+personlevel78 <- read_dta("/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr7-8a_personleveldietarydata.dta")
+head(personlevel$Ndays)
+
+
+names(personlevel)[names(personlevel)=="seriali"] <- "ID"
+names(personlevel56)[names(personlevel56)=="seriali"] <- "ID"
+names(personlevel78)[names(personlevel78)=="seriali"] <- "ID"
+
+personlevel <- personlevel %>% 
+  select(ID, Ndays)
+
+personlevel56 <- personlevel56 %>% 
+  select(ID, Ndays)
+
+personlevel78 <- personlevel78 %>% 
+  select(ID, NDays) %>% 
+  rename(Ndays = NDays)
+
+NDAYS <- rbind(personlevel, personlevel56, personlevel78)
+NDAYS$ID <- as.numeric(NDAYS$ID)
+
 
 
 
@@ -51,78 +74,268 @@ Energy$Slot3g <- factor(Energy$Slot3g, levels = c("Before 12 noon",
 Energy$TimeSlot <- factor(Energy$TimeSlot, levels = c("[6,9)", "[9,12)", "[12,14)", "[14,17)",
                                                       "[17,20)", "[20,22)", "[22, 6)"))
 
-
-FoodbyCW <- Energy %>% 
-  group_by(CW_new, TimeSlot) %>% 
-  summarise(MeanEnergy = mean(Tot_Energ), sdEnergy = sd(Tot_Energ),
-            MeanCarb = mean(Tot_Carb), sdCarb = sd(Tot_Carb), 
-            MeanSugar = mean(Tot_Sugar), sdSugar = sd(Tot_Sugar), 
-            MeanStarch = mean(Tot_Starch), sdStarch = sd(Tot_Starch), 
[…]

### 2018-08-13 Rcode/data transformation.R

@@ -1,0 +1,934 @@
+
+# NDNS analysis, data management ------------------------------------------
+
+
+# Change the data path accordingly ----------------------------------------
+
+setwd("/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/") # on Ubuntu
+
+# setwd("C:/Users/lsh1701745/Downloads/6533STATA11_SE/UKDA-6533-stata11_se/stata11_se/")
+
+
+library(epiDisplay)
+library(plyr)
+library(tidyverse)
+
+
+# Read the data into memory -----------------------------------------------
+
+library(haven)
+
+
+data <- read_dta("ndns_rp_yr1-4a_foodleveldietarydata_uk.dta")
+
+data56 <- read_dta("ndns_rp_yr5-6a_foodleveldietarydata.dta")
+
+data78 <- read_dta("ndns_rp_yr7-8a_foodleveldietarydata.dta")
+
+names(data)
+
+names(data56)
+
+names(data78)
+
+names(data)[names(data)=="seriali"] <- "id"
+names(data56)[names(data56)=="seriali"] <- "id"
+names(data78)[names(data78)=="seriali"] <- "id"
+
+
+
+# Extract the data we needed ----------------------------------------------
+
+
+df14d <- data[,c(113,1,2,3,5,6,7,8,9,21, 22, 23, 24,53, 55,57,58,59,60,61,62,63,64,65)]
+
+var <- names(df14d)
+
+df56d <- data56 %>% 
+  select(var)
+
+df78d <- data78 %>% 
+  select(var)
+
+dfs1 <- rbind(df14d, df56d, df78d)
+
+
+dfs2 <- dfs1[dfs1$Age>=19,]
+rm(data, data56, data78)
+
+dfs2
+
+
+# Calculate the time (minute and hour) when they eat ----------------------
+
+dfs2$MealTime_chr <- as.character(dfs2$MealTime)
+dfs2$MealTime_hm <- unlist(strsplit(dfs2$MealTime_chr," "))[c(FALSE, TRUE)]
+
+
+dfs2$MealHourN <- as.numeric(unlist(strsplit(dfs2$MealTime_hm,":"))[c(TRUE, FALSE, FALSE)])
[…]

### 2018-08-13 paper/Chapters/Chapter3.tex
carb each time slot
individual level fig table added

@@
 		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
-		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviation}: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index;}}\\ 
+		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index;}}\\ 
 		\multicolumn{6}{l}{{\scriptsize Lo-Mendel-Rubin LRT, likelihood ratio test comparing $q$ classes models with $q-1$ classes models.}}\\
@@
 	\centering
-	\includegraphics[width=14cm]{Figures/level1.png}
+	\includegraphics[width=13cm]{Figures/level1.png}
 	\decoRule
@@
 
-\subsection{Features of the three types of carbohydrate eating temporal patterns}\vspace{-0.5cm}
+\subsection{Features of the three types of carbohydrate eating temporal patterns}
 
@@
 
-\begin{table}[H]
+\begin{table}
 
@@
 		\showrowcolors
-		Counts (\%) & 9667 (39.5) & 5002 (20.4\%) & 9814 (40.1\%) & \\
+		Counts (\%) & 9667 (39.5) & 5002 (20.4) & 9814 (40.1) & \\
 		Country (\%) &  &  &  & < 0.001\\
@@
 
-With two individual level latent classes \textbf{(Figure \ref{fig:CB2level2})}, one individual class is comprised of individuals with a relatively slightly higher proportion of having "low carbohydrate day" (22.1\%) compared to the other (17.4\%).
-This class represents nearly 65\% of the individuals.
-However, we believe these individual classes are not very distinguishable to each other.
-
-\begin{figure}
+\begin{figure}[H]
 	%\vspace*{13cm}
@@
 \end{figure}
+
+With two individual level latent classes \textbf{(Figure \ref{fig:CB2level2})}, one individual class is comprised of individuals with a relatively slightly higher proportion of having "low carbohydrate day" (22.1\%) compared to the other (17.4\%).
+This class represents nearly 65\% of the individuals.
+However, we believe these individual classes are not very distinguishable to each other.
 
@@
 
+Average total energy intake over the 4 days of dietary survey was the highest (7985.8 kJ) in the low carbohydrate eaters group.
+As expected, the mean of total carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively.
+Energy contribution from carbohydrate was close to 50\% in the high carbohydrate eaters, but was only 40.6\% in the low carbohydrate eaters.
+It is noteworthy that low carbohydrate eaters consumed the highest average amount of protein (79.9 g, 17.2\% of total energy), fat (74.7g, 35.4\% of total energy), and alcohol (20.8 g, 6.8\% of total energy).
+
+\begin{figure}[H]
+	%\vspace*{13cm}
+	\centering
+	\includegraphics[width=13cm]{Figures/CBenergysources.png}
+	\decoRule
+	\caption[Sources of Energy Contribution at Each Time Slot by Individual Carbohydrate Eating Groups.]{Sources of Energy Contribution at Each Time Slot by Individual Carbohydrate Eating Groups.}
+	\label{fig:level1}
+\end{figure}
+\vspace{-0.6cm}
+
 The social-demographic characteristics of the UK adults according to their individual level latent class membership are shown in \textbf{Table \ref{tab:Level2tab1}}.
@@
 
-Average total energy intake over the 4 days of dietary survey was the highest (7985.8 kJ) in the low carbohydrate eaters group.
-As expected, the mean of total carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively.
-Energy contribution from carbohydrate was close to 50\% in the high carbohydrate eaters, but was only 40.6\% in the low carbohydrate eaters.
-It is noteworthy that low carbohydrate eaters consumed the highest average amount of protein (79.9 g, 17.2\% of total energy), fat (74.7g, 35.4\% of total energy), and alcohol (20.8 g, 6.8\% of total energy).
-
 From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetic (diagnosed by A1C > 6.5\%), while the percentages of diabetes in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011), respectively.
@@
 Total cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}[H]
+
+	\caption{\label{tab:tab-nutri-indi}Weighted means and percentages (95\%CI) of the nutrients intake according to individual level carbohydrate eating latent classes.
+\\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
+	\centering
+	\fontsize{9}{11}\selectfont
+	\begin{tabular}[t]{lcccc}
+		\hiderowcolors
+		\toprule
+	\textbf{Variables} & \textbf{\Centerstack{Low carbo-\\hydrate eaters\\(n = 1730)}} & \textbf{\Centerstack{Moderate carbo-\\hydrate eaters\\(n = 1772)}} & \textbf{\Centerstack{High carbo-\\hydrate eaters\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
+		\midrule
+		\showrowcolors
+		Total energy (kJ) & 7985.8 (7823.3, 8146.295) & 7341.8 (7825.3, 8146.3) & 7677 (7555.8, 7799,8) & < 0.001\\
+		Carbohydrate (g) & 203.8 (199.8, 207.8) & 218.3 (212.9, 223.7) & 233.4 (229.6, 237.2) & < 0.001\\
+		\hspace{1em}\textbf{6 am – 9 am} & 23.0 (21.8,  24.3) & 11.2 (10.0, 12.3) & 37.9 (36.8, 39.2) & \\
+		\hspace{2em}Fibre (g) & 1.4 (1.3, 1.5) & 0.6 (0.5, 0.7) & 2.0 (1.9, 2.2) & \\
+		\hspace{2em}Sugar (g) & 10.2 (9.6, 10.9) & 5.3 (4.8, 5.8) & 19.7 (19.0, 20.4) & \\
+		\hspace{3em}NMES (g)\textsuperscript{\dag} & 4.7 (4.3, 5.1) & 3.2 (2.9, 3.6) & 11.1 (10.7, 11.6) & \\
+		\hspace{2em}Starch (g) & 12.8 (12.0, 13.5) & 5.9 (5.1, 6.6) & 18.3 (17.6, 19.1) & \\
+		\hspace{1em}\textbf{9 am – 12 am} & 25.1 (23.9, 26.3) & 33.0 (31.4, 34.6) & 26.2 (25.1, 27.2) & \\
+		\hspace{2em}Fibre (g) & 1.5 (1.4, 1.6) & 1.6 (1.5, 1.7) & 1.3 (1.2, 1.3) & \\
+		\hspace{2em}Sugar (g) & 11.6 (10.9, 12.3) & 15.7 (14.8, 16.6) & 14.2 (13.6, 14.8) & \\
+		\hspace{3em}NMES (g)\textsuperscript{\dag} & 5.7 (5.2, 6.2) & 9.6 (8.9, 10.2) & 8.1 (7.7, 8.5) & \\
+		\hspace{2em}Starch (g) & 13.5 (12.8, 14.3) & 17.3 (16.4, 18.3) & 11.9 (11.3, 12.6) & \\
+		\hspace{1em}\textbf{12 noon – 2 pm} & 42.6 (40.9, 44.3) & 38.7 (37.0, 40.4) & 51.6 (50.2, 52.9) & \\
+		\hspace{2em}Fibre (g) & 3.1 (2.9, 3.2) & 2.3 (2.2, 2.5) & 3.6 (3.5, 3.7) & \\
+		\hspace{2em}Sugar (g) & 14.7 (14.0, 15.4) & 14.9 (14.0, 15.7) & 19.4 (18.7, 20.0) & \\
+		\hspace{3em}NMES (g)\textsuperscript{\dag} & 7.3 (6.7, 7.8) & 9.1 (8.4, 9.8) & 10.3 (9.8, 10.8) & \\
+		\hspace{2em}Starch (g) & 27.9 (26.6, 29.1) & 23,8 (22.6, 24.9) & 32.2 (31.2, 33.1) & \\
+		\hspace{1em}\textbf{2 pm – 5 pm} & 25.0 (23.6, 26.4) & 33.6 (31.6, 35.6) & 24.7 (23.6, 25.7) & \\
+		\hspace{2em}Fibre (g) & 1.6 (1.5, 1.7) & 1.9 (1.7, 2.0) & 1.3 (1.2, 1.4) & \\
+		\hspace{2em}Sugar (g) & 11.9 (11.3, 12.7) & 14.5 (13.5, 15.5) & 13.4 (12.8, 13.9) & \\
+		\hspace{3em}NMES (g)\textsuperscript{\dag} & 6.9 (6.4, 7.5) & 9.9 (9.0, 8.6) & 8.6 (8.2, 9.1) & \\
+		\hspace{2em}Starch (g) & 13.1 (12.1, 13.9) & 19.1 (17.7, 20.4) & 11.3 (10.6, 11.9) & \\
+		\hspace{1em}\textbf{5 pm – 8 pm} & 55.9 (54.1, 57.9) & 54.6 (52.1, 57.0) & 62.9 (61.3, 64.4) & \\
+		\hspace{2em}Fibre (g) & 4.4 (4.2, 4.5) & 3.7 (3.5, 3.9) & 4.9 (4.7, 5.0) & \\
+		\hspace{2em}Sugar (g) & 18.7 (17.9, 19.5) & 18.6 (17.6, 19.5) & 21.8 (20.9, 22.5) & \\
+		\hspace{3em}NMES (g)\textsuperscript{\dag} & 10.2 (9.6, 10.8) & 11.8 (10.9, 12.6) & 12.1 (11.4, 12.7) & \\
+		\hspace{2em}Starch (g) & 37.3 (35.8, 38.8) & 35.9 (34.1, 37.9) & 41.1 (39.9, 42.2) & \\
+		\hspace{1em}\textbf{8 pm – 10 pm} & 23.3 (21.9, 24.6) & 29.7 (27.6, 31.7) & 23.7 (22.5, 24.9) & \\
+		\hspace{2em}Fibre (g) & 1.4 (1.3, 1.6) & 1.6 (1.5, 1.8) & 1.3 (1.5, 1.8) & \\
+		\hspace{2em}Sugar (g) & 10.9 (10.3, 11.5) & 13.2 (12.2, 14.2) & 12.4 (11.8, 13.0) & \\
+		\hspace{3em}NMES (g)\textsuperscript{\dag} & 7.3 (6.8, 7.8) & 9.4 (8.5, 10.4) & 8.3 (7.8, 8.8) & \\
+		\hspace{2em}Starch (g) & 12.3 (11.4, 13.3) & 16.4 (15.0, 17.8) & 11.3 (10.5, 12.1) & \\
+		\hspace{1em}\textbf{10 pm – 6 am} & 8.8 (7.7, 9.8) & 17.6 (15.2, 19.9) & 6.4 (5.8, 7.1) & \\
+		\hspace{2em}Fibre (g) & 0.34 (0.29, 0.39) & 0.74 (0.63, 0.85) & 0.24 (0.21, 0.27) & \\
+		\hspace{2em}Sugar (g) & 5.3 (4.6, 6.1) & 10.0 (8.6, 11.5) & 4.1 (3.7, 4.5) & \\
+		\hspace{3em}NMES (g)\textsuperscript{\dag} & 3.9 (3.3, 4.6) & 7.7 (6.4, 8.9) & 2.9 (2.6, 3.3) & \\
+		\hspace{2em}Starch (g) & 3.5 (2.9, 3.9) & 7.5 (6.3, 8.8) & 2.3 (1.9, 2.7) & \\
+		Carbohydrate (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
+		Protein (g) & 79.9 (77.9, 81.8) & 69.3 (67.6, 71.0) & 73.7 (72.5, 74.8) & < 0.001\\
+		Protein (\%) & 17.2 (16.9, 17.5) & 16.3 (16.0, 16.6) & 16.5 (16.3, 16.6) & < 0.001\\
+		Fat (g) & 74.7 (73.1, 76.4) & 63.8 (62.1, 65.5) & 65.7 (64.4, 67.0) & < 0.001\\
+		Fat (\%) & 35.4 (34.9, 35.8) & 32.5 (32.1, 32.9) & 32.0 (31.7, 32.3) & < 0.001\\
+		Alcohol (g) & 20.8 (18.3, 23.2) & 10.7 (9.4, 11.9) & 8.9 (8.1, 9.8) & < 0.001\\
+		\bottomrule
+		\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from chi-square test for categorical variables, and one-way ANOVA comparing the means}}\\
+		\multicolumn{5}{l}{{\scriptsize  in multiple groups for continuous variables;}}\\
+		\multicolumn{5}{l}{\textsuperscript{\dag} NMES, Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey, }\\
+		\multicolumn{5}{l}{{\scriptsize glucose, fructose and glucose syrups, sugars added to food and sugars in fruit juices.}}\\
+	\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
 
@@
 		Total energy intake (kJ) & \Centerstack{7985.8\\(7823.3, 8146.3)} & \Centerstack{7341.8\\(7825.3, 8146.3)} & \Centerstack{7677.0\\(7555.8, 7799.8)} & < 0.001\\
-		Carbohydrate intake (g) & \Centerstack{203.8\\(199.8, 207.8)} & \Centerstack{218.3\\(212.9, 223.7)} & \Centerstack{233.4\\(229.6, 237.2)} & < 0.001\\
-		Carbohydrate percent\textsuperscript{\ddag} (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
-		Protein intake (g) & 79.9 (77.9, 81.8) & 69.3 (67.6, 71.0) & 73.7 (72.5, 74.8) & < 0.001\\
-		Protein percent (\%) & 17.2 (16.9, 17.5) & 16.3 (16.0, 16.6) & 16.5 (16.3, 16.6) & < 0.001\\
-		Fat intake (g) & 74.7 (73.1, 76.4) & 63.8 (62.1, 65.5) & 65.7 (64.4, 67.0) & < 0.001\\
-		Fat percent (\%) & 35.4 (34.9, 35.8) & 32.5 (32.1, 32.9) & 32.0 (31.7, 32.3) & < 0.001\\
-		Alcohol intake (g) & 20.8 (18.3, 23.2) &  10.7 (9.4, 11.9) & 8.9 (8.1, 9.8) & < 0.001 \\
-		Alcohol percent (\%) &  6.8 (6.3, 7.4) &  3.8 (3.4, 4.3) & 3.2 (2.9, 3.4)& < 0.001 \\
+%		Carbohydrate intake (g) & \Centerstack{203.8\\(199.8, 207.8)} & \Centerstack{218.3\\(212.9, 223.7)} & \Centerstack{233.4\\(229.6, 237.2)} & < 0.001\\
+%		Carbohydrate percent\textsuperscript{\ddag} (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
+%		Protein intake (g) & 79.9 (77.9, 81.8) & 69.3 (67.6, 71.0) & 73.7 (72.5, 74.8) & < 0.001\\
+%		Protein percent (\%) & 17.2 (16.9, 17.5) & 16.3 (16.0, 16.6) & 16.5 (16.3, 16.6) & < 0.001\\
+%		Fat intake (g) & 74.7 (73.1, 76.4) & 63.8 (62.1, 65.5) & 65.7 (64.4, 67.0) & < 0.001\\
+%		Fat percent (\%) & 35.4 (34.9, 35.8) & 32.5 (32.1, 32.9) & 32.0 (31.7, 32.3) & < 0.001\\
+%		Alcohol intake (g) & 20.8 (18.3, 23.2) &  10.7 (9.4, 11.9) & 8.9 (8.1, 9.8) & < 0.001 \\
+%		Alcohol percent (\%) &  6.8 (6.3, 7.4) &  3.8 (3.4, 4.3) & 3.2 (2.9, 3.4)& < 0.001 \\
 		Glucose (mmol/l) & 5.17 (5.12, 5.23) & 5.05 (4.99, 5.13) & 5.10 (5.05, 5.15) & 0.027\\
@@
 		\multicolumn{5}{l}{{\scriptsize or under treatment for hypertension.}}\\
-		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake.}}\\  
+%		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake.}}\\  
 		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\S} DM was defined by A1C $>$ 6.5\%.}}\\

### 2018-08-13 paper/Tables/2by2Table1.Rmd
individual level fig table added

@@
   add_footnote(c("P values were obtained from chi-square test for categorical variables, and one-way ANOVA comparing the means in multiple groups for continuous variables;", 
-                       "Non-milk extrinsic sugar is defined as:"),  notation = "symbol")
+                       "Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey, glucose, fructose and glucose syrups, sugars added to food and sugars in fruit juices."),  notation = "symbol")
 
@@
                notation = "symbol")
+```
+
+# personal level classes nutrional table
+
+```{r tab-nutri-indi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Carbslotcompo.csv", header = T, row.names = NULL, colClasses = "character")
+names(dt) <- c(" ", "Low carbohydrate eaters (n = 1730)", "Moderate carbohydrate eaters (n = 1772)", "High carbohydrate eaters (n = 2653)", "P value[note]")
+
+dt[6, 1] <- c("Non-milk extrinsic sugar[note]")
+
+kable(dt,  align = "l", row.names = FALSE,
+              format = "latex", caption = "Weighted means and percentages (95CI) of the nutrients intake according to individual level carbohydrate eating latent classes.", booktabs = T,linesep = "") %>%
+    add_indent(c(3:37)) %>% 
+ kable_styling(latex_options = c("striped"), font_size = 9) %>% 
+  add_footnote(c("P values were obtained from chi-square test for categorical variables, and one-way ANOVA comparing the means in multiple groups for continuous variables;", 
+                       "Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey, glucose, fructose and glucose syrups, sugars added to food and sugars in fruit juices."),  notation = "symbol")
 ```

### 2018-08-13 paper/Tables/2by2Table1.tex
individual level fig table added

@@
 \hspace{1em}\hspace{1em}Log-likelihood & -173793.306 & -172669.771 & -172039.204 & -171633.941 & -171377.292\\
+\hspace{1em}\hspace{1em}AIC & 347614.612 & 345397.542 & 344166.407 & 343385.883 & 342902.585\\
 \hspace{1em}\hspace{1em}BIC & 347728.092 & 345632.608 & 344523.06 & 343864.121 & 343502.409\\
-\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & -- & < 0.0001 & 1e-04 & < 0.0001 & < 0.0001\\
+\hspace{1em}\hspace{1em}aBIC & 347683.601 & 345540.447 & 344383.229 & 343676.621 & 343267.239\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Random effects model}}\\
+\hspace{1em}Lo-Mendell-Rubun LRT & -- & < 0.0001 & 1e-04 & < 0.0001 & < 0.0001\\
 \hspace{1em}\hspace{1em}Entropy & 1 & 0.31 & 0.392 & 0.51 & 0.481\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Random effects model}}\\
-\hspace{1em}2 between classes &  &  &  &  & \\
+\hspace{1em}\hspace{1em}2 between classes &  &  &  &  & \\
 \hspace{1em}\hspace{1em}No. of free parameters &  & 59 & 89 & 119 & \\
 \hspace{1em}\hspace{1em}Log-likelihood &  & -169331.132 & -168700.96 & -168366.193 & \\
-\hspace{1em}\hspace{1em}BIC &  & 339258.502 & 338301.338 & 337934.968 & \\
+\hspace{1em}BIC &  & 339258.502 & 338301.338 & 337934.968 & \\
 \hspace{1em}\hspace{1em}Entropy &  & 0.581 & 0.569 & 0.555 & \\
-\hspace{1em}3 between classes &  &  &  &  & \\
+\hspace{1em}\hspace{1em}3 between classes &  &  &  &  & \\
 \hspace{1em}\hspace{1em}No. of free parameters &  & 89 & 134 & 179 & \\
 \hspace{1em}\hspace{1em}Log-likelihood &  & -166936.279 & -166348.815 & -166062.761 & \\
-\hspace{1em}\hspace{1em}BIC &  & 334771.968 & 334051.799 & 333934.448 & \\
+\hspace{1em}BIC &  & 334771.968 & 334051.799 & 333934.448 & \\
 \hspace{1em}\hspace{1em}Entropy &  & 0.677 & 0.63 & 0.644 & \\
-\hspace{1em}4 between classes &  &  &  &  & \\
+\hspace{1em}\hspace{1em}4 between classes &  &  &  &  & \\
 \hspace{1em}\hspace{1em}No. of free parameters &  & 119 & 179 &  & \\
 \hspace{1em}\hspace{1em}Log-likelihood &  & -165441.731 & -164845.696 &  & \\
-\hspace{1em}\hspace{1em}BIC &  & 332086.045 & 331500.318 &  & \\
-\hspace{1em}\hspace{1em}Entropy &  & 0.729 & 0.659 &  & \\
+BIC &  & 332086.045 & 331500.318 &  & \\
+Entropy &  & 0.729 & 0.659 &  & \\
 \bottomrule
@@
 \multicolumn{5}{l}{means in multiple groups for continuous variables;}\\
-\multicolumn{5}{l}{\textsuperscript{\dag} Non-milk extrinsic sugar is defined as:}\\
+\multicolumn{5}{l}{\textsuperscript{\dag} Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey,}\\
+\multicolumn{5}{l}{glucose, fructose and glucose syrups, sugars added to food and sugars in fruit juices.}\\
 \end{tabular}
@@
 \multicolumn{5}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership.}\\
+\end{tabular}
+\end{table}
+
+\rowcolors{2}{white}{white}
+
+\section{personal level classes nutrional
+table}\label{personal-level-classes-nutrional-table}
+
+\rowcolors{2}{gray!6}{white}
+
+\begin{table}
+
+\caption{\label{tab:tab-nutri-indi}Weighted means and percentages (95CI) of the nutrients intake according to individual level carbohydrate eating latent classes.}
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{lllll}
+\hiderowcolors
+\toprule
+  & Low carbohydrate eaters (n = 1730) & Moderate carbohydrate eaters (n = 1772) & High carbohydrate eaters (n = 2653) & P value\textsuperscript{*}\\
+\midrule
+\showrowcolors
+Total energy intake (kJ) & 7985.8 (7823.3, 8146.295) & 7341.8 (7825.3, 8146.3) & 7677 (7555.8, 7799,8) & < 0.001\\
+Carbohydrate intake (g) & 203.8 (199.8, 207.8) & 218.3 (212.9, 223.7) & 233.4 (229.6, 237.2) & < 0.001\\
+\hspace{1em}6 am – 9 am & 23.0 (21.8,  24.3) & 11.2 (10.0, 12.3) & 37.9 (36.8, 39.2) & \\
+\hspace{1em}Fibre (g) & 1.4 (1.3, 1.5) & 0.6 (0.5, 0.7) & 2.0 (1.9, 2.2) & \\
+\hspace{1em}Sugar (g) & 10.2 (9.6, 10.9) & 5.3 (4.8, 5.8) & 19.7 (19.0, 20.4) & \\
+\hspace{1em}Non-milk extrinsic sugar\textsuperscript{\dag} & 4.7 (4.3, 5.1) & 3.2 (2.9, 3.6) & 11.1 (10.7, 11.6) & \\
+\hspace{1em}Starch (g) & 12.8 (12.0, 13.5) & 5.9 (5.1, 6.6) & 18.3 (17.6, 19.1) & \\
+\hspace{1em}9 am – 12 am & 25.1 (23.9, 26.3) & 33.0 (31.4, 34.6) & 26.2 (25.1, 27.2) & \\
+\hspace{1em}Fibre (g) & 1.5 (1.4, 1.6) & 1.6 (1.5, 1.7) & 1.3 (1.2, 1.3) & \\
+\hspace{1em}Sugar (g) & 11.6 (10.9, 12.3) & 15.7 (14.8, 16.6) & 14.2 (13.6, 14.8) & \\
+\hspace{1em}Non-milk extrinsic sugar (g) & 5.7 (5.2, 6.2) & 9.6 (8.9, 10.2) & 8.1 (7.7, 8.5) & \\
+\hspace{1em}Starch (g) & 13.5 (12.8, 14.3) & 17.3 (16.4, 18.3) & 11.9 (11.3, 12.6) & \\
+\hspace{1em}12 noon – 2 pm & 42.6 (40.9, 44.3) & 38.7 (37.0, 40.4) & 51.6 (50.2, 52.9) & \\
+\hspace{1em}Fibre (g) & 3.1 (2.9, 3.2) & 2.3 (2.2, 2.5) & 3.6 (3.5, 3.7) & \\
+\hspace{1em}Sugar (g) & 14.7 (14.0, 15.4) & 14.9 (14.0, 15.7) & 19.4 (18.7, 20.0) & \\
+\hspace{1em}Non-milk extrinsic sugar (g) & 7.3 (6.7, 7.8) & 9.1 (8.4, 9.8) & 10.3 (9.8, 10.8) & \\
+\hspace{1em}Starch (g) & 27.9 (26.6, 29.1) & 23,8 (22.6, 24.9) & 32.2 (31.2, 33.1) & \\
+\hspace{1em}2 pm – 5 pm & 25.0 (23.6, 26.4) & 33.6 (31.6, 35.6) & 24.7 (23.6, 25.7) & \\
+\hspace{1em}Fibre (g) & 1.6 (1.5, 1.7) & 1.9 (1.7, 2.0) & 1.3 (1.2, 1.4) & \\
+\hspace{1em}Sugar (g) & 11.9 (11.3, 12.7) & 14.5 (13.5, 15.5) & 13.4 (12.8, 13.9) & \\
+\hspace{1em}Non-milk extrinsic sugar (g) & 6.9 (6.4, 7.5) & 9.9 (9.0, 8.6) & 8.6 (8.2, 9.1) & \\
+\hspace{1em}Starch (g) & 13.1 (12.1, 13.9) & 19.1 (17.7, 20.4) & 11.3 (10.6, 11.9) & \\
+\hspace{1em}5 pm – 8 pm & 55.9 (54.1, 57.9) & 54.6 (52.1, 57.0) & 62.9 (61.3, 64.4) & \\
+\hspace{1em}Fibre (g) & 4.4 (4.2, 4.5) & 3.7 (3.5, 3.9) & 4.9 (4.7, 5.0) & \\
+\hspace{1em}Sugar (g) & 18.7 (17.9, 19.5) & 18.6 (17.6, 19.5) & 21.8 (20.9, 22.5) & \\
+\hspace{1em}Non-milk extrinsic sugar (g) & 10.2 (9.6, 10.8) & 11.8 (10.9, 12.6) & 12.1 (11.4, 12.7) & \\
+\hspace{1em}Starch (g) & 37.3 (35.8, 38.8) & 35.9 (34.1, 37.9) & 41.1 (39.9, 42.2) & \\
+\hspace{1em}8 pm – 10 pm & 23.3 (21.9, 24.6) & 29.7 (27.6, 31.7) & 23.7 (22.5, 24.9) & \\
+\hspace{1em}Fibre (g) & 1.4 (1.3, 1.6) & 1.6 (1.5, 1.8) & 1.3 (1.5, 1.8) & \\
+\hspace{1em}Sugar (g) & 10.9 (10.3, 11.5) & 13.2 (12.2, 14.2) & 12.4 (11.8, 13.0) & \\
+\hspace{1em}Non-milk extrinsic sugar (g) & 7.3 (6.8, 7.8) & 9.4 (8.5, 10.4) & 8.3 (7.8, 8.8) & \\
+\hspace{1em}Starch (g) & 12.3 (11.4, 13.3) & 16.4 (15.0, 17.8) & 11.3 (10.5, 12.1) & \\
+\hspace{1em}10 pm – 6 am & 8.8 (7.7, 9.8) & 17.6 (15.2, 19.9) & 6.4 (5.8, 7.1) & \\
+\hspace{1em}Fibre (g) & 0.34 (0.29, 0.39) & 0.74 (0.63, 0.85) & 0.24 (0.21, 0.27) & \\
+\hspace{1em}Sugar (g) & 5.3 (4.6, 6.1) & 10.0 (8.6, 11.5) & 4.1 (3.7, 4.5) & \\
+\hspace{1em}Non-milk extrinsic sugar (g) & 3.9 (3.3, 4.6) & 7.7 (6.4, 8.9) & 2.9 (2.6, 3.3) & \\
+\hspace{1em}Starch (g) & 3.5 (2.9, 3.9) & 7.5 (6.3, 8.8) & 2.3 (1.9, 2.7) & \\
+Carbohydrate percent (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
+Protein intake (g) & 79.9 (77.9, 81.8) & 69.3 (67.6, 71.0) & 73.7 (72.5, 74.8) & < 0.001\\
+Protein percent (\%) & 17.2 (16.9, 17.5) & 16.3 (16.0, 16.6) & 16.5 (16.3, 16.6) & < 0.001\\
+Fat intake (g) & 74.7 (73.1, 76.4) & 63.8 (62.1, 65.5) & 65.7 (64.4, 67.0) & < 0.001\\
+Fat percent (\%) & 35.4 (34.9, 35.8) & 32.5 (32.1, 32.9) & 32.0 (31.7, 32.3) & < 0.001\\
+Alcohol intake (g) & 20.8 (18.3, 23.2) & 10.7 (9.4, 11.9) & 8.9 (8.1, 9.8) & < 0.001\\
+\bottomrule
+\multicolumn{5}{l}{\textsuperscript{*} P values were obtained from chi-square test for categorical variables, and one-way ANOVA comparing the means in multiple groups for continuous}\\
+\multicolumn{5}{l}{variables;}\\
+\multicolumn{5}{l}{\textsuperscript{\dag} Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey, glucose, fructose and glucose syrups, sugars added}\\
+\multicolumn{5}{l}{to food and sugars in fruit juices.}\\
 \end{tabular}

### 2018-08-13 paper/Figures/Figureforpaper.R

@@ -259,6 +259,8 @@ grViz("
 #       ")
 
 # Time slots level 1 classes ----------------------------------------------
+library(readr)
+library(tidyverse)
 
 
 CW3CB2 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB2.txt",
@@ -654,3 +656,212 @@ ggplot() +
         text=element_text(family="Atlas Grotesk Light")) +
   labs(title = " ", x = "Between Individual classes", y = "Percentage") +
   scale_y_continuous(labels=percent)
+
+
+
+
+# Sources energy by slot --------------------------------------------------
+library(plyr)
+library(readr)
+CB1sources <- read_csv("Tablecsv/CB1sources.csv")
+library(ggthemr)
+ggthemr("dust", layout = "scientific")
+library(scales)
+CB1sources$Slot <- factor(CB1sources$Slot, levels = c("6 am – 9 am", 
+                                                  "9 am – 12 am",
+                                                  "12 noon – 2 pm",
+                                                  "2 pm – 5 pm",
+                                                  "5 pm – 8 pm",
+                                                  "8 pm – 10 pm",
+                                                  "10 pm – 6 am"))
+
+CB1sources$Sources <- factor(CB1sources$Sources, levels = c("Alc", 
+                                                            "Protein",
+                                                            "Fat", 
+                                                            "Carbohydrate"), 
+                             labels = c( "Alcohol", "Protein",  "Fat", "Carbo"))
+
+
+
+CB1sources <- CB1sources[order(CB1sources$Slot, CB1sources$Sources),]
+CB1sources <- ddply(CB1sources, .(Slot), 
+                    transform, pos = cumsum(pct) - (0.5 * pct)) 
+CB1sources$pos[1] <- -0.03
+CB1sources$pos[5] <- -0.03
+CB1sources$pos[9] <- -0.03
+# CB1sources$pos[13] <- -0.03
+
+CB1sources$Sources <- factor(CB1sources$Sources,
+                             levels = c("Carbo", "Fat", "Protein",  "Alcohol"))
+
+Text <- data.frame(levels(CB1sources$Slot))
+names(Text)[1] <- "Slot"
+Text$TotalEner <-  c("753.1 kJ", "854.6 kJ", "1622.1 kJ", "950.8 kJ", 
[…]

### 2018-08-13 paper/Chapters/Chapter2.tex
adding energy sources figures

@@
 Descriptive statistics for sample characteristics are presented as weighted means (95\% CI) or weighted percentages (95\%CI).
-After examining the distribution of the data, the following variables were log-transformed to improve normality: blood glucose, A1C, TC, LDL, HDL, TG, and average physical activity duration per day.
+After examining the distribution of the data, the following variables were log-transformed to improve normality: fasting blood glucose, A1C, TC, LDL, HDL, TG, and average physical activity duration per day.
 Weighted geometric means (95\% CI) were used for all log-transformed variables.
+
+To see whether there is any temporal pattern for food intake eating could also be defined at individual level, weighted estimates of nutrients consumption across the 7 time slots of the day were calculated for each individual level latent class.
+Contributions (\%) of the average energy intake within time slots were evaluated by determining the percentages of energy coming from carbohydrate, fat, protein, and alcohol intake.
+
 For continuous variables, the \textit{F} test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across $>$ 2 classes when applicable.

### 2018-08-13 paper/Chapters/Chapter3.tex
adding energy sources figures

@@
 
-	\caption{\label{tab:day-level-features}Means (standard deviations), and counts (\%) of the characteristics of different types of days according to carbohydrate intake.}\vspace{-0.3cm}
+	\caption{\label{tab:day-level-features}Means (standard deviations), and counts (\%) of the characteristics of different types of carbohydrate eating days.}\vspace{-0.3cm}
 	\centering
@@
 Moderate carbohydrate eaters have comparable proportions (42.0\% vs.
-40.0\%) of having high carbohydrate days and regular meals day, 18.0\% of their dietary diary were identified as low carbohydrate days.\vspace{-0.2cm}
+40.0\%) of having high carbohydrate days and regular meals day, 18.0\% of their dietary diary were found to be low carbohydrate days.
 
@@
 
-Average total energy intake over the 4 days of dietary survey was the highest (7985.8 kJ) in the low carbohydrate eaters group.
-As expected, the mean of total carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively.
-Energy contribution from carbohydrate was close to 50\% in the high carbohydrate eaters, but was only 40.6\% in the low carbohydrate eaters.
-It is noteworthy that low carbohydrate eaters consumed the highest average amount of protein (79.9 g, 17.2\% of total energy), fat (74.7g, 35.4\% of total energy), and alcohol (20.8 g, 6.8\% of total energy).
+After recognising that there were three potential latent groups of carbohydrate eaters in the UK adults, whose food consumption pattern were also probably switching from one to another, their average carbohydrate contribution to total energy intake (as well as the subtypes of carbohydrate actually consumed) within the 7 pre-defined time slots of the day were still of interest.
+Survey-design-weighted mean energy intake within each time slot of the day and their sources of contribution are illustrated in \textbf{Figure \ref{fig:energysourcesCB}}, weighted mean nutrients intakes are listed in \textbf{Table \ref{tab:tab-nutri-indi}}.
 
@@
 	\caption[Sources of Energy Contribution at Each Time Slot by Individual Carbohydrate Eating Groups.]{Sources of Energy Contribution at Each Time Slot by Individual Carbohydrate Eating Groups.}
-	\label{fig:level1}
+	\label{fig:energysourcesCB}
 \end{figure}
@@
 
-The social-demographic characteristics of the UK adults according to their individual level latent class membership are shown in \textbf{Table \ref{tab:Level2tab1}}.
-Moderate carbohydrate eaters were relatively younger (\textit{p} < 0.001), and slightly less from England (\textit{p} = 0.007).
-Gender distribution across the three types of carbohydrate eaters was fairly even (\textit{p} = 0.119).
-The distribution of the carbohydrate eater types turned out to be changing with the year of survey.
-Low carbohydrate eaters represented 32.5\% of the population in the first year of survey, but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year.
-Proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015).
-There was no evidence of difference in employment status across three types of carbohydrate eaters.
-However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with partner (\textit{p} < 0.001); moderate carbohydrate eaters had the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.
-\vspace{-0.2cm}
+Among the three types of carbohydrate eaters, the mean of total energy intake over the 4 days of dietary survey was the highest (7985.8 kJ, 95\%CI: 7283.3, 8146.3) in the low carbohydrate eaters group, and the lowest (7341.8 kJ, 95\%CI: 7172.5, 7511.2) in the moderate eaters group \textbf{(Table \ref{tab:tab-nutri-indi})}.
+Sources of energy for each type of carbohydrate eaters by the 7 time slots were also different.
+Low carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-A)} never had carbohydrate contributed more than 50\% of their total energy throughout the day.
+Energy from fat were the highest for low carbohydrate eaters most of the time during the day (except for time between 10 pm to 6 am next morning).
+Most impressively, energy from alcohol were always the highest in low carbohydrate eaters, percentages for energy from alcohol for the 7 times slots were 1.4\% (6-9 am), 1.8\% (9-12 am), 3.1\% (12-2 pm), 7.2\% (2-5 pm), 8.4\% (5-8 pm), 20.0\% (8-10 pm), and 31.2\% (10 - 6 am), respectively.
+Contribution from different energy sources are quite similar for moderate and high carbohydrate eaters, but their absolute amount of energy consumption at each time slot were largely different.
+Moderate carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-B)} were characterised as consuming the lowest energy (296.9 kJ) before 9 am, but having higher energy consumption (967.9 kJ) between 9 am and 12 noon time compared with low and high carbohydrate eaters.
+Moderate carbohydrate eaters may turn to have later breakfast, later lunch, and probably later dinner as well.
+They had the highest total energy consumption (599.7 kJ) at night (10 pm - 6 am) across three types of eaters.
+High carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-C)} consumed the highest total energy (929.0 kJ) during 6 am to 9 am in the morning and the lowest total energy between 10 pm to 6 am (205.5 kJ).
+Specifically, carbohydrate contribution to total energy intake were 65.3\% (6-9 am), 56.2\% (9-12 am), 46.2\% (12-2 pm), 50.3\% (2-5 pm), 42.5\% (5-8 pm), 44.1\% (8-10 pm), and 49.9\% (10-6am).
+We also noticed that high carbohydrate eaters consumed their energy mainly from three time slots: 6-9 am, 12-2 pm, and 5-8 pm.
 
-Weighted means, percentages of anthropometric measurements, average of main nutrients intake, as well as biochemical characteristic profiles according to the latent carbohydrate eater groups are given in \textbf{Table \ref{tab:tab2}}.
-Low carbohydrate eaters had higher mean BMI (27.8 kg/m\textsuperscript{2}) and larger mean WC (98.9/89.9 cm in men/women) compared with 27.2, 27.3 kg/m\textsuperscript{2}, and 95.9/88.7 (men/women), 98.1/87.2 (men/women) cm in moderate and high carbohydrate eaters.
-Moderate carbohydrate eaters had the highest prevalence of being a current smoker (27.8\%), shortest time of daily physical activity (geometric mean: 0.87 hours/day), and the lowest prevalence of hypertension (20.2\%).
-
-From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetic (diagnosed by A1C > 6.5\%), while the percentages of diabetes in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011), respectively.
-Although there was some evidence (\textit{p} = 0.027) that fasting blood glucose level may be slightly higher in non-diabetic low carbohydrate eaters, the geometric mean for A1C was probably lower in moderate carbohydrate eaters (4.72, 95\%CI: 5.39, 5.47).
-Total cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.
+As expected, in total, the mean of carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively \textbf{(Table \ref{tab:tab-nutri-indi})}.
+Energy contribution from carbohydrate was close to 50\% in the high carbohydrate eaters, but was only 40.6\% in the low carbohydrate eaters.
+In terms of the subtypes (components) of the carbohydrate consumed at each time slot, high carbohydrate eaters consumed as much as more than 2 times (compared to low carbohydrate eaters) and nearly 4 times (against moderate carbohydrate eaterss) the amount of sugar (37.9g 95\% CI: 36.8, 39.2) and non-milk extrinsic sugar (i.e.
+free sugar) (11.1g 95\%CI: 10.7, 11.6) between 6-9 am.
+Moderate carbohydrate eaters had their carbohydrate intake more spread out.
+They consumed more sugar and starch during 9-12 am, 2-5 pm, 8-10 pm, and 10-6 am.
+Low carbohydrate eaters turned to have similar temporal pattern of consuming carbohydrates but the absolute amount of fibre, sugar, free sugar, and starch were usually lower than that in the high carbohydrate eaters except for time slots of 2-5 pm, and 10-6 am.
+Strong evidence (\textit{p} < 0.001) suggested that the mean of total fibre consumption for low,
 
@@
 
-	\caption{\label{tab:tab-nutri-indi}Weighted means and percentages (95\%CI) of the nutrients intake according to individual level carbohydrate eating latent classes.
+	\caption{\label{tab:tab-nutri-indi}Weighted means and percentages (95\%CI) of the nutrients intake according to individual level carbohydrate eating classes.
 \\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
@@
 		\showrowcolors
-		Total energy (kJ) & 7985.8 (7823.3, 8146.295) & 7341.8 (7825.3, 8146.3) & 7677 (7555.8, 7799,8) & < 0.001\\
+		Total energy (kJ) & 7985.8 (7823.3, 8146.3) & 7341.8 (7172.5, 7511.2) & 7677.8 (7555.8, 7799.8) & < 0.001\\
 		Carbohydrate (g) & 203.8 (199.8, 207.8) & 218.3 (212.9, 223.7) & 233.4 (229.6, 237.2) & < 0.001\\
@@
 		Carbohydrate (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
+		Fibre (g) & 13.7 (13.4, 14.0) & 12.5 (12.1, 12.9) & 14.7 (14.4, 14.9) & < 0.001 \\
 		Protein (g) & 79.9 (77.9, 81.8) & 69.3 (67.6, 71.0) & 73.7 (72.5, 74.8) & < 0.001\\
-		Protein (\%) & 17.2 (16.9, 17.5) & 16.3 (16.0, 16.6) & 16.5 (16.3, 16.6) & < 0.001\\
+%		Protein (\%) & 17.2 (16.9, 17.5) & 16.3 (16.0, 16.6) & 16.5 (16.3, 16.6) & < 0.001\\
 		Fat (g) & 74.7 (73.1, 76.4) & 63.8 (62.1, 65.5) & 65.7 (64.4, 67.0) & < 0.001\\
-		Fat (\%) & 35.4 (34.9, 35.8) & 32.5 (32.1, 32.9) & 32.0 (31.7, 32.3) & < 0.001\\
+%		Fat (\%) & 35.4 (34.9, 35.8) & 32.5 (32.1, 32.9) & 32.0 (31.7, 32.3) & < 0.001\\
 		Alcohol (g) & 20.8 (18.3, 23.2) & 10.7 (9.4, 11.9) & 8.9 (8.1, 9.8) & < 0.001\\
@@
 \rowcolors{2}{white}{white}
+
+moderate, and high carbohydrate eaters were different: 13.7g (13.4, 14.0), 12.5g (12.1, 12.9), and 14.7g (14.4, 14.9) with all 95\% CI being exclusive to each other.
+It is also noteworthy that low carbohydrate eaters consumed the highest average amount of protein (79.9 g, 17.2\% of total energy), fat (74.7g, 35.4\% of total energy), and alcohol (20.8 g, 6.8\% of total energy) as we have described for \textbf{Figure \ref{fig:energysourcesCB}}.
+
+The social-demographic characteristics of the UK adults according to their individual level latent class membership are shown in \textbf{Table \ref{tab:Level2tab1}}.
+Moderate carbohydrate eaters were relatively younger (\textit{p} < 0.001), and slightly less from England (\textit{p} = 0.007).
+Gender distribution across the three types of carbohydrate eaters was fairly even (\textit{p} = 0.119).
+The distribution of the carbohydrate eater types turned out to be changing with the year of survey.
+Low carbohydrate eaters represented 32.5\% of the population in the first year of survey, but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year.
+Proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015).
+There was no evidence of difference in employment status across three types of carbohydrate eaters.
+However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with partner (\textit{p} < 0.001); moderate carbohydrate eaters had the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.
+
+Weighted means, percentages of anthropometric measurements, average of main nutrients intake, as well as biochemical characteristic profiles according to the latent carbohydrate eater groups are given in \textbf{Table \ref{tab:tab2}}.
+Low carbohydrate eaters had higher mean BMI (27.8 kg/m\textsuperscript{2}) and larger mean WC (98.9/89.9 cm in men/women) compared with 27.2, 27.3 kg/m\textsuperscript{2}, and 95.9/88.7 (men/women), 98.1/87.2 (men/women) cm in moderate and high carbohydrate eaters.
+Moderate carbohydrate eaters had the highest prevalence of being a current smoker (27.8\%), shortest time of daily physical activity (geometric mean: 0.87 hours/day), and the lowest prevalence of hypertension (20.2\%).
+
+From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetic (diagnosed by A1C > 6.5\%), while the percentages of diabetes in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011), respectively.
+Although there was some evidence (\textit{p} = 0.027) that fasting blood glucose level may be slightly higher in non-diabetic low carbohydrate eaters, the geometric mean for
 
@@
 \rowcolors{2}{white}{white}
+
+A1C was probably lower in moderate carbohydrate eaters (4.72, 95\%CI: 5.39, 5.47).
+Total cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.
 

### 2018-08-13 paper/main.tex
adding energy sources figures

@@
 
-\thesistitle{The time patterns of carbohydrate intake in UK adults -- the National Dietary and Nutrition Survey (NDNS) 2008/09-15/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+\thesistitle{The time patterns of carbohydrate intake in the UK adults -- the National Dietary and Nutrition Survey 2008/09-15/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
 \supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname

### 2018-08-14 paper/Chapters/Chapter4.tex
before meeting Luigi at 14th August

@@
 
-For the first time, as far as we know, the non-parametric MLCA models successfully captured the day-to-day variability within individuals as expected and showed that from the perspective of carbohydrate eating pattern people were switching between different types of carbohydrate consumptions.
+For the first time, as far as we know, the non-parametric MLCA models successfully captured the day-to-day variability within individuals as expected and showed that from the perspective of carbohydrate consumption people were switching between different types of carbohydrate consumptions.
 The MLCA models allowed the probability of a certain type of carbohydrate eating day to vary across individuals.
 This properly accounted for the fact that for some people, their probability of following a regular meals day during the survey was much higher than the others (low carbohydrate eaters); and for some people, their probability of following high carbohydrate eating day during their survey were quite high (high carbohydrate eaters); while for the rest of the participants, they had similar probabilities of following either regular meals day or high carbohydrate eating day (moderate carbohydrate eaters).
+
+Surprisingly, low carbohydrate eaters turned out to consume the highest amount of total energy,
 

### 2018-08-14 paper/Chapters/Chapter3.tex
after last meeting with Luigi

@@
 		\bottomrule
-		\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from chi-square test for categorical variables, and one-way ANOVA comparing the means}}\\
+		\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from $\chi^2$ test for categorical variables, and one-way ANOVA comparing the means}}\\
 		\multicolumn{5}{l}{{\scriptsize  in multiple groups for continuous variables;}}\\

### 2018-08-14 paper/Chapters/Chapter4.tex
after last meeting with Luigi

@@
 Using multilevel LCA as a novel technique, and the NDNS RP dietary database, this project examined carbohydrate eating temporal patterns in the day level, based on which, individual level carbohydrate eating patterns were also defined subsequently.
-Among all of the dietary diaries, there were three distinct latent classes specifically for carbohydrate intake: 1) high probabilities of having high carbohydrate contained for across the hours of day (high carbohydrate day); 2) low carbohydrate food dominant through out the hours of day (low carbohydrate day); and 3) always having lunch and dinner day (regular meals day).
+Among the dietary diaries collected, there were three distinct latent classes specifically for carbohydrate intake: 1) high probabilities of having high carbohydrate contained food across the hours of day (high carbohydrate day); 2) low carbohydrate food dominant through out the hours of day (low carbohydrate day); and 3) always having lunch and dinner day (regular meals day).
 

### 2018-08-14 paper/Chapters/Chapter2.tex
level 1 names changed

@@
 \begin{itemize}
-	\item Not eating any food (Energy intake = 0 kJ); 
+	\item Not eating any food (energy intake = 0 kJ); 
 	\item Eating, and carbohydrate contributed less than 50\% of the total energy intake;
@@
 
-\subsection{Ethics approval}\vspace{-0.3cm}
+\subsection{Ethical approval}\vspace{-0.3cm}
 
-Ethics approval for the survey was obtained form the Oxfordshire A Research Ethics Committee.
+Ethical approval for the survey was obtained form the Oxfordshire A Research Ethics Committee.
 The letters of approval for the original submission and subsequent substantial amendments, together with approved documents, were sent to all Local Research Ethics Committees covering areas where fieldwork was being conducted.
 Research governance approval was sought for all participating NHS laboratories and obtained where required by the Research and Development Committee for each laboratory.
-Ethics approval for the current project was obtained from the MSc Research Ethics Committee of London School of Hygiene \& Tropical Medicine (LSHTM MSc Ethics Ref: 15624).
+Ethical approval for the current project was obtained from the MSc Research Ethics Committee of London School of Hygiene \& Tropical Medicine (LSHTM MSc Ethics Ref: 15624).
 
@@
 \begin{itemize}
-	\item $\text{logit}{x} = \frac{\log(x)}{\log(1-x)}$;
+	\item $\text{logit}{(x)} = \frac{\log(x)}{\log(1-x)}$;
 	\item $P(C_{ij} = 1)$ as the probability that the randomly selected $i$th observation day of $j$th individual is a high carbohydrate eating day;
@@
 	\item Firstly, we ignored the multilevel structure of the data and estimated a series of traditional LC models to determine the number of classes at the observational day-level;
-	\item Next, a series of MLCA models were fitted to account for the multi-level structrure of the data.
+	\item Next, a series of MLCA models were fitted to account for the multilevel structrure of the data.
 In these models, the number of day-level classes was based on the best fitting LCA model from the first step, and the LCA model at the individual level was estimated to identify the number of individual level latent classes;
@@
 In the steps of performing multilevel LCA, where LMR-LRT is not available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day level and individual level.
-MLCA models were fitted in Mplus 7.4 \parencite{muthen2005mplus}, the Mplus codes and outputs are shown in \textbf{Appendix \ref{AppendixB}}.
+MLCA models were fitted in Mplus 7.4 \parencite{muthen2005mplus}, the Mplus syntax and outputs are shown in \textbf{Appendix \ref{AppendixB}}.
 \vspace{-0.3cm}
@@
 	\item Confounding and/or interaction effect from each of the potential factors were checked one by one.
-Interaction effect were tested using the adjusted Wald test comparing models with and without the interaction terms.
+Interaction effect were tested using the adjusted Wald test testing whether the regression coefficients of the interaction terms are simultaneously equal to zero.
 	\item A preliminary model that includes all of the variables suggested to be confounders in the previous step was established. 
@@
 General checking such as QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance) are not available as well.
-Outliers, leverage, and Cook's distance cannot be check either, however, samples with extreme weightings (if exist) were checked by removing them and refit the models as a sensitivity analysis.
+Outliers, leverage, and Cook's distance cannot be check either, however, participants with extreme weightings (if exist) were checked by removing them and refit the models as a sensitivity analysis.
 	\item Since under survey design data, the sampling-weighted least squares are not maximum likelihood, it would not be possible to compare models using likelihood ratio test.

### 2018-08-14 paper/Chapters/Chapter3.tex
level 1 names changed

@@
 
-Class 1 days \textbf{(Figure \ref{fig:level1}-A)} were given the name of "high carbohydrate day" since in these days of survey, the probabilities of carbohydrate contributed higher or equal to 50\% of the energy consumed were always higher than that in the other two types of days.
-Specifically, high carbohydrate days were characterised with probabilities of over 0.6 in time slots between 6 am to 9 am, 9 am to 12 am, and also 2 pm to 5 pm, during which the time slots may be interpreted as breakfast, morning snack, and afternoon snack time periods for many participants.
+Class 1 days \textbf{(Figure \ref{fig:level1}-A)} were given the name of "high percentage carbohydrate day" since in these days of survey, the probabilities of carbohydrate contributed higher or equal to 50\% of the energy consumed were always higher than that in the other two types of days.
+Specifically, high percentage carbohydrate days were characterised with probabilities of over 0.6 in time slots between 6 am to 9 am, 9 am to 12 noon, and also 2 pm to 5 pm, during which the time slots may be interpreted as breakfast, morning snack, and afternoon snack time periods for many participants.
 Moreover, even during late night time period, such as 8 pm to 10 pm, and 10 pm to 6 am time slots, the probabilities of having higher carbohydrate contained food were still as high as 0.412, and 0.246, respectively.
@@
 		\toprule
-		\textbf{Time slots of} & \textbf{Responses to} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1\\(39.5\%)}} & \textbf{\Centerstack{Class 2\\(20.4\%)}} & \textbf{\Centerstack{Class 3\\(40.1\%)}} \\
+		\textbf{Time slots of} & \textbf{Responses to} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1 days\\(39.5\%)}} & \textbf{\Centerstack{Class 2 days\\(20.4\%)}} & \textbf{\Centerstack{Class 3 days\\(40.1\%)}} \\
 		\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
-		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & (\%) & \textbf{\Centerstack{High carbo- \\ hydrate day}} & \textbf{\Centerstack{Low carbo-\\hydrate day}} & \textbf{\Centerstack{Regular\\meals day}}\\
+		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & (\%) & \textbf{\Centerstack{High perc-\\entage carb}} & \textbf{\Centerstack{Low perc-\\entage carb}} & \textbf{\Centerstack{Regular\\meals}}\\
 		\midrule
@@
 		& Carbohydrate $\geqslant$ 50\%\textsuperscript{\dag} & 12328 & 50.4 & 0.741 & 0.283 & 0.552\\
-		9 am – 12 am &  &  &  &  &  & \\
+		9 am – 12 noon &  &  &  &  &  & \\
 		& Not eating any food & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
@@
 		\multicolumn{7}{l}{{\scriptsize \textit{Note: }}}\\
-		\multicolumn{7}{l}{\scriptsize \textbf{Abbreviation:} LCA, latent class analysis}\\
+		\multicolumn{7}{l}{\scriptsize \textbf{Abbreviation:} LCA, latent class analysis, carb is short for carbohydrates.}\\
 		\multicolumn{7}{l}{{\scriptsize \textsuperscript{*} Carbohydrate $<$ 50\% indicates that within the time slot, carbohydrate contributed $<$ 50\% total energy intake.}}\\
@@
 
-Class 2 days \textbf{(Figure \ref{fig:level1}-B)} were named as "low carbohydrate day" because first of all, in these days the probability of participants skipping breakfast was 0.45.
-And after 9 am, within low carbohydrate days, the probability of having low carbohydrate contained food (carbohydrate contributed $<$ 50\% of total energy intake), was always higher than having high carbohydrate contained food (carbohydrate contributed $\geqslant$ 50\% of total energy intake).
-In these days, participants also turned to have morning snacks (with only 0.079 possibility of not eating any food and similar probabilities of having either high or low carbohydrate contained food).
+Class 2 days \textbf{(Figure \ref{fig:level1}-B)} were named as "low percentage carbohydrate day" because first of all, in these days the probability of participants skipping breakfast was 0.45.
+And after 9 am, within these days, the probability of having low carbohydrate contained food (carbohydrate contributed $<$ 50\% of total energy intake), was always higher than having high carbohydrate contained food (carbohydrate contributed $\geqslant$ 50\% of total energy intake).
+In class 2 days, participants also turned to have morning snacks (with only 0.079 possibility of \textbf{not} eating any food and similar probabilities of having either high or low carbohydrate contained food).
 This phenomenon may also be interpreted as having a long and late breakfast (brunch) in these mornings.
-The probability of not eating any food was the lowest for low carbohydrate days during the midnight time slot (10 pm to 6 am), with probability of 0.590 compared with 0.680 and 0.751 in class 1 and class 3 days, respectively.
+The probability of \textbf{not} eating any food was the lowest for low carbohydrate days during the midnight time slot (10 pm to 6 am), with probability of 0.590 compared with 0.680 and 0.751 in class 1 and class 3 days, respectively.
 
@@
 		\toprule
-		& \textbf{\Centerstack{High carbo-\\hydrate day}} & \textbf{\Centerstack{Low carbo-\\hydrate day}} & \textbf{\Centerstack{Regular\\meals day}} & \textbf{\textit{P} value}\textsuperscript{*}\\
+		& \textbf{\Centerstack{High perc-\\entage carb}} & \textbf{\Centerstack{Low perc-\\entage carb}} & \textbf{\Centerstack{Regular\\meals}} & \textbf{\textit{P} value}\textsuperscript{*}\\
 		\midrule
@@
 		\bottomrule
-		\multicolumn{5}{l}{{\scriptsize \textit{Note: }}}\\
+		\multicolumn{5}{l}{{\scriptsize \textit{Note:} carb is short for carbohydrate.}}\\
 		\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from Pearson $\chi^2$ test for categorical variables, and one-way ANOVA comparing the means}}\\
@@
 
-As expected, consumption of total energy (7539.98 kJ), total carbohydrate (222.79 g), total sugar (98.63 g), starch (124.07 g), and non-milk extrinsic sugar (59.45 g) were highest among high carbohydrate days (all \textit{p} < 0.001).
-On the other hand, the consumption of protein (73.29 g), total fat (67.24 g), and alcohol (13.80 g) were the highest in the so-called regular meals days.
-Moreover, in high carbohydrate days, participants turned to consume the highest amount of fruit (107.40 g).
+As expected, consumption of total energy (7539.98 kJ), total carbohydrate (222.79 g), total sugar (98.63 g), starch (124.07 g), and non-milk extrinsic sugar (59.45 g) were the highest among high percentage carbohydrate days (all \textit{p} < 0.001).
+On the other hand, the consumption of protein (73.29 g), total fat (67.24 g), and alcohol (13.80 g) were the highest in the regular meals days.
+Moreover, in high percentage carbohydrate days, participants turned to consume the highest amount of fruit (107.40 g).
 There was no evidence of any difference for the consumption of yellow, red, or green vegetables across the three types of days (\textit{p} = 0.681).\vspace{-0.6cm}
@@
 
-After recognising that there were three potential latent groups of carbohydrate eaters in the UK adults, whose food consumption pattern were also probably switching from one to another, their average carbohydrate contribution to total energy intake (as well as the subtypes of carbohydrate actually consumed) within the 7 pre-defined time slots of the day were still of interest.
-Survey-design-weighted mean energy intake within each time slot of the day and their sources of contribution are illustrated in \textbf{Figure \ref{fig:energysourcesCB}}, weighted mean nutrients intakes are listed in \textbf{Table \ref{tab:tab-nutri-indi}}.
+After recognising that there were three potential latent groups of carbohydrate eaters in the UK adults, whose food consumption pattern were also probably switching from one to another during the survey, their average carbohydrate contribution to total energy intake (as well as the subtypes of carbohydrate actually consumed) within the 7 pre-defined time slots of the day were still of interest.
+Survey-design-weighted mean energy intake within each time slot of the day and their composition of contribution are illustrated in \textbf{Figure \ref{fig:energysourcesCB}}, weighted mean nutrients intakes are listed in \textbf{Table \ref{tab:tab-nutri-indi}}.
 

### 2018-08-14 paper/Figures/Figureforpaper.R

@@ -351,8 +351,6 @@ pp_long$Time <- as.numeric(pp_long$Time)
 cls1 <- ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Time, group = Carbo, 
                                                linetype = Carbo))  + 
   geom_line(size = 1.2) +
-  scale_x_continuous(limits = c(6, 29),
-                     breaks = seq(6, 29, by = 1)) +
   annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
            alpha = 0.3, fill = "grey") + 
   annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
@@ -361,12 +359,11 @@ cls1 <- ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Time, group = Carbo,
            alpha = 0.3, fill = "grey") + 
   annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
            alpha = 0.3, fill = "grey") +
-  geom_point(aes(shape = Carbo), size = 4,
+  geom_point(aes(shape = Carbo), size = 5,
              fill = "white") + 
   # scale_shape_discrete(solid=F) +
   scale_shape_manual(values=c(21,23,24)) + 
-    theme(axis.title = element_text(size = 18), 
-        axis.text = element_text(size = 18), 
+    theme(axis.text = element_text(size = 15), 
         axis.line = element_line(colour = "black"), 
         panel.border = element_blank(), 
         panel.background = element_blank(), 
@@ -380,21 +377,18 @@ cls1 <- ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Time, group = Carbo,
         # legend.position = "bottom", 
         # legend.direction = "horizontal"
   ) + 
-  scale_linetype_manual(values=c("dotdash", "dashed", "solid")) + 
+  scale_linetype_manual(values=c("dotted", "dashed", "solid")) + 
   # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  labs(title = "Class 1 days - High carbohydrate day (39.5%)", x = "", y = "Probability",
+  labs(title = "Class 1 days - High percentage carbohydrate day (39.5%)", x = "", y = "Probability",
        color = "Carbohydrate\nintake") + 
   # scale_shape_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
-  ylim(c(0,1)) #+ 
[…]

### 2018-08-14 paper/Chapters/Chapter4.tex
little progress in discussion

--- 2018-08-14 paper/Chapters/Chapter4.tex
@@
 
-Using multilevel LCA as a novel technique, and the NDNS RP dietary database, this project examined carbohydrate eating temporal patterns in the day level, based on which, individual level carbohydrate eating patterns were also defined subsequently.
-Among all of the dietary diaries, there were three distinct latent classes specifically for carbohydrate intake: 1) high probabilities of having high carbohydrate contained for across the hours of day (high carbohydrate day); 2) low carbohydrate food dominant through out the hours of day (low carbohydrate day); and 3) always having lunch and dinner day (regular meals day).
+Using multilevel LCA as a novel technique, and the NDNS RP dietary database, this project examined carbohydrate eating temporal patterns firstly in the day level, based on which, individual level carbohydrate eating patterns were also defined subsequently.
 
-For the first time, as far as we know, the non-parametric MLCA models successfully captured the day-to-day variability within individuals as expected and showed that from the perspective of carbohydrate consumption people were switching between different types of carbohydrate consumptions.
+Among the dietary diaries collected, there were three distinct latent classes specifically for carbohydrate intake: 1) high probabilities of having high carbohydrate contained food across the hours of day (high percentage carbohydrate day); 2) low carbohydrate food dominant through out the hours of day (low percentage carbohydrate day); and 3) always having lunch and dinner day (regular meals day).
+And from these day level classification and their features, one might anticipate that individuals who managed to follow the regular meals day might be eating a relatively healthier diet because it seemed to be a regular temporal eating habit; at this time point, we also believe that those who follow either high or low percentages would probably consume total energy.
+
+However, when the MLCA extended the model to individual level, three types of persons are further defined depending on their 4-day-diary: 1) low carbohydrate eaters, who mostly followed "regular meals day"; 2) moderate carbohydrate eaters, who had similar probabilities of following either "regular meals day" or "high percentage carbohydrate day"; 3) high carbohydrate eaters, who followed "high percentage carbohydrate day" for half of their survey.
+For the first time, as far as we know, the day-to-day food intake pattern variation within individuals was successfully captured.
+Results from the MLCA models showed that from the perspective of carbohydrate consumption, people were indeed switching between different types of carbohydrate eating types even within a short term period of survey.
 The MLCA models allowed the probability of a certain type of carbohydrate eating day to vary across individuals.
-This properly accounted for the fact that for some people, their probability of following a regular meals day during the survey was much higher than the others (low carbohydrate eaters); and for some people, their probability of following high carbohydrate eating day during their survey were quite high (high carbohydrate eaters); while for the rest of the participants, they had similar probabilities of following either regular meals day or high carbohydrate eating day (moderate carbohydrate eaters).
+This properly accounted for the fact that for some people, their probability of following a type of food eating pattern during the survey was higher/lower than that in the others.
+Apparently, assuming that a person is always following or characterised by one type of food eating pattern is not appropriate.
 

### 2018-08-15 paper/Chapters/Chapter3.tex
discussion updated

@@
 
-Class 3 days \textbf{(Figure \ref{fig:level1}-C)} were called "regular meals day" due to the following reasons: 1) participants' dietary recordings showed that in these days there was almost 0 possibility of not eating any food at lunch (0.019 between 12 noon and 2 pm) and dinner (0.034 between 5 pm and 8 pm); 2) the probabilities of not eating during morning snack time (9 am to 12 am) and afternoon snack time (2 pm to 5 pm) were also the highest among the three types of days (0.401 and 0.659).
+Class 3 days \textbf{(Figure \ref{fig:level1}-C)} were called "regular meals day" due to the following reasons: 1) participants' dietary recordings showed that in these days there was almost 0 possibility of not eating any food at lunch (0.019 between 12 noon and 2 pm) and dinner (0.034 between 5 pm and 8 pm); 2) the probabilities of not eating during morning snack time (9 am to 12 noon) and afternoon snack time (2 pm to 5 pm) were also the highest among the three types of days (0.401 and 0.659).
 3) during these days, participants may have some high carbohydrate contained food between 8 pm and 10 pm (probability = 0.308), but the probability of not eating any food during 10 pm to 6 am next morning was 0.751, the highest among the three types of days.
@@
 Energy from fat were the highest for low carbohydrate eaters most of the time during the day (except for time between 10 pm to 6 am next morning).
-Most impressively, energy from alcohol were always the highest in low carbohydrate eaters, percentages for energy from alcohol for the 7 times slots were 1.4\% (6-9 am), 1.8\% (9-12 am), 3.1\% (12-2 pm), 7.2\% (2-5 pm), 8.4\% (5-8 pm), 20.0\% (8-10 pm), and 31.2\% (10 - 6 am), respectively.
+Most impressively, energy from alcohol were always the highest in low carbohydrate eaters, percentages for energy from alcohol for the 7 times slots were 1.4\% (6-9 am), 1.8\% (9-12 noon), 3.1\% (12-2 pm), 7.2\% (2-5 pm), 8.4\% (5-8 pm), 20.0\% (8-10 pm), and 31.2\% (10 - 6 am), respectively.
 Contribution from different energy sources are quite similar for moderate and high carbohydrate eaters, but their absolute amount of energy consumption at each time slot were largely different.
@@
 High carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-C)} consumed the highest total energy (929.0 kJ) during 6 am to 9 am in the morning and the lowest total energy between 10 pm to 6 am (205.5 kJ).
-Specifically, carbohydrate contribution to total energy intake were 65.3\% (6-9 am), 56.2\% (9-12 am), 46.2\% (12-2 pm), 50.3\% (2-5 pm), 42.5\% (5-8 pm), 44.1\% (8-10 pm), and 49.9\% (10-6am).
+Specifically, carbohydrate contribution to total energy intake were 65.3\% (6-9 am), 56.2\% (9-12 noon), 46.2\% (12-2 pm), 50.3\% (2-5 pm), 42.5\% (5-8 pm), 44.1\% (8-10 pm), and 49.9\% (10-6am).
 We also noticed that high carbohydrate eaters consumed their energy mainly from three time slots: 6-9 am, 12-2 pm, and 5-8 pm.
@@
 Moderate carbohydrate eaters had their carbohydrate intake more spread out.
-They consumed more sugar and starch during 9-12 am, 2-5 pm, 8-10 pm, and 10-6 am.
+They consumed more sugar and starch during 9-12 noon, 2-5 pm, 8-10 pm, and 10-6 am.
 Low carbohydrate eaters turned to have similar temporal pattern of consuming carbohydrates but the absolute amount of fibre, sugar, free sugar, and starch were usually lower than that in the high carbohydrate eaters except for time slots of 2-5 pm, and 10-6 am.
@@
 		\hspace{2em}Starch (g) & 12.8 (12.0, 13.5) & 5.9 (5.1, 6.6) & 18.3 (17.6, 19.1) & \\
-		\hspace{1em}\textbf{9 am – 12 am} & 25.1 (23.9, 26.3) & 33.0 (31.4, 34.6) & 26.2 (25.1, 27.2) & \\
+		\hspace{1em}\textbf{9 am – 12 noon} & 25.1 (23.9, 26.3) & 33.0 (31.4, 34.6) & 26.2 (25.1, 27.2) & \\
 		\hspace{2em}Fibre (g) & 1.5 (1.4, 1.6) & 1.6 (1.5, 1.7) & 1.3 (1.2, 1.3) & \\

### 2018-08-15 paper/Chapters/Chapter4.tex
discussion updated

@@
 Among the dietary diaries collected, there were three distinct latent classes specifically for carbohydrate intake: 1) high probabilities of having high carbohydrate contained food across the hours of day (high percentage carbohydrate day); 2) low carbohydrate food dominant through out the hours of day (low percentage carbohydrate day); and 3) always having lunch and dinner day (regular meals day).
-And from these day level classification and their features, one might anticipate that individuals who managed to follow the regular meals day might be eating a relatively healthier diet because it seemed to be a regular temporal eating habit; at this time point, we also believe that those who follow either high or low percentages would probably consume total energy.
+And from these day level classifications and their features, one might anticipate that individuals who managed to follow the regular meals day might be eating a relatively healthier diet because it seemed to be a regular temporal eating habit; at this time point, we also believed that those who followed either high or low carbohydrate percentage days would probably consume higher total energy than those who followed most regular meals days.
 
-However, when the MLCA extended the model to individual level, three types of persons are further defined depending on their 4-day-diary: 1) low carbohydrate eaters, who mostly followed "regular meals day"; 2) moderate carbohydrate eaters, who had similar probabilities of following either "regular meals day" or "high percentage carbohydrate day"; 3) high carbohydrate eaters, who followed "high percentage carbohydrate day" for half of their survey.
-For the first time, as far as we know, the day-to-day food intake pattern variation within individuals was successfully captured.
-Results from the MLCA models showed that from the perspective of carbohydrate consumption, people were indeed switching between different types of carbohydrate eating types even within a short term period of survey.
-The MLCA models allowed the probability of a certain type of carbohydrate eating day to vary across individuals.
-This properly accounted for the fact that for some people, their probability of following a type of food eating pattern during the survey was higher/lower than that in the others.
-Apparently, assuming that a person is always following or characterised by one type of food eating pattern is not appropriate.
+However, when the MLCA extended the model to individual level, three types of persons were further defined depending on their 4-day-diary: 1) low carbohydrate eaters, who mostly followed "regular meals day"; 2) moderate carbohydrate eaters, who had similar probabilities of following either "regular meals day" or "high percentage carbohydrate day"; 3) high carbohydrate eaters, who followed "high percentage carbohydrate day" for half of their survey.
+For the first time, as far as we know, the day-to-day food intake pattern variation within individuals was successfully captured by MLCA models.
+Results from the MLCA models showed that from the perspective of carbohydrate consumption, people were indeed changing their diet from day to day even within a short term period of survey.
+The MLCA models allowed the probability of following a certain type of carbohydrate eating day to vary across individuals.
+This properly accounted for the fact that for some people, their probability of following a type of food eating pattern during the survey could be higher/lower than that in the others.
+This finding also suggested that assuming a person will following a certain type of food intake pattern is not appropriate.
 
-Surprisingly, low carbohydrate eaters turned out to consume the highest amount of total energy,
+Surprisingly, low carbohydrate eaters whose dietary recordings suggested that they were mostly following a regular temporal meals pattern turned out to consume the highest amount of total energy among the three type of carbohydrate eaters.
+Detailed profiling of energy composition according to the time slots revealed that low carbohydrate eaters actually had higher proportion of energy contributed by both alcohol and fat.
+High percentage of fat consumption was shown in all 7 time slots, energy coming from alcohol exceeded more than one fifth of the total energy after 8 pm.
+These findings explained why they were actually consuming the highest energy among the three types of carbohydrate eaters.
+However, we also found that participants consuming low carbohydrate had higher prevalence of diabetes, hypertension, and obesity.
+These health issues might possibly lead them (or advices were given from their physicians) to replace carbohydrates in their diet to other energy sources such as fat, protein, or even alcohol.
+Therefore, there is a possibility that they chose to follow low carbohydrate diets out of healthy purpose, but many of them were replacing carbohydrates with higher energy condensed food or even alcohol at night which might indeed be a public health concern.
+
+Further more, looking into the details of the timing and composition of the energy intake among the moderate carbohydrate eaters.
+We realised that although moderate carbohydrate eaters did not consume as much alcohol as low carbohydrate eaters at night.
+But they were
 

### 2018-08-15 paper/Chapters/Chapter4.tex
eating patterns discusses

@@
 Among the dietary diaries collected, there were three distinct latent classes specifically for carbohydrate intake: 1) high probabilities of having high carbohydrate contained food across the hours of day (high percentage carbohydrate day); 2) low carbohydrate food dominant through out the hours of day (low percentage carbohydrate day); and 3) always having lunch and dinner day (regular meals day).
-And from these day level classifications and their features, one might anticipate that individuals who managed to follow the regular meals day might be eating a relatively healthier diet because it seemed to be a regular temporal eating habit; at this time point, we also believed that those who followed either high or low carbohydrate percentage days would probably consume higher total energy than those who followed most regular meals days.
+And from these day level classifications and their features, one might anticipate that individuals who managed to follow the regular meals day might be eating a relatively healthier diet because it seemed to be a regular temporal eating habit; at this time point, we also believed that those who followed either high or low carbohydrate percentage days would probably consume higher total energy than those who followed mostly regular meals days.
 
@@
 This properly accounted for the fact that for some people, their probability of following a type of food eating pattern during the survey could be higher/lower than that in the others.
-This finding also suggested that assuming a person will following a certain type of food intake pattern is not appropriate.
+This finding also suggested that assuming a person will always follow a certain type of food intake pattern is not appropriate.
 
-Surprisingly, low carbohydrate eaters whose dietary recordings suggested that they were mostly following a regular temporal meals pattern turned out to consume the highest amount of total energy among the three type of carbohydrate eaters.
+Surprisingly, low carbohydrate eaters whose dietary recordings suggested that they were mostly following a regular temporal meals pattern turned out to consume the highest amount of total energy among the three types of carbohydrate eaters.
 Detailed profiling of energy composition according to the time slots revealed that low carbohydrate eaters actually had higher proportion of energy contributed by both alcohol and fat.
@@
 These findings explained why they were actually consuming the highest energy among the three types of carbohydrate eaters.
-However, we also found that participants consuming low carbohydrate had higher prevalence of diabetes, hypertension, and obesity.
+However, we also found that participants consuming low carbohydrate food had higher prevalence of diabetes, hypertension, and obesity.
 These health issues might possibly lead them (or advices were given from their physicians) to replace carbohydrates in their diet to other energy sources such as fat, protein, or even alcohol.
-Therefore, there is a possibility that they chose to follow low carbohydrate diets out of healthy purpose, but many of them were replacing carbohydrates with higher energy condensed food or even alcohol at night which might indeed be a public health concern.
+Therefore, there is a possibility that they chose to follow low carbohydrate diets out of health purpose, but many of them were replacing carbohydrates with higher energy condensed food or even alcohol at night which might indeed be a public health concern.
 
-Further more, looking into the details of the timing and composition of the energy intake among the moderate carbohydrate eaters.
-We realised that although moderate carbohydrate eaters did not consume as much alcohol as low carbohydrate eaters at night.
-But they were
+Next, when looking into the details of the timing and composition of the energy intake among the moderate carbohydrate eaters, we realised that although these individuals did not consume as much alcohol as low carbohydrate eaters at night, they consumed the highest amount of energy, especially during time period as late as after 10 pm.
+People fell into moderate carbohydrate eaters group seemed to have the tendency of having their food or meals later than the other two types of carbohydrate eaters.
+They consumed the highest amount of carbohydrates and also total energy during the following time slots: 9-12 noon, 2-5 pm, 8-10 pm, and 10pm-6am.
+These individuals in the NDNS RP were younger, mostly single, with lower average income, and lower education level.
+They might possibly correspond to the "late eaters" defined by previous studies \parencite{leech2017temporal, Mansukhani2018}.
+
+Lastly, the high carbohydrate eaters identified by our MLCA models had the highest absolute total amount of carbohydrate intake.
+Most of their energy intake occured during 6-9 am, 12-2 pm, and 5-8 pm time slots while their average energy consumption was not the highest (between low and moderate carbohydrate eaters).
+High carbohydrate eaters were also found to be the ones that consumed the least amount of energy after 8 pm.
+Therefore, contrary to what was anticipated at the beginning, people who followed high percentage carbohydrate days for most of their time, were actually eating a healthier diet compared with the other two eating patterns.
+
+Our analyses looking for different temporal carbohydrate also highlighted the complexity of eating pattern behaviours in the population and the utility of exploratory, data-driven methods to objectively identify eating patterns that reflect both timing and quantities of food intake, which may have not been detected so far in the literature.
 

### 2018-08-15 paper/main.tex
eating patterns discusses

@@
 
-\thesistitle{The time patterns of carbohydrate intake in the UK adults -- the National Dietary and Nutrition Survey 2008/09-15/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+\thesistitle{The time patterns of carbohydrate intake in the UK adults -- the National Diet and Nutrition Survey 2008/09-15/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
 \supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
@@
 
-I would like to thank the team of the National Dietary and Nutrition Survey Rolling Programme (NDNS RP) who have made their data available to the public for academic study. \\
+I would like to thank the team of the National Diet and Nutrition Survey Rolling Programme (NDNS RP) who have made their data available to the public for academic study. \\
 
@@
 \addchaptertocentry{\abstractname} % Add the abstract to the table of contents
-The National Dietary and Nutrition Survey (NDNS) database of detailed four-day food diaries was used to \dots
+The National Diet and Nutrition Survey (NDNS) database of detailed four-day food diaries was used to \dots
 \end{abstract}
@@
 \textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
-\textbf{NDNS} & the \textbf{N}ational \textbf{D}ietary and \textbf{N}utrition \textbf{S}urvey \\
+\textbf{NDNS} & the \textbf{N}ational \textbf{D}iet and \textbf{N}utrition \textbf{S}urvey \\
 \textbf{OR} & \textbf{O}dds \textbf{R}atio \\

### 2018-08-15 paper/Figures/Figureforpaper.R

@@ -710,7 +710,7 @@ CB1 <- ggplot() +
         axis.text.x=element_blank()) + 
         # legend.position = "bottom", 
         # legend.direction = "horizontal") +
-  labs(title = "Low carbohydrate eaters (28.1%)", x = " ", y = "Percentage") +
+  labs(title = "Low carbohydrate eaters (28.1%) [high fat and drinking at night]", x = " ", y = "Percentage") +
   # theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
   scale_y_continuous(labels=percent)
 
@@ -773,7 +773,7 @@ CB2 <- ggplot() +
         axis.text.x=element_blank()) +
 # legend.position = "bottom", 
 # legend.direction = "horizontal") +
-labs(title = "Moderate carbohydrate eaters (28.8%)", x = " ", y = "Percentage") +
+labs(title = "Moderate carbohydrate eaters (28.8%) [eating late]", x = " ", y = "Percentage") +
   # theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
   scale_y_continuous(labels=percent)
 
@@ -834,7 +834,7 @@ CB3 <- ggplot() +
         text=element_text(family="Atlas Grotesk Light")) +
   scale_fill_manual(values = c("#db735c", "#EFA86E", "#9A8A76", "#F3C57B"),
     labels =  c("Carbo-\nhydrate","Fat", "Protein",  "Alcohol")) + 
-  labs(title = "High carbohydrate eaters (43.1%)", x = "Hours of the day", y = "Percentage") +
+  labs(title = "High carbohydrate eaters (43.1%) [eating early]", x = "Hours of the day", y = "Percentage") +
   theme(axis.text.x = element_text(angle = 14, hjust = 1)) +
   scale_y_continuous(labels=percent)
 

### 2018-08-16 paper/Chapters/Chapter3.tex
results with survery regression updated

@@
 The weighted prevalences of hypertension were 30.4\% in men and 27.5\% in women.
-Among both sexes, there were strong evidence of differences by hypertension status for age, education level, living with a partner or not, smoking status, BMI, WC, and prevalence of diabetes (\textit{p} < 0.01).
-Differences were also found for carbohydrate eating patterns defined previously, total energy intake, as well as total carbohydrate intake (\textit{p} < 0.001).
-No difference was found among either men or women for geographic location, and ethnicity.
-Strong evidence of difference was found in women for average household income (32741.5 \textsterling/year in non-hypertensive vs.
+Among both sexes, there were strong evidence of differences by hypertension status for age, education level, living with a partner or not, smoking status, BMI, abdominal obesity (WC), and prevalence of diabetes (\textit{p} < 0.01).
+No difference was found among either men or women for ethnicity.
+Strong evidence of difference was suggested in women for average household income (32741.5 \textsterling/year in non-hypertensive vs.
 27862.0 \textsterling/year in hypertensive, \textit{p} < 0.001), and physical activity level (geometric mean: 0.81 hours/day in non-hypertensive compared with 0.53 hours/day in hypertensive, \textit{p} < 0.001) but not in men.
+Interestingly, in both sexes, hypertensive participants had higher proportion of being classified as low or high carbohydrate eaters; total energy and carbohydrate intake was higher in people with hypertension (\textit{p} < 0.001).
 
-The sex-specific associations of carbohydrate eating patterns with hypertension with or without diabetes are shown in \textbf{Table \ref{tab:tab2HYT}}.
+The sex-specific associations of carbohydrate eating patterns with hypertension (both in total and in participants without diabetes) are shown in \textbf{Table \ref{tab:tab2HYT}}.
 In the crude models, moderate carbohydrate eaters had statistically significant lower odds of having hypertension than low carbohydrate eaters in both men and women irrespective to diabetes status.
@@
 When diabetic men were excluded in the models, the ORs (95\%CI) for moderate and high carbohydrate eaters compared with low carbohydrate eaters were 0.65 (0.41, 1.03) and 0.73 (0.51, 1.06), respectively.
-The negative associations between carbohydrate eating patterns were still observed in women, however, without any statistical evidence in the full adjusted models.
-\vspace{-0.3cm}
-
-\subsubsection{Obesity (BMI and WC)}\vspace{-0.3cm}
-
-\textbf{Table \ref{tab:tab2BMI}} shows the characteristics for participants according to their obesity status stratified by sex.
-The survey design-weighted prevalence for being overweight and obese in the UK adults were estimated to be 43.4\% and 25.7\% in men, and 30.9\% and 27.4\% in women.
-As expected, WC increased significantly with the elevated BMI level in both men and women.
-Strong evidence of differences by obesity level
+The negative associations between moderate carbohydrate eating pattern and hypertension were also observed in women, however, without any statistically significant evidence in the fully adjusted models.
+High carbohydrate eaters also had lower adjusted odds compared with low carbohydrate eaters, while the 95\% CIs for the adjusted ORs were all wide and included the null value suggesting no evidence of any association in either men or women for high carbohydrate eating pattern and hypertension.
 
@@
 	\centering
-	\fontsize{8}{11}\selectfont
+	\fontsize{9}{11}\selectfont
 	\begin{tabular}[t]{lcccccc}
@@
 		Age (years) & 43.2 (41.7, 44.7) & 59.9 (58.0, 61.7) & < 0.001 & 43.9 (42.7, 45.1) & 64.9 (63.4, 66.5) & < 0.001\\
-		Country (\%) &  &  & 0.109 &  &  & 0.631\\
-		\hspace{1em}England & 84.7 (80.9, 87.2) & 85.4 (81.2, 88.8) &  & 84.0 (81.0, 86.6) & 83.5 (79.1, 87.0) & \\
-		\hspace{1em}Northern Ireland & 3.3 (2.2, 4.8) & 1.6 (0.8, 3.1) &  & 2.5 (1.9, 3.5) & 2.6 (1.5, 4.3) & \\
-		\hspace{1em}Scotland & 8.6 (6.3, 11.7) & 7.1 (4.6, 10.9) &  & 8.7 (6.5, 11.7) & 7.9 (5.1, 11.8) & \\
-		\hspace{1em}Wales & 3.9 (2.7, 5.6) & 5.9 (4.0, 8.5) &  & 4.7 (3.7, 6.0) & 6.1 (4.3, 8.6) & \\
+%		Country (\%) &  &  & 0.109 &  &  & 0.631\\
+%		\hspace{1em}England & 84.7 (80.9, 87.2) & 85.4 (81.2, 88.8) &  & 84.0 (81.0, 86.6) & 83.5 (79.1, 87.0) & \\
+%		\hspace{1em}Northern Ireland & 3.3 (2.2, 4.8) & 1.6 (0.8, 3.1) &  & 2.5 (1.9, 3.5) & 2.6 (1.5, 4.3) & \\
+%		\hspace{1em}Scotland & 8.6 (6.3, 11.7) & 7.1 (4.6, 10.9) &  & 8.7 (6.5, 11.7) & 7.9 (5.1, 11.8) & \\
+%		\hspace{1em}Wales & 3.9 (2.7, 5.6) & 5.9 (4.0, 8.5) &  & 4.7 (3.7, 6.0) & 6.1 (4.3, 8.6) & \\
 		Ethnicity (\%) &  &  & 0.534 &  &  & 0.126\\
@@
 \end{sidewaystable}
-
-were found for age, total energy intake, and carbohydrate intake in both sexes.
-Specifically, education level (\textit{p} = 0.022 for men, < 0.001 for women), average household income (\textit{p} = 0.011 for men, < 0.001 for women) were lower with increasing BMI.
-Living with partner or not was strongly positively associated with obesity in men but not in women.
-Men with obesity were found to have the lowest proportion of never being a smoker (47.9 \%), and the highest proportion of being ex-smoker (32.9\%).
-Association between smoking status and obesity in women was only with very weak evidence (\textit{p} = 0.042) but similar pattern as in men was also observed.
-No difference was found for length of physical activity across obesity levels in men,
 
@@
 
+\subsubsection{Obesity (BMI and WC)}\vspace{-0.3cm}
+
+\textbf{Table \ref{tab:tab2BMI}} shows the characteristics for participants according to their obesity status stratified by sex.
+The survey design-weighted prevalence for being overweight and obese in the UK adults were estimated to be 43.4\% and 25.7\% in men, and 30.9\% and 27.4\% in women.
+Obviously, abdominal obesity (WC) increased significantly with the elevated BMI level in both men and women.
+Overweight or obese participants were older, having lower total energy intake and lower carbohydrate intake compared with normal weight men and women (\textit{p} < 0.001).
+Moreover, edu-
+
 \begin{sidewaystable}
@@
 		\centering
-		\fontsize{8}{11}\selectfont
+		\fontsize{8.5}{11}\selectfont
 		\begin{tabular}[t]{lcccccccc}
@@
 			Age (years) & 40.3 (38.2, 42.4) & 49.6 (47.9, 51.2) & 50.4 (48.5, 52.3) & < 0.001 & 45.0 (43.4, 46.7) & 50.4 (48.6, 52.3) & 50.9 (49.1, 52.7) & < 0.001\\
-			Country (\%) &  &  &  & 0.236 &  &  &  & 0.589\\
-			\hspace{1em}England & 83.9 (79.2, 87.7) & 86.9 (83.6, 89.7) & 81.6 (76.7, 85.7) &  & 84.3 (80.4, 87.5) & 83.7 (79.7, 87.0) & 82.4 (78.2, 85.9) & \\
-			\hspace{1em}Northern Ireland & 3.3 (1.9, 5.8) & 2.3 (1.4, 3.6) & 3.2 (2.0, 4.9) &  & 3.0 (2.1, 4.2) & 2.2 (1.5, 3.2) & 3.4 (2.3, 5.0) & \\
-			\hspace{1em}Scotland & 9.1 (6.1, 13.5) & 6.5 (4.4, 9.7) & 9.0 (5.9, 13.3) &  & 9.0 (6.1, 13.0) & 9.0 (6.3, 12.8) & 8.5 (5.7, 12.6) & \\
-			\hspace{1em}Wales & 3.7 (2.3, 5.8) & 4.3 (3.1, 5.9) & 6.3 (4.0, 9.7) &  & 3.8 (2.9, 5.1) & 5.1 (3.6, 7.2) & 5.7 (4.2, 7.7) & \\
+%			Country (\%) &  &  &  & 0.236 &  &  &  & 0.589\\
+%			\hspace{1em}England & 83.9 (79.2, 87.7) & 86.9 (83.6, 89.7) & 81.6 (76.7, 85.7) &  & 84.3 (80.4, 87.5) & 83.7 (79.7, 87.0) & 82.4 (78.2, 85.9) & \\
+%			\hspace{1em}Northern Ireland & 3.3 (1.9, 5.8) & 2.3 (1.4, 3.6) & 3.2 (2.0, 4.9) &  & 3.0 (2.1, 4.2) & 2.2 (1.5, 3.2) & 3.4 (2.3, 5.0) & \\
+%			\hspace{1em}Scotland & 9.1 (6.1, 13.5) & 6.5 (4.4, 9.7) & 9.0 (5.9, 13.3) &  & 9.0 (6.1, 13.0) & 9.0 (6.3, 12.8) & 8.5 (5.7, 12.6) & \\
+%			\hspace{1em}Wales & 3.7 (2.3, 5.8) & 4.3 (3.1, 5.9) & 6.3 (4.0, 9.7) &  & 3.8 (2.9, 5.1) & 5.1 (3.6, 7.2) & 5.7 (4.2, 7.7) & \\
 			Ethnicity (\%) &  &  &  & 0.466 &  &  &  & 0.879\\
@@
 
-while in women, somewhat weak inverse association (\textit{p}=0.038) was confirmed.
+cation level (\textit{p} = 0.022 for men, < 0.001 for women), average household income (\textit{p} = 0.011 for men, < 0.001 for women) were decreasing with increasing BMI.
+Living with partner or not was strongly positively associated with obesity in men but not in women.
+Men with obesity were also found to have the lowest proportion of never being a smoker (47.9 \%), and the highest proportion of being ex-smoker (32.9\%).
+Association between smoking status and obesity in women was only with very weak evidence (\textit{p} = 0.042) but similar pattern as in men was also observed (higher proportion of ex- and current smokers in overweight or obese women).
+No difference was found for length of physical activity across obesity levels in men, while in women, somewhat weak inverse association (\textit{p}=0.038) was confirmed.
 Interestingly, predefined carbohydrate eating patterns were seemingly not associated with BMI in men (\textit{p} = 0.072) or in women (\textit{p} = 0.253).
-
-Results of the regression analyses showed inverse associations between latent classes of carbohydrate eating patterns and BMI among men \textbf{(Table \ref{tab:tab2BMI})}.
-However, the 95\%CI of the regression coefficients were all too wide and include the null value 0, indicating no statistically supported evidence of the association.
-But, evidence of interaction effect was found in whether live with a partner or not on the association between carbohydrate eating patterns and BMI (\textit{p} for interaction = 0.014 and 0.036 for women in total and without diabetes).
-For women living with her partner, latent classes of carbohydrate eating patterns were negatively associated with BMI.
-Compared with women eating low carbohydrate meals, women having a high
 
@@
 		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
+%		\bottomrule \\
     	\bottomrule
@@
 \end{table}
-\vspace{-0.3cm}
+
 \rowcolors{2}{white}{white}
 
-  carbohydrate eating pattern were averagely associated with 1.76 kg/m\textsuperscript{2} lower BMI after adjusted for age, average household income, education level, smoking status, total energy intake and alcohol consumption.
+Results of the multivariable linear regression analyses showed inverse associations between latent classes of carbohydrate eating patterns and BMI among men \textbf{(Table \ref{tab:tab2BMI})}.
+However, the 95\%CI of the regression coefficients were all wide and included the null value 0, indicating no statistically supported evidence for the inverse association.
+However, evidence of interaction effect was found in whether live with a partner or not on the association between carbohydrate eating patterns and BMI (\textit{p} for interaction = 0.014 and 0.036 for women in total and without diabetes).
+For women who were living with her partner, latent classes of carbohydrate eating patterns were negatively associated with BMI.
+Compared with women eating low carbohydrate food pattern, women having a high carbohydrate eating pattern were averagely associated with 1.76 kg/m\textsuperscript{2} lower BMI after adjustment of age, average household income, education level, smoking status, total energy intake and alcohol consumption.
 95\%CI for the adjusted BMI difference was 0.73 to 2.78 kg/m\textsuperscript{2}, \textit{p} = 0.001.
-After excluding diabetic women, BMI was still 1.62 kg/m\textsuperscript{2} (95\%CI: 0.58, 2.65, \textit{p} = 0.002) lower in high carbohydrate eaters versus low carbohydrate eaters on average.
-On the contrary, latent classes of carbohydrate eating patterns were positively associated with BMI in women who live without a partner, although the regression coefficients were not statistically different from 0.
+After excluding diabetic women, BMI was still 1.62 kg/m\textsuperscript{2} (95\%CI: 0.58, 2.65, \textit{p} = 0.002) smaller in high carbohydrate eaters versus low carbohydrate eaters on average.
+On the contrary, latent classes of carbohydrate eating patterns were positively associated with BMI in women who were living by themselves, although the regression coefficients were not statistically different from 0.
+
+Similarly, when looking at the association between carbohydrate eating pattern and abdominal obesity (WC), men who were classified as moderate carbohydrate eaters were found to had about 3 cm (95\%CI: 0.52, 5.49 cm, \textit{p} = 0.018) smaller WC compared with low carbohydrate eaters in the crude model \textbf{(Table \ref{tab:tab2WC})}.
+However, after adjustment of age, living with partner or not, average household income, education level, hypertension, smoking status, total energy intake, and alcohol consumption, the association attenuated to no difference.
+The interaction effect of whether living with partner or not on the association between carbohydrate eating patterns and WC was again found in women in total and without diabetes.
+Among women who were living with their partners, high carbohydrate eaters had 4.71 cm (95\%CI: 2.43, 7.00, \textit{p} < 0.001) smaller WC on average compared with low carbohydrate eaters.
+The association remained when restricted the sample to non-diabetic women (-3.74 cm, 95\% CI: -5.97, -1.51,  \textit{p} = 0.001).
+However, for women who were living alone, moderate carbohydrate eaters had 3.17 cm (95\%CI: 0.05, 6.30, \textit{p} = 0.047) larger WC on average compared with low carbohydrate eaters.
+The evidence for the positive association between moderate carbohydrate eaters and WC in women became weaker but with borderline significant when excluding diabetic women (3.08 cm, 95\%CI: -0.09, 6.25, \textit{p} = 0.057).
 
@@
 \rowcolors{2}{white}{white}
-
-Similarly, when using WC as another measurement of obesity, compared with men who had low carbohydrate eating pattern, only those had a moderate carbohydrate eating pattern were found with about 3 cm (95\%CI: 0.52, 5.49 cm, \textit{p} = 0.018) smaller WC in the crude model \textbf{(Table \ref{tab:tab2WC})}.
-After adjustment of age, living with partner or not, average household income, education level, hypertension, smoking status, total energy intake, and alcohol consumption, the association attenuated to no difference in men.
-Again, the interaction effect of whether living with partner or not on the association between carbohydrate eating patterns and WC was found in women in total and without diabetes.
-Among women who were living with her partner, high carbohydrate eaters had 4.71 cm (95\%CI: 2.43, 7.00, \textit{p} < 0.001) lower WC on average compared with low carbohydrate eaters.
-The association remained when restricted into non-diabetic women (-3.74 cm, 95\% CI: -5.97, -1.51,  \textit{p} = 0.001).
-However, for women who lived without a partner, moderate carbohydrate eaters had 3.17 cm (95\%CI: 0.05, 6.30, \textit{p} = 0.043) larger WC compared with low carbohydrate eaters.
-The evidence for the positive association between moderate carbohydrate eaters and WC was weak and became borderline significant when excluding diabetic women.
 

### 2018-08-16 paper/Chapters/Chapter4.tex
results with survery regression updated

@@
 People fell into moderate carbohydrate eaters group seemed to have the tendency of having their food or meals later than the other two types of carbohydrate eaters.
-They consumed the highest amount of carbohydrates and also total energy during the following time slots: 9-12 noon, 2-5 pm, 8-10 pm, and 10pm-6am.
+They consumed the highest amount of carbohydrates and also total energy among three types of carbohydrate eaters during the following time slots: 9-12 noon, 2-5 pm, 8-10 pm, and 10pm-6am.
 These individuals in the NDNS RP were younger, mostly single, with lower average income, and lower education level.
-They might possibly correspond to the "late eaters" defined by previous studies \parencite{leech2017temporal, Mansukhani2018}.
+They might possibly correspond to the "late eaters" defined by previous studies \parencite{leech2017temporal, mansukhani2018investigating}.
 

### 2018-08-16 paper/main.tex
results with survery regression updated

@@
 \university{\href{https://www.lshtm.ac.uk/}{London School of Hygiene and Tropical Medicine}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
-\department{\href{}{Page count: XX from Introduction to Conclusions}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
+\department{\href{}{Page count: 42 from Introduction to Conclusions}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
 \group{Candidate number: 110765} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname

### 2018-08-16 paper/Chapters/Chapter3.tex
discussion updated

@@
 	\multicolumn{5}{l}{{\scriptsize \textit{Note: }}}\\
-	\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
+	\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national diet and nutrition survey rolling programme.}}\\
 	\multicolumn{5}{l}{{\scriptsize Variables were weighted by individual weights.}}\\
@@
 %		\multicolumn{5}{l}{\textit{Note: }}\\
-		\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}}\\
+		\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national diet and nutrition survey rolling programme;}}\\
 		\multicolumn{5}{l}{{\scriptsize BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus; TC, total cholesterol, }}\\
@@
 		\multicolumn{7}{l}{{\scriptsize \textit{Note: }}}\\
-		\multicolumn{7}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}}\\
+		\multicolumn{7}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national diet and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}}\\
 		\multicolumn{7}{l}{{\scriptsize Variables are weighted by nurse visiting weights.}}\\
@@
 		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: OR, odds ratio; CI, confidence interval; BMI, body mass index; WC, waist}}\\
-		\multicolumn{6}{l}{{\scriptsize  circumference; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
+		\multicolumn{6}{l}{{\scriptsize  circumference; NDNS RP, national diet and nutrition survey rolling programme.}}\\
 		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other}}\\
@@
 
-\textbf{Table \ref{tab:tab2BMI}} shows the characteristics for participants according to their obesity status stratified by sex.
+\textbf{Table \ref{tab:tab1BMI}} shows the characteristics for participants according to their obesity status stratified by sex.
 The survey design-weighted prevalence for being overweight and obese in the UK adults were estimated to be 43.4\% and 25.7\% in men, and 30.9\% and 27.4\% in women.
@@
 			\multicolumn{9}{l}{{\scriptsize \textit{Note: }}}\\
-			\multicolumn{9}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}}\\
+			\multicolumn{9}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national diet and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}}\\
 			\multicolumn{9}{l}{{\scriptsize Variables are weighted by nurse visiting weights.}}\\
@@
 		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
-		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; NDNS RP, national diet and nutrition survey rolling programme.}}\\
 		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%.}}\\
@@
 However, after adjustment of age, living with partner or not, average household income, education level, hypertension, smoking status, total energy intake, and alcohol consumption, the association attenuated to no difference.
-The interaction effect of whether living with partner or not on the association between carbohydrate eating patterns and WC was again found in women in total and without diabetes.
+The interaction effect of whether living with partner or not on the association between carbohydrate eating patterns and WC was again found in women in total (\textit{p} for interaction = 0.009) and without diabetes (\textit{p} for interaction = 0.012).
 Among women who were living with their partners, high carbohydrate eaters had 4.71 cm (95\%CI: 2.43, 7.00, \textit{p} < 0.001) smaller WC on average compared with low carbohydrate eaters.
@@
 		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
-		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: WC, waist circumference; NDNS RP, national diet and nutrition survey rolling programme.}}\\
 		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. }}\\
-		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} P values were obtained from wald tests from linear regression models.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from linear regression models.}}\\
 		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age, live with partner or not, average household income, education level, hypertension (yes or no),}}\\
 		\multicolumn{6}{l}{{\scriptsize smoking status, total energy intake, alcohol consumption;}}\\
-		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, education level, hypertension, smoking status, total energy intake, alcohol consumption.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, age\textsuperscript{2}, education level, hypertension, smoking status, total energy intake, alcohol consumption.}}\\
 	\end{tabular}
@@
 %			\multicolumn{12}{l}{{\scriptsize \textit{Note: }}}\\
-%			\multicolumn{12}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
+%			\multicolumn{12}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national diet and nutrition survey rolling programme.}}\\
 %			\multicolumn{12}{l}{{\scriptsize DM was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the same with the corresponding Model 1s.}}\\

### 2018-08-16 paper/Chapters/Chapter4.tex
discussion updated

@@
 
-\section{Main Findings}
+%\section{Main Findings}
 
-\subsection{Carbohydrate eating patterns}
+\section{Carbohydrate eating patterns}
 
@@
 
-\subsection{Association between carbohydrate eating patterns and health outcomes}
+\section{Association between carbohydrate eating patterns and health outcomes}
+
+Among men, who were classified as moderate carbohydrate eaters probably had lower odds of having hypertension, after adjustment of age, live with partner or not, educational level, BMI, smoking status and total energy intake.
+As discussed above, moderate carbohydrate eaters turned to have meals (or energy consumption) later in time compared with high carbohydrate eaters, but low carbohydrate eaters also consumed large amount of energy (from both fat and alcohol) at night.
+Therefore, considering that moderate carbohydrate eaters were younger than low carbohydrate eaters (although age was adjusted in the full models), there is probably reverse causality exists here (also due to the nature of cross-sectional study).
+That is, they were potentially both late eaters, however, with their age increased (and so as increased health-related problems/concern) some of them modified their habits, such as quit smoking, replace carbohydrate food with other energy sources which lead to the phenomenon of lower odds of hypertension in moderate carbohydrate eaters.
+Although the hypothesis cannot be determined by NDNS RP's cross-sectional data, if these theories were true, the energy sources they used to replace carbohydrate in their diet were apparently not very wisely chosen.
+
+Among women, whether living with a partner became an interaction factor for the associations between carbohydrate eating patterns and BMI and abdominal obesity (WC).
+Directions of the associations were opposite to each other depending on whether women were living with a partner or not.
+This interaction effect was more obvious when looking at abdominal obesity measurement.
+High carbohydrate eaters had lower BMI and WC in those lived with their partner, while moderate carbohydrate eaters had higher WC in those who lived alone after adjustment of age, education level, smoking status, total energy intake, and alcohol consumption.
+High carbohydrate eaters who were characterised with high and early in the day energy consumption and low fat and alcohol intake may reflect a healthier diet and lifestyle, but this might be different between women who lived alone and those who lived with their partners.
+It was often assumed that live alone may associated with lower diversity of food intake, and a higher likelihood of having an unhealthy dietary pattern \parencite{hanna2015relationship}.
+Therefore, there may be differences in the actual contents consumed in the high carbohydrates eaters, or there may be other social, psychological or lifestyle related factors related with living alone which we did not included in the models, so that the inverse association between high carbohydrate eating pattern and BMI or abdominal obesity were only observed among women who lived with partners, further analysis is needed.
+Whereas the reason why moderate carbohydrate eaters' WC was larger than low carbohydrate eaters only among women who lived alone is unknown, given that the evidence of this association was weak and borderline significant, whether it was just a false positive result should be explored in other studies.
+
+%but if the reverse causality reason still applies, women who lived alone may be less likely to modify their diet (replacing carbohydrate with fat or alcohol) and therefore they stayed
+
+%Women lived with partners had higher proportion of being classified as high carbohydrate eaters
 
@@
 	\item MLCA ignored the order of observation days.
-	\item We used the maximum probability rule and ignored that these are just probabilities.
+	\item We used the maximum probability rule and ignored that these are just probabilities. but inclusive MLCA might perform better.
+	\item we do not have the information of whether the participants were doing job that requires shift work.
+	\item dietary report under estimation
+	\item findings may not be generalizable to populations from other countries.
 \end{itemize}
@@
 \section{Conclusions}
+
+We have successfully defined carbohydrate eating patterns in the general population in the UK adults using the NDNS RP database in both observation day level and participant level.
+Low carbohydrate eaters turned to have more energy that contributed by both fat and alcohol.
+Moderate carbohydrate eaters consumed the lowest total energy, while they had the tendency of having meals later in time-of-day.
+High carbohydrate eaters consumed most of their carbohydrate as well as energy earlier in time-of-day.
+These dietary patterns specifically for carbohydrate intake were found to be differed by timing, quantity and resources of energy consumption.
+Compared with low carbohydrate eaters, men had moderate carbohydrate eating pattern may associated with a lower prevalence of hypertension, women in this latent class who lived alone may associated with a larger waist circumferences.
+Among women who lived with partners, high carbohydrate eating pattern was associated with both lower BMI and smaller waist circumferences.
+Future studies exploring how such carbohydrate eating patterns may relate longitudinally to change of obesity, hypertension and diabetes incidence and other health outcomes are needed.

### 2018-08-16 paper/main.tex
discussion updated

@@
 
-\thesistitle{The time patterns of carbohydrate intake in the UK adults -- the National Diet and Nutrition Survey 2008/09-15/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+\thesistitle{The time and quantity patterns of carbohydrate intake in the UK adults -- the National Diet and Nutrition Survey 2008/09-15/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
 \supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
@@
 \textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
-\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
+%\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
 \textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\

### 2018-08-17 paper/Appendices/Appendix0_10.Rmd
appendix C figlevel 1 CW4

@@
 ```{r eval=FALSE}
+
 # NDNS analysis, data management ------------------------------------------
@@
 # Change the data path accordingly ----------------------------------------
-setwd("/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/") # on Ubuntu
+
+setwd(".../UKDA-6533-stata11_se/stata11_se/") 
+setwd("~/Downloads/UKDA-6533-stata11_se/stata11_se/")
+
 library(epiDisplay)
@@
 # Read the data into memory -----------------------------------------------
+
 library(haven)
@@
 data78 <- read_dta("ndns_rp_yr7-8a_foodleveldietarydata.dta")
+
 names(data)
@@
 names(data78)
-names(data)[names(data) == "seriali"] <- "id"
-names(data56)[names(data56) == "seriali"] <- "id"
-names(data78)[names(data78) == "seriali"] <- "id"
-
-# Extract the data we needed ----------------------------------------------
-df14d <- data[, c(113, 1, 2, 3, 5, 6, 7, 8, 9, 21, 24, 55, 57, 58, 
-    59, 60, 61, 62, 63, 64)]
+names(data)[names(data)=="seriali"] <- "id"
+names(data56)[names(data56)=="seriali"] <- "id"
+names(data78)[names(data78)=="seriali"] <- "id"
+
+# Extract the variables needed -------------------------------------------
+
+df14d <- data[,c(113,1,2,3,5,6,7,8,9,21, 22, 23, 24, 53, 55,
+                 57,58,59,60,61,62,63,64,65)]
 var <- names(df14d)
-df56d <- data56 %>% select(var)
-df78d <- data78 %>% select(var)
+df56d <- data56 %>% 
+  select(var)
+df78d <- data78 %>% 
+  select(var)
 dfs1 <- rbind(df14d, df56d, df78d)
-dfs2 <- dfs1[dfs1$Age >= 19, ]
-rm(data, data56, data78)
+
+dfs2 <- dfs1[dfs1$Age>=19,] # keep participants who aged 19 or older
+rm(data, data56, data78) # remove the unneeded big dataset
+
 dfs2
@@
 dfs2$MealTime_chr <- as.character(dfs2$MealTime)
-dfs2$MealTime_hm <- unlist(strsplit(dfs2$MealTime_chr, " "))[c(FALSE, 
+dfs2$MealTime_hm <- unlist(strsplit(dfs2$MealTime_chr," "))[c(FALSE, 
                                                               TRUE)]
-dfs2$MealHourN <- as.numeric(unlist(strsplit(dfs2$MealTime_hm, ":"))[c(TRUE, 
-    FALSE, FALSE)])
-dfs2$MealMinN <- as.numeric(unlist(strsplit(dfs2$MealTime_hm, ":"))[c(FALSE, 
-    TRUE, FALSE)])
-dfs2$MealMinN0 <- (60 * dfs2$MealHourN) + dfs2$MealMinN
-dfs3 <- dfs2[order(dfs2$id, dfs2$DayNo, dfs2$MealMinN0), ]
+dfs2$MealHourN <- as.numeric(unlist(strsplit(dfs2$MealTime_hm,
+                                             ":"))[c(TRUE, FALSE, FALSE)])
+dfs2$MealMinN <- as.numeric(unlist(strsplit(dfs2$MealTime_hm,
+                                            ":"))[c(FALSE, TRUE, FALSE)])
+
+dfs2$MealMinN0 <- (60*dfs2$MealHourN)+dfs2$MealMinN
+
+dfs3 <- dfs2[order(dfs2$id,dfs2$DayNo,dfs2$MealMinN0),]
+
 length(unique(dfs3$id)) ## number of participants = 6155
 
-# Create a subset data with only the first observation of each
-# participant --------
+# Create a subset data with only the first observation of each participant --------
+
 NDNS <- dfs3[!duplicated(dfs3$id), ]
 with(NDNS, tab1(SurveyYear, graph = FALSE, decimal = 2))
-
+```
+
+```
 # #SurveyYear : 
@@
 #   Total          6155  100.00       100.00
-
+```
+
+```{r eval=FALSE}
+# how many men and women --------------------------------------------------
+
+with(NDNS, tab1(Sex, graph = FALSE, decimal = 2))
+```
+
+```
+# Sex : 
+#          Frequency Percent Cum. percent
+# 1            2537   41.22        41.22 Men
+# 2            3618   58.78       100.00 Women
+#   Total      6155  100.00       100.00
+```
+
+```{r eval=FALSE}
 # create a variable combine id and day No ---------------------------------
+
 dfs3 <- dfs3 %>% 
@@
 
-# For each subject, the total energy/carbohydrate intake for each eating 
-# time can be calculated --------
-old <- Sys.time()
+# For each subject, the total energy/carbohydrate intake for each 
+# eating time can be calculated --------
+
+old<-Sys.time()
 Energy <- ddply(dfs3, .(id_dy, id, SurveyYear, DayNo, Age, Sex, 
                         DiaryDaysCompleted, MealHourN, DayofWeek),  
-                summarise, 
-                Tot_Energ = sum(EnergykJ), 
+                summarise, Tot_Energ = sum(EnergykJ), 
                 Tot_Carb = sum(Carbohydrateg), 
                 Tot_Sugar = sum(Totalsugarsg), 
-                Tot_Starch = sum(Starchg))
-new <- Sys.time() - old
+                Tot_Starch = sum(Starchg), 
+                Tot_Fibre = sum(Englystfibreg),
+                Tot_Fat   = sum(Fatg), 
+                Tot_Prot  = sum(Proteing), 
+                Tot_Alc   = sum(Alcoholg), 
+                Tot_NMES  = sum(Nonmilkextrinsicsugarsg))
+new<-Sys.time()-old
 print(new)
-# Time difference of 3.876385 mins
-
-rm(df14d, df56d, df78d, dfs2)
+# Time difference of 6.429822 min
+
+# reset the time intervals into time slots --------------------------------
+
+### Breakfast:       6am to 9am
+### morning snack:   9am to 12noon
+### lunch:           12noon to 2pm
+### afternoon snack: 2pm to 5pm
+### dinner:          5pm to 8pm
+### night snack:     8pm to 10pm
+### midnight:        10pm to 6am
+
+Energy <- Energy %>% 
+  mutate(TimeSlot = cut(MealHourN, breaks = c(6, 9, 12, 14, 17, 20, 22), 
+                        right = FALSE))
+
+levels(Energy$TimeSlot) <- c(levels(Energy$TimeSlot), "[22, 6)")
+
+Energy$TimeSlot[is.na(Energy$TimeSlot)] <- "[22, 6)"
+
+tab1(Energy$TimeSlot)
+
+# For each subject, the total energy/carbohydrate intake for each 
+# time slot can be calculated --------
+old<-Sys.time()
+Energy <- ddply(Energy, .(id_dy, id, SurveyYear, DayNo, Age, Sex, 
+                          DiaryDaysCompleted, TimeSlot, DayofWeek),  
+                summarise, 
+                Tot_Energ = sum(Tot_Energ), 
+                Tot_Carb = sum(Tot_Carb), 
+                Tot_Sugar = sum(Tot_Sugar),
+                Tot_Starch = sum(Tot_Starch), 
+                Tot_Fibre = sum(Tot_Fibre), 
+                Tot_Fat   = sum(Tot_Fat), 
+                Tot_Prot  = sum(Tot_Prot), 
+                Tot_Alc   = sum(Tot_Alc), 
+                Tot_NMES  = sum(Tot_NMES))
+new<-Sys.time()-old
+print(new)
+# Time difference of 3.74195 mins
 
 # Calculate the energy from total carbohydrates ---------------------------
+
 Energy <- Energy %>% 
-  mutate(KJcarbo = Tot_Carb * 16) %>% 
+  mutate(KJcarbo = Tot_Carb*16) %>% 
   mutate(CarKJpercentage = KJcarbo/Tot_Energ) %>% 
-  mutate(Carbo = cut(CarKJpercentage, breaks = c(0, 0.26, 0.75, 2), 
-        right = FALSE)) %>% mutate(Carbo2 = cut(CarKJpercentage, breaks = c(0, 
-    0.26, 2), right = FALSE))
-Energy0 <- Energy[!(Energy$Tot_Energ == 0), ]  
-          # some food consumption does not contain any carbohydrates
-Energy0$Carbo <- factor(Energy0$Carbo, labels = c("Low_carb", "Med_carb", 
-    "High_carb"))
-Energy0$Carbo2 <- factor(Energy0$Carbo2, labels = c("Low_carb", "Med_or_high_carb"))
-
-# Generate data sets for each day ----------------------------------------------------------
+  mutate(Carbo = cut(CarKJpercentage, breaks = c(0, 0.50, 2), right = FALSE))
+
+Energy0 <- Energy[!(Energy$Tot_Energ == 0), ] # discard those eating occassion 
+# with 0 energy intake 
+write.csv(Energy0, file = "Energy_slots.csv") # for later analysis
+
+Energy0$Carbo <- factor(Energy0$Carbo, labels = c("< 50%", ">= 50%"))
+
+vecid<-unique(Energy0$id)
+
+# Filter the data by observation day--------------------------------------------
+
 dta_day1 <- Energy0 %>% 
   filter(DayNo == 1) %>% 
-  select(c("id", "Age", 
-    "Sex", "DayofWeek", "MealHourN", "Carbo", "Carbo2")) %>% 
+  select(c("id", "id_dy", "Age", "Sex", 
+           "DayofWeek",  "TimeSlot", "Carbo")) %>%  
   mutate(DayofWeek = factor(DayofWeek, 
-    levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", 
-        "Saturday", "Sunday")))
+                            levels = c("Monday", "Tuesday", 
+                                       "Wednesday", "Thursday", 
+                                       "Friday", "Saturday", "Sunday")))
 
@@
   filter(DayNo == 2) %>% 
-  select(c("id", "Age", 
-    "Sex", "DayofWeek", "MealHourN", "Carbo", "Carbo2")) %>% 
+  select(c("id", "id_dy", "Age", "Sex", 
+           "DayofWeek",  "TimeSlot", "Carbo")) %>%  
   mutate(DayofWeek = factor(DayofWeek, 
-    levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", 
-        "Saturday", "Sunday")))
+                            levels = c("Monday", "Tuesday", 
+                                       "Wednesday", "Thursday", 
+                                       "Friday", "Saturday", "Sunday")))
 
@@
   filter(DayNo == 3) %>% 
-  select(c("id", "Age", 
-    "Sex", "DayofWeek", "MealHourN", "Carbo", "Carbo2")) %>% 
+  select(c("id", "id_dy", "Age", "Sex", 
+           "DayofWeek",  "TimeSlot", "Carbo")) %>%  
   mutate(DayofWeek = factor(DayofWeek, 
-    levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", 
-        "Saturday", "Sunday")))
+                            levels = c("Monday", "Tuesday", 
+                                       "Wednesday", "Thursday", 
+                                       "Friday", "Saturday", "Sunday")))
 
@@
   filter(DayNo == 4) %>% 
-  select(c("id", "Age", 
-    "Sex", "DayofWeek", "MealHourN", "Carbo", "Carbo2")) %>% 
+  select(c("id", "id_dy", "Age", "Sex", 
+           "DayofWeek",  "TimeSlot", "Carbo")) %>%  
   mutate(DayofWeek = factor(DayofWeek, 
-    levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", 
-        "Saturday", "Sunday")))
-vecid1 <- unique(dta_day1$id) # n = 6153
-vecid2 <- unique(dta_day2$id) # n = 6153
-vecid3 <- unique(dta_day3$id) # n = 6151
-vecid4 <- unique(dta_day4$id) # n = 6026
+                            levels = c("Monday", "Tuesday", 
+                                       "Wednesday", "Thursday", 
+                                       "Friday", "Saturday", "Sunday")))
+
+vecid1<-unique(dta_day1$id) # n = 6153
+vecid2<-unique(dta_day2$id) # n = 6153
+vecid3<-unique(dta_day3$id) # n = 6151
+vecid4<-unique(dta_day4$id) # n = 6026
 
 Noday1 <- setdiff(vecid, vecid1) # two subjects did not have day 1 data
+
 Noday2 <- setdiff(vecid, vecid2) # two subjects did not have day 2 data
+
 Noday3 <- setdiff(vecid, vecid3) # four subjects did not have day 3 data
+
 Noday4 <- setdiff(vecid, vecid4) # 129 subjects did not have day 4 data
 
-# Transform the data shape from long to wide ---------------------------------
-dta_d1_wide <- dta_day1[, -7] %>% 
-  spread(key = MealHourN, value = Carbo)
-names(dta_d1_wide)[5:28] <- paste(rep("H", 24), 0:23, sep = "")
-
-dta_d2_wide <- dta_day2[, -7] %>% 
-  spread(key = MealHourN, value = Carbo)
-names(dta_d2_wide)[5:28] <- paste(rep("H", 24), 0:23, sep = "")
-
-dta_d3_wide <- dta_day3[, -7] %>% 
-  spread(key = MealHourN, value = Carbo)
-names(dta_d3_wide)[5:28] <- paste(rep("H", 24), 0:23, sep = "")
-
-dta_d4_wide <- dta_day4[, -7] %>% 
-  spread(key = MealHourN, value = Carbo)
-names(dta_d4_wide)[5:28] <- paste(rep("H", 24), 0:23, sep = "")
+# Long to wide data -------------------------------------------------------
+
+dta_d1_wide <- dta_day1 %>% 
+  spread(key = TimeSlot, 
+         value = Carbo)
+
+head(dta_d1_wide)
+names(dta_d1_wide)[6:12] <- c("H6_9", "H9_12", "H12_14", "H14_17", 
+                              "H17_20", "H20_22", "H22_6")
+names(dta_d1_wide)
+
+dta_d2_wide <- dta_day2 %>% 
+  spread(key = TimeSlot, 
+         value = Carbo)
+
+head(dta_d2_wide)
+names(dta_d2_wide)[6:12] <- c("H6_9", "H9_12", "H12_14", "H14_17", 
+                              "H17_20", "H20_22", "H22_6")
+names(dta_d2_wide)
+
+dta_d3_wide <- dta_day3 %>% 
+  spread(key = TimeSlot, 
+         value = Carbo)
+
+head(dta_d3_wide)
+names(dta_d3_wide)[6:12] <- c("H6_9", "H9_12", "H12_14", "H14_17", 
+                              "H17_20", "H20_22", "H22_6")
+names(dta_d3_wide)
+
+dta_d4_wide <- dta_day4 %>% 
+  spread(key = TimeSlot, 
+         value = Carbo)
+
+head(dta_d4_wide)
+names(dta_d4_wide)[6:12] <- c("H6_9", "H9_12", "H12_14", "H14_17", 
+                              "H17_20", "H20_22", "H22_6")
+names(dta_d4_wide)
 
 # recode NA to not eating -------------------------------------------------
-for (i in 5:ncol(dta_d1_wide)) 
-  if (is.factor(dta_d1_wide[, i])) levels(dta_d1_wide[, 
-    i]) <- c(levels(dta_d1_wide[, i]), "Not_eating")
-
-dta_d1_wide[is.na(dta_d1_wide)] <- "Not_eating"
-
-for (i in 5:ncol(dta_d2_wide)) 
-  if (is.factor(dta_d2_wide[, i])) levels(dta_d2_wide[, 
-    i]) <- c(levels(dta_d2_wide[, i]), "Not_eating")
-
-dta_d2_wide[is.na(dta_d2_wide)] <- "Not_eating"
-
-for (i in 5:ncol(dta_d3_wide)) 
-  if (is.factor(dta_d3_wide[, i])) levels(dta_d3_wide[, 
-    i]) <- c(levels(dta_d3_wide[, i]), "Not_eating")
-
-dta_d3_wide[is.na(dta_d3_wide)] <- "Not_eating"
-
-for (i in 5:ncol(dta_d4_wide)) 
-  if (is.factor(dta_d4_wide[, i])) levels(dta_d4_wide[, 
-    i]) <- c(levels(dta_d4_wide[, i]), "Not_eating")
-
-dta_d4_wide[is.na(dta_d4_wide)] <- "Not_eating"
+
+for (i in 6:ncol(dta_d1_wide)) 
+  if(is.factor(dta_d1_wide[,i])) 
+    levels(dta_d1_wide[,i]) <- c("1", "2", "0")
+
+dta_d1_wide[is.na(dta_d1_wide)] <- "0"
+
+for (i in 6:ncol(dta_d2_wide)) 
+  if(is.factor(dta_d2_wide[,i])) 
+    levels(dta_d2_wide[,i]) <- c("1", "2",  "0")
+
+dta_d2_wide[is.na(dta_d2_wide)] <- "0"
+
+for (i in 6:ncol(dta_d3_wide)) 
+  if(is.factor(dta_d3_wide[,i])) 
+    levels(dta_d3_wide[,i]) <-  c("1", "2", "0")
+
+dta_d3_wide[is.na(dta_d3_wide)] <- "0"
+
+for (i in 6:ncol(dta_d4_wide)) 
+  if(is.factor(dta_d4_wide[,i])) 
+    levels(dta_d4_wide[,i]) <-  c("1", "2", "0")
+
+dta_d4_wide[is.na(dta_d4_wide)] <- "0"
+
+dta_all <- rbind(dta_d1_wide, dta_d2_wide, dta_d3_wide, dta_d4_wide)
+
+dta_all <- dta_all[order(dta_all$id,dta_all$id_dy),]
+
+# Export the data for Mplus -------------------------------------------------
+
+write_csv(dta_all, path = "dta_NDNS_Tslots.csv")
+write_delim(dta_all, "dta_NDNS_Tslots.dat", na = ".", delim = " ")
 ```
@@
 ```
+
+```{r  eval=FALSE}
+library(plyr)
+library(epiDisplay)
+library(tidyverse)
+library(dplyr)
+library(readr)
+library(haven)
+library(naniar)
+
+# read the individual level data sets ----------------------------------------
+
+blood78 <- read_dta("ndns_rp_yr7-8a_indiv.dta")
+blood56 <- read_dta("ndns_rp_yr5-6a_indiv.dta")
+blood14 <- read_dta("ndns_rp_yr1-4a_indiv_uk.dta")
+
+food14 <- read_dta("ndns_rp_yr1-4a_personleveldietarydata_uk.dta")
+
+food56 <- read_dta("ndns_rp_yr5-6a_personleveldietarydata.dta")
+
+food78 <- read_dta("ndns_rp_yr7-8a_personleveldietarydata.dta")
+
+names(blood78)[names(blood78)=="seriali"] <- "ID"
+names(blood56)[names(blood56)=="seriali"] <- "ID"
+names(blood14)[names(blood14)=="seriali"] <- "ID"
+names(food78)[names(food78)=="seriali"] <- "ID"
+names(food56)[names(food56)=="seriali"] <- "ID"
+names(food14)[names(food14)=="seriali"] <- "ID"
+
+# Loading the data from Mplus output
+CW3CB3 <- read_table2("../NDNSslot_CW3CB3.txt",  # change the path accordingly
+                      col_names = FALSE)
+
+names(CW3CB3) <- c("Breakfast", "Morning.snack", "Lunch",
+                   "Afternoon.snack", "Dinner", "Before.bedtime.snack",
+                   "Midnight.food", "ID_DAY", "AGE", "SEX", "CPROB1",
+                   "CPROB2", "CPROB3", "CPROB4", "CPROB5", "CPROB6", 
+                   "CPROB7", "CPROB8", "CPROB9", 
+                   "CB", "CW", "MLCJOINT", "ID")
+
+CW3idday <- CW3CB3 %>% 
+  select(ID, ID_DAY, CW, CB, MLCJOINT, AGE, SEX)
+
+Energy_slots <- read_csv("../Energy_slots.csv") # change the path accordingly
+Energy_slots <- Energy_slots %>% 
+  rename(ID = id)
+
+# Recode day level classification to keep consistency
+CW3idday$CW_new <- 0
+CW3idday$CW_new[CW3idday$CW == 1] <- 3
+CW3idday$CW_new[CW3idday$CW == 2] <- 1
+CW3idday$CW_new[CW3idday$CW == 3] <- 2
+
+Energy_slots <- Energy_slots %>% 
+  left_join(CW3idday, by = c("ID", "DayofWeek"))
+
+Energy_slots$TimeSlot <- factor(Energy_slots$TimeSlot, 
+                                levels = c("[6,9)", "[9,12)", 
+                                           "[12,14)", "[14,17)",
+                                           "[17,20)", "[20,22)", "[22, 6)"))
+
+FoodbyCB_7slots <- Energy_slots %>% 
+  group_by(ID, TimeSlot) %>% 
+  summarise(sumEnergy = sum(Tot_Energ),
+            sumCarb = sum(Tot_Carb), 
+            sumSugar = sum(Tot_Sugar), 
+            sumStarch = sum(Tot_Starch),
+            sumFibre = sum(Tot_Fibre), 
+            sumNMES = sum(Tot_NMES),
+            sumFat = sum(Tot_Fat),
+            sumProt = sum(Tot_Prot), 
+            sumAlc = sum(Tot_Alc))
+
+# Calculate the sum of each nutrients for each time slots
+Carbsum <- FoodbyCB_7slots %>% 
+  select(ID, TimeSlot, sumCarb) %>% 
+  spread(key = TimeSlot, 
+         value = sumCarb)
+
+Carbsum[is.na(Carbsum)] <- 0
+
+names(Carbsum) <- c("ID", "Carb6_9", "Carb9_12", "Carb12_14", "Carb14_17",
+                     "Carb17_20", "Carb20_22", "Carb22_6")
+
+Energysum <- FoodbyCB_7slots %>% 
+  select(ID, TimeSlot, sumEnergy) %>% 
+  spread(key = TimeSlot, 
+         value = sumEnergy)
+Energysum[is.na(Energysum)] <- 0
+
+names(Energysum) <- c("ID", "Energy6_9", "Energy9_12", "Energy12_14", "Energy14_17",
+                     "Energy17_20", "Energy20_22", "Energy22_6")
+
+Starchsum <- FoodbyCB_7slots %>% 
+  select(ID, TimeSlot, sumStarch) %>% 
+  spread(key = TimeSlot, 
+         value = sumStarch)
+Starchsum[is.na(Starchsum)] <- 0
+
+names(Starchsum) <- c("ID", "Starch6_9", "Starch9_12", "Starch12_14", "Starch14_17",
+                       "Starch17_20", "Starch20_22", "Starch22_6")
+
+Sugarsum <- FoodbyCB_7slots %>% 
+  select(ID, TimeSlot, sumSugar) %>% 
+  spread(key = TimeSlot, 
+         value = sumSugar)
+Sugarsum[is.na(Sugarsum)] <- 0
+
+names(Sugarsum) <- c("ID", "Sugar6_9", "Sugar9_12", "Sugar12_14", "Sugar14_17",
+                      "Sugar17_20", "Sugar20_22", "Sugar22_6")
+
+Fibresum <- FoodbyCB_7slots %>% 
+  select(ID, TimeSlot, sumFibre) %>% 
+  spread(key = TimeSlot, 
+         value = sumFibre)
+Fibresum[is.na(Fibresum)] <- 0
+
+names(Fibresum) <- c("ID", "Fibre6_9", "Fibre9_12", "Fibre12_14", "Fibre14_17",
+                      "Fibre17_20", "Fibre20_22", "Fibre22_6")
+
+NMESsum <- FoodbyCB_7slots %>% 
+  select(ID, TimeSlot, sumNMES) %>% 
+  spread(key = TimeSlot, 
+         value = sumNMES)
+NMESsum[is.na(NMESsum)] <- 0
+
+names(NMESsum) <- c("ID", "NMES6_9", "NMES9_12", "NMES12_14", "NMES14_17",
+                      "NMES17_20", "NMES20_22", "NMES22_6")
+
+Fatsum <- FoodbyCB_7slots %>% 
+  select(ID, TimeSlot, sumFat) %>% 
+  spread(key = TimeSlot, 
+         value = sumFat)
+Fatsum[is.na(Fatsum)] <- 0
+
+names(Fatsum) <- c("ID", "Fat6_9", "Fat9_12", "Fat12_14", "Fat14_17",
+                     "Fat17_20", "Fat20_22", "Fat22_6")
+
+Protsum <- FoodbyCB_7slots %>% 
+  select(ID, TimeSlot, sumProt) %>% 
+  spread(key = TimeSlot, 
+         value = sumProt)
+Protsum[is.na(Protsum)] <- 0
+
+names(Protsum) <- c("ID", "Prot6_9", "Prot9_12", "Prot12_14", "Prot14_17",
+                    "Prot17_20", "Prot20_22", "Prot22_6")
+
+Alcsum <- FoodbyCB_7slots %>% 
+  select(ID, TimeSlot, sumAlc) %>% 
+  spread(key = TimeSlot, 
+         value = sumAlc)
+Alcsum[is.na(Alcsum)] <- 0
+
+names(Alcsum) <- c("ID", "Alc6_9", "Alc9_12", "Alc12_14", "Alc14_17",
+                     "Alc17_20", "Alc20_22", "Alc22_6")
+
+# Extract number of days of diary completed
+
+blood14 <- blood14 %>% 
+  select(ID, Ndays)
+
+blood56 <- blood56 %>% 
+  select(ID, Ndays)
+
+blood78 <- blood78 %>% 
+  select(ID, NDays) %>% 
+  rename(Ndays = NDays)
+
+NDAYS <- rbind(blood14, blood56, blood78)
+NDAYS$ID <- as.numeric(NDAYS$ID)
+
+IntakeSlots <- Energysum %>% 
+  left_join(Carbsum, by = "ID") %>% 
+  left_join(Sugarsum, by = "ID") %>% 
+  left_join(Starchsum, by = "ID") %>% 
+  left_join(Fibresum, by = "ID") %>% 
+  left_join(Fatsum, by = "ID") %>% 
+  left_join(Protsum, by = "ID") %>% 
+  left_join(NMESsum, by = "ID") %>% 
+  left_join(Alcsum, by = "ID") %>% 
+  left_join(NDAYS, by = "ID")
+
+IntakeSlots$ID <- as.numeric(IntakeSlots$ID)
+
+IntakeSlots$Energy6_9 <- IntakeSlots$Energy6_9/(IntakeSlots$Ndays)
+
+for (i in 3:57){
+  IntakeSlots[, i] <- IntakeSlots[, i]/(IntakeSlots$Ndays)
+}
+
+# select the variables needed, recoding 
+# NAs, renaming to the same ----------------------------------------
+
+BMI78 <- blood78 %>% 
+  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc2, bpmedd2, 
+         hyper140_2, hibp140_2,  Glucose, A1C, cigsta3, dnoft3, 
+         dnnow, wti_Y78, wtn_Y78, wtb_Y78, ethgrp5, ethgrp2,
+         cluster1, cluster2, cluster3, nssec8, paidemployment, 
+         qual7, eqvinc, MarSt2, cluster4, cluster5, area, gor, 
+         LDL, HDL, Chol, Trig) %>% 
+  rename(wti = wti_Y78, wtn = wtn_Y78, wtb = wtb_Y78, 
+         drink = dnoft3) %>% 
+  mutate(Years = "7-8", MVPAtime = NA, MarStat = NA) %>% 
+  replace_with_na(replace = list(bmival = -1, qual7 = -8,
+                                 wstval = -1, eqvinc = -1,
+                                 bpmedd2 = -1, MarSt2 = -1,
+                                 bpmedc2 = -1, hyper140_2 = -7, 
+                                 hibp140_2 = -7, Glucose = -1, 
+                                 A1C  = -1,  LDL = -1, HDL = -1, 
+                                 Chol = -1, Trig = -1, dnnow = -1,
+                                 drink = -1, ethgrp5 = -4, 
+                                 ethgrp2 = -4, cigsta3 = -1, 
+                                 nssec8 = -9,  paidemployment = -1)) %>% 
+  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, 
+                                 nssec8 = 99, qual7 = -1, drink = -8, 
+                                 ethgrp2 = -9, ethgrp5 = -9)) %>% 
+  replace_with_na(replace = list(drink = -9, ethgrp2 = -8, ethgrp5 = -8,
+                                 cigsta3 = -8)) %>% 
+  replace_with_na(replace = list(ethgrp2 = -1, ethgrp5 = -1))
+
+BMI56 <- blood56 %>% 
+  select(ID, Sex, age, area, bmival, wstval, Diabetes, bpmedc2, bpmedd2, 
+         hyper140_2, hibp140_2, MVPAtime, Glucose, A1C, cigsta3, dnoft3, 
+         dnnow, wti_Y56, wtn_Y56, wtb_Y56, ethgrp5, ethgrp2, qual7,
+         cluster1, cluster2, cluster3, nssec8, paidemployment, eqvinc, 
+         MarSt2, cluster4, cluster5, area, gor, LDL, HDL, Chol, Trig) %>% 
+  mutate(Years = "5-6", MarStat = NA) %>% 
+  rename(wti = wti_Y56, wtn = wtn_Y56, wtb = wtb_Y56, drink = dnoft3) %>% 
+  replace_with_na(replace = list(bmival = -1, paidemployment = -9,
+                                 wstval = -1, qual7 = -8,
+                                 bpmedd2 = -1, eqvinc = -1,
+                                 bpmedc2 = -1, MarSt2 = -1,
+                                 hyper140_2 = -7, hibp140_2 = -7, 
+                                 Glucose = -1,  A1C  = -1, 
+                                 dnnow = -1, drink = -1, ethgrp5 = -4,
+                                 ethgrp2 = -4, LDL = -1, HDL = -1, 
+                                 Chol = -1, Trig = -1, cigsta3 = -1,
+                                 MVPAtime = -1, nssec8 = -9)) %>% 
+  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, 
+                                 paidemployment = -8, 
+                                 drink = -8, nssec8 = 99)) %>% 
+    replace_with_na(replace = list(drink = -9, paidemployment = -1, 
+                                   qual7 = -1, cigsta3 = -8))
+
+BMI14 <- blood14 %>% 
+  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc, bpmedd, hyper140, 
+         hibp140, MVPAtime, Glucose, A1C, cigsta3, dnoft3, dnnow, 
+         wti_CY1234, wtn_CY1234, wtb_CY1234, ethgr5, ethgr2, cluster, 
+         area, gor, nssec8, paidemployment, qual7, eqvinc, MarSt2, 
+         MarStat, LDL, HDL, Chol, Trig) %>%
+  rename(hyper140_2 = hyper140, hibp140_2 = hibp140, bpmedd2 = bpmedd, 
+         bpmedc2 = bpmedc, cluster1 = cluster, ethgrp5 = ethgr5, 
+         ethgrp2 = ethgr2, wti = wti_CY1234, wtn = wtn_CY1234, 
+         wtb =  wtb_CY1234, drink = dnoft3) %>% 
+  mutate(cluster2 = NA, cluster3 = NA, cluster4 = NA, cluster5 = NA, 
+         Years = "1-4") %>% 
+  replace_with_na(replace = list(bmival = -1, paidemployment = -9, 
+                                 wstval = -1, qual7 = -8,
+                                 bpmedd2 = -1, eqvinc = -1,
+                                 bpmedc2 = -1, MarSt2 = -4, 
+                                 hyper140_2 = -7, MarStat = -4,
+                                 hibp140_2 = -7,  Glucose = -1, 
+                                 A1C  = -1,  dnnow = -1, LDL = -1, 
+                                 HDL = -1, Chol = -1, Trig = -1,
+                                 drink = -1, ethgrp5 = -4, ethgrp2 = -4,
+                                 cigsta3 = -1, MVPAtime = -4,  
+                                 nssec8 = -8)) %>% 
+  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, 
+                                 MVPAtime = -1, paidemployment = -8,
+                                 drink = -8, nssec8 = -1, qual7 = -1, 
+                                 MarSt2 = -1)) %>% 
+  replace_with_na(replace = list(drink = -9, paidemployment = -4,
+                                 cigsta3 = -8, nssec8 = 99)) %>% 
+  replace_with_na(replace = list(paidemployment = -1))
+
+BMI <- bind_rows(BMI14, BMI56, BMI78)
+
+Energy14 <- food14 %>% 
+  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, 
+         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,
+         Fatg, FatpctotE)
+Energy14$Country[Energy14$Country == "Northern Ireland"] <- "NI"
+
+Energy56 <- food56 %>% 
+  select(ID, Country, Surveyyear, EnergykJ, Carbohydrateg, 
+         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,
+         Fatg, FatpctotE) %>% 
+  rename(SurveyYear = Surveyyear)
+
+Energy78 <- food78 %>% 
+  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, 
+         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,
+         Fatg, FatpctotE)
+
+Energy <- bind_rows(Energy14, Energy56, Energy78)
+
+dta_NDNS <- read_csv("dta_NDNS_Tslots.csv") # extract the day of week data
+
+CW3idday$DayNo <- ave(CW3idday$ID_DAY, CW3idday$ID, 
+                      FUN = seq_along) # adding the day no
+
+dta_DayofWeek <- dta_NDNS %>% 
+  select(id, id_dy, DayofWeek)
+
+dta_DayofWeek$DayNo <- unlist(strsplit(dta_DayofWeek$id_dy,
+                                       "D"))[c(FALSE, TRUE)] # creating a day No
+names(dta_DayofWeek)[1] <- "ID"
+dta_DayofWeek$DayNo <- as.numeric(dta_DayofWeek$DayNo)
+
+CW3idday <-   CW3idday %>%  
+  left_join(dta_DayofWeek, by= c("ID", "DayNo"))
+
+## Manually check the day of week
+CW3idday$DayofWeek[CW3idday$ID_DAY == 40714261000] <- "Saturday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 112050710000] <- "Tuesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 310122510000] <- "Wednesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 5050616100] <- "Monday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 50506161000] <- "Tuesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 505061610000] <- "Wednesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 7090824100] <- "Monday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 70908241000] <- "Tuesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 709082410000] <- "Wednesday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 807021910000] <- "Monday"
+CW3idday$DayofWeek[CW3idday$ID_DAY == 812101310000] <- "Sunday"
+
+CW3CB3_reg <- CW3CB3[!duplicated(CW3CB3$ID), ]
+
+# extract only the CB variable (Between individual classes == 1 or 2)
+CW3CB3_reg <- CW3CB3_reg %>% 
+  select(ID, AGE, SEX, CB)
+
+tab1(CW3CB3_reg$CB, graph = FALSE)
+
+## dataset for 3by3 multilevel latent classes 
+CW3CB3_regss <- CW3CB3_reg %>% 
+  left_join(BMI, by = "ID") %>% 
+  left_join(Energy, by = "ID")
+
+# Rescale the weighting values
+# individual weighting
+
+a <- sum(CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wti)
+b <- sum(CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wti)
+c <- sum(CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wti)
+
+CW3CB3_regss$wti1to8 <- CW3CB3_regss$wti
+
+CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wti1to8 <- 
+  CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wti*(a+b+c)*(1/2)/a
+CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wti1to8 <- 
+  CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wti*(a+b+c)*(1/4)/b
+CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wti1to8 <- 
+  CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wti*(a+b+c)*(1/4)/c
+mean(CW3CB3_regss$wti1to8)
+
+CW3CB3_regss$wti1to8 <- CW3CB3_regss$wti1to8/1.209816814
+summ(CW3CB3_regss$wti1to8, graph = FALSE)
+#Check if the weighting sum up to the sample size we have
+sum(CW3CB3_regss$wti1to8, graph = FALSE)
+
+# Nurse weights
+
+a <- sum(CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wtn)
+b <- sum(CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wtn)
+c <- sum(CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wtn)
+
+CW3CB3_regss$wtn1to8 <- CW3CB3_regss$wtn
+
+CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wtn1to8 <- 
+  CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wtn*(a+b+c)*(1/2)/a
+CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wtn1to8 <- 
+  CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wtn*(a+b+c)*(1/4)/b
+CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wtn1to8 <- 
+  CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wtn*(a+b+c)*(1/4)/c
+mean(CW3CB3_regss$wtn1to8)
+
+CW3CB3_regss$wtn1to8 <- CW3CB3_regss$wtn1to8/0.907003577
+summ(CW3CB3_regss$wtn1to8, graph = FALSE)
+#Check if the weighting sum up to the sample size we have
+sum(CW3CB3_regss$wtn1to8, graph = FALSE)
+
+# Blood weights
+a <- sum(CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wtb)
+b <- sum(CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wtb)
+c <- sum(CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wtb)
+
+CW3CB3_regss$wtb1to8 <- CW3CB3_regss$wtb
+
+CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wtb1to8 <- 
+  CW3CB3_regss[CW3CB3_regss$Years == "1-4",]$wtb*(a+b+c)*(1/2)/a
+CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wtb1to8 <- 
+  CW3CB3_regss[CW3CB3_regss$Years == "5-6",]$wtb*(a+b+c)*(1/4)/b
+CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wtb1to8 <- 
+  CW3CB3_regss[CW3CB3_regss$Years == "7-8",]$wtb*(a+b+c)*(1/4)/c
+mean(CW3CB3_regss$wtb1to8)
+
+CW3CB3_regss$wtb1to8 <- CW3CB3_regss$wtb1to8/0.4817444505
+summ(CW3CB3_regss$wtb1to8, graph = FALSE)
+#Check if the weighting sum up to the sample size we have
+sum(CW3CB3_regss$wtb1to8, graph = FALSE)
+
+weightings <- CW3CB3_regss %>% select(ID, wti1to8, wtn1to8, wtb1to8)
+
+# Combine the data from nutrient intake at each time slot
+CW3CB3_7regss <- CW3CB3_7regss %>% 
+  left_join(IntakeSlots, by = "ID")
+
+## dta ready to be analysed in STATA
+ # change the path accordingly
+write_dta(CW3CB3_regss, "../CW3CB3_7regss.dta")
+```
+
+```
+************************************************
+// Analysing NDNS survey data in stata
+// for CW3CB3 survey data analysis 
+// date created: 2018-08-01
+// manipulation of the data was done in R
+// import data from CW3CB3_7sregss.dta
+// change the path accordingly
+************************************************
+
+use "../CW3CB3_7regss.dta", clear
+
+label define smoking 1 "current" 2 "ex-smoker" 3 "Never"
+label values cigsta3 smoking
+label define gender 1 "Men" 2 "Women"
+label values Sex gender
+label define paid 1 "No" 2 "Yes"
+label values paidemployment paid
+label define ethnicity5 1 "White" 2 "Mixed" 3 "Black" 4 "Asian" 5 "Other"
+label values ethgrp5 ethnicity5
+label define ethnicity2 1 "White" 2 "non-White"
+label values ethgrp2 ethnicity2
+
+gen Married = 1 if MarStat == 2 | MarSt2 == 2 
+replace Married = 1 if MarSt2 == 3
+replace Married = 0 if Married !=1
+tab Married
+tab MarSt2
+tab MarStat
+
+label define Partner 0 "No" 1 "Yes"
+label values Married Partner
+
+gen Education = qual7 == 1
+label define Ed 0 "lower than Degree" 1 "Degree or higher"
+label values Education Ed
+
+replace Education = . if qual7 >100
+tab Educ
+
+egen BMIcat = cut(bmival), at(10, 25, 30, 40, 60)
+tab BMIcat
+
+**********************************************************
+// variables need to be log transfomred                 //
+**********************************************************
+
+gen logalc = ln(Alcoholg+1)
+summ logalc, detail
+gen logMVP = ln(MVPAtime+1)
+summ logMVP, detail
+gen logGlu = ln(Glucose)
+summ logGlu, detail
+gen logA1C = ln(A1C)
+summ logA1C, detail
+gen logChol = ln(Chol)
+summ logChol, detail
+gen logLDL = ln(LDL)
+gen logHDL = ln(HDL)
+gen logTG = ln(Trig)
+
+*********************************************************
+//  weighting use wti to see the individual results    //
+//                                                     //
+*********************************************************
+
+// weighting with individual weights, area is primary sampling unit, 
+// gor is the cluster variable
+
+svyset area [pweight = wti1to8], strata(gor)
+
+svydescribe wti // describe the weighted data set
+
+svy: tabulate Sex CB, row se ci format(%7.3f)
+svy: tabulate Sex CB, col se ci format(%7.3f)
+svy: tabulate Country CB, col se ci format(%7.3f)
+svy: tabulate Country CB, row se ci format(%7.3f)
+svy: tabulate SurveyYear CB, col se ci format(%7.3f)
+svy: tabulate SurveyYear CB, row se ci format(%7.3f)
+svy: tabulate paid CB, col se ci format(%7.3f)
+
+svy: tabulate MarSt2 CB
+svy: tabulate MarStat CB
+svy: tabulate Married CB, row se ci format(%7.3f)
+svy: tabulate Married CB, col se ci format(%7.3f)
+svy: mean eqvinc, over(CB)
+test [eqvinc]1 = [eqvinc]2 = [eqvinc]3, mtest(b) 
+// bonferroni-adjusted p-values for multiple groups using the mtest(b) option
+
+svy: tabulate ethgrp2 CB, row se ci format(%7.3f)
+svy: tabulate ethgrp2 CB, col se ci format(%7.3f)
+svy: tabulate Education CB, row se ci format(%7.3f)
+svy: tabulate Education CB, col se ci format(%7.3f)
+
+*********************************************************
+//  nutritional distribution                           //
+//                                                     //
+*********************************************************
+
+svy: mean EnergykJ, over(CB)
+test [EnergykJ]1 = [EnergykJ]2 = [EnergykJ]3, mtest(b)
+
+svy: mean Energy6, over(CB)
+test [Energy6_9]1 = [Energy6_9]2 = [Energy6_9]3, mtest(b)
+
+svy: mean Energy9, over(CB) 
+test [Energy9_12]1 = [Energy9_12]2 = [Energy9_12]3, mtest(b)
+
+svy: mean Energy12, over(CB)
+test [Energy12_14]1 = [Energy12_14]2 = [Energy12_14]3, mtest(b)
+
+svy: mean Energy14, over(CB)
+test [Energy14_17]1 = [Energy14_17]2 = [Energy14_17]3, mtest(b)
+
+svy: mean Energy17, over(CB)
+test [Energy17_20]1 = [Energy17_20]2 = [Energy17_20]3, mtest(b)
+
+svy: mean Energy20, over(CB)
+test [Energy20_22]1 = [Energy20_22]2 = [Energy20_22]3, mtest(b)
+
+svy: mean Energy22, over(CB)
+test [Energy22_6]1 = [Energy22_6]2 = [Energy22_6]3, mtest(b)
+
+svy: mean Carbohydrateg, over(CB)
+test [Carbohydrateg]1 = [Carbohydrateg]2 = [Carbohydrateg]3, mtest(b)
+
+svy: mean Carb6, over(CB)
+test [Carb6_9]1 = [Carb6_9]2 = [Carb6_9]3, mtest(b)
+
+svy: mean Carb9, over(CB)
+test [Carb9_12]1 = [Carb9_12]2 = [Carb9_12]3, mtest(b)
+
+svy: mean Carb12, over(CB)
+test [Carb12_14]1 = [Carb12_14]2 = [Carb12_14]3, mtest(b)
+
+svy: mean Carb14, over(CB)
+test [Carb14_17]1 = [Carb14_17]2 = [Carb14_17]3, mtest(b)
+
+svy: mean Carb17, over(CB)
+test [Carb17_20]1 = [Carb17_20]2 = [Carb17_20]3, mtest(b)
+
+svy: mean Carb20, over(CB)
+test [Carb20_22]1 = [Carb20_22]2 = [Carb20_22]3, mtest(b)
+
+svy: mean Carb22, over(CB)
+test [Carb22_6]1 = [Carb22_6]2 = [Carb22_6]3, mtest(b)
+
+svy: mean Sugar6, over(CB)
+test [Sugar6_9]1 = [Sugar6_9]2 = [Sugar6_9]3, mtest(b)
+
+svy: mean Sugar9, over(CB)
+test [Sugar9_12]1 = [Sugar9_12]2 = [Sugar9_12]3, mtest(b)
+
+svy: mean Sugar12, over(CB)
+test [Sugar9_12]1 = [Sugar9_12]2 = [Sugar9_12]3, mtest(b)
+
+svy: mean Sugar14, over(CB)
+test [Sugar14_17]1 = [Sugar14_17]2 = [Sugar14_17]3, mtest(b)
+
+svy: mean Sugar17, over(CB)
+test [Sugar17_20]1 = [Sugar17_20]2 = [Sugar17_20]3, mtest(b)
+
+svy: mean Sugar20, over(CB)
+test [Sugar20_22]1 = [Sugar20_22]2 = [Sugar20_22]3, mtest(b)
+
+svy: mean Sugar22, over(CB)
+test [Sugar22_6]1 = [Sugar22_6]2 = [Sugar22_6]3, mtest(b)
+
+svy: mean Starch6, over(CB)
+test [Starch6_9]1 = [Starch6_9]2 = [Starch6_9]3, mtest(b)
+
+svy: mean Starch9, over(CB)
+test [Sugar12_14]1 = [Sugar12_14]2 = [Sugar12_14]3, mtest(b)
+
+svy: mean Starch12, over(CB)
+test [Starch12_14]1 = [Starch12_14]2 = [Starch12_14]3, mtest(b)
+
+svy: mean Starch14, over(CB)
+test [Starch14_17]1 = [Starch14_17]2 = [Starch14_17]3, mtest(b)
+
+svy: mean Starch17, over(CB)
+test [Starch17_20]1 = [Starch17_20]2 = [Starch17_20]3, mtest(b)
+
+svy: mean Starch20, over(CB)
+test [Starch20_22]1 = [Starch20_22]2 = [Starch20_22]3, mtest(b)
+
+svy: mean Starch22, over(CB)
+test [Starch20_22]1 = [Starch20_22]2 = [Starch20_22]3, mtest(b)
+
+svy: mean Fibre6, over(CB)
+test [Starch22_6]1 = [Starch22_6]2 = [Starch22_6]3, mtest(b)
+
+gen Fibreg = Fibre6 + Fibre9 + Fibre12 + Fibre14 + Fibre17 + Fibre20 + Fibre22
+svy: mean Fibreg, over(CB)
+test [Fibreg]1 = [Fibreg]2 = [Fibreg]3, mtest(b)
+
+svy: mean Fibre9, over(CB)
+test [Fibre9_12]1 = [Fibre9_12]2 = [Fibre9_12]3, mtest(b)
+
+svy: mean Fibre12, over(CB)
+test [Fibre12_14]1 = [Fibre12_14]2 = [Fibre12_14]3, mtest(b)
+
+svy: mean Fibre14, over(CB)
+test [Fibre14_17]1 = [Fibre14_17]2 = [Fibre14_17]3, mtest(b)
+
+svy: mean Fibre17, over(CB)
+test [Fibre17_20]1 = [Fibre17_20]2 = [Fibre17_20]3, mtest(b)
+
+svy: mean Fibre20, over(CB)
+test [Fibre20_22]1 = [Fibre20_22]2 = [Fibre20_22]3, mtest(b)
+
+svy: mean Fibre22, over(CB)
+test [Fibre22_6]1 = [Fibre22_6]2 = [Fibre22_6]3, mtest(b)
+
+svy: mean NMES6, over(CB)
+test [NMES6_9]1 = [NMES6_9]2 = [NMES6_9]3, mtest(b)
+
+svy: mean NMES9, over(CB)
+test [NMES9_12]1 = [NMES9_12]2 = [NMES9_12]3, mtest(b)
+
+svy: mean NMES12, over(CB)
+test [NMES12_14]1 = [NMES12_14]2 = [NMES12_14]3, mtest(b)
+
+svy: mean NMES14, over(CB)
+test [NMES14_17]1 = [NMES14_17]2 = [NMES14_17]3, mtest(b)
+
+svy: mean NMES17, over(CB)
+test [NMES17_20]1 = [NMES17_20]2 = [NMES17_20]3, mtest(b)
+
+svy: mean NMES20, over(CB)
+test [NMES20_22]1 = [NMES20_22]2 = [NMES20_22]3, mtest(b)
+
+svy: mean NMES22, over(CB)
+
+svy: mean CHO, over(CB)
+test [CHOpctotE]1 = [CHOpctotE]2 = [CHOpctotE]3, mtest(b)
+
+svy: mean Proteing, over(CB)
+test [Proteing]1 = [Proteing]2 = [Proteing]3, mtest(b)
+
+svy: mean Prot6, over(CB)
+test [Prot6_9]1 = [Prot6_9]2 = [Prot6_9]3, mtest(b)
+
+svy: mean Prot9, over(CB)
+test [Prot9_12]1 = [Prot9_12]2 = [Prot9_12]3, mtest(b)
+
+svy: mean Prot12, over(CB)
+test [Prot12_14]1 = [Prot12_14]2 = [Prot12_14]3, mtest(b)
+
+svy: mean Prot14, over(CB)
+test [Prot14_17]1 = [Prot14_17]2 = [Prot14_17]3, mtest(b)
+
+svy: mean Prot17, over(CB)
+test [Prot17_20]1 = [Prot17_20]2 = [Prot17_20]3, mtest(b)
+
+svy: mean Prot20, over(CB)
+test [Prot20_22]1 = [Prot20_22]2 = [Prot20_22]3, mtest(b)
+
+svy: mean Prot22, over(CB)
+test [Prot22_6]1 = [Prot22_6]2 = [Prot22_6]3, mtest(b)
+
+svy: mean Proteinp, over(CB)
+test [ProteinpctotE]1 = [ProteinpctotE]2 = [ProteinpctotE]3, mtest(b)
+
+svy: mean Fatg, over(CB)
+test [Fatg]1 = [Fatg]2 = [Fatg]3, mtest(b)
+
+svy: mean Fat6, over(CB)
+test [Fat6_9]1 = [Fat6_9]2 = [Fat6_9]3, mtest(b)
+
+svy: mean Fat9, over(CB)
+test [Fat9_12]1 = [Fat9_12]2 = [Fat9_12]3, mtest(b)
+
+svy: mean Fat12, over(CB)
+test [Fat12_14]1 = [Fat12_14]2 = [Fat12_14]3, mtest(b)
+
+svy: mean Fat14, over(CB)
+test [Fat14_17]1 = [Fat14_17]2 = [Fat14_17]3, mtest(b)
+
+svy: mean Fat17, over(CB)
+test [Fat17_20]1 = [Fat17_20]2 = [Fat17_20]3, mtest(b)
+
+svy: mean Fat20, over(CB)
+test [Fat20_22]1 = [Fat20_22]2 = [Fat20_22]3, mtest(b)
+
+svy: mean Fat22, over(CB)
+test [Fat22_6]1 = [Fat22_6]2 = [Fat22_6]3, mtest(b)
+
+svy: mean Fatp, over(CB)
+test [FatpctotE]1 = [FatpctotE]2 = [FatpctotE]3, mtest(b)
+
+svy: mean Alcoholg, over(CB)
+test [Alcoholg]1 = [Alcoholg]2 = [Alcoholg]3, mtest(b)
+
+svy: mean Alc6, over(CB)
+test [Alc6_9]1 = [Alc6_9]2 = [Alc6_9]3, mtest(b)
+
+svy: mean Alc9, over(CB)
+test [Alc9_12]1 = [Alc9_12]2 = [Alc9_12]3, mtest(b)
+
+svy: mean Alc12, over(CB)
+test [Alc12_14]1 = [Alc12_14]2 = [Alc12_14]3, mtest(b)
+
+svy: mean Alc14, over(CB)
+test [Alc14_17]1 = [Alc14_17]2 = [Alc14_17]3, mtest(b)
+
+svy: mean Alc17, over(CB)
+test [Alc14_17]1 = [Alc14_17]2 = [Alc14_17]3, mtest(b)
+
+svy: mean Alc20, over(CB)
+test [Alc14_17]1 = [Alc14_17]2 = [Alc14_17]3, mtest(b)
+
+svy: mean Alcoholp, over(CB)
+test [AlcoholpctotE]1 = [AlcoholpctotE]2 = [AlcoholpctotE]3, mtest(b)
+
+svy: tabulate cigsta3 CB, col se ci format(%7.3f)
+svy: tabulate dnnow CB, col se ci format(%7.3f)
+svy: tabulate hibp CB, col se ci format(%7.3f)
+
+sum MVP [weight=wti1to8] if CB ==1 , det
+sum MVP [weight=wti1to8] if CB ==2 , det
+sum MVP [weight=wti1to8] if CB ==3 , det
+svy: mean MVP, over(CB)
+
+svy: mean logMVP, over(CB) eform
+test [logMVP]1 = [logMVP]2 = [logMVP]3, mtest(b)
+
+disp exp(.731059) - 1    
+dis exp(.6768489) -1 
+dis exp(.7852691) -1
+
+disp exp(.6239265) - 1    
+dis exp(.571165) -1 
+dis exp( .6766879) -1
+
+disp exp(.7273621) - 1    
+dis exp(.684545) -1 
+dis exp(.7701791) -1
+
+svy: mean logalc, over(CB)
+
+disp exp( 2.035795) - 1    
+dis exp(1.933326) -1 
+dis exp(2.138264) -1
+
+*********************************************************
+//  re-weighting use wtn to see the BMI,wc measurements //
+//                                                     //
+*********************************************************
+
+svyset area [pweight = wtn1to8], strata(gor)
+svy: mean wst, over(CB)
+test [wstval]1 = [wstval]2 = [wstval]3, mtest(b)
+
+gen Men = Sex == 1 
+svy, subpop(Men): mean wst, over(CB)
+test [wstval]1 = [wstval]2 = [wstval]3, mtest(b)
+
+gen Women = Sex == 2
+svy, subpop(Women): mean wst, over(CB)
+test [wstval]1 = [wstval]2 = [wstval]3, mtest(b)
+
+svy: mean bmi, over(CB)
+
+test [bmival]1 = [bmival]2 = [bmival]3, mtest(b)
+
+*********************************************************
+//  re-weighting use wtb to see the blood test results //
+//                                                     //
+*********************************************************
+
+svyset area [pweight = wtb1to8], strata(gor)
+
+svy: mean HDL, over(CB)
+test [HDL]1 = [HDL]2 = [HDL]3, mtest(b)
+
+svy: mean Chol, over(CB)
+test [Chol]1 = [Chol]2 = [Chol]3, mtest(b)
+
+svy: mean LDL, over(CB)
+test [LDL]1 = [LDL]2 = [LDL]3, mtest(b)
+
+svy: mean Trig, over(CB)
+test [Trig]1 = [Trig]2 = [Trig]3, mtest(b)
+
+gen DM = A1C <= 6.5 if !missing(A1C)
+
+svy, subpop(DM): mean Glucose, over(CB)
+test [Glucose]1 = [Glucose]2
+test [Glucose]1 = [Glucose]2 = [Glucose]3, mtest(b)
+
+svy, subpop(DM): mean A1C, over(CB)
+test [A1C]1 = [A1C]2
+test [A1C]1 = [A1C]2 = [A1C]3, mtest(b)
+
+svy: tabulate DM CB, col se ci format(%7.3f)
+
+svy, subpop(DM): mean Glucose, over(CB)
+test [Glucose]1 = [Glucose]2
+test [Glucose]1 = [Glucose]2 = [Glucose]3, mtest(b)
+svy, subpop(DM): mean A1C, over(C)
+test [A1C]1 = [A1C]2
+test [A1C]1 = [A1C]2 = [A1C]3, mtest(b)
+
+svy: tabulate DM C, col se ci format(%7.3f)
+
+svy, subpop(DM): mean logGlu, over(CB)
+test [logGlu]1 = [logGlu]2 = [logGlu]3, mtest(b)
+
+dis exp(1.642848)
+dis exp(1.632226)
+dis exp(1.653471)
+
+dis exp(1.620347)
+dis exp(1.606447)
+dis exp(1.634246)
+
+dis exp(1.629356)
+dis exp(1.620271)
+dis exp(1.63844)
+
+svy, subpop(DM): mean logA1C, over(CB)
+test [logA1C]1 = [logA1C]2 = [logA1C]3, mtest(b)
+
+dis exp(1.699581)
+dis exp(1.69296)
+dis exp(1.706203)
+
+dis exp(1.691608)
+dis exp(1.683897)
+dis exp(1.699318)
+
+dis exp(1.705623)
+dis exp(1.700665)
+dis exp(1.710581)
+
+svy: mean logChol, over(CB)
+dis exp(1.598818)
+dis exp(1.577698)
+dis exp(1.619939)
+
+dis exp(1.55251)  
+dis exp(1.530408)
+dis exp(1.574613)
+
+dis exp(1.599389)
+dis exp(1.583391)
+dis exp(1.615388)
+
+test [logChol]1 = [logChol]2 = [logChol]3, mtest(b)
+
+svy: mean logHDL, over(CB)
+dis exp(.3293169)
+dis exp(.3026793)
+dis exp(.3559545)
+
+dis exp(.2749379)  
+dis exp(.2476816)
+dis exp(.3021941)
+
+dis exp(.3269002)
+dis exp(.3062623)
+dis exp(.3475381)
+
+test [logHDL]1 = [logHDL]2 = [logHDL]3, mtest(b)
+
+svy: mean logLDL, over(CB)
+dis exp(1.058635)
+dis exp(1.028391)
+dis exp(1.08888)
+
+dis exp(1.018181)  
+dis exp(.984431)
+dis exp(1.051931)
+
+dis exp(1.075229)
+dis exp(1.051369)
+dis exp(1.09909)
+
+test [logLDL]1 = [logLDL]2 = [logLDL]3, mtest(b)
+
+svy: mean logTG, over(CB)
+dis exp(.1273876)
+dis exp(.0777152)
+dis exp(.17706)
+
+dis exp(.1012169)  
+dis exp(.0460972)
+dis exp(.1563366)
+
+dis exp(.0983298)
+dis exp(.0607423)
+dis exp(.1359172)
+
+test [logTG]1 = [logTG]2 = [logTG]3, mtest(b)
+
+***************************************************
+// Analysing NDNS survey data in stata
+// for CW3CB3 survey data analysis on hypertension
+// date created: 2018-08-06
+// manipulation of the data was done in R
+// import data from CW3CB3_7sregss.dta
+// change the path accordingly
+**************************************************
+
+use "../CW3CB3_7regss.dta", clear
+
+label define smoking 1 "current" 2 "ex-smoker" 3 "Never"
+label values cigsta3 smoking
+label define gender 1 "Men" 2 "Women"
+label values Sex gender
+label define paid 1 "No" 2 "Yes"
+label values paidemployment paid
+label define ethnicity5 1 "White" 2 "Mixed" 3 "Black" 4 "Asian" 5 "Other"
+label values ethgrp5 ethnicity5
+label define ethnicity2 1 "White" 2 "non-White"
+label values ethgrp2 ethnicity2
+
+gen Married = 1 if MarStat == 2 | MarSt2 == 2 
+replace Married = 1 if MarSt2 == 3
+replace Married = 0 if Married !=1
+tab Married
+tab MarSt2
+tab MarStat
+
+label define Partner 0 "No" 1 "Yes"
+label values Married Partner
+
+gen Education = qual7 == 1
+label define Ed 0 "lower than Degree" 1 "Degree or higher"
+label values Education Ed
+
+replace Education = . if qual7 >100
+tab Educ
+
+egen BMIcat = cut(bmival), at(10, 25, 30, 40, 60)
+tab BMIcat
+
+**********************************************************
+// variables need to be log transfomred                 //
+**********************************************************
+
+gen logalc = ln(Alcoholg+1)
+summ logalc, detail
+gen logMVP = ln(MVPAtime+1)
+summ logMVP, detail
+gen logGlu = ln(Glucose)
+summ logGlu, detail
+gen logA1C = ln(A1C)
+summ logA1C, detail
+gen logChol = ln(Chol)
+summ logChol, detail
+gen logLDL = ln(LDL)
+gen logHDL = ln(HDL)
+gen logTG = ln(Trig)
+
+*********************************************************
+//  weighting use wti to see the individual results    //
+//                                                     //
+*********************************************************
+
+// weighting with individual weights, area is primary sampling unit, 
+// gor is the cluster variable
+svyset area [pweight = wti1to8], strata(gor)
+
+svydescribe wti // describe the weighted data set
+
+*********************************************************
+//  re-weighting use wtn to see the BMI,wc measurements //
+//                                                     //
+*********************************************************
+
+svyset area [pweight = wtn1to8], strata(gor)
+
+gen Men = Sex == 1  //  n of men = 2537
+gen Women = Sex == 2 // n of women = 3618
+
+svy, subpop(Men): tab hibp, se ci format(%7.3f)
+svy, subpop(Women): tab hibp, se ci format(%7.3f)
+
+svy, subpop(Men): mean age, over(hibp)
+test [age]1 = [age]0
+svy, subpop(Women): mean age, over(hibp)
+test [age]1 = [age]0
+
+svy, subpop(Men): mean wst, over(hibp)
+test [wstval]1 = [wstval]0
+svy, subpop(Women): mean wst, over(hibp)
+test [wstval]1 = [wstval]0
+
+svy, subpop(Men): tabulate CB hibp, col se ci format(%7.3f)
+
+svy, subpop(Women): tabulate CB hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate Country hibp, col se ci format(%7.3f)
+
+svy, subpop(Women): tabulate Country hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate SurveyYear hibp, col se ci format(%7.3f)
+
+svy, subpop(Women): tabulate SurveyYear hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate ethgrp2 hibp, col se ci format(%7.3f)
+
+svy, subpop(Women): tabulate ethgrp2 hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate Edu hibp, col se ci format(%7.3f)
+
+svy, subpop(Women): tabulate Edu hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate cigsta3 hibp, col se ci format(%7.3f)
+
+svy, subpop(Women): tabulate cigsta3 hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate Married hibp, col  se ci format(%7.3f)
+
+svy, subpop(Men): mean logMVP, over(hibp)
+test [logMVP]1 = [logMVP]0
+
+disp exp(.9234363 ) - 1    
+dis exp(.8457101) -1 
+dis exp(1.001163) -1
+
+disp exp(.828635) - 1    
+dis exp(.730244) -1 
+dis exp( .9270261) -1
+
+svy, subpop(Women): mean logMVP, over(hibp) 
+test [logMVP]1 = [logMVP]0
+
+disp exp(.5916676) - 1    
+dis exp(.5473043) -1 
+dis exp(.6360309) -1
+
+disp exp(.4231103) - 1    
+dis exp(.3536885) -1 
+dis exp(.4925322) -1
+
+svy: mean logalc, over(CB)
+
+disp exp( 2.035795) - 1    
+dis exp(1.933326) -1 
+dis exp(2.138264) -1
+
+svy, subpop(Men): mean bmi, over(hibp)
+test [bmival]1 = [bmival]0
+svy, subpop(Women): mean bmi, over(hibp)
+test [bmival]1 = [bmival]0
+
+svy, subpop(Men): mean EnergykJ, over(hibp)
+test [EnergykJkJ]1 = [EnergykJkJ]0
+svy, subpop(Women): mean EnergykJ, over(hibp)
+test [EnergykJkJ]1 = [EnergykJkJ]0
+
+svy, subpop(Men): mean Carbo, over(hibp)
+test [Carbohydrateg]1 = [Carbohydrateg]0
+
+svy, subpop(Women): mean Carbohydrateg, over(hibp)
+test [Carbohydrateg]1 = [Carbohydrateg]0
+
+svy, subpop(Men): mean Proteing, over(hibp)
+test [Proteing]1 = [Proteing]0
+
+svy, subpop(Women): mean Carbohydrateg, over(hibp)
+test [Carbohydrateg]1 = [Carbohydrateg]0
+
+svy: tabulate Sex hibp, col se ci format(%7.3f)
+
+svy: logistic hibp i.CB
+svy: logistic hibp i.CB#i.Sex
+
+test 2.CB#2.Sex
+
+svy: tabulate paid hibp, col se ci format(%7.3f)
+
+gen DM = A1C > 6.5 if !missing(A1C)
+svyset area [pweight = wtb1to8], strata(gor)
+
+svy, subpop(Men): tabulate DM hibp, col se ci format(%7.3f)
+svy, subpop(Women): tabulate DM hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate Married hibp, col se ci format(%7.3f)
+svy, subpop(Women): tabulate Married hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): mean eqvinc, over(hibp)
+test [eqvinc]1 = [eqvinc]0
+
+svy, subpop(Women): mean eqvinc, over(hibp)
+test [eqvinc]1 = [eqvinc]0
+
+********************************************************
+**   Building the GLM model 
+**   date: 07/08/2018
+**
+**
+********************************************************
+
+svyset area [pweight = wtn1to8], strata(gor)
+
+// crude association between CB and hypertension
+
+svy, subpop(Men): logistic hibp i.CB
+
+svy, subpop(Women): logistic hibp i.CB
+
+// in non DM 
+svy, subpop(Men if DM != 1): logistic hibp i.CB
+svy, subpop(Women if DM != 1): logistic hibp i.CB
+
+// looking for confounders one by one
+// Age: -> confounder
+svy, subpop(Men): logistic hibp i.CB age
+test age
+svy, subpop(Women): logistic hibp i.CB age
+test age
+
+svy, subpop(Men): logistic hibp i.CB##c.age
+svy, subpop(Women): logistic hibp i.CB##c.age
+test 2.CB#c.age 3.CB#c.age // no interaction
+
+// Partner -> confounder
+svy, subpop(Men): logistic hibp i.CB i.Married
+test 1.Married
+svy, subpop(Women): logistic hibp i.CB i.Married
+test 1.Married
+
+svy, subpop(Men): logistic hibp i.CB##i.Married
+svy, subpop(Women): logistic hibp i.CB##i.Married
+
+test 2.CB#1.Married 3.CB#1.Married // -> no interaction
+
+// Income -> not confounder for men but confounder for women
+svy, subpop(Men): logistic hibp i.CB eqvinc 
+test eqvinc
+svy, subpop(Women): logistic hibp i.CB eqvinc 
+test eqvinc
+
+svy, subpop(Men): logistic hibp i.CB##c.eqvinc 
+svy, subpop(Women): logistic hibp i.CB##c.eqvinc
+
+test 2.CB#c.eqvinc 3.CB#c.eqvinc // -> (probably) no interaction
+
+// Education -> confounder
+svy, subpop(Men): logistic hibp i.CB i.Edu 
+test 1.Edu
+svy, subpop(Women): logistic hibp i.CB i.Edu 
+test 1.Edu
+
+svy, subpop(Men): logistic hibp i.CB##i.Edu 
+svy, subpop(Women): logistic hibp i.CB##i.Edu
+
+test 2.CB#1.Edu 3.CB#1.Edu // no interaction
+
+// BMI -> confounder
+svy, subpop(Men): logistic hibp i.CB bmi
+test bmi
+svy, subpop(Women): logistic hibp i.CB bmi
+test bmi
+
+svy, subpop(Men): logistic hibp i.CB##c.bmi
+svy, subpop(Women): logistic hibp i.CB##c.bmi
+
+test 2.CB#c.bmival 3.CB#c.bmival // no ineraction
+
+// paid employment -> not confounder
+svy, subpop(Men): logistic hibp i.CB i.paid
+test 2.paid
+svy, subpop(Women): logistic hibp i.CB i.paid
+test 2.paid
+
+svy, subpop(Men): logistic hibp i.CB##i.paid
+svy, subpop(Women): logistic hibp i.CB##i.paid
+
+test 2.CB#2.paid 3.CB#2.paid
+
+// Smoking -> confounder
+svy, subpop(Men): logistic hibp i.CB i.cigsta3
+test 2.cigsta3 3.cigsta3
+svy, subpop(Women): logistic hibp i.CB i.cigsta3
+test 2.cigsta3 3.cigsta3
+
+svy, subpop(Men): logistic hibp i.CB##i.cigsta3
+svy, subpop(Women): logistic hibp i.CB##i.cigsta3
+
+test 2.CB#2.cigsta3 2.CB#3.cigsta3 3.CB#2.cigsta3 3.CB#3.cigsta3 // no interaction
+
+// Total energy intake -> confounder
+svy, subpop(Men): logistic hibp i.CB EnergykJ
+test EnergykJ
+svy, subpop(Women): logistic hibp i.CB EnergykJ
+test EnergykJ
+
+svy, subpop(Men): logistic hibp i.CB##c.EnergykJ
+svy, subpop(Women): logistic hibp i.CB##c.EnergykJ
+test 2.CB#c.EnergykJkJ 3.CB#c.EnergykJkJ // no interaction
+
+// ethnicity -> not confounder
+svy, subpop(Men): logistic hibp i.CB i.ethgrp2
+test 2.eth
+svy, subpop(Women): logistic hibp i.CB i.ethgrp2
+test 2.eth
+
+svy, subpop(Men): logistic hibp i.CB##i.ethgrp2
+svy, subpop(Women): logistic hibp i.CB##i.ethgrp2
+test 2.CB#2.ethgrp2 // no interaction
+
+// Alcohol -> not confounder for men but confounder for women
+svy, subpop(Men): logistic hibp i.CB Alcoholg
+test Alcoholg
+svy, subpop(Women): logistic hibp i.CB Alcoholg
+test Alcoholg
+
+svy, subpop(Men): logistic hibp i.CB##c.Alcoholg
+svy, subpop(Women): logistic hibp i.CB##c.Alcoholg
+test 2.CB#c.Alcoholg 3.CB#c.Alcoholg // no interaction
+
+// logMVP -> not confounder 
+svy, subpop(Men): logistic hibp i.CB logMVP
+test logMVP
+svy, subpop(Women): logistic hibp i.CB logMVP
+test logMVP
+
+svy, subpop(Men): logistic hibp i.CB##c.logMVP
+svy, subpop(Women): logistic hibp i.CB##c.logMVP
+test 2.CB#c.logMVP 3.CB#c.logMVP // no interaction
+
+//  Preliminary model includes all possible confounders in Men
+
+gen age2 = age^2
+
+svy, subpop(Men): logistic hibp i.CB age i.Married i.Edu bmi i.cig EnergykJ 
+linktest
+svy, subpop(Men): logistic hibp i.CB age i.Married i.Edu wst i.cig EnergykJ 
+linktest
+svy, subpop(if Men & DM != 1): logistic hibp i.CB age i.Married i.Edu bmi i.cig EnergykJ 
+linktest
+svy, subpop(if Men & DM != 1): logistic hibp i.CB age i.Married i.Edu wst i.cig EnergykJ 
+linktest
+
+//  Preliminary model includes all possible confounders in Women
+
+svy, subpop(Women): logistic hibp i.CB age i.Married eqvinc i.Edu bmi i.cig EnergykJ Alcoholg 
+linktest
+svy, subpop(Women): logistic hibp i.CB age i.Married eqvinc i.Edu wst i.cig EnergykJ Alcoholg 
+linktest
+
+svy, subpop(if Women & DM != 1): logistic hibp i.CB age i.Married eqvinc i.Edu bmi i.cig EnergykJ Alcoholg
+linktest
+
+svy, subpop(if Women & DM != 1): logistic hibp i.CB age i.Married eqvinc i.Edu wst i.cig EnergykJ Alcoholg
+linktest
+```

### 2018-08-17 paper/Appendices/Appendix0_10.tex
appendix C figlevel 1 CW4

@@
 \CommentTok{# Change the data path accordingly ----------------------------------------}
-\KeywordTok{setwd}\NormalTok{(}\StringTok{"/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }\CommentTok{# on Ubuntu}
+
+\KeywordTok{setwd}\NormalTok{(}\StringTok{".../UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }
+\KeywordTok{setwd}\NormalTok{(}\StringTok{"~/Downloads/UKDA-6533-stata11_se/stata11_se/"}\NormalTok{)}
+
 \KeywordTok{library}\NormalTok{(epiDisplay)}
@@
 \CommentTok{# Read the data into memory -----------------------------------------------}
+
 \KeywordTok{library}\NormalTok{(haven)}
@@
 \NormalTok{data78 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr7-8a_foodleveldietarydata.dta"}\NormalTok{)}
+
 \KeywordTok{names}\NormalTok{(data)}
@@
 \KeywordTok{names}\NormalTok{(data78)}
-\KeywordTok{names}\NormalTok{(data)[}\KeywordTok{names}\NormalTok{(data) }\OperatorTok{==}\StringTok{ "seriali"}\NormalTok{] <-}\StringTok{ "id"}
-\KeywordTok{names}\NormalTok{(data56)[}\KeywordTok{names}\NormalTok{(data56) }\OperatorTok{==}\StringTok{ "seriali"}\NormalTok{] <-}\StringTok{ "id"}
-\KeywordTok{names}\NormalTok{(data78)[}\KeywordTok{names}\NormalTok{(data78) }\OperatorTok{==}\StringTok{ "seriali"}\NormalTok{] <-}\StringTok{ "id"}
-
-\CommentTok{# Extract the data we needed ----------------------------------------------}
-\NormalTok{df14d <-}\StringTok{ }\NormalTok{data[, }\KeywordTok{c}\NormalTok{(}\DecValTok{113}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{, }\DecValTok{3}\NormalTok{, }\DecValTok{5}\NormalTok{, }\DecValTok{6}\NormalTok{, }\DecValTok{7}\NormalTok{, }\DecValTok{8}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{21}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{55}\NormalTok{, }\DecValTok{57}\NormalTok{, }\DecValTok{58}\NormalTok{, }
-    \DecValTok{59}\NormalTok{, }\DecValTok{60}\NormalTok{, }\DecValTok{61}\NormalTok{, }\DecValTok{62}\NormalTok{, }\DecValTok{63}\NormalTok{, }\DecValTok{64}\NormalTok{)]}
+\KeywordTok{names}\NormalTok{(data)[}\KeywordTok{names}\NormalTok{(data)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
+\KeywordTok{names}\NormalTok{(data56)[}\KeywordTok{names}\NormalTok{(data56)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
+\KeywordTok{names}\NormalTok{(data78)[}\KeywordTok{names}\NormalTok{(data78)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
+
+\CommentTok{# Extract the variables needed -------------------------------------------}
+
+\NormalTok{df14d <-}\StringTok{ }\NormalTok{data[,}\KeywordTok{c}\NormalTok{(}\DecValTok{113}\NormalTok{,}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{5}\NormalTok{,}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{,}\DecValTok{8}\NormalTok{,}\DecValTok{9}\NormalTok{,}\DecValTok{21}\NormalTok{, }\DecValTok{22}\NormalTok{, }\DecValTok{23}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{53}\NormalTok{, }\DecValTok{55}\NormalTok{,}
+                 \DecValTok{57}\NormalTok{,}\DecValTok{58}\NormalTok{,}\DecValTok{59}\NormalTok{,}\DecValTok{60}\NormalTok{,}\DecValTok{61}\NormalTok{,}\DecValTok{62}\NormalTok{,}\DecValTok{63}\NormalTok{,}\DecValTok{64}\NormalTok{,}\DecValTok{65}\NormalTok{)]}
 \NormalTok{var <-}\StringTok{ }\KeywordTok{names}\NormalTok{(df14d)}
-\NormalTok{df56d <-}\StringTok{ }\NormalTok{data56 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(var)}
-\NormalTok{df78d <-}\StringTok{ }\NormalTok{data78 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(var)}
+\NormalTok{df56d <-}\StringTok{ }\NormalTok{data56 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
+\NormalTok{df78d <-}\StringTok{ }\NormalTok{data78 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
 \NormalTok{dfs1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(df14d, df56d, df78d)}
-\NormalTok{dfs2 <-}\StringTok{ }\NormalTok{dfs1[dfs1}\OperatorTok{$}\NormalTok{Age }\OperatorTok{>=}\StringTok{ }\DecValTok{19}\NormalTok{, ]}
-\KeywordTok{rm}\NormalTok{(data, data56, data78)}
+
+\NormalTok{dfs2 <-}\StringTok{ }\NormalTok{dfs1[dfs1}\OperatorTok{$}\NormalTok{Age}\OperatorTok{>=}\DecValTok{19}\NormalTok{,] }\CommentTok{# keep participants who aged 19 or older}
+\KeywordTok{rm}\NormalTok{(data, data56, data78) }\CommentTok{# remove the unneeded big dataset}
+
 \NormalTok{dfs2}
@@
 \NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_chr <-}\StringTok{ }\KeywordTok{as.character}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime)}
-\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_hm <-}\StringTok{ }\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_chr, }\StringTok{" "}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }
+\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_hm <-}\StringTok{ }\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_chr,}\StringTok{" "}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }
                                                               \OtherTok{TRUE}\NormalTok{)]}
-\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm, }\StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{TRUE}\NormalTok{, }
-    \OtherTok{FALSE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
-\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm, }\StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }
-    \OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
-\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN0 <-}\StringTok{ }\NormalTok{(}\DecValTok{60} \OperatorTok{*}\StringTok{ }\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN) }\OperatorTok{+}\StringTok{ }\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN}
-\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs2[}\KeywordTok{order}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{id, dfs2}\OperatorTok{$}\NormalTok{DayNo, dfs2}\OperatorTok{$}\NormalTok{MealMinN0), ]}
+\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm,}
+                                             \StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
+\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm,}
+                                            \StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }\OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
+
+\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN0 <-}\StringTok{ }\NormalTok{(}\DecValTok{60}\OperatorTok{*}\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN)}\OperatorTok{+}\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN}
+
+\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs2[}\KeywordTok{order}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{id,dfs2}\OperatorTok{$}\NormalTok{DayNo,dfs2}\OperatorTok{$}\NormalTok{MealMinN0),]}
+
 \KeywordTok{length}\NormalTok{(}\KeywordTok{unique}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id)) ## number of participants = 6155}
 
-\CommentTok{# Create a subset data with only the first observation of each}
-\CommentTok{# participant --------}
+\CommentTok{# Create a subset data with only the first observation of each participant --------}
+
 \NormalTok{NDNS <-}\StringTok{ }\NormalTok{dfs3[}\OperatorTok{!}\KeywordTok{duplicated}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id), ]}
 \KeywordTok{with}\NormalTok{(NDNS, }\KeywordTok{tab1}\NormalTok{(SurveyYear, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{decimal =} \DecValTok{2}\NormalTok{))}
-
-\CommentTok{# #SurveyYear :}
-            \CommentTok{# Frequency Percent Cum. percent}
-\CommentTok{# NDNS Year 1       801   13.01        13.01}
-\CommentTok{# NDNS Year 2       812   13.19        26.21}
-\CommentTok{# NDNS Year 3       782   12.71        38.91}
-\CommentTok{# NDNS Year 4      1055   17.14        56.05}
-\CommentTok{# NDNS Year 5       625   10.15        66.21}
-\CommentTok{# NDNS Year 6       663   10.77        76.98}
-\CommentTok{# NDNS Year 7       703   11.42        88.40}
-\CommentTok{# NDNS Year 8       714   11.60       100.00}
-  \CommentTok{# Total          6155  100.00       100.00}
-
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+# #SurveyYear : 
+#             Frequency Percent Cum. percent
+# NDNS Year 1       801   13.01        13.01
+# NDNS Year 2       812   13.19        26.21
+# NDNS Year 3       782   12.71        38.91
+# NDNS Year 4      1055   17.14        56.05
+# NDNS Year 5       625   10.15        66.21
+# NDNS Year 6       663   10.77        76.98
+# NDNS Year 7       703   11.42        88.40
+# NDNS Year 8       714   11.60       100.00
+#   Total          6155  100.00       100.00
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# how many men and women --------------------------------------------------}
+
+\KeywordTok{with}\NormalTok{(NDNS, }\KeywordTok{tab1}\NormalTok{(Sex, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{decimal =} \DecValTok{2}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+# Sex : 
+#          Frequency Percent Cum. percent
+# 1            2537   41.22        41.22 Men
+# 2            3618   58.78       100.00 Women
+#   Total      6155  100.00       100.00
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
 \CommentTok{# create a variable combine id and day No ---------------------------------}
-\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs3 }\OperatorTok{%>%}
-\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{id_dy =} \KeywordTok{paste}\NormalTok{(id, DayNo, }\DataTypeTok{sep =} \StringTok{"D"}\NormalTok{))}
-
-\CommentTok{# For each subject, the total energy/carbohydrate intake for each eating }
-\CommentTok{# time can be calculated --------}
-\NormalTok{old <-}\StringTok{ }\KeywordTok{Sys.time}\NormalTok{()}
+
+\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs3 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{id_dy =} \KeywordTok{paste}\NormalTok{(id, DayNo, }\DataTypeTok{sep =} \StringTok{"D"}\NormalTok{))}
+
+\CommentTok{# For each subject, the total energy/carbohydrate intake for each }
+\CommentTok{# eating time can be calculated --------}
+
+\NormalTok{old<-}\KeywordTok{Sys.time}\NormalTok{()}
 \NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(dfs3, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
 \NormalTok{                        DiaryDaysCompleted, MealHourN, DayofWeek),  }
-\NormalTok{                summarise, }
-                \DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(EnergykJ), }
+\NormalTok{                summarise, }\DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(EnergykJ), }
                 \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Carbohydrateg), }
                 \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Totalsugarsg), }
-                \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Starchg))}
-\NormalTok{new <-}\StringTok{ }\KeywordTok{Sys.time}\NormalTok{() }\OperatorTok{-}\StringTok{ }\NormalTok{old}
+                \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Starchg), }
+                \DataTypeTok{Tot_Fibre =} \KeywordTok{sum}\NormalTok{(Englystfibreg),}
+                \DataTypeTok{Tot_Fat   =} \KeywordTok{sum}\NormalTok{(Fatg), }
+                \DataTypeTok{Tot_Prot  =} \KeywordTok{sum}\NormalTok{(Proteing), }
+                \DataTypeTok{Tot_Alc   =} \KeywordTok{sum}\NormalTok{(Alcoholg), }
+                \DataTypeTok{Tot_NMES  =} \KeywordTok{sum}\NormalTok{(Nonmilkextrinsicsugarsg))}
+\NormalTok{new<-}\KeywordTok{Sys.time}\NormalTok{()}\OperatorTok{-}\NormalTok{old}
 \KeywordTok{print}\NormalTok{(new)}
-\CommentTok{# Time difference of 3.876385 mins}
-
-\KeywordTok{rm}\NormalTok{(df14d, df56d, df78d, dfs2)}
+\CommentTok{# Time difference of 6.429822 min}
+
+\CommentTok{# reset the time intervals into time slots --------------------------------}
+
+\NormalTok{### Breakfast:       6am to 9am}
+\NormalTok{### morning snack:   9am to 12noon}
+\NormalTok{### lunch:           12noon to 2pm}
+\NormalTok{### afternoon snack: 2pm to 5pm}
+\NormalTok{### dinner:          5pm to 8pm}
+\NormalTok{### night snack:     8pm to 10pm}
+\NormalTok{### midnight:        10pm to 6am}
+
+\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{TimeSlot =} \KeywordTok{cut}\NormalTok{(MealHourN, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{12}\NormalTok{, }\DecValTok{14}\NormalTok{, }\DecValTok{17}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{22}\NormalTok{), }
+                        \DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
+
+\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot), }\StringTok{"[22, 6)"}\NormalTok{)}
+
+\NormalTok{Energy}\OperatorTok{$}\NormalTok{TimeSlot[}\KeywordTok{is.na}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)] <-}\StringTok{ "[22, 6)"}
+
+\KeywordTok{tab1}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)}
+
+\CommentTok{# For each subject, the total energy/carbohydrate intake for each }
+\CommentTok{# time slot can be calculated --------}
+\NormalTok{old<-}\KeywordTok{Sys.time}\NormalTok{()}
+\NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(Energy, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
+\NormalTok{                          DiaryDaysCompleted, TimeSlot, DayofWeek),  }
+\NormalTok{                summarise, }
+                \DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(Tot_Energ), }
+                \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Tot_Carb), }
+                \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Tot_Sugar),}
+                \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Tot_Starch), }
+                \DataTypeTok{Tot_Fibre =} \KeywordTok{sum}\NormalTok{(Tot_Fibre), }
+                \DataTypeTok{Tot_Fat   =} \KeywordTok{sum}\NormalTok{(Tot_Fat), }
+                \DataTypeTok{Tot_Prot  =} \KeywordTok{sum}\NormalTok{(Tot_Prot), }
+                \DataTypeTok{Tot_Alc   =} \KeywordTok{sum}\NormalTok{(Tot_Alc), }
+                \DataTypeTok{Tot_NMES  =} \KeywordTok{sum}\NormalTok{(Tot_NMES))}
+\NormalTok{new<-}\KeywordTok{Sys.time}\NormalTok{()}\OperatorTok{-}\NormalTok{old}
+\KeywordTok{print}\NormalTok{(new)}
+\CommentTok{# Time difference of 3.74195 mins }
 
 \CommentTok{# Calculate the energy from total carbohydrates ---------------------------}
+
 \NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{KJcarbo =}\NormalTok{ Tot_Carb }\OperatorTok{*}\StringTok{ }\DecValTok{16}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{KJcarbo =}\NormalTok{ Tot_Carb}\OperatorTok{*}\DecValTok{16}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CarKJpercentage =}\NormalTok{ KJcarbo}\OperatorTok{/}\NormalTok{Tot_Energ) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.26}\NormalTok{, }\FloatTok{0.75}\NormalTok{, }\DecValTok{2}\NormalTok{), }
-        \DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo2 =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }
-    \FloatTok{0.26}\NormalTok{, }\DecValTok{2}\NormalTok{), }\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
-\NormalTok{Energy0 <-}\StringTok{ }\NormalTok{Energy[}\OperatorTok{!}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{Tot_Energ }\OperatorTok{==}\StringTok{ }\DecValTok{0}\NormalTok{), ]  }
-          \CommentTok{# some food consumption does not contain any carbohydrates}
-\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Low_carb"}\NormalTok{, }\StringTok{"Med_carb"}\NormalTok{, }
-    \StringTok{"High_carb"}\NormalTok{))}
-\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo2 <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo2, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Low_carb"}\NormalTok{, }\StringTok{"Med_or_high_carb"}\NormalTok{))}
-
-\CommentTok{# Generate data sets for each day ----------------------------------------------------------}
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.50}\NormalTok{, }\DecValTok{2}\NormalTok{), }\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
+
+\NormalTok{Energy0 <-}\StringTok{ }\NormalTok{Energy[}\OperatorTok{!}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{Tot_Energ }\OperatorTok{==}\StringTok{ }\DecValTok{0}\NormalTok{), ] }\CommentTok{# discard those eating occassion }
+\CommentTok{# with 0 energy intake }
+\KeywordTok{write.csv}\NormalTok{(Energy0, }\DataTypeTok{file =} \StringTok{"Energy_slots.csv"}\NormalTok{) }\CommentTok{# for later analysis}
+
+\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"< 50%"}\NormalTok{, }\StringTok{">= 50%"}\NormalTok{))}
+
+\NormalTok{vecid<-}\KeywordTok{unique}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{id)}
+
+\CommentTok{# Filter the data by observation day--------------------------------------------}
+
 \NormalTok{dta_day1 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
 \StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
-    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
+           \StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
-    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
-        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
+                            \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
+                                       \StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
+                                       \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
 
@@
 \StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{2}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
-    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
+           \StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
-    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
-        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
+                            \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
+                                       \StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
+                                       \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
 
@@
 \StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
-    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
+           \StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
-    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
-        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
+                            \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
+                                       \StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
+                                       \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
 
@@
 \StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
-    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
+           \StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
-    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
-        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
-\NormalTok{vecid1 <-}\StringTok{ }\KeywordTok{unique}\NormalTok{(dta_day1}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
-\NormalTok{vecid2 <-}\StringTok{ }\KeywordTok{unique}\NormalTok{(dta_day2}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
-\NormalTok{vecid3 <-}\StringTok{ }\KeywordTok{unique}\NormalTok{(dta_day3}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6151}
-\NormalTok{vecid4 <-}\StringTok{ }\KeywordTok{unique}\NormalTok{(dta_day4}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6026}
+                            \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
+                                       \StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
+                                       \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
+
+\NormalTok{vecid1<-}\KeywordTok{unique}\NormalTok{(dta_day1}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
+\NormalTok{vecid2<-}\KeywordTok{unique}\NormalTok{(dta_day2}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
+\NormalTok{vecid3<-}\KeywordTok{unique}\NormalTok{(dta_day3}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6151}
+\NormalTok{vecid4<-}\KeywordTok{unique}\NormalTok{(dta_day4}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6026}
 
 \NormalTok{Noday1 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid1) }\CommentTok{# two subjects did not have day 1 data}
-\NormalTok{Noday2 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid2)  }\CommentTok{# two subjects did not have day 2 data}
-\NormalTok{Noday3 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid3)  }\CommentTok{# four subjects did not have day 3 data}
+
+\NormalTok{Noday2 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid2) }\CommentTok{# two subjects did not have day 2 data }
+
+\NormalTok{Noday3 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid3) }\CommentTok{# four subjects did not have day 3 data }
+
 \NormalTok{Noday4 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid4) }\CommentTok{# 129 subjects did not have day 4 data}
 
-\CommentTok{# Transform the data shape from long to wide ---------------------------------}
-\NormalTok{dta_d1_wide <-}\StringTok{ }\NormalTok{dta_day1[, }\OperatorTok{-}\DecValTok{7}\NormalTok{] }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ MealHourN, }\DataTypeTok{value =}\NormalTok{ Carbo)}
-\KeywordTok{names}\NormalTok{(dta_d1_wide)[}\DecValTok{5}\OperatorTok{:}\DecValTok{28}\NormalTok{] <-}\StringTok{ }\KeywordTok{paste}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"H"}\NormalTok{, }\DecValTok{24}\NormalTok{), }\DecValTok{0}\OperatorTok{:}\DecValTok{23}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{)}
-
-\NormalTok{dta_d2_wide <-}\StringTok{ }\NormalTok{dta_day2[, }\OperatorTok{-}\DecValTok{7}\NormalTok{] }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ MealHourN, }\DataTypeTok{value =}\NormalTok{ Carbo)}
-\KeywordTok{names}\NormalTok{(dta_d2_wide)[}\DecValTok{5}\OperatorTok{:}\DecValTok{28}\NormalTok{] <-}\StringTok{ }\KeywordTok{paste}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"H"}\NormalTok{, }\DecValTok{24}\NormalTok{), }\DecValTok{0}\OperatorTok{:}\DecValTok{23}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{)}
-
-\NormalTok{dta_d3_wide <-}\StringTok{ }\NormalTok{dta_day3[, }\OperatorTok{-}\DecValTok{7}\NormalTok{] }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ MealHourN, }\DataTypeTok{value =}\NormalTok{ Carbo)}
-\KeywordTok{names}\NormalTok{(dta_d3_wide)[}\DecValTok{5}\OperatorTok{:}\DecValTok{28}\NormalTok{] <-}\StringTok{ }\KeywordTok{paste}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"H"}\NormalTok{, }\DecValTok{24}\NormalTok{), }\DecValTok{0}\OperatorTok{:}\DecValTok{23}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{)}
-
-\NormalTok{dta_d4_wide <-}\StringTok{ }\NormalTok{dta_day4[, }\OperatorTok{-}\DecValTok{7}\NormalTok{] }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ MealHourN, }\DataTypeTok{value =}\NormalTok{ Carbo)}
-\KeywordTok{names}\NormalTok{(dta_d4_wide)[}\DecValTok{5}\OperatorTok{:}\DecValTok{28}\NormalTok{] <-}\StringTok{ }\KeywordTok{paste}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"H"}\NormalTok{, }\DecValTok{24}\NormalTok{), }\DecValTok{0}\OperatorTok{:}\DecValTok{23}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{)}
+\CommentTok{# Long to wide data -------------------------------------------------------}
+
+\NormalTok{dta_d1_wide <-}\StringTok{ }\NormalTok{dta_day1 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+         \DataTypeTok{value =}\NormalTok{ Carbo)}
+
+\KeywordTok{head}\NormalTok{(dta_d1_wide)}
+\KeywordTok{names}\NormalTok{(dta_d1_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
+                              \StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
+\KeywordTok{names}\NormalTok{(dta_d1_wide)}
+
+\NormalTok{dta_d2_wide <-}\StringTok{ }\NormalTok{dta_day2 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+         \DataTypeTok{value =}\NormalTok{ Carbo)}
+
+\KeywordTok{head}\NormalTok{(dta_d2_wide)}
+\KeywordTok{names}\NormalTok{(dta_d2_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
+                              \StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
+\KeywordTok{names}\NormalTok{(dta_d2_wide)}
+
+\NormalTok{dta_d3_wide <-}\StringTok{ }\NormalTok{dta_day3 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+         \DataTypeTok{value =}\NormalTok{ Carbo)}
+
+\KeywordTok{head}\NormalTok{(dta_d3_wide)}
+\KeywordTok{names}\NormalTok{(dta_d3_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
+                              \StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
+\KeywordTok{names}\NormalTok{(dta_d3_wide)}
+
+\NormalTok{dta_d4_wide <-}\StringTok{ }\NormalTok{dta_day4 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+         \DataTypeTok{value =}\NormalTok{ Carbo)}
+
+\KeywordTok{head}\NormalTok{(dta_d4_wide)}
+\KeywordTok{names}\NormalTok{(dta_d4_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
+                              \StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
+\KeywordTok{names}\NormalTok{(dta_d4_wide)}
 
 \CommentTok{# recode NA to not eating -------------------------------------------------}
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{5}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d1_wide)) }
-  \ControlFlowTok{if}\NormalTok{ (}\KeywordTok{is.factor}\NormalTok{(dta_d1_wide[, i])) }\KeywordTok{levels}\NormalTok{(dta_d1_wide[, }
-\NormalTok{    i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(dta_d1_wide[, i]), }\StringTok{"Not_eating"}\NormalTok{)}
-
-\NormalTok{dta_d1_wide[}\KeywordTok{is.na}\NormalTok{(dta_d1_wide)] <-}\StringTok{ "Not_eating"}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{5}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d2_wide)) }
-  \ControlFlowTok{if}\NormalTok{ (}\KeywordTok{is.factor}\NormalTok{(dta_d2_wide[, i])) }\KeywordTok{levels}\NormalTok{(dta_d2_wide[, }
-\NormalTok{    i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(dta_d2_wide[, i]), }\StringTok{"Not_eating"}\NormalTok{)}
-
-\NormalTok{dta_d2_wide[}\KeywordTok{is.na}\NormalTok{(dta_d2_wide)] <-}\StringTok{ "Not_eating"}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{5}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d3_wide)) }
-  \ControlFlowTok{if}\NormalTok{ (}\KeywordTok{is.factor}\NormalTok{(dta_d3_wide[, i])) }\KeywordTok{levels}\NormalTok{(dta_d3_wide[, }
-\NormalTok{    i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(dta_d3_wide[, i]), }\StringTok{"Not_eating"}\NormalTok{)}
-
-\NormalTok{dta_d3_wide[}\KeywordTok{is.na}\NormalTok{(dta_d3_wide)] <-}\StringTok{ "Not_eating"}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{5}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d4_wide)) }
-  \ControlFlowTok{if}\NormalTok{ (}\KeywordTok{is.factor}\NormalTok{(dta_d4_wide[, i])) }\KeywordTok{levels}\NormalTok{(dta_d4_wide[, }
-\NormalTok{    i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(dta_d4_wide[, i]), }\StringTok{"Not_eating"}\NormalTok{)}
-
-\NormalTok{dta_d4_wide[}\KeywordTok{is.na}\NormalTok{(dta_d4_wide)] <-}\StringTok{ "Not_eating"}
+
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{6}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d1_wide)) }
+  \ControlFlowTok{if}\NormalTok{(}\KeywordTok{is.factor}\NormalTok{(dta_d1_wide[,i])) }
+    \KeywordTok{levels}\NormalTok{(dta_d1_wide[,i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2"}\NormalTok{, }\StringTok{"0"}\NormalTok{)}
+
+\NormalTok{dta_d1_wide[}\KeywordTok{is.na}\NormalTok{(dta_d1_wide)] <-}\StringTok{ "0"}
+
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{6}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d2_wide)) }
+  \ControlFlowTok{if}\NormalTok{(}\KeywordTok{is.factor}\NormalTok{(dta_d2_wide[,i])) }
+    \KeywordTok{levels}\NormalTok{(dta_d2_wide[,i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2"}\NormalTok{,  }\StringTok{"0"}\NormalTok{)}
+
+\NormalTok{dta_d2_wide[}\KeywordTok{is.na}\NormalTok{(dta_d2_wide)] <-}\StringTok{ "0"}
+
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{6}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d3_wide)) }
+  \ControlFlowTok{if}\NormalTok{(}\KeywordTok{is.factor}\NormalTok{(dta_d3_wide[,i])) }
+    \KeywordTok{levels}\NormalTok{(dta_d3_wide[,i]) <-}\StringTok{  }\KeywordTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2"}\NormalTok{, }\StringTok{"0"}\NormalTok{)}
+
+\NormalTok{dta_d3_wide[}\KeywordTok{is.na}\NormalTok{(dta_d3_wide)] <-}\StringTok{ "0"}
+
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{6}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d4_wide)) }
+  \ControlFlowTok{if}\NormalTok{(}\KeywordTok{is.factor}\NormalTok{(dta_d4_wide[,i])) }
+    \KeywordTok{levels}\NormalTok{(dta_d4_wide[,i]) <-}\StringTok{  }\KeywordTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2"}\NormalTok{, }\StringTok{"0"}\NormalTok{)}
+
+\NormalTok{dta_d4_wide[}\KeywordTok{is.na}\NormalTok{(dta_d4_wide)] <-}\StringTok{ "0"}
+
+\NormalTok{dta_all <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(dta_d1_wide, dta_d2_wide, dta_d3_wide, dta_d4_wide)}
+
+\NormalTok{dta_all <-}\StringTok{ }\NormalTok{dta_all[}\KeywordTok{order}\NormalTok{(dta_all}\OperatorTok{$}\NormalTok{id,dta_all}\OperatorTok{$}\NormalTok{id_dy),]}
+
+\CommentTok{# Export the data for Mplus -------------------------------------------------}
+
+\KeywordTok{write_csv}\NormalTok{(dta_all, }\DataTypeTok{path =} \StringTok{"dta_NDNS_Tslots.csv"}\NormalTok{)}
+\KeywordTok{write_delim}\NormalTok{(dta_all, }\StringTok{"dta_NDNS_Tslots.dat"}\NormalTok{, }\DataTypeTok{na =} \StringTok{"."}\NormalTok{, }\DataTypeTok{delim =} \StringTok{" "}\NormalTok{)}
 \end{Highlighting}
@@
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{library}\NormalTok{(plyr)}
+\KeywordTok{library}\NormalTok{(epiDisplay)}
+\KeywordTok{library}\NormalTok{(tidyverse)}
+\KeywordTok{library}\NormalTok{(dplyr)}
+\KeywordTok{library}\NormalTok{(readr)}
+\KeywordTok{library}\NormalTok{(haven)}
+\KeywordTok{library}\NormalTok{(naniar)}
+
+\CommentTok{# read the individual level data sets ----------------------------------------}
+
+\NormalTok{blood78 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr7-8a_indiv.dta"}\NormalTok{)}
+\NormalTok{blood56 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr5-6a_indiv.dta"}\NormalTok{)}
+\NormalTok{blood14 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr1-4a_indiv_uk.dta"}\NormalTok{)}
+
+\NormalTok{food14 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr1-4a_personleveldietarydata_uk.dta"}\NormalTok{)}
+
+\NormalTok{food56 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr5-6a_personleveldietarydata.dta"}\NormalTok{)}
+
+\NormalTok{food78 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr7-8a_personleveldietarydata.dta"}\NormalTok{)}
+
+\KeywordTok{names}\NormalTok{(blood78)[}\KeywordTok{names}\NormalTok{(blood78)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "ID"}
+\KeywordTok{names}\NormalTok{(blood56)[}\KeywordTok{names}\NormalTok{(blood56)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "ID"}
+\KeywordTok{names}\NormalTok{(blood14)[}\KeywordTok{names}\NormalTok{(blood14)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "ID"}
+\KeywordTok{names}\NormalTok{(food78)[}\KeywordTok{names}\NormalTok{(food78)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "ID"}
+\KeywordTok{names}\NormalTok{(food56)[}\KeywordTok{names}\NormalTok{(food56)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "ID"}
+\KeywordTok{names}\NormalTok{(food14)[}\KeywordTok{names}\NormalTok{(food14)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "ID"}
+
+\CommentTok{# Loading the data from Mplus output}
+\NormalTok{CW3CB3 <-}\StringTok{ }\KeywordTok{read_table2}\NormalTok{(}\StringTok{"../NDNSslot_CW3CB3.txt"}\NormalTok{,  }\CommentTok{# change the path accordingly}
+                      \DataTypeTok{col_names =} \OtherTok{FALSE}\NormalTok{)}
+
+\KeywordTok{names}\NormalTok{(CW3CB3) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"Breakfast"}\NormalTok{, }\StringTok{"Morning.snack"}\NormalTok{, }\StringTok{"Lunch"}\NormalTok{,}
+                   \StringTok{"Afternoon.snack"}\NormalTok{, }\StringTok{"Dinner"}\NormalTok{, }\StringTok{"Before.bedtime.snack"}\NormalTok{,}
+                   \StringTok{"Midnight.food"}\NormalTok{, }\StringTok{"ID_DAY"}\NormalTok{, }\StringTok{"AGE"}\NormalTok{, }\StringTok{"SEX"}\NormalTok{, }\StringTok{"CPROB1"}\NormalTok{,}
+                   \StringTok{"CPROB2"}\NormalTok{, }\StringTok{"CPROB3"}\NormalTok{, }\StringTok{"CPROB4"}\NormalTok{, }\StringTok{"CPROB5"}\NormalTok{, }\StringTok{"CPROB6"}\NormalTok{, }
+                   \StringTok{"CPROB7"}\NormalTok{, }\StringTok{"CPROB8"}\NormalTok{, }\StringTok{"CPROB9"}\NormalTok{, }
+                   \StringTok{"CB"}\NormalTok{, }\StringTok{"CW"}\NormalTok{, }\StringTok{"MLCJOINT"}\NormalTok{, }\StringTok{"ID"}\NormalTok{)}
+
+\NormalTok{CW3idday <-}\StringTok{ }\NormalTok{CW3CB3 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, ID_DAY, CW, CB, MLCJOINT, AGE, SEX)}
+
+\NormalTok{Energy_slots <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"../Energy_slots.csv"}\NormalTok{) }\CommentTok{# change the path accordingly}
+\NormalTok{Energy_slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{ID =}\NormalTok{ id)}
+
+\CommentTok{# Recode day level classification to keep consistency}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{CW_new <-}\StringTok{ }\DecValTok{0}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{CW_new[CW3idday}\OperatorTok{$}\NormalTok{CW }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{] <-}\StringTok{ }\DecValTok{3}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{CW_new[CW3idday}\OperatorTok{$}\NormalTok{CW }\OperatorTok{==}\StringTok{ }\DecValTok{2}\NormalTok{] <-}\StringTok{ }\DecValTok{1}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{CW_new[CW3idday}\OperatorTok{$}\NormalTok{CW }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{] <-}\StringTok{ }\DecValTok{2}
+
+\NormalTok{Energy_slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(CW3idday, }\DataTypeTok{by =} \KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{))}
+
+\NormalTok{Energy_slots}\OperatorTok{$}\NormalTok{TimeSlot <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy_slots}\OperatorTok{$}\NormalTok{TimeSlot, }
+                                \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"[6,9)"}\NormalTok{, }\StringTok{"[9,12)"}\NormalTok{, }
+                                           \StringTok{"[12,14)"}\NormalTok{, }\StringTok{"[14,17)"}\NormalTok{,}
+                                           \StringTok{"[17,20)"}\NormalTok{, }\StringTok{"[20,22)"}\NormalTok{, }\StringTok{"[22, 6)"}\NormalTok{))}
+
+\NormalTok{FoodbyCB_7slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{group_by}\NormalTok{(ID, TimeSlot) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{sumEnergy =} \KeywordTok{sum}\NormalTok{(Tot_Energ),}
+            \DataTypeTok{sumCarb =} \KeywordTok{sum}\NormalTok{(Tot_Carb), }
+            \DataTypeTok{sumSugar =} \KeywordTok{sum}\NormalTok{(Tot_Sugar), }
+            \DataTypeTok{sumStarch =} \KeywordTok{sum}\NormalTok{(Tot_Starch),}
+            \DataTypeTok{sumFibre =} \KeywordTok{sum}\NormalTok{(Tot_Fibre), }
+            \DataTypeTok{sumNMES =} \KeywordTok{sum}\NormalTok{(Tot_NMES),}
+            \DataTypeTok{sumFat =} \KeywordTok{sum}\NormalTok{(Tot_Fat),}
+            \DataTypeTok{sumProt =} \KeywordTok{sum}\NormalTok{(Tot_Prot), }
+            \DataTypeTok{sumAlc =} \KeywordTok{sum}\NormalTok{(Tot_Alc))}
+
+\CommentTok{# Calculate the sum of each nutrients for each time slots}
+\NormalTok{Carbsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumCarb) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+         \DataTypeTok{value =}\NormalTok{ sumCarb)}
+
+\NormalTok{Carbsum[}\KeywordTok{is.na}\NormalTok{(Carbsum)] <-}\StringTok{ }\DecValTok{0}
+
+\KeywordTok{names}\NormalTok{(Carbsum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Carb6_9"}\NormalTok{, }\StringTok{"Carb9_12"}\NormalTok{, }\StringTok{"Carb12_14"}\NormalTok{, }\StringTok{"Carb14_17"}\NormalTok{,}
+                     \StringTok{"Carb17_20"}\NormalTok{, }\StringTok{"Carb20_22"}\NormalTok{, }\StringTok{"Carb22_6"}\NormalTok{)}
+
+\NormalTok{Energysum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumEnergy) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+         \DataTypeTok{value =}\NormalTok{ sumEnergy)}
+\NormalTok{Energysum[}\KeywordTok{is.na}\NormalTok{(Energysum)] <-}\StringTok{ }\DecValTok{0}
+
+\KeywordTok{names}\NormalTok{(Energysum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Energy6_9"}\NormalTok{, }\StringTok{"Energy9_12"}\NormalTok{, }\StringTok{"Energy12_14"}\NormalTok{, }\StringTok{"Energy14_17"}\NormalTok{,}
+                     \StringTok{"Energy17_20"}\NormalTok{, }\StringTok{"Energy20_22"}\NormalTok{, }\StringTok{"Energy22_6"}\NormalTok{)}
+
+\NormalTok{Starchsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumStarch) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+         \DataTypeTok{value =}\NormalTok{ sumStarch)}
+\NormalTok{Starchsum[}\KeywordTok{is.na}\NormalTok{(Starchsum)] <-}\StringTok{ }\DecValTok{0}
+
+\KeywordTok{names}\NormalTok{(Starchsum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Starch6_9"}\NormalTok{, }\StringTok{"Starch9_12"}\NormalTok{, }\StringTok{"Starch12_14"}\NormalTok{, }\StringTok{"Starch14_17"}\NormalTok{,}
+                       \StringTok{"Starch17_20"}\NormalTok{, }\StringTok{"Starch20_22"}\NormalTok{, }\StringTok{"Starch22_6"}\NormalTok{)}
+
+\NormalTok{Sugarsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumSugar) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+         \DataTypeTok{value =}\NormalTok{ sumSugar)}
+\NormalTok{Sugarsum[}\KeywordTok{is.na}\NormalTok{(Sugarsum)] <-}\StringTok{ }\DecValTok{0}
+
+\KeywordTok{names}\NormalTok{(Sugarsum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Sugar6_9"}\NormalTok{, }\StringTok{"Sugar9_12"}\NormalTok{, }\StringTok{"Sugar12_14"}\NormalTok{, }\StringTok{"Sugar14_17"}\NormalTok{,}
+                      \StringTok{"Sugar17_20"}\NormalTok{, }\StringTok{"Sugar20_22"}\NormalTok{, }\StringTok{"Sugar22_6"}\NormalTok{)}
+
+\NormalTok{Fibresum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumFibre) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+         \DataTypeTok{value =}\NormalTok{ sumFibre)}
+\NormalTok{Fibresum[}\KeywordTok{is.na}\NormalTok{(Fibresum)] <-}\StringTok{ }\DecValTok{0}
+
+\KeywordTok{names}\NormalTok{(Fibresum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Fibre6_9"}\NormalTok{, }\StringTok{"Fibre9_12"}\NormalTok{, }\StringTok{"Fibre12_14"}\NormalTok{, }\StringTok{"Fibre14_17"}\NormalTok{,}
+                      \StringTok{"Fibre17_20"}\NormalTok{, }\StringTok{"Fibre20_22"}\NormalTok{, }\StringTok{"Fibre22_6"}\NormalTok{)}
+
+\NormalTok{NMESsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumNMES) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+         \DataTypeTok{value =}\NormalTok{ sumNMES)}
+\NormalTok{NMESsum[}\KeywordTok{is.na}\NormalTok{(NMESsum)] <-}\StringTok{ }\DecValTok{0}
+
+\KeywordTok{names}\NormalTok{(NMESsum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"NMES6_9"}\NormalTok{, }\StringTok{"NMES9_12"}\NormalTok{, }\StringTok{"NMES12_14"}\NormalTok{, }\StringTok{"NMES14_17"}\NormalTok{,}
+                      \StringTok{"NMES17_20"}\NormalTok{, }\StringTok{"NMES20_22"}\NormalTok{, }\StringTok{"NMES22_6"}\NormalTok{)}
+
+\NormalTok{Fatsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumFat) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+         \DataTypeTok{value =}\NormalTok{ sumFat)}
+\NormalTok{Fatsum[}\KeywordTok{is.na}\NormalTok{(Fatsum)] <-}\StringTok{ }\DecValTok{0}
+
+\KeywordTok{names}\NormalTok{(Fatsum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Fat6_9"}\NormalTok{, }\StringTok{"Fat9_12"}\NormalTok{, }\StringTok{"Fat12_14"}\NormalTok{, }\StringTok{"Fat14_17"}\NormalTok{,}
+                     \StringTok{"Fat17_20"}\NormalTok{, }\StringTok{"Fat20_22"}\NormalTok{, }\StringTok{"Fat22_6"}\NormalTok{)}
+
+\NormalTok{Protsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumProt) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+         \DataTypeTok{value =}\NormalTok{ sumProt)}
+\NormalTok{Protsum[}\KeywordTok{is.na}\NormalTok{(Protsum)] <-}\StringTok{ }\DecValTok{0}
+
+\KeywordTok{names}\NormalTok{(Protsum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Prot6_9"}\NormalTok{, }\StringTok{"Prot9_12"}\NormalTok{, }\StringTok{"Prot12_14"}\NormalTok{, }\StringTok{"Prot14_17"}\NormalTok{,}
+                    \StringTok{"Prot17_20"}\NormalTok{, }\StringTok{"Prot20_22"}\NormalTok{, }\StringTok{"Prot22_6"}\NormalTok{)}
+
+\NormalTok{Alcsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumAlc) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+         \DataTypeTok{value =}\NormalTok{ sumAlc)}
+\NormalTok{Alcsum[}\KeywordTok{is.na}\NormalTok{(Alcsum)] <-}\StringTok{ }\DecValTok{0}
+
+\KeywordTok{names}\NormalTok{(Alcsum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Alc6_9"}\NormalTok{, }\StringTok{"Alc9_12"}\NormalTok{, }\StringTok{"Alc12_14"}\NormalTok{, }\StringTok{"Alc14_17"}\NormalTok{,}
+                     \StringTok{"Alc17_20"}\NormalTok{, }\StringTok{"Alc20_22"}\NormalTok{, }\StringTok{"Alc22_6"}\NormalTok{)}
+
+\CommentTok{# Extract number of days of diary completed}
+
+\NormalTok{blood14 <-}\StringTok{ }\NormalTok{blood14 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Ndays)}
+
+\NormalTok{blood56 <-}\StringTok{ }\NormalTok{blood56 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Ndays)}
+
+\NormalTok{blood78 <-}\StringTok{ }\NormalTok{blood78 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, NDays) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{Ndays =}\NormalTok{ NDays)}
+
+\NormalTok{NDAYS <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(blood14, blood56, blood78)}
+\NormalTok{NDAYS}\OperatorTok{$}\NormalTok{ID <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(NDAYS}\OperatorTok{$}\NormalTok{ID)}
+
+\NormalTok{IntakeSlots <-}\StringTok{ }\NormalTok{Energysum }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Carbsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Sugarsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Starchsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Fibresum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Fatsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Protsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(NMESsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Alcsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(NDAYS, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{)}
+
+\NormalTok{IntakeSlots}\OperatorTok{$}\NormalTok{ID <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(IntakeSlots}\OperatorTok{$}\NormalTok{ID)}
+
+\NormalTok{IntakeSlots}\OperatorTok{$}\NormalTok{Energy6_}\DecValTok{9}\NormalTok{ <-}\StringTok{ }\NormalTok{IntakeSlots}\OperatorTok{$}\NormalTok{Energy6_}\DecValTok{9}\OperatorTok{/}\NormalTok{(IntakeSlots}\OperatorTok{$}\NormalTok{Ndays)}
+
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{3}\OperatorTok{:}\DecValTok{57}\NormalTok{)\{}
+\NormalTok{  IntakeSlots[, i] <-}\StringTok{ }\NormalTok{IntakeSlots[, i]}\OperatorTok{/}\NormalTok{(IntakeSlots}\OperatorTok{$}\NormalTok{Ndays)}
+\NormalTok{\}}
+
+\CommentTok{# select the variables needed, recoding }
+\CommentTok{# NAs, renaming to the same ----------------------------------------}
+
+\NormalTok{BMI78 <-}\StringTok{ }\NormalTok{blood78 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Sex, age, bmival, wstval, Diabetes, bpmedc2, bpmedd2, }
+\NormalTok{         hyper140_}\DecValTok{2}\NormalTok{, hibp140_}\DecValTok{2}\NormalTok{,  Glucose, A1C, cigsta3, dnoft3, }
+\NormalTok{         dnnow, wti_Y78, wtn_Y78, wtb_Y78, ethgrp5, ethgrp2,}
+\NormalTok{         cluster1, cluster2, cluster3, nssec8, paidemployment, }
+\NormalTok{         qual7, eqvinc, MarSt2, cluster4, cluster5, area, gor, }
+\NormalTok{         LDL, HDL, Chol, Trig) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{wti =}\NormalTok{ wti_Y78, }\DataTypeTok{wtn =}\NormalTok{ wtn_Y78, }\DataTypeTok{wtb =}\NormalTok{ wtb_Y78, }
+         \DataTypeTok{drink =}\NormalTok{ dnoft3) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Years =} \StringTok{"7-8"}\NormalTok{, }\DataTypeTok{MVPAtime =} \OtherTok{NA}\NormalTok{, }\DataTypeTok{MarStat =} \OtherTok{NA}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{bmival =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{qual7 =} \OperatorTok{-}\DecValTok{8}\NormalTok{,}
+                                 \DataTypeTok{wstval =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{eqvinc =} \OperatorTok{-}\DecValTok{1}\NormalTok{,}
+                                 \DataTypeTok{bpmedd2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{MarSt2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{,}
+                                 \DataTypeTok{bpmedc2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{hyper140_2 =} \OperatorTok{-}\DecValTok{7}\NormalTok{, }
+                                 \DataTypeTok{hibp140_2 =} \OperatorTok{-}\DecValTok{7}\NormalTok{, }\DataTypeTok{Glucose =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
+                                 \DataTypeTok{A1C  =} \OperatorTok{-}\DecValTok{1}\NormalTok{,  }\DataTypeTok{LDL =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{HDL =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
+                                 \DataTypeTok{Chol =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{Trig =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{dnnow =} \OperatorTok{-}\DecValTok{1}\NormalTok{,}
+                                 \DataTypeTok{drink =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{ethgrp5 =} \OperatorTok{-}\DecValTok{4}\NormalTok{, }
+                                 \DataTypeTok{ethgrp2 =} \OperatorTok{-}\DecValTok{4}\NormalTok{, }\DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
+                                 \DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{9}\NormalTok{,  }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{1}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{hyper140_2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{hibp140_2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
+                                 \DataTypeTok{nssec8 =} \DecValTok{99}\NormalTok{, }\DataTypeTok{qual7 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{drink =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }
+                                 \DataTypeTok{ethgrp2 =} \OperatorTok{-}\DecValTok{9}\NormalTok{, }\DataTypeTok{ethgrp5 =} \OperatorTok{-}\DecValTok{9}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{drink =} \OperatorTok{-}\DecValTok{9}\NormalTok{, }\DataTypeTok{ethgrp2 =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }\DataTypeTok{ethgrp5 =} \OperatorTok{-}\DecValTok{8}\NormalTok{,}
+                                 \DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{8}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{ethgrp2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{ethgrp5 =} \OperatorTok{-}\DecValTok{1}\NormalTok{))}
+
+\NormalTok{BMI56 <-}\StringTok{ }\NormalTok{blood56 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Sex, age, area, bmival, wstval, Diabetes, bpmedc2, bpmedd2, }
+\NormalTok{         hyper140_}\DecValTok{2}\NormalTok{, hibp140_}\DecValTok{2}\NormalTok{, MVPAtime, Glucose, A1C, cigsta3, dnoft3, }
+\NormalTok{         dnnow, wti_Y56, wtn_Y56, wtb_Y56, ethgrp5, ethgrp2, qual7,}
+\NormalTok{         cluster1, cluster2, cluster3, nssec8, paidemployment, eqvinc, }
+\NormalTok{         MarSt2, cluster4, cluster5, area, gor, LDL, HDL, Chol, Trig) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Years =} \StringTok{"5-6"}\NormalTok{, }\DataTypeTok{MarStat =} \OtherTok{NA}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{wti =}\NormalTok{ wti_Y56, }\DataTypeTok{wtn =}\NormalTok{ wtn_Y56, }\DataTypeTok{wtb =}\NormalTok{ wtb_Y56, }\DataTypeTok{drink =}\NormalTok{ dnoft3) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{bmival =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{9}\NormalTok{,}
+                                 \DataTypeTok{wstval =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{qual7 =} \OperatorTok{-}\DecValTok{8}\NormalTok{,}
+                                 \DataTypeTok{bpmedd2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{eqvinc =} \OperatorTok{-}\DecValTok{1}\NormalTok{,}
+                                 \DataTypeTok{bpmedc2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{MarSt2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{,}
+                                 \DataTypeTok{hyper140_2 =} \OperatorTok{-}\DecValTok{7}\NormalTok{, }\DataTypeTok{hibp140_2 =} \OperatorTok{-}\DecValTok{7}\NormalTok{, }
+                                 \DataTypeTok{Glucose =} \OperatorTok{-}\DecValTok{1}\NormalTok{,  }\DataTypeTok{A1C  =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
+                                 \DataTypeTok{dnnow =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{drink =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{ethgrp5 =} \OperatorTok{-}\DecValTok{4}\NormalTok{,}
+                                 \DataTypeTok{ethgrp2 =} \OperatorTok{-}\DecValTok{4}\NormalTok{, }\DataTypeTok{LDL =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{HDL =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
+                                 \DataTypeTok{Chol =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{Trig =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{1}\NormalTok{,}
+                                 \DataTypeTok{MVPAtime =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{9}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{hyper140_2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{hibp140_2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
+                                 \DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }
+                                 \DataTypeTok{drink =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }\DataTypeTok{nssec8 =} \DecValTok{99}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{    }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{drink =} \OperatorTok{-}\DecValTok{9}\NormalTok{, }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
+                                   \DataTypeTok{qual7 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{8}\NormalTok{))}
+
+\NormalTok{BMI14 <-}\StringTok{ }\NormalTok{blood14 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Sex, age, bmival, wstval, Diabetes, bpmedc, bpmedd, hyper140, }
+\NormalTok{         hibp140, MVPAtime, Glucose, A1C, cigsta3, dnoft3, dnnow, }
+\NormalTok{         wti_CY1234, wtn_CY1234, wtb_CY1234, ethgr5, ethgr2, cluster, }
+\NormalTok{         area, gor, nssec8, paidemployment, qual7, eqvinc, MarSt2, }
+\NormalTok{         MarStat, LDL, HDL, Chol, Trig) }\OperatorTok{%>%}
+\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{hyper140_2 =}\NormalTok{ hyper140, }\DataTypeTok{hibp140_2 =}\NormalTok{ hibp140, }\DataTypeTok{bpmedd2 =}\NormalTok{ bpmedd, }
+         \DataTypeTok{bpmedc2 =}\NormalTok{ bpmedc, }\DataTypeTok{cluster1 =}\NormalTok{ cluster, }\DataTypeTok{ethgrp5 =}\NormalTok{ ethgr5, }
+         \DataTypeTok{ethgrp2 =}\NormalTok{ ethgr2, }\DataTypeTok{wti =}\NormalTok{ wti_CY1234, }\DataTypeTok{wtn =}\NormalTok{ wtn_CY1234, }
+         \DataTypeTok{wtb =}\NormalTok{  wtb_CY1234, }\DataTypeTok{drink =}\NormalTok{ dnoft3) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{cluster2 =} \OtherTok{NA}\NormalTok{, }\DataTypeTok{cluster3 =} \OtherTok{NA}\NormalTok{, }\DataTypeTok{cluster4 =} \OtherTok{NA}\NormalTok{, }\DataTypeTok{cluster5 =} \OtherTok{NA}\NormalTok{, }
+         \DataTypeTok{Years =} \StringTok{"1-4"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{bmival =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{9}\NormalTok{, }
+                                 \DataTypeTok{wstval =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{qual7 =} \OperatorTok{-}\DecValTok{8}\NormalTok{,}
+                                 \DataTypeTok{bpmedd2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{eqvinc =} \OperatorTok{-}\DecValTok{1}\NormalTok{,}
+                                 \DataTypeTok{bpmedc2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{MarSt2 =} \OperatorTok{-}\DecValTok{4}\NormalTok{, }
+                                 \DataTypeTok{hyper140_2 =} \OperatorTok{-}\DecValTok{7}\NormalTok{, }\DataTypeTok{MarStat =} \OperatorTok{-}\DecValTok{4}\NormalTok{,}
+                                 \DataTypeTok{hibp140_2 =} \OperatorTok{-}\DecValTok{7}\NormalTok{,  }\DataTypeTok{Glucose =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
+                                 \DataTypeTok{A1C  =} \OperatorTok{-}\DecValTok{1}\NormalTok{,  }\DataTypeTok{dnnow =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{LDL =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
+                                 \DataTypeTok{HDL =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{Chol =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{Trig =} \OperatorTok{-}\DecValTok{1}\NormalTok{,}
+                                 \DataTypeTok{drink =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{ethgrp5 =} \OperatorTok{-}\DecValTok{4}\NormalTok{, }\DataTypeTok{ethgrp2 =} \OperatorTok{-}\DecValTok{4}\NormalTok{,}
+                                 \DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{MVPAtime =} \OperatorTok{-}\DecValTok{4}\NormalTok{,  }
+                                 \DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{8}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{hyper140_2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{hibp140_2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
+                                 \DataTypeTok{MVPAtime =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{8}\NormalTok{,}
+                                 \DataTypeTok{drink =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }\DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{qual7 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
+                                 \DataTypeTok{MarSt2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{drink =} \OperatorTok{-}\DecValTok{9}\NormalTok{, }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{4}\NormalTok{,}
+                                 \DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }\DataTypeTok{nssec8 =} \DecValTok{99}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{1}\NormalTok{))}
+
+\NormalTok{BMI <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(BMI14, BMI56, BMI78)}
+
+\NormalTok{Energy14 <-}\StringTok{ }\NormalTok{food14 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, }
+\NormalTok{         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,}
+\NormalTok{         Fatg, FatpctotE)}
+\NormalTok{Energy14}\OperatorTok{$}\NormalTok{Country[Energy14}\OperatorTok{$}\NormalTok{Country }\OperatorTok{==}\StringTok{ "Northern Ireland"}\NormalTok{] <-}\StringTok{ "NI"}
+
+\NormalTok{Energy56 <-}\StringTok{ }\NormalTok{food56 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Country, Surveyyear, EnergykJ, Carbohydrateg, }
+\NormalTok{         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,}
+\NormalTok{         Fatg, FatpctotE) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{SurveyYear =}\NormalTok{ Surveyyear)}
+
+\NormalTok{Energy78 <-}\StringTok{ }\NormalTok{food78 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, }
+\NormalTok{         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,}
+\NormalTok{         Fatg, FatpctotE)}
+
+\NormalTok{Energy <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(Energy14, Energy56, Energy78)}
+
+\NormalTok{dta_NDNS <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"dta_NDNS_Tslots.csv"}\NormalTok{) }\CommentTok{# extract the day of week data}
+
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{DayNo <-}\StringTok{ }\KeywordTok{ave}\NormalTok{(CW3idday}\OperatorTok{$}\NormalTok{ID_DAY, CW3idday}\OperatorTok{$}\NormalTok{ID, }
+                      \DataTypeTok{FUN =}\NormalTok{ seq_along) }\CommentTok{# adding the day no }
+
+\NormalTok{dta_DayofWeek <-}\StringTok{ }\NormalTok{dta_NDNS }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(id, id_dy, DayofWeek)}
+
+\NormalTok{dta_DayofWeek}\OperatorTok{$}\NormalTok{DayNo <-}\StringTok{ }\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dta_DayofWeek}\OperatorTok{$}\NormalTok{id_dy,}
+                                       \StringTok{"D"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }\OtherTok{TRUE}\NormalTok{)] }\CommentTok{# creating a day No}
+\KeywordTok{names}\NormalTok{(dta_DayofWeek)[}\DecValTok{1}\NormalTok{] <-}\StringTok{ "ID"}
+\NormalTok{dta_DayofWeek}\OperatorTok{$}\NormalTok{DayNo <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(dta_DayofWeek}\OperatorTok{$}\NormalTok{DayNo)}
+
+\NormalTok{CW3idday <-}\StringTok{   }\NormalTok{CW3idday }\OperatorTok{%>%}\StringTok{  }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(dta_DayofWeek, }\DataTypeTok{by=} \KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"DayNo"}\NormalTok{))}
+
+\NormalTok{## Manually check the day of week}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{DayofWeek[CW3idday}\OperatorTok{$}\NormalTok{ID_DAY }\OperatorTok{==}\StringTok{ }\DecValTok{40714261000}\NormalTok{] <-}\StringTok{ "Saturday"}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{DayofWeek[CW3idday}\OperatorTok{$}\NormalTok{ID_DAY }\OperatorTok{==}\StringTok{ }\DecValTok{112050710000}\NormalTok{] <-}\StringTok{ "Tuesday"}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{DayofWeek[CW3idday}\OperatorTok{$}\NormalTok{ID_DAY }\OperatorTok{==}\StringTok{ }\DecValTok{310122510000}\NormalTok{] <-}\StringTok{ "Wednesday"}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{DayofWeek[CW3idday}\OperatorTok{$}\NormalTok{ID_DAY }\OperatorTok{==}\StringTok{ }\DecValTok{5050616100}\NormalTok{] <-}\StringTok{ "Monday"}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{DayofWeek[CW3idday}\OperatorTok{$}\NormalTok{ID_DAY }\OperatorTok{==}\StringTok{ }\DecValTok{50506161000}\NormalTok{] <-}\StringTok{ "Tuesday"}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{DayofWeek[CW3idday}\OperatorTok{$}\NormalTok{ID_DAY }\OperatorTok{==}\StringTok{ }\DecValTok{505061610000}\NormalTok{] <-}\StringTok{ "Wednesday"}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{DayofWeek[CW3idday}\OperatorTok{$}\NormalTok{ID_DAY }\OperatorTok{==}\StringTok{ }\DecValTok{7090824100}\NormalTok{] <-}\StringTok{ "Monday"}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{DayofWeek[CW3idday}\OperatorTok{$}\NormalTok{ID_DAY }\OperatorTok{==}\StringTok{ }\DecValTok{70908241000}\NormalTok{] <-}\StringTok{ "Tuesday"}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{DayofWeek[CW3idday}\OperatorTok{$}\NormalTok{ID_DAY }\OperatorTok{==}\StringTok{ }\DecValTok{709082410000}\NormalTok{] <-}\StringTok{ "Wednesday"}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{DayofWeek[CW3idday}\OperatorTok{$}\NormalTok{ID_DAY }\OperatorTok{==}\StringTok{ }\DecValTok{807021910000}\NormalTok{] <-}\StringTok{ "Monday"}
+\NormalTok{CW3idday}\OperatorTok{$}\NormalTok{DayofWeek[CW3idday}\OperatorTok{$}\NormalTok{ID_DAY }\OperatorTok{==}\StringTok{ }\DecValTok{812101310000}\NormalTok{] <-}\StringTok{ "Sunday"}
+
+\NormalTok{CW3CB3_reg <-}\StringTok{ }\NormalTok{CW3CB3[}\OperatorTok{!}\KeywordTok{duplicated}\NormalTok{(CW3CB3}\OperatorTok{$}\NormalTok{ID), ]}
+
+\CommentTok{# extract only the CB variable (Between individual classes == 1 or 2)}
+\NormalTok{CW3CB3_reg <-}\StringTok{ }\NormalTok{CW3CB3_reg }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, AGE, SEX, CB) }
+
+\KeywordTok{tab1}\NormalTok{(CW3CB3_reg}\OperatorTok{$}\NormalTok{CB, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{)}
+
+\NormalTok{## dataset for 3by3 multilevel latent classes }
+\NormalTok{CW3CB3_regss <-}\StringTok{ }\NormalTok{CW3CB3_reg }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(BMI, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Energy, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }
+
+\CommentTok{# Rescale the weighting values}
+\CommentTok{# individual weighting}
+
+\NormalTok{a <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "1-4"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wti)}
+\NormalTok{b <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "5-6"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wti)}
+\NormalTok{c <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "7-8"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wti)}
+
+\NormalTok{CW3CB3_regss}\OperatorTok{$}\NormalTok{wti1to8 <-}\StringTok{ }\NormalTok{CW3CB3_regss}\OperatorTok{$}\NormalTok{wti}
+
+\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "1-4"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wti1to8 <-}\StringTok{ }
+\StringTok{  }\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "1-4"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wti}\OperatorTok{*}\NormalTok{(a}\OperatorTok{+}\NormalTok{b}\OperatorTok{+}\NormalTok{c)}\OperatorTok{*}\NormalTok{(}\DecValTok{1}\OperatorTok{/}\DecValTok{2}\NormalTok{)}\OperatorTok{/}\NormalTok{a}
+\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "5-6"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wti1to8 <-}\StringTok{ }
+\StringTok{  }\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "5-6"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wti}\OperatorTok{*}\NormalTok{(a}\OperatorTok{+}\NormalTok{b}\OperatorTok{+}\NormalTok{c)}\OperatorTok{*}\NormalTok{(}\DecValTok{1}\OperatorTok{/}\DecValTok{4}\NormalTok{)}\OperatorTok{/}\NormalTok{b}
+\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "7-8"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wti1to8 <-}\StringTok{ }
+\StringTok{  }\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "7-8"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wti}\OperatorTok{*}\NormalTok{(a}\OperatorTok{+}\NormalTok{b}\OperatorTok{+}\NormalTok{c)}\OperatorTok{*}\NormalTok{(}\DecValTok{1}\OperatorTok{/}\DecValTok{4}\NormalTok{)}\OperatorTok{/}\NormalTok{c}
+\KeywordTok{mean}\NormalTok{(CW3CB3_regss}\OperatorTok{$}\NormalTok{wti1to8)}
+
+\NormalTok{CW3CB3_regss}\OperatorTok{$}\NormalTok{wti1to8 <-}\StringTok{ }\NormalTok{CW3CB3_regss}\OperatorTok{$}\NormalTok{wti1to8}\OperatorTok{/}\FloatTok{1.209816814}
+\KeywordTok{summ}\NormalTok{(CW3CB3_regss}\OperatorTok{$}\NormalTok{wti1to8, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{)}
+\CommentTok{#Check if the weighting sum up to the sample size we have}
+\KeywordTok{sum}\NormalTok{(CW3CB3_regss}\OperatorTok{$}\NormalTok{wti1to8, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{) }
+
+\CommentTok{# Nurse weights}
+
+\NormalTok{a <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "1-4"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtn)}
+\NormalTok{b <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "5-6"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtn)}
+\NormalTok{c <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "7-8"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtn)}
+
+\NormalTok{CW3CB3_regss}\OperatorTok{$}\NormalTok{wtn1to8 <-}\StringTok{ }\NormalTok{CW3CB3_regss}\OperatorTok{$}\NormalTok{wtn}
+
+\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "1-4"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtn1to8 <-}\StringTok{ }
+\StringTok{  }\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "1-4"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtn}\OperatorTok{*}\NormalTok{(a}\OperatorTok{+}\NormalTok{b}\OperatorTok{+}\NormalTok{c)}\OperatorTok{*}\NormalTok{(}\DecValTok{1}\OperatorTok{/}\DecValTok{2}\NormalTok{)}\OperatorTok{/}\NormalTok{a}
+\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "5-6"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtn1to8 <-}\StringTok{ }
+\StringTok{  }\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "5-6"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtn}\OperatorTok{*}\NormalTok{(a}\OperatorTok{+}\NormalTok{b}\OperatorTok{+}\NormalTok{c)}\OperatorTok{*}\NormalTok{(}\DecValTok{1}\OperatorTok{/}\DecValTok{4}\NormalTok{)}\OperatorTok{/}\NormalTok{b}
+\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "7-8"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtn1to8 <-}\StringTok{ }
+\StringTok{  }\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "7-8"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtn}\OperatorTok{*}\NormalTok{(a}\OperatorTok{+}\NormalTok{b}\OperatorTok{+}\NormalTok{c)}\OperatorTok{*}\NormalTok{(}\DecValTok{1}\OperatorTok{/}\DecValTok{4}\NormalTok{)}\OperatorTok{/}\NormalTok{c}
+\KeywordTok{mean}\NormalTok{(CW3CB3_regss}\OperatorTok{$}\NormalTok{wtn1to8)}
+
+\NormalTok{CW3CB3_regss}\OperatorTok{$}\NormalTok{wtn1to8 <-}\StringTok{ }\NormalTok{CW3CB3_regss}\OperatorTok{$}\NormalTok{wtn1to8}\OperatorTok{/}\FloatTok{0.907003577}
+\KeywordTok{summ}\NormalTok{(CW3CB3_regss}\OperatorTok{$}\NormalTok{wtn1to8, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{)}
+\CommentTok{#Check if the weighting sum up to the sample size we have}
+\KeywordTok{sum}\NormalTok{(CW3CB3_regss}\OperatorTok{$}\NormalTok{wtn1to8, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{) }
+
+\CommentTok{# Blood weights}
+\NormalTok{a <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "1-4"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtb)}
+\NormalTok{b <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "5-6"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtb)}
+\NormalTok{c <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "7-8"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtb)}
+
+\NormalTok{CW3CB3_regss}\OperatorTok{$}\NormalTok{wtb1to8 <-}\StringTok{ }\NormalTok{CW3CB3_regss}\OperatorTok{$}\NormalTok{wtb}
+
+\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "1-4"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtb1to8 <-}\StringTok{ }
+\StringTok{  }\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "1-4"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtb}\OperatorTok{*}\NormalTok{(a}\OperatorTok{+}\NormalTok{b}\OperatorTok{+}\NormalTok{c)}\OperatorTok{*}\NormalTok{(}\DecValTok{1}\OperatorTok{/}\DecValTok{2}\NormalTok{)}\OperatorTok{/}\NormalTok{a}
+\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "5-6"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtb1to8 <-}\StringTok{ }
+\StringTok{  }\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "5-6"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtb}\OperatorTok{*}\NormalTok{(a}\OperatorTok{+}\NormalTok{b}\OperatorTok{+}\NormalTok{c)}\OperatorTok{*}\NormalTok{(}\DecValTok{1}\OperatorTok{/}\DecValTok{4}\NormalTok{)}\OperatorTok{/}\NormalTok{b}
+\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "7-8"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtb1to8 <-}\StringTok{ }
+\StringTok{  }\NormalTok{CW3CB3_regss[CW3CB3_regss}\OperatorTok{$}\NormalTok{Years }\OperatorTok{==}\StringTok{ "7-8"}\NormalTok{,]}\OperatorTok{$}\NormalTok{wtb}\OperatorTok{*}\NormalTok{(a}\OperatorTok{+}\NormalTok{b}\OperatorTok{+}\NormalTok{c)}\OperatorTok{*}\NormalTok{(}\DecValTok{1}\OperatorTok{/}\DecValTok{4}\NormalTok{)}\OperatorTok{/}\NormalTok{c}
+\KeywordTok{mean}\NormalTok{(CW3CB3_regss}\OperatorTok{$}\NormalTok{wtb1to8)}
+
+\NormalTok{CW3CB3_regss}\OperatorTok{$}\NormalTok{wtb1to8 <-}\StringTok{ }\NormalTok{CW3CB3_regss}\OperatorTok{$}\NormalTok{wtb1to8}\OperatorTok{/}\FloatTok{0.4817444505}
+\KeywordTok{summ}\NormalTok{(CW3CB3_regss}\OperatorTok{$}\NormalTok{wtb1to8, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{)}
+\CommentTok{#Check if the weighting sum up to the sample size we have}
+\KeywordTok{sum}\NormalTok{(CW3CB3_regss}\OperatorTok{$}\NormalTok{wtb1to8, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{)}
+
+\NormalTok{weightings <-}\StringTok{ }\NormalTok{CW3CB3_regss }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(ID, wti1to8, wtn1to8, wtb1to8)}
+
+\CommentTok{# Combine the data from nutrient intake at each time slot}
+\NormalTok{CW3CB3_7regss <-}\StringTok{ }\NormalTok{CW3CB3_7regss }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(IntakeSlots, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{)}
+
+\NormalTok{## dta ready to be analysed in STATA}
+ \CommentTok{# change the path accordingly}
+\KeywordTok{write_dta}\NormalTok{(CW3CB3_regss, }\StringTok{"../CW3CB3_7regss.dta"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+************************************************
+// Analysing NDNS survey data in stata
+// for CW3CB3 survey data analysis 
+// date created: 2018-08-01
+// manipulation of the data was done in R
+// import data from CW3CB3_7sregss.dta
+// change the path accordingly
+************************************************
+
+use "../CW3CB3_7regss.dta", clear
+
+label define smoking 1 "current" 2 "ex-smoker" 3 "Never"
+label values cigsta3 smoking
+label define gender 1 "Men" 2 "Women"
+label values Sex gender
+label define paid 1 "No" 2 "Yes"
+label values paidemployment paid
+label define ethnicity5 1 "White" 2 "Mixed" 3 "Black" 4 "Asian" 5 "Other"
+label values ethgrp5 ethnicity5
+label define ethnicity2 1 "White" 2 "non-White"
+label values ethgrp2 ethnicity2
+
+gen Married = 1 if MarStat == 2 | MarSt2 == 2 
+replace Married = 1 if MarSt2 == 3
+replace Married = 0 if Married !=1
+tab Married
+tab MarSt2
+tab MarStat
+
+label define Partner 0 "No" 1 "Yes"
+label values Married Partner
+
+gen Education = qual7 == 1
+label define Ed 0 "lower than Degree" 1 "Degree or higher"
+label values Education Ed
+
+replace Education = . if qual7 >100
+tab Educ
+
+egen BMIcat = cut(bmival), at(10, 25, 30, 40, 60)
+tab BMIcat
+
+**********************************************************
+// variables need to be log transfomred                 //
+**********************************************************
+
+gen logalc = ln(Alcoholg+1)
+summ logalc, detail
+gen logMVP = ln(MVPAtime+1)
+summ logMVP, detail
+gen logGlu = ln(Glucose)
+summ logGlu, detail
+gen logA1C = ln(A1C)
+summ logA1C, detail
+gen logChol = ln(Chol)
+summ logChol, detail
+gen logLDL = ln(LDL)
+gen logHDL = ln(HDL)
+gen logTG = ln(Trig)
+
+*********************************************************
+//  weighting use wti to see the individual results    //
+//                                                     //
+*********************************************************
+
+// weighting with individual weights, area is primary sampling unit, 
+// gor is the cluster variable
+
+svyset area [pweight = wti1to8], strata(gor)
+
+svydescribe wti // describe the weighted data set
+
+svy: tabulate Sex CB, row se ci format(%7.3f)
+svy: tabulate Sex CB, col se ci format(%7.3f)
+svy: tabulate Country CB, col se ci format(%7.3f)
+svy: tabulate Country CB, row se ci format(%7.3f)
+svy: tabulate SurveyYear CB, col se ci format(%7.3f)
+svy: tabulate SurveyYear CB, row se ci format(%7.3f)
+svy: tabulate paid CB, col se ci format(%7.3f)
+
+svy: tabulate MarSt2 CB
+svy: tabulate MarStat CB
+svy: tabulate Married CB, row se ci format(%7.3f)
+svy: tabulate Married CB, col se ci format(%7.3f)
+svy: mean eqvinc, over(CB)
+test [eqvinc]1 = [eqvinc]2 = [eqvinc]3, mtest(b) 
+// bonferroni-adjusted p-values for multiple groups using the mtest(b) option
+
+svy: tabulate ethgrp2 CB, row se ci format(%7.3f)
+svy: tabulate ethgrp2 CB, col se ci format(%7.3f)
+svy: tabulate Education CB, row se ci format(%7.3f)
+svy: tabulate Education CB, col se ci format(%7.3f)
+
+*********************************************************
+//  nutritional distribution                           //
+//                                                     //
+*********************************************************
+
+svy: mean EnergykJ, over(CB)
+test [EnergykJ]1 = [EnergykJ]2 = [EnergykJ]3, mtest(b)
+
+svy: mean Energy6, over(CB)
+test [Energy6_9]1 = [Energy6_9]2 = [Energy6_9]3, mtest(b)
+
+svy: mean Energy9, over(CB) 
+test [Energy9_12]1 = [Energy9_12]2 = [Energy9_12]3, mtest(b)
+
+svy: mean Energy12, over(CB)
+test [Energy12_14]1 = [Energy12_14]2 = [Energy12_14]3, mtest(b)
+
+svy: mean Energy14, over(CB)
+test [Energy14_17]1 = [Energy14_17]2 = [Energy14_17]3, mtest(b)
+
+svy: mean Energy17, over(CB)
+test [Energy17_20]1 = [Energy17_20]2 = [Energy17_20]3, mtest(b)
+
+svy: mean Energy20, over(CB)
+test [Energy20_22]1 = [Energy20_22]2 = [Energy20_22]3, mtest(b)
+
+svy: mean Energy22, over(CB)
+test [Energy22_6]1 = [Energy22_6]2 = [Energy22_6]3, mtest(b)
+
+svy: mean Carbohydrateg, over(CB)
+test [Carbohydrateg]1 = [Carbohydrateg]2 = [Carbohydrateg]3, mtest(b)
+
+svy: mean Carb6, over(CB)
+test [Carb6_9]1 = [Carb6_9]2 = [Carb6_9]3, mtest(b)
+
+svy: mean Carb9, over(CB)
+test [Carb9_12]1 = [Carb9_12]2 = [Carb9_12]3, mtest(b)
+
+svy: mean Carb12, over(CB)
+test [Carb12_14]1 = [Carb12_14]2 = [Carb12_14]3, mtest(b)
+
+svy: mean Carb14, over(CB)
+test [Carb14_17]1 = [Carb14_17]2 = [Carb14_17]3, mtest(b)
+
+svy: mean Carb17, over(CB)
+test [Carb17_20]1 = [Carb17_20]2 = [Carb17_20]3, mtest(b)
+
+svy: mean Carb20, over(CB)
+test [Carb20_22]1 = [Carb20_22]2 = [Carb20_22]3, mtest(b)
+
+svy: mean Carb22, over(CB)
+test [Carb22_6]1 = [Carb22_6]2 = [Carb22_6]3, mtest(b)
+
+svy: mean Sugar6, over(CB)
+test [Sugar6_9]1 = [Sugar6_9]2 = [Sugar6_9]3, mtest(b)
+
+svy: mean Sugar9, over(CB)
+test [Sugar9_12]1 = [Sugar9_12]2 = [Sugar9_12]3, mtest(b)
+
+svy: mean Sugar12, over(CB)
+test [Sugar9_12]1 = [Sugar9_12]2 = [Sugar9_12]3, mtest(b)
+
+svy: mean Sugar14, over(CB)
+test [Sugar14_17]1 = [Sugar14_17]2 = [Sugar14_17]3, mtest(b)
+
+svy: mean Sugar17, over(CB)
+test [Sugar17_20]1 = [Sugar17_20]2 = [Sugar17_20]3, mtest(b)
+
+svy: mean Sugar20, over(CB)
+test [Sugar20_22]1 = [Sugar20_22]2 = [Sugar20_22]3, mtest(b)
+
+svy: mean Sugar22, over(CB)
+test [Sugar22_6]1 = [Sugar22_6]2 = [Sugar22_6]3, mtest(b)
+
+svy: mean Starch6, over(CB)
+test [Starch6_9]1 = [Starch6_9]2 = [Starch6_9]3, mtest(b)
+
+svy: mean Starch9, over(CB)
+test [Sugar12_14]1 = [Sugar12_14]2 = [Sugar12_14]3, mtest(b)
+
+svy: mean Starch12, over(CB)
+test [Starch12_14]1 = [Starch12_14]2 = [Starch12_14]3, mtest(b)
+
+svy: mean Starch14, over(CB)
+test [Starch14_17]1 = [Starch14_17]2 = [Starch14_17]3, mtest(b)
+
+svy: mean Starch17, over(CB)
+test [Starch17_20]1 = [Starch17_20]2 = [Starch17_20]3, mtest(b)
+
+svy: mean Starch20, over(CB)
+test [Starch20_22]1 = [Starch20_22]2 = [Starch20_22]3, mtest(b)
+
+svy: mean Starch22, over(CB)
+test [Starch20_22]1 = [Starch20_22]2 = [Starch20_22]3, mtest(b)
+
+svy: mean Fibre6, over(CB)
+test [Starch22_6]1 = [Starch22_6]2 = [Starch22_6]3, mtest(b)
+
+gen Fibreg = Fibre6 + Fibre9 + Fibre12 + Fibre14 + Fibre17 + Fibre20 + Fibre22
+svy: mean Fibreg, over(CB)
+test [Fibreg]1 = [Fibreg]2 = [Fibreg]3, mtest(b)
+
+svy: mean Fibre9, over(CB)
+test [Fibre9_12]1 = [Fibre9_12]2 = [Fibre9_12]3, mtest(b)
+
+svy: mean Fibre12, over(CB)
+test [Fibre12_14]1 = [Fibre12_14]2 = [Fibre12_14]3, mtest(b)
+
+svy: mean Fibre14, over(CB)
+test [Fibre14_17]1 = [Fibre14_17]2 = [Fibre14_17]3, mtest(b)
+
+svy: mean Fibre17, over(CB)
+test [Fibre17_20]1 = [Fibre17_20]2 = [Fibre17_20]3, mtest(b)
+
+svy: mean Fibre20, over(CB)
+test [Fibre20_22]1 = [Fibre20_22]2 = [Fibre20_22]3, mtest(b)
+
+svy: mean Fibre22, over(CB)
+test [Fibre22_6]1 = [Fibre22_6]2 = [Fibre22_6]3, mtest(b)
+
+svy: mean NMES6, over(CB)
+test [NMES6_9]1 = [NMES6_9]2 = [NMES6_9]3, mtest(b)
+
+svy: mean NMES9, over(CB)
+test [NMES9_12]1 = [NMES9_12]2 = [NMES9_12]3, mtest(b)
+
+svy: mean NMES12, over(CB)
+test [NMES12_14]1 = [NMES12_14]2 = [NMES12_14]3, mtest(b)
+
+svy: mean NMES14, over(CB)
+test [NMES14_17]1 = [NMES14_17]2 = [NMES14_17]3, mtest(b)
+
+svy: mean NMES17, over(CB)
+test [NMES17_20]1 = [NMES17_20]2 = [NMES17_20]3, mtest(b)
+
+svy: mean NMES20, over(CB)
+test [NMES20_22]1 = [NMES20_22]2 = [NMES20_22]3, mtest(b)
+
+svy: mean NMES22, over(CB)
+
+svy: mean CHO, over(CB)
+test [CHOpctotE]1 = [CHOpctotE]2 = [CHOpctotE]3, mtest(b)
+
+svy: mean Proteing, over(CB)
+test [Proteing]1 = [Proteing]2 = [Proteing]3, mtest(b)
+
+svy: mean Prot6, over(CB)
+test [Prot6_9]1 = [Prot6_9]2 = [Prot6_9]3, mtest(b)
+
+svy: mean Prot9, over(CB)
+test [Prot9_12]1 = [Prot9_12]2 = [Prot9_12]3, mtest(b)
+
+svy: mean Prot12, over(CB)
+test [Prot12_14]1 = [Prot12_14]2 = [Prot12_14]3, mtest(b)
+
+svy: mean Prot14, over(CB)
+test [Prot14_17]1 = [Prot14_17]2 = [Prot14_17]3, mtest(b)
+
+svy: mean Prot17, over(CB)
+test [Prot17_20]1 = [Prot17_20]2 = [Prot17_20]3, mtest(b)
+
+svy: mean Prot20, over(CB)
+test [Prot20_22]1 = [Prot20_22]2 = [Prot20_22]3, mtest(b)
+
+svy: mean Prot22, over(CB)
+test [Prot22_6]1 = [Prot22_6]2 = [Prot22_6]3, mtest(b)
+
+svy: mean Proteinp, over(CB)
+test [ProteinpctotE]1 = [ProteinpctotE]2 = [ProteinpctotE]3, mtest(b)
+
+svy: mean Fatg, over(CB)
+test [Fatg]1 = [Fatg]2 = [Fatg]3, mtest(b)
+
+svy: mean Fat6, over(CB)
+test [Fat6_9]1 = [Fat6_9]2 = [Fat6_9]3, mtest(b)
+
+svy: mean Fat9, over(CB)
+test [Fat9_12]1 = [Fat9_12]2 = [Fat9_12]3, mtest(b)
+
+svy: mean Fat12, over(CB)
+test [Fat12_14]1 = [Fat12_14]2 = [Fat12_14]3, mtest(b)
+
+svy: mean Fat14, over(CB)
+test [Fat14_17]1 = [Fat14_17]2 = [Fat14_17]3, mtest(b)
+
+svy: mean Fat17, over(CB)
+test [Fat17_20]1 = [Fat17_20]2 = [Fat17_20]3, mtest(b)
+
+svy: mean Fat20, over(CB)
+test [Fat20_22]1 = [Fat20_22]2 = [Fat20_22]3, mtest(b)
+
+svy: mean Fat22, over(CB)
+test [Fat22_6]1 = [Fat22_6]2 = [Fat22_6]3, mtest(b)
+
+svy: mean Fatp, over(CB)
+test [FatpctotE]1 = [FatpctotE]2 = [FatpctotE]3, mtest(b)
+
+svy: mean Alcoholg, over(CB)
+test [Alcoholg]1 = [Alcoholg]2 = [Alcoholg]3, mtest(b)
+
+svy: mean Alc6, over(CB)
+test [Alc6_9]1 = [Alc6_9]2 = [Alc6_9]3, mtest(b)
+
+svy: mean Alc9, over(CB)
+test [Alc9_12]1 = [Alc9_12]2 = [Alc9_12]3, mtest(b)
+
+svy: mean Alc12, over(CB)
+test [Alc12_14]1 = [Alc12_14]2 = [Alc12_14]3, mtest(b)
+
+svy: mean Alc14, over(CB)
+test [Alc14_17]1 = [Alc14_17]2 = [Alc14_17]3, mtest(b)
+
+svy: mean Alc17, over(CB)
+test [Alc14_17]1 = [Alc14_17]2 = [Alc14_17]3, mtest(b)
+
+svy: mean Alc20, over(CB)
+test [Alc14_17]1 = [Alc14_17]2 = [Alc14_17]3, mtest(b)
+
+svy: mean Alcoholp, over(CB)
+test [AlcoholpctotE]1 = [AlcoholpctotE]2 = [AlcoholpctotE]3, mtest(b)
+
+svy: tabulate cigsta3 CB, col se ci format(%7.3f)
+svy: tabulate dnnow CB, col se ci format(%7.3f)
+svy: tabulate hibp CB, col se ci format(%7.3f)
+
+sum MVP [weight=wti1to8] if CB ==1 , det
+sum MVP [weight=wti1to8] if CB ==2 , det
+sum MVP [weight=wti1to8] if CB ==3 , det
+svy: mean MVP, over(CB)
+
+svy: mean logMVP, over(CB) eform
+test [logMVP]1 = [logMVP]2 = [logMVP]3, mtest(b)
+
+disp exp(.731059) - 1    
+dis exp(.6768489) -1 
+dis exp(.7852691) -1
+
+disp exp(.6239265) - 1    
+dis exp(.571165) -1 
+dis exp( .6766879) -1
+
+disp exp(.7273621) - 1    
+dis exp(.684545) -1 
+dis exp(.7701791) -1
+
+svy: mean logalc, over(CB)
+
+disp exp( 2.035795) - 1    
+dis exp(1.933326) -1 
+dis exp(2.138264) -1
+
+*********************************************************
+//  re-weighting use wtn to see the BMI,wc measurements //
+//                                                     //
+*********************************************************
+
+svyset area [pweight = wtn1to8], strata(gor)
+svy: mean wst, over(CB)
+test [wstval]1 = [wstval]2 = [wstval]3, mtest(b)
+
+gen Men = Sex == 1 
+svy, subpop(Men): mean wst, over(CB)
+test [wstval]1 = [wstval]2 = [wstval]3, mtest(b)
+
+gen Women = Sex == 2
+svy, subpop(Women): mean wst, over(CB)
+test [wstval]1 = [wstval]2 = [wstval]3, mtest(b)
+
+svy: mean bmi, over(CB)
+
+test [bmival]1 = [bmival]2 = [bmival]3, mtest(b)
+
+*********************************************************
+//  re-weighting use wtb to see the blood test results //
+//                                                     //
+*********************************************************
+
+svyset area [pweight = wtb1to8], strata(gor)
+
+svy: mean HDL, over(CB)
+test [HDL]1 = [HDL]2 = [HDL]3, mtest(b)
+
+svy: mean Chol, over(CB)
+test [Chol]1 = [Chol]2 = [Chol]3, mtest(b)
+
+svy: mean LDL, over(CB)
+test [LDL]1 = [LDL]2 = [LDL]3, mtest(b)
+
+svy: mean Trig, over(CB)
+test [Trig]1 = [Trig]2 = [Trig]3, mtest(b)
+
+gen DM = A1C <= 6.5 if !missing(A1C)
+
+svy, subpop(DM): mean Glucose, over(CB)
+test [Glucose]1 = [Glucose]2
+test [Glucose]1 = [Glucose]2 = [Glucose]3, mtest(b)
+
+svy, subpop(DM): mean A1C, over(CB)
+test [A1C]1 = [A1C]2
+test [A1C]1 = [A1C]2 = [A1C]3, mtest(b)
+
+svy: tabulate DM CB, col se ci format(%7.3f)
+
+svy, subpop(DM): mean Glucose, over(CB)
+test [Glucose]1 = [Glucose]2
+test [Glucose]1 = [Glucose]2 = [Glucose]3, mtest(b)
+svy, subpop(DM): mean A1C, over(C)
+test [A1C]1 = [A1C]2
+test [A1C]1 = [A1C]2 = [A1C]3, mtest(b)
+
+svy: tabulate DM C, col se ci format(%7.3f)
+
+svy, subpop(DM): mean logGlu, over(CB)
+test [logGlu]1 = [logGlu]2 = [logGlu]3, mtest(b)
+
+dis exp(1.642848)
+dis exp(1.632226)
+dis exp(1.653471)
+
+dis exp(1.620347)
+dis exp(1.606447)
+dis exp(1.634246)
+
+dis exp(1.629356)
+dis exp(1.620271)
+dis exp(1.63844)
+
+svy, subpop(DM): mean logA1C, over(CB)
+test [logA1C]1 = [logA1C]2 = [logA1C]3, mtest(b)
+
+dis exp(1.699581)
+dis exp(1.69296)
+dis exp(1.706203)
+
+dis exp(1.691608)
+dis exp(1.683897)
+dis exp(1.699318)
+
+dis exp(1.705623)
+dis exp(1.700665)
+dis exp(1.710581)
+
+svy: mean logChol, over(CB)
+dis exp(1.598818)
+dis exp(1.577698)
+dis exp(1.619939)
+
+dis exp(1.55251)  
+dis exp(1.530408)
+dis exp(1.574613)
+
+dis exp(1.599389)
+dis exp(1.583391)
+dis exp(1.615388)
+
+test [logChol]1 = [logChol]2 = [logChol]3, mtest(b)
+
+svy: mean logHDL, over(CB)
+dis exp(.3293169)
+dis exp(.3026793)
+dis exp(.3559545)
+
+dis exp(.2749379)  
+dis exp(.2476816)
+dis exp(.3021941)
+
+dis exp(.3269002)
+dis exp(.3062623)
+dis exp(.3475381)
+
+test [logHDL]1 = [logHDL]2 = [logHDL]3, mtest(b)
+
+svy: mean logLDL, over(CB)
+dis exp(1.058635)
+dis exp(1.028391)
+dis exp(1.08888)
+
+dis exp(1.018181)  
+dis exp(.984431)
+dis exp(1.051931)
+
+dis exp(1.075229)
+dis exp(1.051369)
+dis exp(1.09909)
+
+test [logLDL]1 = [logLDL]2 = [logLDL]3, mtest(b)
+
+svy: mean logTG, over(CB)
+dis exp(.1273876)
+dis exp(.0777152)
+dis exp(.17706)
+
+dis exp(.1012169)  
+dis exp(.0460972)
+dis exp(.1563366)
+
+dis exp(.0983298)
+dis exp(.0607423)
+dis exp(.1359172)
+
+test [logTG]1 = [logTG]2 = [logTG]3, mtest(b)
+
+***************************************************
+// Analysing NDNS survey data in stata
+// for CW3CB3 survey data analysis on hypertension
+// date created: 2018-08-06
+// manipulation of the data was done in R
+// import data from CW3CB3_7sregss.dta
+// change the path accordingly
+**************************************************
+
+use "../CW3CB3_7regss.dta", clear
+
+label define smoking 1 "current" 2 "ex-smoker" 3 "Never"
+label values cigsta3 smoking
+label define gender 1 "Men" 2 "Women"
+label values Sex gender
+label define paid 1 "No" 2 "Yes"
+label values paidemployment paid
+label define ethnicity5 1 "White" 2 "Mixed" 3 "Black" 4 "Asian" 5 "Other"
+label values ethgrp5 ethnicity5
+label define ethnicity2 1 "White" 2 "non-White"
+label values ethgrp2 ethnicity2
+
+gen Married = 1 if MarStat == 2 | MarSt2 == 2 
+replace Married = 1 if MarSt2 == 3
+replace Married = 0 if Married !=1
+tab Married
+tab MarSt2
+tab MarStat
+
+label define Partner 0 "No" 1 "Yes"
+label values Married Partner
+
+gen Education = qual7 == 1
+label define Ed 0 "lower than Degree" 1 "Degree or higher"
+label values Education Ed
+
+replace Education = . if qual7 >100
+tab Educ
+
+egen BMIcat = cut(bmival), at(10, 25, 30, 40, 60)
+tab BMIcat
+
+**********************************************************
+// variables need to be log transfomred                 //
+**********************************************************
+
+gen logalc = ln(Alcoholg+1)
+summ logalc, detail
+gen logMVP = ln(MVPAtime+1)
+summ logMVP, detail
+gen logGlu = ln(Glucose)
+summ logGlu, detail
+gen logA1C = ln(A1C)
+summ logA1C, detail
+gen logChol = ln(Chol)
+summ logChol, detail
+gen logLDL = ln(LDL)
+gen logHDL = ln(HDL)
+gen logTG = ln(Trig)
+
+*********************************************************
+//  weighting use wti to see the individual results    //
+//                                                     //
+*********************************************************
+
+// weighting with individual weights, area is primary sampling unit, 
+// gor is the cluster variable
+svyset area [pweight = wti1to8], strata(gor)
+
+svydescribe wti // describe the weighted data set
+
+*********************************************************
+//  re-weighting use wtn to see the BMI,wc measurements //
+//                                                     //
+*********************************************************
+
+svyset area [pweight = wtn1to8], strata(gor)
+
+gen Men = Sex == 1  //  n of men = 2537
+gen Women = Sex == 2 // n of women = 3618
+
+svy, subpop(Men): tab hibp, se ci format(%7.3f)
+svy, subpop(Women): tab hibp, se ci format(%7.3f)
+
+svy, subpop(Men): mean age, over(hibp)
+test [age]1 = [age]0
+svy, subpop(Women): mean age, over(hibp)
+test [age]1 = [age]0
+
+svy, subpop(Men): mean wst, over(hibp)
+test [wstval]1 = [wstval]0
+svy, subpop(Women): mean wst, over(hibp)
+test [wstval]1 = [wstval]0
+
+svy, subpop(Men): tabulate CB hibp, col se ci format(%7.3f)
+
+svy, subpop(Women): tabulate CB hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate Country hibp, col se ci format(%7.3f)
+
+svy, subpop(Women): tabulate Country hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate SurveyYear hibp, col se ci format(%7.3f)
+
+svy, subpop(Women): tabulate SurveyYear hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate ethgrp2 hibp, col se ci format(%7.3f)
+
+svy, subpop(Women): tabulate ethgrp2 hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate Edu hibp, col se ci format(%7.3f)
+
+svy, subpop(Women): tabulate Edu hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate cigsta3 hibp, col se ci format(%7.3f)
+
+svy, subpop(Women): tabulate cigsta3 hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate Married hibp, col  se ci format(%7.3f)
+
+svy, subpop(Men): mean logMVP, over(hibp)
+test [logMVP]1 = [logMVP]0
+
+disp exp(.9234363 ) - 1    
+dis exp(.8457101) -1 
+dis exp(1.001163) -1
+
+disp exp(.828635) - 1    
+dis exp(.730244) -1 
+dis exp( .9270261) -1
+
+svy, subpop(Women): mean logMVP, over(hibp) 
+test [logMVP]1 = [logMVP]0
+
+disp exp(.5916676) - 1    
+dis exp(.5473043) -1 
+dis exp(.6360309) -1
+
+disp exp(.4231103) - 1    
+dis exp(.3536885) -1 
+dis exp(.4925322) -1
+
+svy: mean logalc, over(CB)
+
+disp exp( 2.035795) - 1    
+dis exp(1.933326) -1 
+dis exp(2.138264) -1
+
+svy, subpop(Men): mean bmi, over(hibp)
+test [bmival]1 = [bmival]0
+svy, subpop(Women): mean bmi, over(hibp)
+test [bmival]1 = [bmival]0
+
+svy, subpop(Men): mean EnergykJ, over(hibp)
+test [EnergykJkJ]1 = [EnergykJkJ]0
+svy, subpop(Women): mean EnergykJ, over(hibp)
+test [EnergykJkJ]1 = [EnergykJkJ]0
+
+svy, subpop(Men): mean Carbo, over(hibp)
+test [Carbohydrateg]1 = [Carbohydrateg]0
+
+svy, subpop(Women): mean Carbohydrateg, over(hibp)
+test [Carbohydrateg]1 = [Carbohydrateg]0
+
+svy, subpop(Men): mean Proteing, over(hibp)
+test [Proteing]1 = [Proteing]0
+
+svy, subpop(Women): mean Carbohydrateg, over(hibp)
+test [Carbohydrateg]1 = [Carbohydrateg]0
+
+svy: tabulate Sex hibp, col se ci format(%7.3f)
+
+svy: logistic hibp i.CB
+svy: logistic hibp i.CB#i.Sex
+
+test 2.CB#2.Sex
+
+svy: tabulate paid hibp, col se ci format(%7.3f)
+
+gen DM = A1C > 6.5 if !missing(A1C)
+svyset area [pweight = wtb1to8], strata(gor)
+
+svy, subpop(Men): tabulate DM hibp, col se ci format(%7.3f)
+svy, subpop(Women): tabulate DM hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): tabulate Married hibp, col se ci format(%7.3f)
+svy, subpop(Women): tabulate Married hibp, col se ci format(%7.3f)
+
+svy, subpop(Men): mean eqvinc, over(hibp)
+test [eqvinc]1 = [eqvinc]0
+
+svy, subpop(Women): mean eqvinc, over(hibp)
+test [eqvinc]1 = [eqvinc]0
+
+********************************************************
+**   Building the GLM model 
+**   date: 07/08/2018
+**
+**
+********************************************************
+
+svyset area [pweight = wtn1to8], strata(gor)
+
+// crude association between CB and hypertension
+
+svy, subpop(Men): logistic hibp i.CB
+
+svy, subpop(Women): logistic hibp i.CB
+
+// in non DM 
+svy, subpop(Men if DM != 1): logistic hibp i.CB
+svy, subpop(Women if DM != 1): logistic hibp i.CB
+
+// looking for confounders one by one
+// Age: -> confounder
+svy, subpop(Men): logistic hibp i.CB age
+test age
+svy, subpop(Women): logistic hibp i.CB age
+test age
+
+svy, subpop(Men): logistic hibp i.CB##c.age
+svy, subpop(Women): logistic hibp i.CB##c.age
+test 2.CB#c.age 3.CB#c.age // no interaction
+
+// Partner -> confounder
+svy, subpop(Men): logistic hibp i.CB i.Married
+test 1.Married
+svy, subpop(Women): logistic hibp i.CB i.Married
+test 1.Married
+
+svy, subpop(Men): logistic hibp i.CB##i.Married
+svy, subpop(Women): logistic hibp i.CB##i.Married
+
+test 2.CB#1.Married 3.CB#1.Married // -> no interaction
+
+// Income -> not confounder for men but confounder for women
+svy, subpop(Men): logistic hibp i.CB eqvinc 
+test eqvinc
+svy, subpop(Women): logistic hibp i.CB eqvinc 
+test eqvinc
+
+svy, subpop(Men): logistic hibp i.CB##c.eqvinc 
+svy, subpop(Women): logistic hibp i.CB##c.eqvinc
+
+test 2.CB#c.eqvinc 3.CB#c.eqvinc // -> (probably) no interaction
+
+// Education -> confounder
+svy, subpop(Men): logistic hibp i.CB i.Edu 
+test 1.Edu
+svy, subpop(Women): logistic hibp i.CB i.Edu 
+test 1.Edu
+
+svy, subpop(Men): logistic hibp i.CB##i.Edu 
+svy, subpop(Women): logistic hibp i.CB##i.Edu
+
+test 2.CB#1.Edu 3.CB#1.Edu // no interaction
+
+// BMI -> confounder
+svy, subpop(Men): logistic hibp i.CB bmi
+test bmi
+svy, subpop(Women): logistic hibp i.CB bmi
+test bmi
+
+svy, subpop(Men): logistic hibp i.CB##c.bmi
+svy, subpop(Women): logistic hibp i.CB##c.bmi
+
+test 2.CB#c.bmival 3.CB#c.bmival // no ineraction
+
+// paid employment -> not confounder
+svy, subpop(Men): logistic hibp i.CB i.paid
+test 2.paid
+svy, subpop(Women): logistic hibp i.CB i.paid
+test 2.paid
+
+svy, subpop(Men): logistic hibp i.CB##i.paid
+svy, subpop(Women): logistic hibp i.CB##i.paid
+
+test 2.CB#2.paid 3.CB#2.paid
+
+// Smoking -> confounder
+svy, subpop(Men): logistic hibp i.CB i.cigsta3
+test 2.cigsta3 3.cigsta3
+svy, subpop(Women): logistic hibp i.CB i.cigsta3
+test 2.cigsta3 3.cigsta3
+
+svy, subpop(Men): logistic hibp i.CB##i.cigsta3
+svy, subpop(Women): logistic hibp i.CB##i.cigsta3
+
+test 2.CB#2.cigsta3 2.CB#3.cigsta3 3.CB#2.cigsta3 3.CB#3.cigsta3 // no interaction
+
+// Total energy intake -> confounder
+svy, subpop(Men): logistic hibp i.CB EnergykJ
+test EnergykJ
+svy, subpop(Women): logistic hibp i.CB EnergykJ
+test EnergykJ
+
+svy, subpop(Men): logistic hibp i.CB##c.EnergykJ
+svy, subpop(Women): logistic hibp i.CB##c.EnergykJ
+test 2.CB#c.EnergykJkJ 3.CB#c.EnergykJkJ // no interaction
+
+// ethnicity -> not confounder
+svy, subpop(Men): logistic hibp i.CB i.ethgrp2
+test 2.eth
+svy, subpop(Women): logistic hibp i.CB i.ethgrp2
+test 2.eth
+
+svy, subpop(Men): logistic hibp i.CB##i.ethgrp2
+svy, subpop(Women): logistic hibp i.CB##i.ethgrp2
+test 2.CB#2.ethgrp2 // no interaction
+
+// Alcohol -> not confounder for men but confounder for women
+svy, subpop(Men): logistic hibp i.CB Alcoholg
+test Alcoholg
+svy, subpop(Women): logistic hibp i.CB Alcoholg
+test Alcoholg
+
+svy, subpop(Men): logistic hibp i.CB##c.Alcoholg
+svy, subpop(Women): logistic hibp i.CB##c.Alcoholg
+test 2.CB#c.Alcoholg 3.CB#c.Alcoholg // no interaction
+
+// logMVP -> not confounder 
+svy, subpop(Men): logistic hibp i.CB logMVP
+test logMVP
+svy, subpop(Women): logistic hibp i.CB logMVP
+test logMVP
+
+svy, subpop(Men): logistic hibp i.CB##c.logMVP
+svy, subpop(Women): logistic hibp i.CB##c.logMVP
+test 2.CB#c.logMVP 3.CB#c.logMVP // no interaction
+
+//  Preliminary model includes all possible confounders in Men
+
+gen age2 = age^2
+
+svy, subpop(Men): logistic hibp i.CB age i.Married i.Edu bmi i.cig EnergykJ 
+linktest
+svy, subpop(Men): logistic hibp i.CB age i.Married i.Edu wst i.cig EnergykJ 
+linktest
+svy, subpop(if Men & DM != 1): logistic hibp i.CB age i.Married i.Edu bmi i.cig EnergykJ 
+linktest
+svy, subpop(if Men & DM != 1): logistic hibp i.CB age i.Married i.Edu wst i.cig EnergykJ 
+linktest
+
+//  Preliminary model includes all possible confounders in Women
+
+svy, subpop(Women): logistic hibp i.CB age i.Married eqvinc i.Edu bmi i.cig EnergykJ Alcoholg 
+linktest
+svy, subpop(Women): logistic hibp i.CB age i.Married eqvinc i.Edu wst i.cig EnergykJ Alcoholg 
+linktest
+
+svy, subpop(if Women & DM != 1): logistic hibp i.CB age i.Married eqvinc i.Edu bmi i.cig EnergykJ Alcoholg
+linktest
+
+svy, subpop(if Women & DM != 1): logistic hibp i.CB age i.Married eqvinc i.Edu wst i.cig EnergykJ Alcoholg
+linktest
+\end{verbatim}
+
 \end{document}

### 2018-08-17 paper/Appendices/AppendixA.tex
aims and objectives
appendix C figlevel 1 CW4

@@
 \label{AppendixA} % For referencing this appendix elsewhere, use \ref{AppendixA}
+\linespread{0.8}
 
@@
 \CommentTok{# NDNS analysis, data management ------------------------------------------}
-
 \CommentTok{# Change the data path accordingly ----------------------------------------}
-\KeywordTok{setwd}\NormalTok{(}\StringTok{"/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }\CommentTok{# in Ubuntu}
+\KeywordTok{setwd}\NormalTok{(}\StringTok{".../UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }
+\KeywordTok{setwd}\NormalTok{(}\StringTok{"~/Downloads/UKDA-6533-stata11_se/stata11_se/"}\NormalTok{)}
 \KeywordTok{library}\NormalTok{(epiDisplay)}
@@
 \KeywordTok{library}\NormalTok{(tidyverse)}
-
 \CommentTok{# Read the data into memory -----------------------------------------------}
@@
 \KeywordTok{names}\NormalTok{(data78)}
-\KeywordTok{names}\NormalTok{(data)[}\KeywordTok{names}\NormalTok{(data) }\OperatorTok{==}\StringTok{ "seriali"}\NormalTok{] <-}\StringTok{ "id"}
-\KeywordTok{names}\NormalTok{(data56)[}\KeywordTok{names}\NormalTok{(data56) }\OperatorTok{==}\StringTok{ "seriali"}\NormalTok{] <-}\StringTok{ "id"}
-\KeywordTok{names}\NormalTok{(data78)[}\KeywordTok{names}\NormalTok{(data78) }\OperatorTok{==}\StringTok{ "seriali"}\NormalTok{] <-}\StringTok{ "id"}
+\KeywordTok{names}\NormalTok{(data)[}\KeywordTok{names}\NormalTok{(data)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
+\KeywordTok{names}\NormalTok{(data56)[}\KeywordTok{names}\NormalTok{(data56)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
+\KeywordTok{names}\NormalTok{(data78)[}\KeywordTok{names}\NormalTok{(data78)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
 
-\CommentTok{# Extract the data we needed ----------------------------------------------}
-\NormalTok{df14d <-}\StringTok{ }\NormalTok{data[, }\KeywordTok{c}\NormalTok{(}\DecValTok{113}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{, }\DecValTok{3}\NormalTok{, }\DecValTok{5}\NormalTok{, }\DecValTok{6}\NormalTok{, }\DecValTok{7}\NormalTok{, }\DecValTok{8}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{21}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{55}\NormalTok{, }\DecValTok{57}\NormalTok{, }\DecValTok{58}\NormalTok{, }
-    \DecValTok{59}\NormalTok{, }\DecValTok{60}\NormalTok{, }\DecValTok{61}\NormalTok{, }\DecValTok{62}\NormalTok{, }\DecValTok{63}\NormalTok{, }\DecValTok{64}\NormalTok{)]}
+\CommentTok{# Extract the variables needed -------------------------------------------}
+\NormalTok{df14d <-}\StringTok{ }\NormalTok{data[,}\KeywordTok{c}\NormalTok{(}\DecValTok{113}\NormalTok{,}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{5}\NormalTok{,}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{,}\DecValTok{8}\NormalTok{,}\DecValTok{9}\NormalTok{,}\DecValTok{21}\NormalTok{, }\DecValTok{22}\NormalTok{, }\DecValTok{23}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{53}\NormalTok{, }\DecValTok{55}\NormalTok{,}
+\DecValTok{57}\NormalTok{,}\DecValTok{58}\NormalTok{,}\DecValTok{59}\NormalTok{,}\DecValTok{60}\NormalTok{,}\DecValTok{61}\NormalTok{,}\DecValTok{62}\NormalTok{,}\DecValTok{63}\NormalTok{,}\DecValTok{64}\NormalTok{,}\DecValTok{65}\NormalTok{)]}
 \NormalTok{var <-}\StringTok{ }\KeywordTok{names}\NormalTok{(df14d)}
-\NormalTok{df56d <-}\StringTok{ }\NormalTok{data56 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(var)}
-\NormalTok{df78d <-}\StringTok{ }\NormalTok{data78 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(var)}
+\NormalTok{df56d <-}\StringTok{ }\NormalTok{data56 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
+\NormalTok{df78d <-}\StringTok{ }\NormalTok{data78 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
 \NormalTok{dfs1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(df14d, df56d, df78d)}
-\NormalTok{dfs2 <-}\StringTok{ }\NormalTok{dfs1[dfs1}\OperatorTok{$}\NormalTok{Age }\OperatorTok{>=}\StringTok{ }\DecValTok{19}\NormalTok{, ]}
-\KeywordTok{rm}\NormalTok{(data, data56, data78)}
+
+\NormalTok{dfs2 <-}\StringTok{ }\NormalTok{dfs1[dfs1}\OperatorTok{$}\NormalTok{Age}\OperatorTok{>=}\DecValTok{19}\NormalTok{,] }\CommentTok{# keep participants who aged 19 or older}
+\KeywordTok{rm}\NormalTok{(data, data56, data78) }\CommentTok{# remove the unneeded big dataset}
+
 \NormalTok{dfs2}
@@
 \NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_chr <-}\StringTok{ }\KeywordTok{as.character}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime)}
-\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_hm <-}\StringTok{ }\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_chr, }\StringTok{" "}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }
+\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_hm <-}\StringTok{ }\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_chr,}\StringTok{" "}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }
             \OtherTok{TRUE}\NormalTok{)]}
-\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm, }\StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{TRUE}\NormalTok{, }
-    \OtherTok{FALSE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
-\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm, }\StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }
-    \OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
-\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN0 <-}\StringTok{ }\NormalTok{(}\DecValTok{60} \OperatorTok{*}\StringTok{ }\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN) }\OperatorTok{+}\StringTok{ }\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN}
-\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs2[}\KeywordTok{order}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{id, dfs2}\OperatorTok{$}\NormalTok{DayNo, dfs2}\OperatorTok{$}\NormalTok{MealMinN0), ]}
+\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm,}
+			\StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
+\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm,}
+				\StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }\OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
+
+\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN0 <-}\StringTok{ }\NormalTok{(}\DecValTok{60}\OperatorTok{*}\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN)}\OperatorTok{+}\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN}
+
+\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs2[}\KeywordTok{order}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{id,dfs2}\OperatorTok{$}\NormalTok{DayNo,dfs2}\OperatorTok{$}\NormalTok{MealMinN0),]}
+
 \KeywordTok{length}\NormalTok{(}\KeywordTok{unique}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id)) ## number of participants = 6155}
 
-\CommentTok{# Create a subset data with only the first observation of each}
-\CommentTok{# participant --------}
+\CommentTok{# Create a subset data with only the first observation of each participant --------}
+
 \NormalTok{NDNS <-}\StringTok{ }\NormalTok{dfs3[}\OperatorTok{!}\KeywordTok{duplicated}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id), ]}
 \KeywordTok{with}\NormalTok{(NDNS, }\KeywordTok{tab1}\NormalTok{(SurveyYear, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{decimal =} \DecValTok{2}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
 
-\CommentTok{# #SurveyYear :}
-            \CommentTok{# Frequency Percent Cum. percent}
-\CommentTok{# NDNS Year 1       801   13.01        13.01}
-\CommentTok{# NDNS Year 2       812   13.19        26.21}
-\CommentTok{# NDNS Year 3       782   12.71        38.91}
-\CommentTok{# NDNS Year 4      1055   17.14        56.05}
-\CommentTok{# NDNS Year 5       625   10.15        66.21}
-\CommentTok{# NDNS Year 6       663   10.77        76.98}
-\CommentTok{# NDNS Year 7       703   11.42        88.40}
-\CommentTok{# NDNS Year 8       714   11.60       100.00}
-  \CommentTok{# Total          6155  100.00       100.00}
+				\begin{verbatim}
+				# #SurveyYear : 
+				#             Frequency Percent Cum. percent
+				# NDNS Year 1       801   13.01        13.01
+				# NDNS Year 2       812   13.19        26.21
+				# NDNS Year 3       782   12.71        38.91
+				# NDNS Year 4      1055   17.14        56.05
+				# NDNS Year 5       625   10.15        66.21
+				# NDNS Year 6       663   10.77        76.98
+				# NDNS Year 7       703   11.42        88.40
+				# NDNS Year 8       714   11.60       100.00
+				#   Total          6155  100.00       100.00
+				\end{verbatim}
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# how many men and women --------------------------------------------------}
+
+\KeywordTok{with}\NormalTok{(NDNS, }\KeywordTok{tab1}\NormalTok{(Sex, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{decimal =} \DecValTok{2}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+				\begin{verbatim}
+				# Sex : 
+				#          Frequency Percent Cum. percent
+				# 1            2537   41.22        41.22 Men
+				# 2            3618   58.78       100.00 Women
+				#   Total      6155  100.00       100.00
+				\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
 \CommentTok{# create a variable combine id and day No ---------------------------------}
-\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs3 }\OperatorTok{%>%}
-\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{id_dy =} \KeywordTok{paste}\NormalTok{(id, DayNo, }\DataTypeTok{sep =} \StringTok{"D"}\NormalTok{))}
 
-\CommentTok{# For each subject, the total energy/carbohydrate intake for each eating }
-\CommentTok{# time can be calculated --------}
-\NormalTok{old <-}\StringTok{ }\KeywordTok{Sys.time}\NormalTok{()}
+\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs3 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{id_dy =} \KeywordTok{paste}\NormalTok{(id, DayNo, }\DataTypeTok{sep =} \StringTok{"D"}\NormalTok{))}
+
+\CommentTok{# For each subject, the total energy/carbohydrate intake for each }
+\CommentTok{# eating time can be calculated --------}
+
+\NormalTok{old<-}\KeywordTok{Sys.time}\NormalTok{()}
 \NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(dfs3, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
 \NormalTok{                        DiaryDaysCompleted, MealHourN, DayofWeek),  }
-\NormalTok{                summarise, }
-                \DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(EnergykJ), }
+\NormalTok{                summarise, }\DataTypeTok{Tot_Energ =}\KeywordTok{sum}\NormalTok{(EnergykJ), }
                     \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Carbohydrateg), }
                     \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Totalsugarsg), }
-                \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Starchg))}
-\NormalTok{new <-}\StringTok{ }\KeywordTok{Sys.time}\NormalTok{() }\OperatorTok{-}\StringTok{ }\NormalTok{old}
+                    \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Starchg), }
+                    \DataTypeTok{Tot_Fibre =} \KeywordTok{sum}\NormalTok{(Englystfibreg),}
+                    \DataTypeTok{Tot_Fat   =} \KeywordTok{sum}\NormalTok{(Fatg), }
+                    \DataTypeTok{Tot_Prot  =} \KeywordTok{sum}\NormalTok{(Proteing), }
+                    \DataTypeTok{Tot_Alc   =} \KeywordTok{sum}\NormalTok{(Alcoholg), }
+                    \DataTypeTok{Tot_NMES  =} \KeywordTok{sum}\NormalTok{(Nonmilkextrinsicsugarsg))}
+\NormalTok{new<-}\KeywordTok{Sys.time}\NormalTok{()}\OperatorTok{-}\NormalTok{old}
 \KeywordTok{print}\NormalTok{(new)}
-\CommentTok{# Time difference of 3.876385 mins}
+\CommentTok{# Time difference of 6.429822 min}
 
-\KeywordTok{rm}\NormalTok{(df14d, df56d, df78d, dfs2)}
+\CommentTok{# reset the time intervals into time slots --------------------------------}
+
+\NormalTok{### Breakfast:       6am to 9am}
+\NormalTok{### morning snack:   9am to 12noon}
+\NormalTok{### lunch:           12noon to 2pm}
+\NormalTok{### afternoon snack: 2pm to 5pm}
+\NormalTok{### dinner:          5pm to 8pm}
+\NormalTok{### night snack:     8pm to 10pm}
+\NormalTok{### midnight:        10pm to 6am}
+\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{TimeSlot =} \KeywordTok{cut}\NormalTok{(MealHourN, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{12}\NormalTok{, }\DecValTok{14}\NormalTok{, }\DecValTok{17}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{22}\NormalTok{), }
+				\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
+\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot), }\StringTok{"[22, 6)"}\NormalTok{)}
+\NormalTok{Energy}\OperatorTok{$}\NormalTok{TimeSlot[}\KeywordTok{is.na}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)] <-}\StringTok{ "[22, 6)"}
+\KeywordTok{tab1}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)}
+\CommentTok{# For each subject, the total energy/carbohydrate intake for each }
+\CommentTok{# time slot can be calculated --------}
+\NormalTok{old<-}\KeywordTok{Sys.time}\NormalTok{()}
+\NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(Energy, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
+\NormalTok{                          DiaryDaysCompleted, TimeSlot, DayofWeek),  }
+\NormalTok{                summarise, }
+              \DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(Tot_Energ), }
+              \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Tot_Carb), }
+              \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Tot_Sugar),}
+              \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Tot_Starch), }
+              \DataTypeTok{Tot_Fibre =} \KeywordTok{sum}\NormalTok{(Tot_Fibre), }
+              \DataTypeTok{Tot_Fat   =} \KeywordTok{sum}\NormalTok{(Tot_Fat), }
+              \DataTypeTok{Tot_Prot  =} \KeywordTok{sum}\NormalTok{(Tot_Prot), }
+              \DataTypeTok{Tot_Alc   =} \KeywordTok{sum}\NormalTok{(Tot_Alc), }
+              \DataTypeTok{Tot_NMES  =} \KeywordTok{sum}\NormalTok{(Tot_NMES))}
+\NormalTok{new<-}\KeywordTok{Sys.time}\NormalTok{()}\OperatorTok{-}\NormalTok{old}
+\KeywordTok{print}\NormalTok{(new)}
+\CommentTok{# Time difference of 3.74195 mins }
 
@@
 \NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{KJcarbo =}\NormalTok{ Tot_Carb }\OperatorTok{*}\StringTok{ }\DecValTok{16}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{KJcarbo =}\NormalTok{ Tot_Carb}\OperatorTok{*}\DecValTok{16}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CarKJpercentage =}\NormalTok{ KJcarbo}\OperatorTok{/}\NormalTok{Tot_Energ) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.26}\NormalTok{, }\FloatTok{0.75}\NormalTok{, }\DecValTok{2}\NormalTok{), }
-        \DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo2 =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }
-    \FloatTok{0.26}\NormalTok{, }\DecValTok{2}\NormalTok{), }\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
-\NormalTok{Energy0 <-}\StringTok{ }\NormalTok{Energy[}\OperatorTok{!}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{Tot_Energ }\OperatorTok{==}\StringTok{ }\DecValTok{0}\NormalTok{), ]  }
-          \CommentTok{# some food consumption does not contain any carbohydrates}
-\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Low_carb"}\NormalTok{, }\StringTok{"Med_carb"}\NormalTok{, }
-    \StringTok{"High_carb"}\NormalTok{))}
-\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo2 <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo2, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Low_carb"}\NormalTok{, }\StringTok{"Med_or_high_carb"}\NormalTok{))}
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.50}\NormalTok{, }\DecValTok{2}\NormalTok{), }\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
 
-\CommentTok{# Generate data sets for each day ----------------------------------------------------------}
+\NormalTok{Energy0 <-}\StringTok{ }\NormalTok{Energy[}\OperatorTok{!}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{Tot_Energ }\OperatorTok{==}\StringTok{ }\DecValTok{0}\NormalTok{), ] }\CommentTok{# discard those eating occassion }
+\CommentTok{# with 0 energy intake }
+\KeywordTok{write.csv}\NormalTok{(Energy0, }\DataTypeTok{file =} \StringTok{"Energy_slots.csv"}\NormalTok{) }\CommentTok{# for later analysis}	
+\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"< 50%"}\NormalTok{, }\StringTok{">= 50%"}\NormalTok{))}
+
+\NormalTok{vecid<-}\KeywordTok{unique}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{id)}
+
+\CommentTok{# Filter the data by observation day--------------------------------------------}
+
 \NormalTok{dta_day1 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
 \StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
-    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
+\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
-    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
-        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
+\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
+\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
+\StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
 
@@
 \StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{2}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
-    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
+\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
-    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
-        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
+\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
+\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
+\StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
 
@@
 \StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
-    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
+\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
-    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
-        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
+\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
+\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
+\StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
 
@@
 \StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
-    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
-    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
-        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
-\NormalTok{vecid1 <-}\StringTok{ }\KeywordTok{unique}\NormalTok{(dta_day1}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
-\NormalTok{vecid2 <-}\StringTok{ }\KeywordTok{unique}\NormalTok{(dta_day2}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
-\NormalTok{vecid3 <-}\StringTok{ }\KeywordTok{unique}\NormalTok{(dta_day3}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6151}
-\NormalTok{vecid4 <-}\StringTok{ }\KeywordTok{unique}\NormalTok{(dta_day4}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6026}
+\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
+\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
+StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
+\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
+\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
+\StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
 
+\NormalTok{vecid1<-}\KeywordTok{unique}\NormalTok{(dta_day1}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
+\NormalTok{vecid2<-}\KeywordTok{unique}\NormalTok{(dta_day2}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
+\NormalTok{vecid3<-}\KeywordTok{unique}\NormalTok{(dta_day3}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6151}
+\NormalTok{vecid4<-}\KeywordTok{unique}\NormalTok{(dta_day4}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6026}
 \NormalTok{Noday1 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid1) }\CommentTok{# two subjects did not have day 1 data}
-\NormalTok{Noday2 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid2)  }\CommentTok{# two subjects did not have day 2 data}
-\NormalTok{Noday3 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid3)  }\CommentTok{# four subjects did not have day 3 data}
+\NormalTok{Noday2 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid2) }\CommentTok{# two subjects did not have day 2 data }
+\NormalTok{Noday3 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid3) }\CommentTok{# four subjects did not have day 3 data }
 \NormalTok{Noday4 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid4) }\CommentTok{# 129 subjects did not have day 4 data}
 
-\CommentTok{# Transform the data shape from long to wide ---------------------------------}
-\NormalTok{dta_d1_wide <-}\StringTok{ }\NormalTok{dta_day1[, }\OperatorTok{-}\DecValTok{7}\NormalTok{] }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ MealHourN, }\DataTypeTok{value =}\NormalTok{ Carbo)}
-\KeywordTok{names}\NormalTok{(dta_d1_wide)[}\DecValTok{5}\OperatorTok{:}\DecValTok{28}\NormalTok{] <-}\StringTok{ }\KeywordTok{paste}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"H"}\NormalTok{, }\DecValTok{24}\NormalTok{), }\DecValTok{0}\OperatorTok{:}\DecValTok{23}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{)}
-
-\NormalTok{dta_d2_wide <-}\StringTok{ }\NormalTok{dta_day2[, }\OperatorTok{-}\DecValTok{7}\NormalTok{] }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ MealHourN, }\DataTypeTok{value =}\NormalTok{ Carbo)}
-\KeywordTok{names}\NormalTok{(dta_d2_wide)[}\DecValTok{5}\OperatorTok{:}\DecValTok{28}\NormalTok{] <-}\StringTok{ }\KeywordTok{paste}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"H"}\NormalTok{, }\DecValTok{24}\NormalTok{), }\DecValTok{0}\OperatorTok{:}\DecValTok{23}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{)}
-
-\NormalTok{dta_d3_wide <-}\StringTok{ }\NormalTok{dta_day3[, }\OperatorTok{-}\DecValTok{7}\NormalTok{] }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ MealHourN, }\DataTypeTok{value =}\NormalTok{ Carbo)}
-\KeywordTok{names}\NormalTok{(dta_d3_wide)[}\DecValTok{5}\OperatorTok{:}\DecValTok{28}\NormalTok{] <-}\StringTok{ }\KeywordTok{paste}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"H"}\NormalTok{, }\DecValTok{24}\NormalTok{), }\DecValTok{0}\OperatorTok{:}\DecValTok{23}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{)}
-
-\NormalTok{dta_d4_wide <-}\StringTok{ }\NormalTok{dta_day4[, }\OperatorTok{-}\DecValTok{7}\NormalTok{] }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ MealHourN, }\DataTypeTok{value =}\NormalTok{ Carbo)}
-\KeywordTok{names}\NormalTok{(dta_d4_wide)[}\DecValTok{5}\OperatorTok{:}\DecValTok{28}\NormalTok{] <-}\StringTok{ }\KeywordTok{paste}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"H"}\NormalTok{, }\DecValTok{24}\NormalTok{), }\DecValTok{0}\OperatorTok{:}\DecValTok{23}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{)}
-
+\CommentTok{# Long to wide data -------------------------------------------------------}
+\NormalTok{dta_d1_wide <-}\StringTok{ }\NormalTok{dta_day1 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+\DataTypeTok{value =}\NormalTok{ Carbo)}
+\KeywordTok{head}\NormalTok{(dta_d1_wide)}
+\KeywordTok{names}\NormalTok{(dta_d1_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
+\StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
+\KeywordTok{names}\NormalTok{(dta_d1_wide)}
+\NormalTok{dta_d2_wide <-}\StringTok{ }\NormalTok{dta_day2 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+\DataTypeTok{value =}\NormalTok{ Carbo)}
+\KeywordTok{head}\NormalTok{(dta_d2_wide)}
+\KeywordTok{names}\NormalTok{(dta_d2_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
+\StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
+\KeywordTok{names}\NormalTok{(dta_d2_wide)}
+\NormalTok{dta_d3_wide <-}\StringTok{ }\NormalTok{dta_day3 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+\DataTypeTok{value =}\NormalTok{ Carbo)}
+\KeywordTok{head}\NormalTok{(dta_d3_wide)}
+\KeywordTok{names}\NormalTok{(dta_d3_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
+\StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
+\KeywordTok{names}\NormalTok{(dta_d3_wide)}
+\NormalTok{dta_d4_wide <-}\StringTok{ }\NormalTok{dta_day4 }\OperatorTok{%>%}\StringTok{ }
+\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
+\DataTypeTok{value =}\NormalTok{ Carbo)}
+\KeywordTok{head}\NormalTok{(dta_d4_wide)}
+\KeywordTok{names}\NormalTok{(dta_d4_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
+\StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
+\KeywordTok{names}\NormalTok{(dta_d4_wide)}
 \CommentTok{# recode NA to not eating -------------------------------------------------}
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{5}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d1_wide)) }
-  \ControlFlowTok{if}\NormalTok{ (}\KeywordTok{is.factor}\NormalTok{(dta_d1_wide[, i])) }\KeywordTok{levels}\NormalTok{(dta_d1_wide[, }
-\NormalTok{    i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(dta_d1_wide[, i]), }\StringTok{"Not_eating"}\NormalTok{)}
-
-\NormalTok{dta_d1_wide[}\KeywordTok{is.na}\NormalTok{(dta_d1_wide)] <-}\StringTok{ "Not_eating"}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{5}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d2_wide)) }
-  \ControlFlowTok{if}\NormalTok{ (}\KeywordTok{is.factor}\NormalTok{(dta_d2_wide[, i])) }\KeywordTok{levels}\NormalTok{(dta_d2_wide[, }
-\NormalTok{    i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(dta_d2_wide[, i]), }\StringTok{"Not_eating"}\NormalTok{)}
-
-\NormalTok{dta_d2_wide[}\KeywordTok{is.na}\NormalTok{(dta_d2_wide)] <-}\StringTok{ "Not_eating"}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{5}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d3_wide)) }
-  \ControlFlowTok{if}\NormalTok{ (}\KeywordTok{is.factor}\NormalTok{(dta_d3_wide[, i])) }\KeywordTok{levels}\NormalTok{(dta_d3_wide[, }
-\NormalTok{    i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(dta_d3_wide[, i]), }\StringTok{"Not_eating"}\NormalTok{)}
-
-\NormalTok{dta_d3_wide[}\KeywordTok{is.na}\NormalTok{(dta_d3_wide)] <-}\StringTok{ "Not_eating"}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{5}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d4_wide)) }
-  \ControlFlowTok{if}\NormalTok{ (}\KeywordTok{is.factor}\NormalTok{(dta_d4_wide[, i])) }\KeywordTok{levels}\NormalTok{(dta_d4_wide[, }
-\NormalTok{    i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(dta_d4_wide[, i]), }\StringTok{"Not_eating"}\NormalTok{)}
-
-\NormalTok{dta_d4_wide[}\KeywordTok{is.na}\NormalTok{(dta_d4_wide)] <-}\StringTok{ "Not_eating"}
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{6}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d1_wide)) }
+\ControlFlowTok{if}\NormalTok{(}\KeywordTok{is.factor}\NormalTok{(dta_d1_wide[,i])) }
+\KeywordTok{levels}\NormalTok{(dta_d1_wide[,i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2"}\NormalTok{, }\StringTok{"0"}\NormalTok{)}
+\NormalTok{dta_d1_wide[}\KeywordTok{is.na}\NormalTok{(dta_d1_wide)] <-}\StringTok{ "0"}
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{6}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d2_wide)) }
+\ControlFlowTok{if}\NormalTok{(}\KeywordTok{is.factor}\NormalTok{(dta_d2_wide[,i])) }
+\KeywordTok{levels}\NormalTok{(dta_d2_wide[,i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2"}\NormalTok{,  }\StringTok{"0"}\NormalTok{)}
+\NormalTok{dta_d2_wide[}\KeywordTok{is.na}\NormalTok{(dta_d2_wide)] <-}\StringTok{ "0"}
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{6}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d3_wide)) }
+\ControlFlowTok{if}\NormalTok{(}\KeywordTok{is.factor}\NormalTok{(dta_d3_wide[,i])) }
+\KeywordTok{levels}\NormalTok{(dta_d3_wide[,i]) <-}\StringTok{  }\KeywordTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2"}\NormalTok{, }\StringTok{"0"}\NormalTok{)}
+\NormalTok{dta_d3_wide[}\KeywordTok{is.na}\NormalTok{(dta_d3_wide)] <-}\StringTok{ "0"}
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{6}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d4_wide)) }
+\ControlFlowTok{if}\NormalTok{(}\KeywordTok{is.factor}\NormalTok{(dta_d4_wide[,i])) }
+\KeywordTok{levels}\NormalTok{(dta_d4_wide[,i]) <-}\StringTok{  }\KeywordTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2"}\NormalTok{, }\StringTok{"0"}\NormalTok{)}
+\NormalTok{dta_d4_wide[}\KeywordTok{is.na}\NormalTok{(dta_d4_wide)] <-}\StringTok{ "0"}
+\NormalTok{dta_all <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(dta_d1_wide, dta_d2_wide, dta_d3_wide, dta_d4_wide)}
+\NormalTok{dta_all <-}\StringTok{ }\NormalTok{dta_all[}\KeywordTok{order}\NormalTok{(dta_all}\OperatorTok{$}\NormalTok{id,dta_all}\OperatorTok{$}\NormalTok{id_dy),]}
+\CommentTok{# Export the data for Mplus -------------------------------------------------}
+\KeywordTok{write_csv}\NormalTok{(dta_all, }\DataTypeTok{path =} \StringTok{"NDNS_Tslots.csv"}\NormalTok{)}
+\KeywordTok{write_delim}\NormalTok{(dta_all, }\StringTok{"NDNS_Tslots.dat"}\NormalTok{, }\DataTypeTok{na =} \StringTok{"."}\NormalTok{, }\DataTypeTok{delim =} \StringTok{" "}\NormalTok{)}
 \end{Highlighting}
 \end{Shaded}
-
-%\section{How do I change the colors of links?}
-%
-%The color of links can be changed to your liking using:
-%
-%{\small\verb!\hypersetup{urlcolor=red}!}, or
-%
-%{\small\verb!\hypersetup{citecolor=green}!}, or
-%
-%{\small\verb!\hypersetup{allcolor=blue}!}.
-%
-%\noindent If you want to completely hide the links, you can use:
-%
-%{\small\verb!\hypersetup{allcolors=.}!}, or even better:
-%
-%{\small\verb!\hypersetup{hidelinks}!}.
-%
-%\noindent If you want to have obvious links in the PDF but not %the printed text, use:
-%
-%{\small\verb!\hypersetup{colorlinks=false}!}.

### 2018-08-17 paper/Appendices/AppendixC.tex
appendix C figlevel 1 CW4

@@
 
-\chapter{Example of a food diary for one day} % Main appendix title
+\chapter{Other Solutions for MLCA} % Main appendix title
+
+\section{2 classes in day level}
 
 \label{AppendixC} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}
-%\begin{verbatim}
 
@@
 	\centering
-\includegraphics{Figures/Diary1.png}
+	\includegraphics{Figures/CW2level1.png}
 	\decoRule
-\caption[One day food diary example 6 am to 2 pm]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, from 6 am to 2 pm.}
+	\caption[2 Classes solution in Day level]{2 Classes solution in Day level.}
 	\label{fig:diary1}
 \end{figure}
-%\end{verbatim}
 
@@
 	\centering
-\includegraphics{Figures/Diary2.png}
+	\includegraphics[width=13cm]{Figures/CW2CB2.png}
 	\decoRule
-\caption[One day food diary example 2 pm to 6 am]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, from 2 pm to 6 am.}
-\label{fig:diary2}
+	\caption[Multilevel Latent Class Solution (2 $\times$ 2).]{Multilevel Latent Class Solution, 2 classes in day level, 2 classes in individual level.}
+	\label{fig:diary1}
 \end{figure}
-%\end{verbatim}
 
@@
 	\centering
-\includegraphics{Figures/Diary3.png}
+	\includegraphics[width=13cm]{Figures/CW2CB3.png}
 	\decoRule
-\caption[Food diary example of home made food recipes]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, home made food recipes.}
-\label{fig:diary3}
+	\caption[Multilevel Latent Class Solution (2 $\times$ 3).]{Multilevel Latent Class Solution, 2 classes in day level, 3 classes in individual level.}
+	\label{fig:diary1}
 \end{figure}
+
+\begin{figure}[H]
+	%\vspace*{13cm}
+	\centering
+	\includegraphics[width=13cm]{Figures/CW2CB4.png}
+	\decoRule
+	\caption[Multilevel Latent Class Solution (2 $\times$ 4).]{Multilevel Latent Class Solution, 2 classes in day level, 4 classes in individual level.}
+	\label{fig:diary1}
+\end{figure}
+
+\section{3 classes in day level, 4 classes in individual level}\vspace{-0.3cm}
+
+\begin{figure}[H]
+	%\vspace*{13cm}
+	\centering
+	\includegraphics[width=13cm]{Figures/CW3CB4.png}
+	\decoRule
+	\caption[Multilevel Latent Class Solution (3 $\times$ 4).]{Multilevel Latent Class Solution, 3 classes in day level, 4 classes in individual level.}
+	\label{fig:diary1}
+\end{figure}
+
+\section{4 classes in day level}
+
+\begin{figure}[H]
+	%\vspace*{13cm}
+	\centering
+	\includegraphics[width=15cm]{Figures/CW4level1.png}
+	\decoRule
+	\caption[2 Classes Solution in Day level]{4 Classes Solution in Day level.}
+	\label{fig:diary1}
+\end{figure}

### 2018-08-17 paper/Appendices/AppendixD.tex
appendix C figlevel 1 CW4

--- 2018-08-17 paper/Appendices/Appendix0_10.tex
@@
-\documentclass[]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\usepackage[margin=1in]{geometry}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
-            pdftitle={Appendix0\_10},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{255,255,255}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.67,0.33,0.00}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.57,0.30,0.62}{#1}}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.24,0.68,0.91}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{1.00,0.33,0.00}{#1}}
-\newcommand{\ImportTok}[1]{\textcolor[rgb]{1.00,0.33,0.00}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.54,0.53,0.53}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.38,0.47,0.50}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.79,0.38,0.79}{#1}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.00,0.58,1.00}{#1}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.43,0.16}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.39,0.29,0.61}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{\textbf{#1}}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{#1}}
-\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.39,0.29,0.61}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.58,1.00}{\textbf{#1}}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.00,0.43,0.16}{#1}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
-\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{\textbf{#1}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{\underline{#1}}}
-\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{#1}}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\newcommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
-
-  \title{Appendix0\_10}
-    \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-    \author{}
-    \preauthor{}\postauthor{}
-    \date{}
-    \predate{}\postdate{}
-
-\begin{document}
-\maketitle
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# NDNS analysis, data management ------------------------------------------}
-
-\CommentTok{# Change the data path accordingly ----------------------------------------}
-
-\KeywordTok{setwd}\NormalTok{(}\StringTok{".../UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }
-\KeywordTok{setwd}\NormalTok{(}\StringTok{"~/Downloads/UKDA-6533-stata11_se/stata11_se/"}\NormalTok{)}
-
-\KeywordTok{library}\NormalTok{(epiDisplay)}
-\KeywordTok{library}\NormalTok{(plyr)}
-\KeywordTok{library}\NormalTok{(tidyverse)}
-
-\CommentTok{# Read the data into memory -----------------------------------------------}
-
-\KeywordTok{library}\NormalTok{(haven)}
-\NormalTok{data <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr1-4a_foodleveldietarydata_uk.dta"}\NormalTok{)}
-\NormalTok{data56 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr5-6a_foodleveldietarydata.dta"}\NormalTok{)}
-\NormalTok{data78 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr7-8a_foodleveldietarydata.dta"}\NormalTok{)}
-
-\KeywordTok{names}\NormalTok{(data)}
-\KeywordTok{names}\NormalTok{(data56)}
-\KeywordTok{names}\NormalTok{(data78)}
-\KeywordTok{names}\NormalTok{(data)[}\KeywordTok{names}\NormalTok{(data)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
-\KeywordTok{names}\NormalTok{(data56)[}\KeywordTok{names}\NormalTok{(data56)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
-\KeywordTok{names}\NormalTok{(data78)[}\KeywordTok{names}\NormalTok{(data78)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
-
-\CommentTok{# Extract the variables needed -------------------------------------------}
-
-\NormalTok{df14d <-}\StringTok{ }\NormalTok{data[,}\KeywordTok{c}\NormalTok{(}\DecValTok{113}\NormalTok{,}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{5}\NormalTok{,}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{,}\DecValTok{8}\NormalTok{,}\DecValTok{9}\NormalTok{,}\DecValTok{21}\NormalTok{, }\DecValTok{22}\NormalTok{, }\DecValTok{23}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{53}\NormalTok{, }\DecValTok{55}\NormalTok{,}
-                 \DecValTok{57}\NormalTok{,}\DecValTok{58}\NormalTok{,}\DecValTok{59}\NormalTok{,}\DecValTok{60}\NormalTok{,}\DecValTok{61}\NormalTok{,}\DecValTok{62}\NormalTok{,}\DecValTok{63}\NormalTok{,}\DecValTok{64}\NormalTok{,}\DecValTok{65}\NormalTok{)]}
-\NormalTok{var <-}\StringTok{ }\KeywordTok{names}\NormalTok{(df14d)}
-\NormalTok{df56d <-}\StringTok{ }\NormalTok{data56 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
-\NormalTok{df78d <-}\StringTok{ }\NormalTok{data78 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
-\NormalTok{dfs1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(df14d, df56d, df78d)}
-
-\NormalTok{dfs2 <-}\StringTok{ }\NormalTok{dfs1[dfs1}\OperatorTok{$}\NormalTok{Age}\OperatorTok{>=}\DecValTok{19}\NormalTok{,] }\CommentTok{# keep participants who aged 19 or older}
-\KeywordTok{rm}\NormalTok{(data, data56, data78) }\CommentTok{# remove the unneeded big dataset}
-
-\NormalTok{dfs2}
-
-\CommentTok{# Calculate the time (minute and hour) when they eat ----------------------}
-
-\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_chr <-}\StringTok{ }\KeywordTok{as.character}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime)}
-\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_hm <-}\StringTok{ }\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_chr,}\StringTok{" "}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }
-                                                              \OtherTok{TRUE}\NormalTok{)]}
-\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm,}
-                                             \StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
-\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm,}
-                                            \StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }\OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
-
-\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN0 <-}\StringTok{ }\NormalTok{(}\DecValTok{60}\OperatorTok{*}\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN)}\OperatorTok{+}\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN}
-
-\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs2[}\KeywordTok{order}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{id,dfs2}\OperatorTok{$}\NormalTok{DayNo,dfs2}\OperatorTok{$}\NormalTok{MealMinN0),]}
-
-\KeywordTok{length}\NormalTok{(}\KeywordTok{unique}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id)) ## number of participants = 6155}
-
-\CommentTok{# Create a subset data with only the first observation of each participant --------}
-
-\NormalTok{NDNS <-}\StringTok{ }\NormalTok{dfs3[}\OperatorTok{!}\KeywordTok{duplicated}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id), ]}
-\KeywordTok{with}\NormalTok{(NDNS, }\KeywordTok{tab1}\NormalTok{(SurveyYear, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{decimal =} \DecValTok{2}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# #SurveyYear : 
-#             Frequency Percent Cum. percent
-# NDNS Year 1       801   13.01        13.01
-# NDNS Year 2       812   13.19        26.21
-# NDNS Year 3       782   12.71        38.91
-# NDNS Year 4      1055   17.14        56.05
-# NDNS Year 5       625   10.15        66.21
-# NDNS Year 6       663   10.77        76.98
-# NDNS Year 7       703   11.42        88.40
-# NDNS Year 8       714   11.60       100.00
-#   Total          6155  100.00       100.00
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# how many men and women --------------------------------------------------}
-
-\KeywordTok{with}\NormalTok{(NDNS, }\KeywordTok{tab1}\NormalTok{(Sex, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{decimal =} \DecValTok{2}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# Sex : 
-#          Frequency Percent Cum. percent
-# 1            2537   41.22        41.22 Men
-# 2            3618   58.78       100.00 Women
-#   Total      6155  100.00       100.00
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# create a variable combine id and day No ---------------------------------}
-
-\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs3 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{id_dy =} \KeywordTok{paste}\NormalTok{(id, DayNo, }\DataTypeTok{sep =} \StringTok{"D"}\NormalTok{))}
-
-\CommentTok{# For each subject, the total energy/carbohydrate intake for each }
-\CommentTok{# eating time can be calculated --------}
-
-\NormalTok{old<-}\KeywordTok{Sys.time}\NormalTok{()}
-\NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(dfs3, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
-\NormalTok{                        DiaryDaysCompleted, MealHourN, DayofWeek),  }
-\NormalTok{                summarise, }\DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(EnergykJ), }
-                \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Carbohydrateg), }
-                \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Totalsugarsg), }
-                \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Starchg), }
-                \DataTypeTok{Tot_Fibre =} \KeywordTok{sum}\NormalTok{(Englystfibreg),}
-                \DataTypeTok{Tot_Fat   =} \KeywordTok{sum}\NormalTok{(Fatg), }
-                \DataTypeTok{Tot_Prot  =} \KeywordTok{sum}\NormalTok{(Proteing), }
-                \DataTypeTok{Tot_Alc   =} \KeywordTok{sum}\NormalTok{(Alcoholg), }
-                \DataTypeTok{Tot_NMES  =} \KeywordTok{sum}\NormalTok{(Nonmilkextrinsicsugarsg))}
-\NormalTok{new<-}\KeywordTok{Sys.time}\NormalTok{()}\OperatorTok{-}\NormalTok{old}
-\KeywordTok{print}\NormalTok{(new)}
-\CommentTok{# Time difference of 6.429822 min}
-
-\CommentTok{# reset the time intervals into time slots --------------------------------}
-
-\NormalTok{### Breakfast:       6am to 9am}
-\NormalTok{### morning snack:   9am to 12noon}
-\NormalTok{### lunch:           12noon to 2pm}
-\NormalTok{### afternoon snack: 2pm to 5pm}
-\NormalTok{### dinner:          5pm to 8pm}
-\NormalTok{### night snack:     8pm to 10pm}
-\NormalTok{### midnight:        10pm to 6am}
-
-\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{TimeSlot =} \KeywordTok{cut}\NormalTok{(MealHourN, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{12}\NormalTok{, }\DecValTok{14}\NormalTok{, }\DecValTok{17}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{22}\NormalTok{), }
-                        \DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
-
-\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot), }\StringTok{"[22, 6)"}\NormalTok{)}
-
-\NormalTok{Energy}\OperatorTok{$}\NormalTok{TimeSlot[}\KeywordTok{is.na}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)] <-}\StringTok{ "[22, 6)"}
-
-\KeywordTok{tab1}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)}
-
-\CommentTok{# For each subject, the total energy/carbohydrate intake for each }
-\CommentTok{# time slot can be calculated --------}
-\NormalTok{old<-}\KeywordTok{Sys.time}\NormalTok{()}
-\NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(Energy, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
-\NormalTok{                          DiaryDaysCompleted, TimeSlot, DayofWeek),  }
-\NormalTok{                summarise, }
-                \DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(Tot_Energ), }
-                \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Tot_Carb), }
-                \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Tot_Sugar),}
-                \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Tot_Starch), }
-                \DataTypeTok{Tot_Fibre =} \KeywordTok{sum}\NormalTok{(Tot_Fibre), }
-                \DataTypeTok{Tot_Fat   =} \KeywordTok{sum}\NormalTok{(Tot_Fat), }
-                \DataTypeTok{Tot_Prot  =} \KeywordTok{sum}\NormalTok{(Tot_Prot), }
-                \DataTypeTok{Tot_Alc   =} \KeywordTok{sum}\NormalTok{(Tot_Alc), }
-                \DataTypeTok{Tot_NMES  =} \KeywordTok{sum}\NormalTok{(Tot_NMES))}
-\NormalTok{new<-}\KeywordTok{Sys.time}\NormalTok{()}\OperatorTok{-}\NormalTok{old}
-\KeywordTok{print}\NormalTok{(new)}
-\CommentTok{# Time difference of 3.74195 mins }
-
-\CommentTok{# Calculate the energy from total carbohydrates ---------------------------}
-
-\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{KJcarbo =}\NormalTok{ Tot_Carb}\OperatorTok{*}\DecValTok{16}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CarKJpercentage =}\NormalTok{ KJcarbo}\OperatorTok{/}\NormalTok{Tot_Energ) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.50}\NormalTok{, }\DecValTok{2}\NormalTok{), }\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
-
-\NormalTok{Energy0 <-}\StringTok{ }\NormalTok{Energy[}\OperatorTok{!}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{Tot_Energ }\OperatorTok{==}\StringTok{ }\DecValTok{0}\NormalTok{), ] }\CommentTok{# discard those eating occassion }
-\CommentTok{# with 0 energy intake }
-\KeywordTok{write.csv}\NormalTok{(Energy0, }\DataTypeTok{file =} \StringTok{"Energy_slots.csv"}\NormalTok{) }\CommentTok{# for later analysis}
-
-\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"< 50%"}\NormalTok{, }\StringTok{">= 50%"}\NormalTok{))}
-
-\NormalTok{vecid<-}\KeywordTok{unique}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{id)}
-
-\CommentTok{# Filter the data by observation day--------------------------------------------}
-
-\NormalTok{dta_day1 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
-           \StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
-                            \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
-                                       \StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
-                                       \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
-
-\NormalTok{dta_day2 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{2}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
-           \StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
-                            \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
-                                       \StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
-                                       \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
-
-\NormalTok{dta_day3 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
-           \StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
-                            \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
-                                       \StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
-                                       \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
-
-\NormalTok{dta_day4 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
-           \StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
-                            \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
-                                       \StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
-                                       \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}
-
-\NormalTok{vecid1<-}\KeywordTok{unique}\NormalTok{(dta_day1}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
-\NormalTok{vecid2<-}\KeywordTok{unique}\NormalTok{(dta_day2}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
-\NormalTok{vecid3<-}\KeywordTok{unique}\NormalTok{(dta_day3}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6151}
-\NormalTok{vecid4<-}\KeywordTok{unique}\NormalTok{(dta_day4}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6026}
-
-\NormalTok{Noday1 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid1) }\CommentTok{# two subjects did not have day 1 data}
-
-\NormalTok{Noday2 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid2) }\CommentTok{# two subjects did not have day 2 data }
-
-\NormalTok{Noday3 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid3) }\CommentTok{# four subjects did not have day 3 data }
-
-\NormalTok{Noday4 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid4) }\CommentTok{# 129 subjects did not have day 4 data}
-
-\CommentTok{# Long to wide data -------------------------------------------------------}
-
-\NormalTok{dta_d1_wide <-}\StringTok{ }\NormalTok{dta_day1 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
-         \DataTypeTok{value =}\NormalTok{ Carbo)}
-
-\KeywordTok{head}\NormalTok{(dta_d1_wide)}
-\KeywordTok{names}\NormalTok{(dta_d1_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
-                              \StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
-\KeywordTok{names}\NormalTok{(dta_d1_wide)}
-
-\NormalTok{dta_d2_wide <-}\StringTok{ }\NormalTok{dta_day2 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
-         \DataTypeTok{value =}\NormalTok{ Carbo)}
-
-\KeywordTok{head}\NormalTok{(dta_d2_wide)}
-\KeywordTok{names}\NormalTok{(dta_d2_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
-                              \StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
-\KeywordTok{names}\NormalTok{(dta_d2_wide)}
-
-\NormalTok{dta_d3_wide <-}\StringTok{ }\NormalTok{dta_day3 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
-         \DataTypeTok{value =}\NormalTok{ Carbo)}
-
-\KeywordTok{head}\NormalTok{(dta_d3_wide)}
-\KeywordTok{names}\NormalTok{(dta_d3_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
-                              \StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
-\KeywordTok{names}\NormalTok{(dta_d3_wide)}
-
-\NormalTok{dta_d4_wide <-}\StringTok{ }\NormalTok{dta_day4 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
-         \DataTypeTok{value =}\NormalTok{ Carbo)}
-
-\KeywordTok{head}\NormalTok{(dta_d4_wide)}
-\KeywordTok{names}\NormalTok{(dta_d4_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
-                              \StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
-\KeywordTok{names}\NormalTok{(dta_d4_wide)}
-
-\CommentTok{# recode NA to not eating -------------------------------------------------}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{6}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d1_wide)) }
-  \ControlFlowTok{if}\NormalTok{(}\KeywordTok{is.factor}\NormalTok{(dta_d1_wide[,i])) }
-    \KeywordTok{levels}\NormalTok{(dta_d1_wide[,i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2"}\NormalTok{, }\StringTok{"0"}\NormalTok{)}
-
-\NormalTok{dta_d1_wide[}\KeywordTok{is.na}\NormalTok{(dta_d1_wide)] <-}\StringTok{ "0"}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{6}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d2_wide)) }
-  \ControlFlowTok{if}\NormalTok{(}\KeywordTok{is.factor}\NormalTok{(dta_d2_wide[,i])) }
-    \KeywordTok{levels}\NormalTok{(dta_d2_wide[,i]) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2"}\NormalTok{,  }\StringTok{"0"}\NormalTok{)}
-
-\NormalTok{dta_d2_wide[}\KeywordTok{is.na}\NormalTok{(dta_d2_wide)] <-}\StringTok{ "0"}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{6}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d3_wide)) }
-  \ControlFlowTok{if}\NormalTok{(}\KeywordTok{is.factor}\NormalTok{(dta_d3_wide[,i])) }
-    \KeywordTok{levels}\NormalTok{(dta_d3_wide[,i]) <-}\StringTok{  }\KeywordTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2"}\NormalTok{, }\StringTok{"0"}\NormalTok{)}
-
-\NormalTok{dta_d3_wide[}\KeywordTok{is.na}\NormalTok{(dta_d3_wide)] <-}\StringTok{ "0"}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{6}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(dta_d4_wide)) }
-  \ControlFlowTok{if}\NormalTok{(}\KeywordTok{is.factor}\NormalTok{(dta_d4_wide[,i])) }
-    \KeywordTok{levels}\NormalTok{(dta_d4_wide[,i]) <-}\StringTok{  }\KeywordTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2"}\NormalTok{, }\StringTok{"0"}\NormalTok{)}
-
-\NormalTok{dta_d4_wide[}\KeywordTok{is.na}\NormalTok{(dta_d4_wide)] <-}\StringTok{ "0"}
-
-\NormalTok{dta_all <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(dta_d1_wide, dta_d2_wide, dta_d3_wide, dta_d4_wide)}
-
-\NormalTok{dta_all <-}\StringTok{ }\NormalTok{dta_all[}\KeywordTok{order}\NormalTok{(dta_all}\OperatorTok{$}\NormalTok{id,dta_all}\OperatorTok{$}\NormalTok{id_dy),]}
-
-\CommentTok{# Export the data for Mplus -------------------------------------------------}
-
-\KeywordTok{write_csv}\NormalTok{(dta_all, }\DataTypeTok{path =} \StringTok{"dta_NDNS_Tslots.csv"}\NormalTok{)}
-\KeywordTok{write_delim}\NormalTok{(dta_all, }\StringTok{"dta_NDNS_Tslots.dat"}\NormalTok{, }\DataTypeTok{na =} \StringTok{"."}\NormalTok{, }\DataTypeTok{delim =} \StringTok{" "}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-Mplus VERSION 7.4
-MUTHEN & MUTHEN
-07/28/2018   9:55 AM
-
-INPUT INSTRUCTIONS
-
-  TITLE:    3-class at level 1 (CW), 3-classes at level 2 (CB) random effects model - non-pa
-            ordered polytomous variables for carb intake at each time slot over four
-            days of NDNS survey 2008/09 - 2015/16
-            variable 0 = not eating
-                     1 = eating & carb provided < 50% calorie
-                     2 = eating & carb provided >= 50% calorie
-
-  DATA:     File is H:\summer_project\Mplus\TimeSlots\NDNS_Tslots.dat;
-
-  VARIABLE: NAMES = id id_dy Age Sex H6_9 H9_12 H12_14 H14_17 H17_20
-                    H20_22 H22_6;
-
-            USEVAR = H6_9 H9_12 H12_14 H14_17 H17_20
-                    H20_22 H22_6;
-
-            auxiliary = Age Sex;
-
-            CATEGORICAL =  H6_9 H9_12 H12_14 H14_17 H17_20
-                    H20_22 H22_6;
-
-            CLUSTER = id;
-
-            IDVARIABLE = id_dy;
-
-            BETWEEN = CB;
-
-            WITHIN = H6_9 H9_12 H12_14 H14_17 H17_20
-                    H20_22 H22_6;
-
-            CLASSES = CB(3) CW(3);
-
-            MISSING are .;
-
-  ANALYSIS:
-  type = mixture twolevel;
-  starts = 50 25;
-  process = 8(starts);
-
-  MODEL:
-  %within%
-  %overall%
-  %between%
-  %overall%
-  CW ON CB;
-
-  Savedata:
-    file is H:\summer_project\Mplus\TimeSlots\Multilevel\NDNSslot_CW3CB3.txt;
-    save is cprob;
-    format is free;
-
-3-class at level 1 (CW), 3-classes at level 2 (CB) random effects model - non-par
-ordered polytomous variables for carb intake at each time slot over four
-days of NDNS survey 2008/09 - 2015/16
-variable 0 = not eating
-1 = eating & carb provided < 50% calorie
-2 = eating & carb provided >= 50% calorie
-
-SUMMARY OF ANALYSIS
-
-Number of groups                                                 1
-Number of observations                                       24483
-
-Number of dependent variables                                    7
-Number of independent variables                                  0
-Number of continuous latent variables                            0
-Number of categorical latent variables                           2
-
-Observed dependent variables
-
-  Binary and ordered categorical (ordinal)
-   H6_9        H9_12       H12_14      H14_17      H17_20      H20_22
-   H22_6
-
-Observed auxiliary variables
-   AGE         SEX
-
-Categorical latent variables
-   CB          CW
-
-Variables with special functions
-
-  Cluster variable      ID
-  ID variable           ID_DY
-
-  Within variables
-   H6_9        H9_12       H12_14      H14_17      H17_20      H20_22
-   H22_6
-
-Estimator                                                      MLR
-Information matrix                                        OBSERVED
-Optimization Specifications for the Quasi-Newton Algorithm for
-Continuous Outcomes
-  Maximum number of iterations                                 100
-  Convergence criterion                                  0.100D-05
-Optimization Specifications for the EM Algorithm
-  Maximum number of iterations                                 500
-  Convergence criteria
-    Loglikelihood change                                 0.100D-02
-    Relative loglikelihood change                        0.100D-05
-    Derivative                                           0.100D-02
-Optimization Specifications for the M step of the EM Algorithm for
-Categorical Latent variables
-  Number of M step iterations                                    1
-  M step convergence criterion                           0.100D-02
-  Basis for M step termination                           ITERATION
-Optimization Specifications for the M step of the EM Algorithm for
-Censored, Binary or Ordered Categorical (Ordinal), Unordered
-Categorical (Nominal) and Count Outcomes
-  Number of M step iterations                                    1
-  M step convergence criterion                           0.100D-02
-  Basis for M step termination                           ITERATION
-  Maximum value for logit thresholds                            15
-  Minimum value for logit thresholds                           -15
-  Minimum expected cell size for chi-square              0.100D-01
-Maximum number of iterations for H1                           2000
-Convergence criterion for H1                             0.100D-03
-Optimization algorithm                                         EMA
-Integration Specifications
-  Type                                                    STANDARD
-  Number of integration points                                  15
-  Dimensions of numerical integration                            0
-  Adaptive quadrature                                           ON
-Random Starts Specifications
-  Number of initial stage random starts                         50
-  Number of final stage optimizations                           25
-  Number of initial stage iterations                            10
-  Initial stage convergence criterion                    0.100D+01
-  Random starts scale                                    0.500D+01
-  Random seed for generating random starts                       0
-Parameterization                                             LOGIT
-Link                                                         LOGIT
-Cholesky                                                       OFF
-
-Input data file(s)
-  H:\summer_project\Mplus\TimeSlots\NDNS_Tslots.dat
-Input data format  FREE
-
-SUMMARY OF DATA
-
-     Number of missing data patterns             1
-     Number of y missing data patterns           0
-     Number of u missing data patterns           1
-     Number of clusters                       6155
-
-COVARIANCE COVERAGE OF DATA
-
-Minimum covariance coverage value   0.100
-
-UNIVARIATE PROPORTIONS AND COUNTS FOR CATEGORICAL VARIABLES
-
-    H6_9
-      Category 1    0.313         7655.000
-      Category 2    0.184         4500.000
-      Category 3    0.504        12328.000
-    H9_12
-      Category 1    0.222         5447.000
-      Category 2    0.295         7227.000
-      Category 3    0.482        11809.000
-    H12_14
-      Category 1    0.195         4783.000
-      Category 2    0.454        11112.000
-      Category 3    0.351         8588.000
-    H14_17
-      Category 1    0.283         6926.000
-      Category 2    0.338         8277.000
-      Category 3    0.379         9280.000
-    H17_20
-      Category 1    0.124         3043.000
-      Category 2    0.582        14240.000
-      Category 3    0.294         7200.000
-    H20_22
-      Category 1    0.356         8722.000
-      Category 2    0.363         8898.000
-      Category 3    0.280         6863.000
-    H22_6
-      Category 1    0.666        16295.000
-      Category 2    0.169         4144.000
-      Category 3    0.165         4044.000
-
-RANDOM STARTS RESULTS RANKED FROM THE BEST TO THE WORST LOGLIKELIHOOD VALUES
-
-Final stage loglikelihood values at local maxima, seeds, and initial stage start numbers:
-
-         -166348.815  153942           31
-         -166348.815  573096           20
-         -166348.815  253358           2
-         -166348.816  318230           46
-         -166348.816  246261           38
-         -166348.873  285380           1
-         -166348.908  903420           5
-         -166349.394  120506           45
-         -166349.394  966014           37
-         -166349.394  207896           25
-         -166349.395  195873           6
-         -166349.513  68985            17
-         -166349.514  366706           29
-         -166352.737  76974            16
-         -166357.057  127215           9
-         -166482.723  533738           11
-         -166495.844  645664           39
-         -166668.918  372176           23
-
-THE BEST LOGLIKELIHOOD VALUE HAS BEEN REPLICATED.  RERUN WITH AT LEAST TWICE THE
-RANDOM STARTS TO CHECK THAT THE BEST LOGLIKELIHOOD IS STILL OBTAINED AND REPLICATED.
-
-THE MODEL ESTIMATION TERMINATED NORMALLY
-
-MODEL FIT INFORMATION
-
-Number of Free Parameters                      134
-
-Loglikelihood
-
-          H0 Value                     -166348.815
-          H0 Scaling Correction Factor      1.8182
-            for MLR
-
-Information Criteria
-
-          Akaike (AIC)                  332965.630
-          Bayesian (BIC)                334051.799
-          Sample-Size Adjusted BIC      333625.950
-            (n* = (n + 2) / 24)
-
-MODEL RESULTS USE THE LATENT CLASS VARIABLE ORDER
-
-   CB  CW
-
-  Latent Class Variable Patterns
-
-         CB        CW
-      Class     Class
-
-         1         1
-         1         2
-         1         3
-         2         1
-         2         2
-         2         3
-         3         1
-         3         2
-         3         3
-
-FINAL CLASS COUNTS AND PROPORTIONS FOR THE LATENT CLASS PATTERNS
-BASED ON ESTIMATED POSTERIOR PROBABILITIES
-
-  Latent Class
-    Pattern
-
-    1  1       4050.97975          0.16546
-    1  2       1561.55249          0.06378
-    1  3       1286.46696          0.05255
-    2  1       2746.94031          0.11220
-    2  2       3011.00217          0.12298
-    2  3       1341.59686          0.05480
-    3  1       2748.25320          0.11225
-    3  2       4770.55950          0.19485
-    3  3       2965.64876          0.12113
-
-FINAL CLASS COUNTS AND PROPORTIONS FOR EACH LATENT CLASS VARIABLE
-BASED ON ESTIMATED POSTERIOR PROBABILITIES
-
-  Latent Class
-    Variable    Class
-
-    CB             1      6898.99902          0.28179
-                   2      7099.53906          0.28998
-                   3     10484.46094          0.42823
-    CW             1      9546.17285          0.38991
-                   2      9343.11426          0.38162
-                   3      5593.71240          0.22847
-
-FINAL CLASS COUNTS AND PROPORTIONS FOR THE LATENT CLASS PATTERNS
-BASED ON THEIR MOST LIKELY LATENT CLASS PATTERN
-
-Class Counts and Proportions
-
-  Latent Class
-    Pattern
-
-    1  1             4262          0.17408
-    1  2             1406          0.05743
-    1  3             1178          0.04812
-    2  1             2807          0.11465
-    2  2             2946          0.12033
-    2  3             1260          0.05146
-    3  1             2745          0.11212
-    3  2             5315          0.21709
-    3  3             2564          0.10473
-
-FINAL CLASS COUNTS AND PROPORTIONS FOR EACH LATENT CLASS VARIABLE
-BASED ON THEIR MOST LIKELY LATENT CLASS PATTERN
-
-  Latent Class
-    Variable    Class
-
-    CB             1            6846          0.27962
-                   2            7013          0.28644
-                   3           10624          0.43393
-    CW             1            9814          0.40085
-                   2            9667          0.39485
-                   3            5002          0.20431
-
-CLASSIFICATION QUALITY
-
-     Entropy                         0.630
-
-Average Latent Class Probabilities for Most Likely Latent Class Pattern (Row)
-by Latent Class Pattern (Column)
-
-  Latent Class Variable Patterns
-
-  Latent Class         CB        CW
-   Pattern No.      Class     Class
-
-         1             1         1
-         2             1         2
-         3             1         3
-         4             2         1
-         5             2         2
-         6             2         3
-         7             3         1
-         8             3         2
-         9             3         3
-
-           1        2        3        4        5        6        7        8        9
-
-    1   0.720    0.091    0.073    0.016    0.032    0.004    0.005    0.033    0.025
-    2   0.183    0.609    0.098    0.005    0.002    0.030    0.040    0.005    0.027
-    3   0.211    0.084    0.629    0.008    0.005    0.007    0.011    0.036    0.009
-    4   0.019    0.004    0.002    0.692    0.184    0.051    0.011    0.034    0.003
-    5   0.042    0.001    0.001    0.158    0.709    0.045    0.001    0.035    0.009
-    6   0.012    0.037    0.013    0.065    0.084    0.702    0.042    0.003    0.042
-    7   0.011    0.029    0.004    0.012    0.002    0.022    0.641    0.126    0.153
-    8   0.026    0.003    0.009    0.025    0.024    0.001    0.115    0.675    0.123
-    9   0.046    0.024    0.004    0.003    0.010    0.018    0.079    0.174    0.642
-
-MODEL RESULTS
-
-                                                    Two-Tailed
-                    Estimate       S.E.  Est./S.E.    P-Value
-
-Within Level
-
-Latent Class Pattern 1 1
-
- Thresholds
-    H6_9$1            -0.718      0.218     -3.294      0.001
-    H6_9$2             0.973      0.299      3.258      0.001
-    H9_12$1           -2.516      0.463     -5.433      0.000
-    H9_12$2            0.675      0.132      5.118      0.000
-    H12_14$1          -1.025      0.145     -7.057      0.000
-    H12_14$2           1.240      0.116     10.725      0.000
-    H14_17$1          -1.566      0.149    -10.520      0.000
-    H14_17$2           1.090      0.100     10.909      0.000
-    H17_20$1          -1.998      0.125    -16.000      0.000
-    H17_20$2           1.549      0.100     15.556      0.000
-    H20_22$1          -0.933      0.085    -10.914      0.000
-    H20_22$2           1.829      0.103     17.770      0.000
-    H22_6$1            0.253      0.083      3.046      0.002
-    H22_6$2            2.308      0.117     19.691      0.000
-
-Latent Class Pattern 1 2
-
- Thresholds
-    H6_9$1            -4.021      1.788     -2.249      0.025
-    H6_9$2            -0.115      0.259     -0.445      0.656
-    H9_12$1            0.167      0.373      0.448      0.654
-    H9_12$2            2.142      0.586      3.657      0.000
-    H12_14$1          -3.210      1.518     -2.115      0.034
-    H12_14$2           0.858      0.167      5.124      0.000
-    H14_17$1           0.044      0.384      0.114      0.909
-    H14_17$2           1.617      0.293      5.509      0.000
-    H17_20$1          -2.109      0.390     -5.409      0.000
-    H17_20$2           1.399      0.196      7.126      0.000
-    H20_22$1          -0.367      0.174     -2.109      0.035
-    H20_22$2           2.347      0.382      6.151      0.000
-    H22_6$1            0.754      0.259      2.912      0.004
-    H22_6$2            2.542      0.264      9.646      0.000
-
-Latent Class Pattern 1 3
-
- Thresholds
-    H6_9$1           -15.000      0.000    999.000    999.000
-    H6_9$2             2.357      0.783      3.011      0.003
-    H9_12$1           -1.433      0.372     -3.850      0.000
-    H9_12$2           -0.604      0.279     -2.166      0.030
-    H12_14$1          -1.988      0.257     -7.749      0.000
-    H12_14$2           0.524      0.125      4.209      0.000
-    H14_17$1          -1.027      0.232     -4.436      0.000
-    H14_17$2           0.274      0.131      2.087      0.037
-    H17_20$1          -2.665      0.310     -8.605      0.000
-    H17_20$2           0.707      0.112      6.322      0.000
-    H20_22$1          -0.527      0.152     -3.462      0.001
-    H20_22$2           0.702      0.138      5.102      0.000
-    H22_6$1            1.119      0.185      6.062      0.000
-    H22_6$2            1.748      0.183      9.544      0.000
-
-Latent Class Pattern 2 1
-
- Thresholds
-    H6_9$1             1.663      0.199      8.370      0.000
-    H6_9$2             1.839      0.198      9.274      0.000
-    H9_12$1           -2.150      0.281     -7.643      0.000
-    H9_12$2           -0.869      0.140     -6.190      0.000
-    H12_14$1          -1.978      0.191    -10.349      0.000
-    H12_14$2           0.323      0.078      4.139      0.000
-    H14_17$1           0.237      0.183      1.293      0.196
-    H14_17$2           0.782      0.123      6.352      0.000
-    H17_20$1          -2.936      0.428     -6.853      0.000
-    H17_20$2           0.632      0.081      7.807      0.000
-    H20_22$1           0.028      0.142      0.194      0.846
-    H20_22$2           0.868      0.086     10.145      0.000
-    H22_6$1            0.658      0.109      6.010      0.000
-    H22_6$2            1.326      0.100     13.215      0.000
-
-Latent Class Pattern 2 2
-
- Thresholds
-    H6_9$1             1.640      0.171      9.619      0.000
-    H6_9$2             1.906      0.179     10.678      0.000
-    H9_12$1           -1.954      0.347     -5.636      0.000
-    H9_12$2           -0.360      0.127     -2.842      0.004
-    H12_14$1          -0.016      0.189     -0.084      0.933
-    H12_14$2           0.948      0.135      7.029      0.000
-    H14_17$1          -1.906      0.301     -6.327      0.000
-    H14_17$2           0.371      0.080      4.614      0.000
-    H17_20$1          -0.812      0.116     -7.030      0.000
-    H17_20$2           0.910      0.089     10.259      0.000
-    H20_22$1          -0.742      0.089     -8.318      0.000
-    H20_22$2           0.998      0.085     11.705      0.000
-    H22_6$1            0.298      0.083      3.608      0.000
-    H22_6$2            1.337      0.099     13.475      0.000
-
-Latent Class Pattern 2 3
-
- Thresholds
-    H6_9$1            -1.072      0.500     -2.144      0.032
-    H6_9$2            -0.309      0.346     -0.892      0.372
-    H9_12$1            2.441      1.044      2.339      0.019
-    H9_12$2            3.599      1.983      1.815      0.069
-    H12_14$1          -1.029      0.211     -4.880      0.000
-    H12_14$2           0.603      0.123      4.913      0.000
-    H14_17$1          -0.010      0.243     -0.041      0.967
-    H14_17$2           0.784      0.157      4.977      0.000
-    H17_20$1          -0.953      0.203     -4.684      0.000
-    H17_20$2           0.779      0.135      5.784      0.000
-    H20_22$1          -0.105      0.210     -0.500      0.617
-    H20_22$2           1.203      0.135      8.914      0.000
-    H22_6$1            0.582      0.299      1.950      0.051
-    H22_6$2            1.370      0.206      6.653      0.000
-
-Latent Class Pattern 3 1
-
- Thresholds
-    H6_9$1            -4.593      1.699     -2.703      0.007
-    H6_9$2            -2.975      0.428     -6.957      0.000
-    H9_12$1           -0.322      0.207     -1.553      0.120
-    H9_12$2            0.398      0.363      1.095      0.274
-    H12_14$1          -5.060      3.668     -1.380      0.168
-    H12_14$2           0.307      0.100      3.080      0.002
-    H14_17$1           0.186      0.530      0.351      0.726
-    H14_17$2           0.317      0.245      1.295      0.195
-    H17_20$1          -4.019      0.957     -4.199      0.000
-    H17_20$2           0.747      0.093      7.987      0.000
-    H20_22$1          -0.233      0.132     -1.767      0.077
-    H20_22$2           0.607      0.109      5.571      0.000
-    H22_6$1            1.304      0.146      8.918      0.000
-    H22_6$2            1.850      0.160     11.579      0.000
-
-Latent Class Pattern 3 2
-
- Thresholds
-    H6_9$1            -1.232      0.195     -6.305      0.000
-    H6_9$2            -0.858      0.169     -5.068      0.000
-    H9_12$1           -4.377      1.937     -2.260      0.024
-    H9_12$2           -1.488      0.316     -4.717      0.000
-    H12_14$1          -1.727      0.227     -7.611      0.000
-    H12_14$2           0.302      0.082      3.666      0.000
-    H14_17$1          -1.834      0.237     -7.730      0.000
-    H14_17$2          -0.294      0.186     -1.582      0.114
-    H17_20$1          -2.588      0.487     -5.313      0.000
-    H17_20$2           0.631      0.062     10.187      0.000
-    H20_22$1          -0.920      0.078    -11.852      0.000
-    H20_22$2           0.462      0.073      6.308      0.000
-    H22_6$1            0.640      0.119      5.361      0.000
-    H22_6$2            1.162      0.129      9.039      0.000
-
-Latent Class Pattern 3 3
-
- Thresholds
-    H6_9$1            -4.941      5.813     -0.850      0.395
-    H6_9$2            -2.680      0.887     -3.024      0.002
-    H9_12$1           -0.765      0.640     -1.195      0.232
-    H9_12$2            1.164      0.920      1.265      0.206
-    H12_14$1          -1.415      0.439     -3.226      0.001
-    H12_14$2           0.566      0.085      6.626      0.000
-    H14_17$1          -2.052      0.650     -3.158      0.002
-    H14_17$2           0.612      0.210      2.909      0.004
-    H17_20$1          -1.627      0.427     -3.810      0.000
-    H17_20$2           0.713      0.103      6.935      0.000
-    H20_22$1          -0.850      0.329     -2.585      0.010
-    H20_22$2           0.685      0.134      5.104      0.000
-    H22_6$1            1.237      0.195      6.349      0.000
-    H22_6$2            1.893      0.179     10.582      0.000
-
-Between Level
-
-Categorical Latent Variables
-
-Within Level
-
- Intercepts
-    CW#1              -0.076      0.366     -0.208      0.835
-    CW#2               0.475      0.309      1.539      0.124
-
-Between Level
-
- CW#1       ON
-    CB#1               1.223      0.473      2.585      0.010
-    CB#2               0.793      0.441      1.796      0.073
-
- CW#2       ON
-    CB#1              -0.282      0.535     -0.526      0.599
-    CB#2               0.333      0.455      0.733      0.464
-
- Means
-    CB#1              -0.417      0.100     -4.178      0.000
-    CB#2              -0.386      0.067     -5.770      0.000
-
-QUALITY OF NUMERICAL RESULTS
-
-     Condition Number for the Information Matrix              0.428E-04
-       (ratio of smallest to largest eigenvalue)
-
-SAVEDATA INFORMATION
-
-  Save file
-    H:\summer_project\Mplus\TimeSlots\Multilevel\NDNSslot_CW3CB3.txt
-
-  Order of variables
-
-    H6_9
-    H9_12
-    H12_14
-    H14_17
-    H17_20
-    H20_22
-    H22_6
-    ID_DY
-    AGE
-    SEX
-    CPROB1
-    CPROB2
-    CPROB3
-    CPROB4
-    CPROB5
-    CPROB6
-    CPROB7
-    CPROB8
-    CPROB9
-    CB
-    CW
-    MLCJOINT
-    ID
-
-  Save file format           Free
-
-  Save file record length    10000
-
-DIAGRAM INFORMATION
-
-  Mplus diagrams are currently not available for Mixture analysis.
-  No diagram output was produced.
-
-     Beginning Time:  09:55:10
-        Ending Time:  10:02:01
-       Elapsed Time:  00:06:51
-
-MUTHEN & MUTHEN
-3463 Stoner Ave.
-Los Angeles, CA  90066
-
-Tel: (310) 391-9971
-Fax: (310) 391-8971
-Web: www.StatModel.com
-Support: Support@StatModel.com
-
-Copyright (c) 1998-2015 Muthen & Muthen
-\end{verbatim}
+% Appendix Template
+
+\chapter{R \& Stata codes for processing individual level data analysis} % Main appendix title
+
+\label{AppendixD}
+\linespread{0.8}
 
@@
 \NormalTok{blood14 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr1-4a_indiv_uk.dta"}\NormalTok{)}
-
 \NormalTok{food14 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr1-4a_personleveldietarydata_uk.dta"}\NormalTok{)}
-
 \NormalTok{food56 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr5-6a_personleveldietarydata.dta"}\NormalTok{)}
-
 \NormalTok{food78 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr7-8a_personleveldietarydata.dta"}\NormalTok{)}
-
 \KeywordTok{names}\NormalTok{(blood78)[}\KeywordTok{names}\NormalTok{(blood78)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "ID"}
@@
 
-\KeywordTok{names}\NormalTok{(Energysum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Energy6_9"}\NormalTok{, }\StringTok{"Energy9_12"}\NormalTok{, }\StringTok{"Energy12_14"}\NormalTok{, }\StringTok{"Energy14_17"}\NormalTok{,}
-                     \StringTok{"Energy17_20"}\NormalTok{, }\StringTok{"Energy20_22"}\NormalTok{, }\StringTok{"Energy22_6"}\NormalTok{)}
+\KeywordTok{names}\NormalTok{(Energysum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Energy6_9"}\NormalTok{, }\StringTok{"Energy9_12"}\NormalTok{, }\StringTok{"Energy12_14"}\NormalTok{, }
+\StringTok{"Energy14_17"}\NormalTok{, }\StringTok{"Energy17_20"}\NormalTok{, }\StringTok{"Energy20_22"}\NormalTok{, }\StringTok{"Energy22_6"}\NormalTok{)}
 
@@
 
-\KeywordTok{names}\NormalTok{(Starchsum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Starch6_9"}\NormalTok{, }\StringTok{"Starch9_12"}\NormalTok{, }\StringTok{"Starch12_14"}\NormalTok{, }\StringTok{"Starch14_17"}\NormalTok{,}
-                       \StringTok{"Starch17_20"}\NormalTok{, }\StringTok{"Starch20_22"}\NormalTok{, }\StringTok{"Starch22_6"}\NormalTok{)}
+\KeywordTok{names}\NormalTok{(Starchsum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Starch6_9"}\NormalTok{, }\StringTok{"Starch9_12"}\NormalTok{, }\StringTok{"Starch12_14"}\NormalTok{, }
+\StringTok{"Starch14_17"}\NormalTok{, }\StringTok{"Starch17_20"}\NormalTok{, }\StringTok{"Starch20_22"}\NormalTok{, }\StringTok{"Starch22_6"}\NormalTok{)}
 
@@
 
-\KeywordTok{names}\NormalTok{(Sugarsum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Sugar6_9"}\NormalTok{, }\StringTok{"Sugar9_12"}\NormalTok{, }\StringTok{"Sugar12_14"}\NormalTok{, }\StringTok{"Sugar14_17"}\NormalTok{,}
-                      \StringTok{"Sugar17_20"}\NormalTok{, }\StringTok{"Sugar20_22"}\NormalTok{, }\StringTok{"Sugar22_6"}\NormalTok{)}
+\KeywordTok{names}\NormalTok{(Sugarsum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Sugar6_9"}\NormalTok{, }\StringTok{"Sugar9_12"}\NormalTok{, }\StringTok{"Sugar12_14"}\NormalTok{, }
+\StringTok{"Sugar14_17"}\NormalTok{, }\StringTok{"Sugar17_20"}\NormalTok{, }\StringTok{"Sugar20_22"}\NormalTok{, }\StringTok{"Sugar22_6"}\NormalTok{)}
 
@@
 
-\KeywordTok{names}\NormalTok{(Fibresum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Fibre6_9"}\NormalTok{, }\StringTok{"Fibre9_12"}\NormalTok{, }\StringTok{"Fibre12_14"}\NormalTok{, }\StringTok{"Fibre14_17"}\NormalTok{,}
-                      \StringTok{"Fibre17_20"}\NormalTok{, }\StringTok{"Fibre20_22"}\NormalTok{, }\StringTok{"Fibre22_6"}\NormalTok{)}
+\KeywordTok{names}\NormalTok{(Fibresum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"Fibre6_9"}\NormalTok{, }\StringTok{"Fibre9_12"}\NormalTok{, }\StringTok{"Fibre12_14"}\NormalTok{, }
+\StringTok{"Fibre14_17"}\NormalTok{, }\StringTok{"Fibre17_20"}\NormalTok{, }\StringTok{"Fibre20_22"}\NormalTok{, }\StringTok{"Fibre22_6"}\NormalTok{)}
 
@@
 
-\KeywordTok{names}\NormalTok{(NMESsum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"NMES6_9"}\NormalTok{, }\StringTok{"NMES9_12"}\NormalTok{, }\StringTok{"NMES12_14"}\NormalTok{, }\StringTok{"NMES14_17"}\NormalTok{,}
-                      \StringTok{"NMES17_20"}\NormalTok{, }\StringTok{"NMES20_22"}\NormalTok{, }\StringTok{"NMES22_6"}\NormalTok{)}
+\KeywordTok{names}\NormalTok{(NMESsum) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"NMES6_9"}\NormalTok{, }\StringTok{"NMES9_12"}\NormalTok{, }\StringTok{"NMES12_14"}\NormalTok{, }
+\StringTok{"NMES14_17"}\NormalTok{, }\StringTok{"NMES17_20"}\NormalTok{, }\StringTok{"NMES20_22"}\NormalTok{, }\StringTok{"NMES22_6"}\NormalTok{)}
 
@@
 //  weighting use wti to see the individual results    //
-//                                                     //
 *********************************************************
@@
 //  re-weighting use wtn to see the BMI,wc measurements //
-//                                                     //
 *********************************************************
-
 svyset area [pweight = wtn1to8], strata(gor)
@@
 
-svy: logistic hibp i.CB
-svy: logistic hibp i.CB#i.Sex
-
-test 2.CB#2.Sex
-
 svy: tabulate paid hibp, col se ci format(%7.3f)
@@
 gen DM = A1C > 6.5 if !missing(A1C)
-svyset area [pweight = wtb1to8], strata(gor)
-
-svy, subpop(Men): tabulate DM hibp, col se ci format(%7.3f)
-svy, subpop(Women): tabulate DM hibp, col se ci format(%7.3f)
 
@@
 **   date: 07/08/2018
-**
-**
 ********************************************************
@@
 
-//  Preliminary model includes all possible confounders in Men
-
-gen age2 = age^2
-
+//  Model includes all possible confounders in Men
 svy, subpop(Men): logistic hibp i.CB age i.Married i.Edu bmi i.cig EnergykJ 
@@
 linktest
-svy, subpop(if Men & DM != 1): logistic hibp i.CB age i.Married i.Edu bmi i.cig EnergykJ 
+svy, subpop(if Men & DM != 1): logistic hibp i.CB age i.Married ///
+ i.Edu bmi i.cig EnergykJ 
 linktest
-svy, subpop(if Men & DM != 1): logistic hibp i.CB age i.Married i.Edu wst i.cig EnergykJ 
+svy, subpop(if Men & DM != 1): logistic hibp i.CB age i.Married ///
+ i.Edu wst i.cig EnergykJ 
 linktest
 
-//  Preliminary model includes all possible confounders in Women
-
-svy, subpop(Women): logistic hibp i.CB age i.Married eqvinc i.Edu bmi i.cig EnergykJ Alcoholg 
+// use the model above to see whether any other factors are confounders 
+// conditional on the other variables
+
+// income -> not confounder
+svy, subpop(Men): logistic hibp i.CB age i.Married i.Edu bmi i.cig /// 
+ EnergykJ eqvinc
+test eqvinc
+
+// ethnicity -> not confounder
+svy, subpop(Men): logistic hibp i.CB age i.Married i.Edu bmi i.cig /// 
+ EnergykJ i.ethgrp2
+test 2.ethgrp2
+
+// alcohol -> not confounder
+svy, subpop(Men): logistic hibp i.CB age i.Married i.Edu bmi i.cig /// 
+ EnergykJ Alcoholg
+test Alcoholg
+
+// MVP(physical activity) -> not confounder
+svy, subpop(Men): logistic hibp i.CB age i.Married i.Edu bmi i.cig /// 
+ EnergykJ logMVP
+test logMVP
+
+//  Model includes all possible confounders in Women
+svy, subpop(Women): logistic hibp i.CB age i.Married eqvinc i.Edu ///
+ bmi i.cig EnergykJ Alcoholg 
 linktest
-svy, subpop(Women): logistic hibp i.CB age i.Married eqvinc i.Edu wst i.cig EnergykJ Alcoholg 
+svy, subpop(Women): logistic hibp i.CB age i.Married eqvinc i.Edu ///
+ wst i.cig EnergykJ Alcoholg 
 linktest
 
-svy, subpop(if Women & DM != 1): logistic hibp i.CB age i.Married eqvinc i.Edu bmi i.cig EnergykJ Alcoholg
+// use the model above to see whether any other factors are confounders 
+// conditional on the other variables
+
+// ethnicity -> not confounder
+svy, subpop(Women): logistic hibp i.CB age i.Married eqvinc i.Edu /// 
+ bmi i.cig EnergykJ Alcoholg i.ethgrp2
+test 2.ethgrp2
+
+// MVP (physical activity) -> not confounder
+svy, subpop(Women): logistic hibp i.CB age i.Married eqvinc i.Edu /// 
+ bmi i.cig EnergykJ Alcoholg logMVP
+test logMVP
+
+svy, subpop(if Women & DM != 1): logistic hibp i.CB age i.Married /// 
+ eqvinc i.Edu bmi i.cig EnergykJ Alcoholg
 linktest
 
-svy, subpop(if Women & DM != 1): logistic hibp i.CB age i.Married eqvinc i.Edu wst i.cig EnergykJ Alcoholg
+svy, subpop(if Women & DM != 1): logistic hibp i.CB age i.Married /// 
+ eqvinc i.Edu wst i.cig EnergykJ Alcoholg
 linktest
 \end{verbatim}
-
-\end{document}

### 2018-08-17 paper/Appendices/AppendixE.tex
appendix C figlevel 1 CW4

% Appendix Template

\chapter{Example of a food diary for one day} % Main appendix title

\label{AppendixE} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}
%\begin{verbatim}

\begin{figure}[H]
%\vspace*{13cm}
\centering
\includegraphics{Figures/Diary1.png}
\decoRule
\caption[One day food diary example 6 am to 2 pm]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, from 6 am to 2 pm.}
\label{fig:diary1}
\end{figure}
%\end{verbatim}

\begin{figure}[H]
%\vspace*{13cm}
\centering
\includegraphics{Figures/Diary2.png}
\decoRule
\caption[One day food diary example 2 pm to 6 am]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, from 2 pm to 6 am.}
\label{fig:diary2}
\end{figure}
%\end{verbatim}

\begin{figure}[H]
%\vspace*{13cm}
\centering
\includegraphics{Figures/Diary3.png}
\decoRule
\caption[Food diary example of home made food recipes]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, home made food recipes.}
\label{fig:diary3}
\end{figure}

### 2018-08-17 paper/Chapters/Chapter2.tex
appendix C figlevel 1 CW4

@@
 In each eating occasion, in addition to the details of what and how much was eaten, participants were also asked to record: when was it, where they were, and who they were eating with.
-An example, used as guidance for participants, of a food diary for one day is shown in \textbf{Appendix \ref{AppendixC}}.\vspace{-0.3cm}
+An example, used as guidance for participants, of a food diary for one day is shown in \textbf{Appendix \ref{AppendixE}}.\vspace{-0.3cm}
 
@@
 All statistical analyses, except for MLCA models, were performed with \code{svyset} command as implemented in Stata software version 15.1 \parencite{stata15}.
+The process of model fitting, covariates selection, interaction effect testings for the association between carbohydrate eating patterns and hypertension is shown as an example in \textbf{Appendix \ref{AppendixD}}.
 All \textit{p} values were two-sided.

### 2018-08-17 paper/Chapters/Chapter3.tex
appendix C figlevel 1 CW4

@@
 However, after these solutions were checked in more details, the potentially most substantively interpretable model was found to be the 3$\times$3 random effect model, which is the model with 3 latent classes in the day level, and 3 latent classes in the individual level.
-We must emphasize that different researchers may have made decision slightly different from ours, we provided the descriptions and figures for other solutions in the \textbf{Appendix xxx} for reference.
+We must emphasize that different researchers may have made decision slightly different from ours, we provided the descriptions and figures for other solutions in the \textbf{Appendix \ref{AppendixC}} for reference.
 
@@
 		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous),}}\\ 
-		\multicolumn{6}{l}{{\scriptsize education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);}}\\
+		\multicolumn{6}{l}{{\scriptsize education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day).}}\\
 	\end{tabular}

### 2018-08-17 Rcode/data transformation.R

@@ -353,14 +353,14 @@ names(dta_d4_wide)
 
 for (i in 6:ncol(dta_d1_wide)) 
   if(is.factor(dta_d1_wide[,i])) 
-    levels(dta_d1_wide[,i]) <- c("1", "2", "3", "0")
+    levels(dta_d1_wide[,i]) <- c("1", "2", "0")
 
 dta_d1_wide[is.na(dta_d1_wide)] <- "0"
 
 
 for (i in 6:ncol(dta_d2_wide)) 
   if(is.factor(dta_d2_wide[,i])) 
-    levels(dta_d2_wide[,i]) <- c("1", "2", "3", "0")
+    levels(dta_d2_wide[,i]) <- c("1", "2",  "0")
 
 
 dta_d2_wide[is.na(dta_d2_wide)] <- "0"
@@ -368,36 +368,23 @@ dta_d2_wide[is.na(dta_d2_wide)] <- "0"
 
 for (i in 6:ncol(dta_d3_wide)) 
   if(is.factor(dta_d3_wide[,i])) 
-    levels(dta_d3_wide[,i]) <-  c("1", "2", "3", "0")
+    levels(dta_d3_wide[,i]) <-  c("1", "2", "0")
 
 dta_d3_wide[is.na(dta_d3_wide)] <- "0"
 
 
 for (i in 6:ncol(dta_d4_wide)) 
   if(is.factor(dta_d4_wide[,i])) 
-    levels(dta_d4_wide[,i]) <-  c("1", "2", "3", "0")
+    levels(dta_d4_wide[,i]) <-  c("1", "2", "0")
 
 dta_d4_wide[is.na(dta_d4_wide)] <- "0"
 
-# setwd("H:/summer project/Rcodes")
-
-# dta_d1_sas <- dta_d1_wide
-# 
-# write_csv(dta_d1_wide, path = "dta_d1.csv")
-# 
-# write_csv(dta_d2_wide, path = "dta_d2.csv")
-# write_csv(dta_d3_wide, path = "dta_d3.csv")
-# write_csv(dta_d4_wide, path = "dta_d4.csv")
 
 dta_all <- rbind(dta_d1_wide, dta_d2_wide, dta_d3_wide, dta_d4_wide)
 
 dta_all <- dta_all[order(dta_all$id,dta_all$id_dy),]
 
-# write_csv(dta_all, path = "dta_NDNS.csv")
-# write_csv(dta_all, path = "dta_NDNS_Tslots.csv")
[…]

### 2018-08-17 paper/Figures/Figureforpaper.R

@@ -551,7 +551,7 @@ chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"),
 
 
 library(ggthemr)
-ggthemr("greyscale", layout = "scientific")
+ggthemr("dust", layout = "scientific")
 ggplot() + 
   geom_bar(aes(y = pct, x = CB, fill = CW_new), data = chart.data, width = 0.6,
            stat="identity") +
@@ -648,6 +648,94 @@ ggplot() +
         text=element_text(family="Atlas Grotesk Light")) +
   labs(title = " ", x = "Between Individual classes", y = "Percentage") +
   scale_y_continuous(labels=percent)
+
+
+
+# Level 2 (CB=4) classes solution  ----------------------------------------
+
+
+CW3CB2 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB2.txt",
+                      col_names = FALSE)
+
+names(CW3CB2) <- c("Breakfast", "Morning.snack", "Lunch",
+                   "Afternoon.snack", "Dinner", "Before.bedtime.snack",
+                   "Midnight.food", "ID_DAY", "AGE", "SEX",
+                   "CPROB1", "CPROB2", "CPROB3", "CPROB4",
+                   "CPROB5", "CPROB6",
+                   # "CPROB7",
+                   # "CPROB8",
+                   # "CPROB9",
+                   "CB", "CW", "MLCJOINT", "ID")
+
+
+CW3CB4 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB4.txt",
+                      col_names = FALSE)
+
+names(CW3CB4) <- c("Breakfast",  "Morning.snack", "Lunch",
+                   "Afternoon.snack", "Dinner", "Before.bedtime.snack",
+                   "Midnight.food", "ID_DAY", "AGE", "SEX",
+                   "CPROB1", "CPROB2", "CPROB3", "CPROB4",
+                   "CPROB5", "CPROB6", "CPROB7", "CPROB8",
+                   "CPROB9", "CPROB10", "CPROB11", "CPROB12", 
+                   "CB", "CW", "MLCJOINT", "ID")
+
[…]

### 2018-08-17 paper/Appendices/AppendixC.tex
appendix done

@@
 	\caption[2 Classes solution in Day level]{2 Classes solution in Day level.}
-	\label{fig:diary1}
+	\label{fig:CW2level1}
 \end{figure}
@@
 	\caption[Multilevel Latent Class Solution (2 $\times$ 2).]{Multilevel Latent Class Solution, 2 classes in day level, 2 classes in individual level.}
-	\label{fig:diary1}
+	\label{fig:CW2CB2}
 \end{figure}
@@
 	\caption[Multilevel Latent Class Solution (2 $\times$ 3).]{Multilevel Latent Class Solution, 2 classes in day level, 3 classes in individual level.}
-	\label{fig:diary1}
+	\label{fig:CW2CB3}
 \end{figure}
@@
 	\caption[Multilevel Latent Class Solution (2 $\times$ 4).]{Multilevel Latent Class Solution, 2 classes in day level, 4 classes in individual level.}
-	\label{fig:diary1}
+	\label{fig:CW2CB4}
 \end{figure}
@@
 	\caption[Multilevel Latent Class Solution (3 $\times$ 4).]{Multilevel Latent Class Solution, 3 classes in day level, 4 classes in individual level.}
-	\label{fig:diary1}
+	\label{fig:CW3CB4}
 \end{figure}
@@
 	\caption[2 Classes Solution in Day level]{4 Classes Solution in Day level.}
-	\label{fig:diary1}
+	\label{fig:CW4level1}
 \end{figure}
+
+\begin{figure}[H]
+	%\vspace*{13cm}
+	\centering
+	\includegraphics[width=13cm]{Figures/CW4CB2.png}
+	\decoRule
+	\caption[Multilevel Latent Class Solution (4 $\times$ 2).]{Multilevel Latent Class Solution, 4 classes in day level, 2 classes in individual level.}
+	\label{fig:CW4CB2}
+\end{figure}
+
+\begin{figure}[H]
+	%\vspace*{13cm}
+	\centering
+	\includegraphics[width=13cm]{Figures/CW4CB3.png}
+	\decoRule
+	\caption[Multilevel Latent Class Solution (4 $\times$ 3).]{Multilevel Latent Class Solution, 4 classes in day level, 3 classes in individual level.}
+	\label{fig:CW4CB3}
+\end{figure}

### 2018-08-17 paper/Figures/Figureforpaper.R

@@ -1611,3 +1611,130 @@ Carbohydrate >= 50% indicates that within the time slot, carbohydrate contribute
 
 library(cowplot)
 plot_grid(cls1, cls2, cls3, cls4, ncol = 1, labels = c('A', 'B'), rel_heights=c(1,1,1,1.44))
+
+
+
+chart.data <- CW4CB2 %>%
+  group_by(CB, CW) %>%
+  tally %>%
+  group_by(CB) %>%
+  mutate(pct = n/sum(n))
+
+
+# chart.data$CW[chart.data$CW == 1] <- 0
+# chart.data$CW[chart.data$CW == 3] <- 1
+# chart.data$CW[chart.data$CW == 0] <- 3
+
+chart.data <- chart.data[order(chart.data$CB, chart.data$CW),]
+chart.data <- ddply(chart.data, .(CB),
+                    transform, pos = cumsum(pct) - (0.5 * pct))
+
+
+
+chart.data$CW <- factor(chart.data$CW, levels = c("4", "3", "2", "1"),
+                        labels = c("Class 4 days", "Class 3 days", "Class 2 days", "Class 1 days"))
+chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"),
+                        labels = c("Individual\nclass 1\n(52.6%)",  "Individual\nclass 2\n(47.4%)"))
+
+
+
+library(ggthemr)
+ggplot() +
+  geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6,
+           stat="identity") +
+  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
+            size=4, colour="white", family="Atlas Grotesk Medium") +
+  theme(legend.position="right", #legend.direction="horizontal",
+        legend.title = element_blank(),
+        axis.text = element_text(size = 15),
+        legend.text = element_text(size = 13), 
+        axis.title = element_text(size = 18),
+        axis.line = element_line(colour = "black"),
+        plot.title=element_text(family="Atlas Grotesk Medium"),
+        text=element_text(family="Atlas Grotesk Light")) +
+  labs(title = " ", x = "Between Individual classes", y = "Percentage") +
+  scale_y_continuous(labels=percent)
+
+
+
+## Visualisation of level 2 latent classes (CB = 3)
+
+
+
+
[…]

### 2018-08-18 paper/Appendices/AppendixD.tex
appendix done
limitation 1

@@
 
-\chapter{R \& Stata codes for processing individual level data analysis} % Main appendix title
+\chapter{R and STATA codes for processing individual level data analysis} % Main appendix title
 
@@
 \CommentTok{# read the individual level data sets ----------------------------------------}
-
+\CommentTok{# Change the data path accordingly ----------------------------------------}
+\KeywordTok{setwd}\NormalTok{(}\StringTok{".../UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }
 \NormalTok{blood78 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr7-8a_indiv.dta"}\NormalTok{)}
@@
 
-\NormalTok{blood14 <-}\StringTok{ }\NormalTok{blood14 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{NDAYS14 <-}\StringTok{ }\NormalTok{blood14 }\OperatorTok{%>%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(ID, Ndays)}
 
-\NormalTok{blood56 <-}\StringTok{ }\NormalTok{blood56 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{NDAYS56 <-}\StringTok{ }\NormalTok{blood56 }\OperatorTok{%>%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(ID, Ndays)}
 
-\NormalTok{blood78 <-}\StringTok{ }\NormalTok{blood78 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{NDAYS78 <-}\StringTok{ }\NormalTok{blood78 }\OperatorTok{%>%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(ID, NDays) }\OperatorTok{%>%}\StringTok{ }
@@
 
-\NormalTok{NDAYS <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(blood14, blood56, blood78)}
+\NormalTok{NDAYS <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(NDAYS14, NDAYS56, NDAYS78)}
 \NormalTok{NDAYS}\OperatorTok{$}\NormalTok{ID <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(NDAYS}\OperatorTok{$}\NormalTok{ID)}
@@
  \CommentTok{# change the path accordingly}
-\KeywordTok{write_dta}\NormalTok{(CW3CB3_regss, }\StringTok{"../CW3CB3_7regss.dta"}\NormalTok{)}
+\KeywordTok{write_dta}\NormalTok{(CW3CB3_7regss, }\StringTok{"../CW3CB3_7regss.dta"}\NormalTok{)}
 \end{Highlighting}
@@
 **********************************************************
-// variables need to be log transfomred                 //
+// variables need to be log transformed                 //
 **********************************************************

### 2018-08-18 paper/Chapters/Chapter4.tex
limitation 1

@@
 
-Surprisingly, low carbohydrate eaters whose dietary recordings suggested that they were mostly following a regular temporal meals pattern turned out to consume the highest amount of total energy among the three types of carbohydrate eaters.
+Surprisingly, low carbohydrate eaters whose dietary recordings suggested that they were mostly following a regular temporal meals pattern turned out to be consuming the highest amount of total energy among the three types of carbohydrate eaters.
 Detailed profiling of energy composition according to the time slots revealed that low carbohydrate eaters actually had higher proportion of energy contributed by both alcohol and fat.
@@
 
-Next, when looking into the details of the timing and composition of the energy intake among the moderate carbohydrate eaters, we realised that although these individuals did not consume as much alcohol as low carbohydrate eaters at night, they consumed the highest amount of energy, especially during time period as late as after 10 pm.
-People fell into moderate carbohydrate eaters group seemed to have the tendency of having their food or meals later than the other two types of carbohydrate eaters.
+Next, when looking into the details of the timing and composition of the energy intake among the moderate carbohydrate eaters, we realised that although these individuals did not consume as much alcohol as low carbohydrate eaters did at night, they consumed the highest amount of energy, especially during time period as late as after 10 pm.
+People fell into moderate carbohydrate eaters group seemed to have the tendency of having their food or meals later than high carbohydrate eaters.
 They consumed the highest amount of carbohydrates and also total energy among three types of carbohydrate eaters during the following time slots: 9-12 noon, 2-5 pm, 8-10 pm, and 10pm-6am.
-These individuals in the NDNS RP were younger, mostly single, with lower average income, and lower education level.
+These individuals in the NDNS RP were younger, largely single, with lower average income, and lower education level.
 They might possibly correspond to the "late eaters" defined by previous studies \parencite{leech2017temporal, mansukhani2018investigating}.
 
-Lastly, the high carbohydrate eaters identified by our MLCA models had the highest absolute total amount of carbohydrate intake.
-Most of their energy intake occured during 6-9 am, 12-2 pm, and 5-8 pm time slots while their average energy consumption was not the highest (between low and moderate carbohydrate eaters).
+Finally, the high carbohydrate eaters identified by our MLCA models had the highest absolute total amount of carbohydrate intake.
+Most (nearly 70\%) of their total energy intake occurred during 6-9 am, 12-2 pm, and 5-8 pm time slots although their total energy consumption was not the highest (between low and moderate carbohydrate eaters).
 High carbohydrate eaters were also found to be the ones that consumed the least amount of energy after 8 pm.
@@
 Therefore, considering that moderate carbohydrate eaters were younger than low carbohydrate eaters (although age was adjusted in the full models), there is probably reverse causality exists here (also due to the nature of cross-sectional study).
-That is, they were potentially both late eaters, however, with their age increased (and so as increased health-related problems/concern) some of them modified their habits, such as quit smoking, replace carbohydrate food with other energy sources which lead to the phenomenon of lower odds of hypertension in moderate carbohydrate eaters.
-Although the hypothesis cannot be determined by NDNS RP's cross-sectional data, if these theories were true, the energy sources they used to replace carbohydrate in their diet were apparently not very wisely chosen.
+That is, they were potentially both late eaters, however, with increased age (and so as increased health-related problems/concern) some of them modified their habits, such as quit smoking, replace carbohydrate food with other energy sources which lead to the phenomenon of lower odds of hypertension in moderate carbohydrate eaters.
+Although these hypotheses cannot be determined by the cross-sectional data from NDNS RP, if they were true, the energy sources they used to replace carbohydrate in their diet were apparently not very wisely chosen.
 
@@
 It was often assumed that live alone may associated with lower diversity of food intake, and a higher likelihood of having an unhealthy dietary pattern \parencite{hanna2015relationship}.
-Therefore, there may be differences in the actual contents consumed in the high carbohydrates eaters, or there may be other social, psychological or lifestyle related factors related with living alone which we did not included in the models, so that the inverse association between high carbohydrate eating pattern and BMI or abdominal obesity were only observed among women who lived with partners, further analysis is needed.
-Whereas the reason why moderate carbohydrate eaters' WC was larger than low carbohydrate eaters only among women who lived alone is unknown, given that the evidence of this association was weak and borderline significant, whether it was just a false positive result should be explored in other studies.
+Therefore, there may be differences in the actual contents consumed in high carbohydrates eating women, or there may be other social, psychological or lifestyle related factors related with living alone which were not measured or did not included in the models, so that the inverse association between high carbohydrate eating pattern and BMI or abdominal obesity were only observed among women who lived with partners, further analysis is needed.
+Whereas the reason why moderate carbohydrate eaters' WC was larger than low carbohydrate eaters only among women who lived alone is unknown, given that the evidence of this association was weak and borderline significant, whether it was just a false positive finding should be explored in other studies.
 
@@
 
-\section{Strengths and limitations}
+\section{Limitations and strengths}
+
+There are several limitations in the current project that merits consideration.
+
+Firstly, we ignored the order of observation days in the MLCA models.
+The food consumption diaries were accomplished by participants for at least 3 out of 4 consecutive days.
+In the multilevel analyses, these 3 or 4 days' observations were treated as if they were exchangeable in the models.
+Since one's diet might change according to season, day of the week (weekdays or weekends), or sometimes depends on what they had consumed the day before, exchangeability of their diaries is a strong assumption and cannot be overcome by the MLCA models adopted here.
+Other statistical techniques, which could take the order or the longitudinal nature of the data into account, such as repeated measures latent class analysis (RMLCA), latent transition analysis (LTA) \parencite{collins2010latent}, or latent class growth analysis (LCGA) \parencite{davidian2008growth,jung2008introduction,andruff2009latent} are not applicable for the NDNS RP dataset.
+For the purpose of maintaining the response rate, flexibility was allowed for the NDNS RP participants in their choice of which day to begin their diary.
+Additionally, these models require that the 3 or 4 repeated measurements of food diaries should be recorded at the same time points longitudinally.
+LCGA models (also called growth mixture modelling) will need to model the change of the odds of the probability over time as a function (quadratic, or cubic) which is apparently not the objective in the current project.
+
+Secondly, the classification of individuals to latent carbohydrate eating classes are defined by maximum posterior probability assignment rule.
+This approach assigns individuals to the class for which they have the highest posterior probability of membership \parencite{nagin2005group}.
 
 \begin{itemize}
-	\item MLCA ignored the order of observation days.
 	\item We used the maximum probability rule and ignored that these are just probabilities. but inclusive MLCA might perform better.

### 2018-08-18 paper/Chapters/Chapter4.tex
before go to chaed party

@@
 
-Secondly, the classification of individuals to latent carbohydrate eating classes are defined by maximum posterior probability assignment rule.
+Secondly, the classification of individuals to latent carbohydrate eating classes were defined by maximum posterior probability assignment rule.
 This approach assigns individuals to the class for which they have the highest posterior probability of membership \parencite{nagin2005group}.
+The other approach is multiple pseudo-class draws \parencite{wang2005residual}, which was proposed in attempt to account for uncertainty in class assignment.
+However, the maximum probability rule is still believed to be able to minimize the number of incorrect assignments \parencite{goodman20071}.
+A Monte Carlo simulation study \parencite{bray2015eliminating} also demonstrated that maximum probability assignment is less biased than multiple pseudo-class draws.
+Moreover, this simulation study also found that an inclusive LCA (i.e.
+LCA with covariates) would perform better, and reduce bias.
+Since whether this advantage can be extended to MLCA in the current project is unknown, and also due to the reason that the associations between the latent classes and distal outcomes (hypertension, and BMI) in our analyses were mostly still under exploration, therefore, the model for LCA with covariates can never be well-known before our analyses.
+Thus, as a first step, also given the complexity of the NDNS RP dataset itself, we chose to conduct the MLCA modellings without any covariate in either day level or individual level models.
+Future studies may be advised to consider incorporating other predictors in the MLCA models to see whether the classifications in both levels can be improved or not.
+
+Thirdly, information regarding the detailed occupations of the participants was not available, so we could not exclude those who had a shift work involving night work.
+But considering that completing a 4-consecutive-day food diary would be a large burden for the participants, those had a shift work involving night work might possibly performed relatively lower compliance and could not complete their diary for at least 3 days.
+But this cannot be verified in the NDNS RP dataset.
+If people working with shift work were included in the NDNS RP sample, the classification in both levels as well as their associations with either hypertension or BMI would be biased.
+Furthermore, under-reporting is also a concern in the diaries collected.
+To evaluate the influence of under-reporting in the NDNS RP sample, study team of NDNS RP conducted doubly labelled water (DLW) sub-study within the survey.
+The details of this sub-study can be accessed from the Appendix X of the Official Reports provided by Public Health England \parencite{bates2014national,roberts2018national,NDNSofficial}.
 
 \begin{itemize}
-	\item We used the maximum probability rule and ignored that these are just probabilities. but inclusive MLCA might perform better.
-	\item we do not have the information of whether the participants were doing job that requires shift work.
 	\item dietary report under estimation

### 2018-08-19 paper/Chapters/Chapter4.tex
updated discussion done

@@
 For the purpose of maintaining the response rate, flexibility was allowed for the NDNS RP participants in their choice of which day to begin their diary.
-Additionally, these models require that the 3 or 4 repeated measurements of food diaries should be recorded at the same time points longitudinally.
-LCGA models (also called growth mixture modelling) will need to model the change of the odds of the probability over time as a function (quadratic, or cubic) which is apparently not the objective in the current project.
+But the above mentioned alternative models require that the 3 or 4 repeated measurements of food diaries to be recorded at the same time points longitudinally.
+Specifically, LCGA models (also called growth mixture modelling) will also need to model the change of the odds of the probability over time as a function (quadratic, or cubic) which is apparently not the objective in the current project.
 
@@
 Moreover, this simulation study also found that an inclusive LCA (i.e.
-LCA with covariates) would perform better, and reduce bias.
-Since whether this advantage can be extended to MLCA in the current project is unknown, and also due to the reason that the associations between the latent classes and distal outcomes (hypertension, and BMI) in our analyses were mostly still under exploration, therefore, the model for LCA with covariates can never be well-known before our analyses.
-Thus, as a first step, also given the complexity of the NDNS RP dataset itself, we chose to conduct the MLCA modellings without any covariate in either day level or individual level models.
+LCA with covariates) would perform better than non-inclusive LCA, and has the potential to reduce bias of class assignment.
+However, whether this advantage can be extended to MLCA in the current project is unknown, and also due to the reason that the associations between the latent classes and distal outcomes (hypertension, and BMI) in our analyses are mostly still under exploration, therefore, the model for LCA with covariates can never be well-known before our analyses.
+Thus, as a first step, given the complexity of the NDNS RP dataset itself, we chose to conduct the MLCA modellings without any covariate in either day level or individual level models.
 Future studies may be advised to consider incorporating other predictors in the MLCA models to see whether the classifications in both levels can be improved or not.
 
-Thirdly, information regarding the detailed occupations of the participants was not available, so we could not exclude those who had a shift work involving night work.
+Thirdly, information regarding the detailed occupations of the participants was not available and because of which we could not exclude those who had a shift work involving night work.
 But considering that completing a 4-consecutive-day food diary would be a large burden for the participants, those had a shift work involving night work might possibly performed relatively lower compliance and could not complete their diary for at least 3 days.
-But this cannot be verified in the NDNS RP dataset.
+But this hypothesis cannot be verified in the NDNS RP dataset.
 If people working with shift work were included in the NDNS RP sample, the classification in both levels as well as their associations with either hypertension or BMI would be biased.
-Furthermore, under-reporting is also a concern in the diaries collected.
+Furthermore, under-reporting due to the burden of writing down everything they eat at each occasion is also a concern in the food diaries collected.
 To evaluate the influence of under-reporting in the NDNS RP sample, study team of NDNS RP conducted doubly labelled water (DLW) sub-study within the survey.
 The details of this sub-study can be accessed from the Appendix X of the Official Reports provided by Public Health England \parencite{bates2014national,roberts2018national,NDNSofficial}.
+Briefly, in healthy adults, if, for a given period of time, energy consumed in food matches total energy expended, they are in energy balance.
+In NDNS RP sub-study, estimates of energy intake (EI) from the four-day diary were compared with measurements of total energy expenditure (TEE) using the DLW technique in a sub-sample of survey participants.
+Results of the sub-study showed reasonable agreement between EI and TEE (overall ratio: 0.73).
+Reasons such as misreporting of actual consumption; under-reported or modified usual intake due to the burden of the survey/DLW sub-study are potential factors may contributed to under-reporting of their EI.
+We cannot extrapolate the estimated under-reporting to the whole sample since other individuals' diet might be affected by under-reporting differentially.
 
-\begin{itemize}
-	\item dietary report under estimation
-	\item findings may not be generalizable to populations from other countries.
-\end{itemize}
+Lastly, it should be noted that findings from data-driven, exploratory methods may not be
+generalizable to populations in other countries.
+Since the carbohydrate eating patterns in both day level and individual level probably only represent the socio-cultural and life-style characteristics of the adult population in the UK.
+Further researches are warranted to explore and better understand the eating patterns in other populations.
+Besides, the cross-sectional study design also refrained us from deducing any causal effect between the carbohydrate eating patterns and hypertension or BMI.
 
@@
 
-We have successfully defined carbohydrate eating patterns in the general population in the UK adults using the NDNS RP database in both observation day level and participant level.
+We have successfully defined carbohydrate eating patterns in the general population in the UK adults using the NDNS RP database in both observation day level and individual level.
 Low carbohydrate eaters turned to have more energy that contributed by both fat and alcohol.
@@
 High carbohydrate eaters consumed most of their carbohydrate as well as energy earlier in time-of-day.
-These dietary patterns specifically for carbohydrate intake were found to be differed by timing, quantity and resources of energy consumption.
+These dietary patterns specifically for carbohydrate intake were found to be differed by timing, quantity and contributions to energy consumption.
 Compared with low carbohydrate eaters, men had moderate carbohydrate eating pattern may associated with a lower prevalence of hypertension, women in this latent class who lived alone may associated with a larger waist circumferences.
 Among women who lived with partners, high carbohydrate eating pattern was associated with both lower BMI and smaller waist circumferences.
-Future studies exploring how such carbohydrate eating patterns may relate longitudinally to change of obesity, hypertension and diabetes incidence and other health outcomes are needed.
+Longitudinal designed studies are needed in finding whether the eating patterns themselves are changing over time and in investigating how such circadian eating patterns may relate to the change of blood pressure, obesity, and even mortality.

### 2018-08-19 paper/main.tex
appendix C figlevel 1 CW4
limitation 1
before go to chaed party
updated discussion done

@@
 
-\large \textit{Submitted in part fulfillment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
+\large \textbf{Submitted in part fulfillment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
 %\textit{in the}\\[0.4cm]
@@
 \addchaptertocentry{\abstractname} % Add the abstract to the table of contents
-The National Diet and Nutrition Survey (NDNS) database of detailed four-day food diaries was used to \dots
+The National Diet and Nutrition Survey (NDNS) database of detailed four-day food diaries was used in exploration of both temporal and quantity eating patterns of carbohydrates in the general adults living in the UK.
+6155 participants aged 19 or older were kept in the analysis.
+\\
+Multilevel latent class analysis (MLCA) models were applied in finding the latent classes of carbohydrate consumption both at the observation day level, and individual level.
 \end{abstract}
@@
 \textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
-%\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
-%\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
+\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
+\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
 \textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
@@
 \textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
+\textbf{RMLCA} & \textbf{R}epeated \textbf{Measures} \textbf{LCA} \\
 \textbf{TC} & \textbf{T}otal \textbf{C}holesterol \\
@@
 \include{Appendices/AppendixC}
+\include{Appendices/AppendixD}
+\include{Appendices/AppendixE}
 

### 2018-08-19 paper/Chapters/Chapter4.tex
adding strengths in the discussion

@@
 
+Strengths of this study include the large, nationally representative sample of men and women in the UK.
+We applied a novel, objective approach using MLCA to examine the carbohydrate eating patterns while using standardised criteria to determine the numbers of latent classes.
+The process of finding the classifications through model-based, data-driven procedure minimises reliance on researchers' preconcieved notions of eating patterns.
+Eating patterns were determined from 4 consecutive days of well-designed, fully-examined food diaries.
+MLCA correctly accounted for the multilevel structure of the data which means that the 4-day diet diaries were nested within the participants.
+Our findings also captured the day-to-day variation of following different carbohydrate eating patterns within individuals.
+Moreover, the examination of associations between the individual level carbohydrate eating patterns and hypertension, BMI, abdominal obesity were conducted correctly considering the probability of participant selection and the clustered survey design.
+Health outcomes such as weight, height, waist circumferences, and blood pressure, diabetes status were measured by trained nurses and blood tests which could also minimise the misclassification and under-reporting of these measurements.
+
 \section{Conclusions}

### 2018-08-20 paper/Appendices/AppendixA.tex
limitation 1
abstract almost done, proof reading first round done

@@
 \KeywordTok{setwd}\NormalTok{(}\StringTok{".../UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }
-\KeywordTok{setwd}\NormalTok{(}\StringTok{"~/Downloads/UKDA-6533-stata11_se/stata11_se/"}\NormalTok{)}
 \KeywordTok{library}\NormalTok{(epiDisplay)}
@@
 \NormalTok{var <-}\StringTok{ }\KeywordTok{names}\NormalTok{(df14d)}
-\NormalTok{df56d <-}\StringTok{ }\NormalTok{data56 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{df56d <-}\StringTok{ }\NormalTok{data56 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(var)}
-\NormalTok{df78d <-}\StringTok{ }\NormalTok{data78 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{df78d <-}\StringTok{ }\NormalTok{data78 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(var)}
@@
 
-\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs3 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs3 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{id_dy =} \KeywordTok{paste}\NormalTok{(id, DayNo, }\DataTypeTok{sep =} \StringTok{"D"}\NormalTok{))}
@@
 \NormalTok{### midnight:        10pm to 6am}
-\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{TimeSlot =} \KeywordTok{cut}\NormalTok{(MealHourN, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{12}\NormalTok{, }\DecValTok{14}\NormalTok{, }\DecValTok{17}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{22}\NormalTok{), }
@@
 \CommentTok{# Calculate the energy from total carbohydrates ---------------------------}
-\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{KJcarbo =}\NormalTok{ Tot_Carb}\OperatorTok{*}\DecValTok{16}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CarKJpercentage =}\NormalTok{ KJcarbo}\OperatorTok{/}\NormalTok{Tot_Energ) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{KJcarbo =}\NormalTok{ Tot_Carb}\OperatorTok{*}\DecValTok{16}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CarKJpercentage =}\NormalTok{ KJcarbo}\OperatorTok{/}\NormalTok{Tot_Energ) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.50}\NormalTok{, }\DecValTok{2}\NormalTok{), }\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
@@
 \KeywordTok{write.csv}\NormalTok{(Energy0, }\DataTypeTok{file =} \StringTok{"Energy_slots.csv"}\NormalTok{) }\CommentTok{# for later analysis}	
-\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"< 50%"}\NormalTok{, }\StringTok{">= 50%"}\NormalTok{))}
+\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"< 50\%"}\NormalTok{, }\StringTok{">= 50\%"}\NormalTok{))}
 
@@
 
-\NormalTok{dta_day1 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{dta_day1 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
-\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
+\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{  }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
@@
 
-\NormalTok{dta_day2 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{2}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{dta_day2 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{2}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
-\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
+\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{  }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
@@
 
-\NormalTok{dta_day3 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{dta_day3 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
-\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
+\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{  }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
@@
 
-\NormalTok{dta_day4 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{dta_day4 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
-\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
+\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{  }
 StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
@@
 \CommentTok{# Long to wide data -------------------------------------------------------}
-\NormalTok{dta_d1_wide <-}\StringTok{ }\NormalTok{dta_day1 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{dta_d1_wide <-}\StringTok{ }\NormalTok{dta_day1 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
@@
 \KeywordTok{names}\NormalTok{(dta_d1_wide)}
-\NormalTok{dta_d2_wide <-}\StringTok{ }\NormalTok{dta_day2 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{dta_d2_wide <-}\StringTok{ }\NormalTok{dta_day2 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
@@
 \KeywordTok{names}\NormalTok{(dta_d2_wide)}
-\NormalTok{dta_d3_wide <-}\StringTok{ }\NormalTok{dta_day3 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{dta_d3_wide <-}\StringTok{ }\NormalTok{dta_day3 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
@@
 \KeywordTok{names}\NormalTok{(dta_d3_wide)}
-\NormalTok{dta_d4_wide <-}\StringTok{ }\NormalTok{dta_day4 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{dta_d4_wide <-}\StringTok{ }\NormalTok{dta_day4 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }

### 2018-08-20 paper/Appendices/AppendixD.tex
abstract almost done, proof reading first round done

@@
 
-\NormalTok{CW3idday <-}\StringTok{ }\NormalTok{CW3CB3 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{CW3idday <-}\StringTok{ }\NormalTok{CW3CB3 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(ID, ID_DAY, CW, CB, MLCJOINT, AGE, SEX)}
@@
 \NormalTok{Energy_slots <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"../Energy_slots.csv"}\NormalTok{) }\CommentTok{# change the path accordingly}
-\NormalTok{Energy_slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Energy_slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{ID =}\NormalTok{ id)}
@@
 
-\NormalTok{Energy_slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Energy_slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{left_join}\NormalTok{(CW3idday, }\DataTypeTok{by =} \KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{))}
@@
 
-\NormalTok{FoodbyCB_7slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{group_by}\NormalTok{(ID, TimeSlot) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{FoodbyCB_7slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{group_by}\NormalTok{(ID, TimeSlot) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{sumEnergy =} \KeywordTok{sum}\NormalTok{(Tot_Energ),}
@@
 \CommentTok{# Calculate the sum of each nutrients for each time slots}
-\NormalTok{Carbsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumCarb) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Carbsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumCarb) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
@@
 
-\NormalTok{Energysum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumEnergy) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Energysum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumEnergy) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
@@
 
-\NormalTok{Starchsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumStarch) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Starchsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumStarch) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
@@
 
-\NormalTok{Sugarsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumSugar) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Sugarsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumSugar) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
@@
 
-\NormalTok{Fibresum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumFibre) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Fibresum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumFibre) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
@@
 
-\NormalTok{NMESsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumNMES) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{NMESsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumNMES) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
@@
 
-\NormalTok{Fatsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumFat) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Fatsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumFat) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
@@
 
-\NormalTok{Protsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumProt) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Protsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumProt) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
@@
 
-\NormalTok{Alcsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumAlc) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Alcsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumAlc) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
@@
 
-\NormalTok{NDAYS14 <-}\StringTok{ }\NormalTok{blood14 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{NDAYS14 <-}\StringTok{ }\NormalTok{blood14 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(ID, Ndays)}
 
-\NormalTok{NDAYS56 <-}\StringTok{ }\NormalTok{blood56 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{NDAYS56 <-}\StringTok{ }\NormalTok{blood56 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(ID, Ndays)}
 
-\NormalTok{NDAYS78 <-}\StringTok{ }\NormalTok{blood78 }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(ID, NDays) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{NDAYS78 <-}\StringTok{ }\NormalTok{blood78 }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(ID, NDays) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{Ndays =}\NormalTok{ NDays)}
@@
 
-\NormalTok{IntakeSlots <-}\StringTok{ }\NormalTok{Energysum }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{left_join}\NormalTok{(Carbsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{left_join}\NormalTok{(Sugarsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{left_join}\NormalTok{(Starchsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{left_join}\NormalTok{(Fibresum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{left_join}\NormalTok{(Fatsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{left_join}\NormalTok{(Protsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{left_join}\NormalTok{(NMESsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{left_join}\NormalTok{(Alcsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{IntakeSlots <-}\StringTok{ }\NormalTok{Energysum }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Carbsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Sugarsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Starchsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Fibresum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Fatsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Protsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(NMESsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(Alcsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{left_join}\NormalTok{(NDAYS, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{)}
@@
 
-\NormalTok{BMI78 <-}\StringTok{ }\NormalTok{blood78 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{BMI78 <-}\StringTok{ }\NormalTok{blood78 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(ID, Sex, age, bmival, wstval, Diabetes, bpmedc2, bpmedd2, }
@@
 \NormalTok{         qual7, eqvinc, MarSt2, cluster4, cluster5, area, gor, }
-\NormalTok{         LDL, HDL, Chol, Trig) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{         LDL, HDL, Chol, Trig) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{wti =}\NormalTok{ wti_Y78, }\DataTypeTok{wtn =}\NormalTok{ wtn_Y78, }\DataTypeTok{wtb =}\NormalTok{ wtb_Y78, }
-         \DataTypeTok{drink =}\NormalTok{ dnoft3) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Years =} \StringTok{"7-8"}\NormalTok{, }\DataTypeTok{MVPAtime =} \OtherTok{NA}\NormalTok{, }\DataTypeTok{MarStat =} \OtherTok{NA}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+         \DataTypeTok{drink =}\NormalTok{ dnoft3) }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Years =} \StringTok{"7-8"}\NormalTok{, }\DataTypeTok{MVPAtime =} \OtherTok{NA}\NormalTok{, }\DataTypeTok{MarStat =} \OtherTok{NA}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{bmival =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{qual7 =} \OperatorTok{-}\DecValTok{8}\NormalTok{,}
@@
                                  \DataTypeTok{ethgrp2 =} \OperatorTok{-}\DecValTok{4}\NormalTok{, }\DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
-                                 \DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{9}\NormalTok{,  }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{1}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+                                 \DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{9}\NormalTok{,  }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{1}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{hyper140_2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{hibp140_2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
                                  \DataTypeTok{nssec8 =} \DecValTok{99}\NormalTok{, }\DataTypeTok{qual7 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{drink =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }
-                                 \DataTypeTok{ethgrp2 =} \OperatorTok{-}\DecValTok{9}\NormalTok{, }\DataTypeTok{ethgrp5 =} \OperatorTok{-}\DecValTok{9}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+                                 \DataTypeTok{ethgrp2 =} \OperatorTok{-}\DecValTok{9}\NormalTok{, }\DataTypeTok{ethgrp5 =} \OperatorTok{-}\DecValTok{9}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{drink =} \OperatorTok{-}\DecValTok{9}\NormalTok{, }\DataTypeTok{ethgrp2 =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }\DataTypeTok{ethgrp5 =} \OperatorTok{-}\DecValTok{8}\NormalTok{,}
-                                 \DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{8}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+                                 \DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{8}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{ethgrp2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{ethgrp5 =} \OperatorTok{-}\DecValTok{1}\NormalTok{))}
 
-\NormalTok{BMI56 <-}\StringTok{ }\NormalTok{blood56 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{BMI56 <-}\StringTok{ }\NormalTok{blood56 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(ID, Sex, age, area, bmival, wstval, Diabetes, bpmedc2, bpmedd2, }
@@
 \NormalTok{         cluster1, cluster2, cluster3, nssec8, paidemployment, eqvinc, }
-\NormalTok{         MarSt2, cluster4, cluster5, area, gor, LDL, HDL, Chol, Trig) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Years =} \StringTok{"5-6"}\NormalTok{, }\DataTypeTok{MarStat =} \OtherTok{NA}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{wti =}\NormalTok{ wti_Y56, }\DataTypeTok{wtn =}\NormalTok{ wtn_Y56, }\DataTypeTok{wtb =}\NormalTok{ wtb_Y56, }\DataTypeTok{drink =}\NormalTok{ dnoft3) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{         MarSt2, cluster4, cluster5, area, gor, LDL, HDL, Chol, Trig) }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Years =} \StringTok{"5-6"}\NormalTok{, }\DataTypeTok{MarStat =} \OtherTok{NA}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{wti =}\NormalTok{ wti_Y56, }\DataTypeTok{wtn =}\NormalTok{ wtn_Y56, }\DataTypeTok{wtb =}\NormalTok{ wtb_Y56, }\DataTypeTok{drink =}\NormalTok{ dnoft3) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{bmival =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{9}\NormalTok{,}
@@
                                  \DataTypeTok{Chol =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{Trig =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{1}\NormalTok{,}
-                                 \DataTypeTok{MVPAtime =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{9}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+                                 \DataTypeTok{MVPAtime =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{9}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{hyper140_2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{hibp140_2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
                                  \DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }
-                                 \DataTypeTok{drink =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }\DataTypeTok{nssec8 =} \DecValTok{99}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+                                 \DataTypeTok{drink =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }\DataTypeTok{nssec8 =} \DecValTok{99}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{    }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{drink =} \OperatorTok{-}\DecValTok{9}\NormalTok{, }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
@@
 
-\NormalTok{BMI14 <-}\StringTok{ }\NormalTok{blood14 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{BMI14 <-}\StringTok{ }\NormalTok{blood14 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(ID, Sex, age, bmival, wstval, Diabetes, bpmedc, bpmedd, hyper140, }
@@
 \NormalTok{         area, gor, nssec8, paidemployment, qual7, eqvinc, MarSt2, }
-\NormalTok{         MarStat, LDL, HDL, Chol, Trig) }\OperatorTok{%>%}
+\NormalTok{         MarStat, LDL, HDL, Chol, Trig) }\OperatorTok{\%>\%}
 \StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{hyper140_2 =}\NormalTok{ hyper140, }\DataTypeTok{hibp140_2 =}\NormalTok{ hibp140, }\DataTypeTok{bpmedd2 =}\NormalTok{ bpmedd, }
@@
          \DataTypeTok{ethgrp2 =}\NormalTok{ ethgr2, }\DataTypeTok{wti =}\NormalTok{ wti_CY1234, }\DataTypeTok{wtn =}\NormalTok{ wtn_CY1234, }
-         \DataTypeTok{wtb =}\NormalTok{  wtb_CY1234, }\DataTypeTok{drink =}\NormalTok{ dnoft3) }\OperatorTok{%>%}\StringTok{ }
+         \DataTypeTok{wtb =}\NormalTok{  wtb_CY1234, }\DataTypeTok{drink =}\NormalTok{ dnoft3) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{cluster2 =} \OtherTok{NA}\NormalTok{, }\DataTypeTok{cluster3 =} \OtherTok{NA}\NormalTok{, }\DataTypeTok{cluster4 =} \OtherTok{NA}\NormalTok{, }\DataTypeTok{cluster5 =} \OtherTok{NA}\NormalTok{, }
-         \DataTypeTok{Years =} \StringTok{"1-4"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+         \DataTypeTok{Years =} \StringTok{"1-4"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{bmival =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{9}\NormalTok{, }
@@
                                  \DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{MVPAtime =} \OperatorTok{-}\DecValTok{4}\NormalTok{,  }
-                                 \DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{8}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+                                 \DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{8}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{hyper140_2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{hibp140_2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
@@
                                  \DataTypeTok{drink =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }\DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }\DataTypeTok{qual7 =} \OperatorTok{-}\DecValTok{1}\NormalTok{, }
-                                 \DataTypeTok{MarSt2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+                                 \DataTypeTok{MarSt2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{drink =} \OperatorTok{-}\DecValTok{9}\NormalTok{, }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{4}\NormalTok{,}
-                                 \DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }\DataTypeTok{nssec8 =} \DecValTok{99}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
+                                 \DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }\DataTypeTok{nssec8 =} \DecValTok{99}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{replace_with_na}\NormalTok{(}\DataTypeTok{replace =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{1}\NormalTok{))}
@@
 
-\NormalTok{Energy14 <-}\StringTok{ }\NormalTok{food14 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Energy14 <-}\StringTok{ }\NormalTok{food14 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, }
@@
 
-\NormalTok{Energy56 <-}\StringTok{ }\NormalTok{food56 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Energy56 <-}\StringTok{ }\NormalTok{food56 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(ID, Country, Surveyyear, EnergykJ, Carbohydrateg, }
 \NormalTok{         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,}
-\NormalTok{         Fatg, FatpctotE) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{         Fatg, FatpctotE) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{SurveyYear =}\NormalTok{ Surveyyear)}
 
-\NormalTok{Energy78 <-}\StringTok{ }\NormalTok{food78 }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{Energy78 <-}\StringTok{ }\NormalTok{food78 }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, }
@@
 
-\NormalTok{dta_DayofWeek <-}\StringTok{ }\NormalTok{dta_NDNS }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{dta_DayofWeek <-}\StringTok{ }\NormalTok{dta_NDNS }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(id, id_dy, DayofWeek)}
@@
 
-\NormalTok{CW3idday <-}\StringTok{   }\NormalTok{CW3idday }\OperatorTok{%>%}\StringTok{  }
+\NormalTok{CW3idday <-}\StringTok{   }\NormalTok{CW3idday }\OperatorTok{\%>\%}\StringTok{  }
 \StringTok{  }\KeywordTok{left_join}\NormalTok{(dta_DayofWeek, }\DataTypeTok{by=} \KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"DayNo"}\NormalTok{))}
@@
 \CommentTok{# extract only the CB variable (Between individual classes == 1 or 2)}
-\NormalTok{CW3CB3_reg <-}\StringTok{ }\NormalTok{CW3CB3_reg }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{CW3CB3_reg <-}\StringTok{ }\NormalTok{CW3CB3_reg }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{select}\NormalTok{(ID, AGE, SEX, CB) }
@@
 \NormalTok{## dataset for 3by3 multilevel latent classes }
-\NormalTok{CW3CB3_regss <-}\StringTok{ }\NormalTok{CW3CB3_reg }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{left_join}\NormalTok{(BMI, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{CW3CB3_regss <-}\StringTok{ }\NormalTok{CW3CB3_reg }\OperatorTok{\%>\%}\StringTok{ }
+\StringTok{  }\KeywordTok{left_join}\NormalTok{(BMI, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{left_join}\NormalTok{(Energy, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }
@@
 
-\NormalTok{weightings <-}\StringTok{ }\NormalTok{CW3CB3_regss }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(ID, wti1to8, wtn1to8, wtb1to8)}
+\NormalTok{weightings <-}\StringTok{ }\NormalTok{CW3CB3_regss }\OperatorTok{\%>\%}\StringTok{ }\KeywordTok{select}\NormalTok{(ID, wti1to8, wtn1to8, wtb1to8)}
 
 \CommentTok{# Combine the data from nutrient intake at each time slot}
-\NormalTok{CW3CB3_7regss <-}\StringTok{ }\NormalTok{CW3CB3_7regss }\OperatorTok{%>%}\StringTok{ }
+\NormalTok{CW3CB3_7regss <-}\StringTok{ }\NormalTok{CW3CB3_7regss }\OperatorTok{\%>\%}\StringTok{ }
 \StringTok{  }\KeywordTok{left_join}\NormalTok{(IntakeSlots, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{)}

### 2018-08-20 paper/Appendices/AppendixE.tex
abstract almost done, proof reading first round done

@@
 \decoRule
-\caption[One day food diary example 6 am to 2 pm]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, from 6 am to 2 pm.}
+\caption[One day food diary example 6 am to 12 noon.]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, from 6 am to 12 noon.}
 \label{fig:diary1}
@@
 
-\begin{figure}[H]
+\begin{figure}
 %\vspace*{13cm}
@@
 \decoRule
-\caption[One day food diary example 2 pm to 6 am]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, from 2 pm to 6 am.}
+\caption[One day food diary example 12 noon to 5 pm]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, from 12 noon to 5 pm.}
 \label{fig:diary2}
@@
 
-\begin{figure}[H]
+\begin{figure}
+	%\vspace*{13cm}
+	\centering
+	\includegraphics{Figures/Diary03.png}
+	\decoRule
+	\caption[One day food diary example 5 pm to 6 am]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, from 5 pm to 6 am.}
+	\label{fig:diary2}
+\end{figure}
+%\end{verbatim}
+
+\begin{figure}
 %\vspace*{13cm}

### 2018-08-20 paper/Chapters/Chapter2.tex
abstract almost done, proof reading first round done

@@
 The percentages of energy that contributed by carbohydrate within each time slot were then estimated.
-Since we planed to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical, we then dichotomised the responses according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e.
+Since we planned to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical, the responses were then dichotomised according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e.
 if within a time slot where there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was lower or higher/equal to 50\% of total energy intake within that time slot.
@@
 
-Computer assisted personal interviews were conducted for the selected individuals by trained interviewers to collect background information on smoking habits (current, ex-smokers, and never), ethnicity (white, non-white), education level (lower than degree/degree or above level), living with a partner or not and other socio-demographic related variables.
+Computer assisted personal interviews were conducted for the selected individuals by trained interviewers to collect background information on smoking habits (current, ex-smokers, and never), ethnicity (white, non-white), education level (lower than degree/degree or above level), living with a partner or not and other socio-demographic variables.
 Participants also had their height, weight, blood pressure, waist circumferences (WC) measured by the nurses.
 
-Specifically, blood pressure was measured in a sitting position using an automated, validated machine, the Omron HEM907, after a five minute rest.
+Specifically, blood pressure was measured in a sitting position using an automated, validated machine, the Omron HEM907, after a five-minute rest.
 The means of second and third readings, taken at one minute intervals, were used in the current report.
@@
 \begin{equation}
-P(U_{i1} = s_1, U_{i2} = s_2, \cdots, U_{ik} = s_K) = \sum_{t=t}^{T}P(C_i = t)\prod_{k = 1}^{K}P(U_{ik} = s_k | C_i = t)
+P(U_{i1} = s_1, U_{i2} = s_2, \cdots, U_{ik} = s_k) = \sum_{t=t}^{T}P(C_i = t)\prod_{k = 1}^{K}P(U_{ik} = s_k | C_i = t)
 \label{LCA}
@@
 \begin{itemize}
-	\item $P(U_{i1} = s_1, U_{i2} = s_2, \cdots, U_{ik} = s_k)$ is the probability of observing a particular vector of responses;
+	\item $P(U_{i1} = s_1, U_{i2} = s_2, \cdots, U_{ik} = s_k)$ is the probability of observing a particular vector of responses for $i$th observation;
 	\item $P(C_i = t)$ is the probability that a randomly selected $i$th observation will be in class $t$;
-	\item $P(U_{ik} = s_k | C_i = t)$ is the probability of a particular observed response pattern $U_{ik} = s_k$ conditional on membership in latent class $t$.
+	\item $P(\mathbf{U_{ik}} = \mathbf{s_k} | C_i = t)$ is the probability of a particular observed response pattern $\mathbf{U_{ik}} = \mathbf{s_k}$ conditional on membership in latent class $t$.
 \end{itemize}
@@
 However, in the NDNS RP data set, the assumption of independent observations is violated.
-Each individual completed their dietary diary for four consecutive days, their diary recordings were later converted into four sequences of categorical responses reflecting the type of carbohydrate consumption at each time slot of the day.
-The four observed sequences (observed days) are nested in the participants and therefore are not independent.
+Each individual completed their dietary diary for three/four consecutive days, their diary recordings were later converted into three/four sequences of categorical responses reflecting the type of carbohydrate consumption at each time slot of the day.
+The observed sequences (observed days) are nested within the participants and therefore are not independent.
 This nested data structure requires multilevel techniques.
@@
 \begin{itemize}
-	\item $\text{logit}{(x)} = \frac{\log(x)}{\log(1-x)}$;
+	\item $\text{logit}{(x)} = \log{\frac{x}{1-x}}$, where $x \in [0,1]$;
 	\item $P(C_{ij} = 1)$ as the probability that the randomly selected $i$th observation day of $j$th individual is a high carbohydrate eating day;
@@
 If the day level LCA model (carbohydrate eating temporal pattern typologies) is best defined by $T (T \geqslant 2)$ latent classes, then $T-1$ random intercept will be specified by a two-level multinomial logistic regression model.
-Similar to the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each time slots, throughout 4 consecutive days of survey period).
+Similar to the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each time slots, throughout three/four consecutive days of their survey period).
 Considering the latent class indicators are indicator variables ($U_{ijk}$), the MLCA model can be written as follows:\vspace{-1cm}
@@
 %\begin{aligned}
-P(U_{ij1} = s_1, U_{ij2} = s_2, \cdots, U_{ijk} = s_{K}) = \sum_{t=1}^{T}P(G_{ij}=t)\prod_{k=1}^{K}P(U_{ijk} = s_k | G_{ij} = t)
+P(U_{ij1} = s_1, U_{ij2} = s_2, \cdots, U_{ijk} = s_{k}) = \sum_{t=1}^{T}P(G_{ij}=t)\prod_{k=1}^{K}P(U_{ijk} = s_k | G_{ij} = t)
 %\end{aligned}
@@
 \begin{itemize}
-	\item $ U_{ijk} $ represents the response of eating carbohydrate (one of the following: not eating any food, $< 50\%$ of the energy, or $\geqslant 50\%$ of the energy) on $i$th day of the survey ($i \in (1,2,3,4)$) in $j$th individual at the $k$th time slot of the day ($k \in (1, 2, 3, \cdots, 7)$);
+	\item $ U_{ijk} $ represents the response of carbohydrate eating (one of the following: not eating any food, $< 50\%$ of the energy, or $\geqslant 50\%$ of the energy) on $i$th day of the survey ($i \in (1,2,3,4)$) in $j$th individual at the $k$th time slot of the day ($k \in (1, 2, 3, \cdots, 7)$);
 	\item $G_{ij}$ denotes the latent class membership for $j$th individuals on $i$th day of the survey, the total number of day level latent class is $T$;
@@
 This approach is less computationally demanding compared with the parametric approach.
-These level 2 (individual) latent classes reflect differences in the probability of belonging to a specific day level latent class, so that individuals that contain observation days with similar probabilities for the level 1 latent classes will be grouped together.
-The non-parametric MLCA model can be defined as follows: \vspace{-0.7cm}
+These level 2 (individual) latent classes reflect differences in the probability of belonging to a specific day level latent class, so that individuals that have observation days with similar probabilities for the level 1 latent classes will be grouped together.
+The non-parametric MLCA model can be defined as follows:
 
@@
 In these models, the number of day-level classes was based on the best fitting LCA model from the first step, and the LCA model at the individual level was estimated to identify the number of individual level latent classes;
-	\item Thirdly, when number of individual level latent classes is defined based on the previous stage, day-level classes was modified (one class lower and one class higher than in the second step) to see the effect of changing level 1 classes and confirm the best fitting model.
+	\item Thirdly, when number of individual level latent classes is defined based on the previous stage, number of day-level classes was modified (one class lower and one class higher than in the second step) to see the effect of changing level 1 classes and confirm the best fitting model.
 \end{itemize}
 
-The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Bayesian information criterion (BIC), and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compares $q$ vs.
+The number of classes in level 1 was determined by 1) the evaluation of model fit indices, including the Bayesian information criterion (BIC), and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compares $q$ vs.
 $q-1$ classes models, where $q$ is the number of latent classes and most importantly, 3) pattern interpretability.
@@
 Person level point estimates and 95\% confidence intervals (CIs) were determined by applying individual, nurse visiting, and blood sample weights accordingly which account for the probability of participant selection and the clustered survey design.
-Descriptive statistics for sample characteristics are presented as weighted means (95\% CI) or weighted percentages (95\%CI).
+Descriptive statistics for sample characteristics were presented as weighted means (95\% CI) or weighted percentages (95\%CI).
 After examining the distribution of the data, the following variables were log-transformed to improve normality: fasting blood glucose, A1C, TC, LDL, HDL, TG, and average physical activity duration per day.
@@
 General checking such as QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance) are not available as well.
-Outliers, leverage, and Cook's distance cannot be check either, however, participants with extreme weightings (if exist) were checked by removing them and refit the models as a sensitivity analysis.
+Outliers, leverage, and Cook's distance cannot be checked either, however, participants with extreme weightings (if exist) were checked by removing them and refit the models as a sensitivity analysis.
 	\item Since under survey design data, the sampling-weighted least squares are not maximum likelihood, it would not be possible to compare models using likelihood ratio test.

### 2018-08-20 paper/Chapters/Chapter3.tex
abstract almost done, proof reading first round done

@@
 It is obvious that the BIC improves with the addition of the random effects which account for the nested structure of the data.
-Entropy indicates that 4 classes in individual level and 2 classes in the day level may be the best solution mathematically.
+Entropy indicates that 2 classes in the day level and 4 classes in the individual level may be the best solution mathematically.
 However, after these solutions were checked in more details, the potentially most substantively interpretable model was found to be the 3$\times$3 random effect model, which is the model with 3 latent classes in the day level, and 3 latent classes in the individual level.
-We must emphasize that different researchers may have made decision slightly different from ours, we provided the descriptions and figures for other solutions in the \textbf{Appendix \ref{AppendixC}} for reference.
+We must emphasize that different researchers may have made decision slightly different from ours, we have provided other solutions in the \textbf{Appendix \ref{AppendixC}} for reference.
 
 In the 3$\times$3 random effect model solution we have chosen, there were 39.5\%, 20.4\%, and 40.1\% observations classified into 3 latent groups in the day level.
-The overall counts and percentages for each responses within every time slot and the distributions of the solution are presented in \textbf{Table \ref{tab:daylevel}}.
+The overall counts and percentages for each responses within each time slot and the distributions of the solution are presented in \textbf{Table \ref{tab:daylevel}}.
 The trajectories illustrating the change of the probabilities of each response to carbohydrate eating during the hours of the day are shown separately by three types of days in \textbf{Figure \ref{fig:level1}}.
@@
 
-The details of the characteristics of the three types of carbohydrate eating time pattern were listed in\textbf{ Table \ref{tab:day-level-features}}.
+The details of the characteristics of the three types of carbohydrate eating temporal patterns were listed in\textbf{ Table \ref{tab:day-level-features}}.
 Specifically, regular meals day turned to be recorded slightly more often in Northern Ireland, and Scotland.
-In terms of day of week distribution in the three types of days, there is strong evidence (\textit{p} < 0.001) that high carbohydrate days appeared more frequently in weekends (32.5\%) compared with low carbohydrate day (26.5\%) and regular meals day (30.7\%).
+In terms of day of week distribution in the three types of days, there is strong evidence (\textit{p} < 0.001) that high percentage carbohydrate days appeared more frequently in weekends (32.5\%) compared with low carbohydrate day (26.5\%) and regular meals day (30.7\%).
 
@@
 With three individual level latent classes \textbf{(Figure \ref{fig:level2})}, a low-carbohydrate eaters class, a moderate-carbohydrate eaters class, and a high-carbohydrate eaters class emerges.
-43.1\% participants were identified as high-carbohydrate eaters, in these individuals, about 50\% of the days (2 out of 4 days) of their dietary diary could be classified as having high carbohydrate days.
+43.1\% participants were identified as high-carbohydrate eaters, in these individuals, about 50\% of the days (2 out of 4 days) of their dietary diary could be classified as having high percentage carbohydrate days.
 Nearly 1 out of 4 days of their dietary diary were either "regular meals day" or "low carbohydrate day".
@@
 Energy from fat were the highest for low carbohydrate eaters most of the time during the day (except for time between 10 pm to 6 am next morning).
-Most impressively, energy from alcohol were always the highest in low carbohydrate eaters, percentages for energy from alcohol for the 7 times slots were 1.4\% (6-9 am), 1.8\% (9-12 noon), 3.1\% (12-2 pm), 7.2\% (2-5 pm), 8.4\% (5-8 pm), 20.0\% (8-10 pm), and 31.2\% (10 - 6 am), respectively.
-Contribution from different energy sources are quite similar for moderate and high carbohydrate eaters, but their absolute amount of energy consumption at each time slot were largely different.
+Most impressively, energy contributed by alcohol was always the highest in low carbohydrate eaters, percentages for energy from alcohol for the 7 times slots were 1.4\% (6-9 am), 1.8\% (9-12 noon), 3.1\% (12-2 pm), 7.2\% (2-5 pm), 8.4\% (5-8 pm), 20.0\% (8-10 pm), and 31.2\% (10-6 am), respectively.
+Contributions from different energy sources were quite similar for moderate and high carbohydrate eaters, but their absolute amount of energy consumption at each time slot were largely different.
 Moderate carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-B)} were characterised as consuming the lowest energy (296.9 kJ) before 9 am, but having higher energy consumption (967.9 kJ) between 9 am and 12 noon time compared with low and high carbohydrate eaters.
@@
 High carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-C)} consumed the highest total energy (929.0 kJ) during 6 am to 9 am in the morning and the lowest total energy between 10 pm to 6 am (205.5 kJ).
-Specifically, carbohydrate contribution to total energy intake were 65.3\% (6-9 am), 56.2\% (9-12 noon), 46.2\% (12-2 pm), 50.3\% (2-5 pm), 42.5\% (5-8 pm), 44.1\% (8-10 pm), and 49.9\% (10-6am).
+Specifically, carbohydrate contributions to total energy intake were 65.3\% (6-9 am), 56.2\% (9-12 noon), 46.2\% (12-2 pm), 50.3\% (2-5 pm), 42.5\% (5-8 pm), 44.1\% (8-10 pm), and 49.9\% (10-6am).
 We also noticed that high carbohydrate eaters consumed their energy mainly from three time slots: 6-9 am, 12-2 pm, and 5-8 pm.
 
-As expected, in total, the mean of carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively \textbf{(Table \ref{tab:tab-nutri-indi})}.
-Energy contribution from carbohydrate was close to 50\% in the high carbohydrate eaters, but was only 40.6\% in the low carbohydrate eaters.
+As expected, in total, the mean of total carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively \textbf{(Table \ref{tab:tab-nutri-indi})}.
+Total energy contributed by carbohydrate was close to 50\% in the high carbohydrate eaters, but was only 40.6\% in the low carbohydrate eaters.
 In terms of the subtypes (components) of the carbohydrate consumed at each time slot, high carbohydrate eaters consumed as much as more than 2 times (compared to low carbohydrate eaters) and nearly 4 times (against moderate carbohydrate eaterss) the amount of sugar (37.9g 95\% CI: 36.8, 39.2) and non-milk extrinsic sugar (i.e.
@@
 		\multicolumn{5}{l}{{\scriptsize  in multiple groups for continuous variables;}}\\
-		\multicolumn{5}{l}{\textsuperscript{\dag} NMES, Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey, }\\
+		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\dag} NMES, Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey, }}\\
 		\multicolumn{5}{l}{{\scriptsize glucose, fructose and glucose syrups, sugars added to food and sugars in fruit juices.}}\\
@@
 The social-demographic characteristics of the UK adults according to their individual level latent class membership are shown in \textbf{Table \ref{tab:Level2tab1}}.
-Moderate carbohydrate eaters were relatively younger (\textit{p} < 0.001), and slightly less from England (\textit{p} = 0.007).
+Moderate carbohydrate eaters were relatively younger (\textit{p} < 0.001).
 Gender distribution across the three types of carbohydrate eaters was fairly even (\textit{p} = 0.119).
@@
 
-Weighted means, percentages of anthropometric measurements, average of main nutrients intake, as well as biochemical characteristic profiles according to the latent carbohydrate eater groups are given in \textbf{Table \ref{tab:tab2}}.
+Weighted means, percentages of anthropometric measurements, as well as biochemical characteristic profiles according to the latent carbohydrate eater groups are given in \textbf{Table \ref{tab:tab2}}.
 Low carbohydrate eaters had higher mean BMI (27.8 kg/m\textsuperscript{2}) and larger mean WC (98.9/89.9 cm in men/women) compared with 27.2, 27.3 kg/m\textsuperscript{2}, and 95.9/88.7 (men/women), 98.1/87.2 (men/women) cm in moderate and high carbohydrate eaters.
@@
 From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetic (diagnosed by A1C > 6.5\%), while the percentages of diabetes in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011), respectively.
-Although there was some evidence (\textit{p} = 0.027) that fasting blood glucose level may be slightly higher in non-diabetic low carbohydrate eaters, the geometric mean for
+Although there was some evidence (\textit{p} = 0.027) that fasting blood glucose level may be slightly higher in non-diabetic low carbohydrate eaters, the geometric mean for A1C was probably lower in moderate carbohydrate eaters (5.43, 95\%CI: 5.39, 5.47).
+Total cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.
 
@@
 	Total (\%) & 28.4 (26.9, 29.9) & 28.7 (27.1, 30.3) & 43.0 (41.3, 44.7) & \\
-	Country (\%) &  &  &  & 0.007\\
-	\hspace{1em}England & 84.5 (81.7, 86.9) & 82.0 (79.3, 84.5) & 84.7 (82.3, 86.8) & \\
-	\hspace{1em}Northern Ireland & 2.1 (1.6, 2.8) & 4.2 (3.2, 5.6) & 2.2 (1.7, 3.0) & \\
-	\hspace{1em}Scotland & 9.1 (7.0, 11.8) & 8.6 (6.7, 11.1) & 8.0 (6.3, 10.2) & \\
-	\hspace{1em}Wales & 4.3 (3.3, 5.6) & 5.1 (4.0, 6.4) & 5.1 (4.0, 6.4) & \\
+%	Country (\%) &  &  &  & 0.007\\
+%	\hspace{1em}England & 84.5 (81.7, 86.9) & 82.0 (79.3, 84.5) & 84.7 (82.3, 86.8) & \\
+%	\hspace{1em}Northern Ireland & 2.1 (1.6, 2.8) & 4.2 (3.2, 5.6) & 2.2 (1.7, 3.0) & \\
+%	\hspace{1em}Scotland & 9.1 (7.0, 11.8) & 8.6 (6.7, 11.1) & 8.0 (6.3, 10.2) & \\
+%	\hspace{1em}Wales & 4.3 (3.3, 5.6) & 5.1 (4.0, 6.4) & 5.1 (4.0, 6.4) & \\
 	Age (years) & 51.0 (49.9, 52.1) & 40.3 (39.1, 41.6) & 51.7 (50.7, 52.7) & < 0.001\\
@@
 
-A1C was probably lower in moderate carbohydrate eaters (4.72, 95\%CI: 5.39, 5.47).
-Total cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.
-
 \rowcolors{2}{gray!6}{white}
@@
 
-	\caption{\label{tab:tab2}Weighted means, percentages, and 95\% CIs of the anthropometric measurements, average main nutrients intake and biochemical characteristics by carbohydrate eating latent class memberships in the UK adults.
+	\caption{\label{tab:tab2}Weighted means, percentages, and 95\% CIs of the anthropometric measurements, and biochemical characteristics by carbohydrate eating latent class memberships in the UK adults.
 (NDNS RP 2008/09-15/16, sample size = 6155)}
@@
 27862.0 \textsterling/year in hypertensive, \textit{p} < 0.001), and physical activity level (geometric mean: 0.81 hours/day in non-hypertensive compared with 0.53 hours/day in hypertensive, \textit{p} < 0.001) but not in men.
-Interestingly, in both sexes, hypertensive participants had higher proportion of being classified as low or high carbohydrate eaters; total energy and carbohydrate intake was higher in people with hypertension (\textit{p} < 0.001).
+Interestingly, in both sexes, hypertensive participants had higher proportion of being classified as low or high carbohydrate eaters; total energy and carbohydrate intake was higher in people without hypertension (\textit{p} < 0.001).
 
@@
 95\% CI of the adjusted OR became narrower (OR: 0.64, 95\% CI: 0.41, 1.01, \textit{p} = 0.054) when BMI was replaced with WC in model 2.
-When diabetic men were excluded in the models, the ORs (95\%CI) for moderate and high carbohydrate eaters compared with low carbohydrate eaters were 0.65 (0.41, 1.03) and 0.73 (0.51, 1.06), respectively.
+When diabetic men were excluded in Model 2, the ORs (95\%CI) for moderate and high carbohydrate eaters compared with low carbohydrate eaters were 0.65 (0.41, 1.03) and 0.73 (0.51, 1.06), respectively.
 The negative associations between moderate carbohydrate eating pattern and hypertension were also observed in women, however, without any statistically significant evidence in the fully adjusted models.
@@
 
-	\caption{\label{tab:tab2HYT} ORs (95\%CI) of carbohydrate eating patterns with hypertension in the UK adults, with or without diabetes .\\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
+	\caption{\label{tab:tab2HYT} ORs (95\%CI) for the associations of carbohydrate eating patterns with hypertension in the UK adults, with or without diabetes .\\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
 	\centering
@@
 		\multicolumn{6}{l}{{\scriptsize covariates remained the same with the corresponding Model 1s.}}\\
-		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from logistic regression models.}}\\ 
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from Wald tests in logistic regression models.}}\\ 
 		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level}}\\ 
-		\multicolumn{6}{l}{{\scriptsize (higher or equal to degree level or not), BMI, smoking status (current, ex-smoker, never)}}\\
-		\multicolumn{6}{l}{{\scriptsize , total energy intake (kJ);}}\\
+		\multicolumn{6}{l}{{\scriptsize (higher or equal to degree level or not), BMI, smoking status (current, ex-smoker, never),}}\\
+		\multicolumn{6}{l}{{\scriptsize total energy intake (kJ);}}\\
 		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous),}}\\ 
@@
 Overweight or obese participants were older, having lower total energy intake and lower carbohydrate intake compared with normal weight men and women (\textit{p} < 0.001).
-Moreover, edu-
+Moreover, education
 
@@
 
-cation level (\textit{p} = 0.022 for men, < 0.001 for women), average household income (\textit{p} = 0.011 for men, < 0.001 for women) were decreasing with increasing BMI.
+level (\textit{p} = 0.022 for men, < 0.001 for women), average household income (\textit{p} = 0.011 for men, < 0.001 for women) were decreasing with elevated BMI.
 Living with partner or not was strongly positively associated with obesity in men but not in women.
-Men with obesity were also found to have the lowest proportion of never being a smoker (47.9 \%), and the highest proportion of being ex-smoker (32.9\%).
+Men with obesity were also found to have the lowest proportion of never being a smoker (47.9 \%), and the highest proportion of being an ex-smoker (32.9\%).
 Association between smoking status and obesity in women was only with very weak evidence (\textit{p} = 0.042) but similar pattern as in men was also observed (higher proportion of ex- and current smokers in overweight or obese women).
@@
 		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
-		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
+		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.71) & 0.332\\
 		\addlinespace[0.3em]
@@
 However, the 95\%CI of the regression coefficients were all wide and included the null value 0, indicating no statistically supported evidence for the inverse association.
-However, evidence of interaction effect was found in whether live with a partner or not on the association between carbohydrate eating patterns and BMI (\textit{p} for interaction = 0.014 and 0.036 for women in total and without diabetes).
-For women who were living with her partner, latent classes of carbohydrate eating patterns were negatively associated with BMI.
+In women, evidence of interaction effect was found in whether live with a partner or not on the association between carbohydrate eating patterns and BMI (\textit{p} for interaction = 0.014 and 0.036 for women in total and without diabetes).
+For women who were 5.43living with partners, latent classes of carbohydrate eating patterns were negatively associated with BMI.
 Compared with women eating low carbohydrate food pattern, women having a high carbohydrate eating pattern were averagely associated with 1.76 kg/m\textsuperscript{2} lower BMI after adjustment of age, average household income, education level, smoking status, total energy intake and alcohol consumption.
@@
 However, for women who were living alone, moderate carbohydrate eaters had 3.17 cm (95\%CI: 0.05, 6.30, \textit{p} = 0.047) larger WC on average compared with low carbohydrate eaters.
-The evidence for the positive association between moderate carbohydrate eaters and WC in women became weaker but with borderline significant when excluding diabetic women (3.08 cm, 95\%CI: -0.09, 6.25, \textit{p} = 0.057).
+The evidence for the positive association between moderate carbohydrate eaters and WC in women became weaker but still with borderline significant when excluding diabetic women (3.08 cm, 95\%CI: -0.09, 6.25, \textit{p} = 0.057).
 
@@
 		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. }}\\
-		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from linear regression models.}}\\
+		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from Wald tests in linear regression models.}}\\
 		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age, live with partner or not, average household income, education level, hypertension (yes or no),}}\\

### 2018-08-20 paper/Chapters/Chapter4.tex
abstract almost done, proof reading first round done

@@
 These findings explained why they were actually consuming the highest energy among the three types of carbohydrate eaters.
-However, we also found that participants consuming low carbohydrate food had higher prevalence of diabetes, hypertension, and obesity.
+In the meantime, we also found that participants consuming low carbohydrate food had higher prevalence of diabetes, hypertension, and obesity.
 These health issues might possibly lead them (or advices were given from their physicians) to replace carbohydrates in their diet to other energy sources such as fat, protein, or even alcohol.
@@
 Among men, who were classified as moderate carbohydrate eaters probably had lower odds of having hypertension, after adjustment of age, live with partner or not, educational level, BMI, smoking status and total energy intake.
-As discussed above, moderate carbohydrate eaters turned to have meals (or energy consumption) later in time compared with high carbohydrate eaters, but low carbohydrate eaters also consumed large amount of energy (from both fat and alcohol) at night.
+As discussed above, moderate carbohydrate eaters turned to have meals (or energy consumption) later in time compared with high carbohydrate eaters.
+But, it is noteworthy that low carbohydrate eaters also consumed large amount of energy (from both fat and alcohol) at night.
 Therefore, considering that moderate carbohydrate eaters were younger than low carbohydrate eaters (although age was adjusted in the full models), there is probably reverse causality exists here (also due to the nature of cross-sectional study).
-That is, they were potentially both late eaters, however, with increased age (and so as increased health-related problems/concern) some of them modified their habits, such as quit smoking, replace carbohydrate food with other energy sources which lead to the phenomenon of lower odds of hypertension in moderate carbohydrate eaters.
+That is, they were potentially both late eaters, however, with increased age (and so as increased health-related problems/concern) some of them modified their habits, such as quitting smoking, replacing carbohydrate food with other energy sources (so that they became low carbohydrate eaters with hypertension) which lead to the phenomenon of lower odds of hypertension in moderate carbohydrate eaters.
 Although these hypotheses cannot be determined by the cross-sectional data from NDNS RP, if they were true, the energy sources they used to replace carbohydrate in their diet were apparently not very wisely chosen.
@@
 This interaction effect was more obvious when looking at abdominal obesity measurement.
-High carbohydrate eaters had lower BMI and WC in those lived with their partner, while moderate carbohydrate eaters had higher WC in those who lived alone after adjustment of age, education level, smoking status, total energy intake, and alcohol consumption.
+High carbohydrate eaters had lower BMI and WC in those lived with their partners, while moderate carbohydrate eaters had higher WC in those who lived alone after adjustment of age, education level, smoking status, total energy intake, and alcohol consumption.
 High carbohydrate eaters who were characterised with high and early in the day energy consumption and low fat and alcohol intake may reflect a healthier diet and lifestyle, but this might be different between women who lived alone and those who lived with their partners.
-It was often assumed that live alone may associated with lower diversity of food intake, and a higher likelihood of having an unhealthy dietary pattern \parencite{hanna2015relationship}.
-Therefore, there may be differences in the actual contents consumed in high carbohydrates eating women, or there may be other social, psychological or lifestyle related factors related with living alone which were not measured or did not included in the models, so that the inverse association between high carbohydrate eating pattern and BMI or abdominal obesity were only observed among women who lived with partners, further analysis is needed.
-Whereas the reason why moderate carbohydrate eaters' WC was larger than low carbohydrate eaters only among women who lived alone is unknown, given that the evidence of this association was weak and borderline significant, whether it was just a false positive finding should be explored in other studies.
+It was often assumed that live alone may associated with lower diversity of food intake, and a higher likelihood of having an unhealthy dietary choice \parencite{hanna2015relationship}.
+Therefore, there may be differences in the actual contents consumed in their high carbohydrates, or there may be other social, psychological or lifestyle related factors related with living alone which were not measured or did not included in the models.
+Thus, the inverse association between high carbohydrate eating pattern and BMI or abdominal obesity were only observed among women who lived with partners, further investigation on this hypothesis is needed.
+Whereas the reason why moderate carbohydrate eaters' WC was larger than low carbohydrate eaters only among women who lived alone is unknown, given that the evidence of this association was weak and borderline significant, whether it was just a false positive finding should also be explored in other studies.
 
@@
 But the above mentioned alternative models require that the 3 or 4 repeated measurements of food diaries to be recorded at the same time points longitudinally.
-Specifically, LCGA models (also called growth mixture modelling) will also need to model the change of the odds of the probability over time as a function (quadratic, or cubic) which is apparently not the objective in the current project.
+Specifically, LCGA models (also called growth mixture model) will also need to model the change of the odds of the probability over time as a function (quadratic, or cubic) which is apparently not the objective in the current project.
 
@@
 However, the maximum probability rule is still believed to be able to minimize the number of incorrect assignments \parencite{goodman20071}.
-A Monte Carlo simulation study \parencite{bray2015eliminating} also demonstrated that maximum probability assignment is less biased than multiple pseudo-class draws.
+A Monte Carlo simulation study \parencite{bray2015eliminating} demonstrated that maximum probability assignment is less biased than multiple pseudo-class draws.
 Moreover, this simulation study also found that an inclusive LCA (i.e.
-LCA with covariates) would perform better than non-inclusive LCA, and has the potential to reduce bias of class assignment.
+LCA with covariates) would probably perform better than non-inclusive LCA, and has the potential to reduce bias of class assignment.
 However, whether this advantage can be extended to MLCA in the current project is unknown, and also due to the reason that the associations between the latent classes and distal outcomes (hypertension, and BMI) in our analyses are mostly still under exploration, therefore, the model for LCA with covariates can never be well-known before our analyses.
-Thus, as a first step, given the complexity of the NDNS RP dataset itself, we chose to conduct the MLCA modellings without any covariate in either day level or individual level models.
+Thus, as a first step, given the complexity of the NDNS RP dataset itself, we chose to fit the MLCA models without any covariate in either day level or individual level models.
 Future studies may be advised to consider incorporating other predictors in the MLCA models to see whether the classifications in both levels can be improved or not.
@@
 Thirdly, information regarding the detailed occupations of the participants was not available and because of which we could not exclude those who had a shift work involving night work.
-But considering that completing a 4-consecutive-day food diary would be a large burden for the participants, those had a shift work involving night work might possibly performed relatively lower compliance and could not complete their diary for at least 3 days.
+But considering that completing a 4-consecutive-day food diary would be a large burden for the participants, those had a shift work involving night work might possibly performed with relatively lower compliance and could not complete their diary for at least 3 days.
 But this hypothesis cannot be verified in the NDNS RP dataset.
@@
 Further researches are warranted to explore and better understand the eating patterns in other populations.
-Besides, the cross-sectional study design also refrained us from deducing any causal effect between the carbohydrate eating patterns and hypertension or BMI.
+Besides, the cross-sectional study design also refrained us from deducing any causal effect between the carbohydrate eating patterns and hypertension, BMI or abdominal obesity.
 
 Strengths of this study include the large, nationally representative sample of men and women in the UK.
-We applied a novel, objective approach using MLCA to examine the carbohydrate eating patterns while using standardised criteria to determine the numbers of latent classes.
+We applied a novel, objective approach using MLCA to examine the carbohydrate eating patterns while applying standardised criteria to determine the numbers of latent classes.
 The process of finding the classifications through model-based, data-driven procedure minimises reliance on researchers' preconcieved notions of eating patterns.
@@
 Moreover, the examination of associations between the individual level carbohydrate eating patterns and hypertension, BMI, abdominal obesity were conducted correctly considering the probability of participant selection and the clustered survey design.
-Health outcomes such as weight, height, waist circumferences, and blood pressure, diabetes status were measured by trained nurses and blood tests which could also minimise the misclassification and under-reporting of these measurements.
+Health outcomes such as weight, height, waist circumferences, and blood pressure, diabetes status were measured by trained nurses and blood tests which could also minimise bias caused by misclassification and under-reporting of these measurements.
 
@@
 Among women who lived with partners, high carbohydrate eating pattern was associated with both lower BMI and smaller waist circumferences.
-Longitudinal designed studies are needed in finding whether the eating patterns themselves are changing over time and in investigating how such circadian eating patterns may relate to the change of blood pressure, obesity, and even mortality.
+Longitudinal designed studies are needed in finding whether the eating patterns themselves are changing over time and in investigating how such circadian eating patterns may relate to the change of blood pressure, obesity, and other health outcomes (incidence of cancer, cardiovascular diseases, or perhaps mortality).

### 2018-08-20 paper/main.tex
abstract almost done, proof reading first round done

@@
 \university{\href{https://www.lshtm.ac.uk/}{London School of Hygiene and Tropical Medicine}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
-\department{\href{}{Page count: 42 from Introduction to Conclusions}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
+\department{\href{}{Page count: 43 from Introduction to Conclusions}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
 \group{Candidate number: 110765} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
@@
 \addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
-\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:
+\noindent I, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:
 
@@
 
-\noindent Signed: \;\;\;\;\;\;\includegraphics[height=2.5\baselineskip]{Figures/signature.png}\\
-\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
-
-\noindent Date: \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;2018-09-05\\
-\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
+%\noindent Signed: \;\;\;\;\;\;\includegraphics[height=2.5\baselineskip]{Figures/signature.png}\\
+%\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
+%
+%\noindent Date: \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;2018-09-05\\
+%\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
 \end{declaration}
@@
 I would like to thank my tutor and supervisor \supname, for his guidance, patience, and help while working on this project and also to Dr.
-Suzana Almoosawi for her invaluable nutritional academic insight, and suggestions.
+Suzana Almoosawi for her invaluable nutritional academic insight.
 \\
@@
 \addchaptertocentry{\abstractname} % Add the abstract to the table of contents
-The National Diet and Nutrition Survey (NDNS) database of detailed four-day food diaries was used in exploration of both temporal and quantity eating patterns of carbohydrates in the general adults living in the UK.
+\textbf{Background:}
+Recent evidence suggested that there are 3 types of eaters (grazers, early eaters, and late eaters) in the general population according to the timing of their energy consumption occurred throughout the day.
+This project aimed at investigating the relationship between the timing of eating and carbohydrate intake.
+Additionally, associations between carbohydrate eating patterns defined previously and hypertension, obesity were explored.
+
+\textbf{Methods:}
+The National Diet and Nutrition Survey (NDNS) Rolling Programme (2008/09-15/16) database of detailed four-day food diaries was used in exploration of both timing and quantity eating patterns of carbohydrates in the general adults living in the UK.
 6155 participants aged 19 or older were kept in the analysis.
-\\
-Multilevel latent class analysis (MLCA) models were applied in finding the latent classes of carbohydrate consumption both at the observation day level, and individual level.
+Multilevel latent class analysis (MLCA) models were applied in finding the latent classes of carbohydrate consumption accounting for the hierarchical data structure that the observed daily food diaries nested within individuals.
+Survey-designed multivariable regression models assessed the associations of carbohydrate eating patterns with hypertension, body mass index (BMI), and waist circumferences.
+
+\textbf{Results:}
+Three types of carbohydrate eating days (low/high percentage carbohydrate days, and regular meal days) were found in the elementary level, depending on which, three types of carbohydrate eaters (low/moderate/high carbohydrate eaters) emerged in the NDNS RP participants.
+
+\textbf{Conclusion:}
+
 \end{abstract}

### 2018-08-20 paper/main.tex
abstract done

@@
 
+% change the margins for one page
+\newenvironment{changemargin}[2]{%
+	\begin{list}{}{%
+			\setlength{\topsep}{0pt}%
+			\setlength{\leftmargin}{#1}%
+			\setlength{\rightmargin}{#2}%
+			\setlength{\listparindent}{\parindent}%
+			\setlength{\itemindent}{\parindent}%
+			\setlength{\parsep}{\parskip}%
+		}%
+	\item[]}{\end{list}}
+
 \begin{document}
@@
 
+\begin{changemargin}{-0.6cm}{-0.3cm}
 \begin{abstract}
 \addchaptertocentry{\abstractname} % Add the abstract to the table of contents
+
 \textbf{Background:}
-Recent evidence suggested that there are 3 types of eaters (grazers, early eaters, and late eaters) in the general population according to the timing of their energy consumption occurred throughout the day.
-This project aimed at investigating the relationship between the timing of eating and carbohydrate intake.
-Additionally, associations between carbohydrate eating patterns defined previously and hypertension, obesity were explored.
+Recent evidence suggested that there are 3 types of eaters (grazers, early eaters, and late eaters) according to the timing of energy consumption.
+This project aimed at finding both timing and quantity eating patterns specifically for carbohydrate (carb) intake, and exploring their potential associations with hypertension and obesity.
 
 \textbf{Methods:}
-The National Diet and Nutrition Survey (NDNS) Rolling Programme (2008/09-15/16) database of detailed four-day food diaries was used in exploration of both timing and quantity eating patterns of carbohydrates in the general adults living in the UK.
-6155 participants aged 19 or older were kept in the analysis.
-Multilevel latent class analysis (MLCA) models were applied in finding the latent classes of carbohydrate consumption accounting for the hierarchical data structure that the observed daily food diaries nested within individuals.
-Survey-designed multivariable regression models assessed the associations of carbohydrate eating patterns with hypertension, body mass index (BMI), and waist circumferences.
+Data are from the National Diet and Nutrition Survey (NDNS) Rolling Programme (2008/09-15/16) which included 6155 adults aged 19 or older in the UK.
+Time of the day was defined as: 6-9 am, 9-12 noon, 12-2 pm, 2-5 pm, 5-8 pm, 8-10 pm and 10 pm-6 am.
+Responses for carb intake within each time slot were categorised into: not eating any food, carb contributed $<$ 50\% or $\geqslant$ 50\% of total energy.
+Multilevel latent class analysis (MLCA) models were applied in finding the latent classes of carb consumption accounting for the hierarchical data structure.
+Survey-designed multivariable regression models were used to assess the associations between carb eating patterns and hypertension, body mass index (BMI), and waist circumferences (WC).
 
 \textbf{Results:}
-Three types of carbohydrate eating days (low/high percentage carbohydrate days, and regular meal days) were found in the elementary level, depending on which, three types of carbohydrate eaters (low/moderate/high carbohydrate eaters) emerged in the NDNS RP participants.
+Three carb eating day patterns (low/high percentage, and regular meal days) were found in 24483 observation days, based on which, three types of carb eaters: low (28.1\%), moderate (28.8\%), and high (43.1\%) carb eaters emerged.
+On average, low-carb eaters consumed the highest amount of total energy intake (7985.8 kJ), and they had higher percentages of energy contributed by fat and alcohol, especially after 8 pm.
+Moderate-carb eaters consumed the lowest amount of total energy (7341.8 kJ) while they had the tendency of eating carb later in time-of-day.
+High-carb eaters consumed most of their carb and energy within time slots of 6-9 am, 12-2 pm and 5-8 pm.
+In men, moderate-carb eaters may had lower odds of having hypertension compared with low-carb eaters (adjusted OR: 0.64, 95\%CI: 0.41, 1.01).
+In women, high-carb eaters lived with partners had both lower BMI (-1.76 kg/m\textsuperscript{2}, -2.87, -0.73) and WC (-4.71 cm, -7.00, -2.43) compared with low-carb eaters, although these inverse associations were not observed in women who lived alone (\textit{p} for interaction 0.014, and 0.009).
 
-\textbf{Conclusion:}
+\textbf{Conclusions:}
+Contrary to the expectation, profiles of high-carb eaters seemed to be healthier among three types of carb eaters.
+Low-carb eaters probably followed the diet out of health purposes but they may have chosen fat or alcohol as replacements of carb, which could probably be a concern from public health point of view.
+Whether these circadian carb-eating patterns are associated with change of blood pressure and/or obesity longitudinally should be further investigated.
 
 \end{abstract}
+\end{changemargin}
 

### 2018-08-26 paper/Chapters/Chapter2.tex
grammarly checked

@@
 Detailed dairy checking was performed to code and convert the food consumption into energy and nutrients intake.
-Intakes of nutrients were calculated from the food consumption records using a specially adapted Nutrient Databank \parencite{smithers1993maff}, which was originally developed by the Ministry of Agriculture, Fisheries and Food (MAFF) for the Dietary and Nutritional Survey of British Adults.
+Intakes of nutrients were calculated from the food consumption records using a specially adapted Nutrient Databank \parencite{smithers1993maff}, which was originally developed by the Ministry of Agriculture, Fisheries, and Food (MAFF) for the Dietary and Nutritional Survey of British Adults.
 Further details of data
@@
 To produce a sequence of discrete responses regarding the carbohydrate intake we are interested, the energy consumption within each time slot over the four days of survey for each participant were calculated.
-The percentages of energy that contributed by carbohydrate within each time slot were then estimated.
+The percentages of total energy intake that contributed by carbohydrate within each time slot were then estimated.
 Since we planned to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical, the responses were then dichotomised according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e.
-if within a time slot where there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was lower or higher/equal to 50\% of total energy intake within that time slot.
+if within a time slot where there is any energy intake occurred, carbohydrate consumption was categorised into whether it's energy contribution was lower or higher/equal to 50\% of total energy intake within that time slot.
 Consequently, for each day of the recording, there were 7 data points generated by the diary, each data point included one of the following responses:
@@
 	\item Randomly select one household at that address; 
-	\item Selected addresses were randomly allocated to one of two groups to determine whether an adult (aged 19 years or older) and a child (aged 1.5 to 18 years), or a child only, were selected for interview.
+	\item Selected addresses were randomly allocated to one of two groups to determine whether an adult (aged 19 years or older) and a child (aged 1.5 to 18 years) or a child only, were selected for interviews.
 \end{itemize}
@@
 
-It is necessary to apply weighting factors to the data collected in the NDNS RP for two reasons: to remove any bias in the observed results which may be due to differences in the probability of households and individuals being selected to take part; and to attempt to reduce differential non-response bias by age, sex and geographical region.
+It is necessary to apply weighting factors to the data collected in the NDNS RP for two reasons: to remove any bias in the observed results which may be due to differences in the probability of households and individuals being selected to take part; and to attempt to reduce differential non-response bias by age, sex, and geographical region.
 
@@
 	\item An overall selection weight, which is the product of the address, dwelling unit, catering (household) unit, and individual selection weights, was generated to correct for the unequal selection probabilities.
-These weights are the inverse of the selection probabilities at each level of the random sampling process and they can be used to compensate for differences in the chance of selection of an individual.
-	\item An iterative procedure was used to adjust the selection weights until the distribution of the weighted sample matched that of the population for age-group, sex and geographical region.
+These weights are the inverses of the selection probabilities at each level of the random sampling process and they can be used to compensate for differences in the chance of selection of an individual.
+	\item An iterative procedure was used to adjust the selection weights until the distribution of the weighted sample matched that of the population for age-group, sex, and geographical region.
 Population distributions were taken from the mid-year population estimates \parencite{OfficeofNationalStat}.
@@
 
-Another two sets of weights were generated to correct for differential non-response (either due to refusal or inability) to 1) nurse visit, and 2) giving a blood sample.
-Response rates to the nurse visit among those completed a dietary diary was approximately 75\%, to blood sample in adults were 51\%, 57\%, and 50\% for years 1 to 4, 5 to 6, and 7 to 8, respectively.
-In creating the nurse/blood sample weight, a logistic regression model was used by the NDNS RP study team to model the relationship between response to nurse visit/giving blood sample and a set of predictor variables (socio-demographic, participant and catering/household unit characteristics).
-The model generated a predicted probability for each participant, which is the probability would agree to a nurse visit/provide blood sample, given the characteristics of the individual and the household unit.
+Another two sets of weights were generated to correct for differential non-response (either due to refusal or inability) to 1) nurse visit and 2) giving a blood sample.
+Response rates to the nurse visit among those completed a dietary diary was approximately 75\%, to the blood sample in adults were 51\%, 57\%, and 50\% for years 1 to 4, 5 to 6, and 7 to 8, respectively.
+In creating the nurse/blood sample weight, a logistic regression model was used by the NDNS RP study team to model the relationship between response to nurse visit/giving a blood sample and a set of predictor variables (socio-demographic, participant and catering/household unit characteristics).
+The model generated a predicted probability for each participant, which is the probability would agree to a nurse visit/provide a blood sample, given the characteristics of the individual and the household unit.
 Participants with characteristics associated with non-response were under-represented in the sample and therefore receive a low predicted probability.
-The inverse of these predicted probabilities were used as a set of non-response weights so that participants with a low predicted probability got a larger weight, increasing their representation in the sample.
+The inverses of these predicted probabilities were used as a set of non-response weights so that participants with a low predicted probability got a larger weight, increasing their representation in the sample.
 Then the nurse/blood sample weights were re-scaled so that the sum of the weights equalled the number of participants who had a nurse visit/who provided a blood sample.
-The final nurse/blood weights should therefore make the sample participants representative of all eligible persons in the population.
+The final nurse/blood weights should, therefore, make the sample participants representative of all eligible persons in the population.
 
-Further details of the weighting system developed by the NDNS RP are described in the Appendix B of the reports published by Public Health England (PHE) \parencite{bates2014national,roberts2018national,NDNSofficial}.\vspace{-0.6cm}
+Further details of the weighting system developed by the NDNS RP are described in Appendix B of the reports published by Public Health England (PHE) \parencite{bates2014national,roberts2018national,NDNSofficial}.\vspace{-0.6cm}
 
@@
 
-Computer assisted personal interviews were conducted for the selected individuals by trained interviewers to collect background information on smoking habits (current, ex-smokers, and never), ethnicity (white, non-white), education level (lower than degree/degree or above level), living with a partner or not and other socio-demographic variables.
+Computer-assisted personal interviews were conducted for the selected individuals by trained interviewers to collect background information on smoking habits (current, ex-smokers, and never), ethnicity (white, non-white), education level (lower than degree/degree or above level), living with a partner or not and other socio-demographic variables.
 Participants also had their height, weight, blood pressure, waist circumferences (WC) measured by the nurses.
@@
 Specifically, blood pressure was measured in a sitting position using an automated, validated machine, the Omron HEM907, after a five-minute rest.
-The means of second and third readings, taken at one minute intervals, were used in the current report.
+The means of second and third readings, taken at one-minute intervals, were used in the current report.
 Hypertension was defined as with systolic blood pressure of 140 mmHg or above, and/or diastolic blood pressure of 90 mmHg or above, and/or taking any medication specifically to reduce blood pressure.
@@
 Serum samples were obtained by centrifugation of the coagulated blood sample.
-Serum total, High Density Lipoprotein (HDL) and Low Density Lipoprotein (LDL) cholesterol, triglycerides (TG), fasting blood glucose, haemoglobin A1C were measured.
+Serum total, High-Density Lipoprotein (HDL) and Low-Density Lipoprotein (LDL) cholesterol, triglycerides (TG), fasting blood glucose, haemoglobin A1C were measured.
 A1C value of 6.5\% was used as the cut off point for diagnosing diabetes.
@@
 
-Ethical approval for the survey was obtained form the Oxfordshire A Research Ethics Committee.
+Ethical approval for the survey was obtained from the Oxfordshire A Research Ethics Committee.
 The letters of approval for the original submission and subsequent substantial amendments, together with approved documents, were sent to all Local Research Ethics Committees covering areas where fieldwork was being conducted.
 Research governance approval was sought for all participating NHS laboratories and obtained where required by the Research and Development Committee for each laboratory.
-Ethical approval for the current project was obtained from the MSc Research Ethics Committee of London School of Hygiene \& Tropical Medicine (LSHTM MSc Ethics Ref: 15624).
+Ethical approval for the current project was obtained from the MSc Research Ethics Committee of the London School of Hygiene \& Tropical Medicine (LSHTM MSc Ethics Ref: 15624).
 
@@
 Latent class analysis is a statistical technique that identifies categorical latent (unobserved) class variables on the basis of observed categorical variables \parencite{collins2010latent}.
-It belongs to the family of latent variable models, and is directly analogous to the factor analysis model.
+It belongs to the family of latent variable models and is directly analogous to the factor analysis model.
 The major difference is that the latent variable in LCA is categorical, not continuous as in factor analysis.
@@
 \begin{equation}
-P(U_{i1} = s_1, U_{i2} = s_2, \cdots, U_{ik} = s_k) = \sum_{t=t}^{T}P(C_i = t)\prod_{k = 1}^{K}P(U_{ik} = s_k | C_i = t)
+P(U_{i1} = s_1, U_{i2} = s_2, \cdots, U_{ik} = s_k) = \sum_{t=t}^{T}P(C_i = t)\prod_{k = 1}^{K}P(\mathbf{U_{ik}} = \mathbf{s_k} | C_i = t)
 \label{LCA}
@@
 Essentially this allows the probability that an observation day will belong to a
-particular day level latent class to vary across individual levels.\vspace{-0.5cm}
+particular day-level latent class to vary across individual-levels.\vspace{-0.5cm}
 
@@
 an observed high carbohydrate eating day vs.
-a low carbohydrate eating day) is constant within individual level, which means for each person throughout his/her survey there is some probability of following a high carbohydrate eating day.
+a low carbohydrate eating day) is constant within the individual-level, which means for each person throughout his/her survey there is some probability of following a high carbohydrate eating day.
 A random effect considers the individuals (level 2) to be drawn from the adult population in the UK, and the probability of the outcome (i.e.
@@
 \begin{aligned}
-\text{logit}[P(C_{ij} = 1)] & = \beta_{0j} + \beta_{1}x_{ij} \;\;\;\;\;\;\;\;\; \textbf{(day level)}  \\
-\beta_{0j} & = \gamma_0 + \gamma_1 w_j + u_{0j} \; \textbf{(individual level)} \\ 
+\text{logit}[P(C_{ij} = 1)] & = \beta_{0j} + \beta_{1}x_{ij} \;\;\;\;\;\;\;\;\; \textbf{(day-level)}  \\
+\beta_{0j} & = \gamma_0 + \gamma_1 w_j + u_{0j} \; \textbf{(individual-level)} \\ 
 \Rightarrow P(C_{ij} = 1) & = \frac{\exp{(\gamma_0 + \beta_{1}x_{ij} + \gamma_1 w_j + u_{0j})}}{1 + \exp{(\gamma_0 + \beta_{1}x_{ij} + \gamma_1 w_j + u_{0j})}} \\
@@
 	\item $\text{logit}{(x)} = \log{\frac{x}{1-x}}$, where $x \in [0,1]$;
-	\item $P(C_{ij} = 1)$ as the probability that the randomly selected $i$th observation day of $j$th individual is a high carbohydrate eating day;
-	\item $\beta_{0j}$ as the random intercept, for outcome $C_{ij} = 1$; 
+	\item $P(C_{ij} = 1)$ as the probability that the randomly selected $i$th observation day of the $j$th individual is a high carbohydrate eating day;
+	\item $\beta_{0j}$ as the random intercept, for the outcome $C_{ij} = 1$; 
 	\item the random deviation of the individuals $u_{0j}$ are assumed be normally distributed (i.e.
 $u_{0j} \sim N(0, \sigma_{u_0}^2)$), the magnitude of the $u_{0j}$ variance ($\sigma_{u_0}^2$) indicates the influence of the individuals (level 2);
-	\item $x_{ij}, w_j$ is the predictors for day level (weekdays or weekends) and individual level, such as age, and sex.
+	\item $x_{ij}, w_j$ is the predictors for day-level (weekdays or weekends) and individual-level, such as age, and sex.
 \end{itemize}
 
-Same framework can be used to consider random effects in an LCA model, but instead of saying that $C_{ij}$ is either low or high carbohydrate eating days as if we already know, it is now replaced by a latent variable $G_{ij}$ which indicates the typologies of carbohydrate eating patterns.
-Then we can use the day level data to assess the log-odds of belonging to $k$th type of carbohydrate eating pattern on a specific day of survey, and we allow the log-odds to vary across individuals.
-Therefore, for some persons the log-odds of having a $k$th type of carbohydrate eating pattern during the survey can be high, but for the other persons, the log-odds of following the $k$th type of carbohydrate eating pattern can be low.
+The same framework can be used to consider random effects in an LCA model, but instead of saying that $C_{ij}$ is either low or high carbohydrate eating days as if we already know, it is now replaced by a latent variable $G_{ij}$ which indicates the typologies of carbohydrate eating patterns.
+Then we can use the day-level data to assess the log-odds of belonging to the $k$th type of carbohydrate eating pattern on a specific day of the survey, and we allow the log-odds to vary across individuals.
+Therefore, for some persons, the log-odds of having a $k$th type of carbohydrate eating pattern during the survey can be high, but for the other persons, the log-odds of following the $k$th type of carbohydrate eating pattern can be low.
 
-If the day level LCA model (carbohydrate eating temporal pattern typologies) is best defined by $T (T \geqslant 2)$ latent classes, then $T-1$ random intercept will be specified by a two-level multinomial logistic regression model.
+If the day-level LCA model (carbohydrate eating temporal pattern typologies) is best defined by $T (T \geqslant 2)$ latent classes, then $T-1$ random intercept will be specified by a two-level multinomial logistic regression model.
 Similar to the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each time slots, throughout three/four consecutive days of their survey period).
@@
 \begin{itemize}
-	\item $ U_{ijk} $ represents the response of carbohydrate eating (one of the following: not eating any food, $< 50\%$ of the energy, or $\geqslant 50\%$ of the energy) on $i$th day of the survey ($i \in (1,2,3,4)$) in $j$th individual at the $k$th time slot of the day ($k \in (1, 2, 3, \cdots, 7)$);
-	\item $G_{ij}$ denotes the latent class membership for $j$th individuals on $i$th day of the survey, the total number of day level latent class is $T$;
+	\item $ U_{ijk} $ represents the response of carbohydrate eating (one of the following: not eating any food, $< 50\%$ of the energy, or $\geqslant 50\%$ of the energy) on the $i$th day of the survey ($i \in (1,2,3,4)$) in $j$th individual at the $k$th time slot of the day ($k \in (1, 2, 3, \cdots, 7)$);
+	\item $G_{ij}$ denotes the latent class membership for $j$th individuals on $i$th day of the survey, the total number of day-level latent class is $T$;
 %	\item A specific latent class is referred to as $t$, and the total number of level 1 latent classes is denoted by $T$;
@@
 This approach is less computationally demanding compared with the parametric approach.
-These level 2 (individual) latent classes reflect differences in the probability of belonging to a specific day level latent class, so that individuals that have observation days with similar probabilities for the level 1 latent classes will be grouped together.
+These level 2 (individual) latent classes reflect differences in the probability of belonging to a specific day-level latent class, so that individuals that have observation days with similar probabilities for the level 1 latent classes will be grouped together.
 The non-parametric MLCA model can be defined as follows:
@@
 \begin{itemize}
-	\item $CB_j$ is individual level latent class membership for $j$th individual;
-	\item $\gamma_{tm}$ is day level and individual level indicators. 
+	\item $CB_j$ is the individual-level latent class membership for the $j$th individual;
+	\item $\gamma_{tm}$ is day-level and individual-level indicators. 
 \end{itemize}
@@
 	\item Firstly, we ignored the multilevel structure of the data and estimated a series of traditional LC models to determine the number of classes at the observational day-level;
-	\item Next, a series of MLCA models were fitted to account for the multilevel structrure of the data.
-In these models, the number of day-level classes was based on the best fitting LCA model from the first step, and the LCA model at the individual level was estimated to identify the number of individual level latent classes;
-	\item Thirdly, when number of individual level latent classes is defined based on the previous stage, number of day-level classes was modified (one class lower and one class higher than in the second step) to see the effect of changing level 1 classes and confirm the best fitting model.
+	\item Next, a series of MLCA models were fitted to account for the multilevel structure of the data.
+In these models, the number of day-level classes was based on the best fitting LCA model from the first step, and the LCA model at the individual-level was estimated to identify the number of individual-level latent classes;
+	\item Thirdly, when the number of individual-level latent classes is defined based on the previous stage, the number of day-level classes was modified (one class lower and one class higher than in the second step) to see the effect of changing level 1 classes and confirm the best fitting model.
 \end{itemize}
@@
 $q-1$ classes models, where $q$ is the number of latent classes and most importantly, 3) pattern interpretability.
-In the steps of performing multilevel LCA, where LMR-LRT is not available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day level and individual level.
+In the steps of performing multilevel LCA, where LMR-LRT is not available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day-level and individual-level.
 MLCA models were fitted in Mplus 7.4 \parencite{muthen2005mplus}, the Mplus syntax and outputs are shown in \textbf{Appendix \ref{AppendixB}}.
@@
 
-\subsection{Characteristics of day level latent classes and individual level latent classes}\vspace{-0.3cm}
+\subsection{Characteristics of day-level latent classes and individual-level latent classes}\vspace{-0.3cm}
 
-Day level latent classes identified by the first step of MLCA were tabulated according to day of week and also whether the diary was recorded during weekends or not.
-A contingency table giving the frequency of responses across the 7 time slots of the survey days was produced.
-Descriptive statistics for the dietary day level recordings according to the latent class memberships were presented.
+day-level latent classes identified by the first step of MLCA were tabulated according to the day of week and also whether the diary was recorded during weekends or not.
+A contingency table giving the frequency of responses across the 7-time slots of the survey days was produced.
+Descriptive statistics for the dietary day-level recordings according to the latent class memberships were presented.
 Pearson $\chi^2$ test was used to compare the distribution of categorical variables.
@@
 
-Person level point estimates and 95\% confidence intervals (CIs) were determined by applying individual, nurse visiting, and blood sample weights accordingly which account for the probability of participant selection and the clustered survey design.
+Person-level point estimates and 95\% confidence intervals (CIs) were determined by applying individual, nurse visiting, and blood sample weights accordingly which account for the probability of participant selection and the clustered survey design.
 Descriptive statistics for sample characteristics were presented as weighted means (95\% CI) or weighted percentages (95\%CI).
@@
 
-To see whether there is any temporal pattern for food intake eating could also be defined at individual level, weighted estimates of nutrients consumption across the 7 time slots of the day were calculated for each individual level latent class.
+To see whether there is any temporal pattern for food intake eating could also be defined at the individual-level, weighted estimates of nutrients consumption across the 7-time slots of the day were calculated for each individual-level latent class.
 Contributions (\%) of the average energy intake within time slots were evaluated by determining the percentages of energy coming from carbohydrate, fat, protein, and alcohol intake.
@@
 
-\subsection{Association between individual level latent classes and the prevalence of hypertension, and measurements of obesity}\vspace{-0.3cm}
+\subsection{Association between individual-level latent classes and the prevalence of hypertension, and measurements of obesity}\vspace{-0.3cm}
 
-Associations between individual level carbohydrate eating classes and hypertension (yes/no), body mass index (BMI, kg/m\textsuperscript{2}), and waist circumference (WC, cm) were explored in men and women separately.
+Associations between individual-level carbohydrate eating classes and hypertension (yes/no), body mass index (BMI, kg/m\textsuperscript{2}), and waist circumference (WC, cm) were explored in men and women separately.
 Point estimates of weighted means and proportions and 95\%CI of the characteristics were determined by applying either nurse visiting weights (for outcomes of hypertension, BMI, and WC) or blood sample weights (for diagnosis of DM) accordingly.
@@
 Survey-designed logistic regression models (for hypertension), and linear regression models (for WC, BMI), were used to test for associations between latent classes of carbohydrate eating patterns and hypertension, BMI, and WC, in the NDNS RP sample, separately.
-Since diabetic participants might or might not modify their carbohydrate eating habits, we also fitted all the above mentioned regression models restricted to those without diabetes.
+Since diabetic participants might or might not modify their carbohydrate eating habits, we also fitted all the above-mentioned regression models restricted to those without diabetes.
 
@@
 	\item The crude association between the carbohydrate eating groups and the outcomes was first examined. 
-	\item Potential confounders of the association between carbohydrate eating groups (exposure) and the outcomes were selected depending on the descriptive statisitical analyses conducted above, i.e.
+	\item Potential confounders of the association between carbohydrate eating groups (exposure) and the outcomes were selected depending on the descriptive statistical analyses conducted above, i.e.
 those are associated with both the exposure and the outcome and also not on the causal pathway were selected as potential confounders.
-Those are strongly related with the outcomes but may not associated with carbohydrate eating groups may reduce the standard errors and so improve the precisions are also considered in the linear regression models.
+Those are strongly related with the outcomes but may not associate with carbohydrate eating groups may reduce the standard errors and so improve the precisions are also considered in the linear regression models.
 	\item Confounding and/or interaction effect from each of the potential factors were checked one by one.
-Interaction effect were tested using the adjusted Wald test testing whether the regression coefficients of the interaction terms are simultaneously equal to zero.
+Interaction effects were tested using the adjusted Wald test testing whether the regression coefficients of the interaction terms are simultaneously equal to zero.
 	\item A preliminary model that includes all of the variables suggested to be confounders in the previous step was established. 
-	\item The remaining variables were added to the preliminary model one by one to see if any of them may be a confounder in condition of the presence of the other covariates. 
+	\item The remaining variables were added to the preliminary model one by one to see if any of them may be a confounder in the condition of the presence of the other covariates. 
 	\item For logistic regression models (hypertension) under the survey data, goodness-of-fit was assessed using the adapted \code{svylogitgof} command in Stata \parencite{archer2006goodness}.
 Other diagnostics for regular logistic regression models, such as estimating the pseudo-R\textsuperscript{2},  AIC or BIC, checking the standardized Pearson residuals, or covariate pattern residuals are currently not available for weighted survey data.
-	\item For linear regression models (WC, BMI), assumption of independent observations is violated as soon as we weighted the sample.
-General checking such as QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance) are not available as well.
+	\item For linear regression models (WC, BMI), the assumption of independent observations is violated as soon as we weighted the sample.
+General checking such as QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance) are not available either.
 Outliers, leverage, and Cook's distance cannot be checked either, however, participants with extreme weightings (if exist) were checked by removing them and refit the models as a sensitivity analysis.
-	\item Since under survey design data, the sampling-weighted least squares are not maximum likelihood, it would not be possible to compare models using likelihood ratio test.
+	\item Since under survey designed data, the sampling-weighted least squares are not maximum likelihood, it would not be possible to compare models using likelihood ratio test.
 Instead, adjusted Wald tests with $p < 0.05$ were used as criteria for variable inclusion in the final model.
-Another Stata command \code{linktest} was also used to  decide whether quadratic and cubic terms of continuous variables were necessary in improving the fitting of model \parencite{pregibon1980goodness}.
+Another Stata command \code{linktest} was also used to  decide whether quadratic and cubic terms of continuous variables were necessary in improving fitting of the model \parencite{pregibon1980goodness}.
 \end{enumerate}

### 2018-08-26 paper/Chapters/Chapter3.tex
abstract done
grammarly checked

@@
 
-A series of traditional LCA of the responses to carbohydrate intake within 7 time slots of day was first examined.
+A series of traditional LCA of the responses to carbohydrate intake within 7-time slots of the day was first examined.
 These initial analyses ignored the clustering of observation days within participants of the survey.
@@
 The BIC declines with the number of day level classes increases.
-However, the improvement of BIC dropped to less than 1000 from 3 classes to 4 classes solutions (658.9) and from 4 classes to 5 classses solutions (361.7).
+However, the improvement of BIC dropped to less than 1000 from 3 classes to 4 classes solutions (658.9) and from 4 classes to 5 classes solutions (361.7).
 Entropy index indicates that the 4 classes model could explain about 51\% percent of the data, while \textit{p} values of Lo-Mendell-Rubun LRT suggest that the more classes we fit, the better model we will have until up to 6 classes (\textit{p} = 0.06 and is not shown in the table).
-From the parsimony point of view, we extended the model with random effects building on 2 classes, 3 classes and 4 classes solutions.
+From the parsimony point of view, we extended the model with random effects building on 2 classes, 3 classes, and 4 classes solutions.
 
@@
 However, after these solutions were checked in more details, the potentially most substantively interpretable model was found to be the 3$\times$3 random effect model, which is the model with 3 latent classes in the day level, and 3 latent classes in the individual level.
-We must emphasize that different researchers may have made decision slightly different from ours, we have provided other solutions in the \textbf{Appendix \ref{AppendixC}} for reference.
+We must emphasize that different researchers may have made decision slightly different from ours, we have provided other solutions in \textbf{Appendix \ref{AppendixC}} for reference.
 
-In the 3$\times$3 random effect model solution we have chosen, there were 39.5\%, 20.4\%, and 40.1\% observations classified into 3 latent groups in the day level.
-The overall counts and percentages for each responses within each time slot and the distributions of the solution are presented in \textbf{Table \ref{tab:daylevel}}.
+In the 3$\times$3 random effect model solution we have chosen, there were 39.5\%, 20.4\%, and 40.1\% observations classified into 3 latent groups at the day level.
+The overall counts and percentages for each response within each time slot and the distributions of the solution are presented in \textbf{Table \ref{tab:daylevel}}.
 The trajectories illustrating the change of the probabilities of each response to carbohydrate eating during the hours of the day are shown separately by three types of days in \textbf{Figure \ref{fig:level1}}.
@@
 
-Class 1 days \textbf{(Figure \ref{fig:level1}-A)} were given the name of "high percentage carbohydrate day" since in these days of survey, the probabilities of carbohydrate contributed higher or equal to 50\% of the energy consumed were always higher than that in the other two types of days.
+Class 1 days \textbf{(Figure \ref{fig:level1}-A)} were given the name of "high percentage carbohydrate day" since in these days of the survey, the probabilities of carbohydrate contributed higher or equal to 50\% of the energy consumed were always higher than that in the other two types of days.
 Specifically, high percentage carbohydrate days were characterised with probabilities of over 0.6 in time slots between 6 am to 9 am, 9 am to 12 noon, and also 2 pm to 5 pm, during which the time slots may be interpreted as breakfast, morning snack, and afternoon snack time periods for many participants.
@@
 And after 9 am, within these days, the probability of having low carbohydrate contained food (carbohydrate contributed $<$ 50\% of total energy intake), was always higher than having high carbohydrate contained food (carbohydrate contributed $\geqslant$ 50\% of total energy intake).
-In class 2 days, participants also turned to have morning snacks (with only 0.079 possibility of \textbf{not} eating any food and similar probabilities of having either high or low carbohydrate contained food).
+In class 2 days, participants also turned to have morning snacks (with probability of only 0.079 of \textbf{not} eating any food and similar probabilities of having either high or low carbohydrate contained food).
 This phenomenon may also be interpreted as having a long and late breakfast (brunch) in these mornings.
-The probability of \textbf{not} eating any food was the lowest for low carbohydrate days during the midnight time slot (10 pm to 6 am), with probability of 0.590 compared with 0.680 and 0.751 in class 1 and class 3 days, respectively.
+The probability of \textbf{not} eating any food was the lowest for low carbohydrate days during the midnight time slot (10 pm to 6 am), with a probability of 0.590 compared with 0.680 and 0.751 in class 1 and class 3 days, respectively.
 
@@
 On the other hand, the consumption of protein (73.29 g), total fat (67.24 g), and alcohol (13.80 g) were the highest in the regular meals days.
-Moreover, in high percentage carbohydrate days, participants turned to consume the highest amount of fruit (107.40 g).
-There was no evidence of any difference for the consumption of yellow, red, or green vegetables across the three types of days (\textit{p} = 0.681).\vspace{-0.6cm}
+Moreover, in the high percentage carbohydrate days, participants turned to consume the highest amount of fruit (107.40 g).
+There was no evidence of any difference in the consumption of yellow, red, or green vegetables across the three types of days (\textit{p} = 0.681).\vspace{-0.6cm}
 
@@
 
-\subsection{Individual level LCA solution}\vspace{-0.3cm}
+\subsection{Individual-level LCA solution}\vspace{-0.3cm}
 
-In the random effect models we utilized the non-parametric approach, in which we added a level 2 (individual level) latent classes based on the random means from the level 1 (day level) latent class solution.
+In the random effect models, we utilized the non-parametric approach, in which we added a level 2 (individual level) latent classes based on the random means from the level 1 (day level) latent class solution.
 The results of the individual level LCA solution for 2 and 3 classes are presented in \textbf{Figure \ref{fig:CB2level2}}, and \textbf{\ref{fig:level2}}.
@@
 
-With two individual level latent classes \textbf{(Figure \ref{fig:CB2level2})}, one individual class is comprised of individuals with a relatively slightly higher proportion of having "low carbohydrate day" (22.1\%) compared to the other (17.4\%).
+With two individual-level latent classes \textbf{(Figure \ref{fig:CB2level2})}, one individual class is comprised of individuals with a relatively slightly higher proportion of having "low carbohydrate day" (22.1\%) compared to the other (17.4\%).
 This class represents nearly 65\% of the individuals.
-However, we believe these individual classes are not very distinguishable to each other.
+However, we believe these individual classes are not very distinguishable from each other.
 
-With three individual level latent classes \textbf{(Figure \ref{fig:level2})}, a low-carbohydrate eaters class, a moderate-carbohydrate eaters class, and a high-carbohydrate eaters class emerges.
+With three individual-level latent classes \textbf{(Figure \ref{fig:level2})}, a low-carbohydrate eaters class, a moderate-carbohydrate eaters class, and a high-carbohydrate eaters class emerge.
 43.1\% participants were identified as high-carbohydrate eaters, in these individuals, about 50\% of the days (2 out of 4 days) of their dietary diary could be classified as having high percentage carbohydrate days.
 Nearly 1 out of 4 days of their dietary diary were either "regular meals day" or "low carbohydrate day".
-28.1\% participants fell into the low carbohydrate eaters class in the left hand side of \textbf{Figure \ref{fig:level2}}, their recordings of food intake showed that in more than 60\% of their days, they were having "regular meals" which was characterised as with highest amount of fat and alcohol consumptions as already described in \textbf{Table \ref{tab:day-level-features}}.
+28.1\% participants fell into the low carbohydrate eaters class on the left-hand side of \textbf{Figure \ref{fig:level2}}, their recordings of food intake showed that in more than 60\% of their days, they were having "regular meals" which was characterised as with the highest amount of fat and alcohol consumptions as already described in \textbf{Table \ref{tab:day-level-features}}.
 Moderate carbohydrate eaters have comparable proportions (42.0\% vs.
-40.0\%) of having high carbohydrate days and regular meals day, 18.0\% of their dietary diary were found to be low carbohydrate days.
+40.0\%) of having high carbohydrate days and regular meals day, 18.0\% of their dietary diary was found to be low carbohydrate days.
 
@@
 
-After recognising that there were three potential latent groups of carbohydrate eaters in the UK adults, whose food consumption pattern were also probably switching from one to another during the survey, their average carbohydrate contribution to total energy intake (as well as the subtypes of carbohydrate actually consumed) within the 7 pre-defined time slots of the day were still of interest.
-Survey-design-weighted mean energy intake within each time slot of the day and their composition of contribution are illustrated in \textbf{Figure \ref{fig:energysourcesCB}}, weighted mean nutrients intakes are listed in \textbf{Table \ref{tab:tab-nutri-indi}}.
+After recognising that there were three potential latent groups of carbohydrate eaters in the UK adults, whose food consumption patterns were also probably switching from one to another during the survey, their average carbohydrate contribution to total energy intake (as well as the subtypes of carbohydrate actually consumed) within the 7 pre-defined time slots of the day were still of interest.
+Survey-design-weighted mean energy intake within each time slot of the day and their composition of contribution is illustrated in \textbf{Figure \ref{fig:energysourcesCB}}, weighted mean nutrients intakes are listed in \textbf{Table \ref{tab:tab-nutri-indi}}.
 
@@
 Among the three types of carbohydrate eaters, the mean of total energy intake over the 4 days of dietary survey was the highest (7985.8 kJ, 95\%CI: 7283.3, 8146.3) in the low carbohydrate eaters group, and the lowest (7341.8 kJ, 95\%CI: 7172.5, 7511.2) in the moderate eaters group \textbf{(Table \ref{tab:tab-nutri-indi})}.
-Sources of energy for each type of carbohydrate eaters by the 7 time slots were also different.
+Sources of energy for each type of carbohydrate eaters by the 7-time slots were also different.
 Low carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-A)} never had carbohydrate contributed more than 50\% of their total energy throughout the day.
-Energy from fat were the highest for low carbohydrate eaters most of the time during the day (except for time between 10 pm to 6 am next morning).
-Most impressively, energy contributed by alcohol was always the highest in low carbohydrate eaters, percentages for energy from alcohol for the 7 times slots were 1.4\% (6-9 am), 1.8\% (9-12 noon), 3.1\% (12-2 pm), 7.2\% (2-5 pm), 8.4\% (5-8 pm), 20.0\% (8-10 pm), and 31.2\% (10-6 am), respectively.
-Contributions from different energy sources were quite similar for moderate and high carbohydrate eaters, but their absolute amount of energy consumption at each time slot were largely different.
+Energy from fat was the highest for low carbohydrate eaters most of the time during the day (except for the time slot between 10 pm to 6 am next morning).
+Most impressively, energy contributed by alcohol was always the highest in low carbohydrate eaters, percentages for energy from alcohol for the 7-times slots were 1.4\% (6-9 am), 1.8\% (9-12 noon), 3.1\% (12-2 pm), 7.2\% (2-5 pm), 8.4\% (5-8 pm), 20.0\% (8-10 pm), and 31.2\% (10-6 am), respectively.
+Contributions from different energy sources were quite similar for moderate and high carbohydrate eaters, but their absolute amount of energy consumption at each time slot was largely different.
 Moderate carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-B)} were characterised as consuming the lowest energy (296.9 kJ) before 9 am, but having higher energy consumption (967.9 kJ) between 9 am and 12 noon time compared with low and high carbohydrate eaters.
@@
 Specifically, carbohydrate contributions to total energy intake were 65.3\% (6-9 am), 56.2\% (9-12 noon), 46.2\% (12-2 pm), 50.3\% (2-5 pm), 42.5\% (5-8 pm), 44.1\% (8-10 pm), and 49.9\% (10-6am).
-We also noticed that high carbohydrate eaters consumed their energy mainly from three time slots: 6-9 am, 12-2 pm, and 5-8 pm.
+We also noticed that high carbohydrate eaters consumed their energy mainly from the following three time slots: 6-9 am, 12-2 pm, and 5-8 pm.
 
-As expected, in total, the mean of total carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively \textbf{(Table \ref{tab:tab-nutri-indi})}.
-Total energy contributed by carbohydrate was close to 50\% in the high carbohydrate eaters, but was only 40.6\% in the low carbohydrate eaters.
-In terms of the subtypes (components) of the carbohydrate consumed at each time slot, high carbohydrate eaters consumed as much as more than 2 times (compared to low carbohydrate eaters) and nearly 4 times (against moderate carbohydrate eaterss) the amount of sugar (37.9g 95\% CI: 36.8, 39.2) and non-milk extrinsic sugar (i.e.
+In total, the mean of total carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively \textbf{(Table \ref{tab:tab-nutri-indi})}.
+Total energy contributed by carbohydrate was close to 50\% among the high carbohydrate eaters but was only 40.6\% among the low carbohydrate eaters.
+In terms of the subtypes (components) of the carbohydrate consumed at each time slot, high carbohydrate eaters consumed as much as more than 2 times (compared to low carbohydrate eaters) and nearly 4 times (against moderate carbohydrate eaters) the amount of sugar (37.9g 95\% CI: 36.8, 39.2) and non-milk extrinsic sugar (i.e.
 free sugar) (11.1g 95\%CI: 10.7, 11.6) between 6-9 am.
@@
 They consumed more sugar and starch during 9-12 noon, 2-5 pm, 8-10 pm, and 10-6 am.
-Low carbohydrate eaters turned to have similar temporal pattern of consuming carbohydrates but the absolute amount of fibre, sugar, free sugar, and starch were usually lower than that in the high carbohydrate eaters except for time slots of 2-5 pm, and 10-6 am.
-Strong evidence (\textit{p} < 0.001) suggested that the mean of total fibre consumption for low,
+Low carbohydrate eaters turned to have similar temporal pattern of consuming carbohydrates with the high carbohydrate eaters, but the absolute amount of fibre, sugar, free sugar, and starch were usually lower than that in the high carbohydrate eaters except for time slots of 2-5 pm, and 10-6 am.
+Strong evidence (\textit{p} < 0.001) suggested that the mean of to-
 
@@
 
-moderate, and high carbohydrate eaters were different: 13.7g (13.4, 14.0), 12.5g (12.1, 12.9), and 14.7g (14.4, 14.9) with all 95\% CI being exclusive to each other.
+tal fibre consumption for low, moderate, and high carbohydrate eaters were different: 13.7g (13.4, 14.0), 12.5g (12.1, 12.9), and 14.7g (14.4, 14.9) with all 95\% CI being exclusive to each other.
 It is also noteworthy that low carbohydrate eaters consumed the highest average amount of protein (79.9 g, 17.2\% of total energy), fat (74.7g, 35.4\% of total energy), and alcohol (20.8 g, 6.8\% of total energy) as we have described for \textbf{Figure \ref{fig:energysourcesCB}}.
@@
 The distribution of the carbohydrate eater types turned out to be changing with the year of survey.
-Low carbohydrate eaters represented 32.5\% of the population in the first year of survey, but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year.
-Proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015).
-There was no evidence of difference in employment status across three types of carbohydrate eaters.
+Low carbohydrate eaters represented 32.5\% of the population in the first year of survey but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year.
+The proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015).
+There was no evidence of any difference in employment status across three types of carbohydrate eaters.
 However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with partner (\textit{p} < 0.001); moderate carbohydrate eaters had the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.
@@
 95\% CIs of the social-demographic characteristics by carbohydrate eating latent class memberships in the UK
-adults. \\ (NDNS RP 2008/09-15/16, sample size = 6155)} \centering
+adults. \\ (NDNS RP 2008/09-15/16, sample size = 6155)} \centering\vspace{-0.3cm}
 \fontsize{9}{11}\selectfont
@@
 	\showrowcolors
-	Total (\%) & 28.4 (26.9, 29.9) & 28.7 (27.1, 30.3) & 43.0 (41.3, 44.7) & \\
+	Total (\%) & 28.3 (26.9, 29.9) & 28.7 (27.1, 30.3) & 43.0 (41.3, 44.7) & \\
 %	Country (\%) &  &  &  & 0.007\\
@@
 
-\subsection{Association between individual level latent classes and hypertension, and obesity.}\vspace{-0.3cm}
+\subsection{Association between individual-level latent classes and hypertension, and obesity.}\vspace{-0.3cm}
 
@@
 27862.0 \textsterling/year in hypertensive, \textit{p} < 0.001), and physical activity level (geometric mean: 0.81 hours/day in non-hypertensive compared with 0.53 hours/day in hypertensive, \textit{p} < 0.001) but not in men.
-Interestingly, in both sexes, hypertensive participants had higher proportion of being classified as low or high carbohydrate eaters; total energy and carbohydrate intake was higher in people without hypertension (\textit{p} < 0.001).
+Interestingly, in both sexes, hypertensive participants had a higher proportion of being classified as low or high carbohydrate eaters; total energy and carbohydrate intake were higher in people without hypertension (\textit{p} < 0.001).
 
@@
 level (\textit{p} = 0.022 for men, < 0.001 for women), average household income (\textit{p} = 0.011 for men, < 0.001 for women) were decreasing with elevated BMI.
-Living with partner or not was strongly positively associated with obesity in men but not in women.
+Living with a partner or not was strongly positively associated with obesity in men but not in women.
 Men with obesity were also found to have the lowest proportion of never being a smoker (47.9 \%), and the highest proportion of being an ex-smoker (32.9\%).
@@
 However, after adjustment of age, living with partner or not, average household income, education level, hypertension, smoking status, total energy intake, and alcohol consumption, the association attenuated to no difference.
-The interaction effect of whether living with partner or not on the association between carbohydrate eating patterns and WC was again found in women in total (\textit{p} for interaction = 0.009) and without diabetes (\textit{p} for interaction = 0.012).
+The interaction effect of whether living with a partner or not on the association between carbohydrate eating patterns and WC was again found in women in total (\textit{p} for interaction = 0.009) and without diabetes (\textit{p} for interaction = 0.012).
 Among women who were living with their partners, high carbohydrate eaters had 4.71 cm (95\%CI: 2.43, 7.00, \textit{p} < 0.001) smaller WC on average compared with low carbohydrate eaters.

### 2018-08-26 paper/Chapters/Chapter4.tex
typos again
grammarly checked

@@
 
-Among the dietary diaries collected, there were three distinct latent classes specifically for carbohydrate intake: 1) high probabilities of having high carbohydrate contained food across the hours of day (high percentage carbohydrate day); 2) low carbohydrate food dominant through out the hours of day (low percentage carbohydrate day); and 3) always having lunch and dinner day (regular meals day).
+Among the dietary diaries collected, there were three distinct latent classes specifically for carbohydrate intake: 1) high probabilities of having high carbohydrate contained food across the hours of day (high percentage carbohydrate day); 2) low carbohydrate food dominant throughout the hours of day (low percentage carbohydrate day); and 3) always having lunch and dinner day (regular meals day).
 And from these day level classifications and their features, one might anticipate that individuals who managed to follow the regular meals day might be eating a relatively healthier diet because it seemed to be a regular temporal eating habit; at this time point, we also believed that those who followed either high or low carbohydrate percentage days would probably consume higher total energy than those who followed mostly regular meals days.
@@
 For the first time, as far as we know, the day-to-day food intake pattern variation within individuals was successfully captured by MLCA models.
-Results from the MLCA models showed that from the perspective of carbohydrate consumption, people were indeed changing their diet from day to day even within a short term period of survey.
+Results from the MLCA models showed that from the perspective of carbohydrate consumption, people were indeed changing their diet from day to day even within a short-term period of survey.
 The MLCA models allowed the probability of following a certain type of carbohydrate eating day to vary across individuals.
@@
 Surprisingly, low carbohydrate eaters whose dietary recordings suggested that they were mostly following a regular temporal meals pattern turned out to be consuming the highest amount of total energy among the three types of carbohydrate eaters.
-Detailed profiling of energy composition according to the time slots revealed that low carbohydrate eaters actually had higher proportion of energy contributed by both alcohol and fat.
-High percentage of fat consumption was shown in all 7 time slots, energy coming from alcohol exceeded more than one fifth of the total energy after 8 pm.
+Detailed profiling of energy composition according to the time slots revealed that low carbohydrate eaters actually had a higher proportion of energy contributed by both alcohol and fat.
+A high percentage of fat consumption was shown in all 7-time slots, energy coming from alcohol exceeded more than one-fifth of the total energy after 8 pm.
 These findings explained why they were actually consuming the highest energy among the three types of carbohydrate eaters.
-In the meantime, we also found that participants consuming low carbohydrate food had higher prevalence of diabetes, hypertension, and obesity.
-These health issues might possibly lead them (or advices were given from their physicians) to replace carbohydrates in their diet to other energy sources such as fat, protein, or even alcohol.
+In the meantime, we also found that participants consuming low carbohydrate food had a higher prevalence of diabetes, hypertension, and obesity.
+These health issues might possibly lead them (or advice were given by their physicians) to replace carbohydrates in their diet to other energy sources such as fat, protein, or even alcohol.
 Therefore, there is a possibility that they chose to follow low carbohydrate diets out of health purpose, but many of them were replacing carbohydrates with higher energy condensed food or even alcohol at night which might indeed be a public health concern.
 
-Next, when looking into the details of the timing and composition of the energy intake among the moderate carbohydrate eaters, we realised that although these individuals did not consume as much alcohol as low carbohydrate eaters did at night, they consumed the highest amount of energy, especially during time period as late as after 10 pm.
+Next, when looking into the details of the timing and composition of the energy intake among the moderate carbohydrate eaters, we realised that although these individuals did not consume as much alcohol as low carbohydrate eaters did at night, they consumed the highest amount of energy, especially during the time period as late as after 10 pm.
 People fell into moderate carbohydrate eaters group seemed to have the tendency of having their food or meals later than high carbohydrate eaters.
@@
 High carbohydrate eaters were also found to be the ones that consumed the least amount of energy after 8 pm.
-Therefore, contrary to what was anticipated at the beginning, people who followed high percentage carbohydrate days for most of their time, were actually eating a healthier diet compared with the other two eating patterns.
+Therefore, contrary to what was anticipated at the beginning, people who followed high percentage carbohydrate days for most of their time were actually eating a healthier diet compared with the other two eating patterns.
 
-Our analyses looking for different temporal carbohydrate also highlighted the complexity of eating pattern behaviours in the population and the utility of exploratory, data-driven methods to objectively identify eating patterns that reflect both timing and quantities of food intake, which may have not been detected so far in the literature.
+Our analyses looking for different temporal carbohydrate also highlighted the complexity of eating pattern behaviours in the population and the utility of exploratory, data-driven methods to objectively identify eating patterns that reflect both timing and quantities of food intake, which may not have been detected so far in the literature.
 
-\section{Association between carbohydrate eating patterns and health outcomes}
+\section{Associations between carbohydrate eating patterns and health outcomes}
 
-Among men, who were classified as moderate carbohydrate eaters probably had lower odds of having hypertension, after adjustment of age, live with partner or not, educational level, BMI, smoking status and total energy intake.
+Among men, who were classified as moderate carbohydrate eaters probably had lower odds of having hypertension, after adjustment of age, live with a partner or not, educational level, BMI, smoking status and total energy intake.
 As discussed above, moderate carbohydrate eaters turned to have meals (or energy consumption) later in time compared with high carbohydrate eaters.
-But, it is noteworthy that low carbohydrate eaters also consumed large amount of energy (from both fat and alcohol) at night.
+But, it is noteworthy that low carbohydrate eaters also consumed a large amount of energy (from both fat and alcohol) at night.
 Therefore, considering that moderate carbohydrate eaters were younger than low carbohydrate eaters (although age was adjusted in the full models), there is probably reverse causality exists here (also due to the nature of cross-sectional study).
@@
 High carbohydrate eaters had lower BMI and WC in those lived with their partners, while moderate carbohydrate eaters had higher WC in those who lived alone after adjustment of age, education level, smoking status, total energy intake, and alcohol consumption.
-High carbohydrate eaters who were characterised with high and early in the day energy consumption and low fat and alcohol intake may reflect a healthier diet and lifestyle, but this might be different between women who lived alone and those who lived with their partners.
-It was often assumed that live alone may associated with lower diversity of food intake, and a higher likelihood of having an unhealthy dietary choice \parencite{hanna2015relationship}.
-Therefore, there may be differences in the actual contents consumed in their high carbohydrates, or there may be other social, psychological or lifestyle related factors related with living alone which were not measured or did not included in the models.
-Thus, the inverse association between high carbohydrate eating pattern and BMI or abdominal obesity were only observed among women who lived with partners, further investigation on this hypothesis is needed.
+High carbohydrate eaters who were characterised with high and early in the daily energy consumption and low fat and alcohol intake may reflect a healthier diet and lifestyle, but this might be different between women who lived alone and those who lived with their partners.
+It was often assumed that live alone may associate with a lower diversity of food intake, and a higher likelihood of having an unhealthy dietary choice \parencite{hanna2015relationship}.
+Therefore, there may be differences in the actual contents consumed in their high carbohydrates, or there may be other social, psychological or lifestyle-related factors related with living alone which were not measured or did not include in the models.
+Thus, the inverse association between high carbohydrate eating pattern and BMI or abdominal obesity were only observed among women who lived with partners, further investigation of this hypothesis is needed.
 Whereas the reason why moderate carbohydrate eaters' WC was larger than low carbohydrate eaters only among women who lived alone is unknown, given that the evidence of this association was weak and borderline significant, whether it was just a false positive finding should also be explored in other studies.
@@
 
-There are several limitations in the current project that merits consideration.
+There are several limitations in the current project that merit consideration.
 
@@
 In the multilevel analyses, these 3 or 4 days' observations were treated as if they were exchangeable in the models.
-Since one's diet might change according to season, day of the week (weekdays or weekends), or sometimes depends on what they had consumed the day before, exchangeability of their diaries is a strong assumption and cannot be overcome by the MLCA models adopted here.
+Since one's diet might change according to the season, day of the week (weekdays or weekends), or sometimes depends on what they had consumed the day before, exchangeability of their diaries is a strong assumption and cannot be overcome by the MLCA models adopted here.
 Other statistical techniques, which could take the order or the longitudinal nature of the data into account, such as repeated measures latent class analysis (RMLCA), latent transition analysis (LTA) \parencite{collins2010latent}, or latent class growth analysis (LCGA) \parencite{davidian2008growth,jung2008introduction,andruff2009latent} are not applicable for the NDNS RP dataset.
 For the purpose of maintaining the response rate, flexibility was allowed for the NDNS RP participants in their choice of which day to begin their diary.
-But the above mentioned alternative models require that the 3 or 4 repeated measurements of food diaries to be recorded at the same time points longitudinally.
+But the above mentioned alternative models require that the 3 or 4 repeated measurements of food diaries be recorded at the same time points longitudinally.
 Specifically, LCGA models (also called growth mixture model) will also need to model the change of the odds of the probability over time as a function (quadratic, or cubic) which is apparently not the objective in the current project.
 
-Secondly, the classification of individuals to latent carbohydrate eating classes were defined by maximum posterior probability assignment rule.
+Secondly, the classification of individuals to latent carbohydrate eating classes was defined by maximum posterior probability assignment rule.
 This approach assigns individuals to the class for which they have the highest posterior probability of membership \parencite{nagin2005group}.
-The other approach is multiple pseudo-class draws \parencite{wang2005residual}, which was proposed in attempt to account for uncertainty in class assignment.
+The other approach is multiple pseudo-class draws \parencite{wang2005residual}, which was proposed in an attempt to account for uncertainty in class assignment.
 However, the maximum probability rule is still believed to be able to minimize the number of incorrect assignments \parencite{goodman20071}.
@@
 Thirdly, information regarding the detailed occupations of the participants was not available and because of which we could not exclude those who had a shift work involving night work.
-But considering that completing a 4-consecutive-day food diary would be a large burden for the participants, those had a shift work involving night work might possibly performed with relatively lower compliance and could not complete their diary for at least 3 days.
+But considering that completing a 4-consecutive-day food diary would be a large burden for the participants, those had a shift work involving night work might possibly perform with relatively lower compliance and could not complete their diary for at least 3 days.
 But this hypothesis cannot be verified in the NDNS RP dataset.
-If people working with shift work were included in the NDNS RP sample, the classification in both levels as well as their associations with either hypertension or BMI would be biased.
+If people working with shift work were included in the NDNS RP sample, the classification in both levels, as well as their associations with either hypertension or BMI would be biased.
 Furthermore, under-reporting due to the burden of writing down everything they eat at each occasion is also a concern in the food diaries collected.
-To evaluate the influence of under-reporting in the NDNS RP sample, study team of NDNS RP conducted doubly labelled water (DLW) sub-study within the survey.
+To evaluate the influence of under-reporting in the NDNS RP sample, the study team of NDNS RP conducted doubly labelled water (DLW) sub-study within the survey.
 The details of this sub-study can be accessed from the Appendix X of the Official Reports provided by Public Health England \parencite{bates2014national,roberts2018national,NDNSofficial}.
@@
 Results of the sub-study showed reasonable agreement between EI and TEE (overall ratio: 0.73).
-Reasons such as misreporting of actual consumption; under-reported or modified usual intake due to the burden of the survey/DLW sub-study are potential factors may contributed to under-reporting of their EI.
+Reasons such as misreporting of actual consumption; under-reported or modified usual intake due to the burden of the survey/DLW sub-study are potential factors may contribute to under-reporting of their EI.
 We cannot extrapolate the estimated under-reporting to the whole sample since other individuals' diet might be affected by under-reporting differentially.
@@
 generalizable to populations in other countries.
-Since the carbohydrate eating patterns in both day level and individual level probably only represent the socio-cultural and life-style characteristics of the adult population in the UK.
+Since the carbohydrate eating patterns in both day level and individual level probably only represent the socio-cultural and lifestyle characteristics of the adult population in the UK.
 Further researches are warranted to explore and better understand the eating patterns in other populations.
@@
 We applied a novel, objective approach using MLCA to examine the carbohydrate eating patterns while applying standardised criteria to determine the numbers of latent classes.
-The process of finding the classifications through model-based, data-driven procedure minimises reliance on researchers' preconcieved notions of eating patterns.
+The process of finding the classifications through model-based, data-driven procedure minimises reliance on researchers' preconceived notions of eating patterns.
 Eating patterns were determined from 4 consecutive days of well-designed, fully-examined food diaries.
@@
 We have successfully defined carbohydrate eating patterns in the general population in the UK adults using the NDNS RP database in both observation day level and individual level.
-Low carbohydrate eaters turned to have more energy that contributed by both fat and alcohol.
+Low carbohydrate eaters turned out to have more energy that contributed by both fat and alcohol.
 Moderate carbohydrate eaters consumed the lowest total energy, while they had the tendency of having meals later in time-of-day.
 High carbohydrate eaters consumed most of their carbohydrate as well as energy earlier in time-of-day.
-These dietary patterns specifically for carbohydrate intake were found to be differed by timing, quantity and contributions to energy consumption.
-Compared with low carbohydrate eaters, men had moderate carbohydrate eating pattern may associated with a lower prevalence of hypertension, women in this latent class who lived alone may associated with a larger waist circumferences.
+These dietary patterns specifically for carbohydrate intake were found to be differed by timing, quantity, and contributions to energy consumption.
+Compared with low carbohydrate eaters, men had moderate carbohydrate eating pattern may associate with a lower prevalence of hypertension, women in this latent class who lived alone may associate with a larger waist circumference.
 Among women who lived with partners, high carbohydrate eating pattern was associated with both lower BMI and smaller waist circumferences.
-Longitudinal designed studies are needed in finding whether the eating patterns themselves are changing over time and in investigating how such circadian eating patterns may relate to the change of blood pressure, obesity, and other health outcomes (incidence of cancer, cardiovascular diseases, or perhaps mortality).
+Longitudinally designed studies are needed in finding whether the eating patterns themselves are changing over time and in investigating how such circadian eating patterns may relate to the change of blood pressure, obesity, and other health outcomes (incidence of cancer, cardiovascular diseases, or perhaps mortality).

### 2018-08-26 paper/main.tex
typo fixed
typos again
grammarly checked

@@
 \addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
-\noindent I, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:
+\noindent I declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:
 
@@
 High-carb eaters consumed most of their carb and energy within time slots of 6-9 am, 12-2 pm and 5-8 pm.
-In men, moderate-carb eaters may had lower odds of having hypertension compared with low-carb eaters (adjusted OR: 0.64, 95\%CI: 0.41, 1.01).
+In men, moderate-carb eaters may have lower odds of having hypertension compared with low-carb eaters (adjusted OR: 0.64, 95\%CI: 0.41, 1.01).
 In women, high-carb eaters lived with partners had both lower BMI (-1.76 kg/m\textsuperscript{2}, -2.87, -0.73) and WC (-4.71 cm, -7.00, -2.43) compared with low-carb eaters, although these inverse associations were not observed in women who lived alone (\textit{p} for interaction 0.014, and 0.009).
@@
 Contrary to the expectation, profiles of high-carb eaters seemed to be healthier among three types of carb eaters.
-Low-carb eaters probably followed the diet out of health purposes but they may have chosen fat or alcohol as replacements of carb, which could probably be a concern from public health point of view.
-Whether these circadian carb-eating patterns are associated with change of blood pressure and/or obesity longitudinally should be further investigated.
+Low-carb eaters probably followed the diet out of health purposes but they may have chosen fat or alcohol as replacements of carb, which could probably be a concern from a public health point of view.
+Whether these circadian carb-eating patterns are associated with changes of blood pressure and/or obesity longitudinally should be further investigated.
 
@@
 \textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
-\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated hemoglobin \\
+\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated haemoglobin \\
 %\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
@@
 \textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
-\textbf{RMLCA} & \textbf{R}epeated \textbf{Measures} \textbf{LCA} \\
+\textbf{RMLCA} & \textbf{R}epeated \textbf{M}easures \textbf{LCA} \\
 \textbf{TC} & \textbf{T}otal \textbf{C}holesterol \\

### 2018-08-26 paper/Chapters/Chapter2.tex
grammarly checked again

@@
 	\item $ U_{ijk} $ represents the response of carbohydrate eating (one of the following: not eating any food, $< 50\%$ of the energy, or $\geqslant 50\%$ of the energy) on the $i$th day of the survey ($i \in (1,2,3,4)$) in $j$th individual at the $k$th time slot of the day ($k \in (1, 2, 3, \cdots, 7)$);
-	\item $G_{ij}$ denotes the latent class membership for $j$th individuals on $i$th day of the survey, the total number of day-level latent class is $T$;
+	\item $G_{ij}$ denotes the latent class membership for $j$th individuals on the $i$th day of the survey, the total number of day-level latent class is $T$;
 %	\item A specific latent class is referred to as $t$, and the total number of level 1 latent classes is denoted by $T$;
@@
 	\item $CB_j$ is the individual-level latent class membership for the $j$th individual;
-	\item $\gamma_{tm}$ is day-level and individual-level indicators. 
+	\item $\gamma_{tm}$ is the day-level and individual-level indicators. 
 \end{itemize}

### 2018-08-26 paper/Chapters/Chapter3.tex
grammarly checked again

@@
 And after 9 am, within these days, the probability of having low carbohydrate contained food (carbohydrate contributed $<$ 50\% of total energy intake), was always higher than having high carbohydrate contained food (carbohydrate contributed $\geqslant$ 50\% of total energy intake).
-In class 2 days, participants also turned to have morning snacks (with probability of only 0.079 of \textbf{not} eating any food and similar probabilities of having either high or low carbohydrate contained food).
+In class 2 days, participants also turned to have morning snacks (with a probability of only 0.079 of \textbf{not} eating any food and similar probabilities of having either high or low carbohydrate contained food).
 This phenomenon may also be interpreted as having a long and late breakfast (brunch) in these mornings.
@@
 The distribution of the carbohydrate eater types turned out to be changing with the year of survey.
-Low carbohydrate eaters represented 32.5\% of the population in the first year of survey but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year.
+Low carbohydrate eaters represented 32.5\% of the population in the first year of the survey but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year.
 The proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015).
@@
 
-\textbf{Table \ref{tab:tab1BMI}} shows the characteristics for participants according to their obesity status stratified by sex.
+\textbf{Table \ref{tab:tab1BMI}} shows the characteristics of participants according to their obesity status stratified by sex.
 The survey design-weighted prevalence for being overweight and obese in the UK adults were estimated to be 43.4\% and 25.7\% in men, and 30.9\% and 27.4\% in women.

### 2018-08-26 paper/main.tex
grammarly checked again

@@
 
-\large \textbf{Submitted in part fulfillment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
+\large \textbf{Submitted in partial fulfillment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
 %\textit{in the}\\[0.4cm]
@@
 \begin{itemize}
-\item This work was done wholly while in candidature for a MSc degree in Medical Statistics at London School of Hygiene and Tropical Medicine.
+\item This work was done wholly while in candidature for an MSc degree in Medical Statistics at London School of Hygiene and Tropical Medicine.
 \item No part of this thesis has previously been submitted for a degree or any other qualification at London School of Hygiene and Tropical Medicine or any other institution.
@@
 Low-carb eaters probably followed the diet out of health purposes but they may have chosen fat or alcohol as replacements of carb, which could probably be a concern from a public health point of view.
-Whether these circadian carb-eating patterns are associated with changes of blood pressure and/or obesity longitudinally should be further investigated.
+Whether these circadian carb-eating patterns are associated with changes in blood pressure and/or obesity longitudinally should be further investigated.
 
@@
 
-\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
+\textbf{AIC} & \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
 \textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated haemoglobin \\
@@
 %\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
-\textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
+\textbf{BIC} & \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
 \textbf{CI}  & \textbf{C}onfidence \textbf{I}nterval \\

### 2018-08-28 paper/Chapters/Chapter2.tex
language checked by Hunter

@@
 For homemade dishes, participants were asked to record on a separate page in the diary the individual ingredients and quantities for the whole dish along with a brief description of the cooking method and how much of dish they had consumed.
-In each eating occasion, in addition to the details of what and how much was eaten, participants were also asked to record: when was it, where they were, and who they were eating with.
+For each eating occasion, in addition to the details of what and how much was eaten, participants were also asked to record: when was it, where they were, and who they were eating with.
 An example, used as guidance for participants, of a food diary for one day is shown in \textbf{Appendix \ref{AppendixE}}.\vspace{-0.3cm}
@@
 \begin{itemize}
-	\item Total energy intake = (protein(gram) $\times$ 17) + (fat(gram) $\times$ 37) + (carbohydrate(gram) $\times$ 16) + (alcohol(gram) $\times$ 29)  kJ;
-	\item Carbohydrate intake = total sugars (gram) + starch (gram); 
-%	\item Total sugars = sum of all individual sugars (gramme).
+	\item Total energy intake = (protein $\times$ 17) + (fat $\times$ 37) + (carbohydrate $\times$ 16) + (alcohol $\times$ 29)  kJ;
+	\item Carbohydrate intake = total sugars + starch; 
+	\item Where all quantities above were measured as mass in grams.
 \end{itemize}
@@
 Time across a typical survey day was divided into 7 time slots in the dietary diary of NDNS RP: 6 am to 9 am, 9 am to 12 noon, 12 noon to 2 pm, 2 pm to 5 pm, 5 pm to 8 pm, 8 pm to 10 pm, and 10 pm to 6 am next morning.
-To produce a sequence of discrete responses regarding the carbohydrate intake we are interested, the energy consumption within each time slot over the four days of survey for each participant were calculated.
-The percentages of total energy intake that contributed by carbohydrate within each time slot were then estimated.
-Since we planned to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical, the responses were then dichotomised according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e.
-if within a time slot where there is any energy intake occurred, carbohydrate consumption was categorised into whether it's energy contribution was lower or higher/equal to 50\% of total energy intake within that time slot.
-Consequently, for each day of the recording, there were 7 data points generated by the diary, each data point included one of the following responses:
+To produce a list of discrete responses for our variable of interest, the energy consumed within each time slot over the four days of survey for each participant were calculated.
+The percentages of total energy intake contributed by carbohydrate within each time slot were then calculated.
+Since we planned to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical, the responses were then dichotomised according to these percentages of the energy intake at a cut-off value of 50\%, i.e.
+if within a time slot where there any energy intake occurred, carbohydrate consumption was categorised by whether its energy contribution was lower or higher/equal to 50\% of total energy intake within that time slot.
+Consequently, for each day of the recording, there were 7 data points generated by the diary.
+Each data point included one of the following responses:
 
@@
 	\item Randomly select 27 or 28 addresses in that postcode area; 
-	\item Randomly select one household at that address; 
-	\item Selected addresses were randomly allocated to one of two groups to determine whether an adult (aged 19 years or older) and a child (aged 1.5 to 18 years) or a child only, were selected for interviews.
+	\item Randomly select one household at that address for interviews; 
+	\item Selected addresses where children resided were randomly allocated to one of two groups to determine whether an adult (aged 19 years or older) and a child (aged 1.5 to 18 years) or a child only, were selected for interviews.
 \end{itemize}
@@
 
-The strata that used to calibrate proportions in the sample include: age-group (1.5-3, 4-6, 7-10, 11-15, 16-18, 19-24, 25-29, 30-39, 40-49, 50-59, 60-64, 65-69, and over 70 years); sex (men or women); and regions (Northern Ireland, Scotland, Wales, and the nine regions of England).
+The strata used to calibrate proportions in the sample include: age-group (1.5-3, 4-6, 7-10, 11-15, 16-18, 19-24, 25-29, 30-39, 40-49, 50-59, 60-64, 65-69, and over 70 years); sex (men or women); and regions (Northern Ireland, Scotland, Wales, and the nine regions of England).
 
-Two steps of weighting system are designed in the NDNS RP to assure that the combined sample will be representative of the UK population:
+Two steps of the weighting system were designed in the NDNS RP to assure that the combined sample would be representative of the UK population:
 
@@
 	\item An overall selection weight, which is the product of the address, dwelling unit, catering (household) unit, and individual selection weights, was generated to correct for the unequal selection probabilities.
-These weights are the inverses of the selection probabilities at each level of the random sampling process and they can be used to compensate for differences in the chance of selection of an individual.
+These weights are the inverses of the selection probabilities at each level of the random sampling process, and they can be used to compensate for differences in the chance of selection of an individual.
 	\item An iterative procedure was used to adjust the selection weights until the distribution of the weighted sample matched that of the population for age-group, sex, and geographical region.
@@
 The inverses of these predicted probabilities were used as a set of non-response weights so that participants with a low predicted probability got a larger weight, increasing their representation in the sample.
-Then the nurse/blood sample weights were re-scaled so that the sum of the weights equalled the number of participants who had a nurse visit/who provided a blood sample.
+Then the nurse/blood sample weights were re-scaled so that the sum of the weights equalled the number of participants who had a nurse visit or who provided a blood sample.
 The final nurse/blood weights should, therefore, make the sample participants representative of all eligible persons in the population.
@@
 
-Computer-assisted personal interviews were conducted for the selected individuals by trained interviewers to collect background information on smoking habits (current, ex-smokers, and never), ethnicity (white, non-white), education level (lower than degree/degree or above level), living with a partner or not and other socio-demographic variables.
-Participants also had their height, weight, blood pressure, waist circumferences (WC) measured by the nurses.
+Computer-assisted personal interviews were conducted for the selected individuals by trained interviewers to collect background information on smoking habits (current, ex-smokers, and never), ethnicity (white, non-white), education level (lower than degree/degree or above level), living with a partner or not, and other socio-demographic variables.
+Participants also had their height, weight, blood pressure, and waist circumferences (WC) measured by the nurses.
 
 Specifically, blood pressure was measured in a sitting position using an automated, validated machine, the Omron HEM907, after a five-minute rest.
-The means of second and third readings, taken at one-minute intervals, were used in the current report.
+The mean of the second and third readings, taken at one-minute intervals, were used in the current report.
 Hypertension was defined as with systolic blood pressure of 140 mmHg or above, and/or diastolic blood pressure of 90 mmHg or above, and/or taking any medication specifically to reduce blood pressure.
@@
 The major difference is that the latent variable in LCA is categorical, not continuous as in factor analysis.
-The basic assumptions in LCA are independent observations, and local independence, as shown in the fundamental expression of a typical LCA model: \vspace{-0.8cm}
+The basic assumptions in LCA are independent observations and local independence, the latter as shown in the fundamental expression of a typical LCA model: \vspace{-0.8cm}
 
@@
 However, in the NDNS RP data set, the assumption of independent observations is violated.
-Each individual completed their dietary diary for three/four consecutive days, their diary recordings were later converted into three/four sequences of categorical responses reflecting the type of carbohydrate consumption at each time slot of the day.
+Each individual completed their dietary diary for three/four consecutive days, their diary recordings were later converted into three/four vectors of categorical responses reflecting the type of carbohydrate consumption at each time slot of the day.
 The observed sequences (observed days) are nested within the participants and therefore are not independent.
@@
 
-Multilevel latent class analysis accounts for the nested structure of the data by allowing latent class intercepts to vary across level 2 units and thereby examining if and how level 2 units influence the level 1 latent classes.
+Multilevel latent class analysis accounts for the nested structure of the data by allowing latent class intercepts to vary across level 2 units, thereby examining if and how level 2 units influence the level 1 latent classes.
 These random intercepts allow the probability of membership in a particular level 1 (observation days) latent class to vary across level 2 units (e.g., here in the current context are the individuals).
@@
 
-Thus, for a binary outcome $C_{ij} = 0, 1$ (low $=0$ or high $=1$ carbohydrate eating days), where $i$ denotes the observation days $(i = 1, 2, 3, 4)$, and $j$ denotes the individual $(j = 1, 2, \cdots, 6155)$.
-The 2-level random intercept logistic regression model can be expressed as:\vspace{-0.4cm}
+Thus, for a binary outcome $C_{ij} = 0, 1$ (low $=0$ or high $=1$ carbohydrate eating days), where $i$ denotes the observation days $(i = 1, 2, 3, 4)$, and $j$ denotes the individual $(j = 1, 2, \cdots, 6155)$, the 2-level random intercept logistic regression model can be expressed as:\vspace{-0.4cm}
 
@@
 
-The same framework can be used to consider random effects in an LCA model, but instead of saying that $C_{ij}$ is either low or high carbohydrate eating days as if we already know, it is now replaced by a latent variable $G_{ij}$ which indicates the typologies of carbohydrate eating patterns.
-Then we can use the day-level data to assess the log-odds of belonging to the $k$th type of carbohydrate eating pattern on a specific day of the survey, and we allow the log-odds to vary across individuals.
+The same framework can be used to consider random effects in an LCA model, but instead of saying that $C_{ij}$ is either low or high carbohydrate eating days as if we already know the set of latent classes, it is now replaced by a latent variable $G_{ij}$ which indicates the typologies of carbohydrate eating patterns.
+Then we can use the day-level data to assess the log-odds of belonging to the $k$th type of carbohydrate eating pattern on a specific day of the survey and allow the log-odds to vary across individuals.
 Therefore, for some persons, the log-odds of having a $k$th type of carbohydrate eating pattern during the survey can be high, but for the other persons, the log-odds of following the $k$th type of carbohydrate eating pattern can be low.
@@
 \begin{equation}
-P(C_{ij} = t | CB_j = m)  = \frac{\exp(\gamma_{tm})}{\sum_{r=1}^{T}\exp(\gamma_{tm})}
+P(C_{ij} = t | CB_j = m)  = \frac{\exp(\gamma_{tm})}{\sum_{r=1}^{T}\exp(\gamma_{rm})}
 \end{equation}
@@
 \begin{itemize}
-	\item Firstly, we ignored the multilevel structure of the data and estimated a series of traditional LC models to determine the number of classes at the observational day-level;
+	\item First, we ignored the multilevel structure of the data and estimated a series of traditional LC models to determine the number of classes at the observational day-level;
 	\item Next, a series of MLCA models were fitted to account for the multilevel structure of the data.
 In these models, the number of day-level classes was based on the best fitting LCA model from the first step, and the LCA model at the individual-level was estimated to identify the number of individual-level latent classes;
-	\item Thirdly, when the number of individual-level latent classes is defined based on the previous stage, the number of day-level classes was modified (one class lower and one class higher than in the second step) to see the effect of changing level 1 classes and confirm the best fitting model.
+	\item Last, once the number of individual-level latent classes was defined based on the previous stage, the number of day-level classes was modified (one class lower and one class higher than in the second step) to investigate the effect of changing level 1 classes and to confirm the best fitting model.
 \end{itemize}
 
-The number of classes in level 1 was determined by 1) the evaluation of model fit indices, including the Bayesian information criterion (BIC), and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compares $q$ vs.
-$q-1$ classes models, where $q$ is the number of latent classes and most importantly, 3) pattern interpretability.
-In the steps of performing multilevel LCA, where LMR-LRT is not available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day-level and individual-level.
+The number of classes in level 1 was determined by 1) the evaluation of model fit indices, including the Bayesian information criterion (BIC) and entropy, which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compares $q$ vs.
+$q-1$ classes models, where $q$ is the number of latent classes; most importantly, 3) pattern interpretability.
+In the steps of performing multilevel LCA, where LMR-LRT is not available, the same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day-level and individual-level.
 MLCA models were fitted in Mplus 7.4 \parencite{muthen2005mplus}, the Mplus syntax and outputs are shown in \textbf{Appendix \ref{AppendixB}}.
@@
 
-day-level latent classes identified by the first step of MLCA were tabulated according to the day of week and also whether the diary was recorded during weekends or not.
+Day-level latent classes identified by the first step of MLCA were tabulated according to the day of week and also whether the diary was recorded during weekends or not.
 A contingency table giving the frequency of responses across the 7-time slots of the survey days was produced.
 Descriptive statistics for the dietary day-level recordings according to the latent class memberships were presented.
-Pearson $\chi^2$ test was used to compare the distribution of categorical variables.
+Pearson $\chi^2$ test was used to assess evidence fora difference in the distribution of categorical variables.
 One-way Analysis of Variance (ANOVA) was used to compare the means across the multiple groups for continuous variables.
@@
 	\item Potential confounders of the association between carbohydrate eating groups (exposure) and the outcomes were selected depending on the descriptive statistical analyses conducted above, i.e.
-those are associated with both the exposure and the outcome and also not on the causal pathway were selected as potential confounders.
-Those are strongly related with the outcomes but may not associate with carbohydrate eating groups may reduce the standard errors and so improve the precisions are also considered in the linear regression models.
-	\item Confounding and/or interaction effect from each of the potential factors were checked one by one.
-Interaction effects were tested using the adjusted Wald test testing whether the regression coefficients of the interaction terms are simultaneously equal to zero.
+those associated with both the exposure and the outcome and also not on the causal pathway were selected as potential confounders.
+Covariates that are strongly related with the outcomes but not associate with carbohydrate eating groups may reduce the standard errors and improve the precisions, so they were also considered in the linear regression models.
+	\item Confounding and/or interaction effects from each of the potential factors were checked one by one.
+Interaction effects were tested using the adjusted Wald test for whether the regression coefficients of the interaction terms are simultaneously equal to zero.
 	\item A preliminary model that includes all of the variables suggested to be confounders in the previous step was established. 
@@
 Other diagnostics for regular logistic regression models, such as estimating the pseudo-R\textsuperscript{2},  AIC or BIC, checking the standardized Pearson residuals, or covariate pattern residuals are currently not available for weighted survey data.
-	\item For linear regression models (WC, BMI), the assumption of independent observations is violated as soon as we weighted the sample.
+	\item For linear regression models (WC, BMI), the assumption of independent observations is violated as soon as we weight the sample.
 General checking such as QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance) are not available either.
-Outliers, leverage, and Cook's distance cannot be checked either, however, participants with extreme weightings (if exist) were checked by removing them and refit the models as a sensitivity analysis.
+Outliers, leverage, and Cook's distance cannot be checked either, however, participants with extreme weightings (if any) were checked by removing them and refitting the models as a sensitivity analysis.
 	\item Since under survey designed data, the sampling-weighted least squares are not maximum likelihood, it would not be possible to compare models using likelihood ratio test.
@@
 All statistical analyses, except for MLCA models, were performed with \code{svyset} command as implemented in Stata software version 15.1 \parencite{stata15}.
-The process of model fitting, covariates selection, interaction effect testings for the association between carbohydrate eating patterns and hypertension is shown as an example in \textbf{Appendix \ref{AppendixD}}.
+The process of model fitting, covariate selection, and interaction effect testing for the association between carbohydrate eating patterns and hypertension is shown as an example in \textbf{Appendix \ref{AppendixD}}.
 All \textit{p} values were two-sided.

### 2018-08-28 paper/Chapters/Chapter3.tex
language checked by Hunter

@@
 
-A series of traditional LCA of the responses to carbohydrate intake within 7-time slots of the day was first examined.
+A series of traditional LCA of the responses to carbohydrate intake within the 7 time slots of the day was first examined.
 These initial analyses ignored the clustering of observation days within participants of the survey.
 \textbf{Table \ref{tab:mixmodels}} shows the latent class solutions for one to five classes (see rows under the Fixed effects model section).
-The BIC declines with the number of day level classes increases.
-However, the improvement of BIC dropped to less than 1000 from 3 classes to 4 classes solutions (658.9) and from 4 classes to 5 classes solutions (361.7).
-Entropy index indicates that the 4 classes model could explain about 51\% percent of the data, while \textit{p} values of Lo-Mendell-Rubun LRT suggest that the more classes we fit, the better model we will have until up to 6 classes (\textit{p} = 0.06 and is not shown in the table).
-From the parsimony point of view, we extended the model with random effects building on 2 classes, 3 classes, and 4 classes solutions.
+The BIC declines with increases in the number of day level classes increases.
+However, the improvement of BIC dropped to less than 1000 from 3 class to 4 class solutions (658.9) and from 4 class to 5 class solutions (361.7).
+Entropy index indicates that the 4 class model could explain about 51\% percent of the data, while \textit{p} values of Lo-Mendell-Rubun LRT suggest that the more classes we fit, the better model we will have until up to 6 classes (\textit{p} = 0.06 and is not shown in the table).
+For the sake of parsimony, we only extended the model with random effects building on 2 class, 3 class, and 4 class solutions.
 
-The results of the random effect included models are presented in \textbf{Table \ref{tab:mixmodels}} under the Random effects model section.
-It is obvious that the BIC improves with the addition of the random effects which account for the nested structure of the data.
+The results of the random effects models are presented in \textbf{Table \ref{tab:mixmodels}} under the Random effects model section.
+It is obvious that the BIC improves with the addition of random effects to account for the nested structure of the data.
 Entropy indicates that 2 classes in the day level and 4 classes in the individual level may be the best solution mathematically.
-However, after these solutions were checked in more details, the potentially most substantively interpretable model was found to be the 3$\times$3 random effect model, which is the model with 3 latent classes in the day level, and 3 latent classes in the individual level.
-We must emphasize that different researchers may have made decision slightly different from ours, we have provided other solutions in \textbf{Appendix \ref{AppendixC}} for reference.
+However, after these solutions were checked in more details, the most substantively interpretable model was found to be the 3$\times$3 random effect model, which is the model with 3 latent classes in the day level and 3 latent classes in the individual level.
+We must emphasize that different researchers may have made decisions slightly different from ours, we have provided other solutions in \textbf{Appendix \ref{AppendixC}} for reference.
 
@@
 		\showrowcolors
-		Counts (\%) & 9667 (39.5) & 5002 (20.4) & 9814 (40.1) & \\
+		Counts (\% in row) & 9667 (39.5) & 5002 (20.4) & 9814 (40.1) & \\
 		Country (\%) &  &  &  & < 0.001\\
@@
 
-With two individual-level latent classes \textbf{(Figure \ref{fig:CB2level2})}, one individual class is comprised of individuals with a relatively slightly higher proportion of having "low carbohydrate day" (22.1\%) compared to the other (17.4\%).
+With two individual-level latent classes \textbf{(Figure \ref{fig:CB2level2})}, one individual class comprises individuals with a relatively slightly higher proportion of having "low carbohydrate day" (22.1\%) compared to the other (17.4\%).
 This class represents nearly 65\% of the individuals.
@@
 Moderate carbohydrate eaters have comparable proportions (42.0\% vs.
-40.0\%) of having high carbohydrate days and regular meals day, 18.0\% of their dietary diary was found to be low carbohydrate days.
+40.0\%) of having high carbohydrate days and regular meals days; 18.0\% of their dietary diary was found to be low carbohydrate days.
 
@@
 Contributions from different energy sources were quite similar for moderate and high carbohydrate eaters, but their absolute amount of energy consumption at each time slot was largely different.
-Moderate carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-B)} were characterised as consuming the lowest energy (296.9 kJ) before 9 am, but having higher energy consumption (967.9 kJ) between 9 am and 12 noon time compared with low and high carbohydrate eaters.
-Moderate carbohydrate eaters may turn to have later breakfast, later lunch, and probably later dinner as well.
-They had the highest total energy consumption (599.7 kJ) at night (10 pm - 6 am) across three types of eaters.
+Moderate carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-B)} were characterised as consuming the lowest energy (296.9 kJ) before 9 am but having higher energy consumption (967.9 kJ) between 9 am and 12 noon time compared with low and high carbohydrate eaters.
+Moderate carbohydrate eaters may tend to have later breakfast, later lunch, and probably later dinner as well.
+They had the highest total energy consumption (599.7 kJ) at night (10 pm - 6 am) across all three types of eaters.
 High carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-C)} consumed the highest total energy (929.0 kJ) during 6 am to 9 am in the morning and the lowest total energy between 10 pm to 6 am (205.5 kJ).
-Specifically, carbohydrate contributions to total energy intake were 65.3\% (6-9 am), 56.2\% (9-12 noon), 46.2\% (12-2 pm), 50.3\% (2-5 pm), 42.5\% (5-8 pm), 44.1\% (8-10 pm), and 49.9\% (10-6am).
+Specifically, carbohydrate contributions to total energy intake were 65.3\% (6-9 am), 56.2\% (9-12 noon), 46.2\% (12-2 pm), 50.3\% (2-5 pm), 42.5\% (5-8 pm), 44.1\% (8-10 pm), and 49.9\% (10-6 am).
 We also noticed that high carbohydrate eaters consumed their energy mainly from the following three time slots: 6-9 am, 12-2 pm, and 5-8 pm.
@@
 Total energy contributed by carbohydrate was close to 50\% among the high carbohydrate eaters but was only 40.6\% among the low carbohydrate eaters.
-In terms of the subtypes (components) of the carbohydrate consumed at each time slot, high carbohydrate eaters consumed as much as more than 2 times (compared to low carbohydrate eaters) and nearly 4 times (against moderate carbohydrate eaters) the amount of sugar (37.9g 95\% CI: 36.8, 39.2) and non-milk extrinsic sugar (i.e.
-free sugar) (11.1g 95\%CI: 10.7, 11.6) between 6-9 am.
-Moderate carbohydrate eaters had their carbohydrate intake more spread out.
+In terms of the subtypes (components) of the carbohydrate consumed at each time slot, high carbohydrate eaters consumed more than 2 times (compared to low carbohydrate eaters) and nearly 4 times (against moderate carbohydrate eaters) the amount of sugar (37.9g 95\% CI: 36.8, 39.2) and non-milk extrinsic sugar (i.e.
+free sugar, 11.1g 95\%CI: 10.7, 11.6) between 6-9 am.
+Moderate carbohydrate eaters had carbohydrate intakes that were more spread out throughout the day.
 They consumed more sugar and starch during 9-12 noon, 2-5 pm, 8-10 pm, and 10-6 am.
-Low carbohydrate eaters turned to have similar temporal pattern of consuming carbohydrates with the high carbohydrate eaters, but the absolute amount of fibre, sugar, free sugar, and starch were usually lower than that in the high carbohydrate eaters except for time slots of 2-5 pm, and 10-6 am.
-Strong evidence (\textit{p} < 0.001) suggested that the mean of to-
+Low carbohydrate eaters turned to have similar temporal pattern of consuming carbohydrates with the high carbohydrate eaters, but the absolute amount of fibre, sugar, free sugar, and starch consumed were usually lower than that in the high carbohydrate eaters except for time slots of 2-5 pm, and 10-6 am.
+Strong evidence (\textit{p} < 0.001) suggested that the
 
@@
 
-tal fibre consumption for low, moderate, and high carbohydrate eaters were different: 13.7g (13.4, 14.0), 12.5g (12.1, 12.9), and 14.7g (14.4, 14.9) with all 95\% CI being exclusive to each other.
+mean of total fibre consumption for low, moderate, and high carbohydrate eaters were different: 13.7g (95\%CI: 13.4, 14.0), 12.5g (95\%CI: 12.1, 12.9), and 14.7g (95\%CI: 14.4, 14.9) with all 95\% CI being exclusive to each other.
 It is also noteworthy that low carbohydrate eaters consumed the highest average amount of protein (79.9 g, 17.2\% of total energy), fat (74.7g, 35.4\% of total energy), and alcohol (20.8 g, 6.8\% of total energy) as we have described for \textbf{Figure \ref{fig:energysourcesCB}}.
@@
 Gender distribution across the three types of carbohydrate eaters was fairly even (\textit{p} = 0.119).
-The distribution of the carbohydrate eater types turned out to be changing with the year of survey.
+The distribution of the carbohydrate eater types appears to be changing with the year of survey.
 Low carbohydrate eaters represented 32.5\% of the population in the first year of the survey but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year.
@@
 There was no evidence of any difference in employment status across three types of carbohydrate eaters.
-However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with partner (\textit{p} < 0.001); moderate carbohydrate eaters had the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.
+However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with partner (\textit{p} < 0.001); moderate carbohydrate eaters had the lowest average income (27180.8 \textsterling/year), the highest proportion of non-white population (20.5\%), and a lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.
 
@@
 Low carbohydrate eaters had higher mean BMI (27.8 kg/m\textsuperscript{2}) and larger mean WC (98.9/89.9 cm in men/women) compared with 27.2, 27.3 kg/m\textsuperscript{2}, and 95.9/88.7 (men/women), 98.1/87.2 (men/women) cm in moderate and high carbohydrate eaters.
-Moderate carbohydrate eaters had the highest prevalence of being a current smoker (27.8\%), shortest time of daily physical activity (geometric mean: 0.87 hours/day), and the lowest prevalence of hypertension (20.2\%).
+Moderate carbohydrate eaters had the highest prevalence of being a current smoker (27.8\%), shortest time of daily physical activity (geometric mean: 0.87 hours/day), and lowest prevalence of hypertension (20.2\%).
 
@@
 The weighted prevalences of hypertension were 30.4\% in men and 27.5\% in women.
-Among both sexes, there were strong evidence of differences by hypertension status for age, education level, living with a partner or not, smoking status, BMI, abdominal obesity (WC), and prevalence of diabetes (\textit{p} < 0.01).
+Among both sexes, there was strong evidence of differences by hypertension status for age, education level, living with a partner or not, smoking status, BMI, abdominal obesity (WC), and prevalence of diabetes (\textit{p} < 0.01).
 No difference was found among either men or women for ethnicity.
@@
 95\% CI of the adjusted OR became narrower (OR: 0.64, 95\% CI: 0.41, 1.01, \textit{p} = 0.054) when BMI was replaced with WC in model 2.
-When diabetic men were excluded in Model 2, the ORs (95\%CI) for moderate and high carbohydrate eaters compared with low carbohydrate eaters were 0.65 (0.41, 1.03) and 0.73 (0.51, 1.06), respectively.
+When diabetic men were excluded in Model 2, the odds for moderate and high carbohydrate eaters compared with low carbohydrate eaters were 35\% (OR: 0.65, 95\%CI: 0.41, 1.03) and 27\% (OR:0.73, 95\%CI: 0.51, 1.06) lower, respectively.
 The negative associations between moderate carbohydrate eating pattern and hypertension were also observed in women, however, without any statistically significant evidence in the fully adjusted models.
@@
 
-level (\textit{p} = 0.022 for men, < 0.001 for women), average household income (\textit{p} = 0.011 for men, < 0.001 for women) were decreasing with elevated BMI.
-Living with a partner or not was strongly positively associated with obesity in men but not in women.
-Men with obesity were also found to have the lowest proportion of never being a smoker (47.9 \%), and the highest proportion of being an ex-smoker (32.9\%).
-Association between smoking status and obesity in women was only with very weak evidence (\textit{p} = 0.042) but similar pattern as in men was also observed (higher proportion of ex- and current smokers in overweight or obese women).
+level (\textit{p} = 0.022 for men, < 0.001 for women), and average household income (\textit{p} = 0.011 for men, < 0.001 for women) decreased with increases in BMI.
+Living with a partner or not was strongly positively associated with obesity for men but not for women.
+Men with obesity were also found to have the lowest proportion of never being a smoker (47.9\%) and the highest proportion of being an ex-smoker (32.9\%).
+Association between smoking status and obesity in women had only very weak evidence (\textit{p} = 0.042), but a similar pattern as in men was observed (higher proportion of ex- and current smokers in overweight or obese women).
 No difference was found for length of physical activity across obesity levels in men, while in women, somewhat weak inverse association (\textit{p}=0.038) was confirmed.
-Interestingly, predefined carbohydrate eating patterns were seemingly not associated with BMI in men (\textit{p} = 0.072) or in women (\textit{p} = 0.253).
+Interestingly, predefined carbohydrate eating patterns lacked evidence for an association with BMI in men (\textit{p} = 0.072) or in women (\textit{p} = 0.253).
 
@@
 
-	\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults, with or without diabetes. \\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
+	\caption{\label{tab:tab2BMI}Associations of moderate/high carbohydrate eating patterns versus low on BMI in UK adults, with or without diabetes.
+\\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
 	\centering
@@
     	\bottomrule
-		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
+		\multicolumn{6}{l}{{\scriptsize \textit{Note: }all units of BMI in kg/m\textsuperscript{2};}}\\
 		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; NDNS RP, national diet and nutrition survey rolling programme.}}\\
@@
 However, the 95\%CI of the regression coefficients were all wide and included the null value 0, indicating no statistically supported evidence for the inverse association.
-In women, evidence of interaction effect was found in whether live with a partner or not on the association between carbohydrate eating patterns and BMI (\textit{p} for interaction = 0.014 and 0.036 for women in total and without diabetes).
-For women who were 5.43living with partners, latent classes of carbohydrate eating patterns were negatively associated with BMI.
-Compared with women eating low carbohydrate food pattern, women having a high carbohydrate eating pattern were averagely associated with 1.76 kg/m\textsuperscript{2} lower BMI after adjustment of age, average household income, education level, smoking status, total energy intake and alcohol consumption.
+In women, evidence of an interaction effect was found between living with a partner or not and carbohydrate eating patterns for the outcome of BMI (\textit{p} for interaction = 0.014 and 0.036 for women in total and without diabetes).
+For women who were living with partners, latent classes of carbohydrate eating patterns were negatively associated with BMI.
+Compared with women eating a low carbohydrate food pattern, women having a high carbohydrate eating pattern were associated with an average 1.76 kg/m\textsuperscript{2} lower BMI after adjustment of age, average household income, education level, smoking status, total energy intake and alcohol consumption.
 95\%CI for the adjusted BMI difference was 0.73 to 2.78 kg/m\textsuperscript{2}, \textit{p} = 0.001.
 After excluding diabetic women, BMI was still 1.62 kg/m\textsuperscript{2} (95\%CI: 0.58, 2.65, \textit{p} = 0.002) smaller in high carbohydrate eaters versus low carbohydrate eaters on average.
-On the contrary, latent classes of carbohydrate eating patterns were positively associated with BMI in women who were living by themselves, although the regression coefficients were not statistically different from 0.
+On the contrary, latent classes of carbohydrate eating patterns were positively associated with BMI in women who were living by themselves, although there was no evidence that regression coefficients different from 0 (\textit{p} > 0.05).
 
-Similarly, when looking at the association between carbohydrate eating pattern and abdominal obesity (WC), men who were classified as moderate carbohydrate eaters were found to had about 3 cm (95\%CI: 0.52, 5.49 cm, \textit{p} = 0.018) smaller WC compared with low carbohydrate eaters in the crude model \textbf{(Table \ref{tab:tab2WC})}.
+Similarly, when looking at the association between carbohydrate eating pattern and abdominal obesity (WC), men who were classified as moderate carbohydrate eaters were found to have about 3 cm (95\%CI: 0.52, 5.49 cm, \textit{p} = 0.018) smaller WC compared to low carbohydrate eaters in the crude model \textbf{(Table \ref{tab:tab2WC})}.
 However, after adjustment of age, living with partner or not, average household income, education level, hypertension, smoking status, total energy intake, and alcohol consumption, the association attenuated to no difference.
-The interaction effect of whether living with a partner or not on the association between carbohydrate eating patterns and WC was again found in women in total (\textit{p} for interaction = 0.009) and without diabetes (\textit{p} for interaction = 0.012).
+The interaction effect of living with a partner or not on the association between carbohydrate eating patterns and WC was again found in women in total (\textit{p} for interaction = 0.009) and without diabetes (\textit{p} for interaction = 0.012).
 Among women who were living with their partners, high carbohydrate eaters had 4.71 cm (95\%CI: 2.43, 7.00, \textit{p} < 0.001) smaller WC on average compared with low carbohydrate eaters.
-The association remained when restricted the sample to non-diabetic women (-3.74 cm, 95\% CI: -5.97, -1.51,  \textit{p} = 0.001).
+The association remained after restricting the sample to non-diabetic women (-3.74 cm, 95\% CI: -5.97, -1.51,  \textit{p} = 0.001).
 However, for women who were living alone, moderate carbohydrate eaters had 3.17 cm (95\%CI: 0.05, 6.30, \textit{p} = 0.047) larger WC on average compared with low carbohydrate eaters.
-The evidence for the positive association between moderate carbohydrate eaters and WC in women became weaker but still with borderline significant when excluding diabetic women (3.08 cm, 95\%CI: -0.09, 6.25, \textit{p} = 0.057).
+The evidence for the positive association between moderate carbohydrate eaters and WC in women became weaker, but still had borderline significance when excluding diabetic women (3.08 cm, 95\%CI: -0.09, 6.25, \textit{p} = 0.057).
 
@@
 
-	\caption{\label{tab:tab2WC}Associations of carbohydrate eating patterns with WC in the UK adults , with or without diabetes. \\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
+	\caption{\label{tab:tab2WC}Associations of moderate/high carbohydrate eating patterns versus low on WC in UK adults, with or without diabetes.
+\\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
 	\centering
@@
 		\bottomrule
-		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
+		\multicolumn{6}{l}{{\scriptsize \textit{Note: }} All units of WC in cm;}\\
 		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: WC, waist circumference; NDNS RP, national diet and nutrition survey rolling programme.}}\\

### 2018-08-28 paper/Chapters/Chapter4.tex
language checked by Hunter

@@
 Among the dietary diaries collected, there were three distinct latent classes specifically for carbohydrate intake: 1) high probabilities of having high carbohydrate contained food across the hours of day (high percentage carbohydrate day); 2) low carbohydrate food dominant throughout the hours of day (low percentage carbohydrate day); and 3) always having lunch and dinner day (regular meals day).
-And from these day level classifications and their features, one might anticipate that individuals who managed to follow the regular meals day might be eating a relatively healthier diet because it seemed to be a regular temporal eating habit; at this time point, we also believed that those who followed either high or low carbohydrate percentage days would probably consume higher total energy than those who followed mostly regular meals days.
+From these day level classifications and their features, one might anticipate that individuals followed much of class 3) days, the regular meals day, might be eating a healthier diet because of regular eating habits.
+We might also believe that those who followed either high or low carbohydrate percentage days would consume higher total energy than those who followed mostly regular meals days.
 
-However, when the MLCA extended the model to individual level, three types of persons were further defined depending on their 4-day-diary: 1) low carbohydrate eaters, who mostly followed "regular meals day"; 2) moderate carbohydrate eaters, who had similar probabilities of following either "regular meals day" or "high percentage carbohydrate day"; 3) high carbohydrate eaters, who followed "high percentage carbohydrate day" for half of their survey.
+However, when the MLCA extended the model to an individual level, three types of persons were further defined depending on their 4-day-diary: 1) low carbohydrate eaters, who mostly followed "regular meals day"; 2) moderate carbohydrate eaters, who had similar probabilities of following either "regular meals day" or "high percentage carbohydrate day"; 3) high carbohydrate eaters, who followed "high percentage carbohydrate day" for half of their survey.
 For the first time, as far as we know, the day-to-day food intake pattern variation within individuals was successfully captured by MLCA models.
@@
 In the meantime, we also found that participants consuming low carbohydrate food had a higher prevalence of diabetes, hypertension, and obesity.
-These health issues might possibly lead them (or advice were given by their physicians) to replace carbohydrates in their diet to other energy sources such as fat, protein, or even alcohol.
-Therefore, there is a possibility that they chose to follow low carbohydrate diets out of health purpose, but many of them were replacing carbohydrates with higher energy condensed food or even alcohol at night which might indeed be a public health concern.
+These health issues might lead them (or advice were given by their physicians) to replace carbohydrates in their diet to other energy sources such as fat, protein, or even alcohol.
+Therefore, there is a possibility that they chose to follow low carbohydrate diets for health purposes, but many of them were replacing carbohydrates with higher energy condensed food or even alcohol at night which might indeed be a public health concern.
 
@@
 These individuals in the NDNS RP were younger, largely single, with lower average income, and lower education level.
-They might possibly correspond to the "late eaters" defined by previous studies \parencite{leech2017temporal, mansukhani2018investigating}.
+They might correspond to the "late eaters" defined by previous studies \parencite{leech2017temporal, mansukhani2018investigating}.
 
@@
 
-Among men, who were classified as moderate carbohydrate eaters probably had lower odds of having hypertension, after adjustment of age, live with a partner or not, educational level, BMI, smoking status and total energy intake.
-As discussed above, moderate carbohydrate eaters turned to have meals (or energy consumption) later in time compared with high carbohydrate eaters.
+Men who were classified as moderate carbohydrate eaters were estimated to have lower odds of having hypertension, after adjustment of age, live with a partner or not, educational level, BMI, smoking status and total energy intake.
+As discussed above, moderate carbohydrate eaters tended to have meals (or energy consumption) later in time compared with high carbohydrate eaters.
 But, it is noteworthy that low carbohydrate eaters also consumed a large amount of energy (from both fat and alcohol) at night.
-Therefore, considering that moderate carbohydrate eaters were younger than low carbohydrate eaters (although age was adjusted in the full models), there is probably reverse causality exists here (also due to the nature of cross-sectional study).
-That is, they were potentially both late eaters, however, with increased age (and so as increased health-related problems/concern) some of them modified their habits, such as quitting smoking, replacing carbohydrate food with other energy sources (so that they became low carbohydrate eaters with hypertension) which lead to the phenomenon of lower odds of hypertension in moderate carbohydrate eaters.
-Although these hypotheses cannot be determined by the cross-sectional data from NDNS RP, if they were true, the energy sources they used to replace carbohydrate in their diet were apparently not very wisely chosen.
+Therefore, considering that moderate carbohydrate eaters were younger than low carbohydrate eaters (although age was adjusted in the full models), it is probable that reverse causality exists here (also due to the nature of cross-sectional study).
+That is, they were potentially both late eaters, however, with increased age (and so with increased health-related problems/concerns) some of them modified their habits, perhaps quitting smoking, replacing carbohydrate food with other energy sources (so that they became low carbohydrate eaters with hypertension) leading to the phenomenon of lower odds of hypertension in moderate carbohydrate eaters.
+Although these hypotheses cannot be determined by the cross-sectional data from NDNS RP, if they are true, the energy sources individuals used to replace carbohydrate in their diet were apparently not wisely chosen.
 
-Among women, whether living with a partner became an interaction factor for the associations between carbohydrate eating patterns and BMI and abdominal obesity (WC).
+Among women, living with a partner was an interaction factor for the associations between carbohydrate eating patterns and BMI and abdominal obesity (WC).
 Directions of the associations were opposite to each other depending on whether women were living with a partner or not.
 This interaction effect was more obvious when looking at abdominal obesity measurement.
-High carbohydrate eaters had lower BMI and WC in those lived with their partners, while moderate carbohydrate eaters had higher WC in those who lived alone after adjustment of age, education level, smoking status, total energy intake, and alcohol consumption.
-High carbohydrate eaters who were characterised with high and early in the daily energy consumption and low fat and alcohol intake may reflect a healthier diet and lifestyle, but this might be different between women who lived alone and those who lived with their partners.
-It was often assumed that live alone may associate with a lower diversity of food intake, and a higher likelihood of having an unhealthy dietary choice \parencite{hanna2015relationship}.
+High carbohydrate eaters who lived with partners had lower BMI and WC than low carbohydrate eaters, while moderate carbohydrate eaters who lived alone had higher WC than their low carbohydrate eating counterparts, after adjustment of age, education level, smoking status, total energy intake, and alcohol consumption.
+High carbohydrate eaters who were characterised with high and early daily energy consumption and low fat and alcohol intake may reflect a healthier diet and lifestyle, but this might be different between women who lived alone and those who lived with their partners.
+It was often assumed that living alone may be associated with a lower diversity of food intake and a higher likelihood of having an unhealthy dietary choice \parencite{hanna2015relationship}.
 Therefore, there may be differences in the actual contents consumed in their high carbohydrates, or there may be other social, psychological or lifestyle-related factors related with living alone which were not measured or did not include in the models.
-Thus, the inverse association between high carbohydrate eating pattern and BMI or abdominal obesity were only observed among women who lived with partners, further investigation of this hypothesis is needed.
-Whereas the reason why moderate carbohydrate eaters' WC was larger than low carbohydrate eaters only among women who lived alone is unknown, given that the evidence of this association was weak and borderline significant, whether it was just a false positive finding should also be explored in other studies.
+Since the inverse association between high carbohydrate eating pattern and BMI or abdominal obesity were only observed among women who lived with partners, further investigation of this hypothesis is needed.
+In addition, the reason why moderate carbohydrate eaters' WC was larger than low carbohydrate eaters only among women who lived alone is unknown.
+Given that the evidence of this association was weak and borderline significant, whether it was just a false positive finding should also be explored in other studies.
 
@@
 
-There are several limitations in the current project that merit consideration.
+Several limitations in the current project merit consideration.
 
-Firstly, we ignored the order of observation days in the MLCA models.
+First, we ignored the order of observation days in the MLCA models.
 The food consumption diaries were accomplished by participants for at least 3 out of 4 consecutive days.
 In the multilevel analyses, these 3 or 4 days' observations were treated as if they were exchangeable in the models.
-Since one's diet might change according to the season, day of the week (weekdays or weekends), or sometimes depends on what they had consumed the day before, exchangeability of their diaries is a strong assumption and cannot be overcome by the MLCA models adopted here.
-Other statistical techniques, which could take the order or the longitudinal nature of the data into account, such as repeated measures latent class analysis (RMLCA), latent transition analysis (LTA) \parencite{collins2010latent}, or latent class growth analysis (LCGA) \parencite{davidian2008growth,jung2008introduction,andruff2009latent} are not applicable for the NDNS RP dataset.
-For the purpose of maintaining the response rate, flexibility was allowed for the NDNS RP participants in their choice of which day to begin their diary.
-But the above mentioned alternative models require that the 3 or 4 repeated measurements of food diaries be recorded at the same time points longitudinally.
+Since one's diet might change according to the season, day of the week (weekdays or weekends), or sometimes depend on what one had consumed the day before, exchangeability of daily diaries is a strong assumption and cannot be overcome by the MLCA models adopted here.
+Other statistical Other statistical techniques which could take the order or the longitudinal nature of the data into account, such as repeated measures latent class analysis (RMLCA), latent transition analysis (LTA)\parencite{collins2010latent}, or latent class growth analysis (LCGA) \parencite{davidian2008growth,jung2008introduction,andruff2009latent} are not applicable for the NDNS RP dataset.
+The NDNS RP participants were allowed to choose which days to begin their food diaries, but the alternative models above would require that the 3 or 4 repeated measurements of food diaries be recorded at the same time points longitudinally.
 Specifically, LCGA models (also called growth mixture model) will also need to model the change of the odds of the probability over time as a function (quadratic, or cubic) which is apparently not the objective in the current project.
 
-Secondly, the classification of individuals to latent carbohydrate eating classes was defined by maximum posterior probability assignment rule.
+Second, the classification of individuals to latent carbohydrate eating classes was defined by maximum posterior probability assignment rule.
 This approach assigns individuals to the class for which they have the highest posterior probability of membership \parencite{nagin2005group}.
@@
 Moreover, this simulation study also found that an inclusive LCA (i.e.
-LCA with covariates) would probably perform better than non-inclusive LCA, and has the potential to reduce bias of class assignment.
-However, whether this advantage can be extended to MLCA in the current project is unknown, and also due to the reason that the associations between the latent classes and distal outcomes (hypertension, and BMI) in our analyses are mostly still under exploration, therefore, the model for LCA with covariates can never be well-known before our analyses.
+LCA with covariates) would probably perform better than non-inclusive LCA and has the potential to reduce bias of class assignment.
+However, whether this advantage can be extended to MLCA in the current project is unknown.
+Also, because the associations between the latent classes and distal outcomes (hypertension, and obesity) are still under exploration, appropriate covariates for an inclusive LCA model may not be known or yet knowable.
 Thus, as a first step, given the complexity of the NDNS RP dataset itself, we chose to fit the MLCA models without any covariate in either day level or individual level models.
@@
 
-Thirdly, information regarding the detailed occupations of the participants was not available and because of which we could not exclude those who had a shift work involving night work.
-But considering that completing a 4-consecutive-day food diary would be a large burden for the participants, those had a shift work involving night work might possibly perform with relatively lower compliance and could not complete their diary for at least 3 days.
-But this hypothesis cannot be verified in the NDNS RP dataset.
-If people working with shift work were included in the NDNS RP sample, the classification in both levels, as well as their associations with either hypertension or BMI would be biased.
-Furthermore, under-reporting due to the burden of writing down everything they eat at each occasion is also a concern in the food diaries collected.
-To evaluate the influence of under-reporting in the NDNS RP sample, the study team of NDNS RP conducted doubly labelled water (DLW) sub-study within the survey.
+Third, detailed information on the occupations of the participants was not available and thus we could not account for those who had shift or night work.
+But considering that completing a 4-consecutive-day food diary may be a large burden for all participants, those with shift or night work might be less able to comply and complete their diary for at least 3 days.
+Unfortunately, this hypothesis cannot be verified in the NDNS RP dataset.
+If people on shifts were included in the NDNS RP sample, the classification in both levels, as well as their associations with either hypertension or BMI would be biased.
+Furthermore, under-reporting due to the burden of writing down everything eaten at each occasion is also a concern in the food diaries collected.
+To evaluate the influence of under-reporting in the NDNS RP sample, the study team of NDNS RP conducted a doubly labelled water (DLW) sub-study within the survey.
 The details of this sub-study can be accessed from the Appendix X of the Official Reports provided by Public Health England \parencite{bates2014national,roberts2018national,NDNSofficial}.
@@
 Results of the sub-study showed reasonable agreement between EI and TEE (overall ratio: 0.73).
-Reasons such as misreporting of actual consumption; under-reported or modified usual intake due to the burden of the survey/DLW sub-study are potential factors may contribute to under-reporting of their EI.
+Reasons such as misreporting of actual consumption, under-reporting or modified usual intake due to the burden of the survey/DLW sub-study may contribute to under-reporting of their EI.
 We cannot extrapolate the estimated under-reporting to the whole sample since other individuals' diet might be affected by under-reporting differentially.
 
-Lastly, it should be noted that findings from data-driven, exploratory methods may not be
-generalizable to populations in other countries.
-Since the carbohydrate eating patterns in both day level and individual level probably only represent the socio-cultural and lifestyle characteristics of the adult population in the UK.
-Further researches are warranted to explore and better understand the eating patterns in other populations.
-Besides, the cross-sectional study design also refrained us from deducing any causal effect between the carbohydrate eating patterns and hypertension, BMI or abdominal obesity.
+Last, it should be noted that findings from data-driven, exploratory methods may not be
+generalizable to populations in other countries, since the carbohydrate eating patterns in both day level and individual level probably only represent the socio-cultural and lifestyle characteristics of the adult population in the UK.
+Further research is warranted to explore and better understand the eating patterns in other populations.
+In particular, the cross-sectional study design also prevented us from deducing any causal effect between the carbohydrate eating patterns and hypertension, BMI or abdominal obesity.
 
 Strengths of this study include the large, nationally representative sample of men and women in the UK.
-We applied a novel, objective approach using MLCA to examine the carbohydrate eating patterns while applying standardised criteria to determine the numbers of latent classes.
+We applied a novel, objective approach using MLCA to examine the carbohydrate eating patterns while applying standardised criteria to determine the number of latent classes.
 The process of finding the classifications through model-based, data-driven procedure minimises reliance on researchers' preconceived notions of eating patterns.
 Eating patterns were determined from 4 consecutive days of well-designed, fully-examined food diaries.
-MLCA correctly accounted for the multilevel structure of the data which means that the 4-day diet diaries were nested within the participants.
+MLCA correctly accounted for the multilevel structure of the data, where the 4-day diet diaries were nested within the participants.
 Our findings also captured the day-to-day variation of following different carbohydrate eating patterns within individuals.
@@
 We have successfully defined carbohydrate eating patterns in the general population in the UK adults using the NDNS RP database in both observation day level and individual level.
-Low carbohydrate eaters turned out to have more energy that contributed by both fat and alcohol.
-Moderate carbohydrate eaters consumed the lowest total energy, while they had the tendency of having meals later in time-of-day.
-High carbohydrate eaters consumed most of their carbohydrate as well as energy earlier in time-of-day.
-These dietary patterns specifically for carbohydrate intake were found to be differed by timing, quantity, and contributions to energy consumption.
-Compared with low carbohydrate eaters, men had moderate carbohydrate eating pattern may associate with a lower prevalence of hypertension, women in this latent class who lived alone may associate with a larger waist circumference.
-Among women who lived with partners, high carbohydrate eating pattern was associated with both lower BMI and smaller waist circumferences.
-Longitudinally designed studies are needed in finding whether the eating patterns themselves are changing over time and in investigating how such circadian eating patterns may relate to the change of blood pressure, obesity, and other health outcomes (incidence of cancer, cardiovascular diseases, or perhaps mortality).
+Low carbohydrate eaters tended to consume more energy through fat and alcohol than other groups.
+Moderate carbohydrate eaters consumed the lowest total energy, and tended to have later in the day.
+High carbohydrate eaters consumed most of their carbohydrate as well as energy earlier in the day.
+These dietary patterns specifically for carbohydrate intake were found to differ by timing, quantity, and contributions to energy consumption.
+Compared with low carbohydrate eaters, men with a moderate carbohydrate eating pattern may associate with a lower prevalence of hypertension; women in this latent class who lived alone may associate with a larger waist circumference.
+Among women who lived with partners, a high carbohydrate eating pattern was associated with both lower BMI and smaller waist circumferences.
+Longitudinally designed studies are needed to investigate whether the eating patterns themselves are changing over time and to study how such circadian eating patterns may relate to the change of blood pressure, obesity, and other health outcomes (incidence of cancer, cardiovascular diseases, or mortality).

### 2018-08-28 paper/main.tex
language checked by Hunter

@@
 
-I would like to thank all of the teachers, lecturers, staffs, and fellow course mates in the Department of Medical Statistics for providing their wonderful teaching techniques, sharing their excellent ideas that made this year such fruitful and enjoyable.\\
+I would like to thank all of the teachers, lecturers, staffs, and fellow course mates in the Department of Medical Statistics for providing their wonderful teaching techniques, and for sharing their excellent ideas that made this year such fruitful and enjoyable.\\
 
@@
 Recent evidence suggested that there are 3 types of eaters (grazers, early eaters, and late eaters) according to the timing of energy consumption.
-This project aimed at finding both timing and quantity eating patterns specifically for carbohydrate (carb) intake, and exploring their potential associations with hypertension and obesity.
+This project aims at finding both timing and quantity eating patterns specifically for carbohydrate (carb) intake, and exploring their potential associations with hypertension and obesity.
 
@@
 \textbf{Results:}
-Three carb eating day patterns (low/high percentage, and regular meal days) were found in 24483 observation days, based on which, three types of carb eaters: low (28.1\%), moderate (28.8\%), and high (43.1\%) carb eaters emerged.
+Three carb eating day patterns (low/high percentage, and regular meal days) were found in 24483 observation days, based on which three types of carb eaters were defined: low (28.1\%), moderate (28.8\%), and high (43.1\%) carb eaters.
 On average, low-carb eaters consumed the highest amount of total energy intake (7985.8 kJ), and they had higher percentages of energy contributed by fat and alcohol, especially after 8 pm.

### 2018-08-31 paper/Chapters/Chapter2.tex
paper modified accordingly

@@
 Since we planned to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical, the responses were then dichotomised according to these percentages of the energy intake at a cut-off value of 50\%, i.e.
-if within a time slot where there any energy intake occurred, carbohydrate consumption was categorised by whether its energy contribution was lower or higher/equal to 50\% of total energy intake within that time slot.
+if within a time slot where any energy intake occurred, carbohydrate consumption was categorised by whether its energy contribution was lower or higher/equal to 50\% of total energy intake within that time slot.
 Consequently, for each day of the recording, there were 7 data points generated by the diary.
@@
 Another two sets of weights were generated to correct for differential non-response (either due to refusal or inability) to 1) nurse visit and 2) giving a blood sample.
-Response rates to the nurse visit among those completed a dietary diary was approximately 75\%, to the blood sample in adults were 51\%, 57\%, and 50\% for years 1 to 4, 5 to 6, and 7 to 8, respectively.
+Response rates to the nurse visit among those who completed a dietary diary was approximately 75\%, to the blood sample in adults were 51\%, 57\%, and 50\% for years 1 to 4, 5 to 6, and 7 to 8, respectively.
 In creating the nurse/blood sample weight, a logistic regression model was used by the NDNS RP study team to model the relationship between response to nurse visit/giving a blood sample and a set of predictor variables (socio-demographic, participant and catering/household unit characteristics).
-The model generated a predicted probability for each participant, which is the probability would agree to a nurse visit/provide a blood sample, given the characteristics of the individual and the household unit.
+The model generated a predicted probability for each participant, which is the probability of agreeing to a nurse visit/providing a blood sample, given the characteristics of the individual and the household unit.
 Participants with characteristics associated with non-response were under-represented in the sample and therefore receive a low predicted probability.
@@
 Serum samples were obtained by centrifugation of the coagulated blood sample.
-Serum total, High-Density Lipoprotein (HDL) and Low-Density Lipoprotein (LDL) cholesterol, triglycerides (TG), fasting blood glucose, haemoglobin A1C were measured.
-A1C value of 6.5\% was used as the cut off point for diagnosing diabetes.
+Serum total, High-Density Lipoprotein (HDL) and Low-Density Lipoprotein (LDL) cholesterol, triglycerides (TG), fasting blood glucose, haemoglobin HbHbA1C were measured.
+HbA1C value of 6.5\% was used as the cut off point for diagnosing diabetes.
 
@@
 $u_{0j} \sim N(0, \sigma_{u_0}^2)$), the magnitude of the $u_{0j}$ variance ($\sigma_{u_0}^2$) indicates the influence of the individuals (level 2);
-	\item $x_{ij}, w_j$ is the predictors for day-level (weekdays or weekends) and individual-level, such as age, and sex.
+	\item $x_{ij}, w_j$ are the predictors for respectively day-level (weekdays or weekends) and individual-level, such as age, and sex.
 \end{itemize}
@@
 Similar to the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each time slots, throughout three/four consecutive days of their survey period).
-Considering the latent class indicators are indicator variables ($U_{ijk}$), the MLCA model can be written as follows:\vspace{-1cm}
+Considering the latent class indicators as indicator variables ($U_{ijk}$), the MLCA model can be written as follows:\vspace{-1cm}
 
@@
 %\begin{aligned}
-P(U_{ij1} = s_1, U_{ij2} = s_2, \cdots, U_{ijk} = s_{k}) = \sum_{t=1}^{T}P(G_{ij}=t)\prod_{k=1}^{K}P(U_{ijk} = s_k | G_{ij} = t)
+P(U_{ij1} = s_1, U_{ij2} = s_2, \cdots, U_{ijk} = s_{k}) = \sum_{t=1}^{T}P(G_{ij}=t)\prod_{k=1}^{K}P(\mathbf{U_{ijk} = s_k} | G_{ij} = t)
 %\end{aligned}
@@
 %	\item A specific latent class is referred to as $t$, and the total number of level 1 latent classes is denoted by $T$;
-	\item $P(U_{ijk} = s_k|C_{ij} = t)$ is the probability of a specific response pattern, conditional on membership in latent class $t$.
+	\item $P(\mathbf{U_{ijk} = s_k}|C_{ij} = t)$ is the probability of a specific response pattern, conditional on membership in latent class $t$.
 \end{itemize}
@@
 
-Person-level point estimates and 95\% confidence intervals (CIs) were determined by applying individual, nurse visiting, and blood sample weights accordingly which account for the probability of participant selection and the clustered survey design.
+Person-level point estimates and 95\% confidence intervals (CIs) were determined by applying individual, nurse visiting, and blood sample weights and the clustered survey design.
 Descriptive statistics for sample characteristics were presented as weighted means (95\% CI) or weighted percentages (95\%CI).
-After examining the distribution of the data, the following variables were log-transformed to improve normality: fasting blood glucose, A1C, TC, LDL, HDL, TG, and average physical activity duration per day.
+After examining the distribution of the data, the following variables were log-transformed to improve normality: fasting blood glucose, HbA1C, TC, LDL, HDL, TG, and average physical activity duration per day.
 Weighted geometric means (95\% CI) were used for all log-transformed variables.
 
-To see whether there is any temporal pattern for food intake eating could also be defined at the individual-level, weighted estimates of nutrients consumption across the 7-time slots of the day were calculated for each individual-level latent class.
+To see whether there is any temporal pattern for food intake at the individual-level, weighted estimates of nutrients consumption across the 7-time slots of the day were calculated for each individual-level latent class.
 Contributions (\%) of the average energy intake within time slots were evaluated by determining the percentages of energy coming from carbohydrate, fat, protein, and alcohol intake.
 
-For continuous variables, the \textit{F} test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across $>$ 2 classes when applicable.
+For continuous variables, the \textit{F} test was used to determine differences between latent classes with Bonferroni correction to account for multiple comparisons across $>$ 2 classes when applicable.
 For categorical variables, differences between latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.\vspace{-0.5cm}
@@
 	\item A preliminary model that includes all of the variables suggested to be confounders in the previous step was established. 
-	\item The remaining variables were added to the preliminary model one by one to see if any of them may be a confounder in the condition of the presence of the other covariates. 
-	\item For logistic regression models (hypertension) under the survey data, goodness-of-fit was assessed using the adapted \code{svylogitgof} command in Stata \parencite{archer2006goodness}.
+	\item The remaining variables were added to the preliminary model one by one to see if any of them may be a confounder in the presence of the other covariates. 
+	\item For logistic regression models (hypertension) under the survey data, goodness-of-fit was assessed using \textit{F}-adjusted mean residual test \parencite{archer2001goodness,archer2007goodness} which is implemented in Stata using command \code{svylogitgof} \parencite{archer2006goodness}.
 Other diagnostics for regular logistic regression models, such as estimating the pseudo-R\textsuperscript{2},  AIC or BIC, checking the standardized Pearson residuals, or covariate pattern residuals are currently not available for weighted survey data.
-	\item For linear regression models (WC, BMI), the assumption of independent observations is violated as soon as we weight the sample.
-General checking such as QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance) are not available either.
+	\item For linear regression models (WC, BMI), the assumption of independent observations is violated because of the clustered structure of the data.
+Therefore, inference from such models is based on design rather than the model.
+	General checking such as QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance) are unneeded (also not available).
 Outliers, leverage, and Cook's distance cannot be checked either, however, participants with extreme weightings (if any) were checked by removing them and refitting the models as a sensitivity analysis.
-	\item Since under survey designed data, the sampling-weighted least squares are not maximum likelihood, it would not be possible to compare models using likelihood ratio test.
+	\item Since under complex survey designed data, the sampling-weighted least squares are not maximum likelihood, it would not be possible to compare models using likelihood ratio test.
 Instead, adjusted Wald tests with $p < 0.05$ were used as criteria for variable inclusion in the final model.
-Another Stata command \code{linktest} was also used to  decide whether quadratic and cubic terms of continuous variables were necessary in improving fitting of the model \parencite{pregibon1980goodness}.
+Another Stata command \code{linktest} was used to decide whether quadratic and cubic terms of continuous variables were necessary in improving fitting of the model \parencite{pregibon1980goodness}.
 \end{enumerate}

### 2018-08-31 paper/Chapters/Chapter3.tex
paper modified accordingly

@@
 \textbf{Table \ref{tab:mixmodels}} shows the latent class solutions for one to five classes (see rows under the Fixed effects model section).
-The BIC declines with increases in the number of day level classes increases.
+The BIC declines as the number of day level classes increases.
 However, the improvement of BIC dropped to less than 1000 from 3 class to 4 class solutions (658.9) and from 4 class to 5 class solutions (361.7).
@@
 On the other hand, the consumption of protein (73.29 g), total fat (67.24 g), and alcohol (13.80 g) were the highest in the regular meals days.
-Moreover, in the high percentage carbohydrate days, participants turned to consume the highest amount of fruit (107.40 g).
+Moreover, in the high percentage carbohydrate days, participants turned out to consume the highest amount of fruit (107.40 g).
 There was no evidence of any difference in the consumption of yellow, red, or green vegetables across the three types of days (\textit{p} = 0.681).\vspace{-0.6cm}
@@
 Moderate carbohydrate eaters have comparable proportions (42.0\% vs.
-40.0\%) of having high carbohydrate days and regular meals days; 18.0\% of their dietary diary was found to be low carbohydrate days.
+40.0\%) of high carbohydrate days and regular meals days; 18.0\% of their dietary diary was found to be low carbohydrate days.
 
@@
 Sources of energy for each type of carbohydrate eaters by the 7-time slots were also different.
-Low carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-A)} never had carbohydrate contributed more than 50\% of their total energy throughout the day.
+Low carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-A)} never had carbohydrate contributing more than 50\% of their total energy throughout the day.
 Energy from fat was the highest for low carbohydrate eaters most of the time during the day (except for the time slot between 10 pm to 6 am next morning).
@@
 They consumed more sugar and starch during 9-12 noon, 2-5 pm, 8-10 pm, and 10-6 am.
-Low carbohydrate eaters turned to have similar temporal pattern of consuming carbohydrates with the high carbohydrate eaters, but the absolute amount of fibre, sugar, free sugar, and starch consumed were usually lower than that in the high carbohydrate eaters except for time slots of 2-5 pm, and 10-6 am.
+Low carbohydrate eaters turned to have similar temporal pattern of consuming carbohydrates as the high carbohydrate eaters, but the absolute amount of fibre, sugar, free sugar, and starch consumed were usually lower than that in the high carbohydrate eaters except for time slots of 2-5 pm, and 10-6 am.
 Strong evidence (\textit{p} < 0.001) suggested that the
@@
 
-mean of total fibre consumption for low, moderate, and high carbohydrate eaters were different: 13.7g (95\%CI: 13.4, 14.0), 12.5g (95\%CI: 12.1, 12.9), and 14.7g (95\%CI: 14.4, 14.9) with all 95\% CI being exclusive to each other.
+mean of total fibre consumption for low, moderate, and high carbohydrate eaters were different: 13.7g (95\%CI: 13.4, 14.0), 12.5g (95\%CI: 12.1, 12.9), and 14.7g (95\%CI: 14.4, 14.9) with all 95\% CI being non-overlapping.
 It is also noteworthy that low carbohydrate eaters consumed the highest average amount of protein (79.9 g, 17.2\% of total energy), fat (74.7g, 35.4\% of total energy), and alcohol (20.8 g, 6.8\% of total energy) as we have described for \textbf{Figure \ref{fig:energysourcesCB}}.
@@
 The distribution of the carbohydrate eater types appears to be changing with the year of survey.
-Low carbohydrate eaters represented 32.5\% of the population in the first year of the survey but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year.
+Low carbohydrate eaters represented 32.5\% of the population in the first year of the survey but later dropped to lower than 30\% (minimum in the third year at 22.6\%) until the most recent year.
 The proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015).
@@
 
-From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetic (diagnosed by A1C > 6.5\%), while the percentages of diabetes in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011), respectively.
-Although there was some evidence (\textit{p} = 0.027) that fasting blood glucose level may be slightly higher in non-diabetic low carbohydrate eaters, the geometric mean for A1C was probably lower in moderate carbohydrate eaters (5.43, 95\%CI: 5.39, 5.47).
+From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetic (diagnosed by HbA1C > 6.5\%), while the percentages of diabetes in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011), respectively.
+Although there was some evidence (\textit{p} = 0.027) that fasting blood glucose level may be slightly higher in non-diabetic low carbohydrate eaters, the geometric mean for HbA1C was probably lower (\textit{p} = 0.010) in moderate carbohydrate eaters (5.43, 95\%CI: 5.39, 5.47).
 Total cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.
@@
 		Glucose (mmol/l) & 5.17 (5.12, 5.23) & 5.05 (4.99, 5.13) & 5.10 (5.05, 5.15) & 0.027\\
-		A1C (\%) & 5.47 (5.44, 5.51) & 5.43 (5.39, 5.47) & 5.50 (5.48, 5.53) & 0.010\\
+		HbA1C (\%) & 5.47 (5.44, 5.51) & 5.43 (5.39, 5.47) & 5.50 (5.48, 5.53) & 0.010\\
 		DM \textsuperscript{\S} & 6.9 (5.0, 9.3) & 3.5 (2.3, 5.3) & 4.1 (2.9, 5.6) & 0.011\\
@@
 		\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national diet and nutrition survey rolling programme;}}\\
-		\multicolumn{5}{l}{{\scriptsize BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus; TC, total cholesterol, }}\\
+		\multicolumn{5}{l}{{\scriptsize BMI body mass index; WC, waist circumference; HbA1C, haemoglobin HbA1C; DM, diabetes mellitus; TC, total cholesterol, }}\\
 		\multicolumn{5}{l}{{\scriptsize HDL, high density lipoproteins; LDL, low density lipoproteins; TG, triglycerides.}} \\
-		\multicolumn{5}{l}{{\scriptsize Glucose, A1C, TC, HDL, LDL, TG, and physical activity were expressed in geometric means (95\% CI) because }} \\
+		\multicolumn{5}{l}{{\scriptsize Glucose, HbA1C, TC, HDL, LDL, TG, and physical activity were expressed in geometric means (95\% CI) because }} \\
 		\multicolumn{5}{l}{ the data were positively skewed.} \\
-		\multicolumn{5}{l}{{\scriptsize Variables from the blood tests (glucose and A1C) were weighted by blood sample weights, the other variables were}}\\ 
-		\multicolumn{5}{l}{{\scriptsize  weighted by nurse visiting weights. Glucose and A1C levels are estimated in subgroups of people without diabetes.}}\\
+		\multicolumn{5}{l}{{\scriptsize Variables from the blood tests (glucose and HbA1C) were weighted by blood sample weights, the other variables were}}\\ 
+		\multicolumn{5}{l}{{\scriptsize  weighted by nurse visiting weights. Glucose and HbA1C levels are estimated in subgroups of people without diabetes.}}\\
 		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes with}\\ 
@@
 %		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake.}}\\  
-		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\S} DM was defined by A1C $>$ 6.5\%.}}\\
+		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\S} DM was defined by HbA1C $>$ 6.5\%.}}\\
 	\end{tabular}
@@
 In the crude models, moderate carbohydrate eaters had statistically significant lower odds of having hypertension than low carbohydrate eaters in both men and women irrespective to diabetes status.
-Among men, after adjustment for selected confounders, which includes: age, live with partner or not, education level, BMI, smoking status, and total energy intake, the odds ratio (OR) comparing moderate with low carbohydrate eaters was 0.68 (95\% CI: 0.43, 1.07) and remained borderline significant (\textit{p} = 0.093).
+Among men, after adjustment for selected confounders, which includes: age, live with partner or not, education level, BMI, smoking status, and total energy intake, the odds of having hypertension were 32\% lower (OR: 0.68, 95\% CI: 0.43, 1.07) in moderate carbohydrate eaters compared with low carbohydrate eaters, evidence for the OR different from 1 was borderline significant (\textit{p} = 0.093).
 95\% CI of the adjusted OR became narrower (OR: 0.64, 95\% CI: 0.41, 1.01, \textit{p} = 0.054) when BMI was replaced with WC in model 2.
@@
 		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}}\\
-		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\S}  DM was defined by A1C $>$ 6.5\%.}}
+		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\S}  DM was defined by HbA1C $>$ 6.5\%.}}
 	\end{tabular}
@@
 		\multicolumn{6}{l}{{\scriptsize  circumference; NDNS RP, national diet and nutrition survey rolling programme.}}\\
-		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other}}\\
+		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by HbA1C > 6.5\%. BMI was replaced with WC in Model 2s, other}}\\
 		\multicolumn{6}{l}{{\scriptsize covariates remained the same with the corresponding Model 1s.}}\\
@@
 level (\textit{p} = 0.022 for men, < 0.001 for women), and average household income (\textit{p} = 0.011 for men, < 0.001 for women) decreased with increases in BMI.
-Living with a partner or not was strongly positively associated with obesity for men but not for women.
+Living with a partner was strongly positively associated with obesity for men but not for women.
 Men with obesity were also found to have the lowest proportion of never being a smoker (47.9\%) and the highest proportion of being an ex-smoker (32.9\%).
@@
 		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; NDNS RP, national diet and nutrition survey rolling programme.}}\\
-		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%.}}\\
+		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by HbA1C > 6.5\%.}}\\
 		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from linear regression models.}}\\
@@
 
-Results of the multivariable linear regression analyses showed inverse associations between latent classes of carbohydrate eating patterns and BMI among men \textbf{(Table \ref{tab:tab2BMI})}.
+Results of the multivariable linear regression analyses showed smaller BMI for moderate or high carbohydrate eaters compared with low carbohydrate eaters among men \textbf{(Table \ref{tab:tab2BMI})}.
 However, the 95\%CI of the regression coefficients were all wide and included the null value 0, indicating no statistically supported evidence for the inverse association.
@@
 After excluding diabetic women, BMI was still 1.62 kg/m\textsuperscript{2} (95\%CI: 0.58, 2.65, \textit{p} = 0.002) smaller in high carbohydrate eaters versus low carbohydrate eaters on average.
-On the contrary, latent classes of carbohydrate eating patterns were positively associated with BMI in women who were living by themselves, although there was no evidence that regression coefficients different from 0 (\textit{p} > 0.05).
+On the contrary, latent classes of carbohydrate eating patterns were positively associated with BMI in women who were living by themselves, although there was no evidence that regression coefficients differed from 0 (\textit{p} > 0.05).
 
 Similarly, when looking at the association between carbohydrate eating pattern and abdominal obesity (WC), men who were classified as moderate carbohydrate eaters were found to have about 3 cm (95\%CI: 0.52, 5.49 cm, \textit{p} = 0.018) smaller WC compared to low carbohydrate eaters in the crude model \textbf{(Table \ref{tab:tab2WC})}.
-However, after adjustment of age, living with partner or not, average household income, education level, hypertension, smoking status, total energy intake, and alcohol consumption, the association attenuated to no difference.
+However, after adjustment for age, living with partner or not, average household income, education level, hypertension, smoking status, total energy intake, and alcohol consumption, the association attenuated to no difference.
 The interaction effect of living with a partner or not on the association between carbohydrate eating patterns and WC was again found in women in total (\textit{p} for interaction = 0.009) and without diabetes (\textit{p} for interaction = 0.012).
@@
 		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: WC, waist circumference; NDNS RP, national diet and nutrition survey rolling programme.}}\\
-		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. }}\\
+		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by HbA1C > 6.5\%. }}\\
 		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from Wald tests in linear regression models.}}\\
@@
 %			\multicolumn{12}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national diet and nutrition survey rolling programme.}}\\
-%			\multicolumn{12}{l}{{\scriptsize DM was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the same with the corresponding Model 1s.}}\\
+%			\multicolumn{12}{l}{{\scriptsize DM was defined by HbA1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the same with the corresponding Model 1s.}}\\
 %			\multicolumn{12}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from either linear regression models or logistic regression models.}}\\

### 2018-08-31 paper/Chapters/Chapter4.tex
paper modified accordingly

@@
 
-Using multilevel LCA as a novel technique, and the NDNS RP dietary database, this project examined carbohydrate eating temporal patterns firstly in the day level, based on which, individual level carbohydrate eating patterns were also defined subsequently.
+Using multilevel LCA as a novel technique, and data from the NDNS RP, this project examined carbohydrate temporal eating patterns firstly at the day level, based on which, individual level carbohydrate eating patterns were also defined subsequently.
 
@@
 From these day level classifications and their features, one might anticipate that individuals followed much of class 3) days, the regular meals day, might be eating a healthier diet because of regular eating habits.
-We might also believe that those who followed either high or low carbohydrate percentage days would consume higher total energy than those who followed mostly regular meals days.
+We might also speculate that those who followed either high or low carbohydrate percentage days would consume higher total energy than those who followed mostly regular meals days.
 
@@
 For the first time, as far as we know, the day-to-day food intake pattern variation within individuals was successfully captured by MLCA models.
-Results from the MLCA models showed that from the perspective of carbohydrate consumption, people were indeed changing their diet from day to day even within a short-term period of survey.
+Results from the MLCA models showed that from the perspective of carbohydrate consumption, people were indeed changing their diet from day to day even over the captured four days.
 The MLCA models allowed the probability of following a certain type of carbohydrate eating day to vary across individuals.
 This properly accounted for the fact that for some people, their probability of following a type of food eating pattern during the survey could be higher/lower than that in the others.
-This finding also suggested that assuming a person will always follow a certain type of food intake pattern is not appropriate.
+This finding also suggested that assuming a person will always follow a certain type of eating pattern is not appropriate.
 
 Surprisingly, low carbohydrate eaters whose dietary recordings suggested that they were mostly following a regular temporal meals pattern turned out to be consuming the highest amount of total energy among the three types of carbohydrate eaters.
-Detailed profiling of energy composition according to the time slots revealed that low carbohydrate eaters actually had a higher proportion of energy contributed by both alcohol and fat.
+Detailed profiling of energy composition according to the time slots revealed that low carbohydrate eaters actually had a higher proportion of energy contributed by both alcohol and fat across the 7 time slots.
 A high percentage of fat consumption was shown in all 7-time slots, energy coming from alcohol exceeded more than one-fifth of the total energy after 8 pm.
@@
 In the meantime, we also found that participants consuming low carbohydrate food had a higher prevalence of diabetes, hypertension, and obesity.
-These health issues might lead them (or advice were given by their physicians) to replace carbohydrates in their diet to other energy sources such as fat, protein, or even alcohol.
+These health issues might lead them to replace carbohydrates in their diet with other energy sources such as fat, protein, or even alcohol.
 Therefore, there is a possibility that they chose to follow low carbohydrate diets for health purposes, but many of them were replacing carbohydrates with higher energy condensed food or even alcohol at night which might indeed be a public health concern.
@@
 Next, when looking into the details of the timing and composition of the energy intake among the moderate carbohydrate eaters, we realised that although these individuals did not consume as much alcohol as low carbohydrate eaters did at night, they consumed the highest amount of energy, especially during the time period as late as after 10 pm.
-People fell into moderate carbohydrate eaters group seemed to have the tendency of having their food or meals later than high carbohydrate eaters.
+People who fell into moderate carbohydrate eaters group seemed to have the tendency of having their food or meals later than high carbohydrate eaters.
 They consumed the highest amount of carbohydrates and also total energy among three types of carbohydrate eaters during the following time slots: 9-12 noon, 2-5 pm, 8-10 pm, and 10pm-6am.
@@
 High carbohydrate eaters were also found to be the ones that consumed the least amount of energy after 8 pm.
-Therefore, contrary to what was anticipated at the beginning, people who followed high percentage carbohydrate days for most of their time were actually eating a healthier diet compared with the other two eating patterns.
+Therefore, contrary to what was anticipated at the beginning, people who followed high percentage carbohydrate days for most of their time were potentially eating a healthier diet compared with the other two eating patterns.
 
-Our analyses looking for different temporal carbohydrate also highlighted the complexity of eating pattern behaviours in the population and the utility of exploratory, data-driven methods to objectively identify eating patterns that reflect both timing and quantities of food intake, which may not have been detected so far in the literature.
+Our analyses looking for different temporal carbohydrate eating patterns also highlighted the complexity of eating behaviours in the population and the utility of exploratory, data-driven methods to objectively identify eating patterns that reflect both timing and quantities of food intake, which may not have been detected so far in the literature.
 
@@
 
-Men who were classified as moderate carbohydrate eaters were estimated to have lower odds of having hypertension, after adjustment of age, live with a partner or not, educational level, BMI, smoking status and total energy intake.
-As discussed above, moderate carbohydrate eaters tended to have meals (or energy consumption) later in time compared with high carbohydrate eaters.
-But, it is noteworthy that low carbohydrate eaters also consumed a large amount of energy (from both fat and alcohol) at night.
+Men who were classified as moderate carbohydrate eaters were estimated to have lower odds of having hypertension compared with low carbohydrate eaters, after adjustment for age, relationship status (living with a partner or not), educational level, BMI, smoking status and total energy intake.
+As discussed above, moderate carbohydrate eaters tended to have meals (or energy intake) later in time compared with high carbohydrate eaters.
+But, it is noteworthy that low carbohydrate eaters also obtained a large amount of energy from both fat and alcohol at night.
 Therefore, considering that moderate carbohydrate eaters were younger than low carbohydrate eaters (although age was adjusted in the full models), it is probable that reverse causality exists here (also due to the nature of cross-sectional study).
-That is, they were potentially both late eaters, however, with increased age (and so with increased health-related problems/concerns) some of them modified their habits, perhaps quitting smoking, replacing carbohydrate food with other energy sources (so that they became low carbohydrate eaters with hypertension) leading to the phenomenon of lower odds of hypertension in moderate carbohydrate eaters.
+That is, they were potentially both late eaters, however, with increased age (and so with increased health-related problems/concerns) some of the individuals modified their habits,  replacing carbohydrate food with other energy sources (so that they became low carbohydrate eaters) leading to the phenomenon of lower odds of hypertension in moderate carbohydrate eaters.
+This phenomenon may be supported by some current trend in following low carbohydrate diets (ketogenic diets) which was found actually with limited weight losing effect and even associated with adverse event such as nonalcoholic fatty liver disease (NAFLD), and insulin resistance \parencite{kosinski2017effects}.
 Although these hypotheses cannot be determined by the cross-sectional data from NDNS RP, if they are true, the energy sources individuals used to replace carbohydrate in their diet were apparently not wisely chosen.
 
-Among women, living with a partner was an interaction factor for the associations between carbohydrate eating patterns and BMI and abdominal obesity (WC).
+Among women, relationship status acted as an interaction factor influencing the associations between carbohydrate eating patterns and BMI and abdominal obesity (WC).
 Directions of the associations were opposite to each other depending on whether women were living with a partner or not.
@@
 High carbohydrate eaters who lived with partners had lower BMI and WC than low carbohydrate eaters, while moderate carbohydrate eaters who lived alone had higher WC than their low carbohydrate eating counterparts, after adjustment of age, education level, smoking status, total energy intake, and alcohol consumption.
-High carbohydrate eaters who were characterised with high and early daily energy consumption and low fat and alcohol intake may reflect a healthier diet and lifestyle, but this might be different between women who lived alone and those who lived with their partners.
-It was often assumed that living alone may be associated with a lower diversity of food intake and a higher likelihood of having an unhealthy dietary choice \parencite{hanna2015relationship}.
-Therefore, there may be differences in the actual contents consumed in their high carbohydrates, or there may be other social, psychological or lifestyle-related factors related with living alone which were not measured or did not include in the models.
+High carbohydrate eaters who were characterised by high and early daily energy consumption and low fat and alcohol intake may reflect a healthier diet and lifestyle, but this might be different between women who lived alone and those who lived with their partners.
+It was often assumed that living alone may be associated with a lower diversity of food intake and a higher likelihood of having unhealthy dietary choices \parencite{hanna2015relationship}.
+Therefore, there may be differences in the actual contents consumed in their high carbohydrates, or there may be other social, psychological or lifestyle-related factors related with living alone which were not measured or were not included in the models.
 Since the inverse association between high carbohydrate eating pattern and BMI or abdominal obesity were only observed among women who lived with partners, further investigation of this hypothesis is needed.
@@
 Since one's diet might change according to the season, day of the week (weekdays or weekends), or sometimes depend on what one had consumed the day before, exchangeability of daily diaries is a strong assumption and cannot be overcome by the MLCA models adopted here.
-Other statistical Other statistical techniques which could take the order or the longitudinal nature of the data into account, such as repeated measures latent class analysis (RMLCA), latent transition analysis (LTA)\parencite{collins2010latent}, or latent class growth analysis (LCGA) \parencite{davidian2008growth,jung2008introduction,andruff2009latent} are not applicable for the NDNS RP dataset.
+Other statistical techniques which could take the order or the longitudinal nature of the data into account, such as repeated measures latent class analysis (RMLCA), latent transition analysis (LTA)\parencite{collins2010latent}, or latent class growth analysis (LCGA) \parencite{davidian2008growth,jung2008introduction,andruff2009latent} are not applicable for the NDNS RP dataset.
 The NDNS RP participants were allowed to choose which days to begin their food diaries, but the alternative models above would require that the 3 or 4 repeated measurements of food diaries be recorded at the same time points longitudinally.
@@
 However, whether this advantage can be extended to MLCA in the current project is unknown.
-Also, because the associations between the latent classes and distal outcomes (hypertension, and obesity) are still under exploration, appropriate covariates for an inclusive LCA model may not be known or yet knowable.
+Also, because the associations between the latent classes and distal outcomes (hypertension, and obesity) are still under exploration, appropriate covariates for an inclusive LCA model may not be known.
 Thus, as a first step, given the complexity of the NDNS RP dataset itself, we chose to fit the MLCA models without any covariate in either day level or individual level models.
@@
 Third, detailed information on the occupations of the participants was not available and thus we could not account for those who had shift or night work.
-But considering that completing a 4-consecutive-day food diary may be a large burden for all participants, those with shift or night work might be less able to comply and complete their diary for at least 3 days.
-Unfortunately, this hypothesis cannot be verified in the NDNS RP dataset.
+But considering that completing a 4-consecutive-day food diary may be a large burden for all participants, those with shift or night work might be less able to comply and complete their diary for at 4 days.
+However, the latter hypothesis cannot be verified in the NDNS RP dataset.
 If people on shifts were included in the NDNS RP sample, the classification in both levels, as well as their associations with either hypertension or BMI would be biased.
-Furthermore, under-reporting due to the burden of writing down everything eaten at each occasion is also a concern in the food diaries collected.
+Furthermore, under-reporting due to the burden of recording food and drink intake for 4 days for each occasion is also a concern in the current survey.
 To evaluate the influence of under-reporting in the NDNS RP sample, the study team of NDNS RP conducted a doubly labelled water (DLW) sub-study within the survey.
 The details of this sub-study can be accessed from the Appendix X of the Official Reports provided by Public Health England \parencite{bates2014national,roberts2018national,NDNSofficial}.
-Briefly, in healthy adults, if, for a given period of time, energy consumed in food matches total energy expended, they are in energy balance.
-In NDNS RP sub-study, estimates of energy intake (EI) from the four-day diary were compared with measurements of total energy expenditure (TEE) using the DLW technique in a sub-sample of survey participants.
-Results of the sub-study showed reasonable agreement between EI and TEE (overall ratio: 0.73).
-Reasons such as misreporting of actual consumption, under-reporting or modified usual intake due to the burden of the survey/DLW sub-study may contribute to under-reporting of their EI.
-We cannot extrapolate the estimated under-reporting to the whole sample since other individuals' diet might be affected by under-reporting differentially.
+In the sub-study, there is an assumption that in healthy adults, if energy consumed in food matches total energy expended over a given time period, the individuals are deemed to be in energy balance.
+In NDNS RP sub-study, estimates of energy consumption from the 4 day diaries were compared with measurements of total energy expenditure (TEE) using the DLW technique in a sub-sample of survey participants.
+Results of the sub-study showed reasonable agreement between energy consumed and TEE (overall ratio: 0.73), indicating some potential mis-reporting.
+Reasons such as mis-reporting of actual consumption, under-reporting or modified usual intake due to the burden of the survey/DLW sub-study may contribute to under-reporting of their energy consumed.
+We cannot extrapolate the estimated under-reporting to the whole sample since other individuals' diet might be differentially affected by under-reporting.
+Moreover, within NDNS RP, it is not possible to differentiate between under-reporting due to ill health vs.
+actual mis-reporting.
+Subsequently, most previous studies using data from the NDNS RP do not adjust for under-reporting of nutrients intake in the models.
 
-Last, it should be noted that findings from data-driven, exploratory methods may not be
-generalizable to populations in other countries, since the carbohydrate eating patterns in both day level and individual level probably only represent the socio-cultural and lifestyle characteristics of the adult population in the UK.
+Last, it should be noted that the findings from data-driven, exploratory methods may not be
+generalizable to populations in other countries, since the carbohydrate eating patterns in both day level and individual level may only reflect the dietary habits of the current population.
+The latter in turn provide a reflection of the socio-cultural and lifestyle characteristics of the adult population in the UK.
 Further research is warranted to explore and better understand the eating patterns in other populations.
-In particular, the cross-sectional study design also prevented us from deducing any causal effect between the carbohydrate eating patterns and hypertension, BMI or abdominal obesity.
+In particular, the cross-sectional study design prevented us from deducing any causal effect between the carbohydrate eating patterns and respective health outcomes including hypertension, BMI or abdominal obesity.
 
-Strengths of this study include the large, nationally representative sample of men and women in the UK.
+Strengths of this study include the large, nationally representative sample of UK men and women.
 We applied a novel, objective approach using MLCA to examine the carbohydrate eating patterns while applying standardised criteria to determine the number of latent classes.
 The process of finding the classifications through model-based, data-driven procedure minimises reliance on researchers' preconceived notions of eating patterns.
-Eating patterns were determined from 4 consecutive days of well-designed, fully-examined food diaries.
+Eating patterns were determined from 4 consecutive days of well-designed, fully-examined food diaries that provided detailed information of what and when food and drinks were eaten.
 MLCA correctly accounted for the multilevel structure of the data, where the 4-day diet diaries were nested within the participants.
-Our findings also captured the day-to-day variation of following different carbohydrate eating patterns within individuals.
-Moreover, the examination of associations between the individual level carbohydrate eating patterns and hypertension, BMI, abdominal obesity were conducted correctly considering the probability of participant selection and the clustered survey design.
-Health outcomes such as weight, height, waist circumferences, and blood pressure, diabetes status were measured by trained nurses and blood tests which could also minimise bias caused by misclassification and under-reporting of these measurements.
+Our findings also captured the day-to-day variation of the respective carbohydrate eating patterns within individuals.
+Moreover, the examination of associations between the individual level carbohydrate eating patterns and hypertension, BMI, abdominal obesity took the complex and the clustered survey design into consideration, in addition to accounting for participant non-response to survey.
+Health outcomes such as weight, height, waist circumferences, and blood pressure, diabetes status were measured objectively by trained nurses in addition to lipid profile, glucose, and HbA1C being measured in blood.
+These approaches have an advantage over self-reported measurements as they may minimise bias caused by misclassification and under-reporting.
 
@@
 
-We have successfully defined carbohydrate eating patterns in the general population in the UK adults using the NDNS RP database in both observation day level and individual level.
-Low carbohydrate eaters tended to consume more energy through fat and alcohol than other groups.
-Moderate carbohydrate eaters consumed the lowest total energy, and tended to have later in the day.
-High carbohydrate eaters consumed most of their carbohydrate as well as energy earlier in the day.
-These dietary patterns specifically for carbohydrate intake were found to differ by timing, quantity, and contributions to energy consumption.
-Compared with low carbohydrate eaters, men with a moderate carbohydrate eating pattern may associate with a lower prevalence of hypertension; women in this latent class who lived alone may associate with a larger waist circumference.
+We have successfully defined carbohydrate eating patterns in the general population in UK adults using the NDNS RP database in both observation day level and individual level.
+Low carbohydrate eaters tended to have higher energy intake from fat and alcohol compared to other types of carbohydrate eaters.
+Moderate carbohydrate eaters reported the lowest total daily energy intake, and tended to have a higher energy intake later in the day.
+High carbohydrate eaters obtained most of their carbohydrate as well as energy earlier in the day.
+These eating patterns specifically for carbohydrate intake were found to differ by timing, quantity, and contributions to energy consumption.
+Compared with low carbohydrate eaters, men with a moderate carbohydrate eating pattern had a lower prevalence of hypertension.
+Women in moderate carbohydrate eating pattern and lived alone had a larger waist circumference compared with low carbohydrate eaters.
 Among women who lived with partners, a high carbohydrate eating pattern was associated with both lower BMI and smaller waist circumferences.
-Longitudinally designed studies are needed to investigate whether the eating patterns themselves are changing over time and to study how such circadian eating patterns may relate to the change of blood pressure, obesity, and other health outcomes (incidence of cancer, cardiovascular diseases, or mortality).
+Longitudinal studies are needed to investigate whether the identified eating patterns themselves are changing over time and to study how such circadian eating patterns may relate to the change of blood pressure, obesity, and other health outcomes (incidence of cancer, cardiovascular diseases, or mortality).

### 2018-08-31 paper/main.tex
paper modified accordingly

@@
 In men, moderate-carb eaters may have lower odds of having hypertension compared with low-carb eaters (adjusted OR: 0.64, 95\%CI: 0.41, 1.01).
-In women, high-carb eaters lived with partners had both lower BMI (-1.76 kg/m\textsuperscript{2}, -2.87, -0.73) and WC (-4.71 cm, -7.00, -2.43) compared with low-carb eaters, although these inverse associations were not observed in women who lived alone (\textit{p} for interaction 0.014, and 0.009).
+In women, high-carb eaters who lived with partners had both lower BMI (-1.76 kg/m\textsuperscript{2}, -2.87, -0.73) and WC (-4.71 cm, -7.00, -2.43) compared with low-carb eaters, although these inverse associations were not observed in women who lived alone (\textit{p} for interaction 0.014, and 0.009).
 
@@
 Low-carb eaters probably followed the diet out of health purposes but they may have chosen fat or alcohol as replacements of carb, which could probably be a concern from a public health point of view.
-Whether these circadian carb-eating patterns are associated with changes in blood pressure and/or obesity longitudinally should be further investigated.
+Whether these carb-eating patterns are associated with changes in blood pressure and/or obesity longitudinally should be further investigated.
 
@@
 \textbf{AIC} & \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
-\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated haemoglobin \\
+\textbf{HbA1C} & Haemoglobin \textbf{A1C}: Glycated haemoglobin \\
 %\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\

### 2018-09-01 paper/Chapters/Chapter2.tex
grammarly checked

@@
 
-Participants were asked to keep a record of everything eaten or drunk over four consecutive days.
+Participants were required to keep a diary that record everything eaten or drunk over four consecutive days.
 Interviewers undertook three visits with each participant.
 At the first visit, the interviewer explained the method followed a protocol, taking participants through the sections in the diary including how to describe details of food and drink and portion size and an example day.
-The second was a brief visit to check for compliance, answer questions or deal with problems and review the diary to identify and edit possible omissions and missing detail.
+The second visit was a brief one to check for compliance, answer potential questions, and deal with problems.
+Interviewers also reviewed the diary to identify and edit possible omissions and missing detail in the food diary.
 The third visit was to collect the diary and again review and edit possible omissions.
 
-In the diary, participants were asked to record portion sizes in household measures (e.g.
+In the diary, portion sizes of food or drink eaten were asked to be recorded in household measures (e.g.
 one tablespoon of beans, one Kit Kat finger-size), or for packaged foods to note the weight indicated on the packet.
-For homemade dishes, participants were asked to record on a separate page in the diary the individual ingredients and quantities for the whole dish along with a brief description of the cooking method and how much of dish they had consumed.
+Homemade dishes were also described in the diary about their ingredients, quantities, along with a brief description of the cooking procedure and how much of the dish were consumed.
 For each eating occasion, in addition to the details of what and how much was eaten, participants were also asked to record: when was it, where they were, and who they were eating with.
@@
 	\item Carbohydrate intake = total sugars + starch; 
-	\item Where all quantities above were measured as mass in grams.
+	\item All quantities above were measured as the mass in grams.
 \end{itemize}
@@
 The inverses of these predicted probabilities were used as a set of non-response weights so that participants with a low predicted probability got a larger weight, increasing their representation in the sample.
-Then the nurse/blood sample weights were re-scaled so that the sum of the weights equalled the number of participants who had a nurse visit or who provided a blood sample.
+Then the nurse/blood sample weights were re-scaled so that the sum of which equalled the number of participants who had a nurse visit or who provided a blood sample.
 The final nurse/blood weights should, therefore, make the sample participants representative of all eligible persons in the population.
@@
 The mean of the second and third readings, taken at one-minute intervals, were used in the current report.
-Hypertension was defined as with systolic blood pressure of 140 mmHg or above, and/or diastolic blood pressure of 90 mmHg or above, and/or taking any medication specifically to reduce blood pressure.
+Hypertension was defined as with systolic blood pressure of 140 mmHg or above, or diastolic blood pressure of 90 mmHg or above, or taking any medication specifically to reduce blood pressure.
 
@@
 Blood samples were stored at 4 $^\circ$C, and sent directly by post to the Department of Haematology and Department of Clinical Biochemistry and Immunology, Addenbrooke's Hospital, Cambridge within two hours of their collection.
-Serum samples were obtained by centrifugation of the coagulated blood sample.
+Serum samples were collected by centrifugation of the coagulated blood sample.
 Serum total, High-Density Lipoprotein (HDL) and Low-Density Lipoprotein (LDL) cholesterol, triglycerides (TG), fasting blood glucose, haemoglobin HbHbA1C were measured.
@@
 However, in the NDNS RP data set, the assumption of independent observations is violated.
-Each individual completed their dietary diary for three/four consecutive days, their diary recordings were later converted into three/four vectors of categorical responses reflecting the type of carbohydrate consumption at each time slot of the day.
+Each individual completed their dietary diary for three/four consecutive days, and their diary recordings were later converted into three/four vectors of categorical responses reflecting the type of carbohydrate consumption at each time slot of the day.
 The observed sequences (observed days) are nested within the participants and therefore are not independent.
@@
 In an unconditional logistic regression model, the probability of the outcome (i.e.
-an observed high carbohydrate eating day vs.
-a low carbohydrate eating day) is constant within the individual-level, which means for each person throughout his/her survey there is some probability of following a high carbohydrate eating day.
+an observed high carbohydrate eating day vs a low carbohydrate eating day) is constant within the individual-level, which means for each person throughout his/her survey there is some probability of following a high carbohydrate eating day.
 A random effect considers the individuals (level 2) to be drawn from the adult population in the UK, and the probability of the outcome (i.e.
@@
 	\item $\beta_{0j}$ as the random intercept, for the outcome $C_{ij} = 1$; 
-	\item the random deviation of the individuals $u_{0j}$ are assumed be normally distributed (i.e.
+	\item the random deviation of the individuals $u_{0j}$ are assumed to be normally distributed (i.e.
 $u_{0j} \sim N(0, \sigma_{u_0}^2)$), the magnitude of the $u_{0j}$ variance ($\sigma_{u_0}^2$) indicates the influence of the individuals (level 2);
@@
 If the day-level LCA model (carbohydrate eating temporal pattern typologies) is best defined by $T (T \geqslant 2)$ latent classes, then $T-1$ random intercept will be specified by a two-level multinomial logistic regression model.
-Similar to the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each time slots, throughout three/four consecutive days of their survey period).
+Similar to the typical LCA models, the latent class variable in an MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each time slots, throughout three/four consecutive days of their survey period).
 Considering the latent class indicators as indicator variables ($U_{ijk}$), the MLCA model can be written as follows:\vspace{-1cm}
@@
 This approach is less computationally demanding compared with the parametric approach.
-These level 2 (individual) latent classes reflect differences in the probability of belonging to a specific day-level latent class, so that individuals that have observation days with similar probabilities for the level 1 latent classes will be grouped together.
+These level 2 (individual) latent classes reflect differences in the probability of belonging to a specific day-level latent class so that individuals that have observation days with similar probabilities for the level 1 latent classes will be grouped together.
 The non-parametric MLCA model can be defined as follows:
@@
 
-According to Finch and French's simulation study \parencite{finch2014multilevel}, non-parametric approach generally resulted in more accurate recovery of the underlying latent structure of the data at both levels and provided better latent class model compared with parametric approach.
+According to Finch and French's simulation study \parencite{finch2014multilevel}, the non-parametric approach generally resulted in a more accurate recovery of the underlying latent structure of the data at both levels and provided better latent class model compared with the parametric approach.
 In the current project, we are interested in exploring both meaningful individual (level 2) latent classes and the daily (level 1) carbohydrate consumption classification.
@@
 
-The number of classes in level 1 was determined by 1) the evaluation of model fit indices, including the Bayesian information criterion (BIC) and entropy, which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compares $q$ vs.
-$q-1$ classes models, where $q$ is the number of latent classes; most importantly, 3) pattern interpretability.
+The number of classes in level 1 was determined by 1) the evaluation of model fit indices, including the Bayesian information criterion (BIC) and entropy, which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compares $q$ vs $q-1$ classes models, where $q$ is the number of latent classes; most importantly, 3) pattern interpretability.
 In the steps of performing multilevel LCA, where LMR-LRT is not available, the same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day-level and individual-level.
@@
 
-Day-level latent classes identified by the first step of MLCA were tabulated according to the day of week and also whether the diary was recorded during weekends or not.
+Day-level latent classes identified by the first step of MLCA were tabulated according to the day of the week and also whether the diary was recorded during weekends or not.
 A contingency table giving the frequency of responses across the 7-time slots of the survey days was produced.
@@
 Point estimates of weighted means and proportions and 95\%CI of the characteristics were determined by applying either nurse visiting weights (for outcomes of hypertension, BMI, and WC) or blood sample weights (for diagnosis of DM) accordingly.
-Similarly, \textit{F} tests (for continuous variables) and adjusted Pearson $\chi^2$ tests (for categorical variables) were used to determine sex-specific differences by hypertension status, and BMI categories.
+Similarly, \textit{F} tests (for continuous variables) and adjusted Pearson $\chi^2$ tests (for categorical variables) were used to determine sex-specific differences by hypertension status and BMI categories.
 
@@
 Covariates that are strongly related with the outcomes but not associate with carbohydrate eating groups may reduce the standard errors and improve the precisions, so they were also considered in the linear regression models.
-	\item Confounding and/or interaction effects from each of the potential factors were checked one by one.
+	\item Confounding or interaction effects from each of the potential factors were checked one by one.
 Interaction effects were tested using the adjusted Wald test for whether the regression coefficients of the interaction terms are simultaneously equal to zero.
@@
 	\item For logistic regression models (hypertension) under the survey data, goodness-of-fit was assessed using \textit{F}-adjusted mean residual test \parencite{archer2001goodness,archer2007goodness} which is implemented in Stata using command \code{svylogitgof} \parencite{archer2006goodness}.
-Other diagnostics for regular logistic regression models, such as estimating the pseudo-R\textsuperscript{2},  AIC or BIC, checking the standardized Pearson residuals, or covariate pattern residuals are currently not available for weighted survey data.
+Other diagnostics for regular logistic regression models, such as estimating the pseudo-R\textsuperscript{2},  AIC or BIC, checking the standardised Pearson residuals, or covariate pattern residuals are currently not available for weighted survey data.
 	\item For linear regression models (WC, BMI), the assumption of independent observations is violated because of the clustered structure of the data.
@@
 	General checking such as QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance) are unneeded (also not available).
-Outliers, leverage, and Cook's distance cannot be checked either, however, participants with extreme weightings (if any) were checked by removing them and refitting the models as a sensitivity analysis.
+Outliers, leverage, and Cook's distance cannot be checked either.
+However, participants with extreme weightings (if any) were checked by removing them and refitting the models as a sensitivity analysis.
 	\item Since under complex survey designed data, the sampling-weighted least squares are not maximum likelihood, it would not be possible to compare models using likelihood ratio test.
 Instead, adjusted Wald tests with $p < 0.05$ were used as criteria for variable inclusion in the final model.
-Another Stata command \code{linktest} was used to decide whether quadratic and cubic terms of continuous variables were necessary in improving fitting of the model \parencite{pregibon1980goodness}.
+Another Stata command \code{linktest} was used to decide whether quadratic and cubic terms of continuous variables were necessary for improving the fitting of the model \parencite{pregibon1980goodness}.
 \end{enumerate}

### 2018-09-01 paper/Chapters/Chapter3.tex
grammarly checked

@@
 However, the improvement of BIC dropped to less than 1000 from 3 class to 4 class solutions (658.9) and from 4 class to 5 class solutions (361.7).
-Entropy index indicates that the 4 class model could explain about 51\% percent of the data, while \textit{p} values of Lo-Mendell-Rubun LRT suggest that the more classes we fit, the better model we will have until up to 6 classes (\textit{p} = 0.06 and is not shown in the table).
+Entropy index indicates that the 4 class model could explain about 51\% of the data, while \textit{p} values of Lo-Mendell-Rubun LRT suggest that the more classes we fit, the better model we will have until up to 6 classes (\textit{p} = 0.06 and is not shown in the table).
 For the sake of parsimony, we only extended the model with random effects building on 2 class, 3 class, and 4 class solutions.
@@
 The results of the random effects models are presented in \textbf{Table \ref{tab:mixmodels}} under the Random effects model section.
-It is obvious that the BIC improves with the addition of random effects to account for the nested structure of the data.
+It is evident that the BIC improves with the addition of random effects to account for the nested structure of the data.
 Entropy indicates that 2 classes in the day level and 4 classes in the individual level may be the best solution mathematically.
 However, after these solutions were checked in more details, the most substantively interpretable model was found to be the 3$\times$3 random effect model, which is the model with 3 latent classes in the day level and 3 latent classes in the individual level.
-We must emphasize that different researchers may have made decisions slightly different from ours, we have provided other solutions in \textbf{Appendix \ref{AppendixC}} for reference.
+We must emphasise that different researchers may have made decisions slightly different from ours, we have provided other solutions in \textbf{Appendix \ref{AppendixC}} for reference.
 
@@
 
-As expected, consumption of total energy (7539.98 kJ), total carbohydrate (222.79 g), total sugar (98.63 g), starch (124.07 g), and non-milk extrinsic sugar (59.45 g) were the highest among high percentage carbohydrate days (all \textit{p} < 0.001).
+As expected, consumption of total energy (7539.98 kJ), total carbohydrate (222.79 g), total sugar (98.63 g), starch (124.07 g), and non-milk extrinsic sugar (59.45 g) was the highest among high percentage carbohydrate days (all \textit{p} < 0.001).
 On the other hand, the consumption of protein (73.29 g), total fat (67.24 g), and alcohol (13.80 g) were the highest in the regular meals days.
@@
 
-In the random effect models, we utilized the non-parametric approach, in which we added a level 2 (individual level) latent classes based on the random means from the level 1 (day level) latent class solution.
+In the random effect models, we utilised the non-parametric approach, in which we added a level 2 (individual level) latent classes based on the random means from the level 1 (day level) latent class solution.
 The results of the individual level LCA solution for 2 and 3 classes are presented in \textbf{Figure \ref{fig:CB2level2}}, and \textbf{\ref{fig:level2}}.
@@
 28.1\% participants fell into the low carbohydrate eaters class on the left-hand side of \textbf{Figure \ref{fig:level2}}, their recordings of food intake showed that in more than 60\% of their days, they were having "regular meals" which was characterised as with the highest amount of fat and alcohol consumptions as already described in \textbf{Table \ref{tab:day-level-features}}.
-Moderate carbohydrate eaters have comparable proportions (42.0\% vs.
-40.0\%) of high carbohydrate days and regular meals days; 18.0\% of their dietary diary was found to be low carbohydrate days.
+Moderate carbohydrate eaters have comparable proportions (42.0\% vs 40.0\%) of high carbohydrate days and regular meals days; 18.0\% of their dietary diary was found to be low carbohydrate days.
 
@@
 They had the highest total energy consumption (599.7 kJ) at night (10 pm - 6 am) across all three types of eaters.
-High carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-C)} consumed the highest total energy (929.0 kJ) during 6 am to 9 am in the morning and the lowest total energy between 10 pm to 6 am (205.5 kJ).
+High carbohydrate eaters \textbf{(Figure \ref{fig:energysourcesCB}-C)} consumed the highest total energy (929.0 kJ) during 6 am to 9 am in the morning, and the lowest total energy between 10 pm to 6 am (205.5 kJ).
 Specifically, carbohydrate contributions to total energy intake were 65.3\% (6-9 am), 56.2\% (9-12 noon), 46.2\% (12-2 pm), 50.3\% (2-5 pm), 42.5\% (5-8 pm), 44.1\% (8-10 pm), and 49.9\% (10-6 am).
@@
 They consumed more sugar and starch during 9-12 noon, 2-5 pm, 8-10 pm, and 10-6 am.
-Low carbohydrate eaters turned to have similar temporal pattern of consuming carbohydrates as the high carbohydrate eaters, but the absolute amount of fibre, sugar, free sugar, and starch consumed were usually lower than that in the high carbohydrate eaters except for time slots of 2-5 pm, and 10-6 am.
+Low carbohydrate eaters turned to have a similar temporal pattern of consuming carbohydrates as the high carbohydrate eaters, but the absolute amount of fibre, sugar, free sugar, and starch consumed were usually lower than that in the high carbohydrate eaters except for time slots of 2-5 pm, and 10-6 am.
 Strong evidence (\textit{p} < 0.001) suggested that the
@@
 Moderate carbohydrate eaters were relatively younger (\textit{p} < 0.001).
-Gender distribution across the three types of carbohydrate eaters was fairly even (\textit{p} = 0.119).
+Gender distribution across the three types of carbohydrate eaters was reasonably even (\textit{p} = 0.119).
 The distribution of the carbohydrate eater types appears to be changing with the year of survey.
@@
 No difference was found among either men or women for ethnicity.
-Strong evidence of difference was suggested in women for average household income (32741.5 \textsterling/year in non-hypertensive vs.
-27862.0 \textsterling/year in hypertensive, \textit{p} < 0.001), and physical activity level (geometric mean: 0.81 hours/day in non-hypertensive compared with 0.53 hours/day in hypertensive, \textit{p} < 0.001) but not in men.
+Strong evidence of difference was suggested in women for average household income (32741.5 \textsterling/year in non-hypertensive vs 27862.0 \textsterling/year in hypertensive, \textit{p} < 0.001), and physical activity level (geometric mean: 0.81 hours/day in non-hypertensive compared with 0.53 hours/day in hypertensive, \textit{p} < 0.001) but not in men.
 Interestingly, in both sexes, hypertensive participants had a higher proportion of being classified as low or high carbohydrate eaters; total energy and carbohydrate intake were higher in people without hypertension (\textit{p} < 0.001).
@@
 \textbf{Table \ref{tab:tab1BMI}} shows the characteristics of participants according to their obesity status stratified by sex.
-The survey design-weighted prevalence for being overweight and obese in the UK adults were estimated to be 43.4\% and 25.7\% in men, and 30.9\% and 27.4\% in women.
+The survey design-weighted prevalences for being overweight and obese in the UK adults were estimated to be 43.4\% and 25.7\% in men, and 30.9\% and 27.4\% in women.
 Obviously, abdominal obesity (WC) increased significantly with the elevated BMI level in both men and women.
@@
 However, for women who were living alone, moderate carbohydrate eaters had 3.17 cm (95\%CI: 0.05, 6.30, \textit{p} = 0.047) larger WC on average compared with low carbohydrate eaters.
-The evidence for the positive association between moderate carbohydrate eaters and WC in women became weaker, but still had borderline significance when excluding diabetic women (3.08 cm, 95\%CI: -0.09, 6.25, \textit{p} = 0.057).
+The evidence for the positive association between moderate carbohydrate eaters and WC in women became weaker but still had borderline significance when excluding diabetic women (3.08 cm, 95\%CI: -0.09, 6.25, \textit{p} = 0.057).
 

### 2018-09-01 paper/Chapters/Chapter4.tex
grammarly checked

@@
 Surprisingly, low carbohydrate eaters whose dietary recordings suggested that they were mostly following a regular temporal meals pattern turned out to be consuming the highest amount of total energy among the three types of carbohydrate eaters.
-Detailed profiling of energy composition according to the time slots revealed that low carbohydrate eaters actually had a higher proportion of energy contributed by both alcohol and fat across the 7 time slots.
+Detailed profiling of energy composition according to the time slots revealed that low carbohydrate eaters had a higher proportion of energy contributed by both alcohol and fat across the 7 time slots.
 A high percentage of fat consumption was shown in all 7-time slots, energy coming from alcohol exceeded more than one-fifth of the total energy after 8 pm.
@@
 They consumed the highest amount of carbohydrates and also total energy among three types of carbohydrate eaters during the following time slots: 9-12 noon, 2-5 pm, 8-10 pm, and 10pm-6am.
-These individuals in the NDNS RP were younger, largely single, with lower average income, and lower education level.
+These individuals in the NDNS RP were younger, mostly single, with lower average income, and lower education level.
 They might correspond to the "late eaters" defined by previous studies \parencite{leech2017temporal, mansukhani2018investigating}.
@@
 That is, they were potentially both late eaters, however, with increased age (and so with increased health-related problems/concerns) some of the individuals modified their habits,  replacing carbohydrate food with other energy sources (so that they became low carbohydrate eaters) leading to the phenomenon of lower odds of hypertension in moderate carbohydrate eaters.
-This phenomenon may be supported by some current trend in following low carbohydrate diets (ketogenic diets) which was found actually with limited weight losing effect and even associated with adverse event such as nonalcoholic fatty liver disease (NAFLD), and insulin resistance \parencite{kosinski2017effects}.
+This phenomenon may be supported by some current trend in following low carbohydrate diets (ketogenic diets) which were found actually with limited weight losing effect and even associated with adverse events such as nonalcoholic fatty liver disease (NAFLD), and insulin resistance \parencite{kosinski2017effects}.
 Although these hypotheses cannot be determined by the cross-sectional data from NDNS RP, if they are true, the energy sources individuals used to replace carbohydrate in their diet were apparently not wisely chosen.
@@
 Directions of the associations were opposite to each other depending on whether women were living with a partner or not.
-This interaction effect was more obvious when looking at abdominal obesity measurement.
+This interaction effect was more noticeable when looking at abdominal obesity measurement.
 High carbohydrate eaters who lived with partners had lower BMI and WC than low carbohydrate eaters, while moderate carbohydrate eaters who lived alone had higher WC than their low carbohydrate eating counterparts, after adjustment of age, education level, smoking status, total energy intake, and alcohol consumption.
@@
 In the multilevel analyses, these 3 or 4 days' observations were treated as if they were exchangeable in the models.
-Since one's diet might change according to the season, day of the week (weekdays or weekends), or sometimes depend on what one had consumed the day before, exchangeability of daily diaries is a strong assumption and cannot be overcome by the MLCA models adopted here.
+Since one's diet might change according to the season, day of the week (weekdays or weekends), or sometimes depending on what one had consumed the day before, exchangeability of daily diaries is a strong assumption and cannot be overcome by the MLCA models adopted here.
 Other statistical techniques which could take the order or the longitudinal nature of the data into account, such as repeated measures latent class analysis (RMLCA), latent transition analysis (LTA)\parencite{collins2010latent}, or latent class growth analysis (LCGA) \parencite{davidian2008growth,jung2008introduction,andruff2009latent} are not applicable for the NDNS RP dataset.
@@
 The other approach is multiple pseudo-class draws \parencite{wang2005residual}, which was proposed in an attempt to account for uncertainty in class assignment.
-However, the maximum probability rule is still believed to be able to minimize the number of incorrect assignments \parencite{goodman20071}.
+However, the maximum probability rule is still believed to be able to minimise the number of incorrect assignments \parencite{goodman20071}.
 A Monte Carlo simulation study \parencite{bray2015eliminating} demonstrated that maximum probability assignment is less biased than multiple pseudo-class draws.
-Moreover, this simulation study also found that an inclusive LCA (i.e.
+
+Moreover, the Monte Carlo simulation study \parencite{bray2015eliminating} also found that an inclusive LCA (i.e.
 LCA with covariates) would probably perform better than non-inclusive LCA and has the potential to reduce bias of class assignment.
@@
 
-Third, detailed information on the occupations of the participants was not available and thus we could not account for those who had shift or night work.
-But considering that completing a 4-consecutive-day food diary may be a large burden for all participants, those with shift or night work might be less able to comply and complete their diary for at 4 days.
+Third, detailed information on the occupations of the participants was not available, and thus we could not account for those who had a shift or night work.
+But considering that completing a 4-consecutive-day food diary may be a tremendous burden for all participants, those with shift or night work might be less able to comply and complete their diary for at 4 days.
 However, the latter hypothesis cannot be verified in the NDNS RP dataset.
 If people on shifts were included in the NDNS RP sample, the classification in both levels, as well as their associations with either hypertension or BMI would be biased.
+
 Furthermore, under-reporting due to the burden of recording food and drink intake for 4 days for each occasion is also a concern in the current survey.
-To evaluate the influence of under-reporting in the NDNS RP sample, the study team of NDNS RP conducted a doubly labelled water (DLW) sub-study within the survey.
+To evaluate the influence of under-reporting in the NDNS RP sample, the study team conducted a doubly labelled water (DLW) sub-study within the survey.
 The details of this sub-study can be accessed from the Appendix X of the Official Reports provided by Public Health England \parencite{bates2014national,roberts2018national,NDNSofficial}.
 In the sub-study, there is an assumption that in healthy adults, if energy consumed in food matches total energy expended over a given time period, the individuals are deemed to be in energy balance.
-In NDNS RP sub-study, estimates of energy consumption from the 4 day diaries were compared with measurements of total energy expenditure (TEE) using the DLW technique in a sub-sample of survey participants.
-Results of the sub-study showed reasonable agreement between energy consumed and TEE (overall ratio: 0.73), indicating some potential mis-reporting.
-Reasons such as mis-reporting of actual consumption, under-reporting or modified usual intake due to the burden of the survey/DLW sub-study may contribute to under-reporting of their energy consumed.
+Using the DLW technique, total energy expenditure (TEE) from a sub-sample of NDNS RP participants were measured and compared with the estimates of energy consumption from their 4 day diaries.
+Results of the sub-study showed reasonable agreement between energy consumed and TEE (overall ratio: 0.73), indicating some potential misreporting.
+Reasons such as misreporting of actual consumption, under-reporting or modified usual intake due to the burden of the survey/DLW sub-study may contribute to under-reporting of their energy consumed.
 We cannot extrapolate the estimated under-reporting to the whole sample since other individuals' diet might be differentially affected by under-reporting.
-Moreover, within NDNS RP, it is not possible to differentiate between under-reporting due to ill health vs.
-actual mis-reporting.
+Moreover, within NDNS RP, it is not possible to differentiate between under-reporting due to ill health vs actual misreporting.
 Subsequently, most previous studies using data from the NDNS RP do not adjust for under-reporting of nutrients intake in the models.
@@
 generalizable to populations in other countries, since the carbohydrate eating patterns in both day level and individual level may only reflect the dietary habits of the current population.
-The latter in turn provide a reflection of the socio-cultural and lifestyle characteristics of the adult population in the UK.
+The latter reflect the socio-cultural and lifestyle characteristics of the adult population in the UK.
 Further research is warranted to explore and better understand the eating patterns in other populations.
@@
 Low carbohydrate eaters tended to have higher energy intake from fat and alcohol compared to other types of carbohydrate eaters.
-Moderate carbohydrate eaters reported the lowest total daily energy intake, and tended to have a higher energy intake later in the day.
+Moderate carbohydrate eaters reported the lowest total daily energy intake and tended to have a higher energy intake later in the day.
 High carbohydrate eaters obtained most of their carbohydrate as well as energy earlier in the day.

### 2018-09-01 paper/main.tex
grammarly checked

@@
 
-%\noindent Signed: \;\;\;\;\;\;\includegraphics[height=2.5\baselineskip]{Figures/signature.png}\\
-%\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
-%
-%\noindent Date: \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;2018-09-05\\
-%\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
+\noindent Signed: \;\;\;\;\;\;\includegraphics[height=2.5\baselineskip]{Figures/signature.png}\\
+\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
+
+\noindent Date: \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;2018-09-05\\
+\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
 \end{declaration}
@@
 
-%I would also like to thank Aichi Medical Univeristy, and Egashira Hospitality Public Interest Foundation for funding my studentship at the London School of Hygiene and Tropical Medicine. \\
+I would also like to thank Aichi Medical Univeristy for funding my studentship at the London School of Hygiene and Tropical Medicine. \\
+
+%and Egashira Hospitality Public Interest Foundation
 
@@
 \textbf{Background:}
-Recent evidence suggested that there are 3 types of eaters (grazers, early eaters, and late eaters) according to the timing of energy consumption.
+Recent evidence suggested that there are three types of eaters (grazers, early eaters, and late eaters) according to the timing of energy consumption.
 This project aims at finding both timing and quantity eating patterns specifically for carbohydrate (carb) intake, and exploring their potential associations with hypertension and obesity.
@@
 Contrary to the expectation, profiles of high-carb eaters seemed to be healthier among three types of carb eaters.
-Low-carb eaters probably followed the diet out of health purposes but they may have chosen fat or alcohol as replacements of carb, which could probably be a concern from a public health point of view.
-Whether these carb-eating patterns are associated with changes in blood pressure and/or obesity longitudinally should be further investigated.
+Low-carb eaters probably followed the diet out of health purposes, but they may have chosen fat or alcohol as replacements of carb, which could possibly be a concern from a public health point of view.
+Whether these carb-eating patterns are associated with changes in blood pressure or obesity longitudinally should be further investigated.
 

### 2018-09-01 paper/Chapters/Chapter2.tex
pdf prepared to be submitted

@@
 At the first visit, the interviewer explained the method followed a protocol, taking participants through the sections in the diary including how to describe details of food and drink and portion size and an example day.
-The second visit was a brief one to check for compliance, answer potential questions, and deal with problems.
-Interviewers also reviewed the diary to identify and edit possible omissions and missing detail in the food diary.
+The second visit was a brief one to check for compliance, and answer potential questions from the participants.
+Interviewers also reviewed the diary to identify and edited possible omissions and missing detail in the food diary.
 The third visit was to collect the diary and again review and edit possible omissions.

### 2018-09-04 paper/main.tex
pdf prepared to be submitted
before preparing final submission

@@
 
-I would also like to thank Aichi Medical Univeristy for funding my studentship at the London School of Hygiene and Tropical Medicine. \\
+%I would also like to thank Aichi Medical Univeristy for funding my studentship at the London School of Hygiene and Tropical Medicine. \\
 
@@
 High-carb eaters consumed most of their carb and energy within time slots of 6-9 am, 12-2 pm and 5-8 pm.
-In men, moderate-carb eaters may have lower odds of having hypertension compared with low-carb eaters (adjusted OR: 0.64, 95\%CI: 0.41, 1.01).
-In women, high-carb eaters who lived with partners had both lower BMI (-1.76 kg/m\textsuperscript{2}, -2.87, -0.73) and WC (-4.71 cm, -7.00, -2.43) compared with low-carb eaters, although these inverse associations were not observed in women who lived alone (\textit{p} for interaction 0.014, and 0.009).
+In men, moderate-carb eaters may have lower odds of having hypertension compared with low-carb eaters (OR: 0.64, 95\%CI: 0.41, 1.01).
+In women, high-carb eaters who lived with partners had both lower BMI (-1.76 kg/m\textsuperscript{2}, 95\%CI: -2.87, -0.73) and WC (-4.71 cm, 95\%CI: -7.00, -2.43) compared with low-carb eaters, although these inverse associations were not observed in women who lived alone (\textit{p} for interaction 0.014, and 0.009).
 

### 2018-09-04 paper/Chapters/Chapter2.tex
right before submission checked once more

@@
 The second visit was a brief one to check for compliance, and answer potential questions from the participants.
-Interviewers also reviewed the diary to identify and edited possible omissions and missing detail in the food diary.
+Interviewers also reviewed the diary to identify and edited possible omissions and missing details in the food diary.
 The third visit was to collect the diary and again review and edit possible omissions.
 
-In the diary, portion sizes of food or drink eaten were asked to be recorded in household measures (e.g.
+In the diary, portion sizes of food or drink consumed were asked to be recorded in household measures (e.g.
 one tablespoon of beans, one Kit Kat finger-size), or for packaged foods to note the weight indicated on the packet.
@@
 	\item Randomly select 27 or 28 addresses in that postcode area; 
-	\item Randomly select one household at that address for interviews; 
+	\item Randomly select one household at that address for interview; 
 	\item Selected addresses where children resided were randomly allocated to one of two groups to determine whether an adult (aged 19 years or older) and a child (aged 1.5 to 18 years) or a child only, were selected for interviews.
@@
 Serum samples were collected by centrifugation of the coagulated blood sample.
-Serum total, High-Density Lipoprotein (HDL) and Low-Density Lipoprotein (LDL) cholesterol, triglycerides (TG), fasting blood glucose, haemoglobin HbHbA1C were measured.
+Serum total, High-Density Lipoprotein (HDL) and Low-Density Lipoprotein (LDL) cholesterol, triglycerides (TG), fasting blood glucose, haemoglobin(Hb) A1C were measured.
 HbA1C value of 6.5\% was used as the cut off point for diagnosing diabetes.
@@
 %	\item A specific latent class is referred to as $t$, and the total number of level 1 latent classes is denoted by $T$;
-	\item $P(\mathbf{U_{ijk} = s_k}|C_{ij} = t)$ is the probability of a specific response pattern, conditional on membership in latent class $t$.
+	\item $P(\mathbf{U_{ijk} = s_k}|G_{ij} = t)$ is the probability of a specific response pattern, conditional on membership in latent class $t$.
 \end{itemize}
@@
 \begin{itemize}
-	\item First, we ignored the multilevel structure of the data and estimated a series of traditional LC models to determine the number of classes at the observational day-level;
+	\item First, we ignored the multilevel structure of the data and estimated a series of traditional LCA models to determine the number of classes at the observational day-level;
 	\item Next, a series of MLCA models were fitted to account for the multilevel structure of the data.
@@
 Descriptive statistics for the dietary day-level recordings according to the latent class memberships were presented.
-Pearson $\chi^2$ test was used to assess evidence fora difference in the distribution of categorical variables.
+Pearson $\chi^2$ test was used to assess evidence for a difference in the distribution of categorical variables.
 One-way Analysis of Variance (ANOVA) was used to compare the means across the multiple groups for continuous variables.
@@
 
-Survey-designed logistic regression models (for hypertension), and linear regression models (for WC, BMI), were used to test for associations between latent classes of carbohydrate eating patterns and hypertension, BMI, and WC, in the NDNS RP sample, separately.
+Survey-designed logistic regression models (for hypertension), and survey-designed linear regression models (for WC, BMI), were used to test for associations between latent classes of carbohydrate eating patterns and hypertension, BMI, and WC, in the NDNS RP sample, separately.
 Since diabetic participants might or might not modify their carbohydrate eating habits, we also fitted all the above-mentioned regression models restricted to those without diabetes.
@@
 those associated with both the exposure and the outcome and also not on the causal pathway were selected as potential confounders.
-Covariates that are strongly related with the outcomes but not associate with carbohydrate eating groups may reduce the standard errors and improve the precisions, so they were also considered in the linear regression models.
+Covariates that are strongly related with the outcomes but not associate with carbohydrate eating groups may reduce the standard errors and improve the precisions, so they were also considered in the survey-designed linear regression models.
 	\item Confounding or interaction effects from each of the potential factors were checked one by one.

### 2018-09-04 paper/Chapters/Chapter3.tex
pdf prepared to be submitted
right before submission checked once more

@@
 		\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
-		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & (\%) & \textbf{\Centerstack{High perc-\\entage carb}} & \textbf{\Centerstack{Low perc-\\entage carb}} & \textbf{\Centerstack{Regular\\meals}}\\
+		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & \% & \textbf{\Centerstack{High perc-\\entage carb}} & \textbf{\Centerstack{Low perc-\\entage carb}} & \textbf{\Centerstack{Regular\\meals}}\\
 		\midrule
@@
 		9 am – 12 noon &  &  &  &  &  & \\
-		& Not eating any food & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
+		& Not eating any food & 5447 & 22.3 & 0.237 & 0.079 & 0.401\\
 		& Carbohydrate $<$ 50\% & 7227 & 29.5 & 0.158 & 0.492 & 0.173\\
@@
 		& Not eating any food & 8722 & 35.6 & 0.322 & 0.291 & 0.480\\
-		& Carbohydrate $<$ 50\% & 8898 & 36.3 & 0.266 & 0.551 & 0.212\\
+		& Carbohydrate $<$ 50\% & 8898 & 36.4 & 0.266 & 0.551 & 0.212\\
 		& Carbohydrate $\geqslant$ 50\% & 6863 & 28.0 & 0.412 & 0.158 & 0.308\\
@@
 
-From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetic (diagnosed by HbA1C > 6.5\%), while the percentages of diabetes in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011), respectively.
+From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetic (diagnosed by HbA1C > 6.5\%), while the percentages of diabetes in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} = 0.011), respectively.
 Although there was some evidence (\textit{p} = 0.027) that fasting blood glucose level may be slightly higher in non-diabetic low carbohydrate eaters, the geometric mean for HbA1C was probably lower (\textit{p} = 0.010) in moderate carbohydrate eaters (5.43, 95\%CI: 5.39, 5.47).
@@
 		\bottomrule
-%		\multicolumn{5}{l}{\textit{Note: }}\\
+		\multicolumn{5}{l}{\textit{Note: }}\\
 		\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national diet and nutrition survey rolling programme;}}\\
-		\multicolumn{5}{l}{{\scriptsize BMI body mass index; WC, waist circumference; HbA1C, haemoglobin HbA1C; DM, diabetes mellitus; TC, total cholesterol, }}\\
-		\multicolumn{5}{l}{{\scriptsize HDL, high density lipoproteins; LDL, low density lipoproteins; TG, triglycerides.}} \\
-		\multicolumn{5}{l}{{\scriptsize Glucose, HbA1C, TC, HDL, LDL, TG, and physical activity were expressed in geometric means (95\% CI) because }} \\
-		\multicolumn{5}{l}{ the data were positively skewed.} \\
+		\multicolumn{5}{l}{{\scriptsize BMI body mass index; WC, waist circumference; HbA1C, haemoglobin HbA1C; DM, diabetes mellitus; TC, total }}\\
+		\multicolumn{5}{l}{{\scriptsize cholesterol; HDL, high density lipoproteins; LDL, low density lipoproteins; TG, triglycerides.}} \\
+		\multicolumn{5}{l}{{\scriptsize Glucose, HbA1C, TC, HDL, LDL, TG, and physical activity were expressed in geometric means (95\% CI) because the }} \\
+		\multicolumn{5}{l}{ {\scriptsize data were positively skewed.}} \\
 		\multicolumn{5}{l}{{\scriptsize Variables from the blood tests (glucose and HbA1C) were weighted by blood sample weights, the other variables were}}\\ 

### 2018-09-04 paper/Chapters/Chapter4.tex
right before submission checked once more

@@
 This properly accounted for the fact that for some people, their probability of following a type of food eating pattern during the survey could be higher/lower than that in the others.
-This finding also suggested that assuming a person will always follow a certain type of eating pattern is not appropriate.
+This finding also suggested that assuming a person will always follow a certain type of temporal eating pattern is not appropriate.
 
@@
 Third, detailed information on the occupations of the participants was not available, and thus we could not account for those who had a shift or night work.
-But considering that completing a 4-consecutive-day food diary may be a tremendous burden for all participants, those with shift or night work might be less able to comply and complete their diary for at 4 days.
+But considering that completing a 4-consecutive-day food diary may be a tremendous burden for all participants, those with shift or night work might be less able to comply and complete their diary for 4 days.
 However, the latter hypothesis cannot be verified in the NDNS RP dataset.
@@
 
-Furthermore, under-reporting due to the burden of recording food and drink intake for 4 days for each occasion is also a concern in the current survey.
+Furthermore, under-reporting due to the burden of recording food and drink intake for 4 days at each occasion is also a concern in the current survey.
 To evaluate the influence of under-reporting in the NDNS RP sample, the study team conducted a doubly labelled water (DLW) sub-study within the survey.
@@
 We cannot extrapolate the estimated under-reporting to the whole sample since other individuals' diet might be differentially affected by under-reporting.
-Moreover, within NDNS RP, it is not possible to differentiate between under-reporting due to ill health vs actual misreporting.
+Besides, within NDNS RP, it is not possible to differentiate between under-reporting due to ill health vs actual misreporting.
 Subsequently, most previous studies using data from the NDNS RP do not adjust for under-reporting of nutrients intake in the models.
@@
 We have successfully defined carbohydrate eating patterns in the general population in UK adults using the NDNS RP database in both observation day level and individual level.
-Low carbohydrate eaters tended to have higher energy intake from fat and alcohol compared to other types of carbohydrate eaters.
+Low carbohydrate eaters tended to have higher energy intake from fat and alcohol compared to other types of carbohydrate eaters and eating later in the day.
 Moderate carbohydrate eaters reported the lowest total daily energy intake and tended to have a higher energy intake later in the day.
@@
 These eating patterns specifically for carbohydrate intake were found to differ by timing, quantity, and contributions to energy consumption.
-Compared with low carbohydrate eaters, men with a moderate carbohydrate eating pattern had a lower prevalence of hypertension.
+Compared with low carbohydrate eaters, men with a moderate carbohydrate eating pattern may had a lower prevalence of hypertension.
 Women in moderate carbohydrate eating pattern and lived alone had a larger waist circumference compared with low carbohydrate eaters.

### 2018-09-04 paper/Figures/Figureforpaper.R
fig for abstract

@@ -933,6 +933,150 @@ library(cowplot)
 plot_grid(CB1, CB2, CB3, ncol = 1, labels = c('A', 'B', 'C'), rel_heights=c(1,1,1.38))
 
 
+# same bar plot flip the axis for abstract --------------------------------
+CB1sources$Slot <- factor(CB1sources$Slot, levels = c("10 pm – 6 am",
+                                                      "8 pm – 10 pm",
+                                                      "5 pm – 8 pm",
+                                                      "2 pm – 5 pm",
+                                                      "12 noon – 2 pm",
+                                                      "9 am – 12 am",
+                                                      "6 am – 9 am"))
+levels(CB1sources$Slot) <- c("10pm \n-6am",
+                             "8pm \n-10pm",
+                             "5pm \n-8pm",
+                             "2pm \n-5pm",
+                             "12noon \n-2pm",
+                             "9am \n-12noon",
+                             "6am \n-9am")
+
+levels(Text$Slot)<- c("10pm \n-6am",
+                      "8pm \n-10pm",
+                      "5pm \n-8pm",
+                      "2pm \n-5pm",
+                      "12noon \n-2pm",
+                      "9am \n-12noon",
+                      "6am \n-9am")
+Text$TotalEner <-  c("1622.1", "753.1", "1063.5", "2328.6", "950.8", "854.6", 
+                     "422.4")
+Text$pos <- rep(1.06, 7)
+CB1 <- ggplot() +
+  geom_bar(aes(y = pct, x = Slot, fill = Sources), data = CB1sources, width = 0.6,
+           stat="identity") +
+  geom_text(data=CB1sources, aes(x = Slot, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
+            size = 3.5, colour="black", family="Atlas Grotesk Medium") +
+  geom_text(data= Text, aes(x = Slot, y = pos, label = TotalEner), 
+            size = 3.5, colour = "black", family="Atlas Grotesk Medium") +
+  theme(#legend.position="right", #legend.direction="horizontal",
+    legend.title = element_blank(),
+    axis.text = element_text(size = 10),
+    legend.text = element_text(size = 10), 
+    axis.title = element_text(size = 10),
+    axis.line = element_line(colour = "black"),
+    plot.title=element_text(family="Atlas Grotesk Medium", size = 10),
[…]

### 2018-09-05 paper/Figures/Figureforpaper.R
graph modified

@@ -962,7 +962,7 @@ Text$pos <- rep(1.06, 7)
 CB1 <- ggplot() +
   geom_bar(aes(y = pct, x = Slot, fill = Sources), data = CB1sources, width = 0.6,
            stat="identity") +
-  geom_text(data=CB1sources, aes(x = Slot, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
+  geom_text(data=CB1sources, aes(x = Slot, y = pos, label = paste0(sprintf("%1.1f", pct*100))),
             size = 3.5, colour="black", family="Atlas Grotesk Medium") +
   geom_text(data= Text, aes(x = Slot, y = pos, label = TotalEner), 
             size = 3.5, colour = "black", family="Atlas Grotesk Medium") +
@@ -1003,7 +1003,7 @@ Text$TotalEner <-  c("1310.9", "296.9",  "1086.9", "1977.2", "1106.1", "967.9", 
 CB2 <- ggplot() +
   geom_bar(aes(y = pct, x = Slot, fill = Sources), data = CB2sources, width = 0.6,
            stat="identity") +
-  geom_text(data=CB2sources, aes(x = Slot, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
+  geom_text(data=CB2sources, aes(x = Slot, y = pos, label = paste0(sprintf("%1.1f", pct*100))),
             size = 3.5, colour="black", family="Atlas Grotesk Medium") +
   geom_text(data= Text, aes(x = Slot, y = pos, label = TotalEner), 
             size = 3.5, colour = "black", family="Atlas Grotesk Medium") +
@@ -1048,7 +1048,7 @@ Text$TotalEner <-  c("1788.8",  "929.0", "860.2", "2368.9", "785.0",  "746.4",
 CB3 <- ggplot() +
   geom_bar(aes(y = pct, x = Slot, fill = Sources), data = CB3sources, width = 0.6,
            stat="identity") +
-  geom_text(data=CB3sources, aes(x = Slot, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
+  geom_text(data=CB3sources, aes(x = Slot, y = pos, label = paste0(sprintf("%1.1f", pct*100))),
             size = 3.5, colour="black", family="Atlas Grotesk Medium") +
   geom_text(data = Text, aes(x = Slot, y = pos, label = TotalEner), 
             size = 3.5, colour = "black", family="Atlas Grotesk Medium") +

### 2018-09-05 paper/Figures/Figureforpaper.R
update fig

@@ -841,6 +841,7 @@ CB2sources$pos[1] <- -0.03
 CB2sources$pos[5] <- -0.03
 CB2sources$pos[9] <- -0.03
 CB2sources$pos[13] <- -0.03
+CB2sources$pos[17] <- -0.03
 
 CB2 <- ggplot() +
   geom_bar(aes(y = pct, x = Slot, fill = Sources), data = CB2sources, width = 0.6,
@@ -903,6 +904,8 @@ CB3sources$pos[1] <- -0.03
 CB3sources$pos[5] <- -0.03
 CB3sources$pos[9] <- -0.03
 CB3sources$pos[13] <- -0.03
+CB3sources$pos[17] <- -0.03
+
 
 CB3 <- ggplot() +
   geom_bar(aes(y = pct, x = Slot, fill = Sources), data = CB3sources, width = 0.6,
@@ -931,148 +934,6 @@ library(cowplot)
 
 
 plot_grid(CB1, CB2, CB3, ncol = 1, labels = c('A', 'B', 'C'), rel_heights=c(1,1,1.38))
-
-
-# same bar plot flip the axis for abstract --------------------------------
-CB1sources$Slot <- factor(CB1sources$Slot, levels = c("10 pm – 6 am",
-                                                      "8 pm – 10 pm",
-                                                      "5 pm – 8 pm",
-                                                      "2 pm – 5 pm",
-                                                      "12 noon – 2 pm",
-                                                      "9 am – 12 am",
-                                                      "6 am – 9 am"))
-levels(CB1sources$Slot) <- c("10pm \n-6am",
-                             "8pm \n-10pm",
-                             "5pm \n-8pm",
-                             "2pm \n-5pm",
-                             "12noon \n-2pm",
-                             "9am \n-12noon",
-                             "6am \n-9am")
-
-levels(Text$Slot)<- c("10pm \n-6am",
-                      "8pm \n-10pm",
-                      "5pm \n-8pm",
-                      "2pm \n-5pm",
-                      "12noon \n-2pm",
-                      "9am \n-12noon",
-                      "6am \n-9am")
-Text$TotalEner <-  c("1622.1", "753.1", "1063.5", "2328.6", "950.8", "854.6", 
-                     "422.4")
-Text$pos <- rep(1.06, 7)
-CB1 <- ggplot() +
-  geom_bar(aes(y = pct, x = Slot, fill = Sources), data = CB1sources, width = 0.6,
[…]

### 2018-09-05 submission/figure for abstract.R

@@ -1,0 +1,225 @@
+
+# same bar plot flip the axis for abstract --------------------------------
+ggthemr("greyscale")
+
+CB1sources$Slot <- factor(CB1sources$Slot, levels = c("10 pm – 6 am",
+                                                      "8 pm – 10 pm",
+                                                      "5 pm – 8 pm",
+                                                      "2 pm – 5 pm",
+                                                      "12 noon – 2 pm",
+                                                      "9 am – 12 am",
+                                                      "6 am – 9 am"))
+levels(CB1sources$Slot) <- c("10pm \n-6am",
+                             "8pm \n-10pm",
+                             "5pm \n-8pm",
+                             "2pm \n-5pm",
+                             "12noon \n-2pm",
+                             "9am \n-12noon",
+                             "6am \n-9am")
+
+levels(Text$Slot)<- c("10pm \n-6am",
+                      "8pm \n-10pm",
+                      "5pm \n-8pm",
+                      "2pm \n-5pm",
+                      "12noon \n-2pm",
+                      "9am \n-12noon",
+                      "6am \n-9am")
+Text$TotalEner <-  c("1622.1", "753.1", "1063.5", "2328.6", "950.8", "854.6", 
+                     "422.4")
+Text$pos <- rep(1.065, 7)
+CB1 <- ggplot() +
+  geom_bar(aes(y = pct, x = Slot, fill = Sources), data = CB1sources, width = 0.6,
+           stat="identity") +
+  geom_text(data=CB1sources, aes(x = Slot, y = pos, label = paste0(sprintf("%1.1f", pct*100))),
+            size = 3.5, colour="white", family="Atlas Grotesk Medium") +
+  geom_text(data= Text, aes(x = Slot, y = pos, label = TotalEner), 
+            size = 3.5, colour = "black", family="Atlas Grotesk Medium") +
+  geom_text(aes(y=-0.03, x="6am \n-9am", label="1.4"), size = 3.5, colour = "black",
+            family="Atlas Grotesk Medium") +
+  geom_text(aes(y=-0.03, x="9am \n-12noon", label="1.8"), size = 3.5, colour = "black",
+            family="Atlas Grotesk Medium") +
+  geom_text(aes(y=-0.03, x="12noon \n-2pm", label="3.1"), size = 3.5, colour = "black",
[…]

### 2018-09-24 paper/main.tex
renew for egashira

@@
 
-%I would also like to thank Aichi Medical Univeristy for funding my studentship at the London School of Hygiene and Tropical Medicine. \\
+I would also like to thank Aichi Medical Univeristy, and Egashira Hospitality Public Interest Foundation for funding my studentship at the London School of Hygiene and Tropical Medicine. \\
 
-%and Egashira Hospitality Public Interest Foundation
+%
 

### 2018-10-25 Memo_of_meeting.Rmd
some new meeting memo

@@
         - wtb_Y56
+
+----------
+
+**Date and time:** 2018-10-25 9:00 - 11:00 (London Time) / 17:00 - 19:00 Tokyo Time
+
+**Attendees:** Professor Luigi Palla, Chaochen Wang
+
+**Notekeeper:** Chaochen Wang
+
+**Main Topic:** Mainly about the content to include/exclude in the paper
+
+1. We talked about the grants and conferences: 
+    1.
+Conference: [Winter Conference 2018 for nutrition](https://www.nutritionsociety.org/events/winter-conference-2018-optimal-diet-and-lifestyle-strategies-management-cardio-metabolic-risk) - No response yet.
+    2.
+Conference: [CHRONONUTRITION: FROM EPIDEMIOLOGY TO MOLECULAR MECHANISM SYMPOSIUM - LONDON](https://www.bna.org.uk/mediacentre/events/chrononutrition-from-epidemiology-to-molecular-mechanism-symposium-london/) - No response yet.
+    3. Probably both will need to prepare posters.
+    4. Grants: Chao applied the JSPS-kakenhi (Japanese Government Grant), the result will be known after the New Year (probably around the end of March);
+    4. Grants: Suzana applied the Daiwa grant, the result will probably be released before December.
+
+2. We talked where to submit the paper first - to the American Journal of Clinical Nutrition
+    1. Chao will need to confirm about the requirements for authors. 
+    2. tables decisions: 
+        1. Table 3.1 (model fitting criteria) - go to supplementary
+        2. Table 3.2 (day level model solution) - removed and use figure 3.1 instead.
+        3. Table 3.3 (characteristics of day level classes) - go to supplementary
+        4. Table 3.4 (individual level Carb eating composition by time slots) - stay in the main text
+        5. Table 3.5-3.6 (social-demographic/biomedical measurement characteristics of individual level classes) - combined and stay in the main text
+        6. Table

### 2018-10-29 Rcode/data transformation.R
start reanalyses in Japan stratification by gender

@@ -4,8 +4,8 @@
 
 # Change the data path accordingly ----------------------------------------
 
-setwd("/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/") # on Ubuntu
-
+# setwd("/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/") # on Ubuntu
+setwd("/home/takeshi/ドキュメント/NDNS/UKDA-6533-stata/stata/stata11_se/") # on Ubuntu 16.04 in Japan
 # setwd("C:/Users/lsh1701745/Downloads/6533STATA11_SE/UKDA-6533-stata11_se/stata11_se/")
 
 
@@ -19,18 +19,22 @@ library(tidyverse)
 library(haven)
 
 
-data <- read_dta("ndns_rp_yr1-4a_foodleveldietarydata_uk.dta")
+data <- read_dta("ndns_rp_yr1-4a_foodleveldietarydata_uk_v2.dta")
+data14v1 <- read_dta("/home/takeshi/ドキュメント/NDNS/6533STATA11/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr1-4a_foodleveldietarydata_uk.dta")
 
-data56 <- read_dta("ndns_rp_yr5-6a_foodleveldietarydata.dta")
+data56 <- read_dta("ndns_rp_yr5-6a_foodleveldietarydata_v2.dta")
 
 data78 <- read_dta("ndns_rp_yr7-8a_foodleveldietarydata.dta")
 
 names(data)
+names(data14v1)
+
 
 names(data56)
 
 names(data78)
 
+names(data14v1)[names(data14v1)=="seriali"] <- "id"
 names(data)[names(data)=="seriali"] <- "id"
 names(data56)[names(data56)=="seriali"] <- "id"
 names(data78)[names(data78)=="seriali"] <- "id"
@@ -40,7 +44,7 @@ names(data78)[names(data78)=="seriali"] <- "id"
 # Extract the data we needed ----------------------------------------------
 
 
-df14d <- data[,c(113,1,2,3,5,6,7,8,9,21, 22, 23, 24,53, 55,57,58,59,60,61,62,63,64,65)]
+df14d <- data14v1[,c(113, 1,2,3,4,5,6,7,8,9,21, 22, 23, 24,53, 55,57,58,59,60,61,62,63,64,65)]
 
 var <- names(df14d)
 
@@ -147,8 +151,8 @@ print(new)
[…]

### 2018-10-29 Memo_of_meeting.Rmd

@@
     1.
-Conference: [Winter Conference 2018 for nutrition](https://www.nutritionsociety.org/events/winter-conference-2018-optimal-diet-and-lifestyle-strategies-management-cardio-metabolic-risk) - No response yet.
+Conference: [Winter Conference 2018 for nutrition](https://www.nutritionsociety.org/events/winter-conference-2018-optimal-diet-and-lifestyle-strategies-management-cardio-metabolic-risk) - No response yet **(But Chao may not be able to physically attend the meeting in London)**.
     2.
@@
     1. Chao will need to confirm about the requirements for authors. 
-    2. tables decisions: 
+    2. Tables decisions: 
         1. Table 3.1 (model fitting criteria) - go to supplementary
@@
         5. Table 3.5-3.6 (social-demographic/biomedical measurement characteristics of individual level classes) - combined and stay in the main text
-        6. Table
+        6. Table 3.7-3.8 (individual level latent classes' associations with hypertension) - deleted
+        7.
+Table 3.9-3.11 (individual level latent classes' associations with BMI/WC) - if we decide to include the associations with outcome, probably obesity is prefered to be included.
+Whether to stop at table 3.6 will need to be discussed again.
+    3. Figures decisions:
+        1. Figure 3.1 (day level model solution): keep in the main text
+        2. Figure 3.2-3.3 (individual level solution): we keep them in the supplementary files, but description of the chosen model (figure 3.3) is needed in the main text in words. 
+        3.
+Figure 3.4 (composition of consumption in individual solutions): stay in the main text.
+However, the one submitted in the abstract to the nutrition winter conference is prefered (i.e.
+the horizontal, black and white one).
+
+3.
+The last thing Chao and Luigi discussed was about run models (MLCA) stratified by gender.
+Especially if we decide to have the results with the health outcomes (BMI, WC) in the paper, we might consider to have individual solutions in men and women.
+However, we anticipate there is potentially little difference from what we already have in the individual level solution since in Table 3.5 we have seen that the gender distribution in each class is almost the same (50% to 50%).
+But in case the reviewers might ask about different classes solutions in men and in women, we might need to have a look at the results done stratified by this variable.
+Chao will do the analyses and keep all of us updated about the details of this additional analyses in the coming weeks.
+
+4.
+In the meantime, we plan to start preparing the manuscript and a draft that will be suitable to be submitted to AJCN by the end of December (Let's aim at submitting before attending the winter conference, I (Chao) am afraid that during the New Year's vacation, serious delay of the decision by the Journal may happen.)

### 2018-10-30 Rcode/Conduct Mplus MLCA in R.R
finally start analysing stratified by gender

@@ -1,0 +1,15 @@
+ # Date: 2018-10-29 created
+ # Date updated: "Mon Oct 29 13:39:14 2018"
+ # Objective: Conduct MLCA modelling in R using Mplus
+
+library(MplusAutomation)
+setwd("~/ドキュメント/githubprojects/LSHTMproject/Rcode/MplusCode")
+# Run LCA without multilevel structure, only day level --------------------
+
+# Class = 1
+runModels("LCA01.inp", showOutput = TRUE, Mplus_command = "/opt/mplus/8.1/mplus")
+
+# Class = 2
+runModels("LCA02.inp", showOutput = TRUE, Mplus_command = "/opt/mplus/8.1/mplus")
+
+# -> Rstudio crashes so back to work in terminals

### 2018-10-30 Rcode/data transformation.R

@@ -158,7 +158,6 @@ print(new)
 head(Energy)
 
 
-vecid<-unique(Energy$id)
 
 
 
@@ -207,9 +206,9 @@ print(new)
 Energy <- Energy %>% 
   mutate(KJcarbo = Tot_Carb*16) %>% 
   mutate(CarKJpercentage = KJcarbo/Tot_Energ) %>% 
-  mutate(Carbo = cut(CarKJpercentage, breaks = c(0, 0.50, 2), right = FALSE)) %>% 
-  mutate(Fibrecarb = Tot_Fibre/Tot_Carb)  %>% 
-  mutate(Cbfb_ratio = cut(Fibrecarb, breaks = c(0, 0.09999999, Inf), right = FALSE))
+  mutate(Carbo = cut(CarKJpercentage, breaks = c(0, 0.50, 2), right = FALSE)) #%>% 
+ # mutate(Fibrecarb = Tot_Fibre/Tot_Carb)  %>% 
+ # mutate(Cbfb_ratio = cut(Fibrecarb, breaks = c(0, 0.09999999, Inf), right = FALSE))
   # mutate(Carbo = cut(CarKJpercentage, breaks = c(0, 0.25999999999999, 0.75, 2), right = FALSE)) %>% 
   # mutate(Carbo2 = cut(CarKJpercentage, breaks = c(0, 0.25999999999999, 2), right = FALSE))
 
@@ -221,75 +220,84 @@ write.csv(Energy0, file = "Energy_slots.csv")
 
 # Energy0$Carbo <- factor(Energy0$Carbo, labels = c("Low_carb", "Med_carb", "High_carb"))
 
-Energy0$Carbo2 <- factor(Energy0$Carbo2, labels = c("Low_carb", "Med_or_high_carb"))
+# Energy0$Carbo2 <- factor(Energy0$Carbo2, labels = c("Low_carb", "Med_or_high_carb"))
 
 Energy0$Carbo <- factor(Energy0$Carbo, labels = c("< 50%", ">= 50%"))
 
-Energy0$Cbfb_ratio <- factor(Energy0$Cbfb_ratio, labels = c("< 0.1", ">= 0.1"))
+# Energy0$Cbfb_ratio <- factor(Energy0$Cbfb_ratio, labels = c("< 0.1", ">= 0.1"))
 
 
 with(Energy0, tab1(Carbo))
 # with(Energy0, summary(CarKJpercentage))
-with(Energy0, tab1(Cbfb_ratio))
[…]

### 2018-10-30 Rcode/data transformation.R
LCA level 1 only files ready for analysis

@@ -452,27 +452,16 @@ setwd("~/ドキュメント/githubprojects/LSHTMproject/Rcode")
 
 
 # export the data from R to Mplus -----------------------------------------
-write_csv(dta_all, path = "dta_NDNS_Tslots.csv")
 
 library(MplusAutomation)
 
-for (i in 6:ncol(dta_all)) 
-  if(is.factor(dta_all[,i])) 
-    levels(dta_all[,i]) <-  c( "0", "1", "2")
-
-for (i in 6:ncol(dta_all))
-  dta_all[,i] <- as.character(dta_all[,i])
-
-
-
-write_csv(dta_all, path = "dta_NDNS_Tslots.csv")
-write_delim(dta_all, path = "dta_NDNS_Tslots.dat", na = ".", delim = " ")
 
 
 CHECK <- CHECK %>% 
   mutate(id_day_n = paste(id.x, DayNo, sep = "0")) %>% 
   mutate(id_day_n = as.numeric(id_day_n)) %>% 
   mutate(Sex.x = as.numeric(Sex.x))
+
 
 
 prepareMplusData(CHECK, "Mplusdata/NDNS_Tslots.dat", 
@@ -485,11 +474,17 @@ prepareMplusData(CHECK, "Mplusdata/NDNS_Tslots.dat",
 # Filter data by gender  --------------------------------------------------
 
 
-dta_men <- dta_all %>% 
-    filter(Sex == 1)
+dta_men <- CHECK %>% 
+    filter(Sex.x == 1) %>% 
+    select(c("id.x", "DayNo", "Age.x", "H6_9.y",
+             "H9_12.y", "H12_14.y", "H14_17.y", "H17_20.y",   
+             "H20_22.y", "H22_6.y", "id_day_n"))
 
-dta_women <- dta_all %>% 
-  filter(Sex == 2)
+dta_women <- CHECK %>% 
+  filter(Sex.x == 2) %>% 
+  select(c("id.x", "DayNo", "Age.x", "H6_9.y",
+           "H9_12.y", "H12_14.y", "H14_17.y", "H17_20.y",   
+           "H20_22.y", "H22_6.y", "id_day_n"))
 
 prepareMplusData(dta_men, "Mplusdata/NDNS_Tslots_men.dat")
 prepareMplusData(dta_women, "Mplusdata/NDNS_Tslots_women.dat")

### 2018-11-15 paper/Tables/2by2Table1.Rmd
table for AJCN, 3.5+3.6 added

@@
 library(kableExtra)
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/CW2CB2results.csv", header = T, row.names = NULL, colClasses = "character")
+# dt <- read.csv("../../Tablecsv/CW2CB2results.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/CW2CB2results.csv", header = T, row.names = NULL, colClasses = "character")
+
 names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "P value [note]")
@@
 # library(kableExtra)
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/ndns_level1only.csv", header = T)
+dt <- read.csv("../../Tablecsv/ndns_level1only.csv", header = T)
 names(dt) <- c("N of classes", "N of free parameters","log-likelihood",  "AIC", "BIC", "aBIC", "Entropy", "Lo-Mendel-Rubin LRT")
@@
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/LCGA3Cresults.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/LCGA3Cresults.csv", header = T, row.names = NULL, colClasses = "character")
 names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "Latent class = 3", "P value [note]")
@@
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Mixed_7slots.csv", header = T)
+dt <- read.csv("../../Tablecsv/Mixed_7slots.csv", header = T)
 dt <- dt[,-7]
@@
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/timeslots_cw3cb3_univariate.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/timeslots_cw3cb3_univariate.csv", header = T, row.names = NULL, colClasses = "character")
 names(dt) <- c("Time slots of the day", "Responses of carbohydrate intake", "Frequency", "Precentages (%)", 
@@
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Daylevel.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/Daylevel.csv", header = T, row.names = NULL, colClasses = "character")
 names(dt) <- c(" ", "High carbohydrate day", "Low carbohydrate day", "Regular meals day", "P value[note]")
@@
 ```{r tab1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Timeslots_CW3CB3results.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/Timeslots_CW3CB3results.csv", header = T, row.names = NULL, colClasses = "character")
 names(dt) <- c("Variables", "Individual class 1 (n = 1730)", "Individual class = 2 (n = 1772)", "Individual class = 3 (n = 2653)", "P value [note]")
@@
 ```{r tab-nutri-indi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Carbslotcompo.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/Carbslotcompo.csv", header = T, row.names = NULL, colClasses = "character")
 names(dt) <- c(" ", "Low carbohydrate eaters (n = 1730)", "Moderate carbohydrate eaters (n = 1772)", "High carbohydrate eaters (n = 2653)", "P value[note]")
@@
 ```{r tab2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Timeslots_CW3CB3table2_bmiDM.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/Timeslots_CW3CB3table2_bmiDM.csv", header = T, row.names = NULL, colClasses = "character")
 names(dt) <- c("Variables", "Individual class 1 (n = 1730)", "Individual class (n = 1772)", "Individual class 3 (n = 2653)", "P value[note]")
@@
 ```{r tab1hypetension, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/hypertensiontab1.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/hypertensiontab1.csv", header = T, row.names = NULL, colClasses = "character")
 names(dt) <- c(" ", "Non-hypertensive", "Hypertensive", "P value[note]", 
@@
 ```{r tab1BMI, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/BMItab1.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/BMItab1.csv", header = T, row.names = NULL, colClasses = "character")
 names(dt) <- c(" ", "Normal weight", "Overweight", "Obese", "P value[note]", "Normal weight", "Overweight", "Obese", "P value")
@@
 ```{r tab1DM, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/DMtab1.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/DMtab1.csv", header = T, row.names = NULL, colClasses = "character")
 names(dt) <- c(" ", "Non-diabetes", "Diabetes", "P value[note]", 
@@
 ```{r survgression, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/SurveyReg.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/SurveyReg.csv", header = T, row.names = NULL, colClasses = "character")
 names(dt) <- c("Models", "Low", "Moderate", "P value[note]", "High", "P value", "Models", "Low", "Moderate", "P value", "High", "P value")
@@
 ```{r tab2HYT, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/hypertensionReg.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/hypertensionReg.csv", header = T, row.names = NULL, colClasses = "character")
 names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")
@@
 ```{r tab2BMI, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/BMItab2.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/BMItab2.csv", header = T, row.names = NULL, colClasses = "character")
 names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")
@@
 ```{r tab2WC,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/WCtab2.csv", header = T, row.names = NULL, colClasses = "character")
+dt <- read.csv("../../Tablecsv/WCtab2.csv", header = T, row.names = NULL, colClasses = "character")
 names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")

### 2018-11-15 paper/Tables/2by2Table1.tex
table for AJCN, 3.5+3.6 added

@@
 
-\section{Multilevel 2by2 table 1}\label{multilevel-2by2-table-1}
-
-\rowcolors{2}{gray!6}{white}
-
+\hypertarget{multilevel-2by2-table-1}{%
+\section{Multilevel 2by2 table 1}\label{multilevel-2by2-table-1}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
-\section{Day level only models}\label{day-level-only-models}
-
-\rowcolors{2}{gray!6}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{day-level-only-models}{%
+\section{Day level only models}\label{day-level-only-models}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
-\section{LCGA models table 1}\label{lcga-models-table-1}
-
-\rowcolors{2}{gray!6}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{lcga-models-table-1}{%
+\section{LCGA models table 1}\label{lcga-models-table-1}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
-\section{Model fit criteria}\label{model-fit-criteria}
-
-\rowcolors{2}{gray!6}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{model-fit-criteria}{%
+\section{Model fit criteria}\label{model-fit-criteria}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
-\section{Day level solution 1}\label{day-level-solution-1}
-
-\rowcolors{2}{gray!6}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{day-level-solution-1}{%
+\section{Day level solution 1}\label{day-level-solution-1}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{day-level-solution-characteristics}{%
 \section{Day level solution
-characteristics}\label{day-level-solution-characteristics}
-
-\rowcolors{2}{gray!6}{white}
-
+characteristics}\label{day-level-solution-characteristics}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
-\section{Social economic}\label{social-economic}
-
-\rowcolors{2}{gray!6}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{social-economic}{%
+\section{Social economic}\label{social-economic}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{personal-level-classes-nutrional-table}{%
 \section{personal level classes nutrional
-table}\label{personal-level-classes-nutrional-table}
-
-\rowcolors{2}{gray!6}{white}
-
+table}\label{personal-level-classes-nutrional-table}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{anthropometric-measurements-and-biochemical-analysis}{%
 \subsection{Anthropometric measurements and biochemical
-analysis}\label{anthropometric-measurements-and-biochemical-analysis}
-
-\rowcolors{2}{gray!6}{white}
-
+analysis}\label{anthropometric-measurements-and-biochemical-analysis}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
-\subsection{Hypertension table 1}\label{hypertension-table-1}
-
-\rowcolors{2}{gray!6}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{hypertension-table-1}{%
+\subsection{Hypertension table 1}\label{hypertension-table-1}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
-\subsection{BMI}\label{bmi}
-
-\rowcolors{2}{gray!6}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{bmi}{%
+\subsection{BMI}\label{bmi}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
-\subsection{DM}\label{dm}
-
-\rowcolors{2}{gray!6}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{dm}{%
+\subsection{DM}\label{dm}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{table-2-regressions-in-survey}{%
 \subsection{Table 2 regressions in
-survey}\label{table-2-regressions-in-survey}
-
-\rowcolors{2}{gray!6}{white}
-
+survey}\label{table-2-regressions-in-survey}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{table-2-regressions-for-hypertension}{%
 \subsection{Table 2 regressions for
-hypertension}\label{table-2-regressions-for-hypertension}
-
-\rowcolors{2}{gray!6}{white}
-
+hypertension}\label{table-2-regressions-for-hypertension}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{table-2-regressions-for-bmi}{%
 \subsection{Table 2 regressions for
-BMI}\label{table-2-regressions-for-bmi}
-
-\rowcolors{2}{gray!6}{white}
-
+BMI}\label{table-2-regressions-for-bmi}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
-\rowcolors{2}{white}{white}
-
+\rowcolors{2}{white}{white}
+
+\hypertarget{table-2-regressions-for-wc}{%
 \subsection{Table 2 regressions for
-WC}\label{table-2-regressions-for-wc}
-
-\rowcolors{2}{gray!6}{white}
-
+WC}\label{table-2-regressions-for-wc}}
+
+\rowcolors{2}{gray!6}{white}
 \begin{table}
@@
 \end{table}
-
 \rowcolors{2}{white}{white}

### 2018-11-15 paper/Figures/Figureforpaper.R

@@ -380,7 +380,7 @@ cls1 <- ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Time, group = Carbo,
         legend.position = "none",
         plot.title=element_text(size = 17, 
                                 face = "bold", hjust = 0.5),
-        axis.text.x=element_blank(),
+        axis.text.x=element_blank()#,
         # legend.position = "bottom",
         # legend.direction = "horizontal"
   ) + 
@@ -424,7 +424,7 @@ cls2 <- ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Time, group = Carbo,
         legend.position = "none",
         plot.title=element_text(size = 17, 
                                 face = "bold", hjust = 0.5),
-        axis.text.x=element_blank(),
+        axis.text.x=element_blank()#,
         # legend.position = "bottom",
         # legend.direction = "horizontal"
   ) + 
@@ -492,16 +492,24 @@ theme(plot.subtitle = element_text(vjust = 1),
     plot.caption = element_text(family = "Atlas Grotesk Medium", 
         size = 10, face = "bold", colour = "gray24", 
         hjust = 0, vjust = 1)) +
- labs(x = "Hours of the day")#, 
-#       caption = "Note: 
-# Grey, and white shades indicate the 7 time slots;
-# Carbohydrate < 50% indicates CH contributed less than 50% total energy intake; 
-# Carbohydrate >= 50% indicates CH contributed higher or equal to 50% total 
-#       energy intake.")
+ labs(x = "Hours of the day", 
+      caption = "Note:
+Grey, and white shades indicate the 7 time slots;
+Carbohydrate (CH) < 50% indicates CH contributed less than 50% total energy intake;
+Carbohydrate >= 50% indicates CH contributed higher or equal to 50% total
+      energy intake.")
 
 
 library(cowplot)
-plot_grid(cls1, cls2, cls3, ncol = 1, labels = c('A', 'B', 'C'), rel_heights=c(1,1,1.44))
+cls1 <- cls1 + theme(plot.margin = unit(c(0, 0, -0.5, 0), "cm"))
+cls2 <- cls2 + theme(plot.margin = unit(c(0, 0, -0.5, 0), "cm"))
+# plot_grid(cls1, cls2, rel_heights = c(1,1), ncol = 1)
+
[…]
